### 2022-01-06 paper/issta22/abstract.tex
abstract

\begin{abstract}
  Evaluating natural language model (\Nlp) on testset does with
  held-out accuracy does not explain diverse aspects of language
  capabilities, and results in overrating performace of the \Nlp
  model. In addition, it is not trivial to generate natural language
  inputs for each linguistic capability, and 
  it is even hard to measure the comprehensive
  performance of the \Nlp model for each linguistic capability because
  it is not trivial to generate natural language inputs

\end{abstract}

Although measuring held-out accuracy has been the primary approach to
evaluate generalization, it often overestimates the performance of NLP
models, while alternative approaches for evaluating models either
focus on individual tasks or on specific behaviors. Inspired by
principles of behavioral testing in software engineering, we introduce
CheckList, a taskagnostic methodology for testing NLP
models. CheckList includes a matrix of general linguistic capabilities
and test types that facilitate comprehensive test ideation, as well as
a software tool to generate a large and diverse number of test cases
quickly. We illustrate the utility of CheckList with tests for three
tasks, identifying critical failures in both commercial and
state-of-art models. In a user study, a team responsible for a
commercial sentiment analysis model found new and actionable bugs in
an extensively tested model. In another user study, NLP practitioners
with CheckList created twice as many tests, and found almost three
times as many bugs as users without it.

### 2022-01-06 python/testsuite/Search.py
debugging

@@ -427,7 +427,13 @@ class Sst:
                 selected = sorted([(s[0],s[1],s[2]) for s in req_obj.search(sents)], key=lambda x: x[0])
             # end if
         else:
-            selected = sents
+            if len(sents[0])==4:
+                selected = [(s_i,Utils.tokenize(s),l,sc) for s_i, s, l, sc in sents]
+                selected = [(s_i,Utils.untokenize(s),l,sc) for s_i, s, l, sc in selected]
+            else:
+                selected = [(s_i,Utils.tokenize(s),l) for s_i, s, l in sents]
+                selected = [(s_i,Utils.untokenize(s),l) for s_i, s, l in selected]
+            # end if
         # end if
         random.shuffle(selected)
         return selected

### 2022-01-06 python/testsuite/cfg/CFG.py

@@ -38,7 +38,7 @@ class BeneparCFG:
         left = tree._.labels
         
         if len(left)==0: # if terminal
-            re_search = re.search(r'\((\:|\,|\'\'|\`\`|\.|\-?[A-Z]+\-?|[A-Z]+\$)\s(.+)\)', tree._.parse_string)
+            re_search = re.search(r'\((\:|\,|\$|\'\'|\`\`|\.|\-?[A-Z]+\-?|[A-Z]+\$)\s(.+)\)', tree._.parse_string)
             rlabel = re_search.group(1)
             rword = re_search.group(2)
             plabel = tree._.parent._.labels[0]
@@ -100,7 +100,7 @@ class BeneparCFG:
                     rule_dict[llabel].append(_rule_dict)
                 # end if
             else:
-                re_search = re.search(f'\({llabel}\s\((\:|\,|\'\'|\`\`|\.|\-?[A-Z]+\-?|[A-Z]+\$)\s(.+)\)\)$', tree._.parse_string)
+                re_search = re.search(f'\({llabel}\s\((\:|\,|\$|\'\'|\`\`|\.|\-?[A-Z]+\-?|[A-Z]+\$)\s(.+)\)\)$', tree._.parse_string)
                 rlabel = re_search.group(1)
                 rword = re_search.group(2)
                 if (rlabel) not in rule_dict[llabel]:

### 2022-01-07 paper/issta22/abstract.tex
abstract

@@
   Evaluating natural language model (\Nlp) on testset does with
-  held-out accuracy does not explain diverse aspects of language
-  capabilities, and results in overrating performace of the \Nlp
-  model. In addition, it is not trivial to generate natural language
-  inputs for each linguistic capability, and 
-  it is even hard to measure the comprehensive
-  performance of the \Nlp model for each linguistic capability because
-  it is not trivial to generate natural language inputs
+  held-out accuracy is limited to show its quality assurance because
+  the held-out datasets are often not comprehensive. While the
+  behavioral testing over multiple general linguistic capabilities are
+  employed, it relies on manually created test cases, and is still
+  limited to measure its comprehensive performance for each linguistic
+  capability. In this work, we introduce \OurModelName, an \Nlp model
+  testing methodology. Given a linguistic capability, The
+  \OurModelName finds relevant testcases to test the linguistic
+  capability from extisting datasets as seed inputs, generates
+  sufficient number of new test cases by fuzzing the seed inputs based
+  on their context-free grammar (\Cfg). We illustrate the usefulness
+  of the \OurModelName by showing input diversity and identifying
+  critical failures in \sota models for \Nlp task. In our experiment,
+  we show that the \OurModelName generates {} more test cases with {}
+  higher diversity, and finds {} more bugs.
 
 \end{abstract}
-
-Although measuring held-out accuracy has been the primary approach to
-evaluate generalization, it often overestimates the performance of NLP
-models, while alternative approaches for evaluating models either
-focus on individual tasks or on specific behaviors. Inspired by
-principles of behavioral testing in software engineering, we introduce
-CheckList, a taskagnostic methodology for testing NLP
-models. CheckList includes a matrix of general linguistic capabilities
-and test types that facilitate comprehensive test ideation, as well as
-a software tool to generate a large and diverse number of test cases
-quickly. We illustrate the utility of CheckList with tests for three
-tasks, identifying critical failures in both commercial and
-state-of-art models. In a user study, a team responsible for a
-commercial sentiment analysis model found new and actionable bugs in
-an extensively tested model. In another user study, NLP practitioners
-with CheckList created twice as many tests, and found almost three
-times as many bugs as users without it.

### 2022-01-07 paper/issta22/abstract.tex
intro

@@
 \begin{abstract}
+
   Evaluating natural language model (\Nlp) on testset does with

### 2022-01-07 paper/issta22/intro.tex
intro

\section{Introduction}
\label{sec:intro}

\Nlp testing is crucial part for developing a reliable \Nlp model. In
\Nlp, testing is mainly used to check the ML model's performance on
\ho set with respect to the accuracy of the model. The \ho data refers
to a portion of dataset that is held out of the datasets used for
training \ml models. Generally, the \ho set is extracted via
Train-Validation-Test split.

%% One of the primary goals of training NLP models is
%% generalization. Since testing “in the wild” is expensive and does not
%% allow for fast iterations, the standard paradigm for evaluation is
%% using trainvalidation-test splits to estimate the accuracy of the
%% model, including the use of leader boards to track progress on a task
%% (Rajpurkar et al., 2016).

%% While performance on held-out data is a
%% useful indicator, held-out datasets are often not comprehensive, and
%% contain the same biases as the training data (Rajpurkar et al., 2018),
%% such that real-world performance may be overestimated (Patel et al.,
%% 2008; Recht et al., 2019). Further, by summarizing the performance as
%% a single aggregate statistic, it becomes difficult to figure out where
%% the model is failing, and how to fix it (Wu et al., 2019).

### 2022-01-07 paper/issta22/abstract.tex
intro

@@
 \begin{abstract}
-
-  Evaluating natural language model (\Nlp) on testset does with
-  held-out accuracy is limited to show its quality assurance because
-  the held-out datasets are often not comprehensive. While the
+  \Nlp (NLP) technique becomes one of the core techniques for developing
+  text analytics applications.  For developing the NLP applications,
+  the applications are required to achieve high reliability before it
+  goes to market.  The trustworthiness of the prevalent NLP
+  applications is obtained by measuring the accuracy of the
+  applications on held-out dataset.  However, evaluating NLP on
+  testset does with held-out accuracy is limited to show its quality
+  because the held-out datasets are often not comprehensive. While the
   behavioral testing over multiple general linguistic capabilities are
@@
   limited to measure its comprehensive performance for each linguistic
-  capability. In this work, we introduce \OurModelName, an \Nlp model
+  capability. In this work, we introduce \OurModelName, an NLP model
   testing methodology. Given a linguistic capability, The
   \OurModelName finds relevant testcases to test the linguistic
-  capability from extisting datasets as seed inputs, generates
+  capability from existing datasets as seed inputs, generates
   sufficient number of new test cases by fuzzing the seed inputs based
@@
   of the \OurModelName by showing input diversity and identifying
-  critical failures in \sota models for \Nlp task. In our experiment,
+  critical failures in \sota models for NLP task. In our experiment,
   we show that the \OurModelName generates {} more test cases with {}

### 2022-01-07 paper/issta22/intro.tex
intro

@@
 
-\Nlp testing is crucial part for developing a reliable \Nlp model. In
-\Nlp, testing is mainly used to check the ML model's performance on
-\ho set with respect to the accuracy of the model. The \ho data refers
-to a portion of dataset that is held out of the datasets used for
-training \ml models. Generally, the \ho set is extracted via
-Train-Validation-Test split.
+Software testing is the cruicial process when developing software.  It
+evaluates an attribute or capability of the software and determines
+that it meets the requirements by examining the behavior of the
+software under test. Software testing in the early stage of the
+development finds bugs, and fixing them saves amount of costs. In
+addition, reliable software testing methodology ensures software
+quality to users in that the software meets requirements by
+verification and validation. Regarding that, testing NLP application
+becomes important process as well in that NLP application is a branch
+of artifical intelligence software.
+
+Prevalent NLP model is evaluated via train-validation-test
+splits. train and validation set is used to train the NLP model and
+the \ho set is used for testing by measuring accuracy
+
+testing \ml becomes major
+
+\Nlp testing is crucial part for developing a reliable \Nlp
+applications. For developing \Nlp applications, testing is mainly used
+to check the ML model's performance on \ho set with respect to the
+accuracy of the model. The \ho data refers to a portion of dataset
+that is held out of the datasets used for training \ml
+models. Generally, the \ho set is extracted via Train-Validation-Test
+split.
 

### 2022-01-08 paper/issta22/intro.tex
intro

@@
 quality to users in that the software meets requirements by
-verification and validation. Regarding that, testing NLP application
-becomes important process as well in that NLP application is a branch
-of artifical intelligence software.
+verification and validation. Regarding that, NLP application is a branch
+of artifical intelligence software, and testing NLP application
+also becomes important process as well.
 
-Prevalent NLP model is evaluated via train-validation-test
+The prevalent models of NLP are evaluated via train-validation-test
 splits. train and validation set is used to train the NLP model and
-the \ho set is used for testing by measuring accuracy
+the \ho set is used for testing by measuring accuracy. The accuracy is
+a indicator of the performance of the models.
 
-testing \ml becomes major
+Despite its usefulness, the main limitation of the testing paradaigm
+is that the \ho set often overestimates the performances. Each dataset
+comes with specific biases, and the biases increase the discrepancy of
+distribution between dataset and
+real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
+on \ho set does not consider the discrepancy and it is limited to
+achieve comprehensive performrance of the NLP model. As a consequence,
+it is difficult to analyze where the errors comes
+from~\cite{wu2019errudite}.
 
-\Nlp testing is crucial part for developing a reliable \Nlp
-applications. For developing \Nlp applications, testing is mainly used
-to check the ML model's performance on \ho set with respect to the
-accuracy of the model. The \ho data refers to a portion of dataset
-that is held out of the datasets used for training \ml
-models. Generally, the \ho set is extracted via Train-Validation-Test
-split.
+On the subject of the limitation of traditional testing paradaigm, a
+number of methods have been proposed. They approach evaluating
+robustness of the model on adversarial sets~\cite{}, fairness~\cite{},
+logical consistancy~\cite{}, explanations~\cite{}, diagnostic
+datasets~\cite{}, and interactive error analysis. In addition,
+inspired by the behavioral testing of software engineering research,
+Marco \etal proposed a tool for comprehensive behavioral
+testing of NLP models~\cite{marcoACL2020checklist}
+
+%% Machine learning testing poses challenges that arise
+%% from the fundamentally different nature and construction
+%% of machine learning systems, compared to traditional (relatively more deterministic and less statistically-orientated)
+%% software systems.
+
+%% \Nlp testing is crucial part for developing a reliable \Nlp
+%% applications. For developing \Nlp applications, testing is mainly used
+%% to check the ML model's performance on \ho set with respect to the
+%% accuracy of the model. The \ho data refers to a portion of dataset
+%% that is held out of the datasets used for training \ml
+%% models. Generally, the \ho set is extracted via Train-Validation-Test
+%% split.
 

### 2022-01-09 paper/issta22/intro.tex
intro

@@
 On the subject of the limitation of traditional testing paradaigm, a
-number of methods have been proposed. They approach evaluating
-robustness of the model on adversarial sets~\cite{}, fairness~\cite{},
-logical consistancy~\cite{}, explanations~\cite{}, diagnostic
-datasets~\cite{}, and interactive error analysis. In addition,
-inspired by the behavioral testing of software engineering research,
-Marco \etal proposed a tool for comprehensive behavioral
-testing of NLP models~\cite{marcoACL2020checklist}
+number of methods have been proposed. First, multiple diagnostic
+datasets for evaluating NLP model were introduced for obtaning
+generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
+that, model is evaluated on different aspects such as robustness of
+the model on adversarial
+sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
+  rychalska2019wildnlp,iyyer2018adversarial},
+fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
+consistancy~\cite{ribeiro2019consistencyeval}, prediction
+interpretations~\cite{ribeiroSG16lime} and interactive error
+analysis~\cite{wu2019errudite}. Especially, \Chlst implements
+behavioral testing methodolgy for evaluating multiple linguistic
+capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
+introduces input-output behaviors of linguistic capabilities and
+generates behavior-guided inputs for validating the behaviors. It
+provides comprehensive behavioral testing of NLP models through a
+number of generated inputs. However, the approach only relies on
+manually generated input templates, thus the template generation
+becomes expensive and time consuming. In addition, the generated
+templates are selective and often too simple, and it is limited to
+provide restricted evaluation of linguistic capabilities. Thus, it
+does not garauntee the comprehensive evaluation.
 
-%% Machine learning testing poses challenges that arise
-%% from the fundamentally different nature and construction
-%% of machine learning systems, compared to traditional (relatively more deterministic and less statistically-orientated)
-%% software systems.
+In this paper, we present \Model, an automated NLP model evaluation
+method for comprehensive behavioral testing of NLP models on \sa
+task. For each behavior of linguistic capability, \Model does not rely
+on the manual input generation. Instead, it establishes input
+requirement for evaluating a linguistic capability and finds suitable
+inputs that meet the requirement from existing public dataset.
+Therefore, \Model increases input diversity and generality. Further,
+\Model applies the fuzzing testing principle to generate inputs by
+mutating the selected inputs as seed inputs. Fuzzer in \Model first
+expands seed input grammar structures and determines its available
+\pos to maintain structural naturalness. After that, to hold
+contextual naturalness of the mutated inputs, the fuzzer completes the
+expanded new structures via data-driven context-aware word
+suggestion. Additionally, sentiment-independent words in the inputs
+are replaced with rule-based word suggestion.
 
-%% \Nlp testing is crucial part for developing a reliable \Nlp
-%% applications. For developing \Nlp applications, testing is mainly used
-%% to check the ML model's performance on \ho set with respect to the
-%% accuracy of the model. The \ho data refers to a portion of dataset
-%% that is held out of the datasets used for training \ml
-%% models. Generally, the \ho set is extracted via Train-Validation-Test
-%% split.
-
-%% One of the primary goals of training NLP models is
-%% generalization. Since testing “in the wild” is expensive and does not
-%% allow for fast iterations, the standard paradigm for evaluation is
-%% using trainvalidation-test splits to estimate the accuracy of the
-%% model, including the use of leader boards to track progress on a task
-%% (Rajpurkar et al., 2016).
-
-%% While performance on held-out data is a
-%% useful indicator, held-out datasets are often not comprehensive, and
-%% contain the same biases as the training data (Rajpurkar et al., 2018),
-%% such that real-world performance may be overestimated (Patel et al.,
-%% 2008; Recht et al., 2019). Further, by summarizing the performance as
-%% a single aggregate statistic, it becomes difficult to figure out where
-%% the model is failing, and how to fix it (Wu et al., 2019).
+We demonstrate its generality and utility as a NLP model evaluation
+tool by evaluating well-known \sa models: \Bert~\cite{devlin2019bert},
+\Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
+We show that

### 2022-01-10 paper/issta22/experiment.tex
exp outline

\section{Experiment}
\label{sec:experiment}

In this section, we present experiments to
evaluate the effectiveness of our proposed evaluation methodology. In
particular, we address the following research questions:

\begin{enumerate}
  \item[\textbf{RQ1}:] How effective is our proposed evaluation model
    for generating diverse test cases? % self bleu score

  \item[\textbf{RQ2}:] How effective is our new test case generation
    using \cfg expansion?
  \item[\textbf{RQ3}:] How effective is our proposed evaluation model
    for finding failures given a linguistic capability?
\end{enumerate}

\subsection(Experiment Setup}

For \sa task, input requirements are given for each linguistic
capability. Based on the requirements, \Model generates templates and
lexicons.
\MyPara{Model}
\Bert, \Roberta, \Dbert

\MyPara{Dataset}
reference CFG generation: Treebank corpus
word sentiments: sentiwordnet (https://github.com/aesuli/SentiWordNet)
cfg parser: berkeley neural parser (https://github.com/nikitakit/self-attentive-parser)
synonyms: spacy wordnet synsets (https://spacy.io/universe/project/spacy-wordnet)
seed search dataset: stanford sentiment treebank (sst) dataset (https://nlp.stanford.edu/sentiment/)

\MyPara{Hyper-Parameter}
Number of seed inputs: 10 (random sample)
Number of cfg expansions: 10 (random sample)
Number of synonyms for a word: 10 (random sample)

Besides, we retrain the \sota \sa models aformentioned from test cases
generated from \Chlst and \Model. The goal of the retraining is to
assess comprehensiveness of test cases according to performance of
fine-tuned model. We assume that the comprehensive test cases improve
performance of \sa task when fine-tuning with them. On the other hand,
fine-tuning models with less comprehensive test cases increases
overfitting and decrece model performance.

\MyPara{Dataset}
Retraining dataset: checklist and our proposed model test cases

\MyPara{Hyper-Parameter}
Retraining epoach: 1
Retraining batch_size: 16

### 2022-01-10 paper/issta22/experiment.tex
modify rq

@@
 \item[\textbf{RQ1}:] How effective is our proposed evaluation model
-    for generating diverse test cases? % self bleu score
+  for finding failures given a linguistic capability?
+\item[\textbf{RQ2}:] How effective is our proposed model for
+  generating diverse test cases? % self bleu score
+\item[\textbf{RQ3}:]  How effective is our proposed model for
+  detecting diverse type of errors? % retraining acc score
+\item[\textbf{RQ4}:] How effective is our new test case generation
+  using \cfg expansion? % ablation study
 
-  \item[\textbf{RQ2}:] How effective is our new test case generation
-    using \cfg expansion?
-  \item[\textbf{RQ3}:] How effective is our proposed evaluation model
-    for finding failures given a linguistic capability?
 \end{enumerate}
 
-\subsection(Experiment Setup}
+\subsection{Experiment Setup}
 

### 2022-01-10 paper/issta22/experiment.tex
item label

@@
 \label{sec:experiment}
-
+%
 In this section, we present experiments to
@@
 
-\begin{enumerate}
-\item[\textbf{RQ1}:] How effective is our proposed evaluation model
+\begin{enumerate}[label=\textbf{RQ\arabic*}:]
+\item \label{rq:one} How effective is our proposed evaluation model
   for finding failures given a linguistic capability?
-\item[\textbf{RQ2}:] How effective is our proposed model for
+\item \label{rq:two} How effective is our proposed model for
   generating diverse test cases? % self bleu score
-\item[\textbf{RQ3}:]  How effective is our proposed model for
+\item \label{rq:three} How effective is our proposed model for
   detecting diverse type of errors? % retraining acc score
-\item[\textbf{RQ4}:] How effective is our new test case generation
+\item \label{rq:four} How effective is our new test case generation
   using \cfg expansion? % ablation study
-
 \end{enumerate}
@@
 
-For \sa task, input requirements are given for each linguistic
-capability. Based on the requirements, \Model generates templates and
-lexicons.
-\MyPara{Model}
-\Bert, \Roberta, \Dbert
+For answering \ref{rq:one} and \ref{rq:two}, we organize the experiment as
+follows:
+%
+\MyPara{Selection of seed inputs} \MyPara{\Cfg expansion}
+\MyPara{Models}
 
-\MyPara{Dataset}
-reference CFG generation: Treebank corpus
-word sentiments: sentiwordnet (https://github.com/aesuli/SentiWordNet)
-cfg parser: berkeley neural parser (https://github.com/nikitakit/self-attentive-parser)
-synonyms: spacy wordnet synsets (https://spacy.io/universe/project/spacy-wordnet)
-seed search dataset: stanford sentiment treebank (sst) dataset (https://nlp.stanford.edu/sentiment/)
+In addition, we answer \ref{rq:four} by organizing the another
+experiment as follows:
 
-\MyPara{Hyper-Parameter}
-Number of seed inputs: 10 (random sample)
-Number of cfg expansions: 10 (random sample)
-Number of synonyms for a word: 10 (random sample)
+%% For \sa task, input requirements are given for each linguistic
+%% capability. Based on the requirements, \Model generates templates and
+%% lexicons.
+%% \MyPara{Model}
+%% \Bert, \Roberta, \Dbert
 
-Besides, we retrain the \sota \sa models aformentioned from test cases
-generated from \Chlst and \Model. The goal of the retraining is to
-assess comprehensiveness of test cases according to performance of
-fine-tuned model. We assume that the comprehensive test cases improve
-performance of \sa task when fine-tuning with them. On the other hand,
-fine-tuning models with less comprehensive test cases increases
-overfitting and decrece model performance.
+%% \MyPara{Dataset}
+%% reference CFG generation: Treebank corpus
+%% word sentiments: sentiwordnet (https://github.com/aesuli/SentiWordNet)
+%% cfg parser: berkeley neural parser (https://github.com/nikitakit/self-attentive-parser)
+%% synonyms: spacy wordnet synsets (https://spacy.io/universe/project/spacy-wordnet)
+%% seed search dataset: stanford sentiment treebank (sst) dataset (https://nlp.stanford.edu/sentiment/)
 
-\MyPara{Dataset}
-Retraining dataset: checklist and our proposed model test cases
+%% \MyPara{Hyper-Parameter}
+%% Number of seed inputs: 10 (random sample)
+%% Number of cfg expansions: 10 (random sample)
+%% Number of synonyms for a word: 10 (random sample)
 
-\MyPara{Hyper-Parameter}
-Retraining epoach: 1
-Retraining batch_size: 16
+%% Besides, we retrain the \sota \sa models aformentioned from test cases
+%% generated from \Chlst and \Model. The goal of the retraining is to
+%% assess comprehensiveness of test cases according to performance of
+%% fine-tuned model. We assume that the comprehensive test cases improve
+%% performance of \sa task when fine-tuning with them. On the other hand,
+%% fine-tuning models with less comprehensive test cases increases
+%% overfitting and decrece model performance.
+
+%% \MyPara{Dataset}
+%% Retraining dataset: checklist and our proposed model test cases
+
+%% \MyPara{Hyper-Parameter}
+%% Retraining epoach: 1
+%% Retraining batch_size: 16

### 2022-01-11 paper/issta22/experiment.tex
exp

@@
 
-\begin{enumerate}[label=\textbf{RQ\arabic*}:]
-\item \label{rq:one} How effective is our proposed evaluation model
+\begin{enumerate}[label=\textbf{RQ\arabic*}]
+\item \label{rq:one}: How effective is our proposed evaluation model
   for finding failures given a linguistic capability?
-\item \label{rq:two} How effective is our proposed model for
+\item \label{rq:two}: How effective is our proposed model for
   generating diverse test cases? % self bleu score
-\item \label{rq:three} How effective is our proposed model for
+\item \label{rq:three}: How effective is our proposed model for
   detecting diverse type of errors? % retraining acc score
-\item \label{rq:four} How effective is our new test case generation
+\item \label{rq:four}: How effective is our new test case generation
   using \cfg expansion? % ablation study
@@
 
-For answering \ref{rq:one} and \ref{rq:two}, we organize the experiment as
-follows:
-%
-\MyPara{Selection of seed inputs} \MyPara{\Cfg expansion}
-\MyPara{Models}
+For answering \ref{rq:one} and \ref{rq:two}, we organize the
+experiment as follows: we generate test cases used for model
+evaluation.
+
+\MyPara{Seed Input Selection.} For each linguistic capability, we
+search all sentences that meet its requirement. Among found sentences,
+we randomly select 10 sentences due to space constraint.
+
+\MyPara{\Cfg Expansion.}
+
+\MyPara{Models.}
 

### 2022-01-11 paper/issta22/abstract.tex

@@
   limited to measure its comprehensive performance for each linguistic
-  capability. In this work, we introduce \OurModelName, an NLP model
+  capability. In this work, we introduce \Model, an NLP model
   testing methodology. Given a linguistic capability, The
-  \OurModelName finds relevant testcases to test the linguistic
+  \Model finds relevant testcases to test the linguistic
   capability from existing datasets as seed inputs, generates
@@
   on their context-free grammar (\Cfg). We illustrate the usefulness
-  of the \OurModelName by showing input diversity and identifying
+  of the \Model by showing input diversity and identifying
   critical failures in \sota models for NLP task. In our experiment,
-  we show that the \OurModelName generates {} more test cases with {}
+  we show that the \Model generates {} more test cases with {}
   higher diversity, and finds {} more bugs.

### 2022-01-12 paper/issta22/experiment.tex
exp

@@
   generating diverse test cases? % self bleu score
-\item \label{rq:three}: How effective is our proposed model for
-  detecting diverse type of errors? % retraining acc score
+\item \label{rq:three}: How effective is test cases generated from our
+  proposed model for detecting diverse type of errors? % retraining
+  acc score
 \item \label{rq:four}: How effective is our new test case generation
@@
 
+For answering \ref{rq:one} and \ref{rq:two}, we generate test cases
+and use them for evaluating model on linguistic capabilities. In this
+experiment, We assess the ability to find failures by anlyzing model's
+performance on the generated test cases. We also measure the diversity
+among the generated test cases using similarites among them. Next, we
+answer \ref{rq:three} by retraining \sa model with generated test
+cases and measuring performances. The idea behind this is that more
+comprehensive inputs becomes closer to real-world distribution and
+addresses more type of errors.  Therefore, it leads to improve the
+model performance. In this experiment, We retrain the model and
+compare performances of the retrained model. Not only that, we conduct
+ablation study of \cfg expansion to understand the its impact in our
+approach.
+
 \subsection{Experiment Setup}
+%
+\MyPara{Seed Input Selection}
+%
+For each linguistic capability, we first search all sentences that
+meet its requirement. Among found sentences, we randomly select 10
+sentences due to memory constraint.
 
-For answering \ref{rq:one} and \ref{rq:two}, we organize the
-experiment as follows: we generate test cases used for model
-evaluation.
+\MyPara{Word Sentiment}
+%
+we extract sentiments of words using the
+\Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
+available lexical resource of wrods on Wordnet with three numerical
+scores of objectivity, positivity and negativity. Sentiment word
+labels from the scores are classified from the algorithm from Mihaela
+\etal~\cite{mihaela2017sentiwordnetlabel}.
 
-\MyPara{Seed Input Selection.} For each linguistic capability, we
-search all sentences that meet its requirement. Among found sentences,
-we randomly select 10 sentences due to space constraint.
+\MyPara{\Cfg Expansion}
+%
+We build a reference \Cfg of natural language from the Englush Penn
+\Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
+The corpus is sampled from 2,499 stories from a tree year \Wsj
+collection The \Trb provides a parsed text corpus with annotation of
+syntactic and semantic structure. In this experiment We implement the
+\trb corpora available through \Nltk, which is a suite of libraries
+and programs for \Nlp for english. In addition, we parse the seed
+input using into its CFG using the Berkeley Neural
+Parser~\cite{kitaev2018constituency, kitaev2019multilingual}, a
+high-accuracy parser with models for 11 languages. The input is a raw
+text in natural languge and the output is the string representation of
+parse tree. Next after comparing CFGs beteen reference and seed input,
+we randomly select 10 expansions for generating templates due to
+memory constraint.
 
-\MyPara{\Cfg Expansion.}
+\MyPara{Synonyms}
+%
+\Model searches synosyms of each token from synonym sets extracted
+from \Wrdnt using \Spacy open-source library for NLP.
 
-\MyPara{Models.}
+\MyPara{Models}
+%
+We evaluate the following \sa nmodels via \Model:
+\Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
+\Dbert~\cite{sanh2019distilbert}. These models are fineturend on \Sstt
+and ther accuracies are \BertAcc, \RobertaAcc and \DbertAcc.
 
-In addition, we answer \ref{rq:four} by organizing the another
-experiment as follows:
+\MyPara{Retraining}
+%
+We retrain \sa models. we split \Model generated test cases into
+train/validation/test sets with the ratio of 8:1:1. The number of
+epochs and batch_size for retraining are 1 and 16 respectively.
 

### 2022-01-12 python/testsuite/Testsuite.py
debugging

@@ -172,7 +172,7 @@ class Testsuite:
                                         transform_req,
                                         nlp_task=task,
                                         search_dataset=dataset)
-        test_type, func, _property, woi = transformer.transformation_funcs.split('_')
+        test_type, func, _property, woi = transformer.transformation_funcs.split(':')
         if test_type=="INV":
             if func=="replace":
                 if len(sentences)>Macros.max_num_sents_for_perturb: sentences = sentences[:Macros.max_num_sents_for_perturb]

### 2022-01-12 python/testsuite/Transform.py

@@ -120,19 +120,9 @@ class TransformOperator:
                                                        SENT_DICT[f"negative_verb"] + \
                                                        SENT_DICT[f"positive_noun"] + \
                                                        SENT_DICT[f"negative_noun"])
-            else:
-                self.inv_replace_target_words = set(SENT_DICT[f"{_property}_{woi}"])
-                forbidden_property = "negative"
-                if _property=="negative":
-                    forbidden_property = "positive"
-                # end if
-                self.inv_replace_forbidden_words = set(['No', 'no', 'Not', 'not', 'Nothing', 'nothing', 'without', 'but'] + \
-                                                       SENT_DICT[f"{forbidden_property}_adj"] + \
-                                                       SENT_DICT[f"{forbidden_property}_verb"] + \
-                                                       SENT_DICT[f"{forbidden_property}_noun"])
             # end if
-            self.transformation_funcs = f"INV_{func}_{_property}_{woi}"
         # end if
+        self.transformation_funcs = f"INV:{func}:{_property}:{woi}"
         return
 
     def set_dir_env(self, dir_transform_reqs):
@@ -167,7 +157,7 @@ class TransformOperator:
                 }]
                 self.dir_expect_func = Expect.pairwise(self.diff_down)
             # end if
-            self.transformation_funcs = f"DIR_{func}_{_property}_{woi}"
+            self.transformation_funcs = f"DIR:{func}:{_property}:{woi}"
         # end if
         return
                 

### 2022-01-12 run.sh

@@ -18,7 +18,7 @@ function gen_requirements() {
 function gen_templates() {
         # write templates in json
         (cd ${_DIR}
-         python -m python.main --run template --search_dataset sst
+         CUDA_VISIBLE_DEVICES=1,2,3,4 python -m python.main --run template --search_dataset sst
         )
 }
 

### 2022-01-19 paper/issta22/abstract.tex

@@
 \begin{abstract}
-  \Nlp (NLP) technique becomes one of the core techniques for developing
-  text analytics applications.  For developing the NLP applications,
-  the applications are required to achieve high reliability before it
-  goes to market.  The trustworthiness of the prevalent NLP
+  \Nlp (NLP) technique becomes one of the core techniques for
+  developing text analytics applications.  For developing an NLP
+  application, the application is required to achieve high reliability
+  before it goes to market.  The trustworthiness of the prevalent NLP
   applications is obtained by measuring the accuracy of the
-  applications on held-out dataset.  However, evaluating NLP on
-  testset does with held-out accuracy is limited to show its quality
-  because the held-out datasets are often not comprehensive. While the
+  applications on hold-out dataset.  However, evaluating NLP on
+  testset does with hold-out accuracy is limited to show its quality
+  because the held-out datasets are often not comprehensive.
+
+  %% connection saying that why behavior testing is employed.
+
+  While the
   behavioral testing over multiple general linguistic capabilities are
-  employed, it relies on manually created test cases, and is still
-  limited to measure its comprehensive performance for each linguistic
-  capability. In this work, we introduce \Model, an NLP model
-  testing methodology. Given a linguistic capability, The
-  \Model finds relevant testcases to test the linguistic
-  capability from existing datasets as seed inputs, generates
-  sufficient number of new test cases by fuzzing the seed inputs based
-  on their context-free grammar (\Cfg). We illustrate the usefulness
-  of the \Model by showing input diversity and identifying
-  critical failures in \sota models for NLP task. In our experiment,
-  we show that the \Model generates {} more test cases with {}
-  higher diversity, and finds {} more bugs.
+  employed, the testing relies on manually created test cases, and is
+  still limited to measure its comprehensive performance for each
+  linguistic capability. In this work, we introduce \Model, an NLP
+  model testing methodology. Given a linguistic capability, the \Model
+  finds relevant testcases to test the linguistic capability from
+  existing datasets as seed inputs, generates sufficient number of new
+  test cases by fuzzing the seed inputs based on their \cfg (CFG). We
+  illustrate the usefulness of the \Model by showing input diversity
+  and identifying critical failures in \sota models for NLP task. In
+  our experiment, we show that the \Model generates {} more test cases
+  with {} higher diversity, and finds {} more bugs.
 

### 2022-01-19 python/mc/model/Model.py
qqp debugging

@@ -1,0 +1,90 @@
+# This script is to load models to be evaluated
+# given generated test suite
+
+from typing import *
+from pathlib import Path
+from transformers import pipeline, AutoTokenizer
+# from nlp import load_dataset
+
+import os
+import numpy as np
+
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+
+class Model:
+    
+    model_map = {
+        "sa": ("sentiment-analysis", Macros.sa_models_file)
+    }
+
+    @classmethod
+    def read_model_list(cls, task: str):
+        _task, model_file = cls.model_map[task]
+        return _task, [l.strip() for l in Utils.read_txt(model_file)]
+
+    @classmethod
+    def load_models(cls, task: str):
+        _task, model_names = cls.read_model_list(task)
+        for m in model_names:
+            tokenizer = AutoTokenizer.from_pretrained(m)
+            yield m, pipeline(_task, model=m, tokenizer=tokenizer, framework="pt", device=0)
+        # end for
+
+    @classmethod
+    def load_local_model(cls, task, model_name):
+        # model_dir = Macros.retrain_output_dir / model_name.replace("/", "-")
+        model_dir = Macros.retrain_model_dir / task / model_name
+        _task, model_file = cls.model_map[task]
+        checkpoints = sorted([d for d in os.listdir(model_dir) if os.path.isdir(os.path.join(model_dir,d)) and d.startswith("checkpoint-")])
+        checkpoint_dir = model_dir / checkpoints[-1]
+        tokenizer = AutoTokenizer.from_pretrained(model_dir)
+        return pipeline(_task, model=str(checkpoint_dir), tokenizer=tokenizer, framework="pt", device=0)
+
+    @classmethod
+    def get_batch(cls, l, n):
+        """Yield successive n-sized chunks from l."""
+        for i in range(0, len(l), n):
+            yield l[i:i + n]
+        # end for
+
+    @classmethod
+    def batch_predict(cls, data: List[str], batch_size: int = 32):
+        preds = list()
+        for d in cls.get_batch(data, batch_size):
+            preds.extend(cls.model(d))
+        # end for
+        return preds
+    
+    @classmethod
[…]

### 2022-01-19 python/mc/requirement/Requirements.py

@@ -1,0 +1,190 @@
+# This script reads linguisiti capabilities described
+# and generates its requirements
+
+from typing import *
+
+import re, os
+import sys
+import json
+import random
+
+from pathlib import Path
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+
+# dataset for NLP task
+# key: NLP task
+# value: name of dataset for a NLP task
+datasets = Macros.datasets
+
+class Requirements:
+    
+    @classmethod
+    def convert_test_type_txt_to_json(cls):
+        task = Macros.mc_task
+        dataset_path = Macros.result_dir / f"test_type_{task}.txt"
+        result = None
+        if os.path.exists(dataset_path):
+            with open(dataset_path, 'r') as f:
+                result = {
+                    l.split("::")[0].strip(): [
+                        _l.strip()
+                        for _l in l.split("::")[-1].split("|")
+                    ]
+                    for l in f.readlines()
+                }
+            # end with
+            if result is not None:
+                Utils.write_json(result,
+                                 Macros.result_dir / f"test_type_{task}.json",
+                                 pretty_format=True)
+            # end if
+        # end if
+        return
+
+    @classmethod
+    def get_requirements(cls, task):
+        req_file = Macros.result_dir / f"requirements_{task}.json"
+        if os.path.exists(req_file):
+            return Utils.read_json(req_file)
+        # end if
+        
+        reqs = None
+        test_type_file = Macros.result_dir / f"test_type_{task}.json"
+
+        # cap_decp:
+        # key: liguistic capability to be evaluated
+        # value: each test type description
+        if not os.path.exists(test_type_file):
+            cap_desc = cls.convert_test_type_txt_to_json()
+        else:
+            cap_desc = Utils.read_json(test_type_file)
+        # end if
+        reqs = list()
+        for cap, descs in cap_desc.items():
+            for d in descs:
+                if d.lower()=="adding an adjective makes questions non-duplicates":
+                    reqs.append({
+                        "capability": cap,
+                        "description": d,
+                        "search_pairs": False,
+                        "search": [{
+                            "length": "<10",
+                            "exclude": {
+                                "POS": ["adj"],
+                                "word": None,
+                            },
+                        }],
+                        "transform": {
+                            "MFT": "add adj",
+                        }
+                    })
+                elif d.lower()=="add modifiers that preserve question semantics (e.g. 'really')":
+                    reqs.append({
+                        "capability": cap,
+                        "description": d,
+                        "search_pairs": False,
[…]

### 2022-01-19 python/mc/testsuite/InputPerturb.py

@@ -1,0 +1,86 @@
+# This script perturbates input and generate more inputs
+# given the input.
+
+from typing import *
+
+import re, os
+import sys
+import json
+import nltk
+import random
+
+from pathlib import Path
+from nltk.parse.generate import generate, demo_grammar
+from nltk import CFG
+
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+
+class InputPerturb:
+
+    def __init__(self, 
+                 input_file: Path, 
+                 input_cfg_file: Path,
+                 cfg_diff_file: Path):
+        self.input_sents: List[str] = Utils.read_txt(input_file)
+        self.input_cfg: dict = Utils.read_json(input_cfg_file)
+        self.input_cfg_str: str = self.cfg_dict_to_str(self.input_cfg)
+        self.cfg_diff: dict = Utils.read_json(cfg_diff_file)
+        # self.cfg_diff_str: str = self.cfg_dict_to_str(self.cfg_diff)
+        for s_i, sent in enumerate(self.input_sents,1):
+            print("%3d. %s" % (s_i, sent.strip()))
+        
+    def cfg_dict_to_str(self, input_cfg):
+        res_str = "\n  "
+        for lhs, rhs in input_cfg.items():
+            res_str += f"{lhs} -> "
+            random.shuffle(rhs)
+            for r_i, r in enumerate(rhs):
+                res_str += " ".join(r)
+                if r_i+1<len(rhs):
+                    res_str += " | "
+                else:
+                    res_str += "\n  "
+                # end if
+            # end for
+        # end for
+        return res_str
+
+    def get_cfg_grammar(self, cfg_str):
+        return CFG.fromstring(cfg_str)
+
+    def gen_random_sentence(self, cfg_str, num_sents=23, max_length=10):
+        random.seed(Macros.SEED)
+        grammar = self.get_cfg_grammar(cfg_str)
+        print("\n***** INPUT CFG GRAMMAR *****")
+        print(cfg_str)
+        print("*****************************\n")
+        print("\n***** GENERATED SENTS *****")
+        for n, sent in enumerate(generate(grammar, n=num_sents),1):
+            if len(sent)<=max_length:
+                print("%3d. %s" % (n, " ".join(sent)))
+                continue
+            # end if
+        # end for
+        print("*****************************\n")
+
+    def main(self):
[…]

### 2022-01-19 python/mc/testsuite/Search.py

@@ -1,0 +1,370 @@
+# This script searches inputs in datasets that meet requirements
+
+from typing import *
+from pathlib import Path
+
+import re, os
+import sys
+import json
+import spacy
+import random
+import checklist
+import numpy as np
+
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+from ..requirement.Requirements import Requirements
+from .Synonyms import Synonyms
+# from .sentiwordnet.Sentiwordnet import Sentiwordnet
+
+# get name and location data
+basic = Utils.read_json(Macros.dataset_dir / 'checklist' / 'lexicons' / 'basic.json')
+names = Utils.read_json(Macros.dataset_dir / 'checklist' / 'names.json')
+name_set = { x:set(names[x]) for x in names }
+NAME_LOC_DICT = {
+    'name': names,
+    'name_set': name_set,
+    'city': basic['city'],
+    'country': basic['country'],
+}
+
+random.seed(27)
+
+class SearchOperator: 
+    
+    def __init__(self, requirements):
+        self.capability = requirements['capability']
+        self.description = requirements['description']
+        self.search_reqs_list = requirements['search']
+        self.search_pairs = requirements['search_pairs']
+        self.search_method = {
+            "length": self.search_by_len,
+            "include": self.search_by_include,
+            "exclude": self.search_by_exclude,
+            "label": self.search_by_label,
+        }
+
+    def search(self, sents):
+        # sents: question sentences or pairs of questions
+        # issentpair: indicator if sents are question sentences or pairs of questions
+        selected = list()
+        for search_reqs in self.search_reqs_list:
+            _sents = sents.copy()
+            for op, param in search_reqs.items():
+                if len(_sents)>0:
+                    _sents = self.search_method[op](_sents, search_reqs)
+                # end if
+            # end for
+            selected.extend(_sents)
+        # end for
+        return list(set(selected))
+
+    def search_by_len(self, sents, search_reqs):
+        param = search_reqs["length"]
+        match = re.search(r"([<>]=?|==)(\d+)", param)
+        op, _len = match.groups()
+        selected = list()
+        if self.search_pairs:
+            _sents = [(s_i,Utils.tokenize(s1),Utils.tokenize(s2),l) for s_i, s1, s2, l in sents]
+            for s_i, s1, s2, l in _sents:
+                if s1[-1]=="." and (eval(f"{len(s1)-1}{op}{_len}")):
+                    if s2[-1]=="." and (eval(f"{len(s2)-1}{op}{_len}")):
[…]

### 2022-01-19 python/mc/testsuite/Synonyms.py

@@ -1,0 +1,96 @@
+# This script extract synonyms given a word
+
+from typing import *
+
+import re, os
+import sys
+import json
+import random
+
+# from nltk.corpus import wordnet
+from .cfg.CFG import BeneparCFG
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+
+class Synonyms:
+
+    wordnet_tag_map = {
+        'n': 'NN',
+        's': 'JJ',
+        'a': 'JJ',
+        'r': 'RB',
+        'v': 'VB'
+    }
+    
+    @classmethod
+    def get_synsets(cls, nlp, word: str):
+        token = nlp(word)[0]
+        return token._.wordnet.synsets()
+
+    @classmethod
+    def get_word_pos(cls, word: str):
+        try:
+            tree = BeneparCFG.get_word_pos(word)
+            parse_string = tree._.parse_string
+            pattern = r"\(([^\:|^\(|^\)]+)\s"+word+r"\)"
+            search = re.search(pattern, parse_string)
+            if search:
+                return parse_string, search.group(1)
+            # end if
+            return None, None
+        except IndexError:
+            print(f"IndexError: {word}")
+            return None, None
+
+    @classmethod
+    def get_words_pos(cls, words):
+        trees= BeneparCFG.get_words_pos(words)
+        results = list()
+        for tr_i, tree in enumerate(trees):
+            try:
+                parse_string = tree._.parse_string
+                pattern = r"\(([^\:|^\(|^\)]+)\s"+str(tree)+r"\)"
+                search = re.search(pattern, parse_string)
+                if search:
+                    results.append((parse_string, search.group(1)))
+                else:
+                    results.append((None, None))
+                # end if
+            except IndexError:
+                print(f"IndexError: {words[tr_i]}")
+                results.append((None, None))
+            # end try
+        # end for
+        return results
+        
+    @classmethod
+    def get_wn_syn_pos(cls, synset):
+        return cls.wordnet_tag_map[synset.pos()]
+        
+    @classmethod
+    def get_synonyms(cls, nlp, word: str, wpos:str, num_synonyms=Macros.max_num_synonyms):
+        synonyms = list()
+        if wpos is None:
+            return synonyms
+        # end if
+        for syn in cls.get_synsets(nlp, word):
+            wn_spos = cls.get_wn_syn_pos(syn)
+            syns = [lm.name() for lm in syn.lemmas()]
+            if wpos.startswith(wn_spos):
[…]

### 2022-01-19 python/qqp/utils/.#Macros.py

@@ -1,0 +1,1 @@
+jxl115330@bernstein.utdallas.edu.27282:1641915611

### 2022-03-03 paper/fse22/approach.tex
change conf name

\section{Approach}
\label{sec:approach}

\begin{figure*}
  \centering
  \includegraphics[scale=0.5]{figs/overall.pdf}
  \vspace{-5pt}
  \caption{\OverallModelFigCaption}
  \vspace{-10pt}
\end{figure*}

### 2022-03-03 paper/fse22/conclusion.tex
change conf name

\section{Conclusion}

We present methodology of code structure understanding to learn code
contextual representation using control flow graph. To the best of our
knowledge, this is the first pre-trained model that leverages the
control flow graph. We show that our schemes for feeding graph edge
distance and graph node type into \Trsfm self-attention operation
outperformed the state-of-the-art pretraing model on code-related \ds
tasks. Furthermore, our qualitive analysis shows the performance
improvements results from understanding \Cfg code structure. Our study
stands to motivate other researchers and practitioners to develop code
related software engineering techniques based on deep learning for \pl
to provide powerful tools to software engineers.

### 2022-03-03 paper/fse22/intro.tex
change conf name

--- 2022-01-09 paper/issta22/intro.tex
@@
 quality to users in that the software meets requirements by
-verification and validation. Regarding that, NLP application is a branch
-of artifical intelligence software, and testing NLP application
+verification and validation. Regarding that, NLP application is a
+branch of artifical intelligence software, and testing NLP application
 also becomes important process as well.
@@
 the \ho set is used for testing by measuring accuracy. The accuracy is
-a indicator of the performance of the models.
+a indicator of the performance of the models. Despite its usefulness,
+the main limitation of the testing paradigm is that the \ho set often
+overestimates the performances. Each dataset comes with specific
+biases, and the biases increase the discrepancy of distribution
+between dataset and real-world~\cite{recht2019imagenetbias}. The
+aforementioned accuracy on \ho set does not consider the discrepancy
+and it is limited to achieve comprehensive performrance of the NLP
+model. As a consequence, it is difficult to analyze weekness of the
+model~\cite{wu2019errudite}.
 
-Despite its usefulness, the main limitation of the testing paradaigm
-is that the \ho set often overestimates the performances. Each dataset
-comes with specific biases, and the biases increase the discrepancy of
-distribution between dataset and
-real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
-on \ho set does not consider the discrepancy and it is limited to
-achieve comprehensive performrance of the NLP model. As a consequence,
-it is difficult to analyze where the errors comes
-from~\cite{wu2019errudite}.
-
+% this paragraph goes to related, and saying behavioral testing and
+% its limitation based on our model's novelty
 On the subject of the limitation of traditional testing paradaigm, a
@@
 We show that
+
+% our paper's contribution

### 2022-03-04 paper/fse22/approach.tex
paper approach
approach

@@
-\section{Approach}
-\label{sec:approach}
+\section{Technique and implementation}
+%% \label{sec:approach}
 
@@
 \end{figure*}
+
+\Model generates input sentences with the following phases illustrated
+in \ref{fig:OverallModel}: 1. search phase searches seed sentences according to
+its requirement of \lc, 2. seed parsing phase parses the found seed
+sentences and extract their \cfg, 3. reference phase collects large
+corpus, 4. syntax expansion identification, and 5.sentence expansion
+and generation. In this section, we provide more details on each phase.
+
+\subsection{Search phase}
+The search phase in \Model searches and samples subset of sentences in the
+dataset that meets the requirement extracted from each linguistic
+capability. Each linguistic capability represents performance of \nlp
+task on specific input domain
+
+requires certain format of sentences

### 2022-03-04 paper/fse22/approach.tex
appraoch

@@
 \subsection{Search phase}
-The search phase in \Model searches and samples subset of sentences in the
-dataset that meets the requirement extracted from each linguistic
-capability. Each linguistic capability represents performance of \nlp
-task on specific input domain
+The search phase in \Model searches and samples subset of sentences in
+the dataset that meets the requirement extracted from each linguistic
+capability. In order to evaluate NLP models on \lc precisely, there
+are two conditions in our interest. First, inputs in the distrbution
+characterized by each \lc is of importance. Each \lc represents
+performance of NLP model on specific input distribution. Therefore,
+the \lc introduces the constraints of the input distribution, and
+input sentences from the constrained distribution are only qualified
+to be used for evaluating the NLP model on the \lc. In addition,
+diversity in inputs is important to evaluate NLP models on the
+\lc. The idea is that inputs that differ are more likely to cover the
+\NLP model behavior, and more coverage increases trustworthiness of
+the evaluation. Based on them, we approach
 

### 2022-03-04 paper/fse22/approach.tex
approach

--- 2022-03-04 paper/fse22/approach.tex
@@
 \subsection{Search phase}
-The search phase in \Model searches and samples subset of sentences in the
-dataset that meets the requirement extracted from each linguistic
-capability. Each linguistic capability represents performance of \nlp
-task on specific input domain
-
-requires certain format of sentences
+The search phase in \Model searches inputs in dataset and selects
+subset of input sentences in the dataset that meets the \lc
+requirement. The idea behind this phase is that input distribution of
+\lc is important to generate inputs relevant to \lc. \Lc describes
+expected behaviors of NLP model on specific types of input and
+output. The NLP model is evaluated on how much it performs on the
+input and output. Thus, \lc introduces the constraints of the input
+data. Input data from the constrained distribution are only qualified
+to be used for evaluating the NLP model on the \lc.  In addition,
+diversity in inputs is important to evaluate NLP models on the
+\lc. Inputs that differ are more likely to cover the NLP model
+behavior, and more coverage increases trustworthiness of the
+evaluation. To satisfy the same distribution and high
+diversity among inputs, we estabilish requirement of input and output
+for each \lc, and find inputs that fulfil the requirements.

### 2022-03-05 paper/fse22/approach.tex
approach requirement

@@
 
-\Model generates input sentences with the following phases illustrated
-in \ref{fig:OverallModel}: 1. search phase searches seed sentences according to
-its requirement of \lc, 2. seed parsing phase parses the found seed
-sentences and extract their \cfg, 3. reference phase collects large
-corpus, 4. syntax expansion identification, and 5.sentence expansion
-and generation. In this section, we provide more details on each phase.
+\Model generates input \sents with the following phases illustrated
+in \ref{fig:OverallModel}: 1. search phase searches seed \sents
+according to its \req of \lc, 2. seed parsing phase parses the
+found seed \sents and extract their \cfg, 3. reference phase
+collects large corpus, 4. syntax expansion identification, and
+5.\sent expansion and generation. In this section, we provide more
+details on each phase.
 
@@
 The search phase in \Model searches inputs in dataset and selects
-subset of input sentences in the dataset that meets the \lc
-requirement. The idea behind this phase is that input distribution of
-\lc is important to generate inputs relevant to \lc. \Lc describes
+subset of input \sents in the dataset that meets the \lc
+\req. The idea behind this phase is that input distribution of
+\lc is important to generate inputs relevant to \lc. \Lc explains
 expected behaviors of NLP model on specific types of input and
@@
 behavior, and more coverage increases trustworthiness of the
-evaluation. To satisfy the same distribution and high
-diversity among inputs, we estabilish requirement of input and output
-for each \lc, and find inputs that fulfil the requirements.
+evaluation. To generate inputs from same distribution on \lc and high
+diversity of inputs, we estabilish \reqs of input and output
+for each \lc, and find inputs that fulfil the \reqs. Given a
+\lc, a \req consists of search \req, transform
+\req and expansion \req. The search \req
+describes features and functionalities that we seek to have in
+inputs. \Model check each input if it satisfy the \req.
+
+\begin{figure}[t]
+  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
+  \vspace{-10pt}
+  \caption{\SearchRequirementExampleFigCaption}
+  \vspace{-10pt}
+\end{figure}
+
+\begin{figure}[t]
+  \lstinputlisting[language=json-pretty]{code/requirement_sa2.json}
+  \vspace{-10pt}
+  \caption{\TransformRequirementExampleFigCaption}
+  \vspace{-10pt}
+\end{figure}
+
+Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
+this \lc, the input is required to be short and have only \neu \adjs,
+\neu \nns. In addition, the label needs to be \neu. Therefore, all
+short natural \sents with only \neu \adjs and \neu \nns are available
+to evaluate NLP models. Next, transform \req explains how the input
+and output needs to be tranfromed. Some \lc only accepts heavily
+limited input distribution, and it is unlikely to be included in
+searching dataset because of its high structural diversity. Therefore,
+our approach is to find inputs by relaxing search requirement and
+transform the input to match the target requirement of the \lc. In
+this work, the inputs are transformed by word addition or perturbing
+the found inputs with \lc dependent templates. \Lc of \SareqExTwo in
+the figure~\ref{fig:TransformReqEx}, for instance, requires inputs to
+be the negated \pstv \sents and be the neutral expression in the
+middle. Finding such \sents is costly because such sentneces are
+diverse in terms of their structure. Rather, the \Model search \pstv s
+and \neu inputs and combine them into negated \pstv \sents. The
+transformation of inputs produce the transformed inputs in
+distribution on \lc and high diversity in the inputs because of that
+from initially found inputs.

### 2022-03-05 paper/fse22/approach.tex
approach

@@
 
-\Model generates input \sents with the following phases illustrated
-in \ref{fig:OverallModel}: 1. search phase searches seed \sents
-according to its \req of \lc, 2. seed parsing phase parses the
-found seed \sents and extract their \cfg, 3. reference phase
-collects large corpus, 4. syntax expansion identification, and
-5.\sent expansion and generation. In this section, we provide more
-details on each phase.
+\Model generates input \sents with the following phases illustrated in
+\ref{fig:OverallModel}: 1. search phase searches seed \sents according
+to its \req of \lc, 2. seed parsing phase parses the found seed \sents
+and extract their \cfg, 3. reference phase collects large corpus,
+4. syntax expansion phase identifies structure for input augmentation,
+and 5.\sent expansion phase generates natural expanded \sent. In this
+section, we provide more details on each phase.
 
@@
 from initially found inputs.
+
+\subsection{Seed parsing phase}
+In the seed parsing phase,
+
+\subsection{Reference phase}
+
+\subsection{Syntax expansionphase}
+
+\subsection{\Sent expansion phase}

### 2022-03-07 paper/fse22/approach.tex
approach

@@
   \centering
-  \includegraphics[scale=0.5]{figs/overall.pdf}
+  \includegraphics[scale=0.5]{figs/overview.pdf}
   \vspace{-5pt}
@@
 \begin{figure}[t]
+  \centering
   \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
@@
 \begin{figure}[t]
-  \lstinputlisting[language=json-pretty]{code/requirement_sa2.json}
-  \vspace{-10pt}
+  \centering
+  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
+  \\
+  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python-pretty]{code/requirement_sa2.py}}
+  \\
   \caption{\TransformRequirementExampleFigCaption}
@@
 limited input distribution, and it is unlikely to be included in
-searching dataset because of its high structural diversity. Therefore,
-our approach is to find inputs by relaxing search requirement and
-transform the input to match the target requirement of the \lc. In
-this work, the inputs are transformed by word addition or perturbing
-the found inputs with \lc dependent templates. \Lc of \SareqExTwo in
-the figure~\ref{fig:TransformReqEx}, for instance, requires inputs to
-be the negated \pstv \sents and be the neutral expression in the
-middle. Finding such \sents is costly because such sentneces are
-diverse in terms of their structure. Rather, the \Model search \pstv s
-and \neu inputs and combine them into negated \pstv \sents. The
-transformation of inputs produce the transformed inputs in
-distribution on \lc and high diversity in the inputs because of that
-from initially found inputs.
+searching dataset because of its high structural diversity, thus,
+finding such \sents is costly. Therefore, our approach is to find
+inputs by relaxing search requirement and transform the input to match
+the target requirement of the \lc. In this work, the inputs are
+transformed by word addition or perturbing the found inputs with \lc
+dependent templates. The figure~\ref{fig:TransformReqEx} shows the
+example of use of the template requirement. The \lc of \SareqExTwo in
+the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
+negated \pstv \sents and the neutral expression in the middle. Rather
+than searching \sents that match the input distribution of the \lc,
+the \Model search \pstv and \neu inputs and combine them into negated
+\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
+for the \lc. According to the \lc, The value of ``sent1'' and
+``sent2'' become each searched \neu and \pstv inputs respectively, and
+the template completion generates new inputs that matches the target
+\lc. In addition, the transformation of inputs also produce high
+diversity in the inputs because of that from initially found
+inputs. In this paper, we will denote the searched inputs in this
+phase as seed inputs.
 
 \subsection{Seed parsing phase}
-In the seed parsing phase,
+To expands seed sentence and generate fluent and faithful sentence
+used for evaluation, \Model studies structure of each seed input for
+its expansion. To extract the structure, this phase takes each seed as
+input, and the parse tree of the seed input is output.  In this phase,
+\Model implements the Berkeley Neural
+Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}.
 
 \subsection{Reference phase}
+In this phase, we take a large scale corpus as reference. We assume
+that large corpus represents data distribution of real world,
+the descripancy comparing seed sentence with the reference
 
-\subsection{Syntax expansionphase}
+structural information reference corpus is also parsed into \cfg.
+
+\subsection{Syntax expansion phase}
 

### 2022-03-07 paper/fse22/approach.tex
approach

@@
 to its \req of \lc, 2. seed parsing phase parses the found seed \sents
-and extract their \cfg, 3. reference phase collects large corpus,
-4. syntax expansion phase identifies structure for input augmentation,
-and 5.\sent expansion phase generates natural expanded \sent. In this
-section, we provide more details on each phase.
+and extract their \cfg, 3. reference parsing phase collects \pcfg from
+large corpus, 4. production differentiation phase identifies
+structural expansion candidates for input expansion, and 5.\sent
+selection phase generates natural expanded \sent. In this section, we
+provide more details on each phase.
 
@@
 
-\subsection{Reference phase}
-In this phase, we take a large scale corpus as reference. We assume
-that large corpus represents data distribution of real world,
-the descripancy comparing seed sentence with the reference
+\subsection{Reference parsing phase}
+We take a large scale corpus as reference for seed expansion. It is
+motivated by that large corpus represents data distribution of real
+world, and the discrepancy between seed and reference leads to
+determine how the seed can be expanded within real world data
+distribution. This phase builds \pcfg from the reference corpus. \cfg
+is constructed by parsing sentences in the corpus and extracting
+production rules. In addition, the probability of \cfg is estimated by
+its frequency over corpus. The outpus of this phase is the constructed
+\pcfg, and it is compared with seed parse trees. For our
+implementation, we build the \pcfg from the Penn Treebank corpus dataset.
 
-structural information reference corpus is also parsed into \cfg.
+\subsection{production differentiation phase}
+Given the seed parse tree and reference \pcfg, \Model suggests
+structural expansion candidates.
 
-\subsection{Syntax expansion phase}
-
-\subsection{\Sent expansion phase}
+\subsection{\Sent selection phase}

### 2022-03-08 paper/fse22/approach.tex
approach

@@
 \subsection{production differentiation phase}
-Given the seed parse tree and reference \pcfg, \Model suggests
-structural expansion candidates.
+\input{code/prod_diff_pseudocode}
+
+Given the seed parse tree and reference \pcfg, production
+differentiation phase suggests structural expansion candidates on the
+seed input. this phase aims to analyze which structural components and
+where they can be added into the seed structure for its expansion. To
+do so, we explore reference production rules comparing it with each
+production rule used in seed input. This results in the phase
+described in Algorithm~\ref{code:ProdDiffAlg}. For each production
+rule in seed inputs ($seed\_prod$), it searches production rules in
+reference ($ref\_prod$) which it has same non-terminal on the
+left-hand side ($seed\_prod.lhs==ref\_prod.lhs$) and superset of
+right-hand side of the seed production rule ($seed\_prod.rhs \subset
+ref\_prod.rhs$).  As we assume that the reference \cfg is built from
+real world data distribution, the elements in the complement set
+($ref\_prod.rhs - seed\_prod.rhs$) become an expansion candidate which
+can be expanded from the $seed\_prod.rhs$ found in real world. In
+addition, the measure of how consistent the production rule is with
+the given seed structure is given in its probability of the reference
+production rule ($ref\_prob$) multiplied by that of parents of
+$seed\_prod$. The expansion candidate consists of terminal or
+nonterminal symbols. When there is a phrase-level or clause-level
+nonterminal symbol, \eg noun phrase, it needs to be expanded and
+replaced with word-level nonterminal or terminal symbols to generate
+the expansion candidate. The number of feasible replacement is
+unbounded because of its high degree of freedom. Therefore, in this
+work, we focus on the expansion candidate with only the word-level
+nonterminal or terminal symbols for the effectiveness of \Model.
 

### 2022-03-09 paper/fse22/approach.tex
approach

@@
 short natural \sents with only \neu \adjs and \neu \nns are available
-to evaluate NLP models. Next, transform \req explains how the input
-and output needs to be tranfromed. Some \lc only accepts heavily
-limited input distribution, and it is unlikely to be included in
-searching dataset because of its high structural diversity, thus,
+to evaluate NLP models. In this work, the sentiment of the words for
+the search are classified based on the sentiment scores from
+\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
+sentiment lexicons.  It provides lexical sentiment scores and the
+sentiment word labels are categorized by implementing the rules
+in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
+how the input and output needs to be tranfromed. Some \lc only accepts
+heavily limited input distribution, and it is unlikely to be included
+in searching dataset because of its high structural diversity, thus,
 finding such \sents is costly. Therefore, our approach is to find
@@
 is constructed by parsing sentences in the corpus and extracting
-production rules. In addition, the probability of \cfg is estimated by
+\prodrs. In addition, the probability of \cfg is estimated by
 its frequency over corpus. The outpus of this phase is the constructed
@@
 \input{code/prod_diff_pseudocode}
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.33]{figs/expansion.pdf}
+  \vspace{-20pt}
+  \caption{\ExpansionExCaption}
+  \vspace{-30pt}
+\end{figure}
 
@@
 where they can be added into the seed structure for its expansion. To
-do so, we explore reference production rules comparing it with each
-production rule used in seed input. This results in the phase
-described in Algorithm~\ref{code:ProdDiffAlg}. For each production
-rule in seed inputs ($seed\_prod$), it searches production rules in
-reference ($ref\_prod$) which it has same non-terminal on the
-left-hand side ($seed\_prod.lhs==ref\_prod.lhs$) and superset of
-right-hand side of the seed production rule ($seed\_prod.rhs \subset
-ref\_prod.rhs$).  As we assume that the reference \cfg is built from
-real world data distribution, the elements in the complement set
-($ref\_prod.rhs - seed\_prod.rhs$) become an expansion candidate which
-can be expanded from the $seed\_prod.rhs$ found in real world. In
-addition, the measure of how consistent the production rule is with
-the given seed structure is given in its probability of the reference
-production rule ($ref\_prob$) multiplied by that of parents of
-$seed\_prod$. The expansion candidate consists of terminal or
-nonterminal symbols. When there is a phrase-level or clause-level
-nonterminal symbol, \eg noun phrase, it needs to be expanded and
-replaced with word-level nonterminal or terminal symbols to generate
-the expansion candidate. The number of feasible replacement is
-unbounded because of its high degree of freedom. Therefore, in this
-work, we focus on the expansion candidate with only the word-level
-nonterminal or terminal symbols for the effectiveness of \Model.
+do so, we explore reference \prodrs comparing it with each \prodr used
+in seed input. This results in the phase described in
+Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
+inputs ($seed\_prod$), it searches production rules in reference
+($ref\_prod$) which it has same non-terminal on the \lhs
+($seed\_prod.lhs==ref\_prod.lhs$) and superset of \rhs of the seed
+production rule ($seed\_prod.rhs \subset ref\_prod.rhs$).  As we
+assume that the reference \cfg is built from real world data
+distribution, the elements in the complement set ($ref\_prod.rhs -
+seed\_prod.rhs$) become an expansion candidate which can be expanded
+from the $seed\_prod.rhs$ found in real world. In addition, the
+measure of how consistent the production rule is with the given seed
+structure is given in its probability of the reference production rule
+($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
+expansion candidate consists of terminal or nonterminal symbols. When
+there is a phrase-level or clause-level nonterminal symbol, \eg noun
+phrase, it needs to be expanded and replaced with word-level
+nonterminal or terminal symbols to generate the expansion
+candidate. The number of feasible replacement is unbounded because of
+its high degree of freedom. Therefore, in this work, we focus on the
+expansion candidate with only the word-level nonterminal or terminal
+symbols for the effectiveness of \Model. Lastly, the expanded
+component is replaced with the mask token for the next phase. The
+example of the expansion is illustrated in
+Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into
+reference, and ``NP->[DT,NNS]'' is identified as its expansion
+candidate since the \rhs of ``NP->[DT,NNS]'' is superset of that of
+``NP->[DT]''. the component of NNS is replaced with mask token in
+sentence-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
+the next phase.
 
-\subsection{\Sent selection phase}
+\subsection{\Sent expansion and validation phase}
+
+Next, the masked tokens in the expanded masked sentences are estimated
+in this phase. For the mask token prediction, we use the BERT
+pretrained model. The BERT model suggests word for the mask token
+according to its context around in sentence. The suggested word are
+validated by three criteria. First, The tag of POS must be matched with
+that suggested from the production differentiation phase. In the
+example in the Figure~\ref{fig:ExpEx}, the mask token comes from the
+structural component of NNS, plural noun. Therefore, the BERT
+suggested words must be also tagged with the NNS. Accordingly, every
+words of the NNS are only available. Second, \Model focuses on the \sa
+task, and it assume that the suggested words must not change sentiment
+of its input and must preserve its consistency of original sentiment
+label. Therefore, we only accept the \neu words for the
+expansion. Third, the expanded sentences with the BERT suggested words
+must be appropriate for evaluating NLP models on the target \lc, and the
+sentences must pass the \req of the \lc. In this work, the BERT
+suggestions are validated by the three criteria.

### 2022-03-11 python/sa/main.py
add more selection method

@@ -23,7 +23,7 @@ parser.add_argument('--search_dataset', type=str, default="sst",
 parser.add_argument('--num_seeds', type=int, default=Macros.max_num_seeds,
                     help='number of seed inputs found in search dataset')
 parser.add_argument('--syntax_selection', type=str, default='prob',
-                    choices=['prob', 'random'],
+                    choices=['prob', 'random', 'bertscore', 'noselect'],
                     help='method for selection of syntax suggestions')
 parser.add_argument('--model_name', type=str, default=None,
                     help='name of model to be evaluated or retrained')
@@ -56,15 +56,12 @@ def run_templates():
     nlp_task = args.nlp_task
     search_dataset_name = args.search_dataset
     num_seeds = args.num_seeds
-    is_random_select = False
-    if args.syntax_selection=='random':
-        is_random_select = True
-    # end if
+    selection_method = args.syntax_selection
     Template.get_templates(
         num_seeds=num_seeds,
         nlp_task=nlp_task,
         dataset_name=search_dataset_name,
-        is_random_select=is_random_select
+        selection_method=selection_method
     )
     return
 

### 2022-03-11 python/sa/retrain/Retrain.py

@@ -279,7 +279,7 @@ class Retrain:
         model_dir_name = model_name.replace("/", "-")
         self.output_dir = output_dir
         self.batch_size = 16
-        self.num_epochs = 5.0
+        self.num_epochs = 5.
         
     def load_tokenizer(self, model_name):
         return AutoTokenizer.from_pretrained(model_name)

### 2022-03-11 python/sa/testsuite/Suggest.py

@@ -77,7 +77,7 @@ class Suggest:
         return results
     
     @classmethod
-    def match_word_n_pos(cls, nlp, word_suggest, masked_input: str, mask_pos: List, num_target=10):
+    def match_word_n_pos(cls, nlp, word_suggest, masked_input: str, mask_pos: List):
         # word_suggest = editor.suggest(masked_input, return_score=True, remove_duplicates=True)
         # word_suggest = [ws for ws in word_suggest if cls.is_word_suggestion_avail(ws[0])]
         # word_suggest = cls.remove_duplicates(word_suggest)
@@ -94,7 +94,7 @@ class Suggest:
         if any(suggest_res):
             probs = softmax([s[1] for s in suggest_res])
             suggest_res = [(s[0],p) for s, p in zip(suggest_res, probs)]
-            return suggest_res[:num_target]
+            return suggest_res
         # end if
         return suggest_res
 
@@ -247,12 +247,11 @@ class Suggest:
 
         sent_probs = list()
         for ws_sug, prob_ws in words_suggest:
-            # sent = cls.replace_mask_w_suggestion(masked_input, ws_sug)
-            # sent_probs.append((
-            #     ws_sug,
-            #     sent_prob_wo_target*prob*prob_ws
-            # ))
-            sent_probs.append((ws_sug, prob_ws))
+            sent = cls.replace_mask_w_suggestion(masked_input, ws_sug)
+            sent_probs.append((
+                ws_sug,
+                sent_prob_wo_target*prob*prob_ws
+            ))
         # end for
         sent_probs = sorted(sent_probs, key=lambda x: x[-1], reverse=True)
         sent_probs = [s[0] for s in sent_probs[:NUM_TOPK]]
@@ -271,15 +270,27 @@ class Suggest:
                 word_suggestions[masked_input],
                 masked_input,
                 mask_pos,
-                num_target=num_target
             )
-            if selection_method.lower()=="prob":
+            if selection_method.lower()=='prob':
+                # TODO: fix the probability issue with lower prob when deep tree
                 gen_input['words_suggest'] = cls.get_words_by_prob(words_suggest, gen_input, masked_input)
-            elif selection_method.lower()=="random":
-                gen_input['words_suggest'] = [ws[0] for ws in words_suggest]
-            elif selection_method.lower()=="bert":
-            elif selection_method.lower()=="noselection":
-                
+            elif selection_method.lower()=='random':
+                if len(words_suggest)>num_target:
[…]

### 2022-03-11 python/sa/testsuite/Template.py

@@ -226,7 +226,6 @@ class Template:
     def get_templates(cls, num_seeds, nlp_task, dataset_name, selection_method):
         assert nlp_task in Macros.nlp_tasks
         assert dataset_name in Macros.datasets[nlp_task]
-        # selection_method = 'RANDOM' if is_random_select else 'PROB'
         print(f"***** TASK: {nlp_task}, SEARCH_DATASET: {dataset_name}, SELECTION: {selection_method} *****")
         # Search inputs from searching dataset and expand the inputs using ref_cfg
         nlp = spacy.load('en_core_web_md')

### 2022-03-11 python/sa/testsuite/cfg/CFGDiff.py
debugging

@@ -53,14 +53,14 @@ class CFGDiff:
                  pcfg_ref: dict, 
                  cfg_seed: dict,
                  tree_seed,
-                 is_random_select
+                 selection_method
     ):
         self.cfg_diff = self.get_cfg_diff(
             cfg_seed=cfg_seed,
             tree_seed=tree_seed,
             pcfg_ref=pcfg_ref,
             comp_length=COMP_LENGTH,
-            is_random_select=is_random_select
+            selection_method=selection_method
         )
 
     
@@ -298,7 +298,7 @@ class CFGDiff:
                      pcfg_ref,
                      tree_seed,
                      comp_length,
-                     is_random_select):
+                     selection_method):
         cfg_diff = dict()
         for seed_lhs, seed_rhs in cfg_seed.items():
             try:
@@ -317,7 +317,7 @@ class CFGDiff:
                         # end if
                     # end for
 
-                    if any(rule_from_ref) and not is_random_select:
+                    if any(rule_from_ref) and selection_method=='prob':
                         # Get syntax prob
                         rhs_syntax_probs = self.get_exp_syntax_probs(
                             pcfg_ref, tree_seed, seed_lhs, sr, _sr['word'], rule_from_ref
@@ -338,7 +338,7 @@ class CFGDiff:
                                 ], _sr['word'])
                             # end if
                         # end if
-                    elif any(rule_from_ref) and is_random_select:
+                    elif any(rule_from_ref) and selection_method=='prob':
                         # randomly select the syntax expansion suggestion
                         random.shuffle(rule_from_ref)
                         if seed_lhs not in cfg_diff.keys():

### 2022-03-11 python/sa/testsuite/cfg/CFGExpander.py

@@ -24,10 +24,10 @@ random.seed(Macros.SEED)
 
 class CFGExpander:
 
-    def __init__(self, seed_input, pcfg_ref, is_random_select=False, ref_corpus='treebank'):
+    def __init__(self, seed_input, pcfg_ref, selection_method, ref_corpus='treebank'):
         self.corpus_name = ref_corpus
         self.seed_input: str = seed_input
-        self.is_random_select = is_random_select
+        self.selection_method = selection_method
         tree_dict = self.get_seed_cfg()
         self.tree_seed = tree_dict['tree']
         self.cfg_seed: dict = tree_dict['rule']
@@ -51,6 +51,6 @@ class CFGExpander:
             pcfg_ref=self.pcfg_ref,
             cfg_seed=self.cfg_seed,
             tree_seed=self.tree_seed,
-            is_random_select=self.is_random_select
+            selection_method=self.selection_method
         ).cfg_diff
     

### 2022-03-11 python/sa/explainNLP/explain.py
add new denas implementation

@@ -37,7 +37,7 @@ class CasualInferenceExplain:
         return mutated_x, mask
 
     def compute_weights(self, mask, mutated_y):
-        m = LogisticRegression(fit_intercept=True, max_iter=1000)
+        m = LogisticRegression(fit_intercept=True)
         m.fit(mask.detach().cpu().numpy(), mutated_y.reshape(-1).detach().cpu().numpy())
         weight = m.coef_
         return weight.reshape([-1])
@@ -45,10 +45,10 @@ class CasualInferenceExplain:
     def visualization(self, input_token, important_score):
         res = []
         input_token = input_token.reshape([-1])
-        for tk, s in zip(input_token, important_score):
+        for i, (tk, s) in enumerate(zip(input_token, important_score)):
             tk_str = self.tokenizer.decode(tk)
-            res.append([tk_str, s])
-        res = sorted(res, key=lambda t: t[1], reverse=True)
+            res.append([i, int(tk), tk_str, s])
+        res = sorted(res, key=lambda t: t[3], reverse=True)
         return res
 
     def explain(self, input_sentence):
@@ -69,10 +69,39 @@ class CasualInferenceExplain:
         mutated_y = (mutated_y == ori_predict)
         important_score = self.compute_weights(mask, mutated_y)
         res = self.visualization(input_token, important_score)
-        return res
+        mask = self.create_maek(res, input_sentence, ori_predict)
+        mask_str = self.tokenizer.decode([m for m in mask[0]])
+        mask_str = mask_str.replace(self.tokenizer.unk_token, '[MASK]')
+        return mask_str
 
+    def evaluate(self, mask: torch.tensor, ori_pred, mask_pos):
+        new_tensor = mask.repeat(500, 1).to(self.device)
+        rand_tensor = (torch.rand(new_tensor[:, mask_pos].shape, device=self.device) * 10000).int()
+        rand_tensor = rand_tensor.to(torch.long)
+        new_tensor[:, mask_pos] = rand_tensor
 
+        new_pred = self.predict_sentence(new_tensor)
+        return new_pred.eq(ori_pred).sum() / 500
 
+    def create_maek(self, res, input_sentence, orig_pred):
+        reverse_res = list(reversed(res))
+        input_token = self.tokenizer(input_sentence, return_tensors="pt", padding=True).input_ids
+        pad_id = self.tokenizer.pad_token_id
+        unk_id = self.tokenizer.unk_token_id
 
-
+        mask = input_token.clone()
[…]

### 2022-03-15 paper/ase22/abstract.tex
copy n paste

\begin{abstract}
  \Nlp (NLP) technique becomes one of the core techniques for developing
  text analytics applications.  For developing the NLP applications,
  the applications are required to achieve high reliability before it
  goes to market.  The trustworthiness of the prevalent NLP
  applications is obtained by measuring the accuracy of the
  applications on held-out dataset.  However, evaluating NLP on
  testset does with held-out accuracy is limited to show its quality
  because the held-out datasets are often not comprehensive. While the
  behavioral testing over multiple general linguistic capabilities are
  employed, it relies on manually created test cases, and is still
  limited to measure its comprehensive performance for each linguistic
  capability. In this work, we introduce \Model, an NLP model
  testing methodology. Given a linguistic capability, The
  \Model finds relevant testcases to test the linguistic
  capability from existing datasets as seed inputs, generates
  sufficient number of new test cases by fuzzing the seed inputs based
  on their context-free grammar (\Cfg). We illustrate the usefulness
  of the \Model by showing input diversity and identifying
  critical failures in \sota models for NLP task. In our experiment,
  we show that the \Model generates {} more test cases with {}
  higher diversity, and finds {} more bugs.  
\end{abstract}

### 2022-03-15 paper/ase22/approach.tex
copy n paste

\section{Specification- and Syntax-based Linguistic Capability Testing}
%% \label{sec:approach}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/overview.pdf}
  \caption{Overview of \tool{}.}
  \label{fig:overview}
\end{figure*}

\sw{Some paragraphs in this overview part should go earlier in the
  paper. I am just writing them here for now as I don't think we have
  them in the intro/background yet.}  We design and implement
\emph{Specification- and Syntax-based Linguistic Capability Testing
  (\tool{})} to automatically generate test cases to test the
robustness of sentiment analysis models. We identify four goals for a
large and effective test suite:

\begin{description}
\item[{\bf G1}] the test suite should contain realistic sentences;
\item[{\bf G2}] the test suite should cover diverse syntactic
  structures;
  \item[{\bf G3}] each test case should be categorized into a
    linguistic capability;
\item[{\bf G4}] the label of each test case should be
automatically and accurately defined.
\end{description}

\Chlst's templates generate complete and realistic sentences, and each
template maps to a linguistic capability, satisfying {\bf G1} and {\bf
  G3}. But \Chlst only uses \sw{X} manually created templates to
generate its test suite; all test cases generated by the same template
share the same syntactic structure, thus violating {\bf G2}. In
addition, the label of each \Chlst test case has to be decided
manually, associated with each template, violating {\bf G4}.

We present \tool{}, a new linguistic capability test case generation
tool, that satisfies all of these criteria.  \sw{I could not summarize
  a cohesive idea that drives our design. Leaving it here to fill in.
  Also, I felt my writing below still lacks justification for some
  design choices (e.g., why we do the differentiation).}  Figure
\ref{fig:overview} shows the overview of \tool{}, which consists of
two phases.  The \emph{specification-based seed generation} phase
performs rule-based searches from a real-world dataset ({\bf G1}) and
template-based transformation to obtain the initial seed sentences.
The search rules (e.g., search for neutral sentences that do not
include any positive or negative words) and transformation templates
(e.g., \sw{add an example}) are defined in the \emph{linguistic
  capability specifications}, which guarantee that each resulting seed
conforms to a specific linguistic capability ({\bf G3}) and is
labelled correctly ({\bf G4}).

The \emph{syntax-based sentence expansion} phase expands the seed
sentences with additional syntactic elements (i.e., words \sw{more?})
to cover many real-world syntactic structures ({\bf G2}). It first
performs a syntax analysis to identify the part-of-speech (PoS) tags
that can be inserted to each seed, by comparing the PoS parse trees
between the seed sentence and many other sentences from a large
reference dataset. Each identified tag is inserted into the seed as a
\emph{mask}. It then uses an NLP recommendation model (i.e., BERT
\cite{}) to suggest possible words. If a resulting sentence is
validated to be consistent with the specification which additionally
defines the rules for expansion (e.g., the expanded word should be
neutral), {\bf G3} and {\bf G4} are still satisfied.  Last, because
some validated sentences may include unrealistic suggested words or
use a rare syntactic structure \sw{is this the right motivation to do
  selection?}, we use a heuristic (i.e., combination of the confidence
score from the NLP recommendation model and the frequency of the
syntactic productions) to select the more realistic and frequent
expanded sentences into \tool{}'s test suite.

We now describe each phase of \tool{} in detail.

%\Model generates input \sents with the following phases illustrated
%in \ref{fig:OverallModel}: 1. search phase searches seed \sents
%according to its \req of \lc, 2. seed parsing phase parses the found
%seed \sents and extract their \cfg, 3. reference parsing phase
%collects \pcfg from large corpus, 4. production differentiation phase
%identifies structural expansion candidates for input expansion, and
%5.\sent selection phase generates natural expanded \sent. In this
%section, we provide more details on each phase.

\subsection{Specification-based Seed Generation}
The seed generation phase of \tool starts by searching sentences in a
real-world dataset that match the rules defined in the linguistic
capability specification, and then transforming the matched sentences
using templates to generate seed sentences that conform to individual
linguistic capabilities. The reasons for this design choice are
twofold.  First, while generally judging which linguistic capability
any sentence falls into and which label it should have is infeasible,
there exist simple rules and templates to allow classifying the
resulting sentences into individual linguistic capabilities and with
the correct labels, with high confidence.  This enables us to test
each linguistic capability individually.  Second, searching from a
real-world dataset ensures that the sentences used as test cases for
testing linguistic capabilities are realistic and diverse. The diverse
test cases are more likely to achieve a high coverage of the target
model's functionality in each linguistic capability, thus detecting
more errors.

%The search phase in \Model searches inputs in dataset and selects
%subset of input \sents in the dataset that meets the \lc
%\req. The idea behind this phase is that input distribution of
%\lc is important to generate inputs relevant to \lc. \Lc explains
%expected behaviors of NLP model on specific types of input and
%output. The NLP model is evaluated on how much it performs on the
%input and output. Thus, \lc introduces the constraints of the input
%data. Input data from the constrained distribution are only qualified
%to be used for evaluating the NLP model on the \lc.  In addition,
%diversity in inputs is important to evaluate NLP models on the
%\lc. Inputs that differ are more likely to cover the NLP model
%behavior, and more coverage increases trustworthiness of the
%evaluation. To generate inputs from same distribution on \lc and high
%diversity of inputs, we estabilish \reqs of input and output
%for each \lc, and find inputs that fulfil the \reqs. Given a
%\lc, a \req consists of search \req, transform
%\req and expansion \req. The search \req
%describes features and functionalities that we seek to have in
%inputs. \Model check each input if it satisfy the \req.

Table \ref{tab:specification} shows the search rules and the
transformation templates of all 11 linguistic capabilities we
implemented in \tool{}. \sw{will revise the rest of 3.1 after talking
  to Jaeseong... I think we can show all the specifications.}

\begin{table*}[t]
\small
\centering
\begin{tabular}{l|l}
  {\bf Linguistic capability}	 & {\bf Search rule and transformation template}\\
  \hline
  LC1: Short sentences with neutral & search: \{length: <10; include: neutral adjs \& neutral nouns; \\
  adjectives and nouns & exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}  \\
  & transform: - \\
  \hline
  LC2: Short sentences with  & search: \{length: <10; include: pos adjs; exclude: neg adjs \& neg verbs \& neg nouns; label: pos\} \\
  sentiment-laden adjectives  & | \{length: <10; include: neg adjs; exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}  \\
  & transform: - \\
  \hline
  LC3: Sentiment change over time, & search: \{label: pos\} | \{label: neg\} \\
  present should prevail & transform: \\
  \hline
  LC4: Negated negative should be & search: \{start: [This, That, These, Those] X [is, are]; label: neg\} \\
  positive or neutral & transform:  \\
  \hline
  LC5: Negated neutral should & search: \{start: [This, That, These, Those] X [is, are]; label: neutral\} \\
  still be neutral & transform: \\
  \hline
  LC6: Negation of negative at the & search: \{label: neg\} \\
  end, should be positive or neutral & transform: \\
  \hline
  LC7: Negated positive with neutral & search: \{length: <20; label: pos\} | \{length: <20; label: neutral\} \sw{Not sure about this rule.} \\
  content in the middle & transform: \\
  \hline
  LC8: Author sentiment is more & search: \{label: pos\} | \{label: neg\} \\
  important than of others & transform: \\
  \hline
  LC9: parsing sentiment in & search: \{label: pos\} | \{label: neg\} \\
  (question, yes) form & transform: \\
  \hline
  LC10: Parsing positive sentiment & search: \{label: pos\} \\
  in (question, no) form & transform: \\
  \hline
  LC11: Parsing negative sentiment & search: \{label: neg\} \\
  in (question, no) form & transform: \\
  \hline
\end{tabular}
\caption{Search rules and transformation templates for linguistic capabilities. \sw{Add transformation templates. May need to find a better specification language.}}
\label{tab:specification}
\end{table*}

\begin{figure}[t]
  \centering
  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
  \vspace{-10pt}
  \caption{\SearchRequirementExampleFigCaption}
  \vspace{-10pt}
\end{figure}

\begin{figure}[t]
  \centering
  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
  \\
  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python]{code/requirement_sa2.py}}
  \\
  \caption{\TransformRequirementExampleFigCaption}
  \vspace{-10pt}
\end{figure}

Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
this \lc, the input is required to be short and have only \neu \adjs,
\neu \nns. In addition, the label needs to be \neu. Therefore, all
short natural \sents with only \neu \adjs and \neu \nns are available
to evaluate NLP models. In this work, the sentiment of the words for
the search are classified based on the sentiment scores from
\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
sentiment lexicons.  It provides lexical sentiment scores and the
sentiment word labels are categorized by implementing the rules
in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
how the input and output needs to be tranfromed. Some \lc only accepts
heavily limited input distribution, and it is unlikely to be included
in searching dataset because of its high structural diversity, thus,
finding such \sents is costly. Therefore, our approach is to find
inputs by relaxing search requirement and transform the input to match
the target requirement of the \lc. In this work, the inputs are
transformed by word addition or perturbing the found inputs with \lc
dependent templates. The figure~\ref{fig:TransformReqEx} shows the
example of use of the template requirement. The \lc of \SareqExTwo in
the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
negated \pstv \sents and the neutral expression in the middle. Rather
than searching \sents that match the input distribution of the \lc,
the \Model search \pstv and \neu inputs and combine them into negated
\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
for the \lc. According to the \lc, The value of ``sent1'' and
``sent2'' become each searched \neu and \pstv inputs respectively, and
the template completion generates new inputs that matches the target
\lc. In addition, the transformation of inputs also produce high
diversity in the inputs because of that from initially found
inputs. In this paper, we will denote the searched inputs in this
phase as seed inputs.

\subsection{Syntax-based Sentence Expansion}

The simple search rules and transformation templates used to generate
the seed sentences may limit the syntactic structures these seeds may
cover. To address this limitation, the syntax-based sentence expansion
phase extends the seed sentences to cover syntactic structures
commonly used in real-life sentences. Our idea is to differentiate the
parse trees between the seed sentences and the reference sentences
from a large real-world dataset. The extra PoS tags in the reference
parse trees are identified as potential syntactic elements for
expansion and inserted into the seed sentences as masks. We then use
masked language model to suggest the fill-ins. If the resulting
sentences still conform to the linguistic capability specification,
they are added to \tool{}'s test suite. \sw{May have some redundancy
  and inconsistency with the overview part.}

\subsubsection{Syntax Expansion Identification}

Algorithm \ref{alg:diff} shows how masks are identified for each seed
sentence.  It takes the parse trees of the seeds, generated by the
Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}, and a
reference context-free grammar (CFG) from the Penn Treebank corpus
dataset \cite{} as inputs.  The reference CFG is learned from a large
dataset \cite{} that is representative of the distribution of
real-world language usage.  The algorithm identifies the discrepancy
between the seed syntax and the reference grammar to decide how a seed
can be expanded.
%This phase builds \pcfg from the reference corpus. \cfg is
%constructed by parsing sentences in the corpus and extracting
%\prodrs. In addition, the probability of \cfg is estimated by its
%frequency over corpus. The output of this phase is the constructed
%\pcfg, and it is compared with seed parse trees. For our
%implementation, we build the \pcfg from the Penn Treebank corpus
%dataset.

%\paragraph{Seed parsing.}  To expand seed sentence and generate
%fluent and faithful sentence used for evaluation, \Model studies
%structure of each seed input for its expansion.  Seed parsing takes
%each seed as input, and outputs its parse tree of the seed, using the
%Berkeley Neural
%Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}.

%\paragraph{Reference parsing.}  We take a large-scale real-world
%dataset as reference for sentence expansion.

\input{code/prod_diff_pseudocode}

For each production of in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
context-free grammar and match these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
seed sentence, in their respective positions in the expanded
production.  The left to right traversal of the leaves of an expanded
parse tree forms a masked sentence.  Lastly, we randomly select $k$
masked sentences for the next sentence expansion and validation phase.
\sw{Add justification: why we need to select k masked sentences
  (performance?) and why random makes sense.}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/expansion.pdf}
  \caption{Example of masked sentence generation. \sw{Expansion: Or both {MASK}. -> Masked sentence: Or both {MASK.}}}
%  Expansion of the seed sentence ``Or
%both.''. For a \prodr in seed ``NP->[DT]'' on the left, the \prodr of
%``NP->[DT, NNS]'' is found in reference. Thus, the component NNS can be expanded in the
%seed and ``NP->[DT]'' is replaced with ``NP->[DT, NNS]'' and it generates new
%expanded sentence on the right.
\label{fig:ExpEx}
\end{figure}

Figure \ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
to generate a masked sentence. The sentence ``Or both." is a seed of
\sw{which?} linguistic capability.  \sw{Not sure about the quality of
  the example. Maybe use a better seed for this example?}  The tree on
the left shows the parse tree of this seed; it consists of two
productions: ``FRAG->[CC, NP, .]" and ``NP->[DT]".  When matching the
left-hand-side non-terminal of the second production (i.e., ``NP") in
the reference CFG, we found that it includes a production ``NP->[DT,
  NNS]" which has an additional symbol ``NNS" on the right-hand-side.
The algorithm thus expands the parse tree with this symbol, shown on
the right.  The masked sentence ``Or both \{MASK\}." is the result of
the left-to-right traversal of this expanded parse tree.

%Given the seed parse tree and reference \pcfg, production
%differentiation phase suggests structural expansion candidates on the
%seed input. this phase aims to analyze which structural components
%and where they can be added into the seed structure for its
%expansion. To do so, we explore reference \prodrs comparing it with
%each \prodr used in seed input. This results in the phase described
%in Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
%inputs ($seed\_prod$), it searches production rules in reference
%($ref\_prod$) which it has same non-terminal on the \lhs
%($seed\_prod.lhs==ref\_prod.lhs$) and superset of \rhs of the seed
%production rule ($seed\_prod.rhs \subset ref\_prod.rhs$).  As we
%assume that the reference \cfg is built from real world data
%distribution, the elements in the complement set ($ref\_prod.rhs -
%seed\_prod.rhs$) become an expansion candidate which can be expanded
%from the $seed\_prod.rhs$ found in real world. In addition, the
%measure of how consistent the production rule is with the given seed
%structure is given in its probability of the reference production
%rule ($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
%expansion candidate consists of terminal or nonterminal symbols. When
%there is a phrase-level or clause-level nonterminal symbol, \eg noun
%phrase, it needs to be expanded and replaced with word-level
%nonterminal or terminal symbols to generate the expansion
%candidate. The number of feasible replacement is unbounded because of
%its high degree of freedom. Therefore, in this work, we focus on the
%expansion candidate with only the word-level nonterminal or terminal
%symbols for the effectiveness of \Model. Lastly, the expanded
%component is replaced with the mask token for the next phase. The
%example of the expansion is illustrated in
%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into reference,
%and ``NP->[DT,NNS]'' is identified as its expansion candidate since
%the \rhs of ``NP->[DT,NNS]'' is superset of that of ``NP->[DT]''. the
%component of NNS is replaced with mask token in
%sentence-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
%the next phase.

\subsubsection{Sentence Expansion and Validation}

In this phase, the words to fill in the masks in the masked sentences
are suggested by the BERT pretrained model \cite{}.  The BERT model
suggests word for the mask symbol according to its context \sw{what
  does context mean here?} around in sentence.  \sw{Algorithm 1 does
  not require we only have one mask in the masked sentence. Can the
  model suggest multiple words at the same time?}  \sw{Say a bit more
  about the BERT model suggestion. E.g., it may suggest multiple words
  for the same mask but they are ranked?}

Because BERT model is not aware of the linguistic capability
specification and the grammar symbol in the expanded parse tree, an
expanded sentence using the suggested words may no longer satisfy the
linguistic capability specification. Therefore, we perform validation
on the suggested words and only accept them if the following three
criteria are met.

First, the PoS tag of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in Figure
\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural noun);
thus, the suggested word must also be a ``NNS". \sw{Say how we obtain
  the PoS tag of a suggested word.}  \sw{Also, expand Figure 4 to
  actually include the example of the suggested words?  That way, we
  can easily discuss each validation criteria along with the example.}
Second, we require that the sentiment of the expanded sentence is the
same as the seed sentence. To ensure this, the suggested words must be
neutral.  \sw{Should we present this as part of specification, called
  expansion rule?}  Third, the expanded sentence must still conform to
the specification of the seed's linguistic capability specification.
\sw{It is not clear to me how we check with search rules and
  transformation templates.}

%The suggested word are validated by three criteria. First, The tag of
%POS must be matched with that suggested from the production
%differentiation phase. In the example in the Figure~\ref{fig:ExpEx},
%the mask token comes from the structural component of NNS, plural
%noun. Therefore, the BERT suggested words must be also tagged with
%the NNS. Accordingly, every words of the NNS are only
%available. Second, \Model focuses on the \sa task, and it assume that
%the suggested words must not change sentiment of its input and must
%preserve its consistency of original sentiment label. Therefore, we
%only accept the \neu words for the expansion. Third, the expanded
%sentences with the BERT suggested words must be appropriate for
%evaluating NLP models on the target \lc, and the sentences must pass
%the \req of the \lc. In this work, the BERT suggestions are validated
%by the three criteria.

\subsubsection{Sentence Selection}

\sw{Use BERT score as heuristic to select expanded sentences. Motivate
  why.}

### 2022-03-15 paper/ase22/background.tex
copy n paste

\section{Background}
\label{sec:background}

\sw{We should motivate the testing of linguistic capabilities. Give
  background of the work that has been done in CheckList: what
  capabilities they support and their limitations. Maybe find a
  motivating example?}

### 2022-03-15 paper/ase22/experiment.tex
copy n paste

--- 2022-01-12 paper/issta22/experiment.tex
@@
 %
-In this section, we present experiments to
-evaluate the effectiveness of our proposed evaluation methodology. In
-particular, we address the following research questions:
+In this section, we present experiments to evaluate the effectiveness
+of our proposed evaluation methodology. In particular, we address the
+following research questions:
 
@@
 \Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
-available lexical resource of wrods on Wordnet with three numerical
+available lexical resource of words on Wordnet with three numerical
 scores of objectivity, positivity and negativity. Sentiment word
@@
 %
-We build a reference \Cfg of natural language from the Englush Penn
+We build a reference \Cfg of natural language from the English Penn
 \Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
@@
 \trb corpora available through \Nltk, which is a suite of libraries
-and programs for \Nlp for english. In addition, we parse the seed
+and programs for \Nlp for English. In addition, we parse the seed
 input using into its CFG using the Berkeley Neural
@@
 high-accuracy parser with models for 11 languages. The input is a raw
-text in natural languge and the output is the string representation of
-parse tree. Next after comparing CFGs beteen reference and seed input,
+text in natural language and the output is the string representation of
+parse tree. Next after comparing CFGs between reference and seed input,
 we randomly select 10 expansions for generating templates due to
@@
 %
-\Model searches synosyms of each token from synonym sets extracted
+\Model searches synonyms of each token from synonym sets extracted
 from \Wrdnt using \Spacy open-source library for NLP.
@@
 %
-We evaluate the following \sa nmodels via \Model:
+We evaluate the following \sa models via \Model:
 \Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
-\Dbert~\cite{sanh2019distilbert}. These models are fineturend on \Sstt
-and ther accuracies are \BertAcc, \RobertaAcc and \DbertAcc.
+\Dbert~\cite{sanh2019distilbert}. These models are fine-tuned on \Sstt
+and their accuracies are \BertAcc, \RobertaAcc and \DbertAcc.
 
@@
 train/validation/test sets with the ratio of 8:1:1. The number of
-epochs and batch_size for retraining are 1 and 16 respectively.
-
-%% For \sa task, input requirements are given for each linguistic
-%% capability. Based on the requirements, \Model generates templates and
-%% lexicons.
-%% \MyPara{Model}
-%% \Bert, \Roberta, \Dbert
-
-%% \MyPara{Dataset}
-%% reference CFG generation: Treebank corpus
-%% word sentiments: sentiwordnet (https://github.com/aesuli/SentiWordNet)
-%% cfg parser: berkeley neural parser (https://github.com/nikitakit/self-attentive-parser)
-%% synonyms: spacy wordnet synsets (https://spacy.io/universe/project/spacy-wordnet)
-%% seed search dataset: stanford sentiment treebank (sst) dataset (https://nlp.stanford.edu/sentiment/)
-
-%% \MyPara{Hyper-Parameter}
-%% Number of seed inputs: 10 (random sample)
-%% Number of cfg expansions: 10 (random sample)
-%% Number of synonyms for a word: 10 (random sample)
-
-%% Besides, we retrain the \sota \sa models aformentioned from test cases
-%% generated from \Chlst and \Model. The goal of the retraining is to
-%% assess comprehensiveness of test cases according to performance of
-%% fine-tuned model. We assume that the comprehensive test cases improve
-%% performance of \sa task when fine-tuning with them. On the other hand,
-%% fine-tuning models with less comprehensive test cases increases
-%% overfitting and decrece model performance.
-
-%% \MyPara{Dataset}
-%% Retraining dataset: checklist and our proposed model test cases
-
-%% \MyPara{Hyper-Parameter}
-%% Retraining epoach: 1
-%% Retraining batch_size: 16
+epochs and batch size for retraining are 1 and 16 respectively.

### 2022-03-15 paper/ase22/intro.tex
copy n paste

--- 2022-01-09 paper/issta22/intro.tex
@@
 
-Software testing is the cruicial process when developing software.  It
+Software testing is the crucial process when developing software.  It
 evaluates an attribute or capability of the software and determines
@@
 
-Despite its usefulness, the main limitation of the testing paradaigm
+Despite its usefulness, the main limitation of the testing paradigm
 is that the \ho set often overestimates the performances. Each dataset
@@
 
-On the subject of the limitation of traditional testing paradaigm, a
+On the subject of the limitation of traditional testing paradigm, a
 number of methods have been proposed. First, multiple diagnostic
-datasets for evaluating NLP model were introduced for obtaning
+datasets for evaluating NLP model were introduced for obtaining
 generalized evaluation of the NLP model~\cite{wang2018glue}. Not only

### 2022-03-15 paper/ase22/related.tex
copy n paste

\section{Related Work}
\label{sec:related}

\textbf{NLP Testing.} With the increasing use of NLP models,
evaluation of NLP models is becoming more important. Wang \textit{et
  al.}~\cite{wang2018glue} propose multiple diagnostic datasets to
evaluate NLP models. Few recent works have also considered model
robustness as an aspect for model evaluation. Different methods like
adversarial set generation~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial}, fairness
evaluation~\cite{prabhakaran2019fairness,rottger2020hatecheck},
logical consistency evaluation~\cite{ribeiro2019consistencyeval},
prediction interpretations~\cite{ribeiroSG16lime} and interactive
error analysis~\cite{wu2019errudite} have been proposed to evaluate
model robustness. More recently, \Chlst introduces input-output
behaviors of linguistic capabilities and generates behavior-guided
inputs for validating the behaviors.~\cite{marcoACL2020checklist}
However, the approach only relies on manually generated input
templates, thus the template generation becomes expensive and time
consuming. Also, it does not guarantee the comprehensive evaluation.

\begin{comment}
Not only that, model is evaluated on different aspects such as
robustness of the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Chlst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.
\end{comment}

### 2022-03-15 python/sa/paper/Tables.py
add table script

@@ -1,0 +1,108 @@
+
+# This script is for generating all tables used in paper
+
+from typing import *
+
+import collections
+from pathlib import Path
+
+# from seutil import LoggingUtils, IOUtils
+from seutil import latex
+
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+from ..utils.Logger import Logger
+
+
+class Tables:
+
+    METRICS = ["selfbleu", "acc", "f1"]
+    METRICS_THEADS = {
+        "selfbleu": r"\tBleu",
+        "acc": r"\tAccuracy",
+        "f1": r"\tF1-score",
+    }
+
+    FMT_INT = "{:,d}"
+    FMT_PER = "{:.1%}"
+    FMT_FLOAT = "{:,.2f}"
+
+    @classmethod
+    def make_tables(cls, **options):
+        which: Union[str, List[str]] = options.pop("which", [])
+        paper_dir: Path = Path(options.pop("paper_dir", Macros.paper_dir))
+        tables_dir: Path = paper_dir / "tables"
+        tables_dir.mkdir(parents=True, exist_ok=True)
+
+        if not isinstance(which, list):
+            which = [which]
+        # end if
+
+        for item in which:
+            if item == "lc-req":
+                cls.make_numbers_lc_requirement(Macros.results_dir, Macros.data_dir, tables_dir)
+                cls.make_table_lc_requirement(tables_dir)
+            else:
+                cls.logger.warning(f"Unknown table {item}")
+            # end if
+        # end for
+        return
+
+    @classmethod
+    def make_numbers_lc_requirement(cls, results_dir: Path, data_dir: Path, tables_dir: Path):
+        output_file = latex.File(tables_dir / 'lc-requirement-numbers.tex')
+        
+        for lang in Macros.all_lang:
+            # number of repos
+            url_file = data_dir / lang / "repositories.txt"
+            num_repos = len(IOUtils.load(url_file, IOUtils.Format.txt).splitlines())
+            output_file.append_macro(latex.Macro(f"dataset-{lang}-num-repos", cls.FMT_INT.format(num_repos)))
+
+            # number of files, parsable, unparsable, parsable-unique
+            fc_output_file = results_dir / lang / "ALL" / "fc.txt"
+            fc_output = IOUtils.load(fc_output_file, IOUtils.Format.txt)
+            files_parsable = [l.split(":") for l in fc_output.splitlines()]
[…]

### 2022-03-15 python/sa/requirement/Requirements.py

@@ -46,12 +46,14 @@ class Requirements:
     @classmethod
     def get_requirements(cls, task):
         # dataset_name = datasets[task]
-        req_file = Macros.result_dir / f"requirements_{task}.json"
+        req_dir = Macros.result_dir / 'reqs'
+        req_file = req_dir / f"requirements_{task}.json"
         if os.path.exists(req_file):
             return Utils.read_json(req_file)
         # end if
         reqs = None
-        test_type_file = Macros.result_dir / f"test_type_{task}.json"
+        test_type_file = req_dir / f"test_type_{task}.json"
+        req_dir.mkdir(parents=True, exist_ok=True)
 
         # cap_decp:
         # key: liguistic capability to be evaluated

### 2022-03-15 paper/ase22/approach.tex
add table script
debugging

@@
   \includegraphics[width=\linewidth]{figs/overview.pdf}
-  \caption{Overview of \tool{}.}
-  \label{fig:overview}
+  \caption{\OverviewFigCaption}
 \end{figure*}
@@
 \emph{Specification- and Syntax-based Linguistic Capability Testing
-  (\tool{})} to automatically generate test cases to test the
+  (\tool)} to automatically generate test cases to test the
 robustness of sentiment analysis models. We identify four goals for a
@@
   Also, I felt my writing below still lacks justification for some
-  design choices (e.g., why we do the differentiation).}  Figure
-\ref{fig:overview} shows the overview of \tool{}, which consists of
-two phases.  The \emph{specification-based seed generation} phase
-performs rule-based searches from a real-world dataset ({\bf G1}) and
-template-based transformation to obtain the initial seed sentences.
-The search rules (e.g., search for neutral sentences that do not
-include any positive or negative words) and transformation templates
-(e.g., \sw{add an example}) are defined in the \emph{linguistic
-  capability specifications}, which guarantee that each resulting seed
-conforms to a specific linguistic capability ({\bf G3}) and is
-labelled correctly ({\bf G4}).
+  design choices (e.g., why we do the differentiation).}
+Figure~\ref{fig:overview} shows the overview of \tool{}, which
+consists of two phases.  The \emph{specification-based seed
+  generation} phase performs rule-based searches from a real-world
+dataset ({\bf G1}) and template-based transformation to obtain the
+initial seed sentences.  The search rules (e.g., search for neutral
+sentences that do not include any positive or negative words) and
+transformation templates (e.g., \sw{add an example}) are defined in
+the \emph{linguistic capability specifications}, which guarantee that
+each resulting seed conforms to a specific linguistic capability ({\bf
+  G3}) and is labelled correctly ({\bf G4}).
 
@@
 
-Table \ref{tab:specification} shows the search rules and the
+Table~\ref{tab:specification} shows the search rules and the
 transformation templates of all 11 linguistic capabilities we
@@
 
-\begin{table*}[t]
-\small
-\centering
-\begin{tabular}{l|l}
-  {\bf Linguistic capability}	 & {\bf Search rule and transformation template}\\
-  \hline
-  LC1: Short sentences with neutral & search: \{length: <10; include: neutral adjs \& neutral nouns; \\
-  adjectives and nouns & exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}  \\
-  & transform: - \\
-  \hline
-  LC2: Short sentences with  & search: \{length: <10; include: pos adjs; exclude: neg adjs \& neg verbs \& neg nouns; label: pos\} \\
-  sentiment-laden adjectives  & | \{length: <10; include: neg adjs; exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}  \\
-  & transform: - \\
-  \hline
-  LC3: Sentiment change over time, & search: \{label: pos\} | \{label: neg\} \\
-  present should prevail & transform: \\
-  \hline
-  LC4: Negated negative should be & search: \{start: [This, That, These, Those] X [is, are]; label: neg\} \\
-  positive or neutral & transform:  \\
-  \hline
-  LC5: Negated neutral should & search: \{start: [This, That, These, Those] X [is, are]; label: neutral\} \\
-  still be neutral & transform: \\
-  \hline
-  LC6: Negation of negative at the & search: \{label: neg\} \\
-  end, should be positive or neutral & transform: \\
-  \hline
-  LC7: Negated positive with neutral & search: \{length: <20; label: pos\} | \{length: <20; label: neutral\} \sw{Not sure about this rule.} \\
-  content in the middle & transform: \\
-  \hline
-  LC8: Author sentiment is more & search: \{label: pos\} | \{label: neg\} \\
-  important than of others & transform: \\
-  \hline
-  LC9: parsing sentiment in & search: \{label: pos\} | \{label: neg\} \\
-  (question, yes) form & transform: \\
-  \hline
-  LC10: Parsing positive sentiment & search: \{label: pos\} \\
-  in (question, no) form & transform: \\
-  \hline
-  LC11: Parsing negative sentiment & search: \{label: neg\} \\
-  in (question, no) form & transform: \\
-  \hline
-\end{tabular}
-\caption{Search rules and transformation templates for linguistic capabilities. \sw{Add transformation templates. May need to find a better specification language.}}
-\label{tab:specification}
-\end{table*}
+\InputWithSpace{tables/lc-requirement-table}
 

### 2022-03-15 paper/ase22/tables/lc-requirement-numbers.tex
debugging

%% Automatically generated by pyutil.latex

\DefMacro{lc_1_desc}{Short sentences with neutral adjectives and nouns}
\DefMacro{lc_1_search}{search: \{length: <10; include: neutral adjs \& neutral nouns;}
\DefMacro{lc_1_exclude}{exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
\DefMacro{lc_1_transform}{transform: -}
\DefMacro{lc_2_desc}{Short sentences with sentiment-laden adjectives}
\DefMacro{lc_2_search}{search: \{length: <10; include: pos adjs;}
\DefMacro{lc_2_exclude}{exclude: neg adjs \& neg verbs \& neg nouns; label: pos\} | \{length: <10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
\DefMacro{lc_2_transform}{transform: -}
\DefMacro{lc_3_desc}{Sentiment change over time, present should prevail}
\DefMacro{lc_3_search}{search: \{label: pos\} | \{label: neg\}}
\DefMacro{lc_3_transform}{transform:\{['Previously, I used to like it saying that','Last time, I agreed with saying that','I liked it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I don't like it.', 'now I hate it.']\} | \{['I used to disagree with saying that','Last time, I didn't like it saying that','I hated it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I like it.']\}}
\DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
\DefMacro{lc_4_search}{search: \{start: [This, That, These, Those] X [is, are]; label: neg\}}
\DefMacro{lc_4_transform}{transform: negation of demonstratives}
\DefMacro{lc_5_desc}{Negated neutral should still be neutral}
\DefMacro{lc_5_search}{search: \{start: [This, That, These, Those] X [is, are]; label: neutral\}}
\DefMacro{lc_5_transform}{transform: negation of demonstratives}
\DefMacro{lc_6_desc}{Negation of negative at the end, should be positive or neutral}
\DefMacro{lc_6_search}{search: \{label: neg\}}
\DefMacro{lc_6_transform}{transform:\{['I agreed that', 'I thought that']+[neg sent]+['but it wasn't', 'but I didn't']\}}
\DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
\DefMacro{lc_7_search}{search: \{length: <20; label: pos\} | \{length: <20; label: neutral\}}
\DefMacro{lc_7_transform}{transform:\{['I wouldn't say,', 'I do not think,', 'I don't agree with,']+[neutral sent]+[pos sent]\}}
\DefMacro{lc_8_desc}{Author sentiment is more important than others}
\DefMacro{lc_8_search}{search: \{label:pos\} | \{label: neg\}}
\DefMacro{lc_8_transform}{transform:\{['Some people think that', 'Many people agree with that', 'They think that', 'You agree with that']+[pos sent | neg sent]+['but I think that']+[neg sent | pos sent]\}}
\DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}
\DefMacro{lc_9_search}{search: \{label: pos\} | \{label: neg\}}
\DefMacro{lc_9_transform}{transform:\{['Do I think that', 'Do I agree that']+[pos sent | neg sent]+['? yes']\}}
\DefMacro{lc_10_desc}{Parsing positive sentiment in (question, no) form}
\DefMacro{lc_10_search}{search: \{label: pos\}}
\DefMacro{lc_10_transform}{transform:\{['Do I think that', 'Do I agree that']+[pos sent]+['? no']\}}
\DefMacro{lc_11_desc}{Parsing negative sentiment in (question, no) form}
\DefMacro{lc_11_search}{search: \{label: neg\}}
\DefMacro{lc_11_transform}{transform:\{['Do I think that', 'Do I agree that']+[neg sent]+['? no']\}}

### 2022-03-15 python/sa/main.py
debugging

@@ -16,7 +16,8 @@ parser.add_argument('--run', type=str, required=True,
                     choices=[
                         'requirement', 'template', 'testsuite',
                         'testmodel', 'retrain', 'analyze',
-                        'retrain_analyze', 'explain_nlp', 'selfbleu'
+                        'retrain_analyze', 'explain_nlp', 'selfbleu',
+                        'tables'
                     ], help='task to be run')
 parser.add_argument('--nlp_task', type=str, default="sa",
                     choices=['sa'],
@@ -44,6 +45,10 @@ parser.add_argument('--label_vec_len', type=int, default=2,
                     help='label vector length for the model to be evaluated or retrained')
 parser.add_argument('--testing_on_trainset', action='store_true',
                     help='flag for testing the model with train set')
+
+# arguments for tables and plots
+parser.add_argument('--which', type=str, default=None, nargs='+',
+                    help='tables/plots that you are interested in making')
 
 args = parser.parse_args()
 def run_requirements():
@@ -244,7 +249,17 @@ def run_selfbleu():
     # end if
     selfbleu_main(nlp_task, search_dataset_name, selection_method)
     return
+
+# ==========
+# Tables & Plots
+
+def run_make_tables():
+    from .paper.Tables import Tables
+    options = args.which
+    Tables.make_tables(options)
+    return
     
+
 func_map = {
     "sa": {
         'requirement': run_requirements,
@@ -255,7 +270,8 @@ func_map = {
         'analyze': run_analyze,
         'retrain_analyze': run_retrain_analyze,
         'explain_nlp': run_explainNLP,
-        'selfbleu': run_selfbleu
+        'selfbleu': run_selfbleu,
+        'tables': run_make_tables
     }
 }
 

### 2022-03-15 python/sa/paper/Tables.py

@@ -27,10 +27,13 @@ class Tables:
     FMT_PER = "{:.1%}"
     FMT_FLOAT = "{:,.2f}"
 
+    LATEX_SYMBOL_MAP = {
+        '&': '\&', '{': '\{', '}': '\}'
+    }
+
     @classmethod
-    def make_tables(cls, **options):
-        which: Union[str, List[str]] = options.pop("which", [])
-        paper_dir: Path = Path(options.pop("paper_dir", Macros.paper_dir))
+    def make_tables(cls, which):
+        paper_dir: Path = Macros.paper_dir
         tables_dir: Path = paper_dir / "tables"
         tables_dir.mkdir(parents=True, exist_ok=True)
 
@@ -38,10 +41,10 @@ class Tables:
             which = [which]
         # end if
 
-        for item in which:
+        for item in which: 
             if item == "lc-req":
-                cls.make_numbers_lc_requirement(Macros.results_dir, Macros.data_dir, tables_dir)
-                cls.make_table_lc_requirement(tables_dir)
+                cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
+                cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
             else:
                 cls.logger.warning(f"Unknown table {item}")
             # end if
@@ -49,60 +52,80 @@ class Tables:
         return
 
     @classmethod
-    def make_numbers_lc_requirement(cls, results_dir: Path, data_dir: Path, tables_dir: Path):
-        output_file = latex.File(tables_dir / 'lc-requirement-numbers.tex')
-        
-        for lang in Macros.all_lang:
-            # number of repos
-            url_file = data_dir / lang / "repositories.txt"
-            num_repos = len(IOUtils.load(url_file, IOUtils.Format.txt).splitlines())
-            output_file.append_macro(latex.Macro(f"dataset-{lang}-num-repos", cls.FMT_INT.format(num_repos)))
-
-            # number of files, parsable, unparsable, parsable-unique
-            fc_output_file = results_dir / lang / "ALL" / "fc.txt"
-            fc_output = IOUtils.load(fc_output_file, IOUtils.Format.txt)
-            files_parsable = [l.split(":") for l in fc_output.splitlines()]
-            num_files = len(files_parsable)
-            output_file.append_macro(latex.Macro(f"dataset-{lang}-num-all-files", cls.FMT_INT.format(num_files)))
-
[…]

### 2022-03-15 python/sa/requirement/Requirements.py

@@ -18,11 +18,13 @@ from ..utils.Utils import Utils
 datasets = Macros.datasets
 
 class Requirements:
+
+    cls.req_dir = Macros.result_dir / 'reqs'
     
     @classmethod
     def convert_test_type_txt_to_json(cls):
         for task, dataset_name in datasets.items():
-            dataset_path = Macros.result_dir / f"test_type_{task}.txt"
+            dataset_path = cls.req_dir / f"test_type_{task}.txt"
             result = None
             if os.path.exists(dataset_path):
                 with open(dataset_path, 'r') as f:
@@ -36,7 +38,7 @@ class Requirements:
                 # end with
                 if result is not None:
                     Utils.write_json(result,
-                                     Macros.result_dir / f"test_type_{task}.json",
+                                     cls.req_dir / f"test_type_{task}.json",
                                      pretty_format=True)
                 # end if
             # end if
@@ -46,14 +48,13 @@ class Requirements:
     @classmethod
     def get_requirements(cls, task):
         # dataset_name = datasets[task]
-        req_dir = Macros.result_dir / 'reqs'
-        req_file = req_dir / f"requirements_{task}.json"
+        req_file = cls.req_dir / f"requirements_{task}.json"
         if os.path.exists(req_file):
             return Utils.read_json(req_file)
         # end if
         reqs = None
-        test_type_file = req_dir / f"test_type_{task}.json"
-        req_dir.mkdir(parents=True, exist_ok=True)
+        test_type_file = cls.req_dir / f"test_type_{task}.json"
+        cls.req_dir.mkdir(parents=True, exist_ok=True)
 
         # cap_decp:
         # key: liguistic capability to be evaluated
@@ -143,7 +144,7 @@ class Requirements:
                         "search": [
                             {
                                 "label": "negative",
-                                "include": {
+convert_test_type_txt_to_json                                "include": {
                                     "POS": ["<^demonstratives_AUXBE>"],
                                     "word": None
                                 }

### 2022-03-15 python/sa/utils/Macros.py

@@ -13,7 +13,7 @@ class Macros:
     result_dir: Path = root_dir / "_results" # nlptest/_results
     download_dir: Path = root_dir / "_downloads" # nlptest/_downloads
     log_dir: Path = root_dir / "_logs" # nlptest/_downloads
-    paper_dir = result_dir / "papers"
+    paper_dir = root_dir / "paper" / "ase22"
     dataset_dir = download_dir / "datasets"
 
     FMT_INT = "{:,d}"

### 2022-03-16 python/sa/paper/Tables.py
debugging table

@@ -28,7 +28,7 @@ class Tables:
     FMT_FLOAT = "{:,.2f}"
 
     LATEX_SYMBOL_MAP = {
-        '&': '\&', '{': '\{', '}': '\}'
+        '&': '\&', '{': '\{', '}': '\}', '_': '\_'
     }
 
     @classmethod
@@ -68,20 +68,17 @@ class Tables:
             if len(l_split)>3:
                 desc, search, exclude, transform = l_split[0], l_split[1], l_split[2], l_split[3]
                 desc = cls.replace_latex_symbol(desc)
-                search = cls.replace_latex_symbol(search)
-                exclude = cls.replace_latex_symbol(exclude)
-                transform = cls.replace_latex_symbol(transform)
+                search = r"\textbf{Search}~"+cls.replace_latex_symbol(search.split('<SEARCH>')[-1])
+                search += "~exlcude: "+cls.replace_latex_symbol(exclude.split('<EXCLUDE>')[-1])
+                transform = r"\textbf{Transform}~"+cls.replace_latex_symbol(transform.split('<TRANSFORM>')[-1])
             else:
                 desc, search, exclude, transform = l_split[0], l_split[1], None, l_split[2]
                 desc = cls.replace_latex_symbol(desc)
-                search = cls.replace_latex_symbol(search)
-                transform = cls.replace_latex_symbol(transform)
+                search = r"\textbf{Search}~"+cls.replace_latex_symbol(search.split('<SEARCH>')[-1])
+                transform = r"\textbf{Transform}~"+cls.replace_latex_symbol(transform.split('<TRANSFORM>')[-1])
             # end if
             output_file.append_macro(latex.Macro(f"lc_{l_i+1}_desc", desc))
             output_file.append_macro(latex.Macro(f"lc_{l_i+1}_search", search))
-            if exclude is not None:
-                output_file.append_macro(latex.Macro(f"lc_{l_i+1}_exclude", exclude))
-            # end if
             output_file.append_macro(latex.Macro(f"lc_{l_i+1}_transform", transform))
         # end for
         output_file.save()
@@ -108,12 +105,9 @@ class Tables:
         for l_i, l in enumerate(Utils.read_txt(req_file)):
             l_split = l.split('::')
             len_l = len(l_split) # 3 or 4
-            output_file.append("\multirow{" + str(len_l-1) + "}{*}{\parbox{5cm}{" + \
[…]

### 2022-03-16 paper/ase22/tables/lc-requirement-numbers.tex
update table

@@
 \DefMacro{lc_1_desc}{Short sentences with neutral adjectives and nouns}
-\DefMacro{lc_1_search}{search: \{length: <10; include: neutral adjs \& neutral nouns;}
-\DefMacro{lc_1_exclude}{exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
-\DefMacro{lc_1_transform}{transform: -}
+\DefMacro{lc_1_search}{\textbf{Search}~seed=\{length: <10; include: neutral adjs \& neutral nouns;~Exlcude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
+\DefMacro{lc_1_transform}{\textbf{Transform}~N/A}
 \DefMacro{lc_2_desc}{Short sentences with sentiment-laden adjectives}
-\DefMacro{lc_2_search}{search: \{length: <10; include: pos adjs;}
-\DefMacro{lc_2_exclude}{exclude: neg adjs \& neg verbs \& neg nouns; label: pos\} | \{length: <10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
-\DefMacro{lc_2_transform}{transform: -}
+\DefMacro{lc_2_search}{\textbf{Search}~seed=\{length: <10; include: pos adjs;~Exlcude: neg adjs \& neg verbs \& neg nouns; label: pos\} | \{length: <10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
+\DefMacro{lc_2_transform}{\textbf{Transform}~N/A}
 \DefMacro{lc_3_desc}{Sentiment change over time, present should prevail}
-\DefMacro{lc_3_search}{search: \{label: pos\} | \{label: neg\}}
-\DefMacro{lc_3_transform}{transform:\{['Previously, I used to like it saying that','Last time, I agreed with saying that','I liked it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I don't like it.', 'now I hate it.']\} | \{['I used to disagree with saying that','Last time, I didn't like it saying that','I hated it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I like it.']\}}
+\DefMacro{lc_3_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
+\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{['Previously, I used to like it saying that','Last time, I agreed with saying that','I liked it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I don't like it.', 'now I hate it.']\} | \{['I used to disagree with saying that','Last time, I didn't like it saying that','I hated it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I like it.']\}}
 \DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
-\DefMacro{lc_4_search}{search: \{start: [This, That, These, Those] X [is, are]; label: neg\}}
-\DefMacro{lc_4_transform}{transform: negation of demonstratives}
+\DefMacro{lc_4_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] X [is, are]; label: neg\}}
+\DefMacro{lc_4_transform}{\textbf{Transform}~seed=negation of demonstrative\_sent (['is'] -> ['is not', 'isn't'], ['are'] -> ['are not', 'aren't'])}
 \DefMacro{lc_5_desc}{Negated neutral should still be neutral}
-\DefMacro{lc_5_search}{search: \{start: [This, That, These, Those] X [is, are]; label: neutral\}}
-\DefMacro{lc_5_transform}{transform: negation of demonstratives}
+\DefMacro{lc_5_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] X [is, are]; label: neutral\}}
+\DefMacro{lc_5_transform}{\textbf{Transform}~negation of demonstrative\_sent}
 \DefMacro{lc_6_desc}{Negation of negative at the end, should be positive or neutral}
-\DefMacro{lc_6_search}{search: \{label: neg\}}
-\DefMacro{lc_6_transform}{transform:\{['I agreed that', 'I thought that']+[neg sent]+['but it wasn't', 'but I didn't']\}}
+\DefMacro{lc_6_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
+\DefMacro{lc_6_transform}{\textbf{Transform}~seed=\{['I agreed that', 'I thought that']+[neg sent]+['but it wasn't', 'but I didn't']\}}
 \DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
-\DefMacro{lc_7_search}{search: \{length: <20; label: pos\} | \{length: <20; label: neutral\}}
-\DefMacro{lc_7_transform}{transform:\{['I wouldn't say,', 'I do not think,', 'I don't agree with,']+[neutral sent]+[pos sent]\}}
+\DefMacro{lc_7_search}{\textbf{Search}~pos\_sent=\{length: <20; label: pos\}, neutral\_sent=\{length: <20; label: neutral\}}
+\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{['I wouldn't say,', 'I do not think,', 'I don't agree with,']+[neutral sent]+[pos sent]\}}
 \DefMacro{lc_8_desc}{Author sentiment is more important than others}
-\DefMacro{lc_8_search}{search: \{label:pos\} | \{label: neg\}}
-\DefMacro{lc_8_transform}{transform:\{['Some people think that', 'Many people agree with that', 'They think that', 'You agree with that']+[pos sent | neg sent]+['but I think that']+[neg sent | pos sent]\}}
+\DefMacro{lc_8_search}{\textbf{Search}~pos\_sent=\{label:pos\}, neg\_sent=\{label: neg\}}
+\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\} | \{[temp1]+[neg\_sent]+[temp2]+[pos\_sent]\} where temp1=\{['Some people think that', 'Many people agree with that', 'They think that', 'You agree with that'], temp2=['but I think that']\}}
 \DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}
-\DefMacro{lc_9_search}{search: \{label: pos\} | \{label: neg\}}
-\DefMacro{lc_9_transform}{transform:\{['Do I think that', 'Do I agree that']+[pos sent | neg sent]+['? yes']\}}
+\DefMacro{lc_9_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
+\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos sent | neg sent]+['? yes']\}}
 \DefMacro{lc_10_desc}{Parsing positive sentiment in (question, no) form}
-\DefMacro{lc_10_search}{search: \{label: pos\}}
-\DefMacro{lc_10_transform}{transform:\{['Do I think that', 'Do I agree that']+[pos sent]+['? no']\}}
+\DefMacro{lc_10_search}{\textbf{Search}~pos\_sent=\{label: pos\}}
+\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos sent]+['? no']\}}
 \DefMacro{lc_11_desc}{Parsing negative sentiment in (question, no) form}
-\DefMacro{lc_11_search}{search: \{label: neg\}}
-\DefMacro{lc_11_transform}{transform:\{['Do I think that', 'Do I agree that']+[neg sent]+['? no']\}}
+\DefMacro{lc_11_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
+\DefMacro{lc_11_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[neg sent]+['? no']\}}

### 2022-03-19 python/sa/model/Model.py
debugging

@@ -113,7 +113,14 @@ class Model:
         # end if
 
     @classmethod
-    def run(cls, testsuite, model, pred_and_conf_fn, print_fn=None, format_example_fn=None, n=Macros.nsamples, logger=None):
+    def run(cls,
+            testsuite,
+            model,
+            pred_and_conf_fn,
+            print_fn=None,
+            format_example_fn=None,
+            n=Macros.nsamples,
+            logger=None):
         cls.model = model
         testsuite.run(pred_and_conf_fn, n=n, overwrite=True, logger=logger)
         testsuite.summary(n=Macros.nsamples,

### 2022-03-19 python/sa/retrain/Retrain.py

@@ -504,8 +504,8 @@ class Retrain:
         _task, _ = Model.model_map[self.task]
         return pipeline(_task, model=str(checkpoint_dir), tokenizer=tokenizer, framework="pt", device=0)
 
-    def run_model_on_testsuite(self, testsuite, model, pred_and_conf_fn=None, n=Macros.nsamples):
-        Model.run(testsuite, model, pred_and_conf_fn, print_fn=None, format_example_fn=None, n=n)
+    def run_model_on_testsuite(self, testsuite, model, pred_and_conf_fn=None, n=Macros.nsamples, logger=logger):
+        Model.run(testsuite, model, pred_and_conf_fn, print_fn=None, format_example_fn=None, n=n, logger=logger)
 
     def test_on_our_testsuites(self, logger=None):
         _print = print
@@ -530,7 +530,7 @@ class Retrain:
             for testsuite_file in testsuite_files:
                 testsuite = Testmodel.load_testsuite(testsuite_file)
                 _print(f">>>>> RETRAINED MODEL: {self.model_name}")
-                self.run_model_on_testsuite(testsuite, model, Testmodel.model_func_map[self.task], n=Macros.nsamples)
+                self.run_model_on_testsuite(testsuite, model, Testmodel.model_func_map[self.task], n=Macros.nsamples, logger=logger)
                 _print(f"<<<<< RETRAINED MODEL: {self.model_name}")
             # end for
         # end for
@@ -547,7 +547,7 @@ class Retrain:
         _print(f">>>>> RETRAINED MODEL: {self.model_name}")
         model = self.load_retrained_model()
         testsuite = Testmodel.load_testsuite(Macros.BASELINES[Macros.datasets[Macros.sa_task][1]]['testsuite_file'])
-        self.run_model_on_testsuite(testsuite, model, Testmodel.model_func_map[self.task], n=Macros.nsamples)
+        self.run_model_on_testsuite(testsuite, model, Testmodel.model_func_map[self.task], n=Macros.nsamples, logger=logger)
         _print(f"<<<<< RETRAINED MODEL: {self.model_name}")
         _print('**********')
         return

### 2022-03-19 paper/ase22/approach.tex
table debugging

@@
 \emph{Specification- and Syntax-based Linguistic Capability Testing
-  (\tool)} to automatically generate test cases to test the
+  (\tool{})} to automatically generate test cases to test the
 robustness of sentiment analysis models. We identify four goals for a
@@
 \item[{\bf G1}] the test suite should contain realistic sentences;
-\item[{\bf G2}] the test suite should cover diverse syntactic
-  structures;
-  \item[{\bf G3}] each test case should be categorized into a
-    linguistic capability;
+\item[{\bf G2}] the test suite should cover diverse syntactic structures;
+  \item[{\bf G3}] each test case should be
+categorized into a linguistic capability;
 \item[{\bf G4}] the label of each test case should be
@@
 sentences that do not include any positive or negative words) and
-transformation templates (e.g., \sw{add an example}) are defined in
-the \emph{linguistic capability specifications}, which guarantee that
-each resulting seed conforms to a specific linguistic capability ({\bf
-  G3}) and is labelled correctly ({\bf G4}).
+transformation templates (e.g., \sw{add an example} \jl{sentence
+  negation}) are defined in the \emph{linguistic capability
+  specifications}, which guarantee that each resulting seed conforms
+to a specific linguistic capability ({\bf G3}) and is labelled
+correctly ({\bf G4}).
 
 The \emph{syntax-based sentence expansion} phase expands the seed
-sentences with additional syntactic elements (i.e., words \sw{more?})
-to cover many real-world syntactic structures ({\bf G2}). It first
-performs a syntax analysis to identify the part-of-speech (PoS) tags
-that can be inserted to each seed, by comparing the PoS parse trees
-between the seed sentence and many other sentences from a large
-reference dataset. Each identified tag is inserted into the seed as a
-\emph{mask}. It then uses an NLP recommendation model (i.e., BERT
-\cite{}) to suggest possible words. If a resulting sentence is
-validated to be consistent with the specification which additionally
-defines the rules for expansion (e.g., the expanded word should be
-neutral), {\bf G3} and {\bf G4} are still satisfied.  Last, because
-some validated sentences may include unrealistic suggested words or
-use a rare syntactic structure \sw{is this the right motivation to do
-  selection?}, we use a heuristic (i.e., combination of the confidence
-score from the NLP recommendation model and the frequency of the
-syntactic productions) to select the more realistic and frequent
-expanded sentences into \tool{}'s test suite.
+sentences with additional syntactic elements (i.e., words
+\sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
+syntactic structures ({\bf G2}). It first performs a syntax analysis
+to identify the part-of-speech (PoS) tags that can be inserted to each
+seed, by comparing the PoS parse trees between the seed sentence and
+many other sentences from a large reference dataset. Each identified
+tag is inserted into the seed as a \emph{mask}. It then uses an NLP
+recommendation model (i.e., BERT \cite{}) to suggest possible
+words. If a resulting sentence is validated to be consistent with the
+specification which additionally defines the rules for expansion
+(e.g., the expanded word should be neutral), {\bf G3} and {\bf G4} are
+still satisfied.  Last, because some validated sentences may include
+unacceptable suggested words given the context \sw{is this the
+  right motivation to do selection?} \jl{I edited the sentence. please
+  let me know if it is clear}, we use a heuristic (i.e., the
+confidence score from the NLP recommendation model) to select the more
+realistic context-aware expanded sentences into \tool{}'s test suite.
 
@@
 
-Table~\ref{tab:specification} shows the search rules and the
+Table \ref{tab:specification} shows the search rules and the
 transformation templates of all 11 linguistic capabilities we
-implemented in \tool{}. \sw{will revise the rest of 3.1 after talking
-  to Jaeseong... I think we can show all the specifications.}
+implemented in \tool{}. \sw{@Jaeseong: revise the rest of 3.1 based on
+  Table \ref{tab:specification}. I commented out the old text but it
+  is still in the tex file.}
 
@@
 
-\begin{figure}[t]
-  \centering
-  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
-  \vspace{-10pt}
-  \caption{\SearchRequirementExampleFigCaption}
-  \vspace{-10pt}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
-  \\
-  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python]{code/requirement_sa2.py}}
-  \\
-  \caption{\TransformRequirementExampleFigCaption}
-  \vspace{-10pt}
-\end{figure}
-
-Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
-this \lc, the input is required to be short and have only \neu \adjs,
-\neu \nns. In addition, the label needs to be \neu. Therefore, all
-short natural \sents with only \neu \adjs and \neu \nns are available
-to evaluate NLP models. In this work, the sentiment of the words for
-the search are classified based on the sentiment scores from
-\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
-sentiment lexicons.  It provides lexical sentiment scores and the
-sentiment word labels are categorized by implementing the rules
-in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
-how the input and output needs to be tranfromed. Some \lc only accepts
-heavily limited input distribution, and it is unlikely to be included
-in searching dataset because of its high structural diversity, thus,
-finding such \sents is costly. Therefore, our approach is to find
-inputs by relaxing search requirement and transform the input to match
-the target requirement of the \lc. In this work, the inputs are
-transformed by word addition or perturbing the found inputs with \lc
-dependent templates. The figure~\ref{fig:TransformReqEx} shows the
-example of use of the template requirement. The \lc of \SareqExTwo in
-the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
-negated \pstv \sents and the neutral expression in the middle. Rather
-than searching \sents that match the input distribution of the \lc,
-the \Model search \pstv and \neu inputs and combine them into negated
-\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
-for the \lc. According to the \lc, The value of ``sent1'' and
-``sent2'' become each searched \neu and \pstv inputs respectively, and
-the template completion generates new inputs that matches the target
-\lc. In addition, the transformation of inputs also produce high
-diversity in the inputs because of that from initially found
-inputs. In this paper, we will denote the searched inputs in this
-phase as seed inputs.
+%\begin{figure}[t]
+%  \centering
+%  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
+%  \vspace{-10pt}
+%  \caption{\SearchRequirementExampleFigCaption}
+%  \vspace{-10pt}
+%\end{figure}
+%
+%\begin{figure}[t]
+%  \centering
+%  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
+%  \\
+%  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python]{code/requirement_sa2.py}}
+%  \\
+%  \caption{\TransformRequirementExampleFigCaption}
+%  \vspace{-10pt}
+%\end{figure}
+%
+%Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
+%this \lc, the input is required to be short and have only \neu \adjs,
+%\neu \nns. In addition, the label needs to be \neu. Therefore, all
+%short natural \sents with only \neu \adjs and \neu \nns are available
+%to evaluate NLP models. In this work, the sentiment of the words for
+%the search are classified based on the sentiment scores from
+%\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
+%sentiment lexicons.  It provides lexical sentiment scores and the
+%sentiment word labels are categorized by implementing the rules
+%in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
+%how the input and output needs to be tranfromed. Some \lc only accepts
+%heavily limited input distribution, and it is unlikely to be included
+%in searching dataset because of its high structural diversity, thus,
+%finding such \sents is costly. Therefore, our approach is to find
+%inputs by relaxing search requirement and transform the input to match
+%the target requirement of the \lc. In this work, the inputs are
+%transformed by word addition or perturbing the found inputs with \lc
+%dependent templates. The figure~\ref{fig:TransformReqEx} shows the
+%example of use of the template requirement. The \lc of \SareqExTwo in
+%the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
+%negated \pstv \sents and the neutral expression in the middle. Rather
+%than searching \sents that match the input distribution of the \lc,
+%the \Model search \pstv and \neu inputs and combine them into negated
+%\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
+%for the \lc. According to the \lc, The value of ``sent1'' and
+%``sent2'' become each searched \neu and \pstv inputs respectively, and
+%the template completion generates new inputs that matches the target
+%\lc. In addition, the transformation of inputs also produce high
+%diversity in the inputs because of that from initially found
+%inputs. In this paper, we will denote the searched inputs in this
+%phase as seed inputs.
 
@@
 can be expanded.
-%This phase builds \pcfg from the reference corpus. \cfg is
-%constructed by parsing sentences in the corpus and extracting
-%\prodrs. In addition, the probability of \cfg is estimated by its
-%frequency over corpus. The output of this phase is the constructed
+%This phase builds \pcfg from the reference corpus. \cfg
+%is constructed by parsing sentences in the corpus and extracting
+%\prodrs. In addition, the probability of \cfg is estimated by
+%its frequency over corpus. The output of this phase is the constructed
 %\pcfg, and it is compared with seed parse trees. For our
-%implementation, we build the \pcfg from the Penn Treebank corpus
-%dataset.
+%implementation, we build the \pcfg from the Penn Treebank corpus dataset.
 
-%\paragraph{Seed parsing.}  To expand seed sentence and generate
-%fluent and faithful sentence used for evaluation, \Model studies
-%structure of each seed input for its expansion.  Seed parsing takes
-%each seed as input, and outputs its parse tree of the seed, using the
-%Berkeley Neural
+%\paragraph{Seed parsing.}
+%To expand seed sentence and generate fluent and faithful sentence
+%used for evaluation, \Model studies structure of each seed input for
+%its expansion.
+%Seed parsing takes each seed as
+%input, and outputs its parse tree of the seed, using the Berkeley Neural
 %Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}.
 
-%\paragraph{Reference parsing.}  We take a large-scale real-world
-%dataset as reference for sentence expansion.
+%\paragraph{Reference parsing.}
+%We take a large-scale real-world dataset as reference for sentence expansion.
 
@@
 
-\begin{figure}
+\begin{figure*}[t]
   \centering
-  \includegraphics[width=\linewidth]{figs/expansion.pdf}
-  \caption{Example of masked sentence generation. \sw{Expansion: Or both {MASK}. -> Masked sentence: Or both {MASK.}}}
+  \includegraphics[scale=0.7]{figs/running_example.pdf}
+  \caption{\RunningExCaption}
 %  Expansion of the seed sentence ``Or
@@
 %expanded sentence on the right.
-\label{fig:ExpEx}
-\end{figure}
+\end{figure*}
 
-Figure \ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
+\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
 to generate a masked sentence. The sentence ``Or both." is a seed of
-\sw{which?} linguistic capability.  \sw{Not sure about the quality of
-  the example. Maybe use a better seed for this example?}  The tree on
-the left shows the parse tree of this seed; it consists of two
-productions: ``FRAG->[CC, NP, .]" and ``NP->[DT]".  When matching the
-left-hand-side non-terminal of the second production (i.e., ``NP") in
-the reference CFG, we found that it includes a production ``NP->[DT,
-  NNS]" which has an additional symbol ``NNS" on the right-hand-side.
-The algorithm thus expands the parse tree with this symbol, shown on
-the right.  The masked sentence ``Or both \{MASK\}." is the result of
-the left-to-right traversal of this expanded parse tree.
+\sw{which?} linguistic capability.  The tree on the left shows the
+parse tree of this seed; it consists of two productions: ``FRAG->[CC,
+  NP, .]" and ``NP->[DT]".  When matching the left-hand-side
+non-terminal of the second production (i.e., ``NP") in the reference
+CFG, we found that it includes a production ``NP->[DT, NNS]" which has
+an additional symbol ``NNS" on the right-hand-side.  The algorithm
+thus expands the parse tree with this symbol, shown in the second
+tree.  The masked sentence ``Or both \{MASK\}." is the result of the
+left-to-right traversal of this expanded parse tree.
 
@@
 %differentiation phase suggests structural expansion candidates on the
-%seed input. this phase aims to analyze which structural components
-%and where they can be added into the seed structure for its
-%expansion. To do so, we explore reference \prodrs comparing it with
-%each \prodr used in seed input. This results in the phase described
-%in Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
+%seed input. this phase aims to analyze which structural components and
+%where they can be added into the seed structure for its expansion. To
+%do so, we explore reference \prodrs comparing it with each \prodr used
+%in seed input. This results in the phase described in
+%Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
 %inputs ($seed\_prod$), it searches production rules in reference
@@
 %measure of how consistent the production rule is with the given seed
-%structure is given in its probability of the reference production
-%rule ($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
+%structure is given in its probability of the reference production rule
+%($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
 %expansion candidate consists of terminal or nonterminal symbols. When
@@
 %example of the expansion is illustrated in
-%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into reference,
-%and ``NP->[DT,NNS]'' is identified as its expansion candidate since
-%the \rhs of ``NP->[DT,NNS]'' is superset of that of ``NP->[DT]''. the
-%component of NNS is replaced with mask token in
+%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into
+%reference, and ``NP->[DT,NNS]'' is identified as its expansion
+%candidate since the \rhs of ``NP->[DT,NNS]'' is superset of that of
+%``NP->[DT]''. the component of NNS is replaced with mask token in
 %sentence-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
@@
 are suggested by the BERT pretrained model \cite{}.  The BERT model
-suggests word for the mask symbol according to its context \sw{what
-  does context mean here?} around in sentence.  \sw{Algorithm 1 does
-  not require we only have one mask in the masked sentence. Can the
-  model suggest multiple words at the same time?}  \sw{Say a bit more
-  about the BERT model suggestion. E.g., it may suggest multiple words
-  for the same mask but they are ranked?}
+suggests word for the mask symbol
+
+according to its context \sw{what does context mean here?} around in
+sentence.  \sw{Algorithm 1 does not require we only have one mask in
+  the masked sentence. Can the model suggest multiple words at the
+  same time?}  \sw{Say a bit more about the BERT model
+  suggestion. E.g., it may suggest multiple words for the same mask
+  but they are ranked?}
 
@@
 First, the PoS tag of the suggested word must match the PoS tag of the
-expanded symbol in the parse tree. For the example in Figure
-\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural noun);
-thus, the suggested word must also be a ``NNS". \sw{Say how we obtain
-  the PoS tag of a suggested word.}  \sw{Also, expand Figure 4 to
-  actually include the example of the suggested words?  That way, we
-  can easily discuss each validation criteria along with the example.}
-Second, we require that the sentiment of the expanded sentence is the
-same as the seed sentence. To ensure this, the suggested words must be
-neutral.  \sw{Should we present this as part of specification, called
-  expansion rule?}  Third, the expanded sentence must still conform to
-the specification of the seed's linguistic capability specification.
-\sw{It is not clear to me how we check with search rules and
-  transformation templates.}
+expanded symbol in the parse tree. For the example in
+Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
+noun); thus, the suggested word must also be a ``NNS". \sw{Say how we
+  obtain the PoS tag of a suggested word.}  Second, we require that
+the sentiment of the expanded sentence is the same as the seed
+sentence. To ensure this, the suggested words must be neutral.
+\sw{Should we present this as part of specification, called expansion
+  rule?}  Third, we additionally verify that the expanded sentences
+satisfied the same search rules for the seed sentence. Our goal for
+generating the expanded sentences is to use them for evaluating the
+\sa models on the associated \lc in addition to the seed sentence. It
+is only achieved when the expanded sentences are also met with the
+same search rules for the \lc. For LC1 as an example, the expanded
+sentence must still conform to the specification of the seed's
+linguistic capability specification. Therefore, the expanded sentences
+are required to be short and to only have neutral adjectives and
+nouns. \sw{Say why we use the third criteria only for LC1 and LC2.}
+\jl{I added the explanation}
 
-%The suggested word are validated by three criteria. First, The tag of
-%POS must be matched with that suggested from the production
-%differentiation phase. In the example in the Figure~\ref{fig:ExpEx},
-%the mask token comes from the structural component of NNS, plural
-%noun. Therefore, the BERT suggested words must be also tagged with
-%the NNS. Accordingly, every words of the NNS are only
-%available. Second, \Model focuses on the \sa task, and it assume that
-%the suggested words must not change sentiment of its input and must
-%preserve its consistency of original sentiment label. Therefore, we
-%only accept the \neu words for the expansion. Third, the expanded
-%sentences with the BERT suggested words must be appropriate for
-%evaluating NLP models on the target \lc, and the sentences must pass
-%the \req of the \lc. In this work, the BERT suggestions are validated
-%by the three criteria.
+\paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
+by BERT. For this masked sentence, BERT suggested six words. Each word
+is associated with the confidence score provided by BERT, the PoS tag,
+and the sentiment. Among the six words, only ``ways'' and ``things''
+are validated by \tool{} because they have the Pos tag ``NNS'' and are
+neutral. In addition, it is found that both sentences meets the search
+rule of the associated \lc of \SareqExOne. In the end, two sentences
+of ``Or both ways'' and ``Or both things'' are generated.  \sw{Do we
+  also check if the expanded sentence meets the
+  specification?}\jl{Yes. I added the explanation of validation of \lc
+  \req}
+
+%The suggested word are
+%validated by three criteria. First, The tag of POS must be matched with
+%that suggested from the production differentiation phase. In the
+%example in the Figure~\ref{fig:ExpEx}, the mask token comes from the
+%structural component of NNS, plural noun. Therefore, the BERT
+%suggested words must be also tagged with the NNS. Accordingly, every
+%words of the NNS are only available. Second, \Model focuses on the \sa
+%task, and it assume that the suggested words must not change sentiment
+%of its input and must preserve its consistency of original sentiment
+%label. Therefore, we only accept the \neu words for the
+%expansion. Third, the expanded sentences with the BERT suggested words
+%must be appropriate for evaluating NLP models on the target \lc, and the
+%sentences must pass the \req of the \lc. In this work, the BERT
+%suggestions are validated by the three criteria.
 
 \subsubsection{Sentence Selection}
-
-\sw{Use BERT score as heuristic to select expanded sentences. Motivate
-  why.}
+\sw{@Jaeseong: Add how we select expanded sentences and motivate why.}
+After 
+\paragraph{Running example.} \sw{Refer to the example to say how we
+  use the BERT score to select.} \jl{I dont think we need this
+  subsection of sentence selection it is already explained at the
+  previous stage with running example.}

### 2022-03-19 paper/ase22/tables/lc-requirement-numbers.tex
debugging table

@@
 \DefMacro{lc_1_desc}{Short sentences with neutral adjectives and nouns}
-\DefMacro{lc_1_search}{\textbf{Search}~seed=\{length: <10; include: neutral adjs \& neutral nouns;~Exlcude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
+\DefMacro{lc_1_search}{\textbf{Search}~seed=\{length: <10; include: neutral adjs \& neutral nouns;~exlcude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
 \DefMacro{lc_1_transform}{\textbf{Transform}~N/A}
 \DefMacro{lc_2_desc}{Short sentences with sentiment-laden adjectives}
-\DefMacro{lc_2_search}{\textbf{Search}~seed=\{length: <10; include: pos adjs;~Exlcude: neg adjs \& neg verbs \& neg nouns; label: pos\} | \{length: <10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
+\DefMacro{lc_2_search}{\textbf{Search}~seed=\{length: <10; include: pos adjs;~exlcude: neg adjs \& neg verbs \& neg nouns; label: pos\} | \{length: <10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
 \DefMacro{lc_2_transform}{\textbf{Transform}~N/A}
@@
 \DefMacro{lc_3_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{['Previously, I used to like it saying that','Last time, I agreed with saying that','I liked it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I don't like it.', 'now I hate it.']\} | \{['I used to disagree with saying that','Last time, I didn't like it saying that','I hated it much as to say that']+[neg sent]+['but', 'although', 'on the other hand']+['now I like it.']\}}
+\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{['Previously, I used to like it saying that','Last time, I agreed with saying that','I liked it much as to say that']+[neg\_sent, pos\_sent]+['but', 'although', 'on the other hand']+['now I don't like it.', 'now I hate it.']\} | \{['I used to disagree with saying that','Last time, I didn't like it saying that','I hated it much as to say that']+[neg\_sent, pos\_sent]+['but', 'although', 'on the other hand']+['now I like it.']\}}
 \DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
-\DefMacro{lc_4_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] X [is, are]; label: neg\}}
+\DefMacro{lc_4_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] + [is, are]; label: neg\}}
 \DefMacro{lc_4_transform}{\textbf{Transform}~seed=negation of demonstrative\_sent (['is'] -> ['is not', 'isn't'], ['are'] -> ['are not', 'aren't'])}
 \DefMacro{lc_5_desc}{Negated neutral should still be neutral}
-\DefMacro{lc_5_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] X [is, are]; label: neutral\}}
+\DefMacro{lc_5_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] + [is, are]; label: neutral\}}
 \DefMacro{lc_5_transform}{\textbf{Transform}~negation of demonstrative\_sent}
@@
 \DefMacro{lc_6_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
-\DefMacro{lc_6_transform}{\textbf{Transform}~seed=\{['I agreed that', 'I thought that']+[neg sent]+['but it wasn't', 'but I didn't']\}}
+\DefMacro{lc_6_transform}{\textbf{Transform}~seed=\{['I agreed that', 'I thought that']+[neg\_sent]+['but it wasn't', 'but I didn't']\}}
 \DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
 \DefMacro{lc_7_search}{\textbf{Search}~pos\_sent=\{length: <20; label: pos\}, neutral\_sent=\{length: <20; label: neutral\}}
-\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{['I wouldn't say,', 'I do not think,', 'I don't agree with,']+[neutral sent]+[pos sent]\}}
+\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{['I wouldn't say,', 'I do not think,', 'I don't agree with,']+[neutral\_sent]+[pos\_sent]\}}
 \DefMacro{lc_8_desc}{Author sentiment is more important than others}
@@
 \DefMacro{lc_9_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos sent | neg sent]+['? yes']\}}
+\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos\_sent | neg\_sent]+['? yes']\}}
 \DefMacro{lc_10_desc}{Parsing positive sentiment in (question, no) form}
 \DefMacro{lc_10_search}{\textbf{Search}~pos\_sent=\{label: pos\}}
-\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos sent]+['? no']\}}
+\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos\_sent]+['? no']\}}
 \DefMacro{lc_11_desc}{Parsing negative sentiment in (question, no) form}
 \DefMacro{lc_11_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
-\DefMacro{lc_11_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[neg sent]+['? no']\}}
+\DefMacro{lc_11_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[neg\_sent]+['? no']\}}

### 2022-03-19 .#run_sa.sh
debugging runsa

@@ -1,1 +1,0 @@
-jasonlee@thinkpad-x1.7453:1647721853

### 2022-03-19 run_sa.sh

@@ -6,6 +6,8 @@ readonly PYTHON_DIR="${_DIR}/python"
 readonly DL_DIR="${_DIR}/_downloads"
 readonly RESULT_DIR="${_DIR}/_results"
 
+# ==========
+# Exp Results
 
 function gen_requirements() {
         # write requirements in json
@@ -41,7 +43,7 @@ function eval_models() {
          # evaluating models on our generated testcases
          CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection random > /dev/null 2>&1
          # CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection bertscore > /dev/null 2>&1
-         # CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection noselect > /dev/null 2>&1
+         # CUDA_VISIBLE_DEVICES=6,7 time python -m python.sa.main --run testmodel --syntax_selection noselect > /dev/null 2>&1
         )
 }
 
@@ -55,21 +57,19 @@ function retrain_models() {
                              --syntax_selection random \
                              --lcs \
                              --model_name textattack/bert-base-uncased-SST-2 #> /dev/null 2>&1
-
          CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
                              --run retrain \
                              --testing_on_trainset \
                              --search_dataset sst \
                              --syntax_selection random \
+                             --lcs \
                              --model_name textattack/bert-base-uncased-SST-2 #> /dev/null 2>&1
-
-         echo "***** TRAIN: checklist, EVAL: ours *****"
+         echo "***** TRAIN: ours, EVAL: checklist *****"
          CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
                              --run retrain \
                              --search_dataset checklist \
                              --lcs \
                              --model_name textattack/bert-base-uncased-SST-2 #> /dev/null 2>&1
-
          CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
                              --run retrain \
                              --testing_on_trainset \
@@ -81,7 +81,9 @@ function retrain_models() {
 function eval_retrained_models() {
         # evaluate NLP models with generated testsuites
         (cd ${_DIR}
-         python -m python.sa.main --run testmodel --local_model_name checklist-textattack-bert-base-uncased-SST-2
+         python -m python.sa.main \
[…]

### 2022-03-19 paper/ase22/tables/lc-requirement-numbers.tex
debugging table

@@
 \DefMacro{lc_3_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{['Previously, I used to like it saying that','Last time, I agreed with saying that','I liked it much as to say that']+[neg\_sent, pos\_sent]+['but', 'although', 'on the other hand']+['now I don't like it.', 'now I hate it.']\} | \{['I used to disagree with saying that','Last time, I didn't like it saying that','I hated it much as to say that']+[neg\_sent, pos\_sent]+['but', 'although', 'on the other hand']+['now I like it.']\}}
+\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{[`Previously, I used to like it saying that',`Last time, I agreed with saying that',`I liked it much as to say that']+[pos\_sent | neg\_sent]+[`but', `although', `on the other hand']+[`now I don't like it.', `now I hate it.']\} | \{[`I used to disagree with saying that',`Last time, I didn't like it saying that',`I hated it much as to say that']+[neg\_sent, pos\_sent]+[`but', `although', `on the other hand']+[`now I like it.']\}}
 \DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
 \DefMacro{lc_4_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] + [is, are]; label: neg\}}
-\DefMacro{lc_4_transform}{\textbf{Transform}~seed=negation of demonstrative\_sent (['is'] -> ['is not', 'isn't'], ['are'] -> ['are not', 'aren't'])}
+\DefMacro{lc_4_transform}{\textbf{Transform}~seed=negation of demonstrative\_sent ([`is'] -> [`is not', `isn't'], [`are'] -> [`are not', `aren't'])}
 \DefMacro{lc_5_desc}{Negated neutral should still be neutral}
@@
 \DefMacro{lc_6_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
-\DefMacro{lc_6_transform}{\textbf{Transform}~seed=\{['I agreed that', 'I thought that']+[neg\_sent]+['but it wasn't', 'but I didn't']\}}
+\DefMacro{lc_6_transform}{\textbf{Transform}~seed=\{[`I agreed that', `I thought that']+[neg\_sent]+[`but it wasn't', `but I didn't']\}}
 \DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
 \DefMacro{lc_7_search}{\textbf{Search}~pos\_sent=\{length: <20; label: pos\}, neutral\_sent=\{length: <20; label: neutral\}}
-\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{['I wouldn't say,', 'I do not think,', 'I don't agree with,']+[neutral\_sent]+[pos\_sent]\}}
+\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{[`I wouldn't say,', `I do not think,', `I don't agree with,']+[neutral\_sent]+[`,']+[pos\_sent]\}}
 \DefMacro{lc_8_desc}{Author sentiment is more important than others}
 \DefMacro{lc_8_search}{\textbf{Search}~pos\_sent=\{label:pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\} | \{[temp1]+[neg\_sent]+[temp2]+[pos\_sent]\} where temp1=\{['Some people think that', 'Many people agree with that', 'They think that', 'You agree with that'], temp2=['but I think that']\}}
+\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\} | \{[temp1]+[neg\_sent]+[temp2]+[pos\_sent]\} where temp1=\{[`Some people think that', `Many people agree with that', `They think that', `You agree with that'], temp2=[`but I think that']\}}
 \DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}
 \DefMacro{lc_9_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos\_sent | neg\_sent]+['? yes']\}}
+\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent | neg\_sent]+[`? yes']\}}
 \DefMacro{lc_10_desc}{Parsing positive sentiment in (question, no) form}
 \DefMacro{lc_10_search}{\textbf{Search}~pos\_sent=\{label: pos\}}
-\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[pos\_sent]+['? no']\}}
+\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent]+[`? no']\}}
 \DefMacro{lc_11_desc}{Parsing negative sentiment in (question, no) form}
 \DefMacro{lc_11_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
-\DefMacro{lc_11_transform}{\textbf{Transform}~seed=\{['Do I think that', 'Do I agree that']+[neg\_sent]+['? no']\}}
+\DefMacro{lc_11_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[neg\_sent]+[`? no']\}}

### 2022-03-19 paper/ase22/approach.tex
writing approach

@@
 \begin{description}
-\item[{\bf G1}] the test suite should contain realistic sentences;
+\item[{\bf G1}] the test suite should contain realistic \sents;
 \item[{\bf G2}] the test suite should cover diverse syntactic structures;
   \item[{\bf G3}] each test case should be
-categorized into a linguistic capability;
+categorized into a \lc;
 \item[{\bf G4}] the label of each test case should be
@@
 
-\Chlst's templates generate complete and realistic sentences, and each
-template maps to a linguistic capability, satisfying {\bf G1} and {\bf
+\Chlst's templates generate complete and realistic \sents, and each
+template maps to a \lc, satisfying {\bf G1} and {\bf
   G3}. But \Chlst only uses \sw{X} manually created templates to
@@
 
-We present \tool{}, a new linguistic capability test case generation
+We present \tool{}, a new \lc test case generation
 tool, that satisfies all of these criteria.  \sw{I could not summarize
@@
 dataset ({\bf G1}) and template-based transformation to obtain the
-initial seed sentences.  The search rules (e.g., search for neutral
-sentences that do not include any positive or negative words) and
-transformation templates (e.g., \sw{add an example} \jl{sentence
-  negation}) are defined in the \emph{linguistic capability
+initial seed \sents.  The search rules (e.g., search for \neu
+\sents that do not include any \pstv or \ngtv words) and
+transformation templates (e.g., \sw{add an example} \jl{\sent
+  negation}) are defined in the \emph{\lc
   specifications}, which guarantee that each resulting seed conforms
-to a specific linguistic capability ({\bf G3}) and is labelled
+to a specific \lc ({\bf G3}) and is labelled
 correctly ({\bf G4}).
 
-The \emph{syntax-based sentence expansion} phase expands the seed
-sentences with additional syntactic elements (i.e., words
+The \emph{syntax-based \sent expansion} phase expands the seed
+\sents with additional syntactic elements (i.e., words
 \sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
@@
 to identify the part-of-speech (PoS) tags that can be inserted to each
-seed, by comparing the PoS parse trees between the seed sentence and
-many other sentences from a large reference dataset. Each identified
+seed, by comparing the PoS parse trees between the seed \sent and
+many other \sents from a large reference dataset. Each identified
 tag is inserted into the seed as a \emph{mask}. It then uses an NLP
 recommendation model (i.e., BERT \cite{}) to suggest possible
-words. If a resulting sentence is validated to be consistent with the
+words. If a resulting \sent is validated to be consistent with the
 specification which additionally defines the rules for expansion
-(e.g., the expanded word should be neutral), {\bf G3} and {\bf G4} are
-still satisfied.  Last, because some validated sentences may include
+(e.g., the expanded word should be \neu), {\bf G3} and {\bf G4} are
+still satisfied.  Last, because some validated \sents may include
 unacceptable suggested words given the context \sw{is this the
-  right motivation to do selection?} \jl{I edited the sentence. please
+  right motivation to do selection?} \jl{I edited the \sent. please
   let me know if it is clear}, we use a heuristic (i.e., the
 confidence score from the NLP recommendation model) to select the more
-realistic context-aware expanded sentences into \tool{}'s test suite.
+realistic context-aware expanded \sents into \tool{}'s test suite.
 
@@
 \subsection{Specification-based Seed Generation}
-The seed generation phase of \tool starts by searching sentences in a
-real-world dataset that match the rules defined in the linguistic
-capability specification, and then transforming the matched sentences
-using templates to generate seed sentences that conform to individual
-linguistic capabilities. The reasons for this design choice are
-twofold.  First, while generally judging which linguistic capability
-any sentence falls into and which label it should have is infeasible,
-there exist simple rules and templates to allow classifying the
-resulting sentences into individual linguistic capabilities and with
-the correct labels, with high confidence.  This enables us to test
-each linguistic capability individually.  Second, searching from a
-real-world dataset ensures that the sentences used as test cases for
-testing linguistic capabilities are realistic and diverse. The diverse
-test cases are more likely to achieve a high coverage of the target
-model's functionality in each linguistic capability, thus detecting
-more errors.
+The seed generation phase of \tool starts by searching \sents in a
+real-world dataset that match the rules defined in the \lc
+specification, and then transforming the matched \sents using
+templates to generate seed \sents that conform to individual
+\lcs. The reasons for this design choice are twofold.  First, while
+generally judging which \lc any \sent falls into and which label it
+should have is infeasible, there exist simple rules and templates to
+allow classifying the resulting \sents into individual \lcs and
+with the correct labels, with high confidence.  This enables us to
+test each \lc individually.  Second, searching from a real-world
+dataset ensures that the \sents used as test cases for testing \lcs
+are realistic and diverse. The diverse test cases are more likely to
+achieve a high coverage of the target model's functionality in each
+\lc, thus detecting more errors.
+%
+In this phase, \tool first search and selects \sents applicable to
+the \lc in a given real-world dataset with search rules. In case that
+the search rules only fulfill portion of the \lc specifications, the
+selected \sents are not yet appropriate to become seed, we
+transform the selected \sents into seed \sents using the
+heuristic templates.
+%
+Table~\ref{tab:specification} shows the search rules and the
+transformation templates of all 11 linguistic capabilities we
+implemented in \tool. The first column shows the \lc type and its
+description, and the second column shows the search rule and
+transformation template used in each \lc. For LC1 and LC2, the NLP
+models are evaluated in the scope of short \sents with selective
+sentiment words. It does not require any guidance for its
+transformation because the search rule alone is sufficient to conform
+to the \lcs. On the other hand, search rules of LC3 and LC4 are not is
+not enough to match their \lc specification, thus \tool uses heuristic
+templates to conform the found \sents to the \lc. For example, the
+selected \sents becomes seeds by preturbing them with the templates
+and by negating the selected demonstrative \sents to conform to LC3
+and LC4 respectively (see the third and forth rows in
+Table~\ref{tab:specification}).
+\sw{@Jaeseong: revise the rest of 3.1 based on
+  Table~\ref{tab:specification}. I commented out the old text but it
+  is still in the tex file.} \jl{I revised and added the explanation}
 
@@
 %inputs. \Model check each input if it satisfy the \req.
-
-Table \ref{tab:specification} shows the search rules and the
-transformation templates of all 11 linguistic capabilities we
-implemented in \tool{}. \sw{@Jaeseong: revise the rest of 3.1 based on
-  Table \ref{tab:specification}. I commented out the old text but it
-  is still in the tex file.}
 
@@
 %the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
-%negated \pstv \sents and the neutral expression in the middle. Rather
+%negated \pstv \sents and the \neu expression in the middle. Rather
 %than searching \sents that match the input distribution of the \lc,
@@
 
-\subsection{Syntax-based Sentence Expansion}
+\subsection{Syntax-based \Sent Expansion}
 
 The simple search rules and transformation templates used to generate
-the seed sentences may limit the syntactic structures these seeds may
-cover. To address this limitation, the syntax-based sentence expansion
-phase extends the seed sentences to cover syntactic structures
-commonly used in real-life sentences. Our idea is to differentiate the
-parse trees between the seed sentences and the reference sentences
+the seed \sents may limit the syntactic structures these seeds may
+cover. To address this limitation, the syntax-based \sent expansion
+phase extends the seed \sents to cover syntactic structures
+commonly used in real-life \sents. Our idea is to differentiate the
+parse trees between the seed \sents and the reference \sents
 from a large real-world dataset. The extra PoS tags in the reference
 parse trees are identified as potential syntactic elements for
-expansion and inserted into the seed sentences as masks. We then use
+expansion and inserted into the seed \sents as masks. We then use
 masked language model to suggest the fill-ins. If the resulting
-sentences still conform to the linguistic capability specification,
+\sents still conform to the \lc specification,
 they are added to \tool{}'s test suite. \sw{May have some redundancy
@@
 Algorithm \ref{alg:diff} shows how masks are identified for each seed
-sentence.  It takes the parse trees of the seeds, generated by the
+\sent.  It takes the parse trees of the seeds, generated by the
 Berkeley Neural
@@
 %This phase builds \pcfg from the reference corpus. \cfg
-%is constructed by parsing sentences in the corpus and extracting
+%is constructed by parsing \sents in the corpus and extracting
 %\prodrs. In addition, the probability of \cfg is estimated by
@@
 %\paragraph{Seed parsing.}
-%To expand seed sentence and generate fluent and faithful sentence
+%To expand seed \sent and generate fluent and faithful \sent
 %used for evaluation, \Model studies structure of each seed input for
@@
 %\paragraph{Reference parsing.}
-%We take a large-scale real-world dataset as reference for sentence expansion.
+%We take a large-scale real-world dataset as reference for \sent expansion.
 
@@
 symbols in the $r\_rhs$ are inserted as masks in the parse tree of
-seed sentence, in their respective positions in the expanded
+seed \sent, in their respective positions in the expanded
 production.  The left to right traversal of the leaves of an expanded
-parse tree forms a masked sentence.  Lastly, we randomly select $k$
-masked sentences for the next sentence expansion and validation phase.
-\sw{Add justification: why we need to select k masked sentences
+parse tree forms a masked \sent.  Lastly, we randomly select $k$
+masked \sents for the next \sent expansion and validation phase.
+\sw{Add justification: why we need to select k masked \sents
   (performance?) and why random makes sense.}
@@
   \caption{\RunningExCaption}
-%  Expansion of the seed sentence ``Or
+%  Expansion of the seed \sent ``Or
 %both.''. For a \prodr in seed ``NP->[DT]'' on the left, the \prodr of
@@
 %seed and ``NP->[DT]'' is replaced with ``NP->[DT, NNS]'' and it generates new
-%expanded sentence on the right.
+%expanded \sent on the right.
 \end{figure*}
@@
 \paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
-to generate a masked sentence. The sentence ``Or both." is a seed of
-\sw{which?} linguistic capability.  The tree on the left shows the
+to generate a masked \sent. The \sent ``Or both." is a seed of
+\sw{which?} \lc.  The tree on the left shows the
 parse tree of this seed; it consists of two productions: ``FRAG->[CC,
@@
 thus expands the parse tree with this symbol, shown in the second
-tree.  The masked sentence ``Or both \{MASK\}." is the result of the
+tree.  The masked \sent ``Or both \{MASK\}." is the result of the
 left-to-right traversal of this expanded parse tree.
@@
 %``NP->[DT]''. the component of NNS is replaced with mask token in
-%sentence-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
+%\sent-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
 %the next phase.
 
-\subsubsection{Sentence Expansion and Validation}
+\subsubsection{\Sent Expansion and Validation}
 
-In this phase, the words to fill in the masks in the masked sentences
+In this phase, the words to fill in the masks in the masked \sents
 are suggested by the BERT pretrained model \cite{}.  The BERT model
@@
 according to its context \sw{what does context mean here?} around in
-sentence.  \sw{Algorithm 1 does not require we only have one mask in
-  the masked sentence. Can the model suggest multiple words at the
+\sent.  \sw{Algorithm 1 does not require we only have one mask in
+  the masked \sent. Can the model suggest multiple words at the
   same time?}  \sw{Say a bit more about the BERT model
@@
 
-Because BERT model is not aware of the linguistic capability
+Because BERT model is not aware of the \lc
 specification and the grammar symbol in the expanded parse tree, an
-expanded sentence using the suggested words may no longer satisfy the
-linguistic capability specification. Therefore, we perform validation
+expanded \sent using the suggested words may no longer satisfy the
+\lc specification. Therefore, we perform validation
 on the suggested words and only accept them if the following three
@@
   obtain the PoS tag of a suggested word.}  Second, we require that
-the sentiment of the expanded sentence is the same as the seed
-sentence. To ensure this, the suggested words must be neutral.
+the sentiment of the expanded \sent is the same as the seed
+\sent. To ensure this, the suggested words must be \neu.
 \sw{Should we present this as part of specification, called expansion
-  rule?}  Third, we additionally verify that the expanded sentences
-satisfied the same search rules for the seed sentence. Our goal for
-generating the expanded sentences is to use them for evaluating the
-\sa models on the associated \lc in addition to the seed sentence. It
-is only achieved when the expanded sentences are also met with the
+  rule?}  Third, we additionally verify that the expanded \sents
+satisfied the same search rules for the seed \sent. Our goal for
+generating the expanded \sents is to use them for evaluating the
+\sa models on the associated \lc in addition to the seed \sent. It
+is only achieved when the expanded \sents are also met with the
 same search rules for the \lc. For LC1 as an example, the expanded
-sentence must still conform to the specification of the seed's
-linguistic capability specification. Therefore, the expanded sentences
-are required to be short and to only have neutral adjectives and
-nouns. \sw{Say why we use the third criteria only for LC1 and LC2.}
-\jl{I added the explanation}
+\sent must still conform to the specification of the seed's \lc
+specification. Therefore, the expanded \sents are required to be
+short and to only have \neu adjectives and \nns. \sw{Say why we use
+  the third criteria only for LC1 and LC2.}  \jl{I added the
+  explanation}
 
 \paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
-by BERT. For this masked sentence, BERT suggested six words. Each word
+by BERT. For this masked \sent, BERT suggested six words. Each word
 is associated with the confidence score provided by BERT, the PoS tag,
@@
 are validated by \tool{} because they have the Pos tag ``NNS'' and are
-neutral. In addition, it is found that both sentences meets the search
-rule of the associated \lc of \SareqExOne. In the end, two sentences
+\neu. In addition, it is found that both \sents meets the search
+rule of the associated \lc of \SareqExOne. In the end, two \sents
 of ``Or both ways'' and ``Or both things'' are generated.  \sw{Do we
-  also check if the expanded sentence meets the
+  also check if the expanded \sent meets the
   specification?}\jl{Yes. I added the explanation of validation of \lc
@@
 %label. Therefore, we only accept the \neu words for the
-%expansion. Third, the expanded sentences with the BERT suggested words
+%expansion. Third, the expanded \sents with the BERT suggested words
 %must be appropriate for evaluating NLP models on the target \lc, and the
-%sentences must pass the \req of the \lc. In this work, the BERT
+%\sents must pass the \req of the \lc. In this work, the BERT
 %suggestions are validated by the three criteria.
 
-\subsubsection{Sentence Selection}
-\sw{@Jaeseong: Add how we select expanded sentences and motivate why.}
+\subsubsection{\Sent Selection}
+\sw{@Jaeseong: Add how we select expanded \sents and motivate why.}
 After 
@@
   use the BERT score to select.} \jl{I dont think we need this
-  subsection of sentence selection it is already explained at the
+  subsection of \sent selection it is already explained at the
   previous stage with running example.}

### 2022-03-21 run_sa.sh
debugging

@@ -21,16 +21,16 @@ function gen_templates() {
         (cd ${_DIR}
          # CUDA_VISIBLE_DEVICES=5,6 python -m python.sa.main --run template --search_dataset sst --syntax_selection random > /dev/null 2>&1
          # CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run template --search_dataset sst --syntax_selection bertscore > /dev/null 2>&1
-         CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run template --search_dataset sst --syntax_selection noselect > /dev/null 2>&1
+         CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run template --search_dataset sst --syntax_selection noselect
         )
 }
 
 function gen_testsuite() {
         # write test cases into Checklist Testsuite format
         (cd ${_DIR}
-         # python -m python.sa.main --run testsuite --search_dataset sst --syntax_selection random > /dev/null 2>&1
-         # python -m python.sa.main --run testsuite --search_dataset sst --syntax_selection bertscore > /dev/null 2>&1
-         python -m python.sa.main --run testsuite --search_dataset sst --syntax_selection noselect > /dev/null 2>&1
+         # python -m python.sa.main --run testsuite --search_dataset sst --syntax_selection random
+         # python -m python.sa.main --run testsuite --search_dataset sst --syntax_selection bertscore
+         python -m python.sa.main --run testsuite --search_dataset sst --syntax_selection noselect
         )
 }
 
@@ -38,12 +38,12 @@ function eval_models() {
         # evaluate NLP models with generated testsuites
         (cd ${_DIR}
          # evaluating models on checklist testcases
-         CUDA_VISIBLE_DEVICES=1,3,5 python -m python.sa.main --run testmodel --test_baseline > /dev/null 2>&1
+         CUDA_VISIBLE_DEVICES=1,3,5 python -m python.sa.main --run testmodel --test_baseline
 
          # evaluating models on our generated testcases
-         CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection random > /dev/null 2>&1
-         # CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection bertscore > /dev/null 2>&1
[…]

### 2022-03-21 paper/ase22/approach.tex

@@
 syntactic structures ({\bf G2}). It first performs a syntax analysis
-to identify the part-of-speech (PoS) tags that can be inserted to each
+to identify the \pos (PoS) tags that can be inserted to each
 seed, by comparing the PoS parse trees between the seed \sent and
@@
 symbols in the $r\_rhs$ are inserted as masks in the parse tree of
-seed \sent, in their respective positions in the expanded
-production.  The left to right traversal of the leaves of an expanded
-parse tree forms a masked \sent.  Lastly, we randomly select $k$
-masked \sents for the next \sent expansion and validation phase.
-\sw{Add justification: why we need to select k masked \sents
-  (performance?) and why random makes sense.}
+seed \sent, in their respective positions in the expanded production.
+The left to right traversal of the leaves of an expanded parse tree
+forms a masked \sent.  Lastly, due to the inefficient cost of
+accessing full list of the masked \sents, we randomly select $k$
+masked \sents for the next \sent expansion and validation phase when
+the masked \sents are more than maximum number of masked \sents. The
+random sampling is unbiased approach since it gives same chance to be
+chosen. Thus, the random sample becomes representative of the
+population of the masked \sents, and it efficiently shows the
+usefulness of the \tool.  \sw{Add justification: why we need to select
+  k masked \sents (performance?)  and why random makes sense.} \jl{I
+  added the statement for it}
 
@@
 \paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
-to generate a masked \sent. The \sent ``Or both." is a seed of
-\sw{which?} \lc.  The tree on the left shows the
-parse tree of this seed; it consists of two productions: ``FRAG->[CC,
-  NP, .]" and ``NP->[DT]".  When matching the left-hand-side
-non-terminal of the second production (i.e., ``NP") in the reference
-CFG, we found that it includes a production ``NP->[DT, NNS]" which has
-an additional symbol ``NNS" on the right-hand-side.  The algorithm
-thus expands the parse tree with this symbol, shown in the second
-tree.  The masked \sent ``Or both \{MASK\}." is the result of the
-left-to-right traversal of this expanded parse tree.
+to generate a masked \sent. The \sent ``Or both." is a seed of \lc of
+\SareqExOne.  The tree on the left shows the parse tree of this seed;
+it consists of two productions: ``FRAG->[CC, NP, .]" and ``NP->[DT]".
+When matching the left-hand-side non-terminal of the second production
+(i.e., ``NP") in the reference CFG, we found that it includes a
+production ``NP->[DT, NNS]" which has an additional symbol ``NNS" on
+the right-hand-side.  The algorithm thus expands the parse tree with
+this symbol, shown in the second tree.  The masked \sent ``Or both
+\{MASK\}." is the result of the left-to-right traversal of this
+expanded parse tree.
 
@@
 
-In this phase, the words to fill in the masks in the masked \sents
-are suggested by the BERT pretrained model \cite{}.  The BERT model
-suggests word for the mask symbol
-
-according to its context \sw{what does context mean here?} around in
-\sent.  \sw{Algorithm 1 does not require we only have one mask in
-  the masked \sent. Can the model suggest multiple words at the
-  same time?}  \sw{Say a bit more about the BERT model
-  suggestion. E.g., it may suggest multiple words for the same mask
-  but they are ranked?}
-
+In this phase, the words to fill in the masks in the masked \sents are
+suggested by the BERT pretrained model~\cite{devlin2019bert}.  The
+BERT is a transformer-based \nl model. It is pretrained on two tasks
+of masked token prediction and next sentence prediction. As a result
+of the training process, the BERT model suggests word for the mask
+token according to its surrounding context in \sent. For each masked
+token, multiple words are suggested ranked by their confidence scores.
+\sw{Algorithm 1 does not require we only have one mask in the masked
+  \sent. Can the model suggest multiple words at the same time?}
+\jl{yes. it can predict multiple masked tokens at the same time.}
+\sw{Say a bit more about the BERT model suggestion. E.g., it may
+  suggest multiple words for the same mask but they are ranked?}
+\jl{I added the explanation of BERT}
+%
 Because BERT model is not aware of the \lc
@@
 Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
-noun); thus, the suggested word must also be a ``NNS". \sw{Say how we
-  obtain the PoS tag of a suggested word.}  Second, we require that
-the sentiment of the expanded \sent is the same as the seed
-\sent. To ensure this, the suggested words must be \neu.
-\sw{Should we present this as part of specification, called expansion
-  rule?}  Third, we additionally verify that the expanded \sents
-satisfied the same search rules for the seed \sent. Our goal for
-generating the expanded \sents is to use them for evaluating the
-\sa models on the associated \lc in addition to the seed \sent. It
-is only achieved when the expanded \sents are also met with the
-same search rules for the \lc. For LC1 as an example, the expanded
-\sent must still conform to the specification of the seed's \lc
-specification. Therefore, the expanded \sents are required to be
+noun); thus, the suggested word must also be a ``NNS". In this work,
+we use \spacy, a free open-source library for \nlp, for extracting PoS
+tags for each suggested word.\sw{Say how we obtain the PoS tag of a
+  suggested word.}\jl{I added it} Second, it is required that the
+sentiment of the expanded \sent becomes the same as the seed \sent. To
+ensure this, the suggested words must be \neu.  \sw{Should we present
+  this as part of specification, called expansion rule?} \jl{I did it
+  because I think that there is no issue on mentioning it and that is
+  how we assumed and did} Third, we additionally verify that the
+expanded \sents satisfied the same search rules for the seed
+\sent. Our goal for generating the expanded \sents is to use them for
+evaluating the \sa models on the associated \lc in addition to the
+seed \sent. It is only achieved when the expanded \sents are also met
+with the same search rules for the \lc. For LC1 as an example, the
+expanded \sent must still conform to the specification of the seed's
+\lc specification. Therefore, the expanded \sents are required to be
 short and to only have \neu adjectives and \nns. \sw{Say why we use

### 2022-03-21 python/sa/paper/Tables.py
table for selfbleu

@@ -45,6 +45,9 @@ class Tables:
             if item == "lc-req":
                 cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
                 cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
+            elif item == "selfbleu":
+                cls.make_numbers_selfbleu(Macros.result_dir, tables_dir)
+                cls.make_table_selfbleu(Macros.result_dir, tables_dir)
             else:
                 cls.logger.warning(f"Unknown table {item}")
             # end if
@@ -121,4 +124,28 @@ class Tables:
         output_file.append(r"\vspace{\ReqTableVSpace}")
         output_file.append(r"\end{table*}")
         output_file.save()
+        return
+
+    @classmethod
+    def make_numbers_selfbleu(cls, results_dir: Path, tables_dir: Path):
+        output_file = latex.File(tables_dir / 'selfbleu-numbers.tex')
+        selfbleu_file = Macros.selfbleu_result_dir / "{task}_{search_dataset_name}_{selection_method}_testcase_selfbleu.json"
+        selfbleu_res = Utils.read_json(selfbleu_file)
+        our_num_data = selfbleu_res['num_data']
+        our_score = selfbleu_res['score']
+        bl_name = selfbleu_res['baseline_name']
+        bl_num_data = selfbleu_res['baseline_num_data']
+        bl_score = selfbleu_res['baseline_score']
+        output_file.append_macro(latex.Macro("selfbleu_our_num_data", our_num_data))
+        output_file.append_macro(latex.Macro("selfbleu_our_score", FMT_FLOAT.format(our_socre)))
+        output_file.append_macro(latex.Macro("selfbleu_bl_name", bl_name))
+        output_file.append_macro(latex.Macro("selfbleu_bl_num_data", bl_num_data))
+        output_file.append_macro(latex.Macro("selfbleu_bl_score", FMT_FLOAT.format(bl_score)))
+
+        output_file.save()
+        return
+
+    @classmethoe
+    def make_table_selfbleu(cls, results_dir: Path, tables_dir: Path):
+        
         return

### 2022-03-29 python/sa/paper/Tables.py
debugging and table

@@ -127,25 +127,83 @@ class Tables:
         return
 
     @classmethod
-    def make_numbers_selfbleu(cls, results_dir: Path, tables_dir: Path):
+    def make_numbers_selfbleu(cls,
+                              results_dir: Path,
+                              tables_dir: Path,
+                              task: str,
+                              search_dataset_name: str,
+                              selection_method: str):
         output_file = latex.File(tables_dir / 'selfbleu-numbers.tex')
         selfbleu_file = Macros.selfbleu_result_dir / "{task}_{search_dataset_name}_{selection_method}_testcase_selfbleu.json"
         selfbleu_res = Utils.read_json(selfbleu_file)
-        our_num_data = selfbleu_res['num_data']
-        our_score = selfbleu_res['score']
-        bl_name = selfbleu_res['baseline_name']
-        bl_num_data = selfbleu_res['baseline_num_data']
-        bl_score = selfbleu_res['baseline_score']
-        output_file.append_macro(latex.Macro("selfbleu_our_num_data", our_num_data))
-        output_file.append_macro(latex.Macro("selfbleu_our_score", FMT_FLOAT.format(our_socre)))
-        output_file.append_macro(latex.Macro("selfbleu_bl_name", bl_name))
-        output_file.append_macro(latex.Macro("selfbleu_bl_num_data", bl_num_data))
-        output_file.append_macro(latex.Macro("selfbleu_bl_score", FMT_FLOAT.format(bl_score)))
+        our_scores = selfbleu_res['ours']
+        for lc_i, lc in enumerate(our_scores.keys()):
+            output_file.append_macro(latex.Macro(f"selfbleu_our_lc_{lc_i}_desc", lc))
+            output_file.append_macro(latex.Macro(f"selfbleu_our_lc_{lc_i}_num_data", our_scores[lc]['num_data']))
+            output_file.append_macro(latex.Macro(f"selfbleu_our_lc_{lc_i}_score", our_scores[lc]['score']))
+        # end for
 
+        checklist_scores = selfbleu_res['checklist']
+        ours_lc_list = list(our_scores.keys())
+        for lc in checklist_scores.keys():
+            if lc==Macros.CHECKLIST_LC_LIST[8]:
+                our_lc_i = ours_lc_list.index(Macros.CHECKLIST_LC_LIST[8])
+                output_file.append_macro(latex.Macro("selfbleu_checklist_lc_{our_lc_i}_num_data", checklist_scores[lc]['num_data']))
[…]

### 2022-03-29 python/sa/utils/Macros.py

@@ -90,3 +90,45 @@ class Macros:
     # SST2
     sst2_dir: Path = dataset_dir / "sst2"
     sst2_sa_trainset_file: Path = retrain_dataset_dir / "sa_sst2_trainset.json"
+
+
+    CHECKLIST_LC_LIST = [
+        'Sentiment-laden words in context',
+        'neutral words in context',
+        'used to, but now',
+        'simple negations: not negative',
+        'simple negations: not neutral is still neutral',
+        'Hard: Negation of positive with neutral stuff in the middle (should be negative)',
+        'simple negations: I thought x was negative, but it was not (should be neutral or positive)',
+        'my opinion is what matters',
+        'Q & A: yes',
+        'Q & A: yes (neutral)',
+        'Q & A: no'
+    ]
+
+    OUR_LC_LIST = [
+        'Short sentences with sentiment-laden adjectives',
+        'Short sentences with neutral adjectives and nouns',
+        'Sentiment change over time, present should prevail',
+        'Negated negative should be positive or neutral',
+        'Negated neutral should still be neutral',
+        'Negated positive with neutral content in the middle',
+        'Negation of negative at the end, should be positive or neutral',
+        'Author sentiment is more important than of others',
+        'parsing sentiment in (question, yes) form',
+        'Parsing positive sentiment in (question, no) form',
+        'Parsing negative sentiment in (question, no) form'
+    ]
+
+    LC_MAP = {
+        CHECKLIST_LC_LIST[0]: OUR_LC_LIST[0],
+        CHECKLIST_LC_LIST[1]: OUR_LC_LIST[1],
+        CHECKLIST_LC_LIST[2]: OUR_LC_LIST[2],
+        CHECKLIST_LC_LIST[3]: OUR_LC_LIST[3],
+        CHECKLIST_LC_LIST[4]: OUR_LC_LIST[4],
+        CHECKLIST_LC_LIST[5]: OUR_LC_LIST[5],
+        CHECKLIST_LC_LIST[6]: OUR_LC_LIST[6],
+        CHECKLIST_LC_LIST[7]: OUR_LC_LIST[7],
+        str(CHECKLIST_LC_LIST[8:10]): OUR_LC_LIST[8], # Q & A: yes -> parsing sentiment in (question, yes) form
+        CHECKLIST_LC_LIST[10]: str(OUR_LC_LIST[9:]) # Q & A: no -> parsing positive/negative sentiment in (question, yes) form
+    }

### 2022-03-29 python/sa/utils/SelfBleu.py

@@ -3,14 +3,13 @@ import nltk
 import multiprocessing
 
 from multiprocessing import Pool
-from functools import partial
+# from functools import partial
 from nltk.translate.bleu_score import SmoothingFunction
 
 from .Macros import Macros
 from .Utils import Utils
 
-NUM_PROCESSES_IN_USE=8
-
+NUM_PROCESSES_IN_USE=os.cpu_count()
 
 
 class SelfBleu:
@@ -30,48 +29,50 @@ class SelfBleu:
         self.sample_size = 500
         self.reference = None
         self.is_first = True
-        self.num_data = -1
-
-    def get_score(self):
-        self.get_reference()
-        return self.get_bleu()
+        self.num_data = len(self.texts)
 
     def get_reference(self):
+        reference = list()
         if self.reference is None:
-            reference = list()
+            self.reference = self.texts
             for t in self.texts:
-                text = Utils.tokenize(t)
-                reference.append(t)
+                reference.append(Utils.tokenize(t))
             # end for
             self.reference = reference
-            self.num_data = len(reference)
             return reference
-        else:
-            return self.reference
         # end if
+        return self.reference
 
-    def calc_bleu(self, hyp_i, reference, weight):
+    def calc_bleu(self, reference, hypothesis, weight):
         # print(multiprocessing.current_process())
-        hypothesis = Utils.tokenize(self.texts[hyp_i])
         return nltk.translate.bleu_score.sentence_bleu(
             reference, hypothesis, weight,
             smoothing_function=SmoothingFunction().method1
         )
 
-    def get_bleu(self):
+    def get_score(self, reference=None):
         ngram = self.gram
-        bleu = list()
-        reference = self.get_reference()
+        if reference is None:
+            reference = self.get_reference()
+        # end if
         weight = tuple((1. / ngram for _ in range(ngram)))
-        hypothesis = self.texts
-        pool_obj = Pool(processes=NUM_PROCESSES_IN_USE)
-        mp_calc_bleu = partial(self.calc_bleu,
-                               reference=reference,
-                               weight=weight)
-        scores = pool_obj.map(mp_calc_bleu, range(self.num_data))
-        bleu.extend(scores)
-        return float("{:.3f}".format(sum(bleu) / len(bleu)))
-
+        pool = Pool(processes=NUM_PROCESSES_IN_USE)
+        result = list()
[…]

### 2022-03-29 python/sa/paper/Tables.py
add macros

@@ -181,7 +181,7 @@ class Tables:
         output_file.append(r"\toprule")
 
         # Content
-        output_file.append(r"\tLc & \tOurSelfBleuScore & \tChecklistSelfBleuScore \\")
+        output_file.append(r"\tLc & \tOurNumData & \tOurSelfBleuScore & \tChecklistNumData & \tChecklistSelfBleuScore \\")
         output_file.append(r"\midrule")
 
         selfbleu_file = Macros.selfbleu_result_dir / "{task}_{search_dataset_name}_{selection_method}_testcase_selfbleu.json"

### 2022-03-29 python/sa/utils/SelfBleu.py

@@ -141,7 +141,6 @@ def main(task, search_dataset_name, selection_method):
     _, texts_checklist = read_checklist_testcases()
     scores_baseline = dict()
     for lc in texts_checklist.keys():
-        print(lc)
         sbleu = SelfBleu(texts=texts_checklist[lc])
         scores_baseline[lc] = {
             'num_data': sbleu.num_data,

### 2022-03-29 run_sa.sh
add table make in run_sa

@@ -41,7 +41,7 @@ function eval_models() {
          CUDA_VISIBLE_DEVICES=1,3,5 python -m python.sa.main --run testmodel --test_baseline
 
          # evaluating models on our generated testcases
-         CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection random
+         # CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection random
          # CUDA_VISIBLE_DEVICES=6,7 python -m python.sa.main --run testmodel --syntax_selection bertscore
          # CUDA_VISIBLE_DEVICES=6,7 time python -m python.sa.main --run testmodel --syntax_selection noselect
         )
@@ -51,30 +51,19 @@ function retrain_models() {
         # evaluate NLP models with generated testsuites
         (cd ${_DIR}
          echo "***** TRAIN: ours, EVAL: checklist *****"
-         CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
+         CUDA_VISIBLE_DEVICES=3,5,6,7 python -m python.sa.main \
                              --run retrain \
                              --search_dataset sst \
                              --syntax_selection random \
                              --lcs \
-                             --model_name textattack/bert-base-uncased-SST-2
-         CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
-                             --run retrain \
                              --testing_on_trainset \
-                             --search_dataset sst \
-                             --syntax_selection random \
-                             --lcs \
                              --model_name textattack/bert-base-uncased-SST-2
          echo "***** TRAIN: checklist, EVAL: ours *****"
-         CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
+         CUDA_VISIBLE_DEVICES=3,5,6,7 python -m python.sa.main \
                              --run retrain \
                              --search_dataset checklist \
                              --lcs \
-                             --model_name textattack/bert-base-uncased-SST-2
-         CUDA_VISIBLE_DEVICES=5,6,7 python -m python.sa.main \
-                             --run retrain \
                              --testing_on_trainset \
-                             --search_dataset checklist \
-                             --lcs \
                              --model_name textattack/bert-base-uncased-SST-2
         )
 }
@@ -133,7 +122,8 @@ function selfbleu() {
 function make_tables() {
         (cd ${_DIR}
          # Table 1
-         python -m python.sa.main --run tables --which lc-req
[…]

### 2022-03-29 python/sa/main.py
table debugging

@@ -216,8 +216,13 @@ def run_selfbleu():
 
 def run_make_tables():
     from .paper.Tables import Tables
-    options = args.which
-    Tables.make_tables(options)
+    options = {
+        'which': args.which,
+        'task': args.nlp_task,
+        'search_dataset_name': args.search_dataset,
+        'selection_method': args.syntax_selection
+    }
+    Tables.make_tables(**options)
     return
     
 

### 2022-03-29 python/sa/paper/Tables.py

@@ -32,11 +32,12 @@ class Tables:
     }
 
     @classmethod
-    def make_tables(cls, which):
+    def make_tables(cls, **options):
         paper_dir: Path = Macros.paper_dir
         tables_dir: Path = paper_dir / "tables"
         tables_dir.mkdir(parents=True, exist_ok=True)
-
+        which = options['which']
+        
         if not isinstance(which, list):
             which = [which]
         # end if
@@ -46,8 +47,12 @@ class Tables:
                 cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
                 cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
             elif item == "selfbleu":
-                cls.make_numbers_selfbleu(Macros.result_dir, tables_dir)
-                cls.make_table_selfbleu(Macros.result_dir, tables_dir)
+                task = options['task']
+                search_dataset = options['search_dataset_name']
+                selection_method = options['selection_method']
+                print(task, search_dataset, selection_method)
+                cls.make_numbers_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
+                cls.make_table_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
             else:
                 cls.logger.warning(f"Unknown table {item}")
             # end if
@@ -166,7 +171,7 @@ class Tables:
     @classmethoe
     def make_table_selfbleu(cls,
                             results_dir: Path,
-                            tables_dir: Path
+                            tables_dir: Path,
                             task: str,
                             search_dataset_name: str,
                             selection_method: str):

### 2022-03-29 python/sa/utils/SelfBleu.py

@@ -121,7 +121,7 @@ def read_checklist_testcases():
             else:
                 texts_lcs[test_name] = tsuite.tests[test_name].data
             # end if
-            texts_all.extend(texts_lcs[test_name])
+            texts_all.extend(tsuite.tests[test_name].data)
         # end if
     # end for
     return texts_all, texts_lcs

### 2022-04-04 python/sa/paper/Tables.py
table

@@ -47,17 +47,19 @@ class Tables:
                 cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
                 cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
             elif item == "selfbleu":
-                task = options['task']
-                search_dataset = options['search_dataset_name']
-                selection_method = options['selection_method']
+                task = options.pop('task', 'sa')
+                search_dataset = options.pop('search_dataset_name', 'sst')
+                selection_method = options.pop('selection_method', 'random')
                 cls.make_numbers_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
                 cls.make_table_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
-            elif item == "retrain":
-                task = options['task']
-                search_dataset = options['search_dataset_name']
-                selection_method = options['selection_method']
-                cls.make_numbers_retrain(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
-                cls.make_table_retrain(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
+            elif item == "retrain-debug":
+                task = options.pop('task', 'sa')
+                search_dataset = options.pop('search_dataset_name', 'sst')
+                selection_method = options.pop('selection_method', 'random')
+                epochs = options.pop('epochs', 5)
+                model_name = options.pop('model_name')
+                cls.make_numbers_retrain(Macros.result_dir, tables_dir, task, search_dataset, selection_method, epochs, model_name)
+                cls.make_table_retrain(Macros.result_dir, tables_dir, task, search_dataset, selection_method, epochs, model_name)
             else:
                 cls.logger.warning(f"Unknown table {item}")
             # end if
@@ -224,35 +226,60 @@ class Tables:
                              tables_dir: Path,
                              task: str,
                              search_dataset_name: str,
-                             selection_method: str
-                             epochs: int
[…]

### 2022-04-04 run_sa.sh
add table in run_sa.sh

@@ -123,7 +123,14 @@ function make_tables() {
         (cd ${_DIR}
          # Table 1
          # python -m python.sa.main --run tables --which lc-req
-         python -m python.sa.main --run tables --which selfbleu
+         # python -m python.sa.main --run tables --which selfbleu
+         python -m python.sa.main \
+                --run tables \
+                --which retrain-debug \
+                --search_dataset sst \
+                --syntax_selection random \
+                --epochs 5 \
+                --model_name textattack/bert-base-uncased-SST-2
         )
 }
 
@@ -139,9 +146,9 @@ function main() {
         # retrain_models # to retrain models and test the retrained models on testsuite.run on our and checklist generated testsets
         # eval_retrained_models # to ...?
         # analyze_retrained_models # to generate debug_results.json and debug_comparision file
-        selfbleu # to compute the selfbleu
+        # selfbleu # to compute the selfbleu
         # explain_nlp # to run the explainNLP
-        # make_tables
+        make_tables
 }
 
 # please make sure you actiavte nlptest conda environment

### 2022-04-04 python/sa/main.py
modify main.py

@@ -223,7 +223,9 @@ def run_make_tables():
         'which': args.which,
         'task': args.nlp_task,
         'search_dataset_name': args.search_dataset,
-        'selection_method': args.syntax_selection
+        'selection_method': args.syntax_selection,
+        'epochs': args.epochs,
+        'model_name': args.model_name
     }
     Tables.make_tables(**options)
     return

### 2022-04-04 paper/ase22/tables/retrain-debug-numbers.tex
paper

%% Automatically generated by pyutil.latex

\DefMacro{retrain_debug_approach_0}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_0}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_0}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_0}{0}
\DefMacro{retrain_debug_num_fail_orig_0}{860}
\DefMacro{retrain_debug_num_pass_orig_0}{140}
\DefMacro{retrain_debug_num_fail_retrained_0}{1000}
\DefMacro{retrain_debug_num_pass_retrained_0}{0}
\DefMacro{retrain_debug_approach_1}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_1}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_1}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_1}{0}
\DefMacro{retrain_debug_num_fail_orig_1}{26}
\DefMacro{retrain_debug_num_pass_orig_1}{8632}
\DefMacro{retrain_debug_num_fail_retrained_1}{8658}
\DefMacro{retrain_debug_num_pass_retrained_1}{0}
\DefMacro{retrain_debug_approach_2}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_2}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_2}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_2}{1082}
\DefMacro{retrain_debug_num_fail_orig_2}{1793}
\DefMacro{retrain_debug_num_pass_orig_2}{7411}
\DefMacro{retrain_debug_num_fail_retrained_2}{1203}
\DefMacro{retrain_debug_num_pass_retrained_2}{8001}
\DefMacro{retrain_debug_approach_3}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_3}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_3}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_3}{0}
\DefMacro{retrain_debug_num_fail_orig_3}{3741}
\DefMacro{retrain_debug_num_pass_orig_3}{4787}
\DefMacro{retrain_debug_num_fail_retrained_3}{8528}
\DefMacro{retrain_debug_num_pass_retrained_3}{0}
\DefMacro{retrain_debug_approach_4}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_4}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_4}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_4}{1330}
\DefMacro{retrain_debug_num_fail_orig_4}{1330}
\DefMacro{retrain_debug_num_pass_orig_4}{386}
\DefMacro{retrain_debug_num_fail_retrained_4}{0}
\DefMacro{retrain_debug_num_pass_retrained_4}{1716}
\DefMacro{retrain_debug_approach_5}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_5}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_5}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_5}{2427}
\DefMacro{retrain_debug_num_fail_orig_5}{2427}
\DefMacro{retrain_debug_num_pass_orig_5}{69}
\DefMacro{retrain_debug_num_fail_retrained_5}{0}
\DefMacro{retrain_debug_num_pass_retrained_5}{2496}
\DefMacro{retrain_debug_approach_6}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_6}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_eval_lc_6}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_6}{0}
\DefMacro{retrain_debug_num_fail_orig_6}{1680}
\DefMacro{retrain_debug_num_pass_orig_6}{6320}
\DefMacro{retrain_debug_num_fail_retrained_6}{8000}
\DefMacro{retrain_debug_num_pass_retrained_6}{0}
\DefMacro{retrain_debug_approach_7}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_7}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_7}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_7}{0}
\DefMacro{retrain_debug_num_fail_orig_7}{860}
\DefMacro{retrain_debug_num_pass_orig_7}{140}
\DefMacro{retrain_debug_num_fail_retrained_7}{1000}
\DefMacro{retrain_debug_num_pass_retrained_7}{0}
\DefMacro{retrain_debug_approach_8}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_8}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_8}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_8}{0}
\DefMacro{retrain_debug_num_fail_orig_8}{26}
\DefMacro{retrain_debug_num_pass_orig_8}{8632}
\DefMacro{retrain_debug_num_fail_retrained_8}{8658}
\DefMacro{retrain_debug_num_pass_retrained_8}{0}
\DefMacro{retrain_debug_approach_9}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_9}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_9}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_9}{1540}
\DefMacro{retrain_debug_num_fail_orig_9}{1793}
\DefMacro{retrain_debug_num_pass_orig_9}{7411}
\DefMacro{retrain_debug_num_fail_retrained_9}{7644}
\DefMacro{retrain_debug_num_pass_retrained_9}{1560}
\DefMacro{retrain_debug_approach_10}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_10}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_10}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_10}{0}
\DefMacro{retrain_debug_num_fail_orig_10}{3741}
\DefMacro{retrain_debug_num_pass_orig_10}{4787}
\DefMacro{retrain_debug_num_fail_retrained_10}{8528}
\DefMacro{retrain_debug_num_pass_retrained_10}{0}
\DefMacro{retrain_debug_approach_11}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_11}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_11}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_11}{1330}
\DefMacro{retrain_debug_num_fail_orig_11}{1330}
\DefMacro{retrain_debug_num_pass_orig_11}{386}
\DefMacro{retrain_debug_num_fail_retrained_11}{0}
\DefMacro{retrain_debug_num_pass_retrained_11}{1716}
\DefMacro{retrain_debug_approach_12}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_12}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_12}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_12}{2427}
\DefMacro{retrain_debug_num_fail_orig_12}{2427}
\DefMacro{retrain_debug_num_pass_orig_12}{69}
\DefMacro{retrain_debug_num_fail_retrained_12}{0}
\DefMacro{retrain_debug_num_pass_retrained_12}{2496}
\DefMacro{retrain_debug_approach_13}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_13}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_eval_lc_13}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_13}{0}
\DefMacro{retrain_debug_num_fail_orig_13}{1680}
\DefMacro{retrain_debug_num_pass_orig_13}{6320}
\DefMacro{retrain_debug_num_fail_retrained_13}{8000}
\DefMacro{retrain_debug_num_pass_retrained_13}{0}
\DefMacro{retrain_debug_approach_14}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_14}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_14}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_14}{0}
\DefMacro{retrain_debug_num_fail_orig_14}{860}
\DefMacro{retrain_debug_num_pass_orig_14}{140}
\DefMacro{retrain_debug_num_fail_retrained_14}{1000}
\DefMacro{retrain_debug_num_pass_retrained_14}{0}
\DefMacro{retrain_debug_approach_15}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_15}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_15}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_15}{0}
\DefMacro{retrain_debug_num_fail_orig_15}{26}
\DefMacro{retrain_debug_num_pass_orig_15}{8632}
\DefMacro{retrain_debug_num_fail_retrained_15}{8658}
\DefMacro{retrain_debug_num_pass_retrained_15}{0}
\DefMacro{retrain_debug_approach_16}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_16}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_16}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_16}{1540}
\DefMacro{retrain_debug_num_fail_orig_16}{1793}
\DefMacro{retrain_debug_num_pass_orig_16}{7411}
\DefMacro{retrain_debug_num_fail_retrained_16}{7644}
\DefMacro{retrain_debug_num_pass_retrained_16}{1560}
\DefMacro{retrain_debug_approach_17}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_17}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_17}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_17}{0}
\DefMacro{retrain_debug_num_fail_orig_17}{3741}
\DefMacro{retrain_debug_num_pass_orig_17}{4787}
\DefMacro{retrain_debug_num_fail_retrained_17}{8528}
\DefMacro{retrain_debug_num_pass_retrained_17}{0}
\DefMacro{retrain_debug_approach_18}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_18}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_18}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_18}{1330}
\DefMacro{retrain_debug_num_fail_orig_18}{1330}
\DefMacro{retrain_debug_num_pass_orig_18}{386}
\DefMacro{retrain_debug_num_fail_retrained_18}{0}
\DefMacro{retrain_debug_num_pass_retrained_18}{1716}
\DefMacro{retrain_debug_approach_19}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_19}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_19}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_19}{2427}
\DefMacro{retrain_debug_num_fail_orig_19}{2427}
\DefMacro{retrain_debug_num_pass_orig_19}{69}
\DefMacro{retrain_debug_num_fail_retrained_19}{0}
\DefMacro{retrain_debug_num_pass_retrained_19}{2496}
\DefMacro{retrain_debug_approach_20}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_20}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_eval_lc_20}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_20}{0}
\DefMacro{retrain_debug_num_fail_orig_20}{1680}
\DefMacro{retrain_debug_num_pass_orig_20}{6320}
\DefMacro{retrain_debug_num_fail_retrained_20}{8000}
\DefMacro{retrain_debug_num_pass_retrained_20}{0}
\DefMacro{retrain_debug_approach_21}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_21}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_21}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_21}{0}
\DefMacro{retrain_debug_num_fail_orig_21}{860}
\DefMacro{retrain_debug_num_pass_orig_21}{140}
\DefMacro{retrain_debug_num_fail_retrained_21}{1000}
\DefMacro{retrain_debug_num_pass_retrained_21}{0}
\DefMacro{retrain_debug_approach_22}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_22}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_22}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_22}{0}
\DefMacro{retrain_debug_num_fail_orig_22}{26}
\DefMacro{retrain_debug_num_pass_orig_22}{8632}
\DefMacro{retrain_debug_num_fail_retrained_22}{8658}
\DefMacro{retrain_debug_num_pass_retrained_22}{0}
\DefMacro{retrain_debug_approach_23}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_23}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_23}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_23}{1540}
\DefMacro{retrain_debug_num_fail_orig_23}{1793}
\DefMacro{retrain_debug_num_pass_orig_23}{7411}
\DefMacro{retrain_debug_num_fail_retrained_23}{7644}
\DefMacro{retrain_debug_num_pass_retrained_23}{1560}
\DefMacro{retrain_debug_approach_24}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_24}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_24}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_24}{0}
\DefMacro{retrain_debug_num_fail_orig_24}{3741}
\DefMacro{retrain_debug_num_pass_orig_24}{4787}
\DefMacro{retrain_debug_num_fail_retrained_24}{8528}
\DefMacro{retrain_debug_num_pass_retrained_24}{0}
\DefMacro{retrain_debug_approach_25}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_25}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_25}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_25}{1330}
\DefMacro{retrain_debug_num_fail_orig_25}{1330}
\DefMacro{retrain_debug_num_pass_orig_25}{386}
\DefMacro{retrain_debug_num_fail_retrained_25}{0}
\DefMacro{retrain_debug_num_pass_retrained_25}{1716}
\DefMacro{retrain_debug_approach_26}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_26}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_26}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_26}{2427}
\DefMacro{retrain_debug_num_fail_orig_26}{2427}
\DefMacro{retrain_debug_num_pass_orig_26}{69}
\DefMacro{retrain_debug_num_fail_retrained_26}{0}
\DefMacro{retrain_debug_num_pass_retrained_26}{2496}
\DefMacro{retrain_debug_approach_27}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_27}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_eval_lc_27}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_27}{0}
\DefMacro{retrain_debug_num_fail_orig_27}{1680}
\DefMacro{retrain_debug_num_pass_orig_27}{6320}
\DefMacro{retrain_debug_num_fail_retrained_27}{7888}
\DefMacro{retrain_debug_num_pass_retrained_27}{112}
\DefMacro{retrain_debug_approach_28}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_28}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_28}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_28}{840}
\DefMacro{retrain_debug_num_fail_orig_28}{860}
\DefMacro{retrain_debug_num_pass_orig_28}{140}
\DefMacro{retrain_debug_num_fail_retrained_28}{20}
\DefMacro{retrain_debug_num_pass_retrained_28}{980}
\DefMacro{retrain_debug_approach_29}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_29}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_29}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_29}{0}
\DefMacro{retrain_debug_num_fail_orig_29}{26}
\DefMacro{retrain_debug_num_pass_orig_29}{8632}
\DefMacro{retrain_debug_num_fail_retrained_29}{8658}
\DefMacro{retrain_debug_num_pass_retrained_29}{0}
\DefMacro{retrain_debug_approach_30}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_30}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_30}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_30}{1540}
\DefMacro{retrain_debug_num_fail_orig_30}{1793}
\DefMacro{retrain_debug_num_pass_orig_30}{7411}
\DefMacro{retrain_debug_num_fail_retrained_30}{7644}
\DefMacro{retrain_debug_num_pass_retrained_30}{1560}
\DefMacro{retrain_debug_approach_31}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_31}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_31}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_31}{0}
\DefMacro{retrain_debug_num_fail_orig_31}{3741}
\DefMacro{retrain_debug_num_pass_orig_31}{4787}
\DefMacro{retrain_debug_num_fail_retrained_31}{8528}
\DefMacro{retrain_debug_num_pass_retrained_31}{0}
\DefMacro{retrain_debug_approach_32}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_32}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_32}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_32}{1330}
\DefMacro{retrain_debug_num_fail_orig_32}{1330}
\DefMacro{retrain_debug_num_pass_orig_32}{386}
\DefMacro{retrain_debug_num_fail_retrained_32}{0}
\DefMacro{retrain_debug_num_pass_retrained_32}{1716}
\DefMacro{retrain_debug_approach_33}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_33}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_33}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_33}{2427}
\DefMacro{retrain_debug_num_fail_orig_33}{2427}
\DefMacro{retrain_debug_num_pass_orig_33}{69}
\DefMacro{retrain_debug_num_fail_retrained_33}{0}
\DefMacro{retrain_debug_num_pass_retrained_33}{2496}
\DefMacro{retrain_debug_approach_34}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_34}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_eval_lc_34}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_34}{0}
\DefMacro{retrain_debug_num_fail_orig_34}{1680}
\DefMacro{retrain_debug_num_pass_orig_34}{6320}
\DefMacro{retrain_debug_num_fail_retrained_34}{8000}
\DefMacro{retrain_debug_num_pass_retrained_34}{0}
\DefMacro{retrain_debug_approach_35}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_35}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_35}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_35}{0}
\DefMacro{retrain_debug_num_fail_orig_35}{860}
\DefMacro{retrain_debug_num_pass_orig_35}{140}
\DefMacro{retrain_debug_num_fail_retrained_35}{1000}
\DefMacro{retrain_debug_num_pass_retrained_35}{0}
\DefMacro{retrain_debug_approach_36}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_36}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_36}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_36}{0}
\DefMacro{retrain_debug_num_fail_orig_36}{26}
\DefMacro{retrain_debug_num_pass_orig_36}{8632}
\DefMacro{retrain_debug_num_fail_retrained_36}{8658}
\DefMacro{retrain_debug_num_pass_retrained_36}{0}
\DefMacro{retrain_debug_approach_37}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_37}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_37}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_37}{1540}
\DefMacro{retrain_debug_num_fail_orig_37}{1793}
\DefMacro{retrain_debug_num_pass_orig_37}{7411}
\DefMacro{retrain_debug_num_fail_retrained_37}{7644}
\DefMacro{retrain_debug_num_pass_retrained_37}{1560}
\DefMacro{retrain_debug_approach_38}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_38}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_38}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_38}{0}
\DefMacro{retrain_debug_num_fail_orig_38}{3741}
\DefMacro{retrain_debug_num_pass_orig_38}{4787}
\DefMacro{retrain_debug_num_fail_retrained_38}{8528}
\DefMacro{retrain_debug_num_pass_retrained_38}{0}
\DefMacro{retrain_debug_approach_39}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_39}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_39}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_39}{1330}
\DefMacro{retrain_debug_num_fail_orig_39}{1330}
\DefMacro{retrain_debug_num_pass_orig_39}{386}
\DefMacro{retrain_debug_num_fail_retrained_39}{0}
\DefMacro{retrain_debug_num_pass_retrained_39}{1716}
\DefMacro{retrain_debug_approach_40}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_40}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_40}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_40}{2427}
\DefMacro{retrain_debug_num_fail_orig_40}{2427}
\DefMacro{retrain_debug_num_pass_orig_40}{69}
\DefMacro{retrain_debug_num_fail_retrained_40}{0}
\DefMacro{retrain_debug_num_pass_retrained_40}{2496}
\DefMacro{retrain_debug_approach_41}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_41}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_eval_lc_41}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_41}{0}
\DefMacro{retrain_debug_num_fail_orig_41}{1680}
\DefMacro{retrain_debug_num_pass_orig_41}{6320}
\DefMacro{retrain_debug_num_fail_retrained_41}{8000}
\DefMacro{retrain_debug_num_pass_retrained_41}{0}
\DefMacro{retrain_debug_approach_42}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_42}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_42}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_42}{0}
\DefMacro{retrain_debug_num_fail_orig_42}{860}
\DefMacro{retrain_debug_num_pass_orig_42}{140}
\DefMacro{retrain_debug_num_fail_retrained_42}{1000}
\DefMacro{retrain_debug_num_pass_retrained_42}{0}
\DefMacro{retrain_debug_approach_43}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_43}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_43}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_43}{0}
\DefMacro{retrain_debug_num_fail_orig_43}{26}
\DefMacro{retrain_debug_num_pass_orig_43}{8632}
\DefMacro{retrain_debug_num_fail_retrained_43}{8658}
\DefMacro{retrain_debug_num_pass_retrained_43}{0}
\DefMacro{retrain_debug_approach_44}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_44}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_44}{parsing sentiment in (question, yes) form}
\DefMacro{retrain_debug_num_fail2pass_44}{1540}
\DefMacro{retrain_debug_num_fail_orig_44}{1793}
\DefMacro{retrain_debug_num_pass_orig_44}{7411}
\DefMacro{retrain_debug_num_fail_retrained_44}{7644}
\DefMacro{retrain_debug_num_pass_retrained_44}{1560}
\DefMacro{retrain_debug_approach_45}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_45}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_45}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_45}{0}
\DefMacro{retrain_debug_num_fail_orig_45}{3741}
\DefMacro{retrain_debug_num_pass_orig_45}{4787}
\DefMacro{retrain_debug_num_fail_retrained_45}{8528}
\DefMacro{retrain_debug_num_pass_retrained_45}{0}
\DefMacro{retrain_debug_approach_46}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_46}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_46}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_46}{1330}
\DefMacro{retrain_debug_num_fail_orig_46}{1330}
\DefMacro{retrain_debug_num_pass_orig_46}{386}
\DefMacro{retrain_debug_num_fail_retrained_46}{0}
\DefMacro{retrain_debug_num_pass_retrained_46}{1716}
\DefMacro{retrain_debug_approach_47}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_47}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_47}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_47}{2427}
\DefMacro{retrain_debug_num_fail_orig_47}{2427}
\DefMacro{retrain_debug_num_pass_orig_47}{69}
\DefMacro{retrain_debug_num_fail_retrained_47}{0}
\DefMacro{retrain_debug_num_pass_retrained_47}{2496}
\DefMacro{retrain_debug_approach_48}{Retrain:Ours::Test:Checklist}
\DefMacro{retrain_debug_retrained_lc_48}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_eval_lc_48}{Sentiment change over time, present should prevail}
\DefMacro{retrain_debug_num_fail2pass_48}{0}
\DefMacro{retrain_debug_num_fail_orig_48}{1680}
\DefMacro{retrain_debug_num_pass_orig_48}{6320}
\DefMacro{retrain_debug_num_fail_retrained_48}{8000}
\DefMacro{retrain_debug_num_pass_retrained_48}{0}
\DefMacro{retrain_debug_approach_50}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_50}{used to  but now}
\DefMacro{retrain_debug_eval_lc_50}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_50}{0}
\DefMacro{retrain_debug_num_fail_orig_50}{1185}
\DefMacro{retrain_debug_num_pass_orig_50}{1188}
\DefMacro{retrain_debug_num_fail_retrained_50}{2373}
\DefMacro{retrain_debug_num_pass_retrained_50}{0}
\DefMacro{retrain_debug_approach_51}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_51}{used to  but now}
\DefMacro{retrain_debug_eval_lc_51}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_51}{956}
\DefMacro{retrain_debug_num_fail_orig_51}{956}
\DefMacro{retrain_debug_num_pass_orig_51}{79}
\DefMacro{retrain_debug_num_fail_retrained_51}{0}
\DefMacro{retrain_debug_num_pass_retrained_51}{1035}
\DefMacro{retrain_debug_approach_52}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_52}{used to  but now}
\DefMacro{retrain_debug_eval_lc_52}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_52}{0}
\DefMacro{retrain_debug_num_fail_orig_52}{1480}
\DefMacro{retrain_debug_num_pass_orig_52}{204}
\DefMacro{retrain_debug_num_fail_retrained_52}{1684}
\DefMacro{retrain_debug_num_pass_retrained_52}{0}
\DefMacro{retrain_debug_approach_53}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_53}{used to  but now}
\DefMacro{retrain_debug_eval_lc_53}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_53}{4}
\DefMacro{retrain_debug_num_fail_orig_53}{12}
\DefMacro{retrain_debug_num_pass_orig_53}{38}
\DefMacro{retrain_debug_num_fail_retrained_53}{34}
\DefMacro{retrain_debug_num_pass_retrained_53}{16}
\DefMacro{retrain_debug_approach_54}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_54}{used to  but now}
\DefMacro{retrain_debug_eval_lc_54}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_54}{197}
\DefMacro{retrain_debug_num_fail_orig_54}{197}
\DefMacro{retrain_debug_num_pass_orig_54}{32}
\DefMacro{retrain_debug_num_fail_retrained_54}{0}
\DefMacro{retrain_debug_num_pass_retrained_54}{229}
\DefMacro{retrain_debug_approach_55}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_55}{used to  but now}
\DefMacro{retrain_debug_eval_lc_55}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_55}{0}
\DefMacro{retrain_debug_num_fail_orig_55}{19}
\DefMacro{retrain_debug_num_pass_orig_55}{425}
\DefMacro{retrain_debug_num_fail_retrained_55}{444}
\DefMacro{retrain_debug_num_pass_retrained_55}{0}
\DefMacro{retrain_debug_approach_56}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_56}{used to  but now}
\DefMacro{retrain_debug_eval_lc_56}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_56}{0}
\DefMacro{retrain_debug_num_fail_orig_56}{39}
\DefMacro{retrain_debug_num_pass_orig_56}{1384}
\DefMacro{retrain_debug_num_fail_retrained_56}{1423}
\DefMacro{retrain_debug_num_pass_retrained_56}{0}
\DefMacro{retrain_debug_approach_57}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_57}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_57}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_57}{0}
\DefMacro{retrain_debug_num_fail_orig_57}{1185}
\DefMacro{retrain_debug_num_pass_orig_57}{1188}
\DefMacro{retrain_debug_num_fail_retrained_57}{2373}
\DefMacro{retrain_debug_num_pass_retrained_57}{0}
\DefMacro{retrain_debug_approach_58}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_58}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_58}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_58}{956}
\DefMacro{retrain_debug_num_fail_orig_58}{956}
\DefMacro{retrain_debug_num_pass_orig_58}{79}
\DefMacro{retrain_debug_num_fail_retrained_58}{0}
\DefMacro{retrain_debug_num_pass_retrained_58}{1035}
\DefMacro{retrain_debug_approach_59}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_59}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_59}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_59}{0}
\DefMacro{retrain_debug_num_fail_orig_59}{1480}
\DefMacro{retrain_debug_num_pass_orig_59}{204}
\DefMacro{retrain_debug_num_fail_retrained_59}{1684}
\DefMacro{retrain_debug_num_pass_retrained_59}{0}
\DefMacro{retrain_debug_approach_60}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_60}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_60}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_60}{0}
\DefMacro{retrain_debug_num_fail_orig_60}{12}
\DefMacro{retrain_debug_num_pass_orig_60}{38}
\DefMacro{retrain_debug_num_fail_retrained_60}{50}
\DefMacro{retrain_debug_num_pass_retrained_60}{0}
\DefMacro{retrain_debug_approach_61}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_61}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_61}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_61}{197}
\DefMacro{retrain_debug_num_fail_orig_61}{197}
\DefMacro{retrain_debug_num_pass_orig_61}{32}
\DefMacro{retrain_debug_num_fail_retrained_61}{0}
\DefMacro{retrain_debug_num_pass_retrained_61}{229}
\DefMacro{retrain_debug_approach_62}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_62}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_62}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_62}{0}
\DefMacro{retrain_debug_num_fail_orig_62}{19}
\DefMacro{retrain_debug_num_pass_orig_62}{425}
\DefMacro{retrain_debug_num_fail_retrained_62}{444}
\DefMacro{retrain_debug_num_pass_retrained_62}{0}
\DefMacro{retrain_debug_approach_63}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_63}{simple negations: not neutral is still neutral}
\DefMacro{retrain_debug_eval_lc_63}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_63}{0}
\DefMacro{retrain_debug_num_fail_orig_63}{39}
\DefMacro{retrain_debug_num_pass_orig_63}{1384}
\DefMacro{retrain_debug_num_fail_retrained_63}{1423}
\DefMacro{retrain_debug_num_pass_retrained_63}{0}
\DefMacro{retrain_debug_approach_64}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_64}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_64}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_64}{0}
\DefMacro{retrain_debug_num_fail_orig_64}{1185}
\DefMacro{retrain_debug_num_pass_orig_64}{1188}
\DefMacro{retrain_debug_num_fail_retrained_64}{2373}
\DefMacro{retrain_debug_num_pass_retrained_64}{0}
\DefMacro{retrain_debug_approach_65}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_65}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_65}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_65}{956}
\DefMacro{retrain_debug_num_fail_orig_65}{956}
\DefMacro{retrain_debug_num_pass_orig_65}{79}
\DefMacro{retrain_debug_num_fail_retrained_65}{0}
\DefMacro{retrain_debug_num_pass_retrained_65}{1035}
\DefMacro{retrain_debug_approach_66}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_66}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_66}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_66}{0}
\DefMacro{retrain_debug_num_fail_orig_66}{1480}
\DefMacro{retrain_debug_num_pass_orig_66}{204}
\DefMacro{retrain_debug_num_fail_retrained_66}{1684}
\DefMacro{retrain_debug_num_pass_retrained_66}{0}
\DefMacro{retrain_debug_approach_67}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_67}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_67}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_67}{0}
\DefMacro{retrain_debug_num_fail_orig_67}{12}
\DefMacro{retrain_debug_num_pass_orig_67}{38}
\DefMacro{retrain_debug_num_fail_retrained_67}{50}
\DefMacro{retrain_debug_num_pass_retrained_67}{0}
\DefMacro{retrain_debug_approach_68}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_68}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_68}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_68}{197}
\DefMacro{retrain_debug_num_fail_orig_68}{197}
\DefMacro{retrain_debug_num_pass_orig_68}{32}
\DefMacro{retrain_debug_num_fail_retrained_68}{0}
\DefMacro{retrain_debug_num_pass_retrained_68}{229}
\DefMacro{retrain_debug_approach_69}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_69}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_69}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_69}{0}
\DefMacro{retrain_debug_num_fail_orig_69}{19}
\DefMacro{retrain_debug_num_pass_orig_69}{425}
\DefMacro{retrain_debug_num_fail_retrained_69}{444}
\DefMacro{retrain_debug_num_pass_retrained_69}{0}
\DefMacro{retrain_debug_approach_70}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_70}{neutral words in context}
\DefMacro{retrain_debug_eval_lc_70}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_70}{0}
\DefMacro{retrain_debug_num_fail_orig_70}{39}
\DefMacro{retrain_debug_num_pass_orig_70}{1384}
\DefMacro{retrain_debug_num_fail_retrained_70}{1423}
\DefMacro{retrain_debug_num_pass_retrained_70}{0}
\DefMacro{retrain_debug_approach_71}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_71}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_71}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_71}{0}
\DefMacro{retrain_debug_num_fail_orig_71}{1185}
\DefMacro{retrain_debug_num_pass_orig_71}{1188}
\DefMacro{retrain_debug_num_fail_retrained_71}{2373}
\DefMacro{retrain_debug_num_pass_retrained_71}{0}
\DefMacro{retrain_debug_approach_72}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_72}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_72}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_72}{956}
\DefMacro{retrain_debug_num_fail_orig_72}{956}
\DefMacro{retrain_debug_num_pass_orig_72}{79}
\DefMacro{retrain_debug_num_fail_retrained_72}{0}
\DefMacro{retrain_debug_num_pass_retrained_72}{1035}
\DefMacro{retrain_debug_approach_73}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_73}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_73}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_73}{0}
\DefMacro{retrain_debug_num_fail_orig_73}{1480}
\DefMacro{retrain_debug_num_pass_orig_73}{204}
\DefMacro{retrain_debug_num_fail_retrained_73}{1684}
\DefMacro{retrain_debug_num_pass_retrained_73}{0}
\DefMacro{retrain_debug_approach_74}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_74}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_74}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_74}{0}
\DefMacro{retrain_debug_num_fail_orig_74}{12}
\DefMacro{retrain_debug_num_pass_orig_74}{38}
\DefMacro{retrain_debug_num_fail_retrained_74}{50}
\DefMacro{retrain_debug_num_pass_retrained_74}{0}
\DefMacro{retrain_debug_approach_75}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_75}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_75}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_75}{197}
\DefMacro{retrain_debug_num_fail_orig_75}{197}
\DefMacro{retrain_debug_num_pass_orig_75}{32}
\DefMacro{retrain_debug_num_fail_retrained_75}{0}
\DefMacro{retrain_debug_num_pass_retrained_75}{229}
\DefMacro{retrain_debug_approach_76}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_76}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_76}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_76}{0}
\DefMacro{retrain_debug_num_fail_orig_76}{19}
\DefMacro{retrain_debug_num_pass_orig_76}{425}
\DefMacro{retrain_debug_num_fail_retrained_76}{444}
\DefMacro{retrain_debug_num_pass_retrained_76}{0}
\DefMacro{retrain_debug_approach_77}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_77}{my opinion is what matters}
\DefMacro{retrain_debug_eval_lc_77}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_77}{0}
\DefMacro{retrain_debug_num_fail_orig_77}{39}
\DefMacro{retrain_debug_num_pass_orig_77}{1384}
\DefMacro{retrain_debug_num_fail_retrained_77}{1423}
\DefMacro{retrain_debug_num_pass_retrained_77}{0}
\DefMacro{retrain_debug_approach_78}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_78}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_78}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_78}{0}
\DefMacro{retrain_debug_num_fail_orig_78}{1185}
\DefMacro{retrain_debug_num_pass_orig_78}{1188}
\DefMacro{retrain_debug_num_fail_retrained_78}{2373}
\DefMacro{retrain_debug_num_pass_retrained_78}{0}
\DefMacro{retrain_debug_approach_79}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_79}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_79}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_79}{956}
\DefMacro{retrain_debug_num_fail_orig_79}{956}
\DefMacro{retrain_debug_num_pass_orig_79}{79}
\DefMacro{retrain_debug_num_fail_retrained_79}{0}
\DefMacro{retrain_debug_num_pass_retrained_79}{1035}
\DefMacro{retrain_debug_approach_80}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_80}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_80}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_80}{0}
\DefMacro{retrain_debug_num_fail_orig_80}{1480}
\DefMacro{retrain_debug_num_pass_orig_80}{204}
\DefMacro{retrain_debug_num_fail_retrained_80}{1684}
\DefMacro{retrain_debug_num_pass_retrained_80}{0}
\DefMacro{retrain_debug_approach_81}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_81}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_81}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_81}{0}
\DefMacro{retrain_debug_num_fail_orig_81}{12}
\DefMacro{retrain_debug_num_pass_orig_81}{38}
\DefMacro{retrain_debug_num_fail_retrained_81}{50}
\DefMacro{retrain_debug_num_pass_retrained_81}{0}
\DefMacro{retrain_debug_approach_82}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_82}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_82}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_82}{197}
\DefMacro{retrain_debug_num_fail_orig_82}{197}
\DefMacro{retrain_debug_num_pass_orig_82}{32}
\DefMacro{retrain_debug_num_fail_retrained_82}{0}
\DefMacro{retrain_debug_num_pass_retrained_82}{229}
\DefMacro{retrain_debug_approach_83}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_83}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_83}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_83}{0}
\DefMacro{retrain_debug_num_fail_orig_83}{19}
\DefMacro{retrain_debug_num_pass_orig_83}{425}
\DefMacro{retrain_debug_num_fail_retrained_83}{444}
\DefMacro{retrain_debug_num_pass_retrained_83}{0}
\DefMacro{retrain_debug_approach_84}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_84}{Sentiment-laden words in context}
\DefMacro{retrain_debug_eval_lc_84}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_84}{0}
\DefMacro{retrain_debug_num_fail_orig_84}{39}
\DefMacro{retrain_debug_num_pass_orig_84}{1384}
\DefMacro{retrain_debug_num_fail_retrained_84}{1423}
\DefMacro{retrain_debug_num_pass_retrained_84}{0}
\DefMacro{retrain_debug_approach_85}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_85}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_85}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_85}{0}
\DefMacro{retrain_debug_num_fail_orig_85}{1185}
\DefMacro{retrain_debug_num_pass_orig_85}{1188}
\DefMacro{retrain_debug_num_fail_retrained_85}{2373}
\DefMacro{retrain_debug_num_pass_retrained_85}{0}
\DefMacro{retrain_debug_approach_86}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_86}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_86}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_86}{956}
\DefMacro{retrain_debug_num_fail_orig_86}{956}
\DefMacro{retrain_debug_num_pass_orig_86}{79}
\DefMacro{retrain_debug_num_fail_retrained_86}{0}
\DefMacro{retrain_debug_num_pass_retrained_86}{1035}
\DefMacro{retrain_debug_approach_87}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_87}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_87}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_87}{3}
\DefMacro{retrain_debug_num_fail_orig_87}{1480}
\DefMacro{retrain_debug_num_pass_orig_87}{204}
\DefMacro{retrain_debug_num_fail_retrained_87}{1673}
\DefMacro{retrain_debug_num_pass_retrained_87}{11}
\DefMacro{retrain_debug_approach_88}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_88}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_88}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_88}{0}
\DefMacro{retrain_debug_num_fail_orig_88}{12}
\DefMacro{retrain_debug_num_pass_orig_88}{38}
\DefMacro{retrain_debug_num_fail_retrained_88}{50}
\DefMacro{retrain_debug_num_pass_retrained_88}{0}
\DefMacro{retrain_debug_approach_89}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_89}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_89}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_89}{197}
\DefMacro{retrain_debug_num_fail_orig_89}{197}
\DefMacro{retrain_debug_num_pass_orig_89}{32}
\DefMacro{retrain_debug_num_fail_retrained_89}{0}
\DefMacro{retrain_debug_num_pass_retrained_89}{229}
\DefMacro{retrain_debug_approach_90}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_90}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_90}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_90}{0}
\DefMacro{retrain_debug_num_fail_orig_90}{19}
\DefMacro{retrain_debug_num_pass_orig_90}{425}
\DefMacro{retrain_debug_num_fail_retrained_90}{444}
\DefMacro{retrain_debug_num_pass_retrained_90}{0}
\DefMacro{retrain_debug_approach_91}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_91}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
\DefMacro{retrain_debug_eval_lc_91}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_91}{0}
\DefMacro{retrain_debug_num_fail_orig_91}{39}
\DefMacro{retrain_debug_num_pass_orig_91}{1384}
\DefMacro{retrain_debug_num_fail_retrained_91}{1423}
\DefMacro{retrain_debug_num_pass_retrained_91}{0}
\DefMacro{retrain_debug_approach_92}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_92}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_92}{Author sentiment is more important than of others}
\DefMacro{retrain_debug_num_fail2pass_92}{0}
\DefMacro{retrain_debug_num_fail_orig_92}{1185}
\DefMacro{retrain_debug_num_pass_orig_92}{1188}
\DefMacro{retrain_debug_num_fail_retrained_92}{2373}
\DefMacro{retrain_debug_num_pass_retrained_92}{0}
\DefMacro{retrain_debug_approach_93}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_93}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_93}{Negated neutral should still be neutral}
\DefMacro{retrain_debug_num_fail2pass_93}{956}
\DefMacro{retrain_debug_num_fail_orig_93}{956}
\DefMacro{retrain_debug_num_pass_orig_93}{79}
\DefMacro{retrain_debug_num_fail_retrained_93}{0}
\DefMacro{retrain_debug_num_pass_retrained_93}{1035}
\DefMacro{retrain_debug_approach_94}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_94}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_94}{Negated positive with neutral content in the middle}
\DefMacro{retrain_debug_num_fail2pass_94}{0}
\DefMacro{retrain_debug_num_fail_orig_94}{1480}
\DefMacro{retrain_debug_num_pass_orig_94}{204}
\DefMacro{retrain_debug_num_fail_retrained_94}{1684}
\DefMacro{retrain_debug_num_pass_retrained_94}{0}
\DefMacro{retrain_debug_approach_95}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_95}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_95}{Sentiment change over time  present should prevail}
\DefMacro{retrain_debug_num_fail2pass_95}{0}
\DefMacro{retrain_debug_num_fail_orig_95}{12}
\DefMacro{retrain_debug_num_pass_orig_95}{38}
\DefMacro{retrain_debug_num_fail_retrained_95}{50}
\DefMacro{retrain_debug_num_pass_retrained_95}{0}
\DefMacro{retrain_debug_approach_96}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_96}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_96}{Short sentences with neutral adjectives and nouns}
\DefMacro{retrain_debug_num_fail2pass_96}{197}
\DefMacro{retrain_debug_num_fail_orig_96}{197}
\DefMacro{retrain_debug_num_pass_orig_96}{32}
\DefMacro{retrain_debug_num_fail_retrained_96}{0}
\DefMacro{retrain_debug_num_pass_retrained_96}{229}
\DefMacro{retrain_debug_approach_97}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_97}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_97}{Short sentences with sentiment-laden adjectives}
\DefMacro{retrain_debug_num_fail2pass_97}{0}
\DefMacro{retrain_debug_num_fail_orig_97}{19}
\DefMacro{retrain_debug_num_pass_orig_97}{425}
\DefMacro{retrain_debug_num_fail_retrained_97}{444}
\DefMacro{retrain_debug_num_pass_retrained_97}{0}
\DefMacro{retrain_debug_approach_98}{Retrain:Checklist::Test:Ours}
\DefMacro{retrain_debug_retrained_lc_98}{['Q & A: yes'  'Q & A: yes (neutral)']}
\DefMacro{retrain_debug_eval_lc_98}{parsing sentiment in (question  yes) form}
\DefMacro{retrain_debug_num_fail2pass_98}{2}
\DefMacro{retrain_debug_num_fail_orig_98}{39}
\DefMacro{retrain_debug_num_pass_orig_98}{1384}
\DefMacro{retrain_debug_num_fail_retrained_98}{1240}
\DefMacro{retrain_debug_num_pass_retrained_98}{183}

### 2022-04-04 python/sa/paper/Tables.py
retrain-debug table not complete yet

@@ -272,7 +272,7 @@ class Tables:
             elif l_i>empty_l_i:
                 for att_i, att_val in enumerate(l):
                     att = attributes[att_i].strip()
-                    if att=='retrain_lc':
+                    if att=='retrained_lc':
                         _att_val = CH_TO_OUR_MAP[att_val]
                         output_file.append_macro(latex.Macro(f"retrain_debug_{att}_{l_i}", _att_val))
                     else:
@@ -304,7 +304,7 @@ class Tables:
         output_file.append(r"\begin{small}")
         output_file.append(r"\begin{center}")
         output_file.append(r"\caption{\RetrainDebugTableCaption}")
-        output_file.append(r"\begin{tabular}{p{3cm}||p{5cm}||p{5cm}||p{2cm}||p{2cm}||p{2cm}||p{2cm}||p{2cm}}")
+        output_file.append(r"\begin{tabular}{p{2cm}|p{2cm}|p{2cm}|c|c|c|c|c}")
         output_file.append(r"\toprule")
 
         # Content
@@ -318,14 +318,17 @@ class Tables:
                 for att_i, att_val in enumerate(l):
                     att = attributes[att_i].strip()
                     if att_i==0:
-                        output_file.append(latex.Macro(f"retrain_debug_{att}_{l_i}").use())
-                        # elif att_i==1 or att_i==2:
-                        #     output_file.append("\multirow{2}{*}{\parbox{5cm}{" + latex.Macro(f"retrain_debug_{att}_{l_i}").use() + "}}")
+                        output_file.append("\multirow{2}{*}{\parbox{2cm}{" + \
+                                           latex.Macro(f"retrain_debug_{att}_{l_i}").use()+ "}}")
+                    elif att_i in [1,2]:
+                        output_file.append(" & \multirow{2}{*}{\parbox{2cm}{" + \
+                                           latex.Macro(f"retrain_debug_{att}_{l_i}").use() + "}}")
                     else:
                         output_file.append(" & " + latex.Macro(f"retrain_debug_{att}_{l_i}").use())
                     # end if
                 # end for
                 output_file.append(r"\\")
+                output_file.append(r"& & & & & \\")
                 output_file.append(r"\hline")
             # end if
         # end for

### 2022-04-18 paper/ase22/experiment.tex
answering approach comment
paper

@@
 %
+
+\InputWithSpace{tables/retrain-debug-table}
+
 In this section, we present experiments to evaluate the effectiveness
@@
   for finding failures given a linguistic capability?
-\item \label{rq:two}: How effective is our proposed model for
-  generating diverse test cases? % self bleu score
-\item \label{rq:three}: How effective is test cases generated from our
-  proposed model for detecting diverse type of errors? % retraining
-  acc score
-\item \label{rq:four}: How effective is our new test case generation
+\item \label{rq:two}: Can \tool be useful to find root of bug in the
+  NLP models?
+\item \label{rq:three}: How effective is our new test case generation
   using \cfg expansion? % ablation study

### 2022-04-18 paper/ase22/tables/retrain-debug-numbers.tex
paper

@@
 \DefMacro{retrain_debug_approach_50}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_50}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_50}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_50}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_51}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_51}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_51}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_51}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_52}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_52}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_52}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_52}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_53}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_53}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_53}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_53}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_54}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_54}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_54}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_54}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_55}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_55}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_55}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_55}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_56}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_56}{used to  but now}
+\DefMacro{retrain_debug_retrained_lc_56}{Sentiment change over time, present should prevail}
 \DefMacro{retrain_debug_eval_lc_56}{parsing sentiment in (question  yes) form}
@@
 \DefMacro{retrain_debug_approach_57}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_57}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_57}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_57}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_58}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_58}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_58}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_58}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_59}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_59}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_59}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_59}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_60}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_60}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_60}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_60}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_61}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_61}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_61}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_61}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_62}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_62}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_62}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_62}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_63}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_63}{simple negations: not neutral is still neutral}
+\DefMacro{retrain_debug_retrained_lc_63}{Negated neutral should still be neutral}
 \DefMacro{retrain_debug_eval_lc_63}{parsing sentiment in (question  yes) form}
@@
 \DefMacro{retrain_debug_approach_64}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_64}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_64}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_64}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_65}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_65}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_65}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_65}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_66}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_66}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_66}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_66}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_67}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_67}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_67}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_67}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_68}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_68}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_68}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_68}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_69}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_69}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_69}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_69}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_70}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_70}{neutral words in context}
+\DefMacro{retrain_debug_retrained_lc_70}{Short sentences with neutral adjectives and nouns}
 \DefMacro{retrain_debug_eval_lc_70}{parsing sentiment in (question  yes) form}
@@
 \DefMacro{retrain_debug_approach_71}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_71}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_71}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_71}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_72}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_72}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_72}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_72}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_73}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_73}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_73}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_73}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_74}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_74}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_74}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_74}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_75}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_75}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_75}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_75}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_76}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_76}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_76}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_76}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_77}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_77}{my opinion is what matters}
+\DefMacro{retrain_debug_retrained_lc_77}{Author sentiment is more important than of others}
 \DefMacro{retrain_debug_eval_lc_77}{parsing sentiment in (question  yes) form}
@@
 \DefMacro{retrain_debug_approach_78}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_78}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_78}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_78}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_79}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_79}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_79}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_79}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_80}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_80}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_80}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_80}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_81}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_81}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_81}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_81}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_82}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_82}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_82}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_82}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_83}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_83}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_83}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_83}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_84}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_84}{Sentiment-laden words in context}
+\DefMacro{retrain_debug_retrained_lc_84}{Short sentences with sentiment-laden adjectives}
 \DefMacro{retrain_debug_eval_lc_84}{parsing sentiment in (question  yes) form}
@@
 \DefMacro{retrain_debug_approach_85}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_85}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_85}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_85}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_86}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_86}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_86}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_86}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_87}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_87}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_87}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_87}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_88}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_88}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_88}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_88}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_89}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_89}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_89}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_89}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_90}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_90}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_90}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_90}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_91}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_91}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}
+\DefMacro{retrain_debug_retrained_lc_91}{Negated positive with neutral content in the middle}
 \DefMacro{retrain_debug_eval_lc_91}{parsing sentiment in (question  yes) form}
@@
 \DefMacro{retrain_debug_approach_92}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_92}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_92}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_92}{Author sentiment is more important than of others}
@@
 \DefMacro{retrain_debug_approach_93}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_93}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_93}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_93}{Negated neutral should still be neutral}
@@
 \DefMacro{retrain_debug_approach_94}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_94}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_94}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_94}{Negated positive with neutral content in the middle}
@@
 \DefMacro{retrain_debug_approach_95}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_95}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_95}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_95}{Sentiment change over time  present should prevail}
@@
 \DefMacro{retrain_debug_approach_96}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_96}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_96}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_96}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{retrain_debug_approach_97}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_97}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_97}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_97}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{retrain_debug_approach_98}{Retrain:Checklist::Test:Ours}
-\DefMacro{retrain_debug_retrained_lc_98}{['Q & A: yes'  'Q & A: yes (neutral)']}
+\DefMacro{retrain_debug_retrained_lc_98}{parsing sentiment in (question, yes) form}
 \DefMacro{retrain_debug_eval_lc_98}{parsing sentiment in (question  yes) form}

### 2022-04-18 paper/ase22/intro.tex
intro

@@
 
-Software testing is the crucial process when developing software.  It
-evaluates an attribute or capability of the software and determines
-that it meets the requirements by examining the behavior of the
-software under test. Software testing in the early stage of the
-development finds bugs, and fixing them saves amount of costs. In
-addition, reliable software testing methodology ensures software
-quality to users in that the software meets requirements by
-verification and validation. Regarding that, NLP application is a
-branch of artifical intelligence software, and testing NLP application
-also becomes important process as well.
+Software testing is the essential component of software development
+process.  It evaluates an attribute or capability of the software and
+determines quality of the software by examining the behavior of the
+software.  Software testing in the early stage of the development
+finds bugs, and fixing them saves amount of costs. \Ml (ML) application is a
+primary branch of artifical intelligence software, and testing the application
+also becomes important process for NLP model.
+
+In addition, reliable software testing methodology ensures software
+quality to end users in that the software meets requirements by
+verification and validation.
+
+Regarding that,
 

### 2022-04-18 paper/ase22/approach.tex
intro

@@
 
-\Chlst's templates generate complete and realistic \sents, and each
+\Cklst's templates generate complete and realistic \sents, and each
 template maps to a \lc, satisfying {\bf G1} and {\bf
-  G3}. But \Chlst only uses \sw{X} manually created templates to
+  G3}. But \Cklst only uses \sw{X} manually created templates to
 generate its test suite; all test cases generated by the same template
 share the same syntactic structure, thus violating {\bf G2}. In
-addition, the label of each \Chlst test case has to be decided
+addition, the label of each \Cklst test case has to be decided
 manually, associated with each template, violating {\bf G4}.

### 2022-04-18 paper/ase22/intro.tex
intro

@@
 process.  It evaluates an attribute or capability of the software and
-determines quality of the software by examining the behavior of the
-software.  Software testing in the early stage of the development
-finds bugs, and fixing them saves amount of costs. \Ml (ML) application is a
-primary branch of artifical intelligence software, and testing the application
-also becomes important process for NLP model.
+determines correctness of the software by examining the behavior of
+the software and comparing it with the expected outcome. Software
+testing in the early stage of the development identifies errors,
+faults, defects, and fixing them saves amount of costs. Therefore,
+reliable software testing methodology assures quality in software, and
+it meets needs of the end user. Meanwhile, the trustworthiness in
+quality of \nlp (NLP) application also becomes important component for
+its practical use in real world. Traditionally, the prevalent models
+of NLP are evaluated via train-validation-test splits. train and
+validation set is used to train the NLP model and the \ho set is used
+for testing by measuring accuracy. In this method, the accuracy is a
+indicator of the performance of the models, and model with higher
+accuracy becomes better model.
 
-In addition, reliable software testing methodology ensures software
-quality to end users in that the software meets requirements by
-verification and validation.
+Despite its simplilcity and usefulness, the testing paradigm often
+overestimates the performances from the \ho set. Generalization does
+not hold in the \ho dataset and it is likely to introduce specific
+biases. The biases increase the discrepancy of distribution between
+the dataset and real world~\cite{recht2019imagenetbias}. Therefore,
+the \ho set does not represent the real world and the accuracy from
+the dataset fails to measure comprehensive performrance of the NLP
+model. In addition, the aggregated accuracy metric does not validate
+certain behaviors of the model, and, as a consequence, it causes
+costly to locate where the errors comes
+from~\cite{wu2019errudite}. Therefore, on the subject of the
+limitation of traditional testing paradigm, a number of methods have
+been proposed for evaluating multiple perspectives on the NLP model
+such as robustness on adversarial examples, model coverage and
+fairness.  Especially, Ribeiro~\etal intoduced the \Cklst, a
+behavioral testing framework for evaluating NLP model on multiple
+\lcs~\cite{marcoACL2020checklist}. The \Cklst provides predefined
+task-relevant \lcs and generate testcases relevant to each \lc.
+However, the approach only relies on manually generated input
+templates, thus the template generation becomes expensive and time
+consuming. In addition, the generated templates are selective and
+often too simple, and it is limited to provide restricted evaluation
+of linguistic capabilities. Thus, it does not garauntee the
+comprehensive evaluation.
 
-Regarding that,
+Notwithstanding, the evaluating the NLP model on the \lcs enables
+comprehensive testing of the model. Each \lc explain the functionality
+of input and outpus behavior for the NLP model under test. the
+expected bahavior is determined by combining the input and output
+scopes specified on the \lc. Typically, it describes certain type of
+input and outputs observed in real world for the target NLP task
+ranging from simple to complicated behaviors so that they are able to
+evaluate the NLP model comprehensively. Such evaluation on the
+specified functionalities avoids the overestimation of the model
+performance as it equivalently measures the model performance on each
+functionality, and the seperate model performance explain distribution
+of the performaces over the \lcs. In the end, it provides not only the
+overall model performance, but also the malfunction facets of the
+model. However, the prior work currently generated model.
 
-The prevalent models of NLP are evaluated via train-validation-test
-splits. train and validation set is used to train the NLP model and
-the \ho set is used for testing by measuring accuracy. The accuracy is
-a indicator of the performance of the models.
+%% On the subject of the limitation of traditional testing paradigm, a
+%% number of methods have been proposed. First, multiple diagnostic
+%% datasets for evaluating NLP model were introduced for obtaining
+%% generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
+%% that, model is evaluated on different aspects such as robustness of
+%% the model on adversarial
+%% sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
+%%   rychalska2019wildnlp,iyyer2018adversarial},
+%% fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
+%% consistancy~\cite{ribeiro2019consistencyeval}, prediction
+%% interpretations~\cite{ribeiroSG16lime} and interactive error
+%% analysis~\cite{wu2019errudite}. Especially, \Cklst implements
+%% behavioral testing methodolgy for evaluating multiple linguistic
+%% capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
+%% introduces input-output behaviors of linguistic capabilities and
+%% generates behavior-guided inputs for validating the behaviors. It
+%% provides comprehensive behavioral testing of NLP models through a
+%% number of generated inputs. However, the approach only relies on
+%% manually generated input templates, thus the template generation
+%% becomes expensive and time consuming. In addition, the generated
+%% templates are selective and often too simple, and it is limited to
+%% provide restricted evaluation of linguistic capabilities. Thus, it
+%% does not garauntee the comprehensive evaluation.
 
-Despite its usefulness, the main limitation of the testing paradigm
-is that the \ho set often overestimates the performances. Each dataset
-comes with specific biases, and the biases increase the discrepancy of
-distribution between dataset and
-real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
-on \ho set does not consider the discrepancy and it is limited to
-achieve comprehensive performrance of the NLP model. As a consequence,
-it is difficult to analyze where the errors comes
-from~\cite{wu2019errudite}.
-
-On the subject of the limitation of traditional testing paradigm, a
-number of methods have been proposed. First, multiple diagnostic
-datasets for evaluating NLP model were introduced for obtaining
-generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
-that, model is evaluated on different aspects such as robustness of
-the model on adversarial
-sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial},
-fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
-consistancy~\cite{ribeiro2019consistencyeval}, prediction
-interpretations~\cite{ribeiroSG16lime} and interactive error
-analysis~\cite{wu2019errudite}. Especially, \Chlst implements
-behavioral testing methodolgy for evaluating multiple linguistic
-capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
-introduces input-output behaviors of linguistic capabilities and
-generates behavior-guided inputs for validating the behaviors. It
-provides comprehensive behavioral testing of NLP models through a
-number of generated inputs. However, the approach only relies on
-manually generated input templates, thus the template generation
-becomes expensive and time consuming. In addition, the generated
-templates are selective and often too simple, and it is limited to
-provide restricted evaluation of linguistic capabilities. Thus, it
-does not garauntee the comprehensive evaluation.
-
-In this paper, we present \Model, an automated NLP model evaluation
+In this paper, we present \tool, an automated NLP model evaluation
 method for comprehensive behavioral testing of NLP models on \sa
-task. For each behavior of linguistic capability, \Model does not rely
+task. For each behavior of linguistic capability, \tool does not rely
 on the manual input generation. Instead, it establishes input
@@
 inputs that meet the requirement from existing public dataset.
-Therefore, \Model increases input diversity and generality. Further,
-\Model applies the fuzzing testing principle to generate inputs by
-mutating the selected inputs as seed inputs. Fuzzer in \Model first
+Therefore, \tool increases input diversity and generality. Further,
+\tool applies the fuzzing testing principle to generate inputs by
+mutating the selected inputs as seed inputs. Fuzzer in \tool first
 expands seed input grammar structures and determines its available

### 2022-04-18 paper/ase22/related.tex
intro

@@
 error analysis~\cite{wu2019errudite} have been proposed to evaluate
-model robustness. More recently, \Chlst introduces input-output
+model robustness. More recently, \Cklst introduces input-output
 behaviors of linguistic capabilities and generates behavior-guided
@@
 interpretations~\cite{ribeiroSG16lime} and interactive error
-analysis~\cite{wu2019errudite}. Especially, \Chlst implements
+analysis~\cite{wu2019errudite}. Especially, \Cklst implements
 behavioral testing methodolgy for evaluating multiple linguistic
-capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
+capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
 introduces input-output behaviors of linguistic capabilities and

### 2022-04-22 paper/ase22/experiment.tex
exp

@@
 of our proposed evaluation methodology. In particular, we address the
-following research questions:
+following research questions (RQs):
 
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:one}: How effective is our proposed evaluation model
-  for finding failures given a linguistic capability?
-\item \label{rq:two}: Can \tool be useful to find root of bug in the
+\item \label{rq:one}: Can \tool find different bugs from \Cklst?
+\item \label{rq:two}: Can the \tool generated testcases have stronger
+  generalization ability to test NLP models?
+\item \label{rq:three}: Can \tool be useful to find root of bug in the
   NLP models?
-\item \label{rq:three}: How effective is our new test case generation
-  using \cfg expansion? % ablation study
+%% \item \label{rq:three}: How effective is our new test case generation
+%%   using \cfg expansion? % ablation study
 \end{enumerate}
 
-For answering \ref{rq:one} and \ref{rq:two}, we generate test cases
+To answer the RQs, we need to show: (i) effect of testcase
+distribution on finding bugs; (ii) degree of execution of a NLP model
+on testcases; and (iii) ability to guide to find cause of bug in a NLP
+model. First, evaluation on distribution of generated testcase more
+equivalent to real world estimates model performance in practical use
+more accurately. It means more various bugs from the input
+distribution are likely to be detected.  On the other hand, limited
+distribution only represents narrow or uncommon portion of real world,
+and it leads to detect bugs within the restricted range. Therefore,
+demonstrating bugs detected from testcases distribution can answer the
+RQ~\ref{rq:one}. Second,
+
+we generate test cases
 and use them for evaluating model on linguistic capabilities. In this

### 2022-04-22 paper/ase22/related.tex
exp

@@
 \begin{comment}
+
+  %% On the subject of the limitation of traditional testing paradigm, a
+%% number of methods have been proposed. First, multiple diagnostic
+%% datasets for evaluating NLP model were introduced for obtaining
+%% generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
+%% that, model is evaluated on different aspects such as robustness of
+%% the model on adversarial
+%% sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
+%%   rychalska2019wildnlp,iyyer2018adversarial},
+%% fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
+%% consistancy~\cite{ribeiro2019consistencyeval}, prediction
+%% interpretations~\cite{ribeiroSG16lime} and interactive error
+%% analysis~\cite{wu2019errudite}. Especially, \Cklst implements
+%% behavioral testing methodolgy for evaluating multiple linguistic
+%% capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
+%% introduces input-output behaviors of linguistic capabilities and
+%% generates behavior-guided inputs for validating the behaviors. It
+%% provides comprehensive behavioral testing of NLP models through a
+%% number of generated inputs. However, the approach only relies on
+%% manually generated input templates, thus the template generation
+%% becomes expensive and time consuming. In addition, the generated
+%% templates are selective and often too simple, and it is limited to
+%% provide restricted evaluation of linguistic capabilities. Thus, it
+  %% does not garauntee the comprehensive evaluation.
+
 Not only that, model is evaluated on different aspects such as

### 2022-04-22 paper/ase22/experiment.tex
exp

@@
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:one}: Can \tool find different bugs from \Cklst?
-\item \label{rq:two}: Can the \tool generated testcases have stronger
+\item \label{rq:one}: Can \tool generate sentences consistent to their
+  sentiment label and their target \lc?
+\item \label{rq:two}: Can \tool find different bugs from \Cklst?
+\item \label{rq:three}: Can the \tool generated testcases have stronger
   generalization ability to test NLP models?
-\item \label{rq:three}: Can \tool be useful to find root of bug in the
+\item \label{rq:four}: Can \tool be useful to find root of bug in the
   NLP models?
@@
 
-To answer the RQs, we need to show: (i) effect of testcase
-distribution on finding bugs; (ii) degree of execution of a NLP model
-on testcases; and (iii) ability to guide to find cause of bug in a NLP
-model. First, evaluation on distribution of generated testcase more
-equivalent to real world estimates model performance in practical use
-more accurately. It means more various bugs from the input
-distribution are likely to be detected.  On the other hand, limited
-distribution only represents narrow or uncommon portion of real world,
-and it leads to detect bugs within the restricted range. Therefore,
-demonstrating bugs detected from testcases distribution can answer the
-RQ~\ref{rq:one}. Second,
+To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
+evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
+finding bugs; (\romnum{3}) degree of execution of a NLP model on testcases;
+and (\romnum{4}) ability to guide to find cause of bug in a NLP
+model.
 
-we generate test cases
-and use them for evaluating model on linguistic capabilities. In this
+First, \tool generates sentences and its label by empirical reasoning
+derived from \lc statements. Therefore, we meaure acceptibility of the
+testcases by verifying the relevancy between sentence and label, and
+between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
+by verifying the quality of generated testcases. In this work, we
+conduct manual study and measure the correlation of human labeled
+testcases and \tool labeled testcases.
+
+Second, evaluation on testcases more equivalent to real world
+estimates model performance in practical use more accurately. It means
+more various bugs from the input distribution are likely to be
+captured.  On the other hand, limited distribution only represents
+narrow or uncommon portion of real world, and it leads to detect bugs
+within the restricted range. As a result, retraining a model on the
+testcases within  obtains lower
+
+debugs less various bugs.
+
+To answer the RQ~\ref{rq:two}, we retrain
+a NLP model on generated testcases and analyze the retraining performance.
+
+it means that retraining model on more
+generalized testcases can debug more various bugs found in the
+original model.
+
+To answer the RQ~\ref{rq:two}, we retrain a NLP model on generated testcases.
+
+Third, the amount of NLP
+model component executed during testing is also critical measurement
+for assessing quality of software testing. A high software coverage
+results in lower chances of unidentified bugs in the NLP
+model. Accordingly, the ability of testcases to produce high portion
+of model coverage needs to be measured and answer the
+RQ~\ref{rq:three}.
+
+In addition to the detection of bugs in the model,
+explaination of the bugs is also important stage of debugging and
+repairing the model. Therefore, we anwer RQ~\ref{rq:four} by showing
+usefulness of \tool by analyzing the NLP model based on \tool and
+finding root of the bug.
+
+\subsection{Experiment Setup}
+
+To resolve these, we conduct practical experiments and show the
+effectiveness of \tool. We conduct a maual studyRQ~\ref{rq:one}
+
+we generate test cases and use
+them for evaluating model on linguistic capabilities. In this
 experiment, We assess the ability to find failures by anlyzing model's
@@
 
-\subsection{Experiment Setup}
-%
-\MyPara{Seed Input Selection}
-%
-For each linguistic capability, we first search all sentences that
-meet its requirement. Among found sentences, we randomly select 10
-sentences due to memory constraint.
+%% \MyPara{Seed Input Selection}
+%% %
+%% For each linguistic capability, we first search all sentences that
+%% meet its requirement. Among found sentences, we randomly select 10
+%% sentences due to memory constraint.
 
-\MyPara{Word Sentiment}
-%
-we extract sentiments of words using the
-\Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
-available lexical resource of words on Wordnet with three numerical
-scores of objectivity, positivity and negativity. Sentiment word
-labels from the scores are classified from the algorithm from Mihaela
-\etal~\cite{mihaela2017sentiwordnetlabel}.
+%% \MyPara{Word Sentiment}
+%% %
+%% we extract sentiments of words using the
+%% \Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
+%% available lexical resource of words on Wordnet with three numerical
+%% scores of objectivity, positivity and negativity. Sentiment word
+%% labels from the scores are classified from the algorithm from Mihaela
+%% \etal~\cite{mihaela2017sentiwordnetlabel}.
 
-\MyPara{\Cfg Expansion}
-%
-We build a reference \Cfg of natural language from the English Penn
-\Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
-The corpus is sampled from 2,499 stories from a tree year \Wsj
-collection The \Trb provides a parsed text corpus with annotation of
-syntactic and semantic structure. In this experiment We implement the
-\trb corpora available through \Nltk, which is a suite of libraries
-and programs for \Nlp for English. In addition, we parse the seed
-input using into its CFG using the Berkeley Neural
-Parser~\cite{kitaev2018constituency, kitaev2019multilingual}, a
-high-accuracy parser with models for 11 languages. The input is a raw
-text in natural language and the output is the string representation of
-parse tree. Next after comparing CFGs between reference and seed input,
-we randomly select 10 expansions for generating templates due to
-memory constraint.
+%% \MyPara{\Cfg Expansion}
+%% %
+%% We build a reference \Cfg of natural language from the English Penn
+%% \Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
+%% The corpus is sampled from 2,499 stories from a tree year \Wsj
+%% collection The \Trb provides a parsed text corpus with annotation of
+%% syntactic and semantic structure. In this experiment We implement the
+%% \trb corpora available through \Nltk, which is a suite of libraries
+%% and programs for \Nlp for English. In addition, we parse the seed
+%% input using into its CFG using the Berkeley Neural
+%% Parser~\cite{kitaev2018constituency, kitaev2019multilingual}, a
+%% high-accuracy parser with models for 11 languages. The input is a raw
+%% text in natural language and the output is the string representation of
+%% parse tree. Next after comparing CFGs between reference and seed input,
+%% we randomly select 10 expansions for generating templates due to
+%% memory constraint.
 
-\MyPara{Synonyms}
-%
-\Model searches synonyms of each token from synonym sets extracted
-from \Wrdnt using \Spacy open-source library for NLP.
+%% \MyPara{Synonyms}
+%% %
+%% \Model searches synonyms of each token from synonym sets extracted
+%% from \Wrdnt using \Spacy open-source library for NLP.
 
-\MyPara{Models}
-%
-We evaluate the following \sa models via \Model:
-\Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
-\Dbert~\cite{sanh2019distilbert}. These models are fine-tuned on \Sstt
-and their accuracies are \BertAcc, \RobertaAcc and \DbertAcc.
+%% \MyPara{Models}
+%% %
+%% We evaluate the following \sa models via \Model:
+%% \Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
+%% \Dbert~\cite{sanh2019distilbert}. These models are fine-tuned on \Sstt
+%% and their accuracies are \BertAcc, \RobertaAcc and \DbertAcc.
 
-\MyPara{Retraining}
-%
-We retrain \sa models. we split \Model generated test cases into
-train/validation/test sets with the ratio of 8:1:1. The number of
-epochs and batch size for retraining are 1 and 16 respectively.
+%% \MyPara{Retraining}
+%% %
+%% We retrain \sa models. we split \Model generated test cases into
+%% train/validation/test sets with the ratio of 8:1:1. The number of
+%% epochs and batch size for retraining are 1 and 16 respectively.

### 2022-04-22 paper/ase22/experiment.tex
exp

@@
   sentiment label and their target \lc?
-\item \label{rq:two}: Can \tool find different bugs from \Cklst?
-\item \label{rq:three}: Can the \tool generated testcases have stronger
+\item \label{rq:two}: Can the \tool generated testcases have stronger
   generalization ability to test NLP models?
-\item \label{rq:four}: Can \tool be useful to find root of bug in the
+\item \label{rq:three}: Can \tool be useful to find root of bug in the
   NLP models?
@@
 conduct manual study and measure the correlation of human labeled
-testcases and \tool labeled testcases.
-
-Second, evaluation on testcases more equivalent to real world
-estimates model performance in practical use more accurately. It means
-more various bugs from the input distribution are likely to be
-captured.  On the other hand, limited distribution only represents
-narrow or uncommon portion of real world, and it leads to detect bugs
-within the restricted range. As a result, retraining a model on the
-testcases within  obtains lower
-
-debugs less various bugs.
-
-To answer the RQ~\ref{rq:two}, we retrain
-a NLP model on generated testcases and analyze the retraining performance.
-
-it means that retraining model on more
-generalized testcases can debug more various bugs found in the
-original model.
-
-To answer the RQ~\ref{rq:two}, we retrain a NLP model on generated testcases.
-
-Third, the amount of NLP
-model component executed during testing is also critical measurement
-for assessing quality of software testing. A high software coverage
-results in lower chances of unidentified bugs in the NLP
-model. Accordingly, the ability of testcases to produce high portion
-of model coverage needs to be measured and answer the
-RQ~\ref{rq:three}.
-
-In addition to the detection of bugs in the model,
+testcases and \tool labeled testcases. Second, the amount of NLP model
+component executed during testing is a critical measurement for
+assessing quality of software testing. A high software coverage
+results in higher chances of unidentified bugs in the NLP model. On
+the other hand, limited distribution only represents narrow portion of
+real world covering limited execution paths in a NLP model. It leads
+to detect bugs within the restricted execution paths.  Therefore,
+testcases more equivalent to real world represents more generalized
+distribution, and it results in high coverage of the NLP model.
+Accordingly, the ability of testcases to produce high portion of model
+coverage needs to be measured. We answer the RQ~\ref{rq:three}
+measuring neural coverage of the neural NLP model according to the
+measurements. In addition to the detection of bugs in the model,
 explaination of the bugs is also important stage of debugging and
@@
 \subsection{Experiment Setup}
+We conduct practical experiments and show the effectiveness of
+\tool.
 
-To resolve these, we conduct practical experiments and show the
-effectiveness of \tool. We conduct a maual studyRQ~\ref{rq:one}
+\subsubsection{Manual study}
+We sample set of test cases and corresponding \lc randomly sampled
+from seed sentences and expanded sentences from \tool.  Subjects are
+also provided with the sampled testcases. Each subject is asked for
+scoring relevancy between the linguistic capability of the
+sentences. The scores range from 1 to 5 representing strongly not
+relevant to strongly relevant respectively. Additionally, the subject
+scores the relevancy between sentences and their sentiment labels. The
+scores also range from 1 to 5, and they represent strongly negative to
+strongly positive respectively. In this work, we collect manual study
+scores from {} subjects attended. From the collected scores, we
+measure the following metrics:
 
-we generate test cases and use
-them for evaluating model on linguistic capabilities. In this
-experiment, We assess the ability to find failures by anlyzing model's
-performance on the generated test cases. We also measure the diversity
-among the generated test cases using similarites among them. Next, we
-answer \ref{rq:three} by retraining \sa model with generated test
-cases and measuring performances. The idea behind this is that more
-comprehensive inputs becomes closer to real-world distribution and
-addresses more type of errors.  Therefore, it leads to improve the
-model performance. In this experiment, We retrain the model and
-compare performances of the retrained model. Not only that, we conduct
-ablation study of \cfg expansion to understand the its impact in our
-approach.
+\begin{enumerate}[label=\textbf{Metrics}]
+\item \label{mm:one} Reported bugs
+\item \label{mm:two} Incorrect inputs
+\item \label{mm:three} Label Inconsistency
+%% \item \label{rq:three}: How effective is our new test case generation
+%%   using \cfg expansion? % ablation study
+\end{enumerate}
+
+The metrics used for this study
 

### 2022-04-23 paper/ase22/experiment.tex
exp setup

@@
 the other hand, limited distribution only represents narrow portion of
-real world covering limited execution paths in a NLP model. It leads
-to detect bugs within the restricted execution paths.  Therefore,
+real world covering limited execution behaviors in a NLP model. It leads
+to detect bugs within the restricted execution behaviors.  Therefore,
 testcases more equivalent to real world represents more generalized
@@
 explaination of the bugs is also important stage of debugging and
-repairing the model. Therefore, we anwer RQ~\ref{rq:four} by showing
+repairing the model. Therefore, we anwer RQ~\ref{rq:three} by showing
 usefulness of \tool by analyzing the NLP model based on \tool and
@@
 \tool.
-
-\subsubsection{Manual study}
+\subsubsection*{\textbf{Manual Study}}
 We sample set of test cases and corresponding \lc randomly sampled
@@
 scoring relevancy between the linguistic capability of the
-sentences. The scores range from 1 to 5 representing strongly not
-relevant to strongly relevant respectively. Additionally, the subject
-scores the relevancy between sentences and their sentiment labels. The
-scores also range from 1 to 5, and they represent strongly negative to
-strongly positive respectively. In this work, we collect manual study
-scores from {} subjects attended. From the collected scores, we
-measure the following metrics:
+sentences. The score is discrete and it ranges from 1 to 5
+representing ``strongly not relevant'' to ``strongly relevant''
+respectively. Additionally, the subject scores the relevancy between
+sentences and their sentiment labels. The score is also discreate and
+ranges from 1 to 5. It represents ``strongly negative'' to ``strongly
+positive'' respectively. In this work, we collect manual study scores
+from 8 subjects attended. From the collected scores, we measure the
+following metrics:
 
-\begin{enumerate}[label=\textbf{Metrics}]
-\item \label{mm:one} Reported bugs
-\item \label{mm:two} Incorrect inputs
-\item \label{mm:three} Label Inconsistency
-%% \item \label{rq:three}: How effective is our new test case generation
-%%   using \cfg expansion? % ablation study
-\end{enumerate}
+\begin{eqnarray}
+  &Reported\:bugs &=\sum_{i} \delta(label_{S^2LCT}!=pred_{model}) \label{metric:rb}\\
+  &Incorrect\:inputs &= \sum_{i} \delta(pred_{model}!=label_{human}) \label{metric:ii}\\
+  %% &Label\:inconsistency &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:li}
+\end{eqnarray}
 
-The metrics used for this study
+The metrics represents the number of data instance that its label
+assigned from are different between \tool and its model prediction
+(eq~\ref{metric:rb}) and between the model prediction and human
+(eq~\ref{metric:ii}). We show the correspondonce between \tool and
+human by computing the precision and recall from the reported bugs and
+incorrect inputs.
+%% and between \tool and human (eq~\ref{metric:li}).
+
+\subsubsection*{\textbf{Model Coverage}}
+We implement DeepXplore to measure the NLP model
+coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
+whitebox testing framework for large-scale \dl systems. It introduces
+neuron coverage of a set of test inputs as the ratio of the number of
+unique activated neurons and the total number of neurons in input \dl
+system. In this experiment, we compute the neuron coverage of a test
+cases from \tool and \Cklst on the fine-tuned \sa model of
+\bertsamodel and compare the coverage between \tool and \Cklst.
 

### 2022-04-23 paper/ase22/experiment.tex
exp

@@
 \item \label{rq:two}: Can the \tool generated testcases have stronger
-  generalization ability to test NLP models?
+  generalization ability to test \sa models?
 \item \label{rq:three}: Can \tool be useful to find root of bug in the
-  NLP models?
+  \sa models?
 %% \item \label{rq:three}: How effective is our new test case generation
@@
 evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
-finding bugs; (\romnum{3}) degree of execution of a NLP model on testcases;
-and (\romnum{4}) ability to guide to find cause of bug in a NLP
+finding bugs; (\romnum{3}) degree of execution of a \sa model on testcases;
+and (\romnum{4}) ability to guide to find cause of bug in a \sa
 model.
@@
 conduct manual study and measure the correlation of human labeled
-testcases and \tool labeled testcases. Second, the amount of NLP model
+testcases and \tool labeled testcases. Second, the amount of \sa model
 component executed during testing is a critical measurement for
 assessing quality of software testing. A high software coverage
-results in higher chances of unidentified bugs in the NLP model. On
+results in higher chances of unidentified bugs in the \sa model. On
 the other hand, limited distribution only represents narrow portion of
-real world covering limited execution behaviors in a NLP model. It leads
+real world covering limited execution behaviors in a \sa model. It leads
 to detect bugs within the restricted execution behaviors.  Therefore,
 testcases more equivalent to real world represents more generalized
-distribution, and it results in high coverage of the NLP model.
+distribution, and it results in high coverage of the \sa model.
 Accordingly, the ability of testcases to produce high portion of model
 coverage needs to be measured. We answer the RQ~\ref{rq:three}
-measuring neural coverage of the neural NLP model according to the
+measuring neural coverage of the neural \sa model according to the
 measurements. In addition to the detection of bugs in the model,
@@
 repairing the model. Therefore, we anwer RQ~\ref{rq:three} by showing
-usefulness of \tool by analyzing the NLP model based on \tool and
+usefulness of \tool by analyzing the \sa model based on \tool and
 finding root of the bug.
@@
 \subsubsection*{\textbf{Model Coverage}}
-We implement DeepXplore to measure the NLP model
+We implement DeepXplore to measure the \sa model
 coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
@@
 \bertsamodel and compare the coverage between \tool and \Cklst.
+
+\subsubsection*{\textbf{Analysis of Root of bug}}
+In this experiment, we analyze a \sa model based on the test results
+of the set of \tool test inputs and find the root of bug in the
+model. It shows that \tool generated testcases are useful to explain
+the \sa model test results and identify the rationale of the bug
+found. We implement \Denas for this experiment. Rules generated from
+\Denas is interpretable functions mapping certain features of the
+input to the expected output of a deep \nn system, and the generated
+rules are considered as the behaviors of the deep \nn system. To
+anlayze the bug of a \sa model, we generates rules over the test
+inputs using \Denas and identifies falty rules for the failed test
+inputs. We manually identify the root of the falty rules and find the
+root of bug in the end.
 

### 2022-04-28 paper/ase22/abstract.tex
modify abstract

@@
 \begin{abstract}
-  \Nlp (NLP) technique becomes one of the core techniques for developing
-  text analytics applications.  For developing the NLP applications,
-  the applications are required to achieve high reliability before it
-  goes to market.  The trustworthiness of the prevalent NLP
-  applications is obtained by measuring the accuracy of the
-  applications on held-out dataset.  However, evaluating NLP on
-  testset does with held-out accuracy is limited to show its quality
-  because the held-out datasets are often not comprehensive. While the
-  behavioral testing over multiple general linguistic capabilities are
-  employed, it relies on manually created test cases, and is still
-  limited to measure its comprehensive performance for each linguistic
-  capability. In this work, we introduce \Model, an NLP model
-  testing methodology. Given a linguistic capability, The
-  \Model finds relevant testcases to test the linguistic
-  capability from existing datasets as seed inputs, generates
-  sufficient number of new test cases by fuzzing the seed inputs based
-  on their context-free grammar (\Cfg). We illustrate the usefulness
-  of the \Model by showing input diversity and identifying
-  critical failures in \sota models for NLP task. In our experiment,
-  we show that the \Model generates {} more test cases with {}
-  higher diversity, and finds {} more bugs.  
+  \Nlp (NLP) technique becomes one of the core techniques for
+  developing text analytics applications.  For developing the NLP
+  applications, the applications are required to achieve high
+  reliability before it goes to market.  The trustworthiness of the
+  prevalent NLP applications is obtained by measuring the accuracy of
+  the applications on held-out dataset.  However, evaluating NLP on
+  testset with the held-out accuracy is limited to validate its
+  quality because the held-out datasets are often not
+  comprehensive. Along with this, Evaluating a NLP model on
+  task-specific behaviours defined on empirical linguistic
+  capabilities has been introduced. However, it relies on manually
+  created test cases, and is still limited to measure the model
+  performance on biased testcases. In this work, we introduce \tool,
+  an NLP model testing methodology.  Given a linguistic capability,
+  The \tool finds suitable testcases to test the linguistic capability
+  from existing datasets as seed inputs, generates sufficient number
+  of new test cases by fuzzing the seed inputs based on their \cfg
+  (CFG).  We illustrate the usefulness of the \tool by showing its
+  reliability on generated testcases and its generalization ability.
+  In our experiment, we also show that \tool facilitates
+  identification of critical failures and its origins in NLP models
+  for \sa task.
 \end{abstract}

### 2022-04-30 paper/ase22/abstract.tex
abstract

--- 2022-03-15 paper/ase22/abstract.tex
@@
 \begin{abstract}
-  \Nlp (NLP) technique becomes one of the core techniques for developing
-  text analytics applications.  For developing the NLP applications,
-  the applications are required to achieve high reliability before it
-  goes to market.  The trustworthiness of the prevalent NLP
-  applications is obtained by measuring the accuracy of the
-  applications on held-out dataset.  However, evaluating NLP on
-  testset does with held-out accuracy is limited to show its quality
-  because the held-out datasets are often not comprehensive. While the
-  behavioral testing over multiple general linguistic capabilities are
-  employed, it relies on manually created test cases, and is still
-  limited to measure its comprehensive performance for each linguistic
-  capability. In this work, we introduce \Model, an NLP model
-  testing methodology. Given a linguistic capability, The
-  \Model finds relevant testcases to test the linguistic
-  capability from existing datasets as seed inputs, generates
-  sufficient number of new test cases by fuzzing the seed inputs based
-  on their context-free grammar (\Cfg). We illustrate the usefulness
-  of the \Model by showing input diversity and identifying
-  critical failures in \sota models for NLP task. In our experiment,
-  we show that the \Model generates {} more test cases with {}
-  higher diversity, and finds {} more bugs.  
+  \Nlp (NLP) technique has become one of the core techniques for
+  developing text analytic applications.  These applications are
+  required to achieve high reliability to be useful in practice.  The
+  trustworthiness of the prevalent NLP applications is obtained by
+  measuring the accuracy of the applications on held-out dataset.
+  However, evaluating NLP on testset with the held-out accuracy is
+  limited in validating its overall quality because the held-out
+  datasets are often not comprehensive. Along with this, evaluating an
+  NLP model on task-specific behaviors defined on empirical linguistic
+  capabilities has been introduced. However, such evaluation relies on
+  manually created test cases, and is still limited to measure the
+  model performance on biased dataset. In this work, we introduce
+  \tool, an NLP model testing infrastructure.  Given a linguistic
+  capability that users want to evaluate for a NLP model, \tool finds
+  suitable seed inputs from existing datasets, generates sufficient
+  number of new test inputs by fuzzing the seed inputs based on their
+  \cfg (CFG).  We evaluate \tool by showing its reliability on
+  generated inputs and its generalization ability.  In our
+  experiments, we also show that \tool facilitates identification of
+  critical failures and its origins in the NLP models for \sa task.
 \end{abstract}

### 2022-05-01 paper/ase22/intro.tex
exp
intro

--- 2022-03-15 paper/ase22/intro.tex
@@
 
-Software testing is the crucial process when developing software.  It
-evaluates an attribute or capability of the software and determines
-that it meets the requirements by examining the behavior of the
-software under test. Software testing in the early stage of the
-development finds bugs, and fixing them saves amount of costs. In
-addition, reliable software testing methodology ensures software
-quality to users in that the software meets requirements by
-verification and validation. Regarding that, NLP application is a
-branch of artifical intelligence software, and testing NLP application
-also becomes important process as well.
+%% [Thursday 3:01 PM] Yang, Wei
 
-The prevalent models of NLP are evaluated via train-validation-test
-splits. train and validation set is used to train the NLP model and
-the \ho set is used for testing by measuring accuracy. The accuracy is
-a indicator of the performance of the models.
+%% 1. existing NLP testing practice.
 
-Despite its usefulness, the main limitation of the testing paradigm
-is that the \ho set often overestimates the performances. Each dataset
-comes with specific biases, and the biases increase the discrepancy of
-distribution between dataset and
-real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
-on \ho set does not consider the discrepancy and it is limited to
-achieve comprehensive performrance of the NLP model. As a consequence,
-it is difficult to analyze where the errors comes
-from~\cite{wu2019errudite}.
+%% 2. Limitation in three perspectives:
+%% (i) automated input generation,
+%% (ii) test oracle (of generated input),
+%% (iii) metrics/capabilities to debug the issues
 
-On the subject of the limitation of traditional testing paradigm, a
-number of methods have been proposed. First, multiple diagnostic
-datasets for evaluating NLP model were introduced for obtaining
-generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
-that, model is evaluated on different aspects such as robustness of
-the model on adversarial
-sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial},
-fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
-consistancy~\cite{ribeiro2019consistencyeval}, prediction
-interpretations~\cite{ribeiroSG16lime} and interactive error
-analysis~\cite{wu2019errudite}. Especially, \Chlst implements
-behavioral testing methodolgy for evaluating multiple linguistic
-capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
-introduces input-output behaviors of linguistic capabilities and
-generates behavior-guided inputs for validating the behaviors. It
-provides comprehensive behavioral testing of NLP models through a
-number of generated inputs. However, the approach only relies on
-manually generated input templates, thus the template generation
-becomes expensive and time consuming. In addition, the generated
-templates are selective and often too simple, and it is limited to
-provide restricted evaluation of linguistic capabilities. Thus, it
-does not garauntee the comprehensive evaluation.
+%% 3. Issues with existing techniques: cannot satisfy all three requirements. Give some example, checklist (ii) and (iii), adversarial
+%% testing (i) (ii) ....
 
-In this paper, we present \Model, an automated NLP model evaluation
-method for comprehensive behavioral testing of NLP models on \sa
-task. For each behavior of linguistic capability, \Model does not rely
-on the manual input generation. Instead, it establishes input
-requirement for evaluating a linguistic capability and finds suitable
-inputs that meet the requirement from existing public dataset.
-Therefore, \Model increases input diversity and generality. Further,
-\Model applies the fuzzing testing principle to generate inputs by
-mutating the selected inputs as seed inputs. Fuzzer in \Model first
-expands seed input grammar structures and determines its available
-\pos to maintain structural naturalness. After that, to hold
-contextual naturalness of the mutated inputs, the fuzzer completes the
-expanded new structures via data-driven context-aware word
-suggestion. Additionally, sentiment-independent words in the inputs
-are replaced with rule-based word suggestion.
+%% 4. To address the limitation of existing work, we propose....
+
+%% 5. insight that enable the three requirements
+
+In the early stage of the software development process, automated
+software testing and debugging can identify and fix
+defects. Therefore, effective software testing assures software
+quality, and it meets needs of the end user. Nowdays, software at work
+has elements of \ml (ML). Especially, \Nlp (NLP) applications in
+software are growing exponentially. Therefore, as quality assurance of
+software is an essential process in the software development
+processes, trustworthiness in quality of NLP application has become an
+important component for its practical use in real world.
+%% \sw{Should we lead with this paragraph? We are talking about
+%%   functional testing here but next we say NLP uses
+%%   train-validation-test.}
+Traditionally, the prevalent models of NLP are evaluated via
+train-validation-test splits. Training and validation set are used to
+train the NLP models, and the test set, also named as \ho set, is used
+for testing the trained model. Meanwhile, the model performance is
+estimated into numbers used as performance metric. Especially,
+accuracy, the fraction of model output that the model correctly
+predicts, is the most widely the performance metric for classification
+models. Accordingly, a model is considered better if it has higher
+accuracy than another model.
+
+Despite its simplicity and usefulness, there are several limitations
+for the prevalent testing paradigm: First, the testing paradigm mostly
+requires manual work for collecting and generating the data. The
+manual work is costly with respect to time consumption and its impact
+on market price. Therefore, it necessitates automated data generation
+for improving model testing approach. Second, this testing paradigm
+often overestimates the model performances from the \ho
+set~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
+  marcoACL2020checklist}.
+%% \sw{Not sure what overestimate means here}
+The overestimation comes from the discrepancy between distribution of
+data collected and actual distribution in real world.  Oftentimes, the
+\ho dataset is not representative and it is likely to introduce
+specific biases. In addition, the inconsistency between test input and
+its oracle causes biases. Such biases increase the discrepancy of
+distribution between the dataset and real-world data. Consequently,
+representiveness of the test data is required for testing approach.
+Not only that, forced aggregation static into a single number such as
+average makes user to difficult to localize and fix the bug found in
+\ho set. Therefore, making this testing method fails to validate model
+behaviors resulting in localization of the causes of the inaccuracy at
+a high. In cost~\cite{wu2019errudite}. Therefore behavioral testing
+approach provides the better ability to examine the inaccuracy and
+find the bugs in the model.
+
+To address these challenges, several approaches have been proposed to
+evaluate different aspects of the NLP models, such as robustness on
+adversarial examples \cite{ribeiro2018sear,belinkov2018breaknmt,
+  rychalska2019wildnlp,iyyer2018adversarial}, model coverage
+\cite{rottger2020hatecheck}, and fairness
+\cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition,
+Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
+evaluating NLP model on multiple linguistic
+capabilities~\cite{marcoACL2020checklist}. \Cklst defines
+task-relevant linguistic capabilities and generates testcases for each
+\lc. In spite of their effectiveness, they have limitations with
+respective to model evaluation. For example, Testing model coverage
+only shows model behaviors, but not the model performance on existing
+testing set. The fairness and robustness testing only focus on only
+one model capability resulting in its limited comprehensiveness. In
+addition, \Cklst relies on manually generated input templates; thus,
+the template generation requires manual work, and it needs to be
+preset before test data generation. Consequently, the templates
+becomes distributed in limited range of their structure. It restricts
+its ability to comprehensively test the linguistic capabilities.
+
+Despite the limitations, \Cklst approach of testing the linguistic
+capabilities is a promising direction. Each \lc explains the
+functionality of the input and output behavior for the NLP model under
+test. Typically, it describes certain type of input and outputs
+observed in real world for the target NLP task ranging from simple to
+complicated behaviors so that they are able to evaluate the NLP model
+comprehensively. For exmaple, a linguistic capability of ``Negated
+neutral should still be neutral.'' measures how accurately the \sa
+model understands the negative neutral input as an neutral
+sentiment. Therefore, it requires the \sa model to output neural
+sentiment on the negated neutral input.  Such methodology of
+evaluation on the specified functionalities avoids the overestimation
+of the model performance as it equivalently measures the model
+performance on each functionality, and the separate model performance
+explain distribution of the performance over the linguistic
+capabilities. In the end, it provides not only the overall model
+performance, but also the malfunction facets of the model.
+
+To address the limitations of existing works, we present \tool, an
+automated NLP model evaluation method for comprehensive behavioral
+testing of NLP models on \sa task. We first address increasing input
+representiveness. Compared with templates used in \Cklst, \tool
+instead establishes input requirement for evaluating a linguistic
+capability and finds suitable inputs that meet the requirement from
+existing public dataset. In this process, \tool applies the fuzzing
+testing principle to generate inputs by mutating the selected inputs
+as seed inputs. Fuzzer in \tool first expands seed input grammar
+structures and determines its available \pos to maintain structural
+naturalness. After that, to hold contextual naturalness of the mutated
+inputs, the fuzzer completes the expanded new structures via
+data-driven context-aware word suggestion. Additionally,
+sentiment-independent words in the inputs are replaced with rule-based
+word suggestion. Further, we address the manual input generation
+process by automating the process mentioned above. Lastly, we adopts
+behavioral model testing method by introducing multiple behavior of
+linguistic capabilities on \sa task and generating inputs relevant to
+each linguistic capability.
 
@@
 \Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
-We show that
+We show that ...

### 2022-05-02 paper/ase22/experiment.tex
Testcases.py

--- 2022-04-23 paper/ase22/experiment.tex
@@
-\section{Experiment}
+\section{Experimental Setup}
 \label{sec:experiment}
@@
 
-\InputWithSpace{tables/retrain-debug-table}
+% \InputWithSpace{tables/retrain-debug-table}
 
-In this section, we present experiments to evaluate the effectiveness
-of our proposed evaluation methodology. In particular, we address the
+In this section, we present the setup of the experiments to evaluate the effectiveness
+of \tool{}. We address the
 following research questions (RQs):
 
+\sw{We may miss a RQ for the test results using \tool. In the setup,
+  we have not said which sentiment analysis models we tested, and how
+  we measure the results (e.g., number of misclassified test cases).}
+
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:one}: Can \tool generate sentences consistent to their
-  sentiment label and their target \lc?
-\item \label{rq:two}: Can the \tool generated testcases have stronger
-  generalization ability to test NLP models?
-\item \label{rq:three}: Can \tool be useful to find root of bug in the
-  NLP models?
+\item \label{rq:one}: Can \tool generate test cases with the correct \lc categorization and
+  sentiment label?
+\item \label{rq:two}: Can \tool generate more diverse test cases than \Cklst?
+\item \label{rq:three}: Can \tool be useful to find root causes of bugs in the \sa models?
 %% \item \label{rq:three}: How effective is our new test case generation
@@
 
-To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
-evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
-finding bugs; (\romnum{3}) degree of execution of a NLP model on testcases;
-and (\romnum{4}) ability to guide to find cause of bug in a NLP
-model.
+%To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
+%evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
+%finding bugs; (\romnum{3}) degree of execution of a \sa model on testcases;
+%and (\romnum{4}) ability to guide to find cause of bug in a \sa
+%model.
 
-First, \tool generates sentences and its label by empirical reasoning
-derived from \lc statements. Therefore, we meaure acceptibility of the
-testcases by verifying the relevancy between sentence and label, and
-between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
-by verifying the quality of generated testcases. In this work, we
-conduct manual study and measure the correlation of human labeled
-testcases and \tool labeled testcases. Second, the amount of NLP model
-component executed during testing is a critical measurement for
-assessing quality of software testing. A high software coverage
-results in higher chances of unidentified bugs in the NLP model. On
-the other hand, limited distribution only represents narrow portion of
-real world covering limited execution behaviors in a NLP model. It leads
-to detect bugs within the restricted execution behaviors.  Therefore,
-testcases more equivalent to real world represents more generalized
-distribution, and it results in high coverage of the NLP model.
-Accordingly, the ability of testcases to produce high portion of model
-coverage needs to be measured. We answer the RQ~\ref{rq:three}
-measuring neural coverage of the neural NLP model according to the
-measurements. In addition to the detection of bugs in the model,
-explaination of the bugs is also important stage of debugging and
-repairing the model. Therefore, we anwer RQ~\ref{rq:three} by showing
-usefulness of \tool by analyzing the NLP model based on \tool and
-finding root of the bug.
+\sw{Make clear (earlier in the paper): a test case is a sentence in a linguistic capability with a sentiment label.}
 
-\subsection{Experiment Setup}
-We conduct practical experiments and show the effectiveness of
-\tool.
-\subsubsection*{\textbf{Manual Study}}
-We sample set of test cases and corresponding \lc randomly sampled
-from seed sentences and expanded sentences from \tool.  Subjects are
-also provided with the sampled testcases. Each subject is asked for
+\paragraph{RQ1.} As described in Section \ref{sec:approach}, \tool generates test cases in
+two steps: specification-based seed generation and syntax-based sentence expansion. These
+automated steps may generate seed/expanded sentences marked with incorrect sentiment labels or categorized into
+wrong linguistic capabilities. For example, the search rule and template defined in a linguistic capability
+may not always generate seed sentences in that capability or with the correct label.
+To answer {\bf RQ1}, we perform a manual study to measure the correctness of the sentiment labels and linguistic capabilities
+associated with the seed/expanded sentences, produced by \tool
+
+\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated manual study.
+Also, be explicit about the setup: sample size, population size, number of participants, protocol (each given how many sentences, and how disagreement is resolved), etc.}
+In the manual study, we sample a set of test cases and corresponding \lc randomly sampled
+from seed sentences and expanded sentences from \tool. 
+also provided with the sampled test cases. Each subject is asked for
 scoring relevancy between the linguistic capability of the
@@
   &Reported\:bugs &=\sum_{i} \delta(label_{S^2LCT}!=pred_{model}) \label{metric:rb}\\
-  &Incorrect\:inputs &= \sum_{i} \delta(pred_{model}!=label_{human}) \label{metric:ii}\\
+  &Incorrect\:inputs &= \sum_{i} \delta(pred_{model}!=label_{human}) \label{metric:ii}
   %% &Label\:inconsistency &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:li}
@@
 (eq~\ref{metric:rb}) and between the model prediction and human
-(eq~\ref{metric:ii}). We show the correspondonce between \tool and
+(eq~\ref{metric:ii}). We show the correspondence between \tool and
 human by computing the precision and recall from the reported bugs and
@@
 
-\subsubsection*{\textbf{Model Coverage}}
-We implement DeepXplore to measure the NLP model
-coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
-whitebox testing framework for large-scale \dl systems. It introduces
-neuron coverage of a set of test inputs as the ratio of the number of
-unique activated neurons and the total number of neurons in input \dl
-system. In this experiment, we compute the neuron coverage of a test
-cases from \tool and \Cklst on the fine-tuned \sa model of
-\bertsamodel and compare the coverage between \tool and \Cklst.
+\paragraph{RQ2.}
+Recall that a key limitation of \Cklst is that its template-based
+approach that relies on significant manual efforts may not generate test cases that comprehensively cover the sentences
+in a linguistic capability. \tool, instead, automatically generates test cases based on a search
+dataset and the syntax in a large reference corpus. We expect \tool can generate a more diverse test suite
+than \Cklst. To measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
+where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
+\sw{Why is this a good metric for diversity?}
+Specifically, we use the  \sw{are these metrics we define or are they from ma2018deepgauge?} two coverage metrics in existing work \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), as our metrics to evaluate the test suite diversity.
+
+\begin{equation}
+\begin{split}
+    \text{UpperCornerNeuron}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (high_n, +\infty)\}; \\
+    \text{LowerCornerNeuron}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (-\infty, low_n)\}; \\
+\end{split}
+    \label{eq:corner}
+\end{equation}
+
+\noindent Eq.
+\ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n, low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
+Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
+
+\begin{equation}
+\begin{split}
+     & BoundCov(\mathcal{X}) = \frac{|UpperCornerNeuron(\mathcal{X})| + |LowerCornerNeuron| }{2 \times |N|} \\ 
+     & SActCov(\mathcal{X}) = \frac{|UpperCornerNeuron(\mathcal{X})|} {|N|} \\ 
+\end{split}
+    \label{eq:coverage}
+\end{equation}
+
+\noindent The formal definition of our coverage metrics are shown in Eq.\ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
+Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.
+
+% ($Cov(\mathcal{X})$ in \equref{eq:coverage}),
+% where $N$ is the total number blocks, $\mathbb I(\cdot)$ is the indicator function, and
+% $(B_i(x) > \tau_i))$ represents whether $i^{th}$ block is activated by input $x$~(the definition of $B_i$ and $\tau_i$ are the same with \equref{eq:new2} and \equref{eq:new3}).
+% Because AdNNs activate different blocks for decision making, then a higher block coverage indicates the test samples cover more decision behaviors.
+
+To answer {\bf RQ2}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
+After that, we randomly select 100 \sw{Why 100, not all?} test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
+\cm{we repeat this process and record both the average and variance value of each coverage}
+% For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
+% Finally, we feed the generated test samples to AdNNs and measure block coverage.
+% We repeat this process 10 times and record the average coverage and the variance.
+% The results are shown in \tabref{tab:coverage} last two columns.
+
+%
+%The amount of \sa model
+%components \sw{?} executed during testing is a critical measurement for
+%assessing quality of software testing. A high software coverage
+%results in higher chances of unidentified bugs in the \sa model. On
+%the other hand, limited distribution only represents narrow portion of
+%real world covering limited execution behaviors in a \sa model. It leads
+%to detect bugs within the restricted execution behaviors.  Therefore,
+%test cases more representative of real-world data result in more generalized
+%distribution and higher coverage of the \sa model.
+%Therefore, we answer the {\bf RQ2} by
+%measuring the neural coverage of the \sa model.
+%
+%Specifically, we implemented DeepXplore to measure the \sa model
+%coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
+%white-box testing framework for large-scale \dl systems. It introduces
+%neuron coverage of a set of test inputs as the ratio of the number of
+%unique activated neurons and the total number of neurons in input \dl
+%system. In this experiment, we compute the neuron coverage of a test
+%cases from \tool and \Cklst on the fine-tuned \sw{first time mention fine-tuning: reader does not know how we fine-tune} \sa model of
+%\bertsamodel and compare the coverage between \tool and \Cklst.
+
+\paragraph{RQ3.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize
+
+\sw{@Simin: add the setup of the bug explanation case study here.}
+%In addition to the detection of bugs \sw{have we defined ``bug" in this context?} in the model,
+%explanation of the bugs is also important for debugging and
+%repairing the model. Therefore, we answer {\bf RQ3} by analyzing the \sa model based on \tool test cases to find the root causes of the bugs.
+%
+%Specifically, we adapt \Denas{} for this experiment. \sw{Say more what DENAS does.} Rules generated from
+%\Denas{} are interpretable functions mapping certain features of the
+%input to the expected output of a deep \nn system, and the generated
+%rules are considered as the behaviors of the deep \nn system. To
+%analyze the bug of a \sa model, we generates rules over the test
+%inputs using \Denas{} and identifies faulty rules for the failed test
+%inputs.
+%\sw{Previous sounds vague. Any specific adaptation of DENAS we did?}
+%We manually identify the root of the faulty rules and find the
+%root causes of bug in the end.
+
+\noindent\textbf{Implementation Details.}
+
+\sw{Missing: environment running these experiments.}
 
@@
 %% epochs and batch size for retraining are 1 and 16 respectively.
+
+%\input{CM/coverage}
+
+%\input{CM/explain}

### 2022-05-02 python/sa/exp/Testcases.py
testcase

@@ -1,0 +1,22 @@
+
+from typing import *
+
+import re, os
+import nltk
+import copy
+import random
+import numpy
+import spacy
+
+from pathlib import Path
+from spacy_wordnet.wordnet_annotator import WordnetAnnotator
+
+from ..utils.Macros import Macros
+from ..utils.Utils import Utils
+from ..utils.Logger import Logger
+
+random.seed(27)
+
+class Testcases:
+
+    

### 2022-05-02 paper/ase22/experiment.tex
exp

@@
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:one}: Can \tool generate test cases with the correct \lc categorization and
-  sentiment label?
-\item \label{rq:two}: Can \tool generate more diverse test cases than \Cklst?
-\item \label{rq:three}: Can \tool be useful to find root causes of bugs in the \sa models?
+\item \label{rq:one}: Can \tool generate consistent test sentence and
+  its oracle?
+\item \label{rq:two}: Is \tool generated testcases relevant to be used
+  for their \lc evaluation?
+\item \label{rq:three}: Can \tool generate more diverse test cases
+  than \Cklst?
+\item \label{rq:four}: Can \tool be useful to find root causes of bugs
+  in the \sa models?
 %% \item \label{rq:three}: How effective is our new test case generation
@@
 
-\sw{Make clear (earlier in the paper): a test case is a sentence in a linguistic capability with a sentiment label.}
+\sw{Make clear (earlier in the paper): a test case is a sentence in a
+  linguistic capability with a sentiment label.}
 
-\paragraph{RQ1.} As described in Section \ref{sec:approach}, \tool generates test cases in
-two steps: specification-based seed generation and syntax-based sentence expansion. These
-automated steps may generate seed/expanded sentences marked with incorrect sentiment labels or categorized into
-wrong linguistic capabilities. For example, the search rule and template defined in a linguistic capability
-may not always generate seed sentences in that capability or with the correct label.
-To answer {\bf RQ1}, we perform a manual study to measure the correctness of the sentiment labels and linguistic capabilities
-associated with the seed/expanded sentences, produced by \tool
+\paragraph{RQ1.} As described in Section \ref{sec:approach},
+\tool generates test cases in two steps: specification-based seed
+generation and syntax-based sentence expansion. These automated steps
+may generate seed/expanded sentences marked with incorrect sentiment
+labels or categorized into wrong linguistic capabilities. For example,
+the search rule and template defined in a linguistic capability may
+not always generate seed sentences in that capability or with the
+correct label.  To answer {\bf RQ1}, we perform a manual study to
+measure the correctness of the sentiment labels and linguistic
+capabilities associated with the seed/expanded sentences, produced by
+\tool
 
-\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated manual study.
-Also, be explicit about the setup: sample size, population size, number of participants, protocol (each given how many sentences, and how disagreement is resolved), etc.}
-In the manual study, we sample a set of test cases and corresponding \lc randomly sampled
-from seed sentences and expanded sentences from \tool. 
-also provided with the sampled test cases. Each subject is asked for
-scoring relevancy between the linguistic capability of the
+\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated
+  manual study. Also, be explicit about the setup: sample size,
+  population size, number of participants, protocol (each given how
+  many sentences, and how disagreement is resolved), etc.}
+
+In the manual study, we sample a set of test cases and corresponding
+\lc randomly sampled from seed sentences and expanded sentences from
+\tool.  also provided with the sampled test cases. Each subject is
+asked for scoring relevancy between the linguistic capability of the
 sentences. The score is discrete and it ranges from 1 to 5

### 2022-05-02 paper/ase22/background.tex
background

@@
 
-\sw{We should motivate the testing of linguistic capabilities. Give
-  background of the work that has been done in CheckList: what
-  capabilities they support and their limitations. Maybe find a
-  motivating example?}
+%% \sw{We should motivate the testing of linguistic capabilities. Give
+%%   background of the work that has been done in CheckList: what
+%%   capabilities they support and their limitations. Maybe find a
+%%   motivating example?}
+
+\begin{figure}[t]
+ \centering
+ \lstinputlisting[language=python-pretty]{code/checklist_template.py}
+ \vspace{-10pt}
+ \caption{\CklstTemplateFigCaption}
+ \vspace{-10pt}
+\end{figure}
+
+In this section, we provide a brief background on \Cklst testcase
+generation via an example. Quality of software is verified by ensuring
+the proper working of all functionalities without knowing the internal
+workings of the software. Knowing performances of model on the
+multiple functionalities provides users with better understanding and
+debugging the software. The same principle applies to the NLP model.
+traditional NLP model evaluation relying on a test set is lack of
+specification of model functionality. However, In NLP domain, there
+are many phenomena on linguistic input such as negation,
+questionization. Given a NLP task, the phenomena determine
+task-relevant output. Traditional evaluation method neglects them,
+thus, it becomes less efficient to detect and analyze which aspect the
+model yields unexpected outcome. To tackle this limitation, \Cklst
+introduces task-dependent \lcs for monitoring model performance on
+each \lc. It assumes that the linguistic phenomena can be represented
+into the model behaviors as they provide what input and output are
+desired and how the model works with them. For each \lc, \Cklst makes
+testcase templates and generate sentences by filling-in the value for
+each placeholder. We show an example of the templates in
+Figure~\ref{code:TempEx}. The templates in the figure is used for
+evaluating a \sa model on \SareqExThree. For the templates defined
+from line~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}
+have placeholders such as ${it}$, ${air_noun}$, ${pos_adj}$. Values
+for the placeholders are defined at
+line~\ref{code:tempex:itbe},~\ref{code:tempex:airnoun:1}
+and~\ref{code:tempex:posadj:1}. Ater all, all combinations of the
+values of placeholders in a template are filled-in the template, and
+the senteneces are generated such as ``The flight is good'', ``That
+airline was happy'' and so on. Finally, these are used for evaluation
+of \lc. Despite its simplicity of testcase generation, it still has
+limitations: it first relies on manual work for defining template
+structure and its values. Therefore, the manual work for testcase
+generation keeps the process costly. Extended from it, Second, such
+manual work produces the imitative forms between test cases, and it is
+likely to introduce bias on the testcases. We will show that these
+observations contribute to the performance of our models.

### 2022-05-02 paper/ase22/experiment.tex
background

@@
 
-In this section, we present the setup of the experiments to evaluate the effectiveness
-of \tool{}. We address the
-following research questions (RQs):
+In this section, we present the setup of the experiments to evaluate
+the effectiveness of \tool{}. We address the following research
+questions (RQs):
 
@@
 
-\paragraph{RQ1.} As described in Section \ref{sec:approach},
+\paragraph{\textbf{RQ1 and RQ2}} As described in Section \ref{sec:approach},
 \tool generates test cases in two steps: specification-based seed
@@
 not always generate seed sentences in that capability or with the
-correct label.  To answer {\bf RQ1}, we perform a manual study to
+correct label.  To answer RQ1 and RQ2, we perform a manual study to
 measure the correctness of the sentiment labels and linguistic
 capabilities associated with the seed/expanded sentences, produced by
-\tool
+\tool.
 
-\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated
-  manual study. Also, be explicit about the setup: sample size,
-  population size, number of participants, protocol (each given how
-  many sentences, and how disagreement is resolved), etc.}
-
-In the manual study, we sample a set of test cases and corresponding
-\lc randomly sampled from seed sentences and expanded sentences from
-\tool.  also provided with the sampled test cases. Each subject is
-asked for scoring relevancy between the linguistic capability of the
-sentences. The score is discrete and it ranges from 1 to 5
-representing ``strongly not relevant'' to ``strongly relevant''
-respectively. Additionally, the subject scores the relevancy between
-sentences and their sentiment labels. The score is also discreate and
-ranges from 1 to 5. It represents ``strongly negative'' to ``strongly
-positive'' respectively. In this work, we collect manual study scores
-from 8 subjects attended. From the collected scores, we measure the
-following metrics:
+In the manual study, we randomly sample three sets of pairs of seed
+sentences and corresponding \lc from seed test cases. For each set, we
+also select expanded sentences that \tool generated from the formerly
+sampled seed sentences. In this experiment, each set has 100 sentences
+(50 from seed sentences and 50 from expanded sentences) and 300
+sentences, in total, are used for the manual study. For each sampled
+set, two subjects are provided with the same set of sampled
+sentences. The subjects are asked for scoring the two following:
+\textbf{1. relevancy score between sentence and its associated \lc}:
+this score measures the amount of appropriateness of the use of
+sentence for evaluating the model on its \lc.  The scores are discrete
+ranging from 1 to 5, and each represents ``strongly not relevant'' to
+``strongly relevant'' respectively. \textbf{2. sentiment score of
+  sentence}: this score measures the level of sentence sentiment. It
+is also discrete, and it ranges from 1 to 5 representing ``strongly
+negative'' to ``strongly positive'' respectively. In this work, we
+collect manual study scores from 6 subjects in total. From the
+collected scores, we measure the following metrics:
 
 \begin{eqnarray}
-  &Reported\:bugs &=\sum_{i} \delta(label_{S^2LCT}!=pred_{model}) \label{metric:rb}\\
-  &Incorrect\:inputs &= \sum_{i} \delta(pred_{model}!=label_{human}) \label{metric:ii}
-  %% &Label\:inconsistency &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:li}
+  sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
+  LC\_relevancy_{AVG} &= \frac{1}{\#data}\cdot\sum_{i} LC\_relevancy_i \label{metric:lcrel}
 \end{eqnarray}
 
-The metrics represents the number of data instance that its label
-assigned from are different between \tool and its model prediction
-(eq~\ref{metric:rb}) and between the model prediction and human
-(eq~\ref{metric:ii}). We show the correspondence between \tool and
-human by computing the precision and recall from the reported bugs and
-incorrect inputs.
-%% and between \tool and human (eq~\ref{metric:li}).
+The equation~\ref{metric:srel} represent the number of test cases that
+their labels assigned from are different between \tool and
+human. Higher number of this metric indicates worse correlation of
+test oracle that \tool generated with human. In addition, the
+equation~\ref{metric:lcrel} represents the average score of the
+relevancy score between sentence and its associated \lc. higer average
+score means that higher human-level agreement of the use of sentence
+for its \lc, resulting in higher suitability of the use of the
+testcases for evaluating model on the \lc. Given the metrics, we
+answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
+and equation~\ref{metric:lcrel} respectively, thereby, show its ability
+of \tool to understand human intelligence.
 
-\paragraph{RQ2.}
+\paragraph{RQ3.}
 Recall that a key limitation of \Cklst is that its template-based
-approach that relies on significant manual efforts may not generate test cases that comprehensively cover the sentences
-in a linguistic capability. \tool, instead, automatically generates test cases based on a search
-dataset and the syntax in a large reference corpus. We expect \tool can generate a more diverse test suite
-than \Cklst. To measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
-where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
-\sw{Why is this a good metric for diversity?}
-Specifically, we use the  \sw{are these metrics we define or are they from ma2018deepgauge?} two coverage metrics in existing work \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), as our metrics to evaluate the test suite diversity.
+approach that relies on significant manual efforts may not generate
+test cases that comprehensively cover the sentences in a linguistic
+capability. \tool, instead, automatically generates test cases based
+on a search dataset and the syntax in a large reference corpus. We
+expect \tool can generate a more diverse test suite than \Cklst. To
+measure diversity, we follow the approach presented by Ma et
+al. \cite{ma2018deepgauge}, where the authors measure the coverage of
+NLP model intermediate states as corner-case neurons.  \sw{Why is this
+  a good metric for diversity?}  Specifically, we use the \sw{are
+  these metrics we define or are they from ma2018deepgauge?} two
+coverage metrics in existing work \cite{ma2018deepgauge},
+\textit{boundary coverage} (BoundCov) and \textit{strong activation
+  coverage} (SActCov), as our metrics to evaluate the test suite
+diversity.
 
@@
 
-To answer {\bf RQ2}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
+To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
 After that, we randomly select 100 \sw{Why 100, not all?} test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
@@
 
-\paragraph{RQ3.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize
+\paragraph{RQ4.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize
 

### 2022-05-02 paper/ase22/code/checklist_template.py

@@ -1,0 +1,33 @@
+air_noun = [(*@\label{code:tempex:airnoun:1}@*)
+    'flight', 'seat', 'pilot', 'staff', 
+    'service', 'customer service', 'aircraft', 'plane', 
+    'food', 'cabin crew', 'company', 'airline', 'crew'
+](*@\label{code:tempex:airnoun:2}@*)
+pos_adj = [(*@\label{code:tempex:posadj:1}@*)
+    'good', 'great', 'excellent', 'amazing', 
+    'extraordinary', 'beautiful', 'fantastic', 'nice', 
+    'incredible', 'exceptional', 'awesome', 'perfect', 
+    'fun', 'happy', 'adorable', 'brilliant', 'exciting', 
+    'sweet', 'wonderful'
+](*@\label{code:tempex:posadj:2}@*)
+neg_adj = [(*@\label{code:tempex:negadj:1}@*)
+    'awful', 'bad', 'horrible', 'weird', 
+    'rough', 'lousy', 'unhappy', 'average', 
+    'difficult', 'poor', 'sad', 'frustrating', 
+    'hard', 'lame', 'nasty', 'annoying', 'boring', 
+    'creepy', 'dreadful', 'ridiculous', 'terrible', 
+    'ugly', 'unpleasant'
+](*@\label{code:tempex:negadj:2}@*)
+
+t = editor.template('{it} {air_noun} {be} {pos_adj}.', (*@\label{code:tempex:template:1}@*)
+                    it=['The', 'This', 'That'], be=['is', 'was'], labels=2, save=True)(*@\label{code:tempex:itbe}@*)
+t += editor.template('{it} {be} {a:pos_adj} {air_noun}.', 
+                     it=['It', 'This', 'That'], be=['is', 'was'], labels=2, save=True)
+t += editor.template('{i} {pos_verb} {the} {air_noun}.', 
+                     i=['I', 'We'], the=['this', 'that', 'the'], labels=2, save=True)
+t += editor.template('{it} {air_noun} {be} {neg_adj}.', 
+                     it=['That', 'This', 'The'], be=['is', 'was'], labels=0, save=True)
+t += editor.template('{it} {be} {a:neg_adj} {air_noun}.', 
+                     it=['It', 'This', 'That'], be=['is', 'was'], labels=0, save=True)
+t += editor.template('{i} {neg_verb} {the} {air_noun}.', 
[…]

### 2022-05-04 python/sa/exp/Humanstudy.py
manul study table

@@ -125,7 +125,7 @@ class Humanstudy:
         return sample_results
     
     @classmethod
-    def write_samples(cls, sample_dict: Dict):
+    def write_samples(cls, sample_dict: Dict, res_dir: Path):
         for f_i in sample_dict.keys():
             seeds, exps = list(), list()
             seed_res = ""
@@ -140,11 +140,8 @@ class Humanstudy:
             for e, r in exps:
                 exp_res += f"{e} :: {r}\n\n\n"
             # end for
-            res_dir = Macros.result_dir / 'human_study'
-            res_dir.mkdir(parents=True, exist_ok=True)
-            print(seed_res)
-            # Utils.write_txt(seed_res, res_dir / f"seed_samples_raw_{f_i}.txt")
-            # Utils.write_txt(exp_res, res_dir / f"exp_samples_raw_{f_i}.txt")
+            Utils.write_txt(seed_res, res_dir / f"seed_samples_raw_{f_i}.txt")
+            Utils.write_txt(exp_res, res_dir / f"exp_samples_raw_{f_i}.txt")
             print(f"{f_i}:\nnum_seed_samples: {len(seeds)}\nnum_exp_samples: {len(exps)}")
         # end for
         return
@@ -543,9 +540,11 @@ class Humanstudy:
                     search_dataset_name,
                     selection_method):
         target_file = Macros.result_dir / f"cfg_expanded_inputs_{nlp_task}_{search_dataset_name}_{selection_method}.json"
+        res_dir = Macros.result_dir / 'human_study' / f"{nlp_task}_{search_dataset_name}_{selection_method}"
+        res_dir.mkdir(parents=True, exist_ok=True)
         sent_dict = cls.read_sentences(target_file)
         sample_dict = cls.sample_sents(sent_dict, num_files=3, num_samples=5)
-        cls.write_samples(sample_dict)
+        cls.write_samples(sample_dict, res_dir)
         return
 
     @classmethod
@@ -556,7 +555,8 @@ class Humanstudy:
                     model_name,
                     num_samples):
         target_file = Macros.result_dir / f"cfg_expanded_inputs_{nlp_task}_{search_dataset_name}_{selection_method}.json"
-        res_dir = Macros.result_dir / 'human_study'
+        res_dir = Macros.result_dir / 'human_study' / f"{nlp_task}_{search_dataset_name}_{selection_method}"
+        res_dir.mkdir(parents=True, exist_ok=True)
         # model_name = "textattack/bert-base-uncased-SST-2"
[…]

### 2022-05-04 python/sa/paper/Tables.py

@@ -46,13 +46,13 @@ class Tables:
             if item == "lc-req":
                 cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
                 cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
-            elif item == "selfbleu":
+            elif item == "selfbleu": # deprecated
                 task = options.pop('task', 'sa')
                 search_dataset = options.pop('search_dataset_name', 'sst')
                 selection_method = options.pop('selection_method', 'random')
                 cls.make_numbers_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
                 cls.make_table_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
-            elif item == "retrain-debug":
+            elif item == "retrain-debug": # deprecated
                 task = options.pop('task', 'sa')
                 search_dataset = options.pop('search_dataset_name', 'sst')
                 selection_method = options.pop('selection_method', 'random')
@@ -60,6 +60,12 @@ class Tables:
                 model_name = options.pop('model_name')
                 cls.make_numbers_retrain(Macros.result_dir, tables_dir, task, search_dataset, selection_method, epochs, model_name)
                 cls.make_table_retrain(Macros.result_dir, tables_dir, task, search_dataset, selection_method, epochs, model_name)
+            elif item == "manual-study":
+                task = options.pop('task', 'sa')
+                search_dataset = options.pop('search_dataset_name', 'sst')
+                selection_method = options.pop('selection_method', 'random')
+                cls.make_numbers_manual_study(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
+                cls.make_table_manual_study(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
             else:
                 cls.logger.warning(f"Unknown table {item}")
             # end if
@@ -339,6 +345,84 @@ class Tables:
         output_file.append(r"\end{center}")
         output_file.append(r"\end{small}")
         output_file.append(r"\vspace{\RetrainDebugTableVSpace}")
+        output_file.append(r"\end{table*}")
+        output_file.save()
+        return
+
+    @classmethoe
+    def make_numbers_manual_study(cls,
+                                  result_dir,
+                                  tables_dir,
+                                  task,
+                                  search_dataset,
+                                  selection_method):
[…]

### 2022-05-04 python/sa/utils/Macros.py

@@ -9,9 +9,9 @@ class Macros:
 
     this_dir: Path = Path(os.path.dirname(os.path.realpath(__file__))) # nlptest/python/utils
     root_dir: Path = this_dir.parent.parent.parent # nlptest/
-    # storage_dir: Path = Path("/glusterfs/data/jxl115330/nlptest")
-    # result_dir: Path = storage_dir / "_results" # /glusterfs/data/jxl115330/nlptest/_results
-    result_dir: Path = root_dir / "_results" # nlptest/_results
+    storage_dir: Path = Path("/glusterfs/data/jxl115330/nlptest")
+    result_dir: Path = storage_dir / "_results" # /glusterfs/data/jxl115330/nlptest/_results
+    # result_dir: Path = root_dir / "_results" # nlptest/_results
     
     download_dir: Path = result_dir / "_downloads" # /glusterfs/data/jxl115330/nlptest/_downloads
     log_dir: Path = result_dir / "_logs" # /glusterfs/data/jxl115330/nlptest/_downloads

### 2022-05-04 paper/ase22/result.tex
add table in result tex

\section{Result}
\label{sec:result}

\subsection{RQ1: Can \tool generate consistent test sentence and
  its oracle?}

\InputWithSpace{tables/manual-study-table}

### 2022-05-04 run_sa.sh
run_sa

@@ -159,14 +159,15 @@ function make_tables() {
         (cd ${_DIR}
          # Table 1
          # python -m python.sa.main --run tables --which lc-req
-         # python -m python.sa.main --run tables --which selfbleu
-         python -m python.sa.main \
-                --run tables \
-                --which retrain-debug \
-                --search_dataset sst \
-                --syntax_selection random \
-                --epochs 5 \
-                --model_name textattack/bert-base-uncased-SST-2
+         # python -m python.sa.main --run tables --which selfbleu # deprecated
+         # python -m python.sa.main \
+         #        --run tables \
+         #        --which retrain-debug \
+         #        --search_dataset sst \
+         #        --syntax_selection random \
+         #        --epochs 5 \
+         #        --model_name textattack/bert-base-uncased-SST-2 # deprecated
+         python -m python.sa.main --run tables --which manual-study
         )
 }
 
@@ -183,10 +184,10 @@ function main() {
         # analyze_retrained_models # to generate debug_results file
         # selfbleu # to compute the selfbleu
         # explain_nlp # to run the explainNLP
-        # make_tables
         # humanstudy
         # humanstudy_results
-        coverage_sent_gen
+        # coverage_sent_gen
+        make_tables
 
 
         # eval_retrained_models # to ...?

### 2022-05-04 paper/ase22/intro.tex
intro

--- 2022-04-18 paper/ase22/intro.tex
@@
 
-Software testing is the essential component of software development
-process.  It evaluates an attribute or capability of the software and
-determines quality of the software by examining the behavior of the
-software.  Software testing in the early stage of the development
-finds bugs, and fixing them saves amount of costs. \Ml (ML) application is a
-primary branch of artifical intelligence software, and testing the application
-also becomes important process for NLP model.
+% In the early stage of the software development process, automated
+% software testing and debugging can identify and fix
+% defects. Therefore, effective software testing assures software
+% quality, and it meets needs of the end user. Nowdays, software at work
+% has elements of \ml (ML). Especially,
 
-In addition, reliable software testing methodology ensures software
-quality to end users in that the software meets requirements by
-verification and validation.
+\Nlp (NLP) applications are growing exponentially.  As a result,
+trustworthiness in the quality of NLP applications has become critical
+for its practical use in the real world.  Therefore, quality assurance
+of NLP applications is an essential process in the software
+development processes.  Traditionally, the prevalent models of NLP are
+evaluated via train-validation-test splits \cite{}.  Training and
+validation sets are used to train the NLP models, and the test set,
+also called \ho set, is used to test the trained model.  The quality
+of these models is estimated into numbers using performance
+metrics. Especially, accuracy (i.e., the fraction of outputs that the
+model correctly predicts) is the most widely used metric for assessing
+the quality of classification models. When comparing two NLP models,
+one is considered better if it has higher accuracy than the other.
 
-Regarding that,
+Researchers aim to improve the current practices of testing NLP models
+from three perspectives: (i) \emph{Test input generation}, (ii)
+\emph{Automated test oracle}, and (iii) \emph{Meaningful quality
+  metrics}.
 
-The prevalent models of NLP are evaluated via train-validation-test
-splits. train and validation set is used to train the NLP model and
-the \ho set is used for testing by measuring accuracy. The accuracy is
-a indicator of the performance of the models.
+\noindent \textbf{Test input generation.} Currently, most testing of
+an NLP model reuses existing large textual corpus as the testing
+dataset to evaluate the model. This practice will often overestimates
+the model performances from the \ho
+set~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
+  marcoACL2020checklist}.  The overestimation comes from the
+discrepancy between distribution of the used dataset and actual data
+distribution in real world. Oftentimes, the \ho dataset is not
+representative and it is likely to introduce specific biases. Such
+biases lead to make the model delicated to out-of-distribution and
+decrease robustness of model in the end. In this regards, prior works
+have proposed techniques for testing NLP model robustness by crafting
+adversarial examples and attacking a model with them intentionally
+\cite{ribeiro2018sear,belinkov2018breaknmt,
+  rychalska2019wildnlp,iyyer2018adversarial}. \TODO{Jaeseong, mention
+  and cite adversarial testing techniques here.} \jl{done.}
 
-Despite its usefulness, the main limitation of the testing paradigm
-is that the \ho set often overestimates the performances. Each dataset
-comes with specific biases, and the biases increase the discrepancy of
-distribution between dataset and
-real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
-on \ho set does not consider the discrepancy and it is limited to
-achieve comprehensive performrance of the NLP model. As a consequence,
-it is difficult to analyze where the errors comes
-from~\cite{wu2019errudite}.
+\noindent \textbf{Automated test oracle.} The current testing practice
+requires manual work for labelling the test oracles of the \ho
+data. The manual work is costly in terms of time consumption and its
+impact on market price. Therefore, it necessitates automated test
+oracle generation for improving the testing process of NLP
+models. However, validity of the automation is ensured by the
+correctness of test oracle. Auto-generated test orcle may not always
+be feasible; predicting the correct test oracle is one of main
+challenges to gaurantee its practical use. Along with this, software
+metamorphic testing approach has been
+introduced~\cite{segura2016metamorphictest} to alleviate the test
+oracle discrepancy between expected and observed test oracle.
+\TODO{Describe and Add citations to metamorphic testing techniques
+  here}\jl{done.}
 
-On the subject of the limitation of traditional testing paradigm, a
-number of methods have been proposed. First, multiple diagnostic
-datasets for evaluating NLP model were introduced for obtaining
-generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
-that, model is evaluated on different aspects such as robustness of
-the model on adversarial
-sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial},
-fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
-consistancy~\cite{ribeiro2019consistencyeval}, prediction
-interpretations~\cite{ribeiroSG16lime} and interactive error
-analysis~\cite{wu2019errudite}. Especially, \Chlst implements
-behavioral testing methodolgy for evaluating multiple linguistic
-capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
-introduces input-output behaviors of linguistic capabilities and
-generates behavior-guided inputs for validating the behaviors. It
-provides comprehensive behavioral testing of NLP models through a
-number of generated inputs. However, the approach only relies on
-manually generated input templates, thus the template generation
-becomes expensive and time consuming. In addition, the generated
-templates are selective and often too simple, and it is limited to
-provide restricted evaluation of linguistic capabilities. Thus, it
-does not garauntee the comprehensive evaluation.
+%% \sw{Not sure what overestimate means here}
+%  In addition, the inconsistency between test input and
+% its oracle causes biases. Such biases increase the discrepancy of
+% distribution between the dataset and real-world data.
+\noindent \textbf{Meaningful quality metrics.}  As discussed, accuracy
+is the most widely used quality metric for measuring NLP model
+performance. Forced aggregation statistics into a single number makes
+the user difficult to assess the capability of NLP models.  Not to
+mention localizing and fixing the bugs found from the \ho
+set. Therefore, this forced aggregation method not only fails to
+validate model behaviors, but it also makes the localization of the
+causes of the inaccuracy more costly~\cite{wu2019errudite}.
+% Therefore behavioral testing
+% approach provides the better ability to examine the inaccuracy and
+% find the bugs in the model.
+To address this limitation,
+% several approaches have been proposed to
+% evaluate different aspects of the NLP models, such as , model coverage
+% \cite{rottger2020hatecheck}, and fairness
+% \cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition, For example, Testing model coverage
+% only shows model behaviors, but not the model performance on existing
+% testing set. The fairness and robustness testing only focus on only
+% one model capability resulting in its limited comprehensiveness. In
+% addition,
+Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
+evaluating NLP model on multiple linguistic
+capabilities~\cite{marcoACL2020checklist}. \Cklst defines
+task-relevant linguistic capabilities and generates test cases for
+each \lc.
 
-In this paper, we present \Model, an automated NLP model evaluation
-method for comprehensive behavioral testing of NLP models on \sa
-task. For each behavior of linguistic capability, \Model does not rely
-on the manual input generation. Instead, it establishes input
-requirement for evaluating a linguistic capability and finds suitable
-inputs that meet the requirement from existing public dataset.
-Therefore, \Model increases input diversity and generality. Further,
-\Model applies the fuzzing testing principle to generate inputs by
-mutating the selected inputs as seed inputs. Fuzzer in \Model first
-expands seed input grammar structures and determines its available
-\pos to maintain structural naturalness. After that, to hold
-contextual naturalness of the mutated inputs, the fuzzer completes the
-expanded new structures via data-driven context-aware word
-suggestion. Additionally, sentiment-independent words in the inputs
-are replaced with rule-based word suggestion.
+However, none of the above approaches satisfy all three requirements
+at the same time. First, prior adversarial testing approaches merely
+focus on evaluating model robustness. These measure how much model is
+sensetive to the output on which input perturbations while limited to
+provide evaluation on linguistic functionalities of interests in
+real-world. In addition, the metamorphic testing approach is required
+to understand characteristics of metamorphic relations between input
+and output.  However, finding these is one of the most challenging
+problem in the metamorphic
+testing~\cite{segura2016metamorphictest}. Along with this, such
+relations in textual data in NLP domain has not been evaluated despite
+its importance. \TODO{Describe the limitation of adversarial testing
+  and Metamorphic testing} \jl{done.}
+
+Specifically, \Cklst relies on manually generated input templates,
+which need to be preset before test input generation. Consequently,
+\Cklst templates are distributed in a limited range of their
+structures. This restricts \Cklst's ability to comprehensively test
+the linguistic capabilities.
+
+Despite \Cklst's limitations, assessing the quality of NLP models
+through the linguistic capabilities is a promising direction. Each \lc
+explains the functionality of the input and output behavior for the
+NLP model under test. Typically, it describes certain type of inputs
+and outputs observed in real world for the target NLP task ranging
+from simple to complicated behaviors, so the model developers can
+better understand the capabilities and potential issues of the NLP
+models. For example, a linguistic capability of ``Negated neutral
+should still be neutral'' measures how accurately the \sa model
+understands the negative neutral input as an neutral sentiment
+\cite{marcoACL2020checklist}.  Therefore, it requires the \sa model to
+output neutral sentiment on the negated neutral input.  Such
+methodology of evaluation on the specified functionalities avoids the
+overestimation of the model performance as it equivalently measures
+the model performance on each functionality.
+% ,and the separate model performance
+% explain distribution of the performance over the linguistic capabilities
+In the end, testing through linguistic capabilities provides not only
+the overall model performance, but also the malfunction facets of the
+model.
+
+To satisfy all three requirements mentioned above, we present \tool,
+an automated NLP model evaluation method for comprehensive behavioral
+testing of NLP models on \sa task.  There are three main challenges
+that \tool overcomes to satisfy all three aforementioned requirements.
+\begin{description}
+\item[{\bf C1}] The test suite should cover diverse syntactic structures;
+\item[{\bf C2}] Each test case should be categorized into a \lc;
+\item[{\bf C3}] The label of each test case should be automatically
+  and accurately defined.
+\end{description}
+
+\TODO{adding detail description about challenges}
+
+\noindent \textbf{C1.} We first address increasing input
+representiveness. Compared with templates used in \Cklst, \tool
+instead establishes input requirement for evaluating a linguistic
+capability and finds suitable inputs that meet the requirement from
+existing public dataset. In this process, \tool applies the fuzzing
+testing principle to generate inputs by mutating the selected inputs
+as seed inputs. Fuzzer in \tool first expands seed input grammar
+structures and determines its available \pos to maintain structural
+naturalness.
+
+% After that, to hold contextual naturalness of the mutated
+% inputs, the fuzzer completes the expanded new structures via
+% data-driven context-aware word suggestion. Additionally,
+% sentiment-independent words in the inputs are replaced with rule-based
+% word suggestion. Further, we address the manual input generation
+% process by automating the process mentioned above.
+
+\noindent \textbf{C2.} Morover, we adopts behavioral model testing
+method by introducing multiple behaviors from \lcs on \sa task and
+generating inputs relevant to each \lc. Each test case provides not
+only correcteness of model prediction on it, but \lc on the test case
+also gives infromation about classification on the model
+performance. Therefore assigning appropriate \lc for each testcase
+alleviates overestimation of model testing results.
+
+\noindent \textbf{C3.} Lastly, we show the appropriateness of test
+orable that \tool automatically generated by manual study of generated
+test cases. Aggreement of input-output relations between human and
+\tool is crucial to increase trustworthiness of model. In this manner,
+reliabilty of model for its practical use can be achieved in the end.
 
@@
 \Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
-We show that
+We show that ...
+
+% \section{Introduction}
+% \label{sec:intro}
+
+% Software functional testing is an essential component of the software development
+% process. It evaluates an attribute of the software and
+% determines the correctness by comparing the actual and the expected behaviors.
+\sw{Should we lead with this paragraph?
+We are talking about functional testing here but next we say NLP uses train-validation-test.}
+% Automated software
+% testing and debugging in the early stage of the development process can identify and fix defects. Therefore,
+% effective software testing assures software quality, and
+% it meets needs of the end user.
+
+% Meanwhile, the trustworthiness in
+% quality of \nlp (NLP) application has become an important component for
+% its practical use in real world. Traditionally, the prevalent models
+% of NLP are evaluated via train-validation-test splits \cite{}. Training and
+% validation set are used to train the NLP models and the \ho set is used
+% for testing. Accuracy is often used as the performance
+% metric of the models \cite{}, i.e., a model is considered better if it has higher
+% accuracy than another model.
+% Despite its simplicity and usefulness, this testing paradigm often
+% overestimates \sw{Not sure what overestimate means here} the performances from the \ho set. Oftentimes, the \ho dataset is not representative and it is likely to introduce specific
+% biases. Such biases increase the discrepancy of distribution between
+% the dataset and real-world data~\cite{recht2019imagenetbias}. Therefore, making this testing method fail to measure the comprehensive performance of the NLP
+% models. In addition, the accuracy metric does not validate
+% certain behaviors of the model; as a result, it still is costly to localize the causes of the inaccuracy~\cite{wu2019errudite}.
+
+% To address these challenges, several approaches have
+% been proposed to evaluate different aspects of the NLP models,
+% such as robustness on adversarial examples \cite{}, model coverage \cite{}, and
+% fairness \cite{}.  Especially, Ribeiro~\etal introduced \Chlst, a
+% behavioral testing framework for evaluating NLP model on multiple
+% linguistic capabilities~\cite{marcoACL2020checklist}. \Chlst defines
+% task-relevant linguistic capabilities and generates testcases for each \lc.
+% However, the approach relies on manually generated input
+% templates; thus, the template generation becomes expensive and time
+% consuming. In addition, only a few simple templates are used by \Chlst, limiting its ability to comprehensively test the linguistic capabilities.
+
+% Despite the limitations\jl{this paragraph, how about mentioning checklist first and limitations and our model?}, \Chlst's approach of testing the linguistic capabilities is a promising direction.
+Each \lc explain the functionality
+% of the input and output behavior for the NLP model under test. \sw{For example, ...} The
+% expected behavior is determined by combining the input and output
+% scopes specified on the \lc. \sw{Not sure what the last sentence means.} Typically, it describes certain type of
+% input and outputs observed in real world for the target NLP task
+% ranging from simple to complicated behaviors so that they are able to
+% evaluate the NLP model comprehensively. \sw{For example, ...} Such evaluation on the
+% specified functionalities avoids the overestimation of the model
+% performance as it equivalently measures the model performance on each
+% functionality, and the separate model performance explain distribution
+% of the performance over the linguistic capabilities. In the end, it provides not only the
+% overall model performance, but also the malfunction facets of the
+% model. However, the prior work currently generated model. \sw{This paragraph can be moved before the limitations of \Chlst (last paragraph)? I will make the description more concrete.}
+
+% In this paper, we present \tool, an automated NLP model evaluation
+% method for comprehensive behavioral testing of NLP models on \sa
+% task. For each behavior of linguistic capability, \tool does not rely
+% on the manual input generation.
+\sw{Make sure this paragrpah is consistent with our approach description in Section 3.
+Also, make clear in this paragraph: what challenges/limitations from CheckList we address and how.} Instead, it establishes input
+% requirement for evaluating a linguistic capability and finds suitable
+% inputs that meet the requirement from existing public dataset.
+% Therefore, \tool increases input diversity and generality. Further,
+% \tool applies the fuzzing testing principle to generate inputs by
+% mutating the selected inputs as seed inputs. Fuzzer in \tool first
+% expands seed input grammar structures and determines its available
+% \pos to maintain structural naturalness. After that, to hold
+% contextual naturalness of the mutated inputs, the fuzzer completes the
+% expanded new structures via data-driven context-aware word
+% suggestion. Additionally, sentiment-independent words in the inputs
+% are replaced with rule-based word suggestion.
+
+% We demonstrate its generality and utility as a NLP model evaluation
+% tool by evaluating well-known \sa models: \Bert~\cite{devlin2019bert},
+% \Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
+% We show that ...
+
+% Contributions:
+
+% \jl{test oracle relevancy, and relevancy of testcase with lc}

### 2022-05-05 paper/ase22/approach.tex
background
modify appraoch

@@
 \section{Specification- and Syntax-based Linguistic Capability Testing}
-%% \label{sec:approach}
+\label{sec:approach}
 
-\begin{figure*}
+\begin{figure*}[t]
   \centering
@@
 
-\sw{Some paragraphs in this overview part should go earlier in the
-  paper. I am just writing them here for now as I don't think we have
-  them in the intro/background yet.}  We design and implement
+% \sw{Some paragraphs in this overview part should go earlier in the
+%   paper. I am just writing them here for now as I don't think we have
+%   them in the intro/background yet.}
+
+We design and implement a new NLP model testing method,
 \emph{Specification- and Syntax-based Linguistic Capability Testing
-  (\tool{})} to automatically generate test cases to test the
-robustness of sentiment analysis models. We identify four goals for a
-large and effective test suite:
+  (\tool{})}, that automatically generate test cases with oracles to
+test the robustness of sentiment analysis models. \tool{} addresses
+all three challenges discussed above.
 
-\begin{description}
-\item[{\bf G1}] the test suite should contain realistic \sents;
-\item[{\bf G2}] the test suite should cover diverse syntactic structures;
-  \item[{\bf G3}] each test case should be
-categorized into a \lc;
-\item[{\bf G4}] the label of each test case should be
-automatically and accurately defined.
-\end{description}
+% We identify four goals for a
+% large and effective test suite:
 
-\Cklst's templates generate complete and realistic \sents, and each
-template maps to a \lc, satisfying {\bf G1} and {\bf
-  G3}. But \Cklst only uses \sw{X} manually created templates to
-generate its test suite; all test cases generated by the same template
-share the same syntactic structure, thus violating {\bf G2}. In
-addition, the label of each \Cklst test case has to be decided
-manually, associated with each template, violating {\bf G4}.
+% \begin{description}
+% \item[{\bf G1}] the test suite should contain realistic \sents;
+% \item[{\bf G2}] the test suite should cover diverse syntactic structures;
+%   \item[{\bf G3}] each test case should be
+% categorized into a \lc;
+% \item[{\bf G4}] the label of each test case should be
+% automatically and accurately defined.
+% \end{description}
 
-We present \tool{}, a new \lc test case generation
-tool, that satisfies all of these criteria.  \sw{I could not summarize
-  a cohesive idea that drives our design. Leaving it here to fill in.
-  Also, I felt my writing below still lacks justification for some
-  design choices (e.g., why we do the differentiation).}
+% \Cklst's templates generate complete and realistic \sents, and each
+% template maps to a \lc, satisfying {\bf G1} and {\bf
+%   G3}. But \Cklst only uses \sw{X} manually created templates to
+% generate its test suite; all test cases generated by the same template
+% share the same syntactic structure, thus violating {\bf G2}. In
+% addition, the label of each \Cklst test case has to be decided
+% manually, associated with each template, violating {\bf G4}.
+
+% We present \tool{}, a new \lc test case generation
+% tool, that satisfies all of these criteria.  \sw{I could not summarize
+%   a cohesive idea that drives our design. Leaving it here to fill in.
+%   Also, I felt my writing below still lacks justification for some
+%   design choices (e.g., why we do the differentiation).}
 Figure~\ref{fig:overview} shows the overview of \tool{}, which
@@
   generation} phase performs rule-based searches from a real-world
-dataset ({\bf G1}) and template-based transformation to obtain the
-initial seed \sents.  The search rules (e.g., search for \neu
-\sents that do not include any \pstv or \ngtv words) and
-transformation templates (e.g., \sw{add an example} \jl{\sent
-  negation}) are defined in the \emph{\lc
-  specifications}, which guarantee that each resulting seed conforms
-to a specific \lc ({\bf G3}) and is labelled
-correctly ({\bf G4}).
+dataset and template-based transformation to obtain the initial seed
+\sents.  The search rules (e.g., search for \neu \sents that do not
+include any \pstv or \ngtv words) and transformation templates (e.g.,
+negating a sentence) are defined in the \emph{\lc specifications},
+which guarantee that each resulting seed conforms to a specific \lc
+({\bf C2}) and is labelled correctly ({\bf C3}).
 
-The \emph{syntax-based \sent expansion} phase expands the seed
-\sents with additional syntactic elements (i.e., words
-\sw{more?}\jl{and production ruls in \cfg}) to cover many real-world
-syntactic structures ({\bf G2}). It first performs a syntax analysis
-to identify the \pos (PoS) tags that can be inserted to each
-seed, by comparing the PoS parse trees between the seed \sent and
-many other \sents from a large reference dataset. Each identified
-tag is inserted into the seed as a \emph{mask}. It then uses an NLP
+The \emph{syntax-based \sent expansion} phase expands the seed \sents
+with additional syntactic elements (i.e., words) to cover many
+real-world syntactic structures ({\bf C1}). It first performs a syntax
+analysis to identify the \pos (PoS) tags that can be inserted to each
+seed, by comparing the PoS parse trees between the seed \sent and many
+other \sents from a large reference dataset. Each identified tag is
+inserted into the seed as a \emph{mask}. It then uses an NLP
 recommendation model (i.e., BERT \cite{}) to suggest possible
@@
 specification which additionally defines the rules for expansion
-(e.g., the expanded word should be \neu), {\bf G3} and {\bf G4} are
+(e.g., the expanded word should be \neu), {\bf C2} and {\bf C3} are
 still satisfied. Last, because some validated \sents may include
-unacceptable suggested words given the context \sw{is this the
-  right motivation to do selection?} \jl{I edited the \sent. please
-  let me know if it is clear}, we use a heuristic (i.e., the
-confidence score from the NLP recommendation model) to select the more
-realistic context-aware expanded \sents into \tool{}'s test suite.
+unacceptable suggested words given the context, we use a heuristic
+(i.e., the confidence score from the NLP recommendation model) to
+select the more realistic context-aware expanded \sents into \tool{}'s
+test suite.
 
@@
 specification, and then transforming the matched \sents using
-templates to generate seed \sents that conform to individual
-\lcs. The reasons for this design choice are twofold.  First, while
-generally judging which \lc any \sent falls into and which label it
-should have is infeasible, there exist simple rules and templates to
-allow classifying the resulting \sents into individual \lcs and
-with the correct labels, with high confidence.  This enables us to
-test each \lc individually.  Second, searching from a real-world
-dataset ensures that the \sents used as test cases for testing \lcs
-are realistic and diverse. The diverse test cases are more likely to
-achieve a high coverage of the target model's functionality in each
-\lc, thus detecting more errors.
+templates to generate seed \sents that conform to individual \lcs. The
+reasons for this design choice are twofold.  First, while generally
+judging which \lc any \sent falls into and which label it should have
+is infeasible, there exist simple rules and templates to allow
+classifying the resulting \sents into individual \lcs and with the
+correct labels, with high confidence.  This enables us to test each
+\lc individually.  Second, searching from a real-world dataset ensures
+that the \sents used as test cases for testing \lcs are realistic and
+diverse. The diverse test cases are more likely to achieve a high
+coverage of the target model's functionality in each \lc, thus
+detecting more errors.
 %
-In this phase, \tool first search and selects \sents applicable to
-the \lc in a given real-world dataset with search rules. In case that
-the search rules only fulfill portion of the \lc specifications, the
-selected \sents are not yet appropriate to become seed, we
-transform the selected \sents into seed \sents using the
-heuristic templates.
+In this phase, \tool first search and selects \sents applicable to the
+\lc in a given real-world dataset with search rules. In case that the
+search rules only fulfill portion of the \lc specifications, the
+selected \sents are not yet appropriate to become seed, we transform
+the selected \sents into seed \sents using the heuristic templates.
 %
@@
 models are evaluated in the scope of short \sents with selective
-sentiment words. It does not require any guidance for its
-transformation because the search rule alone is sufficient to conform
-to the \lcs. On the other hand, search rules of LC3 and LC4 are not is
-not enough to match their \lc specification, thus \tool uses heuristic
-templates to conform the found \sents to the \lc. For example, the
-selected \sents becomes seeds by preturbing them with the templates
-and by negating the selected demonstrative \sents to conform to LC3
-and LC4 respectively (see the third and forth rows in
-Table~\ref{tab:specification}).
-\sw{@Jaeseong: revise the rest of 3.1 based on
-  Table~\ref{tab:specification}. I commented out the old text but it
-  is still in the tex file.} \jl{I revised and added the explanation}
+sentiment words. It does not require any transformation because the
+search rule alone is sufficient to conform to the \lcs. On the other
+hand, search rules of LC3 to LC11 are not enough to match their \lc
+specification, thus \tool uses heuristic templates to conform the
+searched \sents to the \lc. For example, in LC3's transformation
+template, the searched \sents become seeds by preturbing them with the
+defined templates.  In LC4's transformation template, the searched
+demonstrative sentences are negated.
+% \sw{@Jaeseong: revise the rest of 3.1 based on
+%   Table~\ref{tab:specification}. I commented out the old text but it
+%   is still in the tex file.} \jl{I revised and added the explanation}
 
@@
 cover. To address this limitation, the syntax-based \sent expansion
-phase extends the seed \sents to cover syntactic structures
-commonly used in real-life \sents. Our idea is to differentiate the
-parse trees between the seed \sents and the reference \sents
-from a large real-world dataset. The extra PoS tags in the reference
-parse trees are identified as potential syntactic elements for
-expansion and inserted into the seed \sents as masks. We then use
-masked language model to suggest the fill-ins. If the resulting
-\sents still conform to the \lc specification,
-they are added to \tool{}'s test suite. \sw{May have some redundancy
-  and inconsistency with the overview part.}
+phase extends the seed \sents to cover syntactic structures commonly
+used in real-life \sents. Our idea is to differentiate the parse trees
+between the seed \sents and the reference \sents from a large
+real-world dataset. The extra PoS tags in the reference parse trees
+are identified as potential syntactic elements for expansion and
+inserted into the seed \sents as masks. We then use masked language
+model to suggest the fill-ins. If the resulting \sents still conform
+to the \lc specification, they are added to \tool{}'s test suite.
 
@@
 population of the masked \sents, and it efficiently shows the
-usefulness of the \tool.  \sw{Add justification: why we need to select
-  k masked \sents (performance?)  and why random makes sense.} \jl{I
-  added the statement for it}
+usefulness of the \tool.
 
@@
 token, multiple words are suggested ranked by their confidence scores.
-\sw{Algorithm 1 does not require we only have one mask in the masked
-  \sent. Can the model suggest multiple words at the same time?}
-\jl{yes. it can predict multiple masked tokens at the same time.}
-\sw{Say a bit more about the BERT model suggestion. E.g., it may
-  suggest multiple words for the same mask but they are ranked?}
-\jl{I added the explanation of BERT}
+% \sw{Algorithm 1 does not require we only have one mask in the masked
+%   \sent. Can the model suggest multiple words at the same time?}
+% \jl{yes. it can predict multiple masked tokens at the same time.}
+% \jl{I added the explanation of BERT}
 %
-Because BERT model is not aware of the \lc
-specification and the grammar symbol in the expanded parse tree, an
-expanded \sent using the suggested words may no longer satisfy the
-\lc specification. Therefore, we perform validation
-on the suggested words and only accept them if the following three
-criteria are met.
+Because BERT model is not aware of the \lc specification and the
+grammar symbol in the expanded parse tree, an expanded \sent using the
+suggested words may no longer satisfy the \lc
+specification. Therefore, we perform validation on the suggested words
+and only accept them if the following three criteria are met.
 
@@
 we use \spacy, a free open-source library for \nlp, for extracting PoS
-tags for each suggested word.\sw{Say how we obtain the PoS tag of a
-  suggested word.}\jl{I added it} Second, it is required that the
-sentiment of the expanded \sent becomes the same as the seed \sent. To
-ensure this, the suggested words must be \neu.  \sw{Should we present
-  this as part of specification, called expansion rule?} \jl{I did it
-  because I think that there is no issue on mentioning it and that is
-  how we assumed and did} Third, we additionally verify that the
-expanded \sents satisfied the same search rules for the seed
-\sent. Our goal for generating the expanded \sents is to use them for
-evaluating the \sa models on the associated \lc in addition to the
-seed \sent. It is only achieved when the expanded \sents are also met
-with the same search rules for the \lc. For LC1 as an example, the
-expanded \sent must still conform to the specification of the seed's
-\lc specification. Therefore, the expanded \sents are required to be
-short and to only have \neu adjectives and \nns. \sw{Say why we use
-  the third criteria only for LC1 and LC2.}  \jl{I added the
-  explanation}
+tags for each suggested word.
+
+Second, it is required that the sentiment of the expanded \sent
+becomes the same as the seed \sent. To ensure this, the suggested
+words must be \neu.
+
+Third, we additionally verify that the expanded \sents satisfied the
+same search rules for the seed \sent in LC1 and LC2. This criteria
+cannot be applied to other linguistic capabilities because they have
+additional transformation templates.
+
+In this work, out of the BERT suggested words, we randomly selects
+words that matches their PoS tag of the expanded symbol in the parse
+tree. The words that meets the second and third criteria are finally
+employed for the expanded \sents.
+% Our goal for generating the expanded \sents is to use them for
+% evaluating the \sa models on the associated \lc in addition to the
+% seed \sent. It is only achieved when the expanded \sents are also met
+% with the same search rules for the \lc. For LC1 as an example, the
+% expanded \sent must still conform to the specification of the seed's
+% \lc specification. Therefore, the expanded \sents are required to be
+% short and to only have \neu adjectives and \nns.
+% \sw{Say why we use
+%   the third criteria only for LC1 and LC2.}  \jl{I added the
+%   explanation}
 
 \paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
-by BERT. For this masked \sent, BERT suggested six words. Each word
-is associated with the confidence score provided by BERT, the PoS tag,
+by BERT. For this masked \sent, BERT suggested six words. Each word is
+associated with the confidence score provided by BERT, the PoS tag,
 and the sentiment. Among the six words, only ``ways'' and ``things''
 are validated by \tool{} because they have the Pos tag ``NNS'' and are
-\neu. In addition, it is found that both \sents meets the search
-rule of the associated \lc of \SareqExOne. In the end, two \sents
-of ``Or both ways'' and ``Or both things'' are generated.  \sw{Do we
-  also check if the expanded \sent meets the
-  specification?}\jl{Yes. I added the explanation of validation of \lc
-  \req}
+\neu. In addition, it is found that both \sents meets the search rule
+of the associated \lc of \SareqExOne. In the end, two \sents of ``Or
+both ways'' and ``Or both things'' are generated.
 
@@
 
-\subsubsection{\Sent Selection}
-\sw{@Jaeseong: Add how we select expanded \sents and motivate why.}
-After 
-\paragraph{Running example.} \sw{Refer to the example to say how we
-  use the BERT score to select.} \jl{I dont think we need this
-  subsection of \sent selection it is already explained at the
-  previous stage with running example.}
+% \subsubsection{\Sent Selection}
+% \sw{@Jaeseong: Add how we select expanded \sents and motivate why.}
+
+%% \paragraph{Running example.} \jl{I dont think we need this
+%%   subsection of \sent selection it is already explained at the
+%%   previous stage with running example.} \sw{This is to use the bert score to rank and select. Did we discuss this already?}

### 2022-05-05 python/sa/main.py
add analyze checklist

@@ -147,17 +147,28 @@ def run_retrain():
 def run_analyze():
     from .model.Result import Result
     nlp_task = args.nlp_task
-    selection_method = args.syntax_selection
     search_dataset_name = args.search_dataset
-    result_file = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_results.txt'
-    template_file = Macros.result_dir / f"cfg_expanded_inputs_{nlp_task}_{search_dataset_name}_{selection_method}.json"
-    save_to = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_result_analysis.json'
-    Result.analyze(
-        result_file,
-        Macros.sa_models_file,
-        template_file,
-        save_to
-    )
+    selection_method = args.syntax_selection
+    test_baseline = args.test_baseline
+    if test_baseline:
+        result_file = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_results_checklist.txt'
+        save_to = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_result_checklist_analysis.json'
+        Result.analyze(
+            result_file,
+            Macros.sa_models_file,
+            save_to
+        )
+    else:
+        result_file = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_results.txt'
+        template_file = Macros.result_dir / f"cfg_expanded_inputs_{nlp_task}_{search_dataset_name}_{selection_method}.json"
+        save_to = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_result_analysis.json'
+        Result.analyze(
+            result_file,
+            Macros.sa_models_file,
+            template_file,
+            save_to
+        )
+    # end if
     return
 
 def run_retrain_analyze():

### 2022-05-05 python/sa/model/Result.py

@@ -25,6 +25,29 @@ class Result:
         return model_results
 
     @classmethod
+    def get_model_checklist_results_from_string(cls, result_str, model_name):
+        p = re.compile(
+            f">>>>> MODEL: {model_name}(.*?)?\n<<<<< MODEL: {model_name}",
+            re.DOTALL
+        )
+        model_results_str = [m.strip() for m in p.findall(result_str)]
+        model_results = list()
+        for m in model_result_str[0].split('\n\n\n'):
+            pattern = '(.*?)?\nTest cases\:'
+            p = re.compile(pattern, re.DOTALL)
+            req_search = p.search(m)
+            lc = req_search.group(1).splitlines()[-1]
+            if lc in Macros.CHECKLIST_LC_LIST:
+                model_results.append({
+                    'lc': lc,
+                    'pass': cls.get_pass_sents_from_model_string(m),
+                    'fail': cls.get_fail_sents_from_model_string(m)
+                })
+            # end if
+        # end for
+        return model_results
+
+    @classmethod
     def get_requirement_from_string(cls, model_result_str, task):
         req_search = re.search(f"Running {task}::([A-Z]+)::(.*)", model_result_str)
         if req_search:
@@ -100,12 +123,59 @@ class Result:
         return results
 
     @classmethod
+    def parse_model_on_checklist_results(cls, result_str, model_name, task):
+        results = list()
+        model_results = cls.get_model_checklist_results_from_string(result_str, model_name)
+        temp_dict = dict()
+        for r in model_results:
+            if r['lc'] in Macros.CHECKLIST_LC_LIST[8:10]:
+                lc = str(Macros.CHECKLIST_LC_LIST[8:10])
+                if r['lc'] not in temp_dict.keys():
+                    temp_dict[lc] = {
+                        'req': lc,
+                        'pass': r['pass'],
+                        'fail': r['fail']
+                    }
+                else:
+                    temp_dict[lc]['pass'].extend(r['pass'])
+                    temp_dict[lc]['fail'].extend(r['fail'])
+                    results.append({
+                        'req': lc,
+                        'pass': temp_dict[lc]['pass'],
+                        'fail': temp_dict[lc]['fail']
+                    })
+                # end if
+            else:
+                lc = Macros.LC_MAP[r['lc']]
+                results.append({
+                    'req': lc,
+                    'pass': r['pass'],
+                    'fail': r['fail']
+                })
+            # end if
+        # end for
+        return results
+
+    @classmethod
[…]

### 2022-05-05 python/sa/paper/Tables.py

@@ -30,7 +30,7 @@ class Tables:
     LATEX_SYMBOL_MAP = {
         '&': '\&', '{': '\{', '}': '\}', '_': '\_'
     }
-
+    
     @classmethod
     def make_tables(cls, **options):
         paper_dir: Path = Macros.paper_dir

### 2022-05-05 run_sa.sh

@@ -82,8 +82,16 @@ function eval_retrained_models() {
 function analyze_eval_models() {
         # evaluate NLP models with generated testsuites
         (cd ${_DIR}
-         python -m python.sa.main --run analyze --search_dataset sst --syntax_selection random
-         python -m python.sa.main --run analyze --search_dataset sst --syntax_selection bertscore
+         # python -m python.sa.main \
+         #        --run analyze \
+         #        --search_dataset sst \
+         #        --syntax_selection random
+         python -m python.sa.main \
+                --run analyze \
+                --search_dataset sst \
+                --syntax_selection random \
+                --test_baseline
+         # python -m python.sa.main --run analyze --search_dataset sst --syntax_selection bertscore
          # python -m python.sa.main --run analyze --search_dataset sst --syntax_selection noselect
         )
 }
@@ -184,9 +192,9 @@ function main() {
         # analyze_retrained_models # to generate debug_results file
         # selfbleu # to compute the selfbleu
         # explain_nlp # to run the explainNLP
-        # humanstudy
-        # humanstudy_results
-        # coverage_sent_gen
+        # humanstudy # sample sentences for manual study
+        # humanstudy_results # get results of manual study into human_study.json
+        # coverage_sent_gen # get sentences for coverage experiment
         make_tables
 
 

### 2022-05-05 python/sa/main.py
debug

@@ -153,7 +153,7 @@ def run_analyze():
     if test_baseline:
         result_file = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_results_checklist.txt'
         save_to = Macros.result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_result_checklist_analysis.json'
-        Result.analyze(
+        Result.analyze_checklist(
             result_file,
             Macros.sa_models_file,
             save_to

### 2022-05-05 python/sa/model/Result.py

@@ -32,7 +32,7 @@ class Result:
         )
         model_results_str = [m.strip() for m in p.findall(result_str)]
         model_results = list()
-        for m in model_result_str[0].split('\n\n\n'):
+        for m in model_results_str[0].split('\n\n\n'):
             pattern = '(.*?)?\nTest cases\:'
             p = re.compile(pattern, re.DOTALL)
             req_search = p.search(m)

### 2022-05-05 python/sa/model/Result.py
debugging

@@ -129,8 +129,9 @@ class Result:
         temp_dict = dict()
         for r in model_results:
             if r['lc'] in Macros.CHECKLIST_LC_LIST[8:10]:
-                lc = str(Macros.CHECKLIST_LC_LIST[8:10])
-                if r['lc'] not in temp_dict.keys():
+                lc = Macros.LC_MAP[str(Macros.CHECKLIST_LC_LIST[8:10])]
+                print(lc)
+                if lc not in temp_dict.keys():
                     temp_dict[lc] = {
                         'req': lc,
                         'pass': r['pass'],

### 2022-05-05 python/sa/paper/Tables.py
table

@@ -71,7 +71,7 @@ class Tables:
                 search_dataset = options.pop('search_dataset_name', 'sst')
                 selection_method = options.pop('selection_method', 'random')
                 cls.make_numbers_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
-                cls.make_table_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method)xs
+                cls.make_table_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
             else:
                 cls.logger.warning(f"Unknown table {item}")
             # end if
@@ -440,47 +440,106 @@ class Tables:
                                   task,
                                   search_dataset,
                                   selection_method):
-        result_file = result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_result_analysis.json'
-        baseline_result_file = result_dir / f"test_results_{nlp_task}_{search_dataset_name}_{selection_method}" / 'test_result_checklist_analysis.json'
-        
+        result_file = result_dir / f"test_results_{task}_{search_dataset}_{selection_method}" / 'test_result_analysis.json'
+        baseline_result_file = result_dir / f"test_results_{task}_{search_dataset}_{selection_method}" / 'test_result_checklist_analysis.json'        
         output_file = latex.File(tables_dir / 'test-results-numbers.tex')
         result = Utils.read_json(result_file)
-        for m_i, model_name in enumerate(result.keys()):
-            model_name = model_name.replace('/', '-')
-            for res_i, res in enumerate(result[model_name].keys()):
-                if m_i==0:
-                    desc = cls.replace_latex_symbol(res['lc'])
-                    output_file.append_macro(latex.Macro(f"test-results-lc{res_i}",
-                                                         desc))
-                    output_file.append_macro(latex.Macro(f"test-results-lc{res_i}-num-seeds",
-                                                         res['num_seeds']))
-                    output_file.append_macro(latex.Macro(f"test-results-lc{res_i}-num-exps",
-                                                         res['num_exps']))
-                # end if
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{res_i}-num-seed-fail",
-                                                     res['num_seed_fail']))
-                if res['is_exp_exist']:
[…]

### 2022-05-05 paper/ase22/tables/test-results-numbers.tex
table

%% Automatically generated by pyutil.latex

\DefMacro{test-results-lc0}{Author sentiment is more important than of others}
\DefMacro{test-results-bl-lc0-num-sents}{8528}
\DefMacro{test-results-bl-model0-lc0-num-fail}{3741}
\DefMacro{test-results-lc1}{Negated negative should be positive or neutral}
\DefMacro{test-results-bl-lc1-num-sents}{6786}
\DefMacro{test-results-bl-model0-lc1-num-fail}{799}
\DefMacro{test-results-lc2}{Negated neutral should still be neutral}
\DefMacro{test-results-bl-lc2-num-sents}{2496}
\DefMacro{test-results-bl-model0-lc2-num-fail}{2427}
\DefMacro{test-results-lc3}{Negated positive with neutral content in the middle}
\DefMacro{test-results-bl-lc3-num-sents}{1000}
\DefMacro{test-results-bl-model0-lc3-num-fail}{860}
\DefMacro{test-results-lc4}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-bl-lc4-num-sents}{2124}
\DefMacro{test-results-bl-model0-lc4-num-fail}{1871}
\DefMacro{test-results-lc5}{Sentiment change over time, present should prevail}
\DefMacro{test-results-bl-lc5-num-sents}{8000}
\DefMacro{test-results-bl-model0-lc5-num-fail}{1680}
\DefMacro{test-results-lc6}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-bl-lc6-num-sents}{1716}
\DefMacro{test-results-bl-model0-lc6-num-fail}{1330}
\DefMacro{test-results-lc7}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-bl-lc7-num-sents}{8658}
\DefMacro{test-results-bl-model0-lc7-num-fail}{26}
\DefMacro{test-results-lc8}{Parsing positive and negative sentiment in (question, no) form}
\DefMacro{test-results-bl-lc8-num-sents}{7644}
\DefMacro{test-results-bl-model0-lc8-num-fail}{4056}
\DefMacro{test-results-lc9}{parsing sentiment in (question, yes) form}
\DefMacro{test-results-bl-lc9-num-sents}{9204}
\DefMacro{test-results-bl-model0-lc9-num-fail}{1793}
\DefMacro{test-results-bl-model1-lc0-num-fail}{2692}
\DefMacro{test-results-bl-model1-lc1-num-fail}{218}
\DefMacro{test-results-bl-model1-lc2-num-fail}{2304}
\DefMacro{test-results-bl-model1-lc3-num-fail}{416}
\DefMacro{test-results-bl-model1-lc4-num-fail}{445}
\DefMacro{test-results-bl-model1-lc5-num-fail}{829}
\DefMacro{test-results-bl-model1-lc6-num-fail}{1391}
\DefMacro{test-results-bl-model1-lc7-num-fail}{139}
\DefMacro{test-results-bl-model1-lc8-num-fail}{4576}
\DefMacro{test-results-bl-model1-lc9-num-fail}{1262}
\DefMacro{test-results-bl-model2-lc0-num-fail}{3535}
\DefMacro{test-results-bl-model2-lc1-num-fail}{734}
\DefMacro{test-results-bl-model2-lc2-num-fail}{2450}
\DefMacro{test-results-bl-model2-lc3-num-fail}{865}
\DefMacro{test-results-bl-model2-lc4-num-fail}{2124}
\DefMacro{test-results-bl-model2-lc5-num-fail}{2532}
\DefMacro{test-results-bl-model2-lc6-num-fail}{1661}
\DefMacro{test-results-bl-model2-lc7-num-fail}{125}
\DefMacro{test-results-bl-model2-lc8-num-fail}{6440}
\DefMacro{test-results-bl-model2-lc9-num-fail}{1557}
\DefMacro{test-results-lc0-num-seeds}{50}
\DefMacro{test-results-lc0-num-exps}{2323}
\DefMacro{test-results-model0-lc0-num-seed-fail}{22}
\DefMacro{test-results-model0-lc0-num-exp-fail}{1163}
\DefMacro{test-results-model0-lc0-num-pass-to-fail}{134}
\DefMacro{test-results-lc1-num-seeds}{50}
\DefMacro{test-results-lc1-num-exps}{1784}
\DefMacro{test-results-model0-lc1-num-seed-fail}{46}
\DefMacro{test-results-model0-lc1-num-exp-fail}{1680}
\DefMacro{test-results-model0-lc1-num-pass-to-fail}{49}
\DefMacro{test-results-lc2-num-seeds}{26}
\DefMacro{test-results-lc2-num-exps}{1009}
\DefMacro{test-results-model0-lc2-num-seed-fail}{24}
\DefMacro{test-results-model0-lc2-num-exp-fail}{932}
\DefMacro{test-results-model0-lc2-num-pass-to-fail}{62}
\DefMacro{test-results-lc3-num-seeds}{50}
\DefMacro{test-results-lc3-num-exps}{1634}
\DefMacro{test-results-model0-lc3-num-seed-fail}{42}
\DefMacro{test-results-model0-lc3-num-exp-fail}{1438}
\DefMacro{test-results-model0-lc3-num-pass-to-fail}{40}
\DefMacro{test-results-lc4-num-seeds}{50}
\DefMacro{test-results-lc4-num-exps}{1486}
\DefMacro{test-results-model0-lc4-num-seed-fail}{50}
\DefMacro{test-results-model0-lc4-num-exp-fail}{1486}
\DefMacro{test-results-model0-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-lc8-num-seeds}{100}
\DefMacro{test-results-lc8-num-exps}{2379}
\DefMacro{test-results-model0-lc8-num-seed-fail}{71}
\DefMacro{test-results-model0-lc8-num-exp-fail}{1723}
\DefMacro{test-results-model0-lc8-num-pass-to-fail}{40}
\DefMacro{test-results-lc5-num-seeds}{50}
\DefMacro{test-results-lc5-num-exps}{-}
\DefMacro{test-results-model0-lc5-num-seed-fail}{12}
\DefMacro{test-results-model0-lc5-num-exp-fail}{-}
\DefMacro{test-results-model0-lc5-num-pass-to-fail}{-}
\DefMacro{test-results-lc6-num-seeds}{19}
\DefMacro{test-results-lc6-num-exps}{210}
\DefMacro{test-results-model0-lc6-num-seed-fail}{15}
\DefMacro{test-results-model0-lc6-num-exp-fail}{182}
\DefMacro{test-results-model0-lc6-num-pass-to-fail}{19}
\DefMacro{test-results-lc7-num-seeds}{50}
\DefMacro{test-results-lc7-num-exps}{394}
\DefMacro{test-results-model0-lc7-num-seed-fail}{2}
\DefMacro{test-results-model0-lc7-num-exp-fail}{17}
\DefMacro{test-results-model0-lc7-num-pass-to-fail}{4}
\DefMacro{test-results-lc9-num-seeds}{50}
\DefMacro{test-results-lc9-num-exps}{1373}
\DefMacro{test-results-model0-lc9-num-seed-fail}{2}
\DefMacro{test-results-model0-lc9-num-exp-fail}{37}
\DefMacro{test-results-model0-lc9-num-pass-to-fail}{43}
\DefMacro{test-results-model1-lc0-num-seed-fail}{13}
\DefMacro{test-results-model1-lc0-num-exp-fail}{725}
\DefMacro{test-results-model1-lc0-num-pass-to-fail}{78}
\DefMacro{test-results-model1-lc1-num-seed-fail}{41}
\DefMacro{test-results-model1-lc1-num-exp-fail}{1537}
\DefMacro{test-results-model1-lc1-num-pass-to-fail}{64}
\DefMacro{test-results-model1-lc2-num-seed-fail}{24}
\DefMacro{test-results-model1-lc2-num-exp-fail}{939}
\DefMacro{test-results-model1-lc2-num-pass-to-fail}{38}
\DefMacro{test-results-model1-lc3-num-seed-fail}{21}
\DefMacro{test-results-model1-lc3-num-exp-fail}{664}
\DefMacro{test-results-model1-lc3-num-pass-to-fail}{54}
\DefMacro{test-results-model1-lc4-num-seed-fail}{50}
\DefMacro{test-results-model1-lc4-num-exp-fail}{1486}
\DefMacro{test-results-model1-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-model1-lc8-num-seed-fail}{79}
\DefMacro{test-results-model1-lc8-num-exp-fail}{1947}
\DefMacro{test-results-model1-lc8-num-pass-to-fail}{18}
\DefMacro{test-results-model1-lc5-num-seed-fail}{28}
\DefMacro{test-results-model1-lc5-num-exp-fail}{-}
\DefMacro{test-results-model1-lc5-num-pass-to-fail}{-}
\DefMacro{test-results-model1-lc6-num-seed-fail}{17}
\DefMacro{test-results-model1-lc6-num-exp-fail}{160}
\DefMacro{test-results-model1-lc6-num-pass-to-fail}{9}
\DefMacro{test-results-model1-lc7-num-seed-fail}{2}
\DefMacro{test-results-model1-lc7-num-exp-fail}{19}
\DefMacro{test-results-model1-lc7-num-pass-to-fail}{5}
\DefMacro{test-results-model1-lc9-num-seed-fail}{1}
\DefMacro{test-results-model1-lc9-num-exp-fail}{57}
\DefMacro{test-results-model1-lc9-num-pass-to-fail}{46}
\DefMacro{test-results-model2-lc0-num-seed-fail}{20}
\DefMacro{test-results-model2-lc0-num-exp-fail}{1040}
\DefMacro{test-results-model2-lc0-num-pass-to-fail}{31}
\DefMacro{test-results-model2-lc1-num-seed-fail}{44}
\DefMacro{test-results-model2-lc1-num-exp-fail}{1579}
\DefMacro{test-results-model2-lc1-num-pass-to-fail}{26}
\DefMacro{test-results-model2-lc2-num-seed-fail}{24}
\DefMacro{test-results-model2-lc2-num-exp-fail}{961}
\DefMacro{test-results-model2-lc2-num-pass-to-fail}{74}
\DefMacro{test-results-model2-lc3-num-seed-fail}{38}
\DefMacro{test-results-model2-lc3-num-exp-fail}{1280}
\DefMacro{test-results-model2-lc3-num-pass-to-fail}{9}
\DefMacro{test-results-model2-lc4-num-seed-fail}{50}
\DefMacro{test-results-model2-lc4-num-exp-fail}{1486}
\DefMacro{test-results-model2-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-model2-lc8-num-seed-fail}{93}
\DefMacro{test-results-model2-lc8-num-exp-fail}{2216}
\DefMacro{test-results-model2-lc8-num-pass-to-fail}{12}
\DefMacro{test-results-model2-lc5-num-seed-fail}{39}
\DefMacro{test-results-model2-lc5-num-exp-fail}{-}
\DefMacro{test-results-model2-lc5-num-pass-to-fail}{-}
\DefMacro{test-results-model2-lc6-num-seed-fail}{19}
\DefMacro{test-results-model2-lc6-num-exp-fail}{198}
\DefMacro{test-results-model2-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-model2-lc7-num-seed-fail}{1}
\DefMacro{test-results-model2-lc7-num-exp-fail}{11}
\DefMacro{test-results-model2-lc7-num-pass-to-fail}{8}
\DefMacro{test-results-model2-lc9-num-seed-fail}{3}
\DefMacro{test-results-model2-lc9-num-exp-fail}{76}
\DefMacro{test-results-model2-lc9-num-pass-to-fail}{14}

### 2022-05-05 paper/ase22/tables/test-results-table.tex
table

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\begin{adjustbox}{angle=90}
\begin{tabular}{p{5cm}||ccccccc}
\toprule
\tLc & \tNumBlSents & \tNumBlFail & \tNumSeeds & \tNumSeedFail & \tNumExps & \tNumExpFail & \tNumPasstoFail\\
\midrule
\multirow{3}{*}{\parbox{5cm}{LC1: \UseMacro{test-results-lc0}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc0-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc0-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc0-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc0-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc0-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC2: \UseMacro{test-results-lc1}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc1-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc1-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc1-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc1-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc1-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC3: \UseMacro{test-results-lc2}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc2-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc2-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc2-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc2-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc2-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC4: \UseMacro{test-results-lc3}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc3-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc3-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc3-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc3-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc3-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC5: \UseMacro{test-results-lc4}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc4-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc4-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc4-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc4-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc4-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC6: \UseMacro{test-results-lc5}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc5-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc5-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc5-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc5-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc5-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC7: \UseMacro{test-results-lc6}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc6-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc6-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc6-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc6-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc6-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC8: \UseMacro{test-results-lc7}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc7-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc7-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc7-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc7-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc7-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC9: \UseMacro{test-results-lc8}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc8-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc8-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc8-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc8-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc8-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{5cm}{LC10: \UseMacro{test-results-lc9}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc9-num-sents}}
 & Model1$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc9-num-seeds}}
 & Model1$\colon$\UseMacro{test-results-model0-lc9-num-seed-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc9-num-exps}}
 & Model1$\colon$\UseMacro{test-results-model0-lc9-num-exp-fail}
 & Model1$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
 & & Model2$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
 & & Model2$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
 & Model2$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
 & & Model3$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
 & & Model3$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
 & Model3$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\
\hline
\bottomrule
\end{tabular}
\end{adjustbox}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-05-05 python/sa/paper/Tables.py
debugging table

@@ -469,6 +469,7 @@ class Tables:
         # end for
         
         for m_i, model_name in enumerate(result.keys()):
+            print(m_i, model_name)
             # model_name = model_name.replace('/', '-')
             temp_num_seeds, temp_num_exps = 0,0
             temp_num_seed_fail, temp_num_exp_fail = 0,0
@@ -567,41 +568,42 @@ class Tables:
         output_file.append(r"\begin{small}")
         output_file.append(r"\begin{center}")
         output_file.append(r"\caption{\TestResultsTableCaption}")
-        output_file.append(r"\begin{tabular}{p{5cm}||c c c c c c c}")
+        output_file.append(r"\begin{adjustbox}{angle=90}")
+        output_file.append(r"\begin{tabular}{p{5cm}||ccccccc}")
         output_file.append(r"\toprule")
         
-        output_file.append(r"\tLc & \tNumBlSents & \tNumBlFail & \tNumSeeds & \tNumSeedFail & \tNumExps & \tNumExpsFail & \tNumPasstoFail\\")
+        output_file.append(r"\tLc & \tNumBlSents & \tNumBlFail & \tNumSeeds & \tNumSeedFail & \tNumExps & \tNumExpFail & \tNumPasstoFail\\")
         output_file.append(r"\midrule")
 
         # Content
         for lc_i in range(lcs_len):
-            output_file.append("\multirow{"+str(len(model_names))+"}{*}{" + \
-                               latex.Macro(f"test-results-lc{lc_i}").use() + "}")
+            output_file.append("\multirow{"+str(len(model_names))+"}{*}{\parbox{5cm}{" + \
+                               f"LC{lc_i+1}: " + latex.Macro(f"test-results-lc{lc_i}").use() + "}}")
             output_file.append(" & \multirow{"+str(len(model_names))+"}{*}{" + \
                                latex.Macro(f"test-results-bl-lc{lc_i}-num-sents").use() + "}")
-            output_file.append(" & m0\colon" + latex.Macro("test-results-bl-model0-lc{lc_i}-num-fail").use())
+            output_file.append(" & Model1$\colon$" + latex.Macro(f"test-results-bl-model0-lc{lc_i}-num-fail").use())
 
             output_file.append(" & \multirow{"+str(len(model_names))+"}{*}{" + \
                                latex.Macro(f"test-results-lc{lc_i}-num-seeds").use() + "}")
[…]

### 2022-05-06 paper/ase22/intro.tex
revise intro

@@
 of NLP applications is an essential process in the software
-development processes.  Traditionally, the prevalent models of NLP are
-evaluated via train-validation-test splits \cite{}.  Training and
-validation sets are used to train the NLP models, and the test set,
-also called \ho set, is used to test the trained model.  The quality
-of these models is estimated into numbers using performance
-metrics. Especially, accuracy (i.e., the fraction of outputs that the
-model correctly predicts) is the most widely used metric for assessing
-the quality of classification models. When comparing two NLP models,
-one is considered better if it has higher accuracy than the other.
-
-Researchers aim to improve the current practices of testing NLP models
-from three perspectives: (i) \emph{Test input generation}, (ii)
-\emph{Automated test oracle}, and (iii) \emph{Meaningful quality
-  metrics}.
+development processes.  Researchers aim to improve the current
+practices of testing NLP models from three perspectives: (i)
+\emph{Test input generation}, (ii) \emph{Automated test oracle}, and
+(iii) \emph{Meaningful quality metrics}.
 
@@
   marcoACL2020checklist}.  The overestimation comes from the
-discrepancy between distribution of the used dataset and actual data
-distribution in real world. Oftentimes, the \ho dataset is not
-representative and it is likely to introduce specific biases. Such
-biases lead to make the model delicated to out-of-distribution and
-decrease robustness of model in the end. In this regards, prior works
-have proposed techniques for testing NLP model robustness by crafting
-adversarial examples and attacking a model with them intentionally
-\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial}. \TODO{Jaeseong, mention
-  and cite adversarial testing techniques here.} \jl{done.}
+discrepancy between the distribution of the used dataset and the
+actual data distribution in real world. Oftentimes, the \ho dataset is
+not representative and is likely to introduce specific biases, leading
+to the decreased robustness of NLP models. In this regard, prior works
+have proposed techniques for testing the robustness of NLP models by
+crafting adversarial examples and attacking a model with them
+intentionally \cite{ribeiro2018sear,belinkov2018breaknmt,
+  rychalska2019wildnlp,iyyer2018adversarial}.
 
@@
 impact on market price. Therefore, it necessitates automated test
-oracle generation for improving the testing process of NLP
-models. However, validity of the automation is ensured by the
-correctness of test oracle. Auto-generated test orcle may not always
-be feasible; predicting the correct test oracle is one of main
-challenges to gaurantee its practical use. Along with this, software
-metamorphic testing approach has been
-introduced~\cite{segura2016metamorphictest} to alleviate the test
-oracle discrepancy between expected and observed test oracle.
-\TODO{Describe and Add citations to metamorphic testing techniques
-  here}\jl{done.}
+oracle generation for improving the testing process of NLP models.
+% validity of the automation is ensured by the
+% correctness of test oracle.
+However, automatically generated test oracles may not always be
+feasible; predicting the correct test oracles remains one of main
+challenges. Along with this, software metamorphic testing approach has
+been introduced~\cite{segura2016metamorphictest} to alleviate the test
+oracle discrepancy between expected and observed test oracles.
+% \TODO{Describe and Add citations to metamorphic testing techniques
+%   here}\jl{done.}
 
@@
 % distribution between the dataset and real-world data.
-\noindent \textbf{Meaningful quality metrics.}  As discussed, accuracy
-is the most widely used quality metric for measuring NLP model
-performance. Forced aggregation statistics into a single number makes
-the user difficult to assess the capability of NLP models.  Not to
-mention localizing and fixing the bugs found from the \ho
-set. Therefore, this forced aggregation method not only fails to
-validate model behaviors, but it also makes the localization of the
-causes of the inaccuracy more costly~\cite{wu2019errudite}.
+\noindent \textbf{Meaningful quality metrics.}  Traditionally, the
+quality of NLP models are represented by numbers in quality
+metrics. Especially, accuracy (i.e., the fraction of outputs that the
+model correctly predicts) is the most widely used metric for assessing
+the quality of classification models.  Generally, higher accuracy
+number suggests better quality of a model.  However, all NLP models
+have their strength and weakness and forcing aggregation statistics
+into a single number makes the users difficult to assess the
+capabilities of NLP models.  Not to mention localizing and fixing the
+bugs found from the \ho set (i.e., testing dataset, as opposed to
+training dataset). Therefore, this forced aggregation method not only
+fails to validate the linguistic capability of the model, but it also
+makes the localization of the causes of the inaccuracy more
+costly~\cite{wu2019errudite}.
 % Therefore behavioral testing
@@
 However, none of the above approaches satisfy all three requirements
-at the same time. First, prior adversarial testing approaches merely
-focus on evaluating model robustness. These measure how much model is
-sensetive to the output on which input perturbations while limited to
-provide evaluation on linguistic functionalities of interests in
-real-world. In addition, the metamorphic testing approach is required
-to understand characteristics of metamorphic relations between input
-and output.  However, finding these is one of the most challenging
-problem in the metamorphic
+at the same time. First, adversarial testing approaches merely focus
+on evaluating model robustness. They measure how sensitive the models
+are to input perturbations while do not evaluate linguistic
+functionalities.  Second, the metamorphic testing approach is required
+to understand the characteristics of metamorphic relations between
+inputs and outputs. However, finding these remains one of the most
+challenging problem in metamorphic
 testing~\cite{segura2016metamorphictest}. Along with this, such
-relations in textual data in NLP domain has not been evaluated despite
-its importance. \TODO{Describe the limitation of adversarial testing
-  and Metamorphic testing} \jl{done.}
-
-Specifically, \Cklst relies on manually generated input templates,
-which need to be preset before test input generation. Consequently,
-\Cklst templates are distributed in a limited range of their
-structures. This restricts \Cklst's ability to comprehensively test
-the linguistic capabilities.
+relation in textual data in NLP domain has not been evaluated despite
+its importance.  Third, \Cklst relies on manually generated input
+templates, which need to be preset before test input
+generation. Consequently, \Cklst templates are distributed in a
+limited range of their structures. This restricts \Cklst's ability to
+comprehensively test the linguistic capabilities.
 
@@
 
-\TODO{adding detail description about challenges}
-
-\noindent \textbf{C1.} We first address increasing input
-representiveness. Compared with templates used in \Cklst, \tool
-instead establishes input requirement for evaluating a linguistic
-capability and finds suitable inputs that meet the requirement from
-existing public dataset. In this process, \tool applies the fuzzing
-testing principle to generate inputs by mutating the selected inputs
-as seed inputs. Fuzzer in \tool first expands seed input grammar
-structures and determines its available \pos to maintain structural
-naturalness.
+\noindent \textbf{C1.} generating sentences with diverse syntactic
+structure is challenging since text have a higher order of its
+structure. However, the structures are obscured by word usage. To
+address the challenge, \tool establishes specifications for evaluating
+a linguistic capability and searches suitable sentences that satisfy
+the specification from existing public dataset. In this process, \tool
+generates new inputs by mutating the searched sentences, used as seed
+inputs. \tool expands seed input grammar structures and determines its
+available \pos to maintain structural naturalness.
 
@@
 
-\noindent \textbf{C2.} Morover, we adopts behavioral model testing
-method by introducing multiple behaviors from \lcs on \sa task and
-generating inputs relevant to each \lc. Each test case provides not
-only correcteness of model prediction on it, but \lc on the test case
-also gives infromation about classification on the model
-performance. Therefore assigning appropriate \lc for each testcase
-alleviates overestimation of model testing results.
+\noindent \textbf{C2.} Suitability of test case for evaluating NLP
+model on a \lc is obtained from its high relevancy to the
+\lc. Relevancy between test case and \lc is difficult to be measured
+because the \lc is defined on a specific phenomenon appeared in the
+mixture of textual structure and semantic, and understanding each test
+case with respect to the phenomenon and measuring its relevancy are
+not trivial. To address the difficulty, \tool implements search rules
+and the transformation templates of \lcs. In addition, anlyzing parse
+tree of seed sentence is used for its expansion identification.
+%% \tool adopts behavioral model testing method by
+%% introducing multiple behaviors from \lcs on \sa tasks and generating
+%% inputs relevant to each \lc. Each test case provides not only
+%% correctness of model prediction on it, but \lc on the test case also
+%% gives information about classification on the model
+%% performance. Therefore assigning appropriate \lc for each test case
+%% alleviates overestimation of model testing results.
 
-\noindent \textbf{C3.} Lastly, we show the appropriateness of test
-orable that \tool automatically generated by manual study of generated
-test cases. Aggreement of input-output relations between human and
-\tool is crucial to increase trustworthiness of model. In this manner,
-reliabilty of model for its practical use can be achieved in the end.
+\noindent \textbf{C3.} Last challenge is on estimating the
+appropriateness of test oracle. For \sa task, test oracle is
+determined by understanding meaning from text. The meaning of text is
+sensitive to its semnatic, structure, and the combination of
+two. Therefore, generation of test case ought to ensure the
+correctness of its oracle allocation. In this work, \tool obtain the
+appropriateness of test oracle by implementing domain-specific
+knowledge on word sentiment dataset and word suggestion model
+pre-trained on large corpus for validation of generated sentence and
+its oracle.
 
@@
 
-% Software functional testing is an essential component of the software development
-% process. It evaluates an attribute of the software and
-% determines the correctness by comparing the actual and the expected behaviors.
-\sw{Should we lead with this paragraph?
-We are talking about functional testing here but next we say NLP uses train-validation-test.}
-% Automated software
-% testing and debugging in the early stage of the development process can identify and fix defects. Therefore,
-% effective software testing assures software quality, and
-% it meets needs of the end user.
+% % In the early stage of the software development process, automated
+% % software testing and debugging can identify and fix
+% % defects. Therefore, effective software testing assures software
+% % quality, and it meets needs of the end user. Nowdays, software at work
+% % has elements of \ml (ML). Especially,
 
-% Meanwhile, the trustworthiness in
-% quality of \nlp (NLP) application has become an important component for
-% its practical use in real world. Traditionally, the prevalent models
-% of NLP are evaluated via train-validation-test splits \cite{}. Training and
-% validation set are used to train the NLP models and the \ho set is used
-% for testing. Accuracy is often used as the performance
-% metric of the models \cite{}, i.e., a model is considered better if it has higher
-% accuracy than another model.
-% Despite its simplicity and usefulness, this testing paradigm often
-% overestimates \sw{Not sure what overestimate means here} the performances from the \ho set. Oftentimes, the \ho dataset is not representative and it is likely to introduce specific
-% biases. Such biases increase the discrepancy of distribution between
-% the dataset and real-world data~\cite{recht2019imagenetbias}. Therefore, making this testing method fail to measure the comprehensive performance of the NLP
-% models. In addition, the accuracy metric does not validate
-% certain behaviors of the model; as a result, it still is costly to localize the causes of the inaccuracy~\cite{wu2019errudite}.
+% \Nlp (NLP) applications are growing exponentially.
+% As a result, trustworthiness in the quality of NLP applications has become critical for its practical use in the real world.
+% Therefore, quality assurance of NLP applications is an essential process in the software development
+% processes.
+% Traditionally, the prevalent models of NLP are evaluated via
+% train-validation-test splits \cite{}.
+% Training and validation sets are used to
+% train the NLP models, and the test set, also called \ho set, is used
+% to test the trained model. 
+% The quality of these models is
+% estimated into numbers using performance metrics. Especially,
+% accuracy (i.e., the fraction of outputs that the model correctly
+% predicts) is the most widely used metric for assessing the quality of classification
+% models. When comparing two NLP models, one is considered better if it has higher
+% accuracy than the other.
 
-% To address these challenges, several approaches have
-% been proposed to evaluate different aspects of the NLP models,
-% such as robustness on adversarial examples \cite{}, model coverage \cite{}, and
-% fairness \cite{}.  Especially, Ribeiro~\etal introduced \Chlst, a
-% behavioral testing framework for evaluating NLP model on multiple
-% linguistic capabilities~\cite{marcoACL2020checklist}. \Chlst defines
-% task-relevant linguistic capabilities and generates testcases for each \lc.
-% However, the approach relies on manually generated input
-% templates; thus, the template generation becomes expensive and time
-% consuming. In addition, only a few simple templates are used by \Chlst, limiting its ability to comprehensively test the linguistic capabilities.
+% Researchers aim to improve the current practices of testing NLP models from three perspectives:
+% (i) \emph{Test input generation},
+% (ii) \emph{Automated test oracle},
+% and (iii) \emph{Meaningful quality metrics}.
 
-% Despite the limitations\jl{this paragraph, how about mentioning checklist first and limitations and our model?}, \Chlst's approach of testing the linguistic capabilities is a promising direction.
-Each \lc explain the functionality
-% of the input and output behavior for the NLP model under test. \sw{For example, ...} The
-% expected behavior is determined by combining the input and output
-% scopes specified on the \lc. \sw{Not sure what the last sentence means.} Typically, it describes certain type of
-% input and outputs observed in real world for the target NLP task
-% ranging from simple to complicated behaviors so that they are able to
-% evaluate the NLP model comprehensively. \sw{For example, ...} Such evaluation on the
-% specified functionalities avoids the overestimation of the model
-% performance as it equivalently measures the model performance on each
-% functionality, and the separate model performance explain distribution
-% of the performance over the linguistic capabilities. In the end, it provides not only the
-% overall model performance, but also the malfunction facets of the
-% model. However, the prior work currently generated model. \sw{This paragraph can be moved before the limitations of \Chlst (last paragraph)? I will make the description more concrete.}
+% \noindent \textbf{Test input generation.} Currently, most testing of an NLP model reuses existing large textual corpus as the testing dataset to evaluate the model.
+This practice will often overestimates the model performances from the \ho
+% set~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
+%   marcoACL2020checklist}.
+% The overestimation comes from the discrepancy between distribution of the
+% used dataset and actual data distribution in real world. Oftentimes, the
+% \ho dataset is not representative and it is likely to introduce
+% specific biases \cite{}.
+% Many adversarial testing techniques have been proposed \cite{ribeiro2018sear,belinkov2018breaknmt,
+%   rychalska2019wildnlp,iyyer2018adversarial}. \TODO{Jaeseong, mention and cite adversarial testing techniques here.}
 
-% In this paper, we present \tool, an automated NLP model evaluation
-% method for comprehensive behavioral testing of NLP models on \sa
-% task. For each behavior of linguistic capability, \tool does not rely
-% on the manual input generation.
-\sw{Make sure this paragrpah is consistent with our approach description in Section 3.
-Also, make clear in this paragraph: what challenges/limitations from CheckList we address and how.} Instead, it establishes input
-% requirement for evaluating a linguistic capability and finds suitable
-% inputs that meet the requirement from existing public dataset.
-% Therefore, \tool increases input diversity and generality. Further,
-% \tool applies the fuzzing testing principle to generate inputs by
-% mutating the selected inputs as seed inputs. Fuzzer in \tool first
-% expands seed input grammar structures and determines its available
-% \pos to maintain structural naturalness. After that, to hold
-% contextual naturalness of the mutated inputs, the fuzzer completes the
-% expanded new structures via data-driven context-aware word
-% suggestion. Additionally, sentiment-independent words in the inputs
-% are replaced with rule-based word suggestion.
+% \noindent \textbf{Automated test oracle.} The current testing practice requires manual work for labelling the test oracles of the \ho data.
+The manual work is costly in terms of time consumption and its impact
+% on market price. Therefore, it necessitates automated test oracle generation
+% for improving the testing process of NLP models.  A few techniques \TODO{Describe and Add citations to metamorphic testing techniques here}
+
+% %% \sw{Not sure what overestimate means here}
+% %  In addition, the inconsistency between test input and
+% % its oracle causes biases. Such biases increase the discrepancy of
+% % distribution between the dataset and real-world data.
+% \noindent \textbf{Meaningful quality metrics.}
+% As discussed, accuracy is the most widely used quality metric for measuring NLP model performance.
+Forced aggregation statistics into a single number makes the user difficult to assess the capability of NLP models.
+% Not to mention localizing and fixing the bugs found from the
+% \ho set. Therefore, this forced aggregation method not only fails to validate model
+% behaviors, but it also makes the localization of the causes of the inaccuracy more costly~\cite{wu2019errudite}.
+% % Therefore behavioral testing
+% % approach provides the better ability to examine the inaccuracy and
+% % find the bugs in the model.
+% To address this limitation, 
+% % several approaches have been proposed to
+% % evaluate different aspects of the NLP models, such as , model coverage
+% % \cite{rottger2020hatecheck}, and fairness
+% % \cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition, For example, Testing model coverage
+% % only shows model behaviors, but not the model performance on existing
+% % testing set. The fairness and robustness testing only focus on only
+% % one model capability resulting in its limited comprehensiveness. In
+% % addition,
+% Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
+% evaluating NLP model on multiple linguistic
+% capabilities~\cite{marcoACL2020checklist}. \Cklst defines
+% task-relevant linguistic capabilities and generates test cases for each
+% \lc.
+
+% However, none of the above approaches satisfy all three requirements at the same time. 
+% \TODO{Describe the limitation of adversarial testing and Metamorphic testing}
+% Specifically, \Cklst relies on manually generated input templates, which need to be
+% preset before test input generation. Consequently, \Cklst templates
+% are distributed in a limited range of their structures. This restricts
+% \Cklst's ability to comprehensively test the linguistic capabilities.
+
+% Despite \Cklst's limitations, assessing the quality of NLP models through the linguistic
+% capabilities is a promising direction. Each \lc explains the
+% functionality of the input and output behavior for the NLP model under
+% test. Typically, it describes certain type of inputs and outputs
+% observed in real world for the target NLP task ranging from simple to
+% complicated behaviors, so the model developers can better understand the capabilities and potential issues of the NLP models. For example, a linguistic capability of ``Negated
+% neutral should still be neutral'' measures how accurately the \sa
+% model understands the negative neutral input as an neutral
+% sentiment \cite{marcoACL2020checklist}. 
+% Therefore, it requires the \sa model to output neutral
+% sentiment on the negated neutral input.  Such methodology of
+% evaluation on the specified functionalities avoids the overestimation
+% of the model performance as it equivalently measures the model
+% performance on each functionality.
+% % ,and the separate model performance
+% % explain distribution of the performance over the linguistic capabilities
+% In the end, testing through linguistic capabilities provides not only the overall model
+% performance, but also the malfunction facets of the model.
+
+% To satisfy all three requirements mentioned above, we present \tool, an
+% automated NLP model evaluation method for comprehensive behavioral
+% testing of NLP models on \sa task. 
+% There are three main challenges that \tool overcomes to satisfy all three aforementioned requirements.
+% \begin{description}
+% \item[{\bf C1}] the test suite should cover diverse syntactic structures;
+%   \item[{\bf C2}] each test case should be
+% categorized into a \lc;
+% \item[{\bf C3}] the label of each test case should be
+% automatically and accurately defined.
+% \end{description}
+
+% \TODO{adding detail description about challenges}
+
+% \noindent \textbf{C1.} We first address increasing input
+% representiveness. Compared with templates used in \Cklst, \tool
+% instead establishes input requirement for evaluating a linguistic
+% capability and finds suitable inputs that meet the requirement from
+% existing public dataset. In this process, \tool applies the fuzzing
+% testing principle to generate inputs by mutating the selected inputs
+% as seed inputs. Fuzzer in \tool first expands seed input grammar
+% structures and determines its available \pos to maintain structural
+% naturalness.
+
+% % After that, to hold contextual naturalness of the mutated
+% % inputs, the fuzzer completes the expanded new structures via
+% % data-driven context-aware word suggestion. Additionally,
+% % sentiment-independent words in the inputs are replaced with rule-based
+% % word suggestion. Further, we address the manual input generation
+% % process by automating the process mentioned above.
+
+% \noindent \textbf{C2.} Lastly, we adopts
+% behavioral model testing method by introducing multiple behavior of
+% linguistic capabilities on \sa task and generating inputs relevant to
+% each linguistic capability.
+
+% \noindent \textbf{C3.}
 
@@
 % We show that ...
-
-% Contributions:
-
-% \jl{test oracle relevancy, and relevancy of testcase with lc}

### 2022-05-06 paper/ase22/experiment.tex
edit exp & table

@@
 %
-
-% \InputWithSpace{tables/retrain-debug-table}
-
 In this section, we present the setup of the experiments to evaluate
@@
   its oracle?
-\item \label{rq:two}: Is \tool generated testcases relevant to be used
+\item \label{rq:two}: Are \tool generated test cases relevant to be used
   for their \lc evaluation?
@@
 
+\subsection{Experimental Subjects}
+
+\paragraph{\textbf{NLP Models \& Dataset.}}
+We evaluate our approach on three leaerning-based \sa models
+implemented in Transformer library from the Hugging Face centralized
+Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
+(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
+\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
+language using a masked language modeling (MLM) objective, and
+fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
+searching seeds and expanding the seeds in \tool.
+%% \TODO{introduce details about each model}
+
+\paragraph{\textbf{Comparison Baselines.}}
+We compare our approach with
+\Cklst\footnote{https://github.com/marcotcr/checklist}, which is a
+manual template-based approach to generate test cases. In this
+experiment, we used the \Cklst released \sa test cases which are
+generated from its publicly available jupyter notebook implementation.
+%% \TODO{introduce details about CHECKLIST}
+
+\subsection{Experimental Process}
+
 \paragraph{\textbf{RQ1 and RQ2}} As described in Section \ref{sec:approach},
@@
 sampled seed sentences. In this experiment, each set has 100 sentences
-(50 from seed sentences and 50 from expanded sentences) and 300
+(50 from seed sentences and 50 from expanded sentences) and 200
 sentences, in total, are used for the manual study. For each sampled
@@
 negative'' to ``strongly positive'' respectively. In this work, we
-collect manual study scores from 6 subjects in total. From the
-collected scores, we measure the following metrics:
+collect manual study scores from 3 subjects in total. In case of
+different scores with a same sentence from different subjects, we used
+their average score as a score of the sentence.
+%% \sw{6 or 3 participants? What happened if participants scored differently?}
+From the collected scores, we measure the following metrics:
 
@@
 equation~\ref{metric:lcrel} represents the average score of the
-relevancy score between sentence and its associated \lc. higer average
+relevancy score between sentence and its associated \lc. Higer average
 score means that higher human-level agreement of the use of sentence
@@
 answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
-and equation~\ref{metric:lcrel} respectively, thereby, show its ability
-of \tool to understand human intelligence.
+and equation~\ref{metric:lcrel} respectively, thereby, show its
+ability of \tool to understand human intelligence.
 
@@
 al. \cite{ma2018deepgauge}, where the authors measure the coverage of
-NLP model intermediate states as corner-case neurons.  \sw{Why is this
-  a good metric for diversity?}  Specifically, we use the \sw{are
-  these metrics we define or are they from ma2018deepgauge?} two
-coverage metrics in existing work \cite{ma2018deepgauge},
-\textit{boundary coverage} (BoundCov) and \textit{strong activation
-  coverage} (SActCov), as our metrics to evaluate the test suite
-diversity.
+NLP model intermediate states as corner-case neurons.  Because the
+matrix computation of intermediate states impacts NLP model
+decision-making, a test suite that covers a greater number of
+intermediate states can represent more NLP model decision-making,
+making it more diverse.  Specifically, we used two coverage metrics in
+existing work \cite{ma2018deepgauge}, \textit{boundary coverage}
+(BoundCov) and \textit{strong activation coverage} (SActCov), as our
+metrics to evaluate the test suite diversity.  \TODO{It is worth
+  noting that a test sample with a statistical distribution similar to
+  the training data would rarely be found in the corner case
+  region. As a result, covering a larger corner case region means that
+  the test suite is more likely to be buggy.}
 
@@
 \begin{split}
-    \text{UpperCornerNeuron}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (high_n, +\infty)\}; \\
-    \text{LowerCornerNeuron}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (-\infty, low_n)\}; \\
+    \text{UpperCorner}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (high_n, +\infty)\}; \\
+    \text{LowerCorner}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (-\infty, low_n)\}; \\
 \end{split}
@@
 \begin{split}
-     & BoundCov(\mathcal{X}) = \frac{|UpperCornerNeuron(\mathcal{X})| + |LowerCornerNeuron| }{2 \times |N|} \\ 
-     & SActCov(\mathcal{X}) = \frac{|UpperCornerNeuron(\mathcal{X})|} {|N|} \\ 
+     & BoundCov(\mathcal{X}) = \frac{|UpperCorner(\mathcal{X})| + |LowerCorner(\mathcal{X})| }{2 \times |N|} \\ 
+     &\quad  \qquad \qquad  SActCov(\mathcal{X}) = \frac{|UpperCorner(\mathcal{X})|} {|N|} \\ 
 \end{split}
@@
 To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
-After that, we randomly select 100 \sw{Why 100, not all?} test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
-\cm{we repeat this process and record both the average and variance value of each coverage}
+After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
+
 % For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
@@
 
-\paragraph{RQ4.} To demonstrate that \tool can help developers to understand the bugs in the sentiment analysis modes, we conduct experiments to visualize
+\paragraph{RQ4.}
 
-\sw{@Simin: add the setup of the bug explanation case study here.}
+To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
+Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input).
+Still, it is unclear why mutating one token will cause the model to produce misclassified results.
+We seek to help developers to understand why such mutation will result in the misclassification. 
+Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences).
+Motivated by such intuition, we seek to identify a minimal set of input tokens that dominate the model prediction.
+
+Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token in $x$ or not.
+The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
+
+\begin{equation}
+    P(f(T(x)) = f(x)) \ge P_{thresh}
+    \label{eq:prob}
+\end{equation}
+
+To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{}.
+Following that, we begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Eq.
+\ref{eq:prob}.
+We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Eq. \ref{eq:prob}
+Because we iterate the size of our mask, the generated template $T$ will keep the minimum number of tokens in $x$.
+Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).
+
+% In particular, we apply the explainable ML techniques to visualize the contribution of each input token to the model predictions.
+%
+
+% \sw{@Simin: add the setup of the bug explanation case study here.}
 %In addition to the detection of bugs \sw{have we defined ``bug" in this context?} in the model,

### 2022-05-06 paper/ase22/tables/test-results-table.tex
edit exp & table
revise table

@@
 \caption{\TestResultsTableCaption}
-\begin{adjustbox}{angle=90}
-\begin{tabular}{p{5cm}||ccccccc}
+\resizebox{\textwidth}{!}{
+\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}
 \toprule
-\tLc & \tNumBlSents & \tNumBlFail & \tNumSeeds & \tNumSeedFail & \tNumExps & \tNumExpFail & \tNumPasstoFail\\
+\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.4cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.3cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\
 \midrule
-\multirow{3}{*}{\parbox{5cm}{LC1: \UseMacro{test-results-lc0}}}
+\multirow{3}{*}{\parbox{4cm}{LC1: \UseMacro{test-results-lc0}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc0-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc0-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc0-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc0-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc0-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc0-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc0-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC2: \UseMacro{test-results-lc1}}}
+\multirow{3}{*}{\parbox{4cm}{LC2: \UseMacro{test-results-lc1}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc1-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc1-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc1-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc1-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc1-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc1-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc1-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC3: \UseMacro{test-results-lc2}}}
+\multirow{3}{*}{\parbox{4cm}{LC3: \UseMacro{test-results-lc2}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc2-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc2-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc2-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc2-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc2-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc2-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc2-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC4: \UseMacro{test-results-lc3}}}
+\multirow{3}{*}{\parbox{4cm}{LC4: \UseMacro{test-results-lc3}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc3-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc3-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc3-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc3-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc3-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc3-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc3-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC5: \UseMacro{test-results-lc4}}}
+\multirow{3}{*}{\parbox{4cm}{LC5: \UseMacro{test-results-lc4}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc4-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc4-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc4-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc4-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc4-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc4-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc4-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC6: \UseMacro{test-results-lc5}}}
+\multirow{3}{*}{\parbox{4cm}{LC6: \UseMacro{test-results-lc5}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc5-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc5-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc5-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc5-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc5-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc5-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc5-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC7: \UseMacro{test-results-lc6}}}
+\multirow{3}{*}{\parbox{4cm}{LC7: \UseMacro{test-results-lc6}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc6-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc6-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc6-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc6-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc6-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc6-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc6-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC8: \UseMacro{test-results-lc7}}}
+\multirow{3}{*}{\parbox{4cm}{LC8: \UseMacro{test-results-lc7}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc7-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc7-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc7-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc7-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc7-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc7-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc7-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC9: \UseMacro{test-results-lc8}}}
+\multirow{3}{*}{\parbox{4cm}{LC9: \UseMacro{test-results-lc8}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc8-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc8-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc8-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc8-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc8-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc8-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc8-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{5cm}{LC10: \UseMacro{test-results-lc9}}}
+\multirow{3}{*}{\parbox{4cm}{LC10: \UseMacro{test-results-lc9}}}
  & \multirow{3}{*}{\UseMacro{test-results-bl-lc9-num-sents}}
- & Model1$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}
+ & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc9-num-seeds}}
- & Model1$\colon$\UseMacro{test-results-model0-lc9-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc9-num-seed-fail}
  & \multirow{3}{*}{\UseMacro{test-results-lc9-num-exps}}
- & Model1$\colon$\UseMacro{test-results-model0-lc9-num-exp-fail}
- & Model1$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
- & & Model2$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
- & & Model2$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
- & Model2$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
- & & Model3$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
- & & Model3$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
- & Model3$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\
+ & BERT$\colon$\UseMacro{test-results-model0-lc9-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
+ & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
+ & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
+ & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
+ & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\
 \hline
 \bottomrule
-\end{tabular}
-\end{adjustbox}
+\end{tabular}}
 \end{center}

### 2022-05-06 paper/ase22/CM/coverage.tex
exp restuls

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/covergae.pdf}
    \caption{The coverage results of the generated test
      samples. \sw{Make the figures larger.}}
    \label{fig:coverage}
\end{figure}

Fig. \ref{fig:coverage} shows the coverage results of the generated
test samples, where the red line represents \tool and the black line
represents \Cklst.  Each column in Fig. \ref{fig:coverage} represent
the results for one NLP model, the first row is the \textit{BoundCov}
results and the second row is the \textit{SActCov} results.  From the
results, we make two observations observations. First, for \emph{all}
experimental settings (\eg NLP model, coverage metric), \tool achieves
high coverage than \Cklst. Recall that a higher coverage implies the
test case in the test suite is more diverse and rarely to have a
statistical distribution similar to the model training data. As a
result, a test suite with greater coverage complements the model
training data distribution (\ie hold-out testing data) better.  The
experimental results confirm that \tool can generate more diverse test
cases to complement the hold-out testing data for testing NLP models.
\sw{What does the growth trend in each figure indicate?} \sw{Does the
  absolute numbers or relative difference of the two lines on y axis
  mean anything concrete? E.g., how significant is the improvement in
  diversity?}

Another interesting finding is that for each NLP model, there is no
fixed relationship between \textit{BoundCov} and \textit{SActCov}. In
other words, while a test suite may produce higher \textit{BoundCov}
for some models, the same test suite may get higher \textit{SActCov}
for other NLP models.  Recall that \textit{BoundCov} measures both the
upper and lower corner neurons and \textit{SActCov} measures only the
upper corner neurons.  Such observation implies that the upper and
lower corner neurons are distributed unevenly, and measuring only one
of them is not enough.

### 2022-05-06 paper/ase22/experiment.tex
exp restuls

@@
 fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
-searching seeds and expanding the seeds in \tool.
+searching seeds and expanding the seeds in \tool. The \Sstt is a
+corpus of movie review, and it consists of 11,855 single sentences
+with its sentiment score. As original dataset suggests, we split the
+score range into [0, 0.4], (0.4, 0.6] and (0.6, 0.8] for assigning
+    negative, neutral and positive labels respectively.
 %% \TODO{introduce details about each model}
@@
   sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
-  LC\_relevancy_{AVG} &= \frac{1}{\#data}\cdot\sum_{i} LC\_relevancy_i \label{metric:lcrel}
+  LC\_relevancy_{AVG} &= \frac{1}{\#Data\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
 \end{eqnarray}
@@
 equation~\ref{metric:lcrel} represents the average score of the
-relevancy score between sentence and its associated \lc. Higer average
-score means that higher human-level agreement of the use of sentence
-for its \lc, resulting in higher suitability of the use of the
-testcases for evaluating model on the \lc. Given the metrics, we
-answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
-and equation~\ref{metric:lcrel} respectively, thereby, show its
-ability of \tool to understand human intelligence.
+normalized relevancy score between sentence and its associated
+\lc. Higer average score means that higher human-level agreement of
+the use of sentence for its \lc, resulting in higher suitability of
+the use of the testcases for evaluating model on the \lc. Given the
+metrics, we answer RQ1 and RQ2 by the metrics from the
+equation~\ref{metric:srel} and equation~\ref{metric:lcrel}
+respectively, thereby, show its ability of \tool to understand human
+intelligence.
 

### 2022-05-06 paper/ase22/result.tex
table add
table
exp restuls

@@
-\section{Result}
+\section{Experimental Results}
 \label{sec:result}
 
-\subsection{RQ1: Can \tool generate consistent test sentence and
-  its oracle?}
+This section presents experiment results and answer the RQs by
+studying the results quantatively and qualitatively.
 
 \InputWithSpace{tables/manual-study-table}
+\InputWithSpace{tables/test-results-table}
+
+\subsection{RQ1: \tool Sentiment Label Consistency}
+Table~\ref{table:ManualStudy} shows the statistics of scores collected
+from the manual study of \tool. First column represents type of test
+case. The number of test cases used for the study is represented in
+second column. Label consistency score and \lc relevancy score defined
+at equation~\ref{metric:srel} and~\ref{metric:lcrel} are shown at the
+remaining columns. First, it is shown that high label consistency
+score over 0.8. It means that \tool generates test oracles consistent
+to human understanding. It is also observed that there is no
+difference of the scores between seed and expanded sentences. The
+observation implies that the expansion method in \tool preserves
+sentiment of expanded sentences as its seed, and provides its
+reliability. These observations answer RQ1 and conclude that \tool
+generates test case with high consistency between test sentence and
+its oracle.
+
+\subsection{RQ2: Correctness of Linguistic Capability Categorization}
+The result in table~\ref{table:ManualStudy} also shows that \tool
+achieves high order of agreement with human assessment on \lc
+relevancy. In parallel, it is observed that the expanded sentences
+generated from \tool also have same level of \lc
+relevancy. Accordingly, we answer the RQ2 by concluding that
+\tool generates \lc relevant test cases with the agreement with human.
+
+\subsection{RQ3: Test Suite Diversity}
+\input{CM/coverage}
+
+\subsection{RQ4: Use \tool for Debugging}

### 2022-05-06 paper/ase22/tables/test-results-numbers.tex
exp restuls

@@
 \DefMacro{test-results-bl-lc0-num-sents}{8528}
-\DefMacro{test-results-bl-model0-lc0-num-fail}{3741}
+\DefMacro{test-results-bl-model0-lc0-num-fail}{43.87}
 \DefMacro{test-results-lc1}{Negated negative should be positive or neutral}
 \DefMacro{test-results-bl-lc1-num-sents}{6786}
-\DefMacro{test-results-bl-model0-lc1-num-fail}{799}
+\DefMacro{test-results-bl-model0-lc1-num-fail}{11.77}
 \DefMacro{test-results-lc2}{Negated neutral should still be neutral}
 \DefMacro{test-results-bl-lc2-num-sents}{2496}
-\DefMacro{test-results-bl-model0-lc2-num-fail}{2427}
+\DefMacro{test-results-bl-model0-lc2-num-fail}{97.24}
 \DefMacro{test-results-lc3}{Negated positive with neutral content in the middle}
 \DefMacro{test-results-bl-lc3-num-sents}{1000}
-\DefMacro{test-results-bl-model0-lc3-num-fail}{860}
+\DefMacro{test-results-bl-model0-lc3-num-fail}{86.00}
 \DefMacro{test-results-lc4}{Negation of negative at the end, should be positive or neutral}
 \DefMacro{test-results-bl-lc4-num-sents}{2124}
-\DefMacro{test-results-bl-model0-lc4-num-fail}{1871}
+\DefMacro{test-results-bl-model0-lc4-num-fail}{88.09}
 \DefMacro{test-results-lc5}{Sentiment change over time, present should prevail}
 \DefMacro{test-results-bl-lc5-num-sents}{8000}
-\DefMacro{test-results-bl-model0-lc5-num-fail}{1680}
+\DefMacro{test-results-bl-model0-lc5-num-fail}{21.00}
 \DefMacro{test-results-lc6}{Short sentences with neutral adjectives and nouns}
 \DefMacro{test-results-bl-lc6-num-sents}{1716}
-\DefMacro{test-results-bl-model0-lc6-num-fail}{1330}
+\DefMacro{test-results-bl-model0-lc6-num-fail}{77.51}
 \DefMacro{test-results-lc7}{Short sentences with sentiment-laden adjectives}
 \DefMacro{test-results-bl-lc7-num-sents}{8658}
-\DefMacro{test-results-bl-model0-lc7-num-fail}{26}
+\DefMacro{test-results-bl-model0-lc7-num-fail}{0.30}
 \DefMacro{test-results-lc8}{Parsing positive and negative sentiment in (question, no) form}
 \DefMacro{test-results-bl-lc8-num-sents}{7644}
-\DefMacro{test-results-bl-model0-lc8-num-fail}{4056}
+\DefMacro{test-results-bl-model0-lc8-num-fail}{53.06}
 \DefMacro{test-results-lc9}{parsing sentiment in (question, yes) form}
 \DefMacro{test-results-bl-lc9-num-sents}{9204}
-\DefMacro{test-results-bl-model0-lc9-num-fail}{1793}
-\DefMacro{test-results-bl-model1-lc0-num-fail}{2692}
-\DefMacro{test-results-bl-model1-lc1-num-fail}{218}
-\DefMacro{test-results-bl-model1-lc2-num-fail}{2304}
-\DefMacro{test-results-bl-model1-lc3-num-fail}{416}
-\DefMacro{test-results-bl-model1-lc4-num-fail}{445}
-\DefMacro{test-results-bl-model1-lc5-num-fail}{829}
-\DefMacro{test-results-bl-model1-lc6-num-fail}{1391}
-\DefMacro{test-results-bl-model1-lc7-num-fail}{139}
-\DefMacro{test-results-bl-model1-lc8-num-fail}{4576}
-\DefMacro{test-results-bl-model1-lc9-num-fail}{1262}
-\DefMacro{test-results-bl-model2-lc0-num-fail}{3535}
-\DefMacro{test-results-bl-model2-lc1-num-fail}{734}
-\DefMacro{test-results-bl-model2-lc2-num-fail}{2450}
-\DefMacro{test-results-bl-model2-lc3-num-fail}{865}
-\DefMacro{test-results-bl-model2-lc4-num-fail}{2124}
-\DefMacro{test-results-bl-model2-lc5-num-fail}{2532}
-\DefMacro{test-results-bl-model2-lc6-num-fail}{1661}
-\DefMacro{test-results-bl-model2-lc7-num-fail}{125}
-\DefMacro{test-results-bl-model2-lc8-num-fail}{6440}
-\DefMacro{test-results-bl-model2-lc9-num-fail}{1557}
+\DefMacro{test-results-bl-model0-lc9-num-fail}{19.48}
+\DefMacro{test-results-bl-model1-lc0-num-fail}{31.57}
+\DefMacro{test-results-bl-model1-lc1-num-fail}{3.21}
+\DefMacro{test-results-bl-model1-lc2-num-fail}{92.31}
+\DefMacro{test-results-bl-model1-lc3-num-fail}{41.60}
+\DefMacro{test-results-bl-model1-lc4-num-fail}{20.95}
+\DefMacro{test-results-bl-model1-lc5-num-fail}{10.36}
+\DefMacro{test-results-bl-model1-lc6-num-fail}{81.06}
+\DefMacro{test-results-bl-model1-lc7-num-fail}{1.61}
+\DefMacro{test-results-bl-model1-lc8-num-fail}{59.86}
+\DefMacro{test-results-bl-model1-lc9-num-fail}{13.71}
+\DefMacro{test-results-bl-model2-lc0-num-fail}{41.45}
+\DefMacro{test-results-bl-model2-lc1-num-fail}{10.82}
+\DefMacro{test-results-bl-model2-lc2-num-fail}{98.16}
+\DefMacro{test-results-bl-model2-lc3-num-fail}{86.50}
+\DefMacro{test-results-bl-model2-lc4-num-fail}{100.00}
+\DefMacro{test-results-bl-model2-lc5-num-fail}{31.65}
+\DefMacro{test-results-bl-model2-lc6-num-fail}{96.79}
+\DefMacro{test-results-bl-model2-lc7-num-fail}{1.44}
+\DefMacro{test-results-bl-model2-lc8-num-fail}{84.25}
+\DefMacro{test-results-bl-model2-lc9-num-fail}{16.92}
 \DefMacro{test-results-lc0-num-seeds}{50}
 \DefMacro{test-results-lc0-num-exps}{2323}
-\DefMacro{test-results-model0-lc0-num-seed-fail}{22}
-\DefMacro{test-results-model0-lc0-num-exp-fail}{1163}
+\DefMacro{test-results-model0-lc0-num-seed-fail}{44.00}
+\DefMacro{test-results-model0-lc0-num-exp-fail}{50.06}
 \DefMacro{test-results-model0-lc0-num-pass-to-fail}{134}
@@
 \DefMacro{test-results-lc1-num-exps}{1784}
-\DefMacro{test-results-model0-lc1-num-seed-fail}{46}
-\DefMacro{test-results-model0-lc1-num-exp-fail}{1680}
+\DefMacro{test-results-model0-lc1-num-seed-fail}{92.00}
+\DefMacro{test-results-model0-lc1-num-exp-fail}{94.17}
 \DefMacro{test-results-model0-lc1-num-pass-to-fail}{49}
@@
 \DefMacro{test-results-lc2-num-exps}{1009}
-\DefMacro{test-results-model0-lc2-num-seed-fail}{24}
-\DefMacro{test-results-model0-lc2-num-exp-fail}{932}
+\DefMacro{test-results-model0-lc2-num-seed-fail}{92.31}
+\DefMacro{test-results-model0-lc2-num-exp-fail}{92.37}
 \DefMacro{test-results-model0-lc2-num-pass-to-fail}{62}
@@
 \DefMacro{test-results-lc3-num-exps}{1634}
-\DefMacro{test-results-model0-lc3-num-seed-fail}{42}
-\DefMacro{test-results-model0-lc3-num-exp-fail}{1438}
+\DefMacro{test-results-model0-lc3-num-seed-fail}{84.00}
+\DefMacro{test-results-model0-lc3-num-exp-fail}{88.00}
 \DefMacro{test-results-model0-lc3-num-pass-to-fail}{40}
@@
 \DefMacro{test-results-lc4-num-exps}{1486}
-\DefMacro{test-results-model0-lc4-num-seed-fail}{50}
-\DefMacro{test-results-model0-lc4-num-exp-fail}{1486}
+\DefMacro{test-results-model0-lc4-num-seed-fail}{100.00}
+\DefMacro{test-results-model0-lc4-num-exp-fail}{100.00}
 \DefMacro{test-results-model0-lc4-num-pass-to-fail}{0}
@@
 \DefMacro{test-results-lc8-num-exps}{2379}
-\DefMacro{test-results-model0-lc8-num-seed-fail}{71}
-\DefMacro{test-results-model0-lc8-num-exp-fail}{1723}
+\DefMacro{test-results-model0-lc8-num-seed-fail}{71.00}
+\DefMacro{test-results-model0-lc8-num-exp-fail}{72.43}
 \DefMacro{test-results-model0-lc8-num-pass-to-fail}{40}
@@
 \DefMacro{test-results-lc5-num-exps}{-}
-\DefMacro{test-results-model0-lc5-num-seed-fail}{12}
+\DefMacro{test-results-model0-lc5-num-seed-fail}{24.00}
 \DefMacro{test-results-model0-lc5-num-exp-fail}{-}
@@
 \DefMacro{test-results-lc6-num-exps}{210}
-\DefMacro{test-results-model0-lc6-num-seed-fail}{15}
-\DefMacro{test-results-model0-lc6-num-exp-fail}{182}
+\DefMacro{test-results-model0-lc6-num-seed-fail}{78.95}
+\DefMacro{test-results-model0-lc6-num-exp-fail}{86.67}
 \DefMacro{test-results-model0-lc6-num-pass-to-fail}{19}
@@
 \DefMacro{test-results-lc7-num-exps}{394}
-\DefMacro{test-results-model0-lc7-num-seed-fail}{2}
-\DefMacro{test-results-model0-lc7-num-exp-fail}{17}
+\DefMacro{test-results-model0-lc7-num-seed-fail}{4.00}
+\DefMacro{test-results-model0-lc7-num-exp-fail}{4.31}
 \DefMacro{test-results-model0-lc7-num-pass-to-fail}{4}
@@
 \DefMacro{test-results-lc9-num-exps}{1373}
-\DefMacro{test-results-model0-lc9-num-seed-fail}{2}
-\DefMacro{test-results-model0-lc9-num-exp-fail}{37}
+\DefMacro{test-results-model0-lc9-num-seed-fail}{4.00}
+\DefMacro{test-results-model0-lc9-num-exp-fail}{2.69}
 \DefMacro{test-results-model0-lc9-num-pass-to-fail}{43}
-\DefMacro{test-results-model1-lc0-num-seed-fail}{13}
-\DefMacro{test-results-model1-lc0-num-exp-fail}{725}
+\DefMacro{test-results-model1-lc0-num-seed-fail}{26.00}
+\DefMacro{test-results-model1-lc0-num-exp-fail}{31.21}
 \DefMacro{test-results-model1-lc0-num-pass-to-fail}{78}
-\DefMacro{test-results-model1-lc1-num-seed-fail}{41}
-\DefMacro{test-results-model1-lc1-num-exp-fail}{1537}
+\DefMacro{test-results-model1-lc1-num-seed-fail}{82.00}
+\DefMacro{test-results-model1-lc1-num-exp-fail}{86.15}
 \DefMacro{test-results-model1-lc1-num-pass-to-fail}{64}
-\DefMacro{test-results-model1-lc2-num-seed-fail}{24}
-\DefMacro{test-results-model1-lc2-num-exp-fail}{939}
+\DefMacro{test-results-model1-lc2-num-seed-fail}{92.31}
+\DefMacro{test-results-model1-lc2-num-exp-fail}{93.06}
 \DefMacro{test-results-model1-lc2-num-pass-to-fail}{38}
-\DefMacro{test-results-model1-lc3-num-seed-fail}{21}
-\DefMacro{test-results-model1-lc3-num-exp-fail}{664}
+\DefMacro{test-results-model1-lc3-num-seed-fail}{42.00}
+\DefMacro{test-results-model1-lc3-num-exp-fail}{40.64}
 \DefMacro{test-results-model1-lc3-num-pass-to-fail}{54}
-\DefMacro{test-results-model1-lc4-num-seed-fail}{50}
-\DefMacro{test-results-model1-lc4-num-exp-fail}{1486}
+\DefMacro{test-results-model1-lc4-num-seed-fail}{100.00}
+\DefMacro{test-results-model1-lc4-num-exp-fail}{100.00}
 \DefMacro{test-results-model1-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-model1-lc8-num-seed-fail}{79}
-\DefMacro{test-results-model1-lc8-num-exp-fail}{1947}
+\DefMacro{test-results-model1-lc8-num-seed-fail}{79.00}
+\DefMacro{test-results-model1-lc8-num-exp-fail}{81.84}
 \DefMacro{test-results-model1-lc8-num-pass-to-fail}{18}
-\DefMacro{test-results-model1-lc5-num-seed-fail}{28}
+\DefMacro{test-results-model1-lc5-num-seed-fail}{56.00}
 \DefMacro{test-results-model1-lc5-num-exp-fail}{-}
 \DefMacro{test-results-model1-lc5-num-pass-to-fail}{-}
-\DefMacro{test-results-model1-lc6-num-seed-fail}{17}
-\DefMacro{test-results-model1-lc6-num-exp-fail}{160}
+\DefMacro{test-results-model1-lc6-num-seed-fail}{89.47}
+\DefMacro{test-results-model1-lc6-num-exp-fail}{76.19}
 \DefMacro{test-results-model1-lc6-num-pass-to-fail}{9}
-\DefMacro{test-results-model1-lc7-num-seed-fail}{2}
-\DefMacro{test-results-model1-lc7-num-exp-fail}{19}
+\DefMacro{test-results-model1-lc7-num-seed-fail}{4.00}
+\DefMacro{test-results-model1-lc7-num-exp-fail}{4.82}
 \DefMacro{test-results-model1-lc7-num-pass-to-fail}{5}
-\DefMacro{test-results-model1-lc9-num-seed-fail}{1}
-\DefMacro{test-results-model1-lc9-num-exp-fail}{57}
+\DefMacro{test-results-model1-lc9-num-seed-fail}{2.00}
+\DefMacro{test-results-model1-lc9-num-exp-fail}{4.15}
 \DefMacro{test-results-model1-lc9-num-pass-to-fail}{46}
-\DefMacro{test-results-model2-lc0-num-seed-fail}{20}
-\DefMacro{test-results-model2-lc0-num-exp-fail}{1040}
+\DefMacro{test-results-model2-lc0-num-seed-fail}{40.00}
+\DefMacro{test-results-model2-lc0-num-exp-fail}{44.77}
 \DefMacro{test-results-model2-lc0-num-pass-to-fail}{31}
-\DefMacro{test-results-model2-lc1-num-seed-fail}{44}
-\DefMacro{test-results-model2-lc1-num-exp-fail}{1579}
+\DefMacro{test-results-model2-lc1-num-seed-fail}{88.00}
+\DefMacro{test-results-model2-lc1-num-exp-fail}{88.51}
 \DefMacro{test-results-model2-lc1-num-pass-to-fail}{26}
-\DefMacro{test-results-model2-lc2-num-seed-fail}{24}
-\DefMacro{test-results-model2-lc2-num-exp-fail}{961}
+\DefMacro{test-results-model2-lc2-num-seed-fail}{92.31}
+\DefMacro{test-results-model2-lc2-num-exp-fail}{95.24}
 \DefMacro{test-results-model2-lc2-num-pass-to-fail}{74}
-\DefMacro{test-results-model2-lc3-num-seed-fail}{38}
-\DefMacro{test-results-model2-lc3-num-exp-fail}{1280}
+\DefMacro{test-results-model2-lc3-num-seed-fail}{76.00}
+\DefMacro{test-results-model2-lc3-num-exp-fail}{78.34}
 \DefMacro{test-results-model2-lc3-num-pass-to-fail}{9}
-\DefMacro{test-results-model2-lc4-num-seed-fail}{50}
-\DefMacro{test-results-model2-lc4-num-exp-fail}{1486}
+\DefMacro{test-results-model2-lc4-num-seed-fail}{100.00}
+\DefMacro{test-results-model2-lc4-num-exp-fail}{100.00}
 \DefMacro{test-results-model2-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-model2-lc8-num-seed-fail}{93}
-\DefMacro{test-results-model2-lc8-num-exp-fail}{2216}
+\DefMacro{test-results-model2-lc8-num-seed-fail}{93.00}
+\DefMacro{test-results-model2-lc8-num-exp-fail}{93.15}
 \DefMacro{test-results-model2-lc8-num-pass-to-fail}{12}
-\DefMacro{test-results-model2-lc5-num-seed-fail}{39}
+\DefMacro{test-results-model2-lc5-num-seed-fail}{78.00}
 \DefMacro{test-results-model2-lc5-num-exp-fail}{-}
 \DefMacro{test-results-model2-lc5-num-pass-to-fail}{-}
-\DefMacro{test-results-model2-lc6-num-seed-fail}{19}
-\DefMacro{test-results-model2-lc6-num-exp-fail}{198}
+\DefMacro{test-results-model2-lc6-num-seed-fail}{100.00}
+\DefMacro{test-results-model2-lc6-num-exp-fail}{94.29}
 \DefMacro{test-results-model2-lc6-num-pass-to-fail}{0}
-\DefMacro{test-results-model2-lc7-num-seed-fail}{1}
-\DefMacro{test-results-model2-lc7-num-exp-fail}{11}
+\DefMacro{test-results-model2-lc7-num-seed-fail}{2.00}
+\DefMacro{test-results-model2-lc7-num-exp-fail}{2.79}
 \DefMacro{test-results-model2-lc7-num-pass-to-fail}{8}
-\DefMacro{test-results-model2-lc9-num-seed-fail}{3}
-\DefMacro{test-results-model2-lc9-num-exp-fail}{76}
+\DefMacro{test-results-model2-lc9-num-seed-fail}{6.00}
+\DefMacro{test-results-model2-lc9-num-exp-fail}{5.54}
 \DefMacro{test-results-model2-lc9-num-pass-to-fail}{14}

### 2022-05-06 paper/ase22/tables/test-results-table.tex
exp restuls

@@
 \toprule
-\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.4cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.3cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\
+\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\
 \midrule

### 2022-05-06 python/sa/exp/Humanstudy.py
debugging

@@ -372,6 +372,10 @@ class Humanstudy:
         return res
 
     @classmethod
+    def norm_lc_relevancy(cls, scores, min_val=1, max_val=5):
+        return [(s-min_val)/(max_val-min_val) for s in scores]
+
+    @classmethod
     def get_reported_bugs(cls,
                           pred_results,
                           tgt_results,
@@ -514,6 +518,8 @@ class Humanstudy:
             agg_exp_label_scores.extend(list(res[f_i]['label_scores']['exp'].values()))
             agg_exp_lc_scores.extend(list(res[f_i]['lc_scores']['exp'].values()))
         # end for
+        agg_seed_lc_scores = cls.norm_lc_relevancy(agg_seed_lc_scores)
+        agg_exp_lc_scores = cls.norm_lc_relevancy(agg_exp_lc_scores)
         
         res['agg'] = {
             'seed': {

### 2022-05-06 python/sa/paper/Tables.py

@@ -370,15 +370,15 @@ class Tables:
         output_file.append_macro(latex.Macro(f"manual-study-seed-num-sents",
                                              seed_agg_result['num_sents']))
         output_file.append_macro(latex.Macro(f"manual-study-seed-label-consistency",
-                                             seed_agg_result['avg_label_score']))
+                                             cls.FMT_FLOAT.format(round(seed_agg_result['avg_label_score'],2))))
         output_file.append_macro(latex.Macro(f"manual-study-seed-lc-relevancy",
-                                             seed_agg_result['avg_lc_score']/5.))
+                                             cls.FMT_FLOAT.format(round(seed_agg_result['avg_lc_score'],2))))
         output_file.append_macro(latex.Macro(f"manual-study-exp-num-sents",
                                              exp_agg_result['num_sents']))
         output_file.append_macro(latex.Macro(f"manual-study-exp-label-consistency",
-                                             exp_agg_result['avg_label_score']))
+                                             cls.FMT_FLOAT.format(round(exp_agg_result['avg_label_score'],2))))
         output_file.append_macro(latex.Macro(f"manual-study-exp-lc-relevancy",
-                                             exp_agg_result['avg_lc_score']/5.))
+                                             cls.FMT_FLOAT.format(round(exp_agg_result['avg_lc_score'],2))))
         output_file.save()
         return
 
@@ -458,12 +458,11 @@ class Tables:
                                                          res['num_tcs']))
                 # end if
                 output_file.append_macro(latex.Macro(f"test-results-bl-model{m_i}-lc{res_i}-num-fail",
-                                                     res['num_tc_fail']))
+                                                     cls.FMT_FLOAT.format(res['num_tc_fail']*100./res['num_tcs'])))
             # end for
         # end for
         
         for m_i, model_name in enumerate(result.keys()):
-            print(m_i, model_name)
             # model_name = model_name.replace('/', '-')
             temp_num_seeds, temp_num_exps = 0,0
             temp_num_seed_fail, temp_num_exp_fail = 0,0
@@ -479,6 +478,8 @@ class Tables:
[…]

### 2022-05-06 python/sa/paper/Tables.py
revise table

@@ -563,27 +563,29 @@ class Tables:
         output_file.append(r"\begin{small}")
         output_file.append(r"\begin{center}")
         output_file.append(r"\caption{\TestResultsTableCaption}")
-        output_file.append(r"\resizebox{\textwidth}{!}{")
-        output_file.append(r"\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}")
+        output_file.append(r"\resizebox{0.9\textwidth}{!}{")
+        # output_file.append(r"\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}")
+        output_file.append(r"\begin{tabular}{p{8cm}||cclll}")
         output_file.append(r"\toprule")
         
-        output_file.append(r"\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\")
+        # output_file.append(r"\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\")
+        output_file.append(r"\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumSeedFail} & \parbox{1.5cm}{\centering\tNumExpFail} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\")
         output_file.append(r"\midrule")
-
+        
         # Content
         for lc_i in range(lcs_len):
-            output_file.append("\multirow{"+str(len(model_names))+"}{*}{\parbox{4cm}{" + \
+            output_file.append("\multirow{"+str(len(model_names))+"}{*}{\parbox{8cm}{" + \
                                f"LC{lc_i+1}: " + latex.Macro(f"test-results-lc{lc_i}").use() + "}}")
[…]

### 2022-05-06 paper/ase22/intro.tex
revise table3

@@
 
-\noindent \textbf{C1.} generating sentences with diverse syntactic
-structure is challenging since text have a higher order of its
-structure. However, the structures are obscured by word usage. To
-address the challenge, \tool establishes specifications for evaluating
-a linguistic capability and searches suitable sentences that satisfy
-the specification from existing public dataset. In this process, \tool
+\noindent \textbf{C1.} The first challenge comes with the second and
+third challenges of maintaining the label and linguistic capability of
+the test sentence while making the syntactic structure of the sentence
+more diverse. In addition, text have a higher order of structures and
+structures are obscured by word usage~\cite{}. To address the
+challenge, \tool establishes specifications for evaluating a
+linguistic capability and searches suitable sentences that satisfy the
+specification from existing public dataset. In this process, \tool
 generates new inputs by mutating the searched sentences, used as seed
@@
 
-\noindent \textbf{C2.} Suitability of test case for evaluating NLP
-model on a \lc is obtained from its high relevancy to the
-\lc. Relevancy between test case and \lc is difficult to be measured
-because the \lc is defined on a specific phenomenon appeared in the
-mixture of textual structure and semantic, and understanding each test
-case with respect to the phenomenon and measuring its relevancy are
-not trivial. To address the difficulty, \tool implements search rules
-and the transformation templates of \lcs. In addition, anlyzing parse
-tree of seed sentence is used for its expansion identification.
+\noindent \textbf{C2.} Suitability of test sentences for evaluating
+NLP model on a \lc is obtained from its high relevancy to the
+\lc. Relevancy between a test sentence and its \lc is challenging to
+be maintained during the transformation and expansion of the test
+sentence.  This is because the \lc is defined on a specific mixture of
+syntaxe and semantics of the sentence, and there exists no automatic
+way to check the consistency between each sentence with the semantics
+specified in corresponding \lc due to the inherent ambiguity of
+natural language sentences. To address the difficulty, \tool
+implements search rules and the transformation templates of \lcs. In
+addition, anlyzing parse tree of seed sentence is used for its
+expansion identification.
 %% \tool adopts behavioral model testing method by
@@
 
-\noindent \textbf{C3.} Last challenge is on estimating the
-appropriateness of test oracle. For \sa task, test oracle is
-determined by understanding meaning from text. The meaning of text is
-sensitive to its semnatic, structure, and the combination of
-two. Therefore, generation of test case ought to ensure the
-correctness of its oracle allocation. In this work, \tool obtain the
-appropriateness of test oracle by implementing domain-specific
-knowledge on word sentiment dataset and word suggestion model
-pre-trained on large corpus for validation of generated sentence and
-its oracle.
+\noindent \textbf{C3.} Last challenge is on automated test oracle.
+For NLP tasks, test oracle is determined by understanding meaning from
+texts. This requires domain knowledge for different NLP tasks
+% Therefore, generation of test case ought to ensure the
+%correctness of its oracle allocation.
+In this work, as a first step, we consider \sa as the NLP task for the
+models under test. \tool obtain the appropriateness of test oracle by
+implementing domain-specific knowledge on word sentiment dataset and
+word suggestion model pre-trained on large corpus for validation of
+generated sentence and its oracle.
 

### 2022-05-06 paper/ase22/result.tex
revise table3

@@
 
+\jl{The following needs to be in RQ2 result section after simin
+  completes RQ2 result section} Table~\ref{table:TestResult} shows
+results of evaluation of three \sa models. First column lists
+linguistic capability for \sa task, and Columns 2-3 show the number of
+seed and expanded test cases respectively. Columns 4-5 show the
+failure rate in percentage by running the \sa models on the seed and
+expanded test cases respectively. Column 6 shows the number of
+expanded test cases failed, but their seed test cases passed. For LC9,
+we combine two
+
+From the
+table, we can observe that
+
 \subsection{RQ3: Test Suite Diversity}

### 2022-05-06 paper/ase22/tables/test-results-numbers.tex
revise table3

--- 2022-05-05 paper/ase22/tables/test-results-numbers.tex
@@
 
-\DefMacro{test-results-lc0}{Author sentiment is more important than of others}
-\DefMacro{test-results-bl-lc0-num-sents}{8528}
-\DefMacro{test-results-bl-model0-lc0-num-fail}{3741}
-\DefMacro{test-results-lc1}{Negated negative should be positive or neutral}
-\DefMacro{test-results-bl-lc1-num-sents}{6786}
-\DefMacro{test-results-bl-model0-lc1-num-fail}{799}
-\DefMacro{test-results-lc2}{Negated neutral should still be neutral}
-\DefMacro{test-results-bl-lc2-num-sents}{2496}
-\DefMacro{test-results-bl-model0-lc2-num-fail}{2427}
-\DefMacro{test-results-lc3}{Negated positive with neutral content in the middle}
-\DefMacro{test-results-bl-lc3-num-sents}{1000}
-\DefMacro{test-results-bl-model0-lc3-num-fail}{860}
-\DefMacro{test-results-lc4}{Negation of negative at the end, should be positive or neutral}
-\DefMacro{test-results-bl-lc4-num-sents}{2124}
-\DefMacro{test-results-bl-model0-lc4-num-fail}{1871}
-\DefMacro{test-results-lc5}{Sentiment change over time, present should prevail}
-\DefMacro{test-results-bl-lc5-num-sents}{8000}
-\DefMacro{test-results-bl-model0-lc5-num-fail}{1680}
-\DefMacro{test-results-lc6}{Short sentences with neutral adjectives and nouns}
-\DefMacro{test-results-bl-lc6-num-sents}{1716}
-\DefMacro{test-results-bl-model0-lc6-num-fail}{1330}
-\DefMacro{test-results-lc7}{Short sentences with sentiment-laden adjectives}
-\DefMacro{test-results-bl-lc7-num-sents}{8658}
-\DefMacro{test-results-bl-model0-lc7-num-fail}{26}
-\DefMacro{test-results-lc8}{Parsing positive and negative sentiment in (question, no) form}
-\DefMacro{test-results-bl-lc8-num-sents}{7644}
-\DefMacro{test-results-bl-model0-lc8-num-fail}{4056}
-\DefMacro{test-results-lc9}{parsing sentiment in (question, yes) form}
-\DefMacro{test-results-bl-lc9-num-sents}{9204}
-\DefMacro{test-results-bl-model0-lc9-num-fail}{1793}
-\DefMacro{test-results-bl-model1-lc0-num-fail}{2692}
-\DefMacro{test-results-bl-model1-lc1-num-fail}{218}
-\DefMacro{test-results-bl-model1-lc2-num-fail}{2304}
-\DefMacro{test-results-bl-model1-lc3-num-fail}{416}
-\DefMacro{test-results-bl-model1-lc4-num-fail}{445}
-\DefMacro{test-results-bl-model1-lc5-num-fail}{829}
-\DefMacro{test-results-bl-model1-lc6-num-fail}{1391}
-\DefMacro{test-results-bl-model1-lc7-num-fail}{139}
-\DefMacro{test-results-bl-model1-lc8-num-fail}{4576}
-\DefMacro{test-results-bl-model1-lc9-num-fail}{1262}
-\DefMacro{test-results-bl-model2-lc0-num-fail}{3535}
-\DefMacro{test-results-bl-model2-lc1-num-fail}{734}
-\DefMacro{test-results-bl-model2-lc2-num-fail}{2450}
-\DefMacro{test-results-bl-model2-lc3-num-fail}{865}
-\DefMacro{test-results-bl-model2-lc4-num-fail}{2124}
-\DefMacro{test-results-bl-model2-lc5-num-fail}{2532}
-\DefMacro{test-results-bl-model2-lc6-num-fail}{1661}
-\DefMacro{test-results-bl-model2-lc7-num-fail}{125}
-\DefMacro{test-results-bl-model2-lc8-num-fail}{6440}
-\DefMacro{test-results-bl-model2-lc9-num-fail}{1557}
-\DefMacro{test-results-lc0-num-seeds}{50}
-\DefMacro{test-results-lc0-num-exps}{2323}
-\DefMacro{test-results-model0-lc0-num-seed-fail}{22}
-\DefMacro{test-results-model0-lc0-num-exp-fail}{1163}
-\DefMacro{test-results-model0-lc0-num-pass-to-fail}{134}
+\DefMacro{test-results-lc7}{Author sentiment is more important than of others}
+\DefMacro{test-results-bl-lc7-num-sents}{8528}
+\DefMacro{test-results-bl-model0-lc7-num-fail}{43.87}
+\DefMacro{test-results-lc3}{Negated negative should be positive or neutral}
+\DefMacro{test-results-bl-lc3-num-sents}{6786}
+\DefMacro{test-results-bl-model0-lc3-num-fail}{11.77}
+\DefMacro{test-results-lc4}{Negated neutral should still be neutral}
+\DefMacro{test-results-bl-lc4-num-sents}{2496}
+\DefMacro{test-results-bl-model0-lc4-num-fail}{97.24}
+\DefMacro{test-results-lc6}{Negated positive with neutral content in the middle}
+\DefMacro{test-results-bl-lc6-num-sents}{1000}
+\DefMacro{test-results-bl-model0-lc6-num-fail}{86.00}
+\DefMacro{test-results-lc5}{Negation of negative at the end, should be positive or neutral}
+\DefMacro{test-results-bl-lc5-num-sents}{2124}
+\DefMacro{test-results-bl-model0-lc5-num-fail}{88.09}
+\DefMacro{test-results-lc2}{Sentiment change over time, present should prevail}
+\DefMacro{test-results-bl-lc2-num-sents}{8000}
+\DefMacro{test-results-bl-model0-lc2-num-fail}{21.00}
+\DefMacro{test-results-lc0}{Short sentences with neutral adjectives and nouns}
+\DefMacro{test-results-bl-lc0-num-sents}{1716}
+\DefMacro{test-results-bl-model0-lc0-num-fail}{77.51}
+\DefMacro{test-results-lc1}{Short sentences with sentiment-laden adjectives}
+\DefMacro{test-results-bl-lc1-num-sents}{8658}
+\DefMacro{test-results-bl-model0-lc1-num-fail}{0.30}
+\DefMacro{test-results-lc9}{Parsing positive and negative sentiment in (question, no) form}
+\DefMacro{test-results-bl-lc9-num-sents}{7644}
+\DefMacro{test-results-bl-model0-lc9-num-fail}{53.06}
+\DefMacro{test-results-lc8}{Parsing sentiment in (question, yes) form}
+\DefMacro{test-results-bl-lc8-num-sents}{9204}
+\DefMacro{test-results-bl-model0-lc8-num-fail}{19.48}
+\DefMacro{test-results-bl-model1-lc7-num-fail}{31.57}
+\DefMacro{test-results-bl-model1-lc3-num-fail}{3.21}
+\DefMacro{test-results-bl-model1-lc4-num-fail}{92.31}
+\DefMacro{test-results-bl-model1-lc6-num-fail}{41.60}
+\DefMacro{test-results-bl-model1-lc5-num-fail}{20.95}
+\DefMacro{test-results-bl-model1-lc2-num-fail}{10.36}
+\DefMacro{test-results-bl-model1-lc0-num-fail}{81.06}
+\DefMacro{test-results-bl-model1-lc1-num-fail}{1.61}
+\DefMacro{test-results-bl-model1-lc9-num-fail}{59.86}
+\DefMacro{test-results-bl-model1-lc8-num-fail}{13.71}
+\DefMacro{test-results-bl-model2-lc7-num-fail}{41.45}
+\DefMacro{test-results-bl-model2-lc3-num-fail}{10.82}
+\DefMacro{test-results-bl-model2-lc4-num-fail}{98.16}
+\DefMacro{test-results-bl-model2-lc6-num-fail}{86.50}
+\DefMacro{test-results-bl-model2-lc5-num-fail}{100.00}
+\DefMacro{test-results-bl-model2-lc2-num-fail}{31.65}
+\DefMacro{test-results-bl-model2-lc0-num-fail}{96.79}
+\DefMacro{test-results-bl-model2-lc1-num-fail}{1.44}
+\DefMacro{test-results-bl-model2-lc9-num-fail}{84.25}
+\DefMacro{test-results-bl-model2-lc8-num-fail}{16.92}
+\DefMacro{test-results-lc7-num-seeds}{50}
+\DefMacro{test-results-lc7-num-exps}{2323}
+\DefMacro{test-results-model0-lc7-num-seed-fail}{44.00}
+\DefMacro{test-results-model0-lc7-num-exp-fail}{50.06}
+\DefMacro{test-results-model0-lc7-num-pass-to-fail}{134}
+\DefMacro{test-results-lc3-num-seeds}{50}
+\DefMacro{test-results-lc3-num-exps}{1784}
+\DefMacro{test-results-model0-lc3-num-seed-fail}{92.00}
+\DefMacro{test-results-model0-lc3-num-exp-fail}{94.17}
+\DefMacro{test-results-model0-lc3-num-pass-to-fail}{49}
+\DefMacro{test-results-lc4-num-seeds}{26}
+\DefMacro{test-results-lc4-num-exps}{1009}
+\DefMacro{test-results-model0-lc4-num-seed-fail}{92.31}
+\DefMacro{test-results-model0-lc4-num-exp-fail}{92.37}
+\DefMacro{test-results-model0-lc4-num-pass-to-fail}{62}
+\DefMacro{test-results-lc6-num-seeds}{50}
+\DefMacro{test-results-lc6-num-exps}{1634}
+\DefMacro{test-results-model0-lc6-num-seed-fail}{84.00}
+\DefMacro{test-results-model0-lc6-num-exp-fail}{88.00}
+\DefMacro{test-results-model0-lc6-num-pass-to-fail}{40}
+\DefMacro{test-results-lc5-num-seeds}{50}
+\DefMacro{test-results-lc5-num-exps}{1486}
+\DefMacro{test-results-model0-lc5-num-seed-fail}{100.00}
+\DefMacro{test-results-model0-lc5-num-exp-fail}{100.00}
+\DefMacro{test-results-model0-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-lc9-num-seeds}{100}
+\DefMacro{test-results-lc9-num-exps}{2379}
+\DefMacro{test-results-model0-lc9-num-seed-fail}{71.00}
+\DefMacro{test-results-model0-lc9-num-exp-fail}{72.43}
+\DefMacro{test-results-model0-lc9-num-pass-to-fail}{40}
+\DefMacro{test-results-lc2-num-seeds}{50}
+\DefMacro{test-results-lc2-num-exps}{-}
+\DefMacro{test-results-model0-lc2-num-seed-fail}{24.00}
+\DefMacro{test-results-model0-lc2-num-exp-fail}{-}
+\DefMacro{test-results-model0-lc2-num-pass-to-fail}{-}
+\DefMacro{test-results-lc0-num-seeds}{19}
+\DefMacro{test-results-lc0-num-exps}{210}
+\DefMacro{test-results-model0-lc0-num-seed-fail}{78.95}
+\DefMacro{test-results-model0-lc0-num-exp-fail}{86.67}
+\DefMacro{test-results-model0-lc0-num-pass-to-fail}{19}
 \DefMacro{test-results-lc1-num-seeds}{50}
-\DefMacro{test-results-lc1-num-exps}{1784}
-\DefMacro{test-results-model0-lc1-num-seed-fail}{46}
-\DefMacro{test-results-model0-lc1-num-exp-fail}{1680}
-\DefMacro{test-results-model0-lc1-num-pass-to-fail}{49}
-\DefMacro{test-results-lc2-num-seeds}{26}
-\DefMacro{test-results-lc2-num-exps}{1009}
-\DefMacro{test-results-model0-lc2-num-seed-fail}{24}
-\DefMacro{test-results-model0-lc2-num-exp-fail}{932}
-\DefMacro{test-results-model0-lc2-num-pass-to-fail}{62}
-\DefMacro{test-results-lc3-num-seeds}{50}
-\DefMacro{test-results-lc3-num-exps}{1634}
-\DefMacro{test-results-model0-lc3-num-seed-fail}{42}
-\DefMacro{test-results-model0-lc3-num-exp-fail}{1438}
-\DefMacro{test-results-model0-lc3-num-pass-to-fail}{40}
-\DefMacro{test-results-lc4-num-seeds}{50}
-\DefMacro{test-results-lc4-num-exps}{1486}
-\DefMacro{test-results-model0-lc4-num-seed-fail}{50}
-\DefMacro{test-results-model0-lc4-num-exp-fail}{1486}
-\DefMacro{test-results-model0-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-lc8-num-seeds}{100}
-\DefMacro{test-results-lc8-num-exps}{2379}
-\DefMacro{test-results-model0-lc8-num-seed-fail}{71}
-\DefMacro{test-results-model0-lc8-num-exp-fail}{1723}
-\DefMacro{test-results-model0-lc8-num-pass-to-fail}{40}
-\DefMacro{test-results-lc5-num-seeds}{50}
-\DefMacro{test-results-lc5-num-exps}{-}
-\DefMacro{test-results-model0-lc5-num-seed-fail}{12}
-\DefMacro{test-results-model0-lc5-num-exp-fail}{-}
-\DefMacro{test-results-model0-lc5-num-pass-to-fail}{-}
-\DefMacro{test-results-lc6-num-seeds}{19}
-\DefMacro{test-results-lc6-num-exps}{210}
-\DefMacro{test-results-model0-lc6-num-seed-fail}{15}
-\DefMacro{test-results-model0-lc6-num-exp-fail}{182}
-\DefMacro{test-results-model0-lc6-num-pass-to-fail}{19}
-\DefMacro{test-results-lc7-num-seeds}{50}
-\DefMacro{test-results-lc7-num-exps}{394}
-\DefMacro{test-results-model0-lc7-num-seed-fail}{2}
-\DefMacro{test-results-model0-lc7-num-exp-fail}{17}
-\DefMacro{test-results-model0-lc7-num-pass-to-fail}{4}
-\DefMacro{test-results-lc9-num-seeds}{50}
-\DefMacro{test-results-lc9-num-exps}{1373}
-\DefMacro{test-results-model0-lc9-num-seed-fail}{2}
-\DefMacro{test-results-model0-lc9-num-exp-fail}{37}
-\DefMacro{test-results-model0-lc9-num-pass-to-fail}{43}
-\DefMacro{test-results-model1-lc0-num-seed-fail}{13}
-\DefMacro{test-results-model1-lc0-num-exp-fail}{725}
-\DefMacro{test-results-model1-lc0-num-pass-to-fail}{78}
-\DefMacro{test-results-model1-lc1-num-seed-fail}{41}
-\DefMacro{test-results-model1-lc1-num-exp-fail}{1537}
-\DefMacro{test-results-model1-lc1-num-pass-to-fail}{64}
-\DefMacro{test-results-model1-lc2-num-seed-fail}{24}
-\DefMacro{test-results-model1-lc2-num-exp-fail}{939}
-\DefMacro{test-results-model1-lc2-num-pass-to-fail}{38}
-\DefMacro{test-results-model1-lc3-num-seed-fail}{21}
-\DefMacro{test-results-model1-lc3-num-exp-fail}{664}
-\DefMacro{test-results-model1-lc3-num-pass-to-fail}{54}
-\DefMacro{test-results-model1-lc4-num-seed-fail}{50}
-\DefMacro{test-results-model1-lc4-num-exp-fail}{1486}
-\DefMacro{test-results-model1-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-model1-lc8-num-seed-fail}{79}
-\DefMacro{test-results-model1-lc8-num-exp-fail}{1947}
-\DefMacro{test-results-model1-lc8-num-pass-to-fail}{18}
-\DefMacro{test-results-model1-lc5-num-seed-fail}{28}
-\DefMacro{test-results-model1-lc5-num-exp-fail}{-}
-\DefMacro{test-results-model1-lc5-num-pass-to-fail}{-}
-\DefMacro{test-results-model1-lc6-num-seed-fail}{17}
-\DefMacro{test-results-model1-lc6-num-exp-fail}{160}
-\DefMacro{test-results-model1-lc6-num-pass-to-fail}{9}
-\DefMacro{test-results-model1-lc7-num-seed-fail}{2}
-\DefMacro{test-results-model1-lc7-num-exp-fail}{19}
-\DefMacro{test-results-model1-lc7-num-pass-to-fail}{5}
-\DefMacro{test-results-model1-lc9-num-seed-fail}{1}
-\DefMacro{test-results-model1-lc9-num-exp-fail}{57}
-\DefMacro{test-results-model1-lc9-num-pass-to-fail}{46}
-\DefMacro{test-results-model2-lc0-num-seed-fail}{20}
-\DefMacro{test-results-model2-lc0-num-exp-fail}{1040}
-\DefMacro{test-results-model2-lc0-num-pass-to-fail}{31}
-\DefMacro{test-results-model2-lc1-num-seed-fail}{44}
-\DefMacro{test-results-model2-lc1-num-exp-fail}{1579}
-\DefMacro{test-results-model2-lc1-num-pass-to-fail}{26}
-\DefMacro{test-results-model2-lc2-num-seed-fail}{24}
-\DefMacro{test-results-model2-lc2-num-exp-fail}{961}
-\DefMacro{test-results-model2-lc2-num-pass-to-fail}{74}
-\DefMacro{test-results-model2-lc3-num-seed-fail}{38}
-\DefMacro{test-results-model2-lc3-num-exp-fail}{1280}
-\DefMacro{test-results-model2-lc3-num-pass-to-fail}{9}
-\DefMacro{test-results-model2-lc4-num-seed-fail}{50}
-\DefMacro{test-results-model2-lc4-num-exp-fail}{1486}
-\DefMacro{test-results-model2-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-model2-lc8-num-seed-fail}{93}
-\DefMacro{test-results-model2-lc8-num-exp-fail}{2216}
-\DefMacro{test-results-model2-lc8-num-pass-to-fail}{12}
-\DefMacro{test-results-model2-lc5-num-seed-fail}{39}
-\DefMacro{test-results-model2-lc5-num-exp-fail}{-}
-\DefMacro{test-results-model2-lc5-num-pass-to-fail}{-}
-\DefMacro{test-results-model2-lc6-num-seed-fail}{19}
-\DefMacro{test-results-model2-lc6-num-exp-fail}{198}
-\DefMacro{test-results-model2-lc6-num-pass-to-fail}{0}
-\DefMacro{test-results-model2-lc7-num-seed-fail}{1}
-\DefMacro{test-results-model2-lc7-num-exp-fail}{11}
-\DefMacro{test-results-model2-lc7-num-pass-to-fail}{8}
-\DefMacro{test-results-model2-lc9-num-seed-fail}{3}
-\DefMacro{test-results-model2-lc9-num-exp-fail}{76}
-\DefMacro{test-results-model2-lc9-num-pass-to-fail}{14}
+\DefMacro{test-results-lc1-num-exps}{394}
+\DefMacro{test-results-model0-lc1-num-seed-fail}{4.00}
+\DefMacro{test-results-model0-lc1-num-exp-fail}{4.31}
+\DefMacro{test-results-model0-lc1-num-pass-to-fail}{4}
+\DefMacro{test-results-lc8-num-seeds}{50}
+\DefMacro{test-results-lc8-num-exps}{1373}
+\DefMacro{test-results-model0-lc8-num-seed-fail}{4.00}
+\DefMacro{test-results-model0-lc8-num-exp-fail}{2.69}
+\DefMacro{test-results-model0-lc8-num-pass-to-fail}{43}
+\DefMacro{test-results-model1-lc7-num-seed-fail}{26.00}
+\DefMacro{test-results-model1-lc7-num-exp-fail}{31.21}
+\DefMacro{test-results-model1-lc7-num-pass-to-fail}{78}
+\DefMacro{test-results-model1-lc3-num-seed-fail}{82.00}
+\DefMacro{test-results-model1-lc3-num-exp-fail}{86.15}
+\DefMacro{test-results-model1-lc3-num-pass-to-fail}{64}
+\DefMacro{test-results-model1-lc4-num-seed-fail}{92.31}
+\DefMacro{test-results-model1-lc4-num-exp-fail}{93.06}
+\DefMacro{test-results-model1-lc4-num-pass-to-fail}{38}
+\DefMacro{test-results-model1-lc6-num-seed-fail}{42.00}
+\DefMacro{test-results-model1-lc6-num-exp-fail}{40.64}
+\DefMacro{test-results-model1-lc6-num-pass-to-fail}{54}
+\DefMacro{test-results-model1-lc5-num-seed-fail}{100.00}
+\DefMacro{test-results-model1-lc5-num-exp-fail}{100.00}
+\DefMacro{test-results-model1-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-model1-lc9-num-seed-fail}{79.00}
+\DefMacro{test-results-model1-lc9-num-exp-fail}{81.84}
+\DefMacro{test-results-model1-lc9-num-pass-to-fail}{18}
+\DefMacro{test-results-model1-lc2-num-seed-fail}{56.00}
+\DefMacro{test-results-model1-lc2-num-exp-fail}{-}
+\DefMacro{test-results-model1-lc2-num-pass-to-fail}{-}
+\DefMacro{test-results-model1-lc0-num-seed-fail}{89.47}
+\DefMacro{test-results-model1-lc0-num-exp-fail}{76.19}
+\DefMacro{test-results-model1-lc0-num-pass-to-fail}{9}
+\DefMacro{test-results-model1-lc1-num-seed-fail}{4.00}
+\DefMacro{test-results-model1-lc1-num-exp-fail}{4.82}
+\DefMacro{test-results-model1-lc1-num-pass-to-fail}{5}
+\DefMacro{test-results-model1-lc8-num-seed-fail}{2.00}
+\DefMacro{test-results-model1-lc8-num-exp-fail}{4.15}
+\DefMacro{test-results-model1-lc8-num-pass-to-fail}{46}
+\DefMacro{test-results-model2-lc7-num-seed-fail}{40.00}
+\DefMacro{test-results-model2-lc7-num-exp-fail}{44.77}
+\DefMacro{test-results-model2-lc7-num-pass-to-fail}{31}
+\DefMacro{test-results-model2-lc3-num-seed-fail}{88.00}
+\DefMacro{test-results-model2-lc3-num-exp-fail}{88.51}
+\DefMacro{test-results-model2-lc3-num-pass-to-fail}{26}
+\DefMacro{test-results-model2-lc4-num-seed-fail}{92.31}
+\DefMacro{test-results-model2-lc4-num-exp-fail}{95.24}
+\DefMacro{test-results-model2-lc4-num-pass-to-fail}{74}
+\DefMacro{test-results-model2-lc6-num-seed-fail}{76.00}
+\DefMacro{test-results-model2-lc6-num-exp-fail}{78.34}
+\DefMacro{test-results-model2-lc6-num-pass-to-fail}{9}
+\DefMacro{test-results-model2-lc5-num-seed-fail}{100.00}
+\DefMacro{test-results-model2-lc5-num-exp-fail}{100.00}
+\DefMacro{test-results-model2-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-model2-lc9-num-seed-fail}{93.00}
+\DefMacro{test-results-model2-lc9-num-exp-fail}{93.15}
+\DefMacro{test-results-model2-lc9-num-pass-to-fail}{12}
+\DefMacro{test-results-model2-lc2-num-seed-fail}{78.00}
+\DefMacro{test-results-model2-lc2-num-exp-fail}{-}
+\DefMacro{test-results-model2-lc2-num-pass-to-fail}{-}
+\DefMacro{test-results-model2-lc0-num-seed-fail}{100.00}
+\DefMacro{test-results-model2-lc0-num-exp-fail}{94.29}
+\DefMacro{test-results-model2-lc0-num-pass-to-fail}{0}
+\DefMacro{test-results-model2-lc1-num-seed-fail}{2.00}
+\DefMacro{test-results-model2-lc1-num-exp-fail}{2.79}
+\DefMacro{test-results-model2-lc1-num-pass-to-fail}{8}
+\DefMacro{test-results-model2-lc8-num-seed-fail}{6.00}
+\DefMacro{test-results-model2-lc8-num-exp-fail}{5.54}
+\DefMacro{test-results-model2-lc8-num-pass-to-fail}{14}

### 2022-05-06 paper/ase22/tables/test-results-table.tex
revise table3

@@
 \caption{\TestResultsTableCaption}
-\resizebox{\textwidth}{!}{
-\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}
+\resizebox{0.9\textwidth}{!}{
+\begin{tabular}{p{8.5cm}||cclll}
 \toprule
-\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\
+\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumSeedFail} & \parbox{1.5cm}{\centering\tNumExpFail} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
 \midrule
-\multirow{3}{*}{\parbox{4cm}{LC1: \UseMacro{test-results-lc0}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc0-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc0-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC1: \UseMacro{test-results-lc0}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc0-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc0-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc0-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC2: \UseMacro{test-results-lc1}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc1-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc1-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC2: \UseMacro{test-results-lc1}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc1-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc1-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc1-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC3: \UseMacro{test-results-lc2}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc2-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc2-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC3: \UseMacro{test-results-lc2}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc2-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc2-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc2-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC4: \UseMacro{test-results-lc3}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc3-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc3-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC4: \UseMacro{test-results-lc3}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc3-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc3-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc3-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC5: \UseMacro{test-results-lc4}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc4-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc4-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC5: \UseMacro{test-results-lc4}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc4-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc4-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc4-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC6: \UseMacro{test-results-lc5}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc5-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc5-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC6: \UseMacro{test-results-lc5}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc5-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc5-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc5-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC7: \UseMacro{test-results-lc6}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc6-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc6-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC7: \UseMacro{test-results-lc6}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc6-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc6-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc6-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC8: \UseMacro{test-results-lc7}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc7-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc7-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC8: \UseMacro{test-results-lc7}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc7-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc7-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc7-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC9: \UseMacro{test-results-lc8}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc8-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc8-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC9: \UseMacro{test-results-lc8}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc8-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc8-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc8-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{4cm}{LC10: \UseMacro{test-results-lc9}}}
- & \multirow{3}{*}{\UseMacro{test-results-bl-lc9-num-sents}}
- & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc9-num-seeds}}
+\multirow{3}{*}{\parbox{8.5cm}{LC10\&11: \UseMacro{test-results-lc9}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc9-num-seed-fail}
- & \multirow{3}{*}{\UseMacro{test-results-lc9-num-exps}}
  & BERT$\colon$\UseMacro{test-results-model0-lc9-num-exp-fail}
  & BERT$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
- & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
- & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}
  & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
- & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
- & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
  & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\

### 2022-05-06 python/sa/paper/Tables.py
debugging table

@@ -438,26 +438,41 @@ class Tables:
         baseline_result_file = result_dir / f"test_results_{task}_{search_dataset}_{selection_method}" / 'test_result_checklist_analysis.json'        
         output_file = latex.File(tables_dir / 'test-results-numbers.tex')
         result = Utils.read_json(result_file)
-        lc_ids = dict()
+        lc_orig_ids, lc_ids = dict(), dict()
         baseline_result = Utils.read_json(baseline_result_file)
+        req_dir = result_dir / 'reqs'
+        req_file = req_dir / 'requirements_desc.txt'
+        for l_i, l in enumerate(Utils.read_txt(req_file)):
+            desc = l.split('::')[0]
+            if desc in Macros.OUR_LC_LIST[9:]:
+                desc = 'Parsing positive and negative sentiment in (question, no) form'
+                if desc.lower() not in lc_ids.keys():
+                    lc_ids[desc.lower()] = (desc,l_i)
+                # end if
+            else:
+                lc_ids[desc.lower()] = (desc,l_i)
+            # end if
+        # end for
+        
         for m_i, model_name in enumerate(baseline_result.keys()):
             # model_name = model_name.replace('/', '-')
             for res_i, res in enumerate(baseline_result[model_name]):
                 if res['req']==str(Macros.OUR_LC_LIST[9:]):
                     desc = 'Parsing positive and negative sentiment in (question, no) form'
-                    desc = cls.replace_latex_symbol(desc)
+                    desc, lc_i = lc_ids[desc.lower()]
                 else:
-                    desc = cls.replace_latex_symbol(res['req'])
+                    desc, lc_i = lc_ids[res['req'].lower()]
+                # end if
+                desc = cls.replace_latex_symbol(desc)
+                lc_orig_ids[desc] = lc_i
+                if m_i==0:
+                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}", desc))
                 # end if
                 if m_i==0:
-                    lc_ids[desc] = res_i
-                    output_file.append_macro(latex.Macro(f"test-results-lc{res_i}", desc))
-                # end if
-                if m_i==0:
-                    output_file.append_macro(latex.Macro(f"test-results-bl-lc{res_i}-num-sents",
[…]

### 2022-05-06 paper/ase22/result.tex
result

@@
 seed and expanded test cases respectively. Columns 4-5 show the
-failure rate in percentage by running the \sa models on the seed and
-expanded test cases respectively. Column 6 shows the number of
-expanded test cases failed, but their seed test cases passed. For LC9,
-we combine two
-
-From the
-table, we can observe that
+failure rate in percentage by evaluating the \sa models on the seed
+and expanded test cases respectively. Column 6 shows the number of
+expanded test cases failed, but their seed test cases passed.  From
+the table, we can observe that LC3 has no expanded sentences from its
+seeds. It means that the 50 seeds selected in this experiment does not
+provide any validated expansions. It is because the randomness of
+selection of 50 seeds determines the number of validated
+expansions. we expect that more selection of seeds increases the
+probability of availability of their expansion. In addition, LC1 and
+LC5 obtains 19 and 26 seeds respectively. It represents that \tool
+finds and generates their seeds lower than the target number of seeds,
+which is 50 in this experiment. In this case, use of larger search
+dataset increases the amount of seeds for the \lcs. Finally, we find
+that there are number of a number of failed expanded test cases succeeded
+before the expansion (pass on seed, but fail on its expanded test
+cases). This shows that phase of syntax-based sentence expansion in
+\tool captures failure-inducing expansion given a seed. It finally
+shows usefulness of \tool since the different test results between seed
+and expanded cases provide accurate guidance for debugging model.
 

### 2022-05-06 paper/ase22/tables/test-results-numbers.tex
result

@@
 \DefMacro{test-results-lc7}{Author sentiment is more important than of others}
-\DefMacro{test-results-bl-lc7-num-sents}{8528}
-\DefMacro{test-results-bl-model0-lc7-num-fail}{43.87}
-\DefMacro{test-results-lc3}{Negated negative should be positive or neutral}
-\DefMacro{test-results-bl-lc3-num-sents}{6786}
-\DefMacro{test-results-bl-model0-lc3-num-fail}{11.77}
-\DefMacro{test-results-lc4}{Negated neutral should still be neutral}
-\DefMacro{test-results-bl-lc4-num-sents}{2496}
-\DefMacro{test-results-bl-model0-lc4-num-fail}{97.24}
-\DefMacro{test-results-lc6}{Negated positive with neutral content in the middle}
-\DefMacro{test-results-bl-lc6-num-sents}{1000}
-\DefMacro{test-results-bl-model0-lc6-num-fail}{86.00}
-\DefMacro{test-results-lc5}{Negation of negative at the end, should be positive or neutral}
-\DefMacro{test-results-bl-lc5-num-sents}{2124}
-\DefMacro{test-results-bl-model0-lc5-num-fail}{88.09}
-\DefMacro{test-results-lc2}{Sentiment change over time, present should prevail}
-\DefMacro{test-results-bl-lc2-num-sents}{8000}
-\DefMacro{test-results-bl-model0-lc2-num-fail}{21.00}
-\DefMacro{test-results-lc0}{Short sentences with neutral adjectives and nouns}
-\DefMacro{test-results-bl-lc0-num-sents}{1716}
-\DefMacro{test-results-bl-model0-lc0-num-fail}{77.51}
-\DefMacro{test-results-lc1}{Short sentences with sentiment-laden adjectives}
-\DefMacro{test-results-bl-lc1-num-sents}{8658}
-\DefMacro{test-results-bl-model0-lc1-num-fail}{0.30}
-\DefMacro{test-results-lc9}{Parsing positive and negative sentiment in (question, no) form}
-\DefMacro{test-results-bl-lc9-num-sents}{7644}
-\DefMacro{test-results-bl-model0-lc9-num-fail}{53.06}
-\DefMacro{test-results-lc8}{Parsing sentiment in (question, yes) form}
-\DefMacro{test-results-bl-lc8-num-sents}{9204}
-\DefMacro{test-results-bl-model0-lc8-num-fail}{19.48}
-\DefMacro{test-results-bl-model1-lc7-num-fail}{31.57}
-\DefMacro{test-results-bl-model1-lc3-num-fail}{3.21}
-\DefMacro{test-results-bl-model1-lc4-num-fail}{92.31}
-\DefMacro{test-results-bl-model1-lc6-num-fail}{41.60}
-\DefMacro{test-results-bl-model1-lc5-num-fail}{20.95}
-\DefMacro{test-results-bl-model1-lc2-num-fail}{10.36}
-\DefMacro{test-results-bl-model1-lc0-num-fail}{81.06}
-\DefMacro{test-results-bl-model1-lc1-num-fail}{1.61}
-\DefMacro{test-results-bl-model1-lc9-num-fail}{59.86}
-\DefMacro{test-results-bl-model1-lc8-num-fail}{13.71}
-\DefMacro{test-results-bl-model2-lc7-num-fail}{41.45}
-\DefMacro{test-results-bl-model2-lc3-num-fail}{10.82}
-\DefMacro{test-results-bl-model2-lc4-num-fail}{98.16}
-\DefMacro{test-results-bl-model2-lc6-num-fail}{86.50}
-\DefMacro{test-results-bl-model2-lc5-num-fail}{100.00}
-\DefMacro{test-results-bl-model2-lc2-num-fail}{31.65}
-\DefMacro{test-results-bl-model2-lc0-num-fail}{96.79}
-\DefMacro{test-results-bl-model2-lc1-num-fail}{1.44}
-\DefMacro{test-results-bl-model2-lc9-num-fail}{84.25}
-\DefMacro{test-results-bl-model2-lc8-num-fail}{16.92}
 \DefMacro{test-results-lc7-num-seeds}{50}
@@
 \DefMacro{test-results-model0-lc7-num-pass-to-fail}{134}
+\DefMacro{test-results-lc3}{Negated negative should be positive or neutral}
 \DefMacro{test-results-lc3-num-seeds}{50}
@@
 \DefMacro{test-results-model0-lc3-num-pass-to-fail}{49}
+\DefMacro{test-results-lc4}{Negated neutral should still be neutral}
 \DefMacro{test-results-lc4-num-seeds}{26}
@@
 \DefMacro{test-results-model0-lc4-num-pass-to-fail}{62}
+\DefMacro{test-results-lc6}{Negated positive with neutral content in the middle}
 \DefMacro{test-results-lc6-num-seeds}{50}
@@
 \DefMacro{test-results-model0-lc6-num-pass-to-fail}{40}
+\DefMacro{test-results-lc5}{Negation of negative at the end, should be positive or neutral}
 \DefMacro{test-results-lc5-num-seeds}{50}
@@
 \DefMacro{test-results-model0-lc5-num-pass-to-fail}{0}
-\DefMacro{test-results-lc9-num-seeds}{100}
-\DefMacro{test-results-lc9-num-exps}{2379}
-\DefMacro{test-results-model0-lc9-num-seed-fail}{71.00}
-\DefMacro{test-results-model0-lc9-num-exp-fail}{72.43}
+\DefMacro{test-results-lc10}{Parsing negative sentiment in (question, no) form}
+\DefMacro{test-results-lc10-num-seeds}{50}
+\DefMacro{test-results-lc10-num-exps}{1161}
+\DefMacro{test-results-model0-lc10-num-seed-fail}{100.00}
+\DefMacro{test-results-model0-lc10-num-exp-fail}{100.00}
+\DefMacro{test-results-model0-lc10-num-pass-to-fail}{0}
+\DefMacro{test-results-lc9}{Parsing positive sentiment in (question, no) form}
+\DefMacro{test-results-lc9-num-seeds}{50}
+\DefMacro{test-results-lc9-num-exps}{1218}
+\DefMacro{test-results-model0-lc9-num-seed-fail}{42.00}
+\DefMacro{test-results-model0-lc9-num-exp-fail}{46.14}
 \DefMacro{test-results-model0-lc9-num-pass-to-fail}{40}
+\DefMacro{test-results-lc2}{Sentiment change over time, present should prevail}
 \DefMacro{test-results-lc2-num-seeds}{50}
@@
 \DefMacro{test-results-model0-lc2-num-pass-to-fail}{-}
+\DefMacro{test-results-lc0}{Short sentences with neutral adjectives and nouns}
 \DefMacro{test-results-lc0-num-seeds}{19}
@@
 \DefMacro{test-results-model0-lc0-num-pass-to-fail}{19}
+\DefMacro{test-results-lc1}{Short sentences with sentiment-laden adjectives}
 \DefMacro{test-results-lc1-num-seeds}{50}
@@
 \DefMacro{test-results-model0-lc1-num-pass-to-fail}{4}
+\DefMacro{test-results-lc8}{Parsing sentiment in (question, yes) form}
 \DefMacro{test-results-lc8-num-seeds}{50}
@@
 \DefMacro{test-results-model1-lc5-num-pass-to-fail}{0}
-\DefMacro{test-results-model1-lc9-num-seed-fail}{79.00}
-\DefMacro{test-results-model1-lc9-num-exp-fail}{81.84}
+\DefMacro{test-results-model1-lc10-num-seed-fail}{100.00}
+\DefMacro{test-results-model1-lc10-num-exp-fail}{100.00}
+\DefMacro{test-results-model1-lc10-num-pass-to-fail}{0}
+\DefMacro{test-results-model1-lc9-num-seed-fail}{58.00}
+\DefMacro{test-results-model1-lc9-num-exp-fail}{64.53}
 \DefMacro{test-results-model1-lc9-num-pass-to-fail}{18}
@@
 \DefMacro{test-results-model2-lc5-num-pass-to-fail}{0}
-\DefMacro{test-results-model2-lc9-num-seed-fail}{93.00}
-\DefMacro{test-results-model2-lc9-num-exp-fail}{93.15}
-\DefMacro{test-results-model2-lc9-num-pass-to-fail}{12}
+\DefMacro{test-results-model2-lc10-num-seed-fail}{94.00}
+\DefMacro{test-results-model2-lc10-num-exp-fail}{98.97}
+\DefMacro{test-results-model2-lc10-num-pass-to-fail}{4}
+\DefMacro{test-results-model2-lc9-num-seed-fail}{92.00}
+\DefMacro{test-results-model2-lc9-num-exp-fail}{87.60}
+\DefMacro{test-results-model2-lc9-num-pass-to-fail}{8}
 \DefMacro{test-results-model2-lc2-num-seed-fail}{78.00}

### 2022-05-06 paper/ase22/tables/test-results-table.tex
result

@@
 \resizebox{0.9\textwidth}{!}{
-\begin{tabular}{p{8.5cm}||cclll}
+\begin{tabular}{p{8cm}||cclll}
 \toprule
@@
 \midrule
-\multirow{3}{*}{\parbox{8.5cm}{LC1: \UseMacro{test-results-lc0}}}
+\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-lc0}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC2: \UseMacro{test-results-lc1}}}
+\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-lc1}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC3: \UseMacro{test-results-lc2}}}
+\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-lc2}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC4: \UseMacro{test-results-lc3}}}
+\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-lc3}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC5: \UseMacro{test-results-lc4}}}
+\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-lc4}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC6: \UseMacro{test-results-lc5}}}
+\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-lc5}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC7: \UseMacro{test-results-lc6}}}
+\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-lc6}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC8: \UseMacro{test-results-lc7}}}
+\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-lc7}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC9: \UseMacro{test-results-lc8}}}
+\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-lc8}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-seeds}}
@@
 \hline
-\multirow{3}{*}{\parbox{8.5cm}{LC10\&11: \UseMacro{test-results-lc9}}}
+\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-lc9}}}
  & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-seeds}}
@@
 \hline
+\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-lc10}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc10-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-lc10-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-model0-lc10-num-seed-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc10-num-exp-fail}
+ & BERT$\colon$\UseMacro{test-results-model0-lc10-num-pass-to-fail}\\
+ & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc10-num-seed-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc10-num-exp-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-model1-lc10-num-pass-to-fail}\\
+ & & & dstBERT$\colon$\UseMacro{test-results-model2-lc10-num-seed-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc10-num-exp-fail}
+ & dstBERT$\colon$\UseMacro{test-results-model2-lc10-num-pass-to-fail}\\
+\hline
 \bottomrule

### 2022-05-06 python/sa/paper/Tables.py

@@ -444,38 +444,31 @@ class Tables:
         req_file = req_dir / 'requirements_desc.txt'
         for l_i, l in enumerate(Utils.read_txt(req_file)):
             desc = l.split('::')[0]
-            if desc in Macros.OUR_LC_LIST[9:]:
-                desc = 'Parsing positive and negative sentiment in (question, no) form'
-                if desc.lower() not in lc_ids.keys():
-                    lc_ids[desc.lower()] = (desc,l_i)
-                # end if
-            else:
-                lc_ids[desc.lower()] = (desc,l_i)
-            # end if
+            lc_ids[desc.lower()] = (desc,l_i)
         # end for
         
-        for m_i, model_name in enumerate(baseline_result.keys()):
-            # model_name = model_name.replace('/', '-')
-            for res_i, res in enumerate(baseline_result[model_name]):
-                if res['req']==str(Macros.OUR_LC_LIST[9:]):
-                    desc = 'Parsing positive and negative sentiment in (question, no) form'
-                    desc, lc_i = lc_ids[desc.lower()]
-                else:
-                    desc, lc_i = lc_ids[res['req'].lower()]
-                # end if
-                desc = cls.replace_latex_symbol(desc)
-                lc_orig_ids[desc] = lc_i
-                if m_i==0:
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}", desc))
-                # end if
-                if m_i==0:
-                    output_file.append_macro(latex.Macro(f"test-results-bl-lc{lc_i}-num-sents",
-                                                         res['num_tcs']))
-                # end if
-                output_file.append_macro(latex.Macro(f"test-results-bl-model{m_i}-lc{lc_i}-num-fail",
-                                                     cls.FMT_FLOAT.format(res['num_tc_fail']*100./res['num_tcs'])))
-            # end for
-        # end for
+        # for m_i, model_name in enumerate(baseline_result.keys()):
+        #     # model_name = model_name.replace('/', '-')
+        #     for res_i, res in enumerate(baseline_result[model_name]):
+        #         if res['req']==str(Macros.OUR_LC_LIST[9:]):
+        #             desc = 'Parsing positive and negative sentiment in (question, no) form'
+        #             desc, lc_i = lc_ids[desc.lower()]
+        #         else:
+        #             desc, lc_i = lc_ids[res['req'].lower()]
+        #         # end if
+        #         desc = cls.replace_latex_symbol(desc)
[…]

### 2022-05-07 paper/ase22/CM/coverage.tex
writing

@@
 
-Fig. \ref{fig:coverage} shows the coverage results of the generated
-test samples, where the red line represents \tool and the black line
-represents \Cklst.  Each column in Fig. \ref{fig:coverage} represent
-the results for one NLP model, the first row is the \textit{BoundCov}
-results and the second row is the \textit{SActCov} results.  From the
-results, we make two observations observations. First, for \emph{all}
-experimental settings (\eg NLP model, coverage metric), \tool achieves
-high coverage than \Cklst. Recall that a higher coverage implies the
-test case in the test suite is more diverse and rarely to have a
-statistical distribution similar to the model training data. As a
-result, a test suite with greater coverage complements the model
-training data distribution (\ie hold-out testing data) better.  The
-experimental results confirm that \tool can generate more diverse test
-cases to complement the hold-out testing data for testing NLP models.
-\sw{What does the growth trend in each figure indicate?} \sw{Does the
+Next, Fig. \ref{fig:coverage} shows the coverage results of the
+generated test samples and reliability of the former evaluation
+results. In the figure, the red line represents \tool and the black
+line represents \Cklst. Each column in Fig. \ref{fig:coverage}
+represent the results for one NLP model, the first row is the
+\textit{BoundCov} results and the second row is the \textit{SActCov}
+results.  From the results, we make three observations
+observations. \TODO{First, as the number of test cases increases, the
+  test suite can achieve better coverage. Such observation is
+  intuitive. However, generating a more extensive test suite is not
+  easy, particularly for \Cklst, which is a manually template-based
+  approach.}  Second, for \emph{all} experimental settings (\eg NLP
+model, coverage metric), \tool achieves high coverage than
+\Cklst. Recall that a higher coverage implies the test case in the
+test suite is more diverse and rarely to have a statistical
+distribution similar to the model training data. As a result, a test
+suite with greater coverage complements the model training data
+distribution (\ie hold-out testing data) better.  \TODO{For example,
+  for the first NLP model under test, \tool can achieve a higher
+  coverage than \Cklst with only half test cases.}  Such experimental
+results confirm that \tool can generate more diverse test cases to
+complement the hold-out testing data for testing NLP models.  \sw{What
+  does the growth trend in each figure indicate?} \sw{Does the
   absolute numbers or relative difference of the two lines on y axis

### 2022-05-07 paper/ase22/approach.tex
edit exp & table
writing

@@
 reference context-free grammar (CFG) from the Penn Treebank corpus
-dataset \cite{} as inputs.  The reference CFG is learned from a large
-dataset \cite{} that is representative of the distribution of
-real-world language usage.  The algorithm identifies the discrepancy
-between the seed syntax and the reference grammar to decide how a seed
-can be expanded.
+dataset \cite{mitchell1993treebank} as inputs.  The reference CFG is
+learned from a large dataset \cite{nltkTreebankCorporaWebPage} that is
+representative of the distribution of real-world language usage.  The
+algorithm identifies the discrepancy between the seed syntax and the
+reference grammar to decide how a seed can be expanded.
 %This phase builds \pcfg from the reference corpus. \cfg
@@
 %differentiation phase suggests structural expansion candidates on the
-%seed input. this phase aims to analyze which structural components and
-%where they can be added into the seed structure for its expansion. To
-%do so, we explore reference \prodrs comparing it with each \prodr used
-%in seed input. This results in the phase described in
-%Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
+%seed input. this phase aims to analyze which structural components
+%and where they can be added into the seed structure for its
+%expansion. To do so, we explore reference \prodrs comparing it with
+%each \prodr used in seed input. This results in the phase described
+%in Algorithm~\ref{code:ProdDiffAlg}. For each production rule in seed
 %inputs ($seed\_prod$), it searches production rules in reference
@@
 %measure of how consistent the production rule is with the given seed
-%structure is given in its probability of the reference production rule
-%($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
+%structure is given in its probability of the reference production
+%rule ($ref\_prob$) multiplied by that of parents of $seed\_prod$. The
 %expansion candidate consists of terminal or nonterminal symbols. When
@@
 %example of the expansion is illustrated in
-%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into
-%reference, and ``NP->[DT,NNS]'' is identified as its expansion
-%candidate since the \rhs of ``NP->[DT,NNS]'' is superset of that of
-%``NP->[DT]''. the component of NNS is replaced with mask token in
+%Figure~\ref{fig:ExpEx}. The ``NP->[DT]'' is queried into reference,
+%and ``NP->[DT,NNS]'' is identified as its expansion candidate since
+%the \rhs of ``NP->[DT,NNS]'' is superset of that of ``NP->[DT]''. the
+%component of NNS is replaced with mask token in
 %\sent-level. Therefore, the ``Or both \{MASK\}.'' is suggested for
@@
 % evaluating the \sa models on the associated \lc in addition to the
-% seed \sent. It is only achieved when the expanded \sents are also met
-% with the same search rules for the \lc. For LC1 as an example, the
-% expanded \sent must still conform to the specification of the seed's
-% \lc specification. Therefore, the expanded \sents are required to be
-% short and to only have \neu adjectives and \nns.
-% \sw{Say why we use
-%   the third criteria only for LC1 and LC2.}  \jl{I added the
-%   explanation}
+% seed \sent. It is only achieved when the expanded \sents are also
+% met with the same search rules for the \lc. For LC1 as an example,
+% the expanded \sent must still conform to the specification of the
+% seed's \lc specification. Therefore, the expanded \sents are
+% required to be short and to only have \neu adjectives and \nns.
+% \sw{Say why we use the third criteria only for LC1 and LC2.}  \jl{I
+% added the explanation}
 
@@
 
-%% \paragraph{Running example.} \jl{I dont think we need this
-%%   subsection of \sent selection it is already explained at the
-%%   previous stage with running example.} \sw{This is to use the bert score to rank and select. Did we discuss this already?}
+% \paragraph{Running example.} \jl{I dont think we need this
+%   subsection of \sent selection it is already explained at the
+%   previous stage with running example.} \sw{This is to use the bert score to rank and select. Did we discuss this already?}

### 2022-05-07 paper/ase22/concl.tex
writing

\section{Conclusions}
\label{sec:concl}

In this paper, we present \tool automatically that finds and generates
suitable seed test cases for each \lc. \tool fuzz the seeds into a
sufficient number of test cases by expanding \cfg of the seed inputs.
We evaluated \sa models on the generated test cases and anlyzed its
impact on testing the models. Further, we examined failure-inducing
cases for seeking the root of the bug.  We also studied the quality of
\tool test cases by measuring their consistencies with their test
oracles and \lc. These led to show generalization ability of \tool for
model evaluation and its reliability in the end. Our work stands to
provide automated and comprehensive NLP model testing tool.

### 2022-05-07 paper/ase22/experiment.tex
writing

@@
 score range into [0, 0.4], (0.4, 0.6] and (0.6, 0.8] for assigning
-    negative, neutral and positive labels respectively.
+    negative, neutral and positive labels respectively. In addition,
+    we use \Swn as word sentiment
+    dataset~\cite{baccianella2010sentiwordnet}. \Swn is a publicly
+    available English sentiment lexicons.  It provides lexical
+    sentiment scores and the sentiment word labels are categorized by
+    implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
 %% \TODO{introduce details about each model}
@@
 on a search dataset and the syntax in a large reference corpus.  We
-expect \tool can generate a more diverse test suite than \Cklst. To
-measure diversity, we follow the approach presented by Ma et
-al. \cite{ma2018deepgauge}, where the authors measure the coverage of
-NLP model intermediate states as corner-case neurons.  Because the
-matrix computation of intermediate states impacts NLP model
-decision-making, a test suite that covers a greater number of
-intermediate states can represent more NLP model decision-making,
-making it more diverse.  Specifically, we used two coverage metrics in
-existing work \cite{ma2018deepgauge}, \textit{boundary coverage}
-(BoundCov) and \textit{strong activation coverage} (SActCov), as our
-metrics to evaluate the test suite diversity.  \TODO{It is worth
-  noting that a test sample with a statistical distribution similar to
-  the training data would rarely be found in the corner case
-  region. As a result, covering a larger corner case region means that
-  the test suite is more likely to be buggy.}
+expect \tool can generate a more diverse test suite than \Cklst, and
+achieve more probable evaluation results. We first evaluate the three
+\sa models by testing them on the test cases that \tool
+generates. Next, to measure diversity, we follow the approach
+presented by Ma et al. \cite{ma2018deepgauge}, where the authors
+measure the coverage of NLP model intermediate states as corner-case
+neurons.  Because the matrix computation of intermediate states
+impacts NLP model decision-making, a test suite that covers a greater
+number of intermediate states can represent more NLP model
+decision-making, making it more diverse.  Specifically, we used two
+coverage metrics in existing work \cite{ma2018deepgauge},
+\textit{boundary coverage} (BoundCov) and \textit{strong activation
+  coverage} (SActCov), as our metrics to evaluate the test suite
+diversity.  \TODO{It is worth noting that a test sample with a
+  statistical distribution similar to the training data would rarely
+  be found in the corner case region. As a result, covering a larger
+  corner case region means that the test suite is more likely to be
+  buggy.}
 
@@
 
-\noindent Eq.
-\ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n, low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
-Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
+\noindent Eq. \ref{eq:corner} shows the formal definition of the
+corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is
+the given test suite, $N$ is the number of neurons in model
+$f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n,
+low_n$ are the $n^{th}$ neurons' output bounds on the model training
+dataset.  Eq. \ref{eq:corner} can be interpreted as the collection of
+neurons that emit outputs beyond the model's numerical boundary.
 
@@
 
-\noindent The formal definition of our coverage metrics are shown in Eq.\ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
-Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.
+\noindent The formal definition of our coverage metrics are shown in
+Eq.\ref{eq:coverage}, where BoundCov measures the coverage of neurons
+that produce outputs that exceed the upper or lower bounds, and
+SActCov measures the coverage of neurons that create outputs that
+exceed the lower bound.  Higher coverage indicates the test suite is
+better for triggering the corner-case neurons, thus better test suite
+diversity.
 
@@
 
-To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
-After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
+To answer {\bf RQ3}, for each NLP model under test, we first feed its
+training dataset to compute each neuron's lower and upper
+bounds. After that, we select the same number of test cases from \tool
+and \Cklst as the test suite and compute the corresponding coverage
+metrics.
 
@@
 
-To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
-Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input).
-Still, it is unclear why mutating one token will cause the model to produce misclassified results.
-We seek to help developers to understand why such mutation will result in the misclassification. 
-Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences).
-Motivated by such intuition, we seek to identify a minimal set of input tokens that dominate the model prediction.
+To answer RQ4, we conduct experiments to demonstrate that \tool can
+help developers understand the bugs in the NLP models.  Recall that
+\tool generates test cases by mutating seed sentences (\eg by
+expanding one token in the seed input). Still, it is unclear why
+mutating one token will cause the model to produce misclassified
+results.  We seek to help developers to understand why such mutation
+will result in the misclassification.  Existing work
+\cite{simin2020denas, lemna, lime} has demonstrated that the ML model
+prediction is dominated by a minimal set of input features (\ie tokens
+in input sentences). Motivated by such intuition, we seek to identify
+a minimal set of input tokens that dominate the model prediction.
 
-Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token in $x$ or not.
-The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
+Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and
+the NLP model under test $f(\cdot)$, our goal is to find a masking
+template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1,
+representing masking the $i^{th}$ token in $x$ or not.  The template
+$T$ can mask some tokens in $x$ with attribute tokens, and the masked
+input has a high probability of retaining the original prediction $x$,
+denoted as
 
@@
 
-To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{}.
-Following that, we begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Eq.
-\ref{eq:prob}.
-We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Eq. \ref{eq:prob}
-Because we iterate the size of our mask, the generated template $T$ will keep the minimum number of tokens in $x$.
-Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).
+To create such a template $T$, we first compute the contribution score
+of each input token using an existing explainable ML technique
+\cite{}. Following that, we begin with the full mask template (\ie,
+all tokens are masked); such full mask template definitely does not
+satisfy Eq. \ref{eq:prob}.  We then iteratively shift one position
+from mask to non-mask based on the order of each token's contribution
+score, until the template $T$ satisfies Eq. \ref{eq:prob} Because we
+iterate the size of our mask, the generated template $T$ will keep the
+minimum number of tokens in $x$. Moreover, since the input $x$ is an
+incorrect prediction, the generated template $T$ is likely to produce
+misclassification (i.e., the probability to be misclassified is larger
+than $P_{thresh}$).
 

### 2022-05-07 paper/ase22/result.tex
writing

@@
 \InputWithSpace{tables/test-results-table}
+\subsection{RQ1: \tool Sentiment Label Consistency}
+Table~\ref{table:ManualStudy} shows results of our manual study. The
+first column represents type of test case. The number of test cases
+used for the study is represented in second column. The label
+consistency score defined in equation~\ref{metric:srel} is shown in
+column 3.
 
-\subsection{RQ1: \tool Sentiment Label Consistency}
-Table~\ref{table:ManualStudy} shows the statistics of scores collected
-from the manual study of \tool. First column represents type of test
-case. The number of test cases used for the study is represented in
-second column. Label consistency score and \lc relevancy score defined
-at equation~\ref{metric:srel} and~\ref{metric:lcrel} are shown at the
-remaining columns. First, it is shown that high label consistency
-score over 0.8. It means that \tool generates test oracles consistent
-to human understanding. It is also observed that there is no
-difference of the scores between seed and expanded sentences. The
-observation implies that the expansion method in \tool preserves
-sentiment of expanded sentences as its seed, and provides its
-reliability. These observations answer RQ1 and conclude that \tool
-generates test case with high consistency between test sentence and
-its oracle.
+We observe that \emph{\tool generates test cases that consistently
+  label their sentiment correctly.}  Column 3 shows that the label
+consistency scores are 0.83 and 0.84 for the seed and expanded
+sentences, respectively. We can observe that the scores are not same
+as maximum scores meaning that there are inconsistency on labels
+between \tool and subjects. The cuases of inconsistency in the scores
+are two following: First, complicated sentence leads subjects to
+misunderstand its meaning. Second, phrase in a sentence introduces its
+multiple interpretations to understand its sentiment. For example, the
+word ``easy'' could be interpreted as both compliment and back-handed
+insult.  This means that \tool generates test oracles consistent with
+human understanding most of the time. It is observed that there is
+little difference of the scores between the seed and expanded
+sentences. This implies that the syntax-based sentence expansion in
+\tool preserves the sentiment as its seed.
+%% \sw{What are
+%%   the causes of inconsistency? Looks like the main source of
+%%   inconsistency comes from seed generation? Any insights on how it
+%%   happened (e.g., issue with original labels, search rules, or
+%%   templates?}
 
 \subsection{RQ2: Correctness of Linguistic Capability Categorization}
-The result in table~\ref{table:ManualStudy} also shows that \tool
-achieves high order of agreement with human assessment on \lc
-relevancy. In parallel, it is observed that the expanded sentences
-generated from \tool also have same level of \lc
-relevancy. Accordingly, we answer the RQ2 by concluding that
-\tool generates \lc relevant test cases with the agreement with human.
+The \lc relevancy score defined in~\ref{metric:lcrel} is shown in
+column 4 of Table \ref{table:ManualStudy}. The result shows that
+\emph{\tool generates test cases that are correctly categorized to the
+  corresponding linguistic capabilities most of the time.}  The \lc
+relevancy scores for the seed and expanded sentences are both 0.9,
+achieving high order of agreement with human assessment. The fact that
+the expanded sentences generated by \tool also have same level of \lc
+relevancy as the seed sentences shows that the syntax-based sentence
+expansion retains the linguistic capabilities.
+%% \sw{Source of incorrect
+%% categorization of linguistic capabilities?}
 
-\jl{The following needs to be in RQ2 result section after simin
-  completes RQ2 result section} Table~\ref{table:TestResult} shows
-results of evaluation of three \sa models. First column lists
+\subsection{RQ3: Test Suite Diversity}
+
+We first show evaluation results of three \sa models via
+table~\ref{table:TestResult}. In the table, first column lists
 linguistic capability for \sa task, and Columns 2-3 show the number of
@@
 which is 50 in this experiment. In this case, use of larger search
-dataset increases the amount of seeds for the \lcs. Finally, we find
-that there are number of a number of failed expanded test cases succeeded
-before the expansion (pass on seed, but fail on its expanded test
-cases). This shows that phase of syntax-based sentence expansion in
-\tool captures failure-inducing expansion given a seed. It finally
-shows usefulness of \tool since the different test results between seed
-and expanded cases provide accurate guidance for debugging model.
+dataset increases the amount of seeds for the \lcs. From the table, it
+is found that all three models achieves better performance on LC9 and
+LC2 while they obatains high failure rates on other \lcs. Finally, we
+find that there are number of a number of failed expanded test cases
+succeeded before the expansion (pass on seed, but fail on its expanded
+test cases). This shows that phase of syntax-based sentence expansion
+in \tool captures failure-inducing expansion given a seed. It finally
+shows usefulness of \tool since the different test results between
+seed and expanded cases provide accurate guidance for debugging model.
 
-\subsection{RQ3: Test Suite Diversity}
 \input{CM/coverage}

### 2022-05-07 paper/ase22/threats.tex
writing

\section{Threats to Validity}
\label{sec:threats}

Use of publicly available datasets poses an external validity threat
with respect to the generalizability of our results. We implemented
domain-spefic knowledge on publically available word sentiments
dataset~\cite{baccianella2010sentiwordnet}. We also constructed
reference CFG from publically available corpus dataset
\cite{mitchell1993treebank, nltkTreebankCorporaWebPage}. The dataset
used in our study might not be completely representative of all
English grammatical structures and English word sentiments. We
mitigate this threat by observing that they are widely used in NLP
domain~\cite{husnain2021swnvalidity} and reviewed each script and the
output logs.

### 2022-05-07 paper/ase22/related.tex
related

@@
 
-\textbf{NLP Testing.} With the increasing use of NLP models,
-evaluation of NLP models is becoming more important. Wang \textit{et
-  al.}~\cite{wang2018glue} propose multiple diagnostic datasets to
-evaluate NLP models. Few recent works have also considered model
-robustness as an aspect for model evaluation. Different methods like
-adversarial set generation~\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial}, fairness
-evaluation~\cite{prabhakaran2019fairness,rottger2020hatecheck},
-logical consistency evaluation~\cite{ribeiro2019consistencyeval},
-prediction interpretations~\cite{ribeiroSG16lime} and interactive
+\MyPara{NLP Testing.}
+%
+With the increasing use of NLP models, evaluation of NLP models is
+becoming more important. Apart from the task accuracy based testing
+scheme, recent works have also considered model robustness as an
+aspect for model evaluation. Belinkov
+\textit{\etal}~\cite{belinkov2018breaknmt} aims to fail neural machine
+translation model by intentionally introducing noise in the input
+text.Pinjia
+\textit{\etal}~\cite{pinjia2020structinvtestingnmt,pinjia2020testnmtrt}
+measures the robustness by assuming syntatic and semantic relation
+between input and output of neural machine translation model.  Ribeiro
+\textit{\etal}~\cite{ribeiro2018sear} proposed an approach to
+generalize semantically equivalent adversarial rules. In addition,
+Rychalska \textit{\etal}~\cite{rychalska2019wildnlp} measures drops in
+BLEU scores by corruption operation, and compare model robustness
+based on the amount of the drops. In addition, Iyyer
+\textit{\etal}~\cite{iyyer2018adversarial} introduced learning based
+model for adversarial data augmentation. Not only evaluating the
+robustness on adversarial set, but various aspets on the NLP model are
+considered for the robustness evaluation. Prabhakaran
+\textit{\etal}~\cite{prabhakaran2019fairness} developed an evaluation
+framework to detect unintended societal bias in NLP model. Rottger
+\textit{\etal}~\cite{rottger2020hatecheck} introduced a functional
+test suite for hate speech detection in the NLP model.  Ribeiro
+\textit{\etal}~\cite{ribeiro2019consistencyeval} measures logical
+consistency of NLP model. These techniques evaluate the robustness of
+the NLP model. However, we focused on evaluation of model capability
+over multiple perspectives and give debugging information by comparing
+seed and expanded test cases.
+
+\MyPara{Linguistic Capability Evaluation}
+%
+Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} propose
+multiple diagnostic datasets to evaluate NLP models. This dataset
+evaluates NLP model's ability to understand input sentence via natural
+language inference problems. More recently, \Cklst proposes evaluation
+method of input-output behavior defined as \lcs. \Cklst generates
+behavior-guided inputs for validating the
+behaviors.~\cite{marcoACL2020checklist}. Unlike prior work on manual
+data generation method, we used structural information in text to
+generate data which enables automated data generation.
+
+\MyPara{NLP Model Debugging}
+%
+Futher, researchers have been explaining NLP model prediction and
+analyze it for debugging the model. Ribeiro
+\textit{\etal}~\cite{ribeiroSG16lime} computes the word relevance for
+a model prediction are evaluated and implemented crowdcourcing for
+model inspection with the word relevance explanation.  Interactive
 error analysis~\cite{wu2019errudite} have been proposed to evaluate
-model robustness. More recently, \Cklst introduces input-output
-behaviors of linguistic capabilities and generates behavior-guided
-inputs for validating the behaviors.~\cite{marcoACL2020checklist}
-However, the approach only relies on manually generated input
-templates, thus the template generation becomes expensive and time
-consuming. Also, it does not guarantee the comprehensive evaluation.
-
-\begin{comment}
+model robustness. Zylberajch~\cite{zylberajch2021hildif} used
+influence functions for model explanation generation so as to enable
+interactive debugging using humans effort as feedback with the
+explanation. Lertvittaya~\cite{lertvittayakumjorn2020find} proposed
+approach to understand behavior of text classifier model and improve
+model by disabling irrelevant hidden features. In this work, \tool
+provides source of model failure by comparing performance on seed and
+expanded test cases.
 
@@
   %% does not garauntee the comprehensive evaluation.
-
-Not only that, model is evaluated on different aspects such as
-robustness of the model on adversarial
-sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial},
-fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
-consistancy~\cite{ribeiro2019consistencyeval}, prediction
-interpretations~\cite{ribeiroSG16lime} and interactive error
-analysis~\cite{wu2019errudite}. Especially, \Cklst implements
-behavioral testing methodolgy for evaluating multiple linguistic
-capabilities of NLP model~\cite{marcoACL2020checklist}. \Cklst
-introduces input-output behaviors of linguistic capabilities and
-generates behavior-guided inputs for validating the behaviors. It
-provides comprehensive behavioral testing of NLP models through a
-number of generated inputs. However, the approach only relies on
-manually generated input templates, thus the template generation
-becomes expensive and time consuming. In addition, the generated
-templates are selective and often too simple, and it is limited to
-provide restricted evaluation of linguistic capabilities. Thus, it
-does not garauntee the comprehensive evaluation.
-\end{comment}

### 2022-06-07 paper/ase22/CM/coverage.tex
final paper

--- 2022-05-06 paper/ase22/CM/coverage.tex
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/covergae.pdf}
-    \caption{The coverage results of the generated test
-      samples. \sw{Make the figures larger.}}
+    \includegraphics[width=0.5\textwidth]{figs/coverage.pdf}
+    \vspace{-4mm}
+    \caption{Coverage results of \tool and \Cklst test cases.}
     \label{fig:coverage}
@@
 
-Fig. \ref{fig:coverage} shows the coverage results of the generated
-test samples, where the red line represents \tool and the black line
-represents \Cklst.  Each column in Fig. \ref{fig:coverage} represent
-the results for one NLP model, the first row is the \textit{BoundCov}
-results and the second row is the \textit{SActCov} results.  From the
-results, we make two observations observations. First, for \emph{all}
-experimental settings (\eg NLP model, coverage metric), \tool achieves
-high coverage than \Cklst. Recall that a higher coverage implies the
-test case in the test suite is more diverse and rarely to have a
-statistical distribution similar to the model training data. As a
-result, a test suite with greater coverage complements the model
-training data distribution (\ie hold-out testing data) better.  The
-experimental results confirm that \tool can generate more diverse test
-cases to complement the hold-out testing data for testing NLP models.
-\sw{What does the growth trend in each figure indicate?} \sw{Does the
-  absolute numbers or relative difference of the two lines on y axis
-  mean anything concrete? E.g., how significant is the improvement in
-  diversity?}
+Next, Figure \ref{fig:coverage} shows the coverage results of \tool and \Cklst test cases.
+The red line represents \tool coverage and the black line represents \Cklst coverage.
+Each column in Figure \ref{fig:coverage} represents the results for one NLP model.
+The first row is the \textit{BoundCov} results and the second row is the \textit{SActCov} results.
 
-Another interesting finding is that for each NLP model, there is no
-fixed relationship between \textit{BoundCov} and \textit{SActCov}. In
-other words, while a test suite may produce higher \textit{BoundCov}
-for some models, the same test suite may get higher \textit{SActCov}
-for other NLP models.  Recall that \textit{BoundCov} measures both the
-upper and lower corner neurons and \textit{SActCov} measures only the
-upper corner neurons.  Such observation implies that the upper and
-lower corner neurons are distributed unevenly, and measuring only one
-of them is not enough.
+We made three observations.
+First, for \emph{all} experimental settings (i.e., NLP model and coverage metric), \tool achieves higher coverage than \Cklst.
+Recall that a higher coverage implies the test cases are more diverse and do not have a similar statistical distribution to the model training data.
+As a result, a test suite with greater coverage complements the model training data distribution (\ie holdout testing data) better.
+For example, for the first NLP model under test, \tool can achieve a higher coverage than \Cklst with only half the number of test cases.
+This result confirms that \tool can generate more diverse test cases to complement the holdout dataset for testing NLP models.
+
+Second, as the number of test cases increases, the test suite can achieve better coverage.
+Such observation is intuitive.
+However, generating a more extensive test suite is not easy, particularly  for \Cklst, which is a manually template-based approach.
+
+Third, for each NLP model, there is no fixed relationship between \textit{BoundCov} and \textit{SActCov}.
+In other words, while a test suite may produce higher \textit{BoundCov} for some models, the same test suite may get higher \textit{SActCov} for other NLP models.
+Recall that \textit{BoundCov} measures both the upper and lower corner neurons and \textit{SActCov} measures only the upper corner neurons. 
+Such observation implies that the upper and lower corner neurons are distributed unevenly, and measuring only one of them is not enough.

### 2022-06-07 paper/ase22/abstract.tex
final paper

@@
   \Nlp (NLP) technique has become one of the core techniques for
-  developing text analytic applications.  These applications are
-  required to achieve high reliability to be useful in practice.  The
-  trustworthiness of the prevalent NLP applications is obtained by
-  measuring the accuracy of the applications on held-out dataset.
-  However, evaluating NLP on testset with the held-out accuracy is
-  limited in validating its overall quality because the held-out
-  datasets are often not comprehensive. Along with this, evaluating an
-  NLP model on task-specific behaviors defined on empirical linguistic
-  capabilities has been introduced. However, such evaluation relies on
-  manually created test cases, and is still limited to measure the
-  model performance on biased dataset. In this work, we introduce
-  \tool, an NLP model testing infrastructure.  Given a linguistic
-  capability that users want to evaluate for a NLP model, \tool finds
-  suitable seed inputs from existing datasets, generates sufficient
-  number of new test inputs by fuzzing the seed inputs based on their
-  \cfg (CFG).  We evaluate \tool by showing its reliability on
-  generated inputs and its generalization ability.  In our
-  experiments, we also show that \tool facilitates identification of
-  critical failures and its origins in the NLP models for \sa task.
+  developing text  analytic applications.  These applications need to achieve high
+  reliability to be useful in practice.  The trustworthiness of the NLP applications is often obtained by measuring the accuracy of
+  the applications on holdout datasets. However, evaluating NLP on the accuracy of the holdout datasets is limited in validating its overall
+  quality because these datasets are often not
+  comprehensive. To address this limitation, evaluating an NLP model on
+  task-specific behaviors defined on linguistic
+  capabilities has been introduced. However, such evaluation relies on manually
+  created test cases, and  is still limited to measure the model
+  performance on limited datasets. In this work, we introduce \tool,
+  an NLP model testing infrastructure.  Given a linguistic capability that users want to evaluate for a NLP model, \tool finds suitable seed inputs
+  from existing datasets, generates sufficient number
+  of new test inputs by expanding the seed inputs based on their \cfg
+  (CFG).  We evaluate \tool by showing that it can generate test cases that are more diverse than an existing approach.
+  We also show that \tool facilitates
+  identification of critical failures and its origins in the NLP models
+  for the \sa task.
 \end{abstract}
+
+% \begin{abstract}
+%   \Nlp (NLP) technique\jl{technique, model, application?} becomes one of the core techniques for developing
+%   text analytics applications.  For developing the NLP applications,
+%   the applications are required to achieve high reliability before they
+%   go to market\jl{<-simplify the sentence}.  The trustworthiness of the prevalent NLP
+%   applications is obtained by measuring the accuracy of the
+%   applications on test dataset.  However, evaluating NLP on
+%   testset \jl{does with held-out accuracy??} is limited to show its quality
+%   because the test datasets are often not comprehensive \jl{what does it mean?}. While the behavioral testing over multiple general linguistic capabilities are
+%   employed, it relies on manually created test cases, and is still
+%   limited to measure its comprehensive performance for each linguistic
+%   capability \jl{does not make sense in terms of story telling}. In this work, we introduce \tool, an NLP model
+%   testing methodology. Given a linguistic capability, The
+%   \tool finds relevant testcases to test the linguistic
+%   capability from existing datasets as seed inputs, generates
+%   sufficient number of new test cases by fuzzing the seed inputs based
+%   on their \cfg (CFG) \jl{<-long sentence}. We illustrate the usefulness of the \tool by showing input diversity and identifying
+%   critical failures in \sota models for NLP task. In our experiment,
+%   we show that the \tool generates {} more test cases with {}
+%   higher diversity, and finds {} more bugs. \jl{describe what lc is about in a sentence} \jl{need to mention the result with numeric values}
+
+% \end{abstract}

### 2022-06-07 paper/ase22/concl.tex
final paper

@@
+\vspace{-6pt}
 \section{Conclusions}
@@
 
-In this paper, we present \tool automatically that finds and generates
-suitable seed test cases for each \lc. \tool fuzz the seeds into a
-sufficient number of test cases by expanding \cfg of the seed inputs.
-We evaluated \sa models on the generated test cases and anlyzed its
-impact on testing the models. Further, we examined failure-inducing
-cases for seeking the root of the bug.  We also studied the quality of
-\tool test cases by measuring their consistencies with their test
-oracles and \lc. These led to show generalization ability of \tool for
-model evaluation and its reliability in the end. Our work stands to
-provide automated and comprehensive NLP model testing tool.
+In this paper, we present \tool that automatically searches and generates seed test cases for each \lc. \tool expands the seeds into a
+sufficient number of test cases based on \cfg, covering diverse syntactic structures.
+We evaluated \sa models on the generated test cases.
+It is shown that \tool ensures quality of test cases by showing consistency of test oracle with its input sentence and its \lc.
+In addition, we showed that diversity in \tool test cases leads to cover more region in \sa models, resulting in higher reliability on the testing.
+We also examined failure-inducing
+cases to understand the root causes of the bugs. These results demonstrate the correctness and usefulness \tool for
+model evaluation.

### 2022-06-07 paper/ase22/experiment.tex
final paper

--- 2022-05-06 paper/ase22/experiment.tex
@@
 
-\sw{We may miss a RQ for the test results using \tool. In the setup,
-  we have not said which sentiment analysis models we tested, and how
-  we measure the results (e.g., number of misclassified test cases).}
-
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:one}: Can \tool generate consistent test sentence and
-  its oracle?
-\item \label{rq:two}: Are \tool generated test cases relevant to be used
-  for their \lc evaluation?
 \item \label{rq:three}: Can \tool generate more diverse test cases
   than \Cklst?
+\item \label{rq:one}: Can \tool generate test sentences with correct sentiment labels?
+\item \label{rq:two}: Are \tool generated test sentences correctly categorized into a \lc?
 \item \label{rq:four}: Can \tool be useful to find root causes of bugs
@@
 
-\sw{Make clear (earlier in the paper): a test case is a sentence in a
-  linguistic capability with a sentiment label.}
-
 \subsection{Experimental Subjects}
@@
 \paragraph{\textbf{NLP Models \& Dataset.}}
-We evaluate our approach on three leaerning-based \sa models
+We evaluate our approach on three learning-based \sa models
 implemented in Transformer library from the Hugging Face centralized
-Model Hub.\footnote{https://huggingface.co/models}: \texttt{\Bert}
-(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
-\texttt{\Dbert} (\disbertsamodel). They are pre-trained on English
+Model Hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
+(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
 language using a masked language modeling (MLM) objective, and
-fine-tuned on \sa task. In this experiment, we use \Sstt dataset for
-searching seeds and expanding the seeds in \tool.
+fine-tuned on the \sa task. In this experiment, we use \Sstt \cite{socher2013sst} dataset for
+searching the seeds in \tool. \Sstt is a
+corpus of movie review, and consists of 11,855 sentences
+with sentiment scores. We split the
+scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign 
+negative, neutral and positive labels, respectively. In addition, 
+we use \Swn as the word sentiment dataset~\cite{baccianella2010sentiwordnet}. 
+\Swn is a publicly available English sentiment lexicons.  
+It provides lexical sentiment scores and the sentiment word labels 
+are categorized by implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
 %% \TODO{introduce details about each model}
 
-\paragraph{\textbf{Comparison Baselines.}}
-We compare our approach with
-\Cklst\footnote{https://github.com/marcotcr/checklist}, which is a
+\paragraph{\textbf{Comparison Baseline.}}
+We compare \tool with
+\Cklst,\footnote{https://github.com/marcotcr/checklist} a
 manual template-based approach to generate test cases. In this
@@
 
-\paragraph{\textbf{RQ1 and RQ2}} As described in Section \ref{sec:approach},
-\tool generates test cases in two steps: specification-based seed
-generation and syntax-based sentence expansion. These automated steps
-may generate seed/expanded sentences marked with incorrect sentiment
-labels or categorized into wrong linguistic capabilities. For example,
-the search rule and template defined in a linguistic capability may
-not always generate seed sentences in that capability or with the
-correct label.  To answer RQ1 and RQ2, we perform a manual study to
-measure the correctness of the sentiment labels and linguistic
-capabilities associated with the seed/expanded sentences, produced by
-\tool.
+\paragraph{\textbf{RQ1.}}
+Recall that a key limitation of \Cklst is that its template-based
+approach relies on significant manual efforts and may not generate test cases that comprehensively cover the sentences
+in a linguistic capability. \tool, instead, automatically generates test cases based on a search
+dataset and the syntax in a large reference corpus. 
+We expect \tool can generate a more diverse test suite than \Cklst, and achieve
+more probable evaluation results.
 
-In the manual study, we randomly sample three sets of pairs of seed
-sentences and corresponding \lc from seed test cases. For each set, we
-also select expanded sentences that \tool generated from the formerly
-sampled seed sentences. In this experiment, each set has 100 sentences
-(50 from seed sentences and 50 from expanded sentences) and 200
-sentences, in total, are used for the manual study. For each sampled
-set, two subjects are provided with the same set of sampled
-sentences. The subjects are asked for scoring the two following:
-\textbf{1. relevancy score between sentence and its associated \lc}:
-this score measures the amount of appropriateness of the use of
-sentence for evaluating the model on its \lc.  The scores are discrete
-ranging from 1 to 5, and each represents ``strongly not relevant'' to
-``strongly relevant'' respectively. \textbf{2. sentiment score of
-  sentence}: this score measures the level of sentence sentiment. It
-is also discrete, and it ranges from 1 to 5 representing ``strongly
-negative'' to ``strongly positive'' respectively. In this work, we
-collect manual study scores from 3 subjects in total. In case of
-different scores with a same sentence from different subjects, we used
-their average score as a score of the sentence.
-%% \sw{6 or 3 participants? What happened if participants scored differently?}
-From the collected scores, we measure the following metrics:
+We first evaluate the three \sa
+models by testing them on the \tool generated test cases, reporting number of test cases and each model's failure rate in each linguistic capability.
 
-\begin{eqnarray}
-  sentiment\_relecancy &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:srel} \\
-  LC\_relevancy_{AVG} &= \frac{1}{\#data}\cdot\sum_{i} LC\_relevancy_i \label{metric:lcrel}
-\end{eqnarray}
-
-The equation~\ref{metric:srel} represent the number of test cases that
-their labels assigned from are different between \tool and
-human. Higher number of this metric indicates worse correlation of
-test oracle that \tool generated with human. In addition, the
-equation~\ref{metric:lcrel} represents the average score of the
-relevancy score between sentence and its associated \lc. Higer average
-score means that higher human-level agreement of the use of sentence
-for its \lc, resulting in higher suitability of the use of the
-testcases for evaluating model on the \lc. Given the metrics, we
-answer RQ1 and RQ2 by the metrics from the equation~\ref{metric:srel}
-and equation~\ref{metric:lcrel} respectively, thereby, show its
-ability of \tool to understand human intelligence.
-
-\paragraph{RQ3.}
-Recall that a key limitation of \Cklst is that its template-based
-approach that relies on significant manual efforts may not generate
-test cases that comprehensively cover the sentences in a linguistic
-capability. \tool, instead, automatically generates test cases based
-on a search dataset and the syntax in a large reference corpus. We
-expect \tool can generate a more diverse test suite than \Cklst. To
-measure diversity, we follow the approach presented by Ma et
-al. \cite{ma2018deepgauge}, where the authors measure the coverage of
-NLP model intermediate states as corner-case neurons.  Because the
-matrix computation of intermediate states impacts NLP model
-decision-making, a test suite that covers a greater number of
-intermediate states can represent more NLP model decision-making,
-making it more diverse.  Specifically, we used two coverage metrics in
-existing work \cite{ma2018deepgauge}, \textit{boundary coverage}
-(BoundCov) and \textit{strong activation coverage} (SActCov), as our
-metrics to evaluate the test suite diversity.  \TODO{It is worth
-  noting that a test sample with a statistical distribution similar to
-  the training data would rarely be found in the corner case
-  region. As a result, covering a larger corner case region means that
-  the test suite is more likely to be buggy.}
+Next,
+to measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
+where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
+Because the matrix computation of intermediate states impacts NLP model decision-making, a test suite that covers a greater number of intermediate states can represent more NLP model decision-making, making it more diverse.
+Specifically, we used two coverage metrics by Ma et al.
+\cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
+It is worth noting that a test sample with a statistical distribution similar to the training data would rarely be found in the corner case region.
+As a result, covering a larger corner case region means that the test suite is more likely to be buggy.
 
@@
 
-\noindent Eq.
-\ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n, low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
+\noindent Equation \ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
 Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
@@
 
-\noindent The formal definition of our coverage metrics are shown in Eq.\ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
+\noindent The formal definition of our coverage metrics are shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
 Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.
@@
 
-To answer {\bf RQ3}, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
+To answer RQ1, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
 After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
@@
 
-\paragraph{RQ4.}
+\paragraph{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
+\tool generates test cases in two steps: specification-based seed
+generation and syntax-based sentence expansion. These automated steps
+may generate seed/expanded sentences marked with incorrect sentiment
+labels or categorized into wrong linguistic capabilities. For example,
+the search rule and template defined in a linguistic capability may
+not always generate seed sentences in that capability or with the
+correct label.  To answer RQ2 and RQ3, we performed a manual study to
+measure the correctness of the sentiment labels and linguistic
+capabilities associated with the seed/expanded sentences, produced by
+\tool.
+
+In the manual study, we randomly sample 100 seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set).
+For each sampled seed sentence, we randomly obtain one of its expanded sentences.
+This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
+We recruited three participants of this study; all of them are graduate students with no knowledge about this work. 
+2 of them were assigned one set of sentences and the third was assigned the other set.
+Each participant was asked to provide two scores for each sentence.
+\emph{(1) Relevancy score between sentence and its associated \lc}:
+this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete,
+ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment score of the sentence}: this score measures the sentiment level of the sentence . It
+is also discrete, ranging from 1 (``strongly
+negative'') to 5 (``strongly positive''). 
+We measure the following:
+
+\begin{eqnarray}
+  sent\_consistency &= \frac{1}{\#Sample\cdot~}\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human}) \label{metric:srel} \\
+  LC\_relevancy_{AVG} &= \frac{1}{\#Sample\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
+\end{eqnarray}
+
+Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants produce the same sentiment labels.
+High value of this metric indicates \tool generates test cases with correct labels.
+Equation~\ref{metric:lcrel} represents the average of the
+normalized relevancy score between a sentence and its associated
+\lc. Higher average score means indicates the linguistic capability categorization by \tool is correct. We answer RQ2 and RQ3 using the metrics defined by
+Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
+respectively.
+
+\paragraph{\textbf{RQ4.}}
 
@@
 Still, it is unclear why mutating one token will cause the model to produce misclassified results.
-We seek to help developers to understand why such mutation will result in the misclassification. 
+We seek to help developers understand why such mutation will result in the misclassification. 
 Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences).
-Motivated by such intuition, we seek to identify a minimal set of input tokens that dominate the model prediction.
+Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.
 
-Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token in $x$ or not.
+Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
 The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
-
 \begin{equation}
@@
 \end{equation}
-
-To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{}.
-Following that, we begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Eq.
-\ref{eq:prob}.
-We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Eq. \ref{eq:prob}
-Because we iterate the size of our mask, the generated template $T$ will keep the minimum number of tokens in $x$.
+To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}.
+We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
+We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
+Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$.
 Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).
@@
 
-\noindent\textbf{Implementation Details.}
+% \noindent\textbf{Implementation Details.}
 
-\sw{Missing: environment running these experiments.}
+% \sw{Missing: environment running these experiments.}
 

### 2022-06-07 paper/ase22/result.tex
final paper

--- 2022-05-06 paper/ase22/result.tex
@@
 This section presents experiment results and answer the RQs by
-studying the results quantatively and qualitatively.
+studying the results quantitatively and qualitatively.
+
+\InputWithSpace{tables/test-results-table}
+
+\subsection{RQ1: Test Suite Diversity}
+
+Our experimental results show that \emph{\tool generated many test cases that the sentiment analysis models failed to predict the correct labels, and it produced significantly more diverse test cases than \Cklst did.}
+
+Table~\ref{table:TestResult} shows the testing results of three \sa models. First column lists 
+linguistic capabilities for the \sa task, and Columns 2-3 show 
+the numbers of seed and expanded test cases, respectively. 
+Columns 4-5 show the failure rate (i.e., percentage of test cases that a model predicts incorrect label) of each \sa models on the seed and expanded test cases respectively. 
+Column 6 shows the number of expanded test cases that failed,
+but their corresponding seed test cases passed.
+
+We observe that in all but one linguistic capabilities,
+\tool produces hundreds of test cases, expanding at least an order of magnitude more test cases than the seeds.
+LC3 is an outlier; the 50 randomly selected
+seeds in this linguistic capability did not produce any validated
+expansions.
+LC1 and LC5 have 19 and 26 seeds,
+respectively. This means that \tool's search rules and transformation templates of these two linguistic capabilities produced few seeds.
+Nevertheless, the syntax-base sentence expansion phase allows generation of 210 and 1009 test cases, respectively.
+
+In terms of \sa model performance, all
+three models achieve low failure rates in LC9 and LC2 while the failure rates are high in all other linguistic capabilities (26\%-100\%).
+We also observe that there are significant number of expanded test cases that failed, but their corresponding seeds did not (last column in Table \ref{table:TestResult}).
+This shows that the syntax-based sentence expansion phase indeed introduces more diverse sentence structures in the test cases that cause the models to fail.
+% It finally
+% shows usefulness of \tool since the different test results between
+% seed and expanded cases provide accurate guidance for debugging model.
+
+\input{CM/coverage}
 
 \InputWithSpace{tables/manual-study-table}
-\InputWithSpace{tables/test-results-table}
 
-\subsection{RQ1: \tool Sentiment Label Consistency}
-Table~\ref{table:ManualStudy} shows the statistics of scores collected
-from the manual study of \tool. First column represents type of test
-case. The number of test cases used for the study is represented in
-second column. Label consistency score and \lc relevancy score defined
-at equation~\ref{metric:srel} and~\ref{metric:lcrel} are shown at the
-remaining columns. First, it is shown that high label consistency
-score over 0.8. It means that \tool generates test oracles consistent
-to human understanding. It is also observed that there is no
-difference of the scores between seed and expanded sentences. The
-observation implies that the expansion method in \tool preserves
-sentiment of expanded sentences as its seed, and provides its
-reliability. These observations answer RQ1 and conclude that \tool
-generates test case with high consistency between test sentence and
-its oracle.
+\subsection{RQ2: Correctness of Sentiment Labels}
+Table~\ref{table:ManualStudy} shows results of our manual study. The first column distinguishes the seed and expanded sentences. The number of test cases used for the study is represented in the
+second column. The label consistency score defined
+in Equation~\ref{metric:srel} is shown in column 3.
 
-\subsection{RQ2: Correctness of Linguistic Capability Categorization}
-The result in table~\ref{table:ManualStudy} also shows that \tool
-achieves high order of agreement with human assessment on \lc
-relevancy. In parallel, it is observed that the expanded sentences
-generated from \tool also have same level of \lc
-relevancy. Accordingly, we answer the RQ2 by concluding that
-\tool generates \lc relevant test cases with the agreement with human.
+We observe that \emph{\tool generates test cases that consistently
+  label their sentiment correctly.}  Column 3 shows that the label
+consistency scores are 0.83 and 0.84 for the seed and expanded
+sentences, respectively.
+This means that \tool generates test oracles consistent with
+human understanding most of the time. Also, there is
+little difference of the scores between the seed and expanded
+sentences. This implies that the syntax-based sentence expansion in
+\tool preserves the sentiment as its seed.
 
-\jl{The following needs to be in RQ2 result section after simin
-  completes RQ2 result section} Table~\ref{table:TestResult} shows
-results of evaluation of three \sa models. First column lists
-linguistic capability for \sa task, and Columns 2-3 show the number of
-seed and expanded test cases respectively. Columns 4-5 show the
-failure rate in percentage by running the \sa models on the seed and
-expanded test cases respectively. Column 6 shows the number of
-expanded test cases failed, but their seed test cases passed. For LC9,
-we combine two
+% \sw{This paragraph is problematic.
+We are saying the inconsistency is just caused by human, indicating our tool is always correct?} Nevertheless, there exist inconsistency between \tool and manual labels.
+The causes of inconsistency are twofold.
+First, complicated sentences have led the participants to
+% misunderstand its meaning. Second, phrase in a sentence has
+% multiple interpretations of its sentiment. For example, the
+% word ``easy'' could be interpreted as both compliment and back-handed
+% insult.  
+%% \sw{What are
+%%   the causes of inconsistency? Looks like the main source of
+%%   inconsistency comes from seed generation? Any insights on how it
+%%   happened (e.g., issue with original labels, search rules, or
+%%   templates?}
 
-From the
-table, we can observe that
+\subsection{RQ3: Correctness of Linguistic Capability Categorization}
 
-\subsection{RQ3: Test Suite Diversity}
-\input{CM/coverage}
+The \lc relevancy score defined
+in Equation~\ref{metric:lcrel} is shown in Column 4 of Table \ref{table:ManualStudy}. The result shows that
+\emph{\tool generates test cases that are correctly categorized to the corresponding linguistic capabilities most of the time.}
+The \lc relevancy scores for the seed and expanded sentences are both 0.9, achieving high order of agreement with human assessment. The fact that the expanded sentences
+generated by \tool also have the same level of \lc
+relevancy as the seed sentences shows that the syntax-based sentence expansion retains the linguistic capabilities.
 
-\subsection{RQ4: Use \tool for Debugging}
+\subsection{RQ4: Use \tool for Understanding Errors}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.99\textwidth]{figs/explain.pdf}
+    \vspace{-4mm}
+    \caption{Visualization of the buggy reason of two \tool generated test cases.}
+    \label{fig:explain}
+\end{figure*}
+
+Recall our RQ4 is to generate a template that will dominate the NLP model prediction to assist developers in understanding the false predictions.
+Figure \ref{fig:explain} shows the generated templates for two randomly selected seed inputs and corresponding generated test inputs.
+The first example is to test ``sentiments in (question, yes) form'' (LC9), and the second example is to test ``negative positive with neutral content in the middle''  (LC7).
+The first column contains the seed sentence, the second contains the generated sentence, and the third contains thCT  of each token's contribution score.
+The blue bar indicates thxe score for seed inputs, whereas the orange bar reflects the score f CTor created sentences.
+We highlight the mutated token with yellow background and generated templates with red text.
+
+The results show that after mutating the seed sentence with one token, the token set that dominates the NLP model prediction has changed.
+We can trace the root causes to the bias of training data on the \lc under test; as a result, for the \lc under test, the model has a bias towards positive/negative for certain token sequence patterns.
+For example, \lc 9 has a bias toward the token sequence pattern that includes "maybe ....
+but ...
+even...
+yes".
+Thus, adding the token "even" to the seed sentence will match one of those biased sequence patterns.
+Sentences with s.8gmxuin the training dataset are dominantly positive, thus the models makes the wrong decision on the sentence with ``even'' as positive. 
+The visualization of each token's contribution score in the third column also confirms our observation.
+Once  ``even'' is added, scores of other tokens such as ``but'' and ``yes'' all change from negative to positive.
+To fix the issue for LC9, we ne ed to add more training negative samples with the 还 of ``maybe . .. but ... even ... yes''.
+%he experimental results in Fig. \ref{fig:explain} illustrate that \tool can help developers to understand the buggy reason of the misclassification go no在，

### 2022-08-29 python/hs/testsuite/Fillmask.py
debug hs

@@ -1,0 +1,49 @@
+# This script is to fill mask token using huggingface pipeline
+# loading bert-base-uncased model
+
+from typing import *
+
+import re, os
+import nltk
+import spacy
+import copy
+import time
+import random
+import numpy as np
+
+from pathlib import Path
+from scipy.special import softmax
+
+# from transformers import pipeline
+from transformers import BertTokenizer, BertModel
+
+class Fillmask:
+
+    checklist_mask_token = '{mask}'
+    huggingface_mask_token = '[MASK]'
+    unmasker_model_name = 'bert-base-uncased'
+
+    @classmethod
+    def replace_mask_token(cls, masked_sent):
+        return masked_sent.replace(cls.checklist_mask_token,
+                                   cls.huggingface_mask_token)
+
+    @classmethod
+    def load_unmasker(cls):
+        tokenizer = BertTokenizer.from_pretrained(cls.unmasker_model_name)
+        model = BertModel.from_pretrained(cls.unmasker_model_name)
+        return model, tokenizer
+
+    @classmethod
+    def suggest(cls, masked_sents):
+        # out format example
+        # {'sequence': "[CLS] hello i'm a fashion model. [SEP]",
+        #  'score': 0.1073106899857521,
+        #  'token': 4827,
+        #  'token_str': 'fashion'}
+        if type(masked_sents)==str:
+            out = unmasker(masked_sents)
+        elif type(masked_sents)==list:
+                
+        
+    

### 2022-08-29 python/hs/testsuite/Suggest.py

@@ -7,13 +7,16 @@ from typing import *
 
 import re, os
 import nltk
-# import spacy
+import spacy
 import copy
+import time
 import random
 import numpy as np
+import multiprocessing
 
 from pathlib import Path
 from scipy.special import softmax
+from spacy_wordnet.wordnet_annotator import WordnetAnnotator
 # from nltk.tokenize import word_tokenize as tokenize
 
 import checklist
@@ -25,12 +28,12 @@ from ..utils.Utils import Utils
 # from .cfg.CFG import BeneparCFG
 from .Search import SearchOperator, SENT_DICT
 
-random.seed(Macros.SEED)
 NUM_TOPK = 5
 
 class Suggest:
 
     MASK = Macros.MASK
+    NUM_PROCESSES = Macros.num_processes
 
     @classmethod
     def is_word_suggestion_avail(cls, word_suggest):
@@ -69,14 +72,23 @@ class Suggest:
                             gen_inputs,
                             num_target=10):
         results = dict()
+        # mi_st = time.time()
         masked_inputs = cls.get_masked_inputs(gen_inputs)
-        for m_inp in masked_inputs:
+        # mi_ft = time.time()
+        # print(f"cls.get_word_suggestion::get_masked_inputs:<{round(mi_ft-mi_st,2)} seconds>::")
+        # for_st = time.time()
+        for m_inp_i, m_inp in enumerate(masked_inputs):
+            # ws_st = time.time()
             word_suggest = editor.suggest(m_inp, return_score=True, remove_duplicates=True)
             word_suggest = sorted(word_suggest, key=lambda x: x[-1], reverse=True)[:num_target]
             word_suggest = [ws for ws in word_suggest if cls.is_word_suggestion_avail(ws[0])]
             word_suggest = cls.remove_duplicates(word_suggest)
             results[m_inp] = word_suggest
+            # ws_ft = time.time()
+            # print(f"cls.get_word_suggestion::masked_inputs{m_inp_i}::{m_inp}::<{round(ws_ft-ws_st,2)} seconds>::")
         # end for
+        # for_ft = time.time()
+        # print(f"cls.get_word_suggestion::masked_inputs::for_loop<{round(for_ft-for_st,2)} seconds>::")
         return results
     
     @classmethod
@@ -177,7 +189,7 @@ class Suggest:
         return False
     
     @classmethod
-    def eval_sug_words_by_req(cls, new_input, requirement, label, nlp):
+    def eval_sug_words_by_req(cls, new_input, requirement, label):
[…]

### 2022-08-29 paper/ase22/tables/test-results-3-200-numbers.tex
add new tables and figs

%% Automatically generated by pyutil.latex

\DefMacro{test-results-3-200-lc7}{Author sentiment is more important than of others}
\DefMacro{test-results-3-200-lc7-num-seeds}{200}
\DefMacro{test-results-3-200-lc7-num-exps-avg}{6908.0}
\DefMacro{test-results-3-200-lc7-num-exps-med}{7022}
\DefMacro{test-results-3-200-lc7-num-exps-std}{978.245}
\DefMacro{test-results-3-200-model0-lc7-num-seed-fail-avg}{23.83}
\DefMacro{test-results-3-200-model0-lc7-num-seed-fail-med}{21.0}
\DefMacro{test-results-3-200-model0-lc7-num-seed-fail-std}{2.675}
\DefMacro{test-results-3-200-model0-lc7-num-exp-fail-avg}{25.44}
\DefMacro{test-results-3-200-model0-lc7-num-exp-fail-med}{25.12}
\DefMacro{test-results-3-200-model0-lc7-num-exp-fail-std}{2.355}
\DefMacro{test-results-3-200-model0-lc7-num-pass-to-fail-avg}{110.33}
\DefMacro{test-results-3-200-model0-lc7-num-pass-to-fail-med}{100}
\DefMacro{test-results-3-200-model0-lc7-num-pass-to-fail-std}{35.035}
\DefMacro{test-results-3-200-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-3-200-lc3-num-seeds}{67}
\DefMacro{test-results-3-200-lc3-num-exps-avg}{2845.67}
\DefMacro{test-results-3-200-lc3-num-exps-med}{2839}
\DefMacro{test-results-3-200-lc3-num-exps-std}{9.45}
\DefMacro{test-results-3-200-model0-lc3-num-seed-fail-avg}{89.55}
\DefMacro{test-results-3-200-model0-lc3-num-seed-fail-med}{89.55}
\DefMacro{test-results-3-200-model0-lc3-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model0-lc3-num-exp-fail-avg}{91.45}
\DefMacro{test-results-3-200-model0-lc3-num-exp-fail-med}{91.49}
\DefMacro{test-results-3-200-model0-lc3-num-exp-fail-std}{0.085}
\DefMacro{test-results-3-200-model0-lc3-num-pass-to-fail-avg}{81.33}
\DefMacro{test-results-3-200-model0-lc3-num-pass-to-fail-med}{81}
\DefMacro{test-results-3-200-model0-lc3-num-pass-to-fail-std}{0.765}
\DefMacro{test-results-3-200-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-3-200-lc4-num-seeds}{26}
\DefMacro{test-results-3-200-lc4-num-exps-avg}{1096.67}
\DefMacro{test-results-3-200-lc4-num-exps-med}{1105}
\DefMacro{test-results-3-200-lc4-num-exps-std}{10.395}
\DefMacro{test-results-3-200-model0-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-200-model0-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-200-model0-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model0-lc4-num-exp-fail-avg}{92.52}
\DefMacro{test-results-3-200-model0-lc4-num-exp-fail-med}{92.67}
\DefMacro{test-results-3-200-model0-lc4-num-exp-fail-std}{0.15}
\DefMacro{test-results-3-200-model0-lc4-num-pass-to-fail-avg}{65.67}
\DefMacro{test-results-3-200-model0-lc4-num-pass-to-fail-med}{65}
\DefMacro{test-results-3-200-model0-lc4-num-pass-to-fail-std}{0.575}
\DefMacro{test-results-3-200-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-3-200-lc6-num-seeds}{200}
\DefMacro{test-results-3-200-lc6-num-exps-avg}{4731.0}
\DefMacro{test-results-3-200-lc6-num-exps-med}{4927}
\DefMacro{test-results-3-200-lc6-num-exps-std}{205.36}
\DefMacro{test-results-3-200-model0-lc6-num-seed-fail-avg}{88.5}
\DefMacro{test-results-3-200-model0-lc6-num-seed-fail-med}{90.0}
\DefMacro{test-results-3-200-model0-lc6-num-seed-fail-std}{3.93}
\DefMacro{test-results-3-200-model0-lc6-num-exp-fail-avg}{92.94}
\DefMacro{test-results-3-200-model0-lc6-num-exp-fail-med}{96.43}
\DefMacro{test-results-3-200-model0-lc6-num-exp-fail-std}{3.34}
\DefMacro{test-results-3-200-model0-lc6-num-pass-to-fail-avg}{42.33}
\DefMacro{test-results-3-200-model0-lc6-num-pass-to-fail-med}{53}
\DefMacro{test-results-3-200-model0-lc6-num-pass-to-fail-std}{16.655}
\DefMacro{test-results-3-200-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-3-200-lc5-num-seeds}{200}
\DefMacro{test-results-3-200-lc5-num-exps-avg}{5389.67}
\DefMacro{test-results-3-200-lc5-num-exps-med}{5387}
\DefMacro{test-results-3-200-lc5-num-exps-std}{69.01}
\DefMacro{test-results-3-200-model0-lc5-num-seed-fail-avg}{99.5}
\DefMacro{test-results-3-200-model0-lc5-num-seed-fail-med}{99.5}
\DefMacro{test-results-3-200-model0-lc5-num-seed-fail-std}{0.25}
\DefMacro{test-results-3-200-model0-lc5-num-exp-fail-avg}{99.83}
\DefMacro{test-results-3-200-model0-lc5-num-exp-fail-med}{99.81}
\DefMacro{test-results-3-200-model0-lc5-num-exp-fail-std}{0.06}
\DefMacro{test-results-3-200-model0-lc5-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-200-model0-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-200-model0-lc5-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-200-lc9}{Parsing sentiment in (question, no) form}
\DefMacro{test-results-3-200-lc9-num-seeds}{200}
\DefMacro{test-results-3-200-lc9-num-exps-avg}{5814.0}
\DefMacro{test-results-3-200-lc9-num-exps-med}{5937}
\DefMacro{test-results-3-200-lc9-num-exps-std}{281.335}
\DefMacro{test-results-3-200-model0-lc9-num-seed-fail-avg}{77.17}
\DefMacro{test-results-3-200-model0-lc9-num-seed-fail-med}{76.0}
\DefMacro{test-results-3-200-model0-lc9-num-seed-fail-std}{1.7}
\DefMacro{test-results-3-200-model0-lc9-num-exp-fail-avg}{75.48}
\DefMacro{test-results-3-200-model0-lc9-num-exp-fail-med}{76.47}
\DefMacro{test-results-3-200-model0-lc9-num-exp-fail-std}{0.905}
\DefMacro{test-results-3-200-model0-lc9-num-pass-to-fail-avg}{99.67}
\DefMacro{test-results-3-200-model0-lc9-num-pass-to-fail-med}{76}
\DefMacro{test-results-3-200-model0-lc9-num-pass-to-fail-std}{20.495}
\DefMacro{test-results-3-200-lc2}{Sentiment change over time, present should prevail}
\DefMacro{test-results-3-200-lc2-num-seeds}{200}
\DefMacro{test-results-3-200-lc2-num-exps-avg}{6245.33}
\DefMacro{test-results-3-200-lc2-num-exps-med}{6256}
\DefMacro{test-results-3-200-lc2-num-exps-std}{178.56}
\DefMacro{test-results-3-200-model0-lc2-num-seed-fail-avg}{20.67}
\DefMacro{test-results-3-200-model0-lc2-num-seed-fail-med}{19.5}
\DefMacro{test-results-3-200-model0-lc2-num-seed-fail-std}{1.465}
\DefMacro{test-results-3-200-model0-lc2-num-exp-fail-avg}{20.57}
\DefMacro{test-results-3-200-model0-lc2-num-exp-fail-med}{20.05}
\DefMacro{test-results-3-200-model0-lc2-num-exp-fail-std}{1.24}
\DefMacro{test-results-3-200-model0-lc2-num-pass-to-fail-avg}{199.33}
\DefMacro{test-results-3-200-model0-lc2-num-pass-to-fail-med}{198}
\DefMacro{test-results-3-200-model0-lc2-num-pass-to-fail-std}{13.51}
\DefMacro{test-results-3-200-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-3-200-lc0-num-seeds}{19}
\DefMacro{test-results-3-200-lc0-num-exps-avg}{235.33}
\DefMacro{test-results-3-200-lc0-num-exps-med}{243}
\DefMacro{test-results-3-200-lc0-num-exps-std}{9.36}
\DefMacro{test-results-3-200-model0-lc0-num-seed-fail-avg}{78.95}
\DefMacro{test-results-3-200-model0-lc0-num-seed-fail-med}{78.95}
\DefMacro{test-results-3-200-model0-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model0-lc0-num-exp-fail-avg}{89.5}
\DefMacro{test-results-3-200-model0-lc0-num-exp-fail-med}{89.25}
\DefMacro{test-results-3-200-model0-lc0-num-exp-fail-std}{0.385}
\DefMacro{test-results-3-200-model0-lc0-num-pass-to-fail-avg}{18.33}
\DefMacro{test-results-3-200-model0-lc0-num-pass-to-fail-med}{18}
\DefMacro{test-results-3-200-model0-lc0-num-pass-to-fail-std}{0.765}
\DefMacro{test-results-3-200-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-3-200-lc1-num-seeds}{200}
\DefMacro{test-results-3-200-lc1-num-exps-avg}{1951.0}
\DefMacro{test-results-3-200-lc1-num-exps-med}{1968}
\DefMacro{test-results-3-200-lc1-num-exps-std}{44.365}
\DefMacro{test-results-3-200-model0-lc1-num-seed-fail-avg}{1.5}
\DefMacro{test-results-3-200-model0-lc1-num-seed-fail-med}{1.5}
\DefMacro{test-results-3-200-model0-lc1-num-seed-fail-std}{0.25}
\DefMacro{test-results-3-200-model0-lc1-num-exp-fail-avg}{4.87}
\DefMacro{test-results-3-200-model0-lc1-num-exp-fail-med}{4.53}
\DefMacro{test-results-3-200-model0-lc1-num-exp-fail-std}{0.32}
\DefMacro{test-results-3-200-model0-lc1-num-pass-to-fail-avg}{38.67}
\DefMacro{test-results-3-200-model0-lc1-num-pass-to-fail-med}{42}
\DefMacro{test-results-3-200-model0-lc1-num-pass-to-fail-std}{11.095}
\DefMacro{test-results-3-200-lc8}{Parsing sentiment in (question, yes) form}
\DefMacro{test-results-3-200-lc8-num-seeds}{200}
\DefMacro{test-results-3-200-lc8-num-exps-avg}{5578.67}
\DefMacro{test-results-3-200-lc8-num-exps-med}{5578}
\DefMacro{test-results-3-200-lc8-num-exps-std}{65.5}
\DefMacro{test-results-3-200-model0-lc8-num-seed-fail-avg}{4.83}
\DefMacro{test-results-3-200-model0-lc8-num-seed-fail-med}{5.0}
\DefMacro{test-results-3-200-model0-lc8-num-seed-fail-std}{0.145}
\DefMacro{test-results-3-200-model0-lc8-num-exp-fail-avg}{5.48}
\DefMacro{test-results-3-200-model0-lc8-num-exp-fail-med}{5.66}
\DefMacro{test-results-3-200-model0-lc8-num-exp-fail-std}{0.56}
\DefMacro{test-results-3-200-model0-lc8-num-pass-to-fail-avg}{99.0}
\DefMacro{test-results-3-200-model0-lc8-num-pass-to-fail-med}{87}
\DefMacro{test-results-3-200-model0-lc8-num-pass-to-fail-std}{14.0}
\DefMacro{test-results-3-200-model1-lc7-num-seed-fail-avg}{15.0}
\DefMacro{test-results-3-200-model1-lc7-num-seed-fail-med}{16.5}
\DefMacro{test-results-3-200-model1-lc7-num-seed-fail-std}{2.46}
\DefMacro{test-results-3-200-model1-lc7-num-exp-fail-avg}{16.15}
\DefMacro{test-results-3-200-model1-lc7-num-exp-fail-med}{13.62}
\DefMacro{test-results-3-200-model1-lc7-num-exp-fail-std}{3.07}
\DefMacro{test-results-3-200-model1-lc7-num-pass-to-fail-avg}{171.33}
\DefMacro{test-results-3-200-model1-lc7-num-pass-to-fail-med}{224}
\DefMacro{test-results-3-200-model1-lc7-num-pass-to-fail-std}{53.14}
\DefMacro{test-results-3-200-model1-lc3-num-seed-fail-avg}{85.07}
\DefMacro{test-results-3-200-model1-lc3-num-seed-fail-med}{85.07}
\DefMacro{test-results-3-200-model1-lc3-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model1-lc3-num-exp-fail-avg}{88.59}
\DefMacro{test-results-3-200-model1-lc3-num-exp-fail-med}{88.63}
\DefMacro{test-results-3-200-model1-lc3-num-exp-fail-std}{0.08}
\DefMacro{test-results-3-200-model1-lc3-num-pass-to-fail-avg}{65.33}
\DefMacro{test-results-3-200-model1-lc3-num-pass-to-fail-med}{63}
\DefMacro{test-results-3-200-model1-lc3-num-pass-to-fail-std}{2.02}
\DefMacro{test-results-3-200-model1-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-200-model1-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-200-model1-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model1-lc4-num-exp-fail-avg}{93.13}
\DefMacro{test-results-3-200-model1-lc4-num-exp-fail-med}{93.12}
\DefMacro{test-results-3-200-model1-lc4-num-exp-fail-std}{0.06}
\DefMacro{test-results-3-200-model1-lc4-num-pass-to-fail-avg}{45.33}
\DefMacro{test-results-3-200-model1-lc4-num-pass-to-fail-med}{44}
\DefMacro{test-results-3-200-model1-lc4-num-pass-to-fail-std}{1.605}
\DefMacro{test-results-3-200-model1-lc6-num-seed-fail-avg}{74.17}
\DefMacro{test-results-3-200-model1-lc6-num-seed-fail-med}{73.5}
\DefMacro{test-results-3-200-model1-lc6-num-seed-fail-std}{6.005}
\DefMacro{test-results-3-200-model1-lc6-num-exp-fail-avg}{77.89}
\DefMacro{test-results-3-200-model1-lc6-num-exp-fail-med}{74.05}
\DefMacro{test-results-3-200-model1-lc6-num-exp-fail-std}{4.595}
\DefMacro{test-results-3-200-model1-lc6-num-pass-to-fail-avg}{112.0}
\DefMacro{test-results-3-200-model1-lc6-num-pass-to-fail-med}{97}
\DefMacro{test-results-3-200-model1-lc6-num-pass-to-fail-std}{31.43}
\DefMacro{test-results-3-200-model1-lc5-num-seed-fail-avg}{99.5}
\DefMacro{test-results-3-200-model1-lc5-num-seed-fail-med}{99.5}
\DefMacro{test-results-3-200-model1-lc5-num-seed-fail-std}{0.25}
\DefMacro{test-results-3-200-model1-lc5-num-exp-fail-avg}{99.58}
\DefMacro{test-results-3-200-model1-lc5-num-exp-fail-med}{99.67}
\DefMacro{test-results-3-200-model1-lc5-num-exp-fail-std}{0.145}
\DefMacro{test-results-3-200-model1-lc5-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-200-model1-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-200-model1-lc5-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-200-model1-lc9-num-seed-fail-avg}{86.33}
\DefMacro{test-results-3-200-model1-lc9-num-seed-fail-med}{86.0}
\DefMacro{test-results-3-200-model1-lc9-num-seed-fail-std}{1.505}
\DefMacro{test-results-3-200-model1-lc9-num-exp-fail-avg}{86.8}
\DefMacro{test-results-3-200-model1-lc9-num-exp-fail-med}{86.64}
\DefMacro{test-results-3-200-model1-lc9-num-exp-fail-std}{0.235}
\DefMacro{test-results-3-200-model1-lc9-num-pass-to-fail-avg}{46.33}
\DefMacro{test-results-3-200-model1-lc9-num-pass-to-fail-med}{52}
\DefMacro{test-results-3-200-model1-lc9-num-pass-to-fail-std}{6.25}
\DefMacro{test-results-3-200-model1-lc2-num-seed-fail-avg}{48.33}
\DefMacro{test-results-3-200-model1-lc2-num-seed-fail-med}{49.5}
\DefMacro{test-results-3-200-model1-lc2-num-seed-fail-std}{1.94}
\DefMacro{test-results-3-200-model1-lc2-num-exp-fail-avg}{47.94}
\DefMacro{test-results-3-200-model1-lc2-num-exp-fail-med}{47.1}
\DefMacro{test-results-3-200-model1-lc2-num-exp-fail-std}{1.72}
\DefMacro{test-results-3-200-model1-lc2-num-pass-to-fail-avg}{172.33}
\DefMacro{test-results-3-200-model1-lc2-num-pass-to-fail-med}{161}
\DefMacro{test-results-3-200-model1-lc2-num-pass-to-fail-std}{19.14}
\DefMacro{test-results-3-200-model1-lc0-num-seed-fail-avg}{89.47}
\DefMacro{test-results-3-200-model1-lc0-num-seed-fail-med}{89.47}
\DefMacro{test-results-3-200-model1-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model1-lc0-num-exp-fail-avg}{78.36}
\DefMacro{test-results-3-200-model1-lc0-num-exp-fail-med}{78.19}
\DefMacro{test-results-3-200-model1-lc0-num-exp-fail-std}{0.275}
\DefMacro{test-results-3-200-model1-lc0-num-pass-to-fail-avg}{6.0}
\DefMacro{test-results-3-200-model1-lc0-num-pass-to-fail-med}{5}
\DefMacro{test-results-3-200-model1-lc0-num-pass-to-fail-std}{0.865}
\DefMacro{test-results-3-200-model1-lc1-num-seed-fail-avg}{3.33}
\DefMacro{test-results-3-200-model1-lc1-num-seed-fail-med}{3.0}
\DefMacro{test-results-3-200-model1-lc1-num-seed-fail-std}{0.29}
\DefMacro{test-results-3-200-model1-lc1-num-exp-fail-avg}{4.7}
\DefMacro{test-results-3-200-model1-lc1-num-exp-fail-med}{5.03}
\DefMacro{test-results-3-200-model1-lc1-num-exp-fail-std}{0.485}
\DefMacro{test-results-3-200-model1-lc1-num-pass-to-fail-avg}{42.67}
\DefMacro{test-results-3-200-model1-lc1-num-pass-to-fail-med}{40}
\DefMacro{test-results-3-200-model1-lc1-num-pass-to-fail-std}{11.06}
\DefMacro{test-results-3-200-model1-lc8-num-seed-fail-avg}{4.5}
\DefMacro{test-results-3-200-model1-lc8-num-seed-fail-med}{5.0}
\DefMacro{test-results-3-200-model1-lc8-num-seed-fail-std}{0.435}
\DefMacro{test-results-3-200-model1-lc8-num-exp-fail-avg}{5.33}
\DefMacro{test-results-3-200-model1-lc8-num-exp-fail-med}{4.33}
\DefMacro{test-results-3-200-model1-lc8-num-exp-fail-std}{0.96}
\DefMacro{test-results-3-200-model1-lc8-num-pass-to-fail-avg}{85.33}
\DefMacro{test-results-3-200-model1-lc8-num-pass-to-fail-med}{83}
\DefMacro{test-results-3-200-model1-lc8-num-pass-to-fail-std}{10.3}
\DefMacro{test-results-3-200-model2-lc7-num-seed-fail-avg}{29.5}
\DefMacro{test-results-3-200-model2-lc7-num-seed-fail-med}{23.0}
\DefMacro{test-results-3-200-model2-lc7-num-seed-fail-std}{7.66}
\DefMacro{test-results-3-200-model2-lc7-num-exp-fail-avg}{24.56}
\DefMacro{test-results-3-200-model2-lc7-num-exp-fail-med}{23.81}
\DefMacro{test-results-3-200-model2-lc7-num-exp-fail-std}{0.655}
\DefMacro{test-results-3-200-model2-lc7-num-pass-to-fail-avg}{166.33}
\DefMacro{test-results-3-200-model2-lc7-num-pass-to-fail-med}{197}
\DefMacro{test-results-3-200-model2-lc7-num-pass-to-fail-std}{57.555}
\DefMacro{test-results-3-200-model2-lc3-num-seed-fail-avg}{85.07}
\DefMacro{test-results-3-200-model2-lc3-num-seed-fail-med}{85.07}
\DefMacro{test-results-3-200-model2-lc3-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model2-lc3-num-exp-fail-avg}{86.41}
\DefMacro{test-results-3-200-model2-lc3-num-exp-fail-med}{86.37}
\DefMacro{test-results-3-200-model2-lc3-num-exp-fail-std}{0.16}
\DefMacro{test-results-3-200-model2-lc3-num-pass-to-fail-avg}{43.33}
\DefMacro{test-results-3-200-model2-lc3-num-pass-to-fail-med}{44}
\DefMacro{test-results-3-200-model2-lc3-num-pass-to-fail-std}{3.51}
\DefMacro{test-results-3-200-model2-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-200-model2-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-200-model2-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model2-lc4-num-exp-fail-avg}{95.72}
\DefMacro{test-results-3-200-model2-lc4-num-exp-fail-med}{95.68}
\DefMacro{test-results-3-200-model2-lc4-num-exp-fail-std}{0.085}
\DefMacro{test-results-3-200-model2-lc4-num-pass-to-fail-avg}{84.67}
\DefMacro{test-results-3-200-model2-lc4-num-pass-to-fail-med}{85}
\DefMacro{test-results-3-200-model2-lc4-num-pass-to-fail-std}{1.755}
\DefMacro{test-results-3-200-model2-lc6-num-seed-fail-avg}{88.5}
\DefMacro{test-results-3-200-model2-lc6-num-seed-fail-med}{88.5}
\DefMacro{test-results-3-200-model2-lc6-num-seed-fail-std}{3.75}
\DefMacro{test-results-3-200-model2-lc6-num-exp-fail-avg}{92.07}
\DefMacro{test-results-3-200-model2-lc6-num-exp-fail-med}{96.41}
\DefMacro{test-results-3-200-model2-lc6-num-exp-fail-std}{4.265}
\DefMacro{test-results-3-200-model2-lc6-num-pass-to-fail-avg}{45.0}
\DefMacro{test-results-3-200-model2-lc6-num-pass-to-fail-med}{36}
\DefMacro{test-results-3-200-model2-lc6-num-pass-to-fail-std}{15.74}
\DefMacro{test-results-3-200-model2-lc5-num-seed-fail-avg}{98.5}
\DefMacro{test-results-3-200-model2-lc5-num-seed-fail-med}{98.5}
\DefMacro{test-results-3-200-model2-lc5-num-seed-fail-std}{0.25}
\DefMacro{test-results-3-200-model2-lc5-num-exp-fail-avg}{98.5}
\DefMacro{test-results-3-200-model2-lc5-num-exp-fail-med}{98.92}
\DefMacro{test-results-3-200-model2-lc5-num-exp-fail-std}{0.66}
\DefMacro{test-results-3-200-model2-lc5-num-pass-to-fail-avg}{16.0}
\DefMacro{test-results-3-200-model2-lc5-num-pass-to-fail-med}{17}
\DefMacro{test-results-3-200-model2-lc5-num-pass-to-fail-std}{2.29}
\DefMacro{test-results-3-200-model2-lc9-num-seed-fail-avg}{95.67}
\DefMacro{test-results-3-200-model2-lc9-num-seed-fail-med}{96.0}
\DefMacro{test-results-3-200-model2-lc9-num-seed-fail-std}{1.26}
\DefMacro{test-results-3-200-model2-lc9-num-exp-fail-avg}{94.95}
\DefMacro{test-results-3-200-model2-lc9-num-exp-fail-med}{96.1}
\DefMacro{test-results-3-200-model2-lc9-num-exp-fail-std}{1.51}
\DefMacro{test-results-3-200-model2-lc9-num-pass-to-fail-avg}{31.33}
\DefMacro{test-results-3-200-model2-lc9-num-pass-to-fail-med}{16}
\DefMacro{test-results-3-200-model2-lc9-num-pass-to-fail-std}{18.715}
\DefMacro{test-results-3-200-model2-lc2-num-seed-fail-avg}{62.0}
\DefMacro{test-results-3-200-model2-lc2-num-seed-fail-med}{62.0}
\DefMacro{test-results-3-200-model2-lc2-num-seed-fail-std}{1.5}
\DefMacro{test-results-3-200-model2-lc2-num-exp-fail-avg}{62.25}
\DefMacro{test-results-3-200-model2-lc2-num-exp-fail-med}{62.44}
\DefMacro{test-results-3-200-model2-lc2-num-exp-fail-std}{1.95}
\DefMacro{test-results-3-200-model2-lc2-num-pass-to-fail-avg}{165.33}
\DefMacro{test-results-3-200-model2-lc2-num-pass-to-fail-med}{150}
\DefMacro{test-results-3-200-model2-lc2-num-pass-to-fail-std}{35.135}
\DefMacro{test-results-3-200-model2-lc0-num-seed-fail-avg}{100.0}
\DefMacro{test-results-3-200-model2-lc0-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-200-model2-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-200-model2-lc0-num-exp-fail-avg}{95.36}
\DefMacro{test-results-3-200-model2-lc0-num-exp-fail-med}{95.98}
\DefMacro{test-results-3-200-model2-lc0-num-exp-fail-std}{0.665}
\DefMacro{test-results-3-200-model2-lc0-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-200-model2-lc0-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-200-model2-lc0-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-200-model2-lc1-num-seed-fail-avg}{1.5}
\DefMacro{test-results-3-200-model2-lc1-num-seed-fail-med}{1.5}
\DefMacro{test-results-3-200-model2-lc1-num-seed-fail-std}{0.25}
\DefMacro{test-results-3-200-model2-lc1-num-exp-fail-avg}{4.09}
\DefMacro{test-results-3-200-model2-lc1-num-exp-fail-med}{3.94}
\DefMacro{test-results-3-200-model2-lc1-num-exp-fail-std}{0.535}
\DefMacro{test-results-3-200-model2-lc1-num-pass-to-fail-avg}{41.33}
\DefMacro{test-results-3-200-model2-lc1-num-pass-to-fail-med}{37}
\DefMacro{test-results-3-200-model2-lc1-num-pass-to-fail-std}{9.44}
\DefMacro{test-results-3-200-model2-lc8-num-seed-fail-avg}{4.5}
\DefMacro{test-results-3-200-model2-lc8-num-seed-fail-med}{5.0}
\DefMacro{test-results-3-200-model2-lc8-num-seed-fail-std}{0.435}
\DefMacro{test-results-3-200-model2-lc8-num-exp-fail-avg}{5.39}
\DefMacro{test-results-3-200-model2-lc8-num-exp-fail-med}{6.33}
\DefMacro{test-results-3-200-model2-lc8-num-exp-fail-std}{1.285}
\DefMacro{test-results-3-200-model2-lc8-num-pass-to-fail-avg}{100.0}
\DefMacro{test-results-3-200-model2-lc8-num-pass-to-fail-med}{52}
\DefMacro{test-results-3-200-model2-lc8-num-pass-to-fail-std}{47.31}

### 2022-08-29 paper/ase22/tables/test-results-3-50-numbers.tex
add new tables and figs

%% Automatically generated by pyutil.latex

\DefMacro{test-results-3-50-lc7}{Author sentiment is more important than of others}
\DefMacro{test-results-3-50-lc7-num-seeds}{50}
\DefMacro{test-results-3-50-lc7-num-exps-avg}{1564.67}
\DefMacro{test-results-3-50-lc7-num-exps-med}{1659}
\DefMacro{test-results-3-50-lc7-num-exps-std}{277.77}
\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-avg}{24.0}
\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-med}{24.0}
\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-std}{5.0}
\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-avg}{24.58}
\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-med}{21.87}
\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-std}{3.41}
\DefMacro{test-results-3-50-model0-lc7-num-pass-to-fail-avg}{46.0}
\DefMacro{test-results-3-50-model0-lc7-num-pass-to-fail-med}{51}
\DefMacro{test-results-3-50-model0-lc7-num-pass-to-fail-std}{17.88}
\DefMacro{test-results-3-50-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-3-50-lc3-num-seeds}{50}
\DefMacro{test-results-3-50-lc3-num-exps-avg}{2122.0}
\DefMacro{test-results-3-50-lc3-num-exps-med}{2073}
\DefMacro{test-results-3-50-lc3-num-exps-std}{98.56}
\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-avg}{89.33}
\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-med}{88.0}
\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-std}{1.155}
\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-avg}{90.63}
\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-med}{89.87}
\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-std}{0.705}
\DefMacro{test-results-3-50-model0-lc3-num-pass-to-fail-avg}{60.33}
\DefMacro{test-results-3-50-model0-lc3-num-pass-to-fail-med}{58}
\DefMacro{test-results-3-50-model0-lc3-num-pass-to-fail-std}{3.405}
\DefMacro{test-results-3-50-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-3-50-lc4-num-seeds}{26}
\DefMacro{test-results-3-50-lc4-num-exps-avg}{1091.67}
\DefMacro{test-results-3-50-lc4-num-exps-med}{1090}
\DefMacro{test-results-3-50-lc4-num-exps-std}{8.78}
\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-avg}{93.04}
\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-med}{93.02}
\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-std}{0.035}
\DefMacro{test-results-3-50-model0-lc4-num-pass-to-fail-avg}{62.67}
\DefMacro{test-results-3-50-model0-lc4-num-pass-to-fail-med}{61}
\DefMacro{test-results-3-50-model0-lc4-num-pass-to-fail-std}{3.33}
\DefMacro{test-results-3-50-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-3-50-lc6-num-seeds}{50}
\DefMacro{test-results-3-50-lc6-num-exps-avg}{1110.33}
\DefMacro{test-results-3-50-lc6-num-exps-med}{1137}
\DefMacro{test-results-3-50-lc6-num-exps-std}{56.69}
\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-avg}{84.67}
\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-med}{88.0}
\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-std}{3.785}
\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-avg}{88.51}
\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-med}{89.86}
\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-std}{4.55}
\DefMacro{test-results-3-50-model0-lc6-num-pass-to-fail-avg}{8.0}
\DefMacro{test-results-3-50-model0-lc6-num-pass-to-fail-med}{6}
\DefMacro{test-results-3-50-model0-lc6-num-pass-to-fail-std}{2.18}
\DefMacro{test-results-3-50-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-3-50-lc5-num-seeds}{50}
\DefMacro{test-results-3-50-lc5-num-exps-avg}{1477.0}
\DefMacro{test-results-3-50-lc5-num-exps-med}{1345}
\DefMacro{test-results-3-50-lc5-num-exps-std}{128.42}
\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-avg}{99.33}
\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-avg}{99.73}
\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-med}{99.94}
\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-std}{0.205}
\DefMacro{test-results-3-50-model0-lc5-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-50-model0-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-50-model0-lc5-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-50-lc9}{Parsing sentiment in (question, no) form}
\DefMacro{test-results-3-50-lc9-num-seeds}{50}
\DefMacro{test-results-3-50-lc9-num-exps-avg}{1494.33}
\DefMacro{test-results-3-50-lc9-num-exps-med}{1417}
\DefMacro{test-results-3-50-lc9-num-exps-std}{121.215}
\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-avg}{76.67}
\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-med}{80.0}
\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-std}{3.785}
\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-avg}{75.51}
\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-med}{79.39}
\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-std}{3.86}
\DefMacro{test-results-3-50-model0-lc9-num-pass-to-fail-avg}{38.33}
\DefMacro{test-results-3-50-model0-lc9-num-pass-to-fail-med}{27}
\DefMacro{test-results-3-50-model0-lc9-num-pass-to-fail-std}{15.78}
\DefMacro{test-results-3-50-lc2}{Sentiment change over time, present should prevail}
\DefMacro{test-results-3-50-lc2-num-seeds}{50}
\DefMacro{test-results-3-50-lc2-num-exps-avg}{1544.67}
\DefMacro{test-results-3-50-lc2-num-exps-med}{1523}
\DefMacro{test-results-3-50-lc2-num-exps-std}{34.065}
\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-avg}{14.0}
\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-med}{12.0}
\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-std}{3.605}
\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-avg}{15.77}
\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-med}{13.7}
\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-std}{5.195}
\DefMacro{test-results-3-50-model0-lc2-num-pass-to-fail-avg}{60.67}
\DefMacro{test-results-3-50-model0-lc2-num-pass-to-fail-med}{52}
\DefMacro{test-results-3-50-model0-lc2-num-pass-to-fail-std}{27.26}
\DefMacro{test-results-3-50-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-3-50-lc0-num-seeds}{19}
\DefMacro{test-results-3-50-lc0-num-exps-avg}{232.33}
\DefMacro{test-results-3-50-lc0-num-exps-med}{224}
\DefMacro{test-results-3-50-lc0-num-exps-std}{7.655}
\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-avg}{78.95}
\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-med}{78.95}
\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-avg}{87.8}
\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-med}{88.0}
\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-std}{0.36}
\DefMacro{test-results-3-50-model0-lc0-num-pass-to-fail-avg}{17.33}
\DefMacro{test-results-3-50-model0-lc0-num-pass-to-fail-med}{17}
\DefMacro{test-results-3-50-model0-lc0-num-pass-to-fail-std}{0.29}
\DefMacro{test-results-3-50-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-3-50-lc1-num-seeds}{50}
\DefMacro{test-results-3-50-lc1-num-exps-avg}{454.0}
\DefMacro{test-results-3-50-lc1-num-exps-med}{467}
\DefMacro{test-results-3-50-lc1-num-exps-std}{42.625}
\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-avg}{0.0}
\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-med}{0.0}
\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-avg}{1.38}
\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-med}{1.28}
\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-std}{0.25}
\DefMacro{test-results-3-50-model0-lc1-num-pass-to-fail-avg}{6.0}
\DefMacro{test-results-3-50-model0-lc1-num-pass-to-fail-med}{6}
\DefMacro{test-results-3-50-model0-lc1-num-pass-to-fail-std}{0.5}
\DefMacro{test-results-3-50-lc8}{Parsing sentiment in (question, yes) form}
\DefMacro{test-results-3-50-lc8-num-seeds}{50}
\DefMacro{test-results-3-50-lc8-num-exps-avg}{1330.67}
\DefMacro{test-results-3-50-lc8-num-exps-med}{1319}
\DefMacro{test-results-3-50-lc8-num-exps-std}{33.63}
\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-avg}{4.67}
\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-med}{4.0}
\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-avg}{5.87}
\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-med}{6.67}
\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-std}{1.25}
\DefMacro{test-results-3-50-model0-lc8-num-pass-to-fail-avg}{27.33}
\DefMacro{test-results-3-50-model0-lc8-num-pass-to-fail-med}{20}
\DefMacro{test-results-3-50-model0-lc8-num-pass-to-fail-std}{8.605}
\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-avg}{12.67}
\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-med}{14.0}
\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-std}{2.08}
\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-avg}{20.97}
\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-med}{15.97}
\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-std}{5.215}
\DefMacro{test-results-3-50-model1-lc7-num-pass-to-fail-avg}{59.67}
\DefMacro{test-results-3-50-model1-lc7-num-pass-to-fail-med}{47}
\DefMacro{test-results-3-50-model1-lc7-num-pass-to-fail-std}{31.48}
\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-avg}{86.0}
\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-med}{84.0}
\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-std}{1.73}
\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-avg}{88.14}
\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-med}{87.15}
\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-std}{1.31}
\DefMacro{test-results-3-50-model1-lc3-num-pass-to-fail-avg}{53.67}
\DefMacro{test-results-3-50-model1-lc3-num-pass-to-fail-med}{51}
\DefMacro{test-results-3-50-model1-lc3-num-pass-to-fail-std}{3.685}
\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-avg}{93.31}
\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-med}{93.33}
\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-std}{0.14}
\DefMacro{test-results-3-50-model1-lc4-num-pass-to-fail-avg}{40.33}
\DefMacro{test-results-3-50-model1-lc4-num-pass-to-fail-med}{41}
\DefMacro{test-results-3-50-model1-lc4-num-pass-to-fail-std}{1.53}
\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-avg}{74.67}
\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-med}{74.0}
\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-std}{3.51}
\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-avg}{73.04}
\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-med}{70.1}
\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-std}{5.935}
\DefMacro{test-results-3-50-model1-lc6-num-pass-to-fail-avg}{30.33}
\DefMacro{test-results-3-50-model1-lc6-num-pass-to-fail-med}{26}
\DefMacro{test-results-3-50-model1-lc6-num-pass-to-fail-std}{14.375}
\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-avg}{99.33}
\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-avg}{99.4}
\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-med}{99.26}
\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-std}{0.2}
\DefMacro{test-results-3-50-model1-lc5-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-50-model1-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-50-model1-lc5-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-avg}{78.0}
\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-med}{78.0}
\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-std}{5.0}
\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-avg}{78.77}
\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-med}{82.92}
\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-std}{5.985}
\DefMacro{test-results-3-50-model1-lc9-num-pass-to-fail-avg}{20.0}
\DefMacro{test-results-3-50-model1-lc9-num-pass-to-fail-med}{13}
\DefMacro{test-results-3-50-model1-lc9-num-pass-to-fail-std}{10.21}
\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-avg}{52.0}
\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-med}{50.0}
\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-std}{1.73}
\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-avg}{46.53}
\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-med}{43.06}
\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-std}{4.615}
\DefMacro{test-results-3-50-model1-lc2-num-pass-to-fail-avg}{37.0}
\DefMacro{test-results-3-50-model1-lc2-num-pass-to-fail-med}{31}
\DefMacro{test-results-3-50-model1-lc2-num-pass-to-fail-std}{8.41}
\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-avg}{89.47}
\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-med}{89.47}
\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-avg}{78.7}
\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-med}{78.12}
\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-std}{0.75}
\DefMacro{test-results-3-50-model1-lc0-num-pass-to-fail-avg}{9.33}
\DefMacro{test-results-3-50-model1-lc0-num-pass-to-fail-med}{9}
\DefMacro{test-results-3-50-model1-lc0-num-pass-to-fail-std}{0.29}
\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-avg}{2.67}
\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-med}{2.0}
\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-avg}{2.8}
\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-med}{0.94}
\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-std}{1.66}
\DefMacro{test-results-3-50-model1-lc1-num-pass-to-fail-avg}{12.0}
\DefMacro{test-results-3-50-model1-lc1-num-pass-to-fail-med}{3}
\DefMacro{test-results-3-50-model1-lc1-num-pass-to-fail-std}{8.23}
\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-avg}{5.33}
\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-med}{6.0}
\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-std}{1.53}
\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-avg}{5.85}
\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-med}{6.14}
\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-std}{0.93}
\DefMacro{test-results-3-50-model1-lc8-num-pass-to-fail-avg}{25.67}
\DefMacro{test-results-3-50-model1-lc8-num-pass-to-fail-med}{27}
\DefMacro{test-results-3-50-model1-lc8-num-pass-to-fail-std}{5.53}
\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-avg}{32.0}
\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-med}{24.0}
\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-std}{10.585}
\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-avg}{31.45}
\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-med}{33.91}
\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-std}{5.245}
\DefMacro{test-results-3-50-model2-lc7-num-pass-to-fail-avg}{50.67}
\DefMacro{test-results-3-50-model2-lc7-num-pass-to-fail-med}{49}
\DefMacro{test-results-3-50-model2-lc7-num-pass-to-fail-std}{15.765}
\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-avg}{83.33}
\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-med}{84.0}
\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-avg}{85.71}
\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-med}{86.11}
\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-std}{0.64}
\DefMacro{test-results-3-50-model2-lc3-num-pass-to-fail-avg}{33.67}
\DefMacro{test-results-3-50-model2-lc3-num-pass-to-fail-med}{34}
\DefMacro{test-results-3-50-model2-lc3-num-pass-to-fail-std}{2.255}
\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-avg}{95.66}
\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-med}{95.41}
\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-std}{0.25}
\DefMacro{test-results-3-50-model2-lc4-num-pass-to-fail-avg}{84.0}
\DefMacro{test-results-3-50-model2-lc4-num-pass-to-fail-med}{83}
\DefMacro{test-results-3-50-model2-lc4-num-pass-to-fail-std}{2.29}
\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-avg}{87.33}
\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-med}{88.0}
\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-std}{3.51}
\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-avg}{91.1}
\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-med}{92.9}
\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-std}{4.19}
\DefMacro{test-results-3-50-model2-lc6-num-pass-to-fail-avg}{4.33}
\DefMacro{test-results-3-50-model2-lc6-num-pass-to-fail-med}{4}
\DefMacro{test-results-3-50-model2-lc6-num-pass-to-fail-std}{1.26}
\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-avg}{98.67}
\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-med}{98.0}
\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-avg}{98.44}
\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-med}{99.11}
\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-std}{0.99}
\DefMacro{test-results-3-50-model2-lc5-num-pass-to-fail-avg}{1.33}
\DefMacro{test-results-3-50-model2-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-50-model2-lc5-num-pass-to-fail-std}{1.155}
\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-avg}{80.67}
\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-med}{84.0}
\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-std}{9.61}
\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-avg}{78.54}
\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-med}{82.31}
\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-std}{11.03}
\DefMacro{test-results-3-50-model2-lc9-num-pass-to-fail-avg}{13.0}
\DefMacro{test-results-3-50-model2-lc9-num-pass-to-fail-med}{4}
\DefMacro{test-results-3-50-model2-lc9-num-pass-to-fail-std}{7.795}
\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-avg}{54.67}
\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-med}{58.0}
\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-std}{2.885}
\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-avg}{55.97}
\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-med}{60.67}
\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-std}{4.6}
\DefMacro{test-results-3-50-model2-lc2-num-pass-to-fail-avg}{49.33}
\DefMacro{test-results-3-50-model2-lc2-num-pass-to-fail-med}{60}
\DefMacro{test-results-3-50-model2-lc2-num-pass-to-fail-std}{11.015}
\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-avg}{100.0}
\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-avg}{95.8}
\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-med}{95.96}
\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-std}{0.545}
\DefMacro{test-results-3-50-model2-lc0-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-50-model2-lc0-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-50-model2-lc0-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-avg}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-med}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-avg}{0.92}
\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-med}{0.94}
\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-std}{0.24}
\DefMacro{test-results-3-50-model2-lc1-num-pass-to-fail-avg}{4.0}
\DefMacro{test-results-3-50-model2-lc1-num-pass-to-fail-med}{5}
\DefMacro{test-results-3-50-model2-lc1-num-pass-to-fail-std}{0.865}
\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-avg}{5.33}
\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-med}{6.0}
\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-std}{0.575}
\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-avg}{6.76}
\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-med}{6.07}
\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-std}{1.515}
\DefMacro{test-results-3-50-model2-lc8-num-pass-to-fail-avg}{25.33}
\DefMacro{test-results-3-50-model2-lc8-num-pass-to-fail-med}{13}
\DefMacro{test-results-3-50-model2-lc8-num-pass-to-fail-std}{12.005}

### 2022-08-29 paper/icse23/related.tex
add icse

\vspace{-6pt}
\section{Related Work}

\MyPara{NLP Testing}
%
With the increasing use of NLP models, evaluation of NLP models is
becoming a more important issue. Apart from the accuracy-based testing
scheme, recent works have considered model robustness as an
aspect for evaluation. Belinkov and Bisk
\textit{\etal}~\cite{belinkov2018breaknmt} aimed to fail neural machine
translation model by intentionally introducing noise in the input
text. Pinjia
\textit{\etal}~\cite{pinjia2020structinvtestingnmt,pinjia2020testnmtrt}
measured the robustness by assuming syntactic and semantic relation
between input and output of neural machine translation model.  Ribeiro
\textit{\etal}~\cite{ribeiro2018sear} proposed an approach to
generalize semantically equivalent adversarial rules. In addition,
Rychalska \textit{\etal}~\cite{rychalska2019wildnlp} measured drops in
BLEU scores by corruption operation, and compared model robustness
based on the amount of the drops. Iyyer
\textit{\etal}~\cite{iyyer2018adversarial} introduced learning-based
model for adversarial data augmentation.

In addition to the
robustness on adversarial set, various other aspects of the NLP model have been
considered for the robustness evaluation. Prabhakaran
\textit{\etal}~\cite{prabhakaran2019fairness} developed an evaluation
framework to detect unintended societal bias in NLP models. Rottger
\textit{\etal}~\cite{rottger2020hatecheck} introduced a functional
test suite for hate speech detection in the NLP model.  Ribeiro
\textit{\etal}~\cite{ribeiro2019consistencyeval} measured logical
consistency of NLP model. These techniques evaluate the robustness of
the NLP model. However, we focused on the evaluation of model capability
over multiple perspectives and produce debugging information by comparing
seed and expanded test cases.

\MyPara{Linguistic Capability Evaluation}
%
Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} proposed
multiple diagnostic datasets to evaluate NLP models. These datasets
evaluate NLP model's ability to understand input sentence via natural
language inference problems. More recently, \Cklst proposed an evaluation
method of input-output behavior defined as \lcs. \Cklst generates
behavior-guided inputs for validating the
behaviors.~\cite{marcoACL2020checklist}. Unlike prior work that relies on manual
test case generation, we used structural information in text to
generate test cases automatically.

\MyPara{NLP Model Debugging}
%
Researchers have been explaining NLP model prediction and
analyzing it for debugging the model. Ribeiro
\textit{\etal}~\cite{ribeiroSG16lime} evaluated model prediction guided by human feedback providing relevance scores for words on the model prediction. 
Interactive error analysis~\cite{wu2019errudite} also has been proposed to evaluate
model robustness. Zylberajch~\cite{zylberajch2021hildif} used influence functions to generate model explanation, and it enables interactive debugging incorporating humans feedback
explanation.
Lertvittaya~\cite{lertvittayakumjorn2020find} proposed
an approach to understand behavior of text classifier model and improve the
model by disabling irrelevant hidden features. In this work, \tool
is useful for identifying the sources of model failure as shown in RQ4.

### 2022-08-29 paper/icse23/tables/test-results-3-100-numbers.tex
add icse

%% Automatically generated by pyutil.latex

\DefMacro{test-results-3-100-lc7}{Author sentiment is more important than of others}
\DefMacro{test-results-3-100-lc7-num-seeds}{100}
\DefMacro{test-results-3-100-lc7-num-exps-avg}{3426.33}
\DefMacro{test-results-3-100-lc7-num-exps-med}{3435}
\DefMacro{test-results-3-100-lc7-num-exps-std}{361.02}
\DefMacro{test-results-3-100-model0-lc7-num-seed-fail-avg}{26.0}
\DefMacro{test-results-3-100-model0-lc7-num-seed-fail-med}{23.0}
\DefMacro{test-results-3-100-model0-lc7-num-seed-fail-std}{5.895}
\DefMacro{test-results-3-100-model0-lc7-num-exp-fail-avg}{25.68}
\DefMacro{test-results-3-100-model0-lc7-num-exp-fail-med}{22.15}
\DefMacro{test-results-3-100-model0-lc7-num-exp-fail-std}{3.105}
\DefMacro{test-results-3-100-model0-lc7-num-pass-to-fail-avg}{88.33}
\DefMacro{test-results-3-100-model0-lc7-num-pass-to-fail-med}{107}
\DefMacro{test-results-3-100-model0-lc7-num-pass-to-fail-std}{25.8}
\DefMacro{test-results-3-100-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-3-100-lc3-num-seeds}{67}
\DefMacro{test-results-3-100-lc3-num-exps-avg}{2860.67}
\DefMacro{test-results-3-100-lc3-num-exps-med}{2868}
\DefMacro{test-results-3-100-lc3-num-exps-std}{19.755}
\DefMacro{test-results-3-100-model0-lc3-num-seed-fail-avg}{89.55}
\DefMacro{test-results-3-100-model0-lc3-num-seed-fail-med}{89.55}
\DefMacro{test-results-3-100-model0-lc3-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model0-lc3-num-exp-fail-avg}{91.64}
\DefMacro{test-results-3-100-model0-lc3-num-exp-fail-med}{91.73}
\DefMacro{test-results-3-100-model0-lc3-num-exp-fail-std}{0.185}
\DefMacro{test-results-3-100-model0-lc3-num-pass-to-fail-avg}{77.67}
\DefMacro{test-results-3-100-model0-lc3-num-pass-to-fail-med}{79}
\DefMacro{test-results-3-100-model0-lc3-num-pass-to-fail-std}{1.605}
\DefMacro{test-results-3-100-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-3-100-lc4-num-seeds}{26}
\DefMacro{test-results-3-100-lc4-num-exps-avg}{1086.0}
\DefMacro{test-results-3-100-lc4-num-exps-med}{1090}
\DefMacro{test-results-3-100-lc4-num-exps-std}{3.905}
\DefMacro{test-results-3-100-model0-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-100-model0-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-100-model0-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model0-lc4-num-exp-fail-avg}{92.91}
\DefMacro{test-results-3-100-model0-lc4-num-exp-fail-med}{93.13}
\DefMacro{test-results-3-100-model0-lc4-num-exp-fail-std}{0.355}
\DefMacro{test-results-3-100-model0-lc4-num-pass-to-fail-avg}{63.33}
\DefMacro{test-results-3-100-model0-lc4-num-pass-to-fail-med}{65}
\DefMacro{test-results-3-100-model0-lc4-num-pass-to-fail-std}{1.445}
\DefMacro{test-results-3-100-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-3-100-lc6-num-seeds}{100}
\DefMacro{test-results-3-100-lc6-num-exps-avg}{2312.0}
\DefMacro{test-results-3-100-lc6-num-exps-med}{2296}
\DefMacro{test-results-3-100-lc6-num-exps-std}{53.945}
\DefMacro{test-results-3-100-model0-lc6-num-seed-fail-avg}{86.33}
\DefMacro{test-results-3-100-model0-lc6-num-seed-fail-med}{87.0}
\DefMacro{test-results-3-100-model0-lc6-num-seed-fail-std}{3.51}
\DefMacro{test-results-3-100-model0-lc6-num-exp-fail-avg}{91.58}
\DefMacro{test-results-3-100-model0-lc6-num-exp-fail-med}{94.64}
\DefMacro{test-results-3-100-model0-lc6-num-exp-fail-std}{3.155}
\DefMacro{test-results-3-100-model0-lc6-num-pass-to-fail-avg}{25.67}
\DefMacro{test-results-3-100-model0-lc6-num-pass-to-fail-med}{26}
\DefMacro{test-results-3-100-model0-lc6-num-pass-to-fail-std}{10.25}
\DefMacro{test-results-3-100-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-3-100-lc5-num-seeds}{100}
\DefMacro{test-results-3-100-lc5-num-exps-avg}{2845.0}
\DefMacro{test-results-3-100-lc5-num-exps-med}{2713}
\DefMacro{test-results-3-100-lc5-num-exps-std}{133.37}
\DefMacro{test-results-3-100-model0-lc5-num-seed-fail-avg}{99.33}
\DefMacro{test-results-3-100-model0-lc5-num-seed-fail-med}{99.0}
\DefMacro{test-results-3-100-model0-lc5-num-seed-fail-std}{0.29}
\DefMacro{test-results-3-100-model0-lc5-num-exp-fail-avg}{99.63}
\DefMacro{test-results-3-100-model0-lc5-num-exp-fail-med}{99.67}
\DefMacro{test-results-3-100-model0-lc5-num-exp-fail-std}{0.165}
\DefMacro{test-results-3-100-model0-lc5-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-100-model0-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-100-model0-lc5-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-100-lc9}{Parsing sentiment in (question, no) form}
\DefMacro{test-results-3-100-lc9-num-seeds}{100}
\DefMacro{test-results-3-100-lc9-num-exps-avg}{2830.33}
\DefMacro{test-results-3-100-lc9-num-exps-med}{2607}
\DefMacro{test-results-3-100-lc9-num-exps-std}{221.255}
\DefMacro{test-results-3-100-model0-lc9-num-seed-fail-avg}{74.33}
\DefMacro{test-results-3-100-model0-lc9-num-seed-fail-med}{76.0}
\DefMacro{test-results-3-100-model0-lc9-num-seed-fail-std}{2.845}
\DefMacro{test-results-3-100-model0-lc9-num-exp-fail-avg}{72.26}
\DefMacro{test-results-3-100-model0-lc9-num-exp-fail-med}{71.66}
\DefMacro{test-results-3-100-model0-lc9-num-exp-fail-std}{1.795}
\DefMacro{test-results-3-100-model0-lc9-num-pass-to-fail-avg}{66.0}
\DefMacro{test-results-3-100-model0-lc9-num-pass-to-fail-med}{56}
\DefMacro{test-results-3-100-model0-lc9-num-pass-to-fail-std}{10.44}
\DefMacro{test-results-3-100-lc2}{Sentiment change over time, present should prevail}
\DefMacro{test-results-3-100-lc2-num-seeds}{100}
\DefMacro{test-results-3-100-lc2-num-exps-avg}{3097.33}
\DefMacro{test-results-3-100-lc2-num-exps-med}{3151}
\DefMacro{test-results-3-100-lc2-num-exps-std}{60.86}
\DefMacro{test-results-3-100-model0-lc2-num-seed-fail-avg}{20.0}
\DefMacro{test-results-3-100-model0-lc2-num-seed-fail-med}{18.0}
\DefMacro{test-results-3-100-model0-lc2-num-seed-fail-std}{2.18}
\DefMacro{test-results-3-100-model0-lc2-num-exp-fail-avg}{19.77}
\DefMacro{test-results-3-100-model0-lc2-num-exp-fail-med}{20.11}
\DefMacro{test-results-3-100-model0-lc2-num-exp-fail-std}{3.26}
\DefMacro{test-results-3-100-model0-lc2-num-pass-to-fail-avg}{96.33}
\DefMacro{test-results-3-100-model0-lc2-num-pass-to-fail-med}{80}
\DefMacro{test-results-3-100-model0-lc2-num-pass-to-fail-std}{23.825}
\DefMacro{test-results-3-100-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-3-100-lc0-num-seeds}{19}
\DefMacro{test-results-3-100-lc0-num-exps-avg}{234.33}
\DefMacro{test-results-3-100-lc0-num-exps-med}{239}
\DefMacro{test-results-3-100-lc0-num-exps-std}{5.395}
\DefMacro{test-results-3-100-model0-lc0-num-seed-fail-avg}{78.95}
\DefMacro{test-results-3-100-model0-lc0-num-seed-fail-med}{78.95}
\DefMacro{test-results-3-100-model0-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model0-lc0-num-exp-fail-avg}{88.79}
\DefMacro{test-results-3-100-model0-lc0-num-exp-fail-med}{88.7}
\DefMacro{test-results-3-100-model0-lc0-num-exp-fail-std}{0.405}
\DefMacro{test-results-3-100-model0-lc0-num-pass-to-fail-avg}{18.67}
\DefMacro{test-results-3-100-model0-lc0-num-pass-to-fail-med}{19}
\DefMacro{test-results-3-100-model0-lc0-num-pass-to-fail-std}{0.765}
\DefMacro{test-results-3-100-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-3-100-lc1-num-seeds}{100}
\DefMacro{test-results-3-100-lc1-num-exps-avg}{973.33}
\DefMacro{test-results-3-100-lc1-num-exps-med}{969}
\DefMacro{test-results-3-100-lc1-num-exps-std}{8.95}
\DefMacro{test-results-3-100-model0-lc1-num-seed-fail-avg}{1.67}
\DefMacro{test-results-3-100-model0-lc1-num-seed-fail-med}{2.0}
\DefMacro{test-results-3-100-model0-lc1-num-seed-fail-std}{0.29}
\DefMacro{test-results-3-100-model0-lc1-num-exp-fail-avg}{3.72}
\DefMacro{test-results-3-100-model0-lc1-num-exp-fail-med}{4.53}
\DefMacro{test-results-3-100-model0-lc1-num-exp-fail-std}{0.705}
\DefMacro{test-results-3-100-model0-lc1-num-pass-to-fail-avg}{11.67}
\DefMacro{test-results-3-100-model0-lc1-num-pass-to-fail-med}{12}
\DefMacro{test-results-3-100-model0-lc1-num-pass-to-fail-std}{4.75}
\DefMacro{test-results-3-100-lc8}{Parsing sentiment in (question, yes) form}
\DefMacro{test-results-3-100-lc8-num-seeds}{100}
\DefMacro{test-results-3-100-lc8-num-exps-avg}{2749.0}
\DefMacro{test-results-3-100-lc8-num-exps-med}{2755}
\DefMacro{test-results-3-100-lc8-num-exps-std}{44.575}
\DefMacro{test-results-3-100-model0-lc8-num-seed-fail-avg}{5.33}
\DefMacro{test-results-3-100-model0-lc8-num-seed-fail-med}{6.0}
\DefMacro{test-results-3-100-model0-lc8-num-seed-fail-std}{1.04}
\DefMacro{test-results-3-100-model0-lc8-num-exp-fail-avg}{4.93}
\DefMacro{test-results-3-100-model0-lc8-num-exp-fail-med}{4.93}
\DefMacro{test-results-3-100-model0-lc8-num-exp-fail-std}{0.44}
\DefMacro{test-results-3-100-model0-lc8-num-pass-to-fail-avg}{39.0}
\DefMacro{test-results-3-100-model0-lc8-num-pass-to-fail-med}{39}
\DefMacro{test-results-3-100-model0-lc8-num-pass-to-fail-std}{6.0}
\DefMacro{test-results-3-100-model1-lc7-num-seed-fail-avg}{13.33}
\DefMacro{test-results-3-100-model1-lc7-num-seed-fail-med}{11.0}
\DefMacro{test-results-3-100-model1-lc7-num-seed-fail-std}{3.405}
\DefMacro{test-results-3-100-model1-lc7-num-exp-fail-avg}{15.6}
\DefMacro{test-results-3-100-model1-lc7-num-exp-fail-med}{14.38}
\DefMacro{test-results-3-100-model1-lc7-num-exp-fail-std}{1.825}
\DefMacro{test-results-3-100-model1-lc7-num-pass-to-fail-avg}{121.33}
\DefMacro{test-results-3-100-model1-lc7-num-pass-to-fail-med}{148}
\DefMacro{test-results-3-100-model1-lc7-num-pass-to-fail-std}{43.075}
\DefMacro{test-results-3-100-model1-lc3-num-seed-fail-avg}{85.07}
\DefMacro{test-results-3-100-model1-lc3-num-seed-fail-med}{85.07}
\DefMacro{test-results-3-100-model1-lc3-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model1-lc3-num-exp-fail-avg}{88.99}
\DefMacro{test-results-3-100-model1-lc3-num-exp-fail-med}{88.72}
\DefMacro{test-results-3-100-model1-lc3-num-exp-fail-std}{0.335}
\DefMacro{test-results-3-100-model1-lc3-num-pass-to-fail-avg}{62.67}
\DefMacro{test-results-3-100-model1-lc3-num-pass-to-fail-med}{63}
\DefMacro{test-results-3-100-model1-lc3-num-pass-to-fail-std}{1.26}
\DefMacro{test-results-3-100-model1-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-100-model1-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-100-model1-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model1-lc4-num-exp-fail-avg}{93.55}
\DefMacro{test-results-3-100-model1-lc4-num-exp-fail-med}{93.41}
\DefMacro{test-results-3-100-model1-lc4-num-exp-fail-std}{0.305}
\DefMacro{test-results-3-100-model1-lc4-num-pass-to-fail-avg}{42.67}
\DefMacro{test-results-3-100-model1-lc4-num-pass-to-fail-med}{43}
\DefMacro{test-results-3-100-model1-lc4-num-pass-to-fail-std}{0.765}
\DefMacro{test-results-3-100-model1-lc6-num-seed-fail-avg}{73.0}
\DefMacro{test-results-3-100-model1-lc6-num-seed-fail-med}{69.0}
\DefMacro{test-results-3-100-model1-lc6-num-seed-fail-std}{4.36}
\DefMacro{test-results-3-100-model1-lc6-num-exp-fail-avg}{76.17}
\DefMacro{test-results-3-100-model1-lc6-num-exp-fail-med}{75.28}
\DefMacro{test-results-3-100-model1-lc6-num-exp-fail-std}{5.525}
\DefMacro{test-results-3-100-model1-lc6-num-pass-to-fail-avg}{58.0}
\DefMacro{test-results-3-100-model1-lc6-num-pass-to-fail-med}{42}
\DefMacro{test-results-3-100-model1-lc6-num-pass-to-fail-std}{14.73}
\DefMacro{test-results-3-100-model1-lc5-num-seed-fail-avg}{99.33}
\DefMacro{test-results-3-100-model1-lc5-num-seed-fail-med}{99.0}
\DefMacro{test-results-3-100-model1-lc5-num-seed-fail-std}{0.29}
\DefMacro{test-results-3-100-model1-lc5-num-exp-fail-avg}{99.56}
\DefMacro{test-results-3-100-model1-lc5-num-exp-fail-med}{99.55}
\DefMacro{test-results-3-100-model1-lc5-num-exp-fail-std}{0.07}
\DefMacro{test-results-3-100-model1-lc5-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-100-model1-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-100-model1-lc5-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-100-model1-lc9-num-seed-fail-avg}{86.33}
\DefMacro{test-results-3-100-model1-lc9-num-seed-fail-med}{89.0}
\DefMacro{test-results-3-100-model1-lc9-num-seed-fail-std}{2.755}
\DefMacro{test-results-3-100-model1-lc9-num-exp-fail-avg}{87.16}
\DefMacro{test-results-3-100-model1-lc9-num-exp-fail-med}{86.91}
\DefMacro{test-results-3-100-model1-lc9-num-exp-fail-std}{1.285}
\DefMacro{test-results-3-100-model1-lc9-num-pass-to-fail-avg}{24.67}
\DefMacro{test-results-3-100-model1-lc9-num-pass-to-fail-med}{24}
\DefMacro{test-results-3-100-model1-lc9-num-pass-to-fail-std}{8.505}
\DefMacro{test-results-3-100-model1-lc2-num-seed-fail-avg}{50.33}
\DefMacro{test-results-3-100-model1-lc2-num-seed-fail-med}{52.0}
\DefMacro{test-results-3-100-model1-lc2-num-seed-fail-std}{2.845}
\DefMacro{test-results-3-100-model1-lc2-num-exp-fail-avg}{46.15}
\DefMacro{test-results-3-100-model1-lc2-num-exp-fail-med}{46.32}
\DefMacro{test-results-3-100-model1-lc2-num-exp-fail-std}{1.565}
\DefMacro{test-results-3-100-model1-lc2-num-pass-to-fail-avg}{78.33}
\DefMacro{test-results-3-100-model1-lc2-num-pass-to-fail-med}{76}
\DefMacro{test-results-3-100-model1-lc2-num-pass-to-fail-std}{17.28}
\DefMacro{test-results-3-100-model1-lc0-num-seed-fail-avg}{89.47}
\DefMacro{test-results-3-100-model1-lc0-num-seed-fail-med}{89.47}
\DefMacro{test-results-3-100-model1-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model1-lc0-num-exp-fail-avg}{78.95}
\DefMacro{test-results-3-100-model1-lc0-num-exp-fail-med}{78.83}
\DefMacro{test-results-3-100-model1-lc0-num-exp-fail-std}{0.665}
\DefMacro{test-results-3-100-model1-lc0-num-pass-to-fail-avg}{6.0}
\DefMacro{test-results-3-100-model1-lc0-num-pass-to-fail-med}{6}
\DefMacro{test-results-3-100-model1-lc0-num-pass-to-fail-std}{0.5}
\DefMacro{test-results-3-100-model1-lc1-num-seed-fail-avg}{2.67}
\DefMacro{test-results-3-100-model1-lc1-num-seed-fail-med}{3.0}
\DefMacro{test-results-3-100-model1-lc1-num-seed-fail-std}{0.29}
\DefMacro{test-results-3-100-model1-lc1-num-exp-fail-avg}{3.66}
\DefMacro{test-results-3-100-model1-lc1-num-exp-fail-med}{3.76}
\DefMacro{test-results-3-100-model1-lc1-num-exp-fail-std}{0.31}
\DefMacro{test-results-3-100-model1-lc1-num-pass-to-fail-avg}{14.0}
\DefMacro{test-results-3-100-model1-lc1-num-pass-to-fail-med}{5}
\DefMacro{test-results-3-100-model1-lc1-num-pass-to-fail-std}{8.23}
\DefMacro{test-results-3-100-model1-lc8-num-seed-fail-avg}{5.0}
\DefMacro{test-results-3-100-model1-lc8-num-seed-fail-med}{5.0}
\DefMacro{test-results-3-100-model1-lc8-num-seed-fail-std}{0.5}
\DefMacro{test-results-3-100-model1-lc8-num-exp-fail-avg}{4.73}
\DefMacro{test-results-3-100-model1-lc8-num-exp-fail-med}{5.08}
\DefMacro{test-results-3-100-model1-lc8-num-exp-fail-std}{0.62}
\DefMacro{test-results-3-100-model1-lc8-num-pass-to-fail-avg}{42.67}
\DefMacro{test-results-3-100-model1-lc8-num-pass-to-fail-med}{49}
\DefMacro{test-results-3-100-model1-lc8-num-pass-to-fail-std}{8.22}
\DefMacro{test-results-3-100-model2-lc7-num-seed-fail-avg}{30.67}
\DefMacro{test-results-3-100-model2-lc7-num-seed-fail-med}{25.0}
\DefMacro{test-results-3-100-model2-lc7-num-seed-fail-std}{9.09}
\DefMacro{test-results-3-100-model2-lc7-num-exp-fail-avg}{26.16}
\DefMacro{test-results-3-100-model2-lc7-num-exp-fail-med}{28.7}
\DefMacro{test-results-3-100-model2-lc7-num-exp-fail-std}{2.495}
\DefMacro{test-results-3-100-model2-lc7-num-pass-to-fail-avg}{74.67}
\DefMacro{test-results-3-100-model2-lc7-num-pass-to-fail-med}{91}
\DefMacro{test-results-3-100-model2-lc7-num-pass-to-fail-std}{22.395}
\DefMacro{test-results-3-100-model2-lc3-num-seed-fail-avg}{85.07}
\DefMacro{test-results-3-100-model2-lc3-num-seed-fail-med}{85.07}
\DefMacro{test-results-3-100-model2-lc3-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model2-lc3-num-exp-fail-avg}{86.56}
\DefMacro{test-results-3-100-model2-lc3-num-exp-fail-med}{86.65}
\DefMacro{test-results-3-100-model2-lc3-num-exp-fail-std}{0.135}
\DefMacro{test-results-3-100-model2-lc3-num-pass-to-fail-avg}{40.33}
\DefMacro{test-results-3-100-model2-lc3-num-pass-to-fail-med}{40}
\DefMacro{test-results-3-100-model2-lc3-num-pass-to-fail-std}{3.255}
\DefMacro{test-results-3-100-model2-lc4-num-seed-fail-avg}{92.31}
\DefMacro{test-results-3-100-model2-lc4-num-seed-fail-med}{92.31}
\DefMacro{test-results-3-100-model2-lc4-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model2-lc4-num-exp-fail-avg}{95.43}
\DefMacro{test-results-3-100-model2-lc4-num-exp-fail-med}{95.26}
\DefMacro{test-results-3-100-model2-lc4-num-exp-fail-std}{0.24}
\DefMacro{test-results-3-100-model2-lc4-num-pass-to-fail-avg}{79.33}
\DefMacro{test-results-3-100-model2-lc4-num-pass-to-fail-med}{82}
\DefMacro{test-results-3-100-model2-lc4-num-pass-to-fail-std}{2.755}
\DefMacro{test-results-3-100-model2-lc6-num-seed-fail-avg}{87.33}
\DefMacro{test-results-3-100-model2-lc6-num-seed-fail-med}{86.0}
\DefMacro{test-results-3-100-model2-lc6-num-seed-fail-std}{3.055}
\DefMacro{test-results-3-100-model2-lc6-num-exp-fail-avg}{91.33}
\DefMacro{test-results-3-100-model2-lc6-num-exp-fail-med}{94.68}
\DefMacro{test-results-3-100-model2-lc6-num-exp-fail-std}{3.585}
\DefMacro{test-results-3-100-model2-lc6-num-pass-to-fail-avg}{11.0}
\DefMacro{test-results-3-100-model2-lc6-num-pass-to-fail-med}{9}
\DefMacro{test-results-3-100-model2-lc6-num-pass-to-fail-std}{3.605}
\DefMacro{test-results-3-100-model2-lc5-num-seed-fail-avg}{98.67}
\DefMacro{test-results-3-100-model2-lc5-num-seed-fail-med}{99.0}
\DefMacro{test-results-3-100-model2-lc5-num-seed-fail-std}{0.765}
\DefMacro{test-results-3-100-model2-lc5-num-exp-fail-avg}{98.42}
\DefMacro{test-results-3-100-model2-lc5-num-exp-fail-med}{98.99}
\DefMacro{test-results-3-100-model2-lc5-num-exp-fail-std}{0.77}
\DefMacro{test-results-3-100-model2-lc5-num-pass-to-fail-avg}{1.0}
\DefMacro{test-results-3-100-model2-lc5-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-100-model2-lc5-num-pass-to-fail-std}{0.865}
\DefMacro{test-results-3-100-model2-lc9-num-seed-fail-avg}{94.67}
\DefMacro{test-results-3-100-model2-lc9-num-seed-fail-med}{97.0}
\DefMacro{test-results-3-100-model2-lc9-num-seed-fail-std}{2.465}
\DefMacro{test-results-3-100-model2-lc9-num-exp-fail-avg}{94.43}
\DefMacro{test-results-3-100-model2-lc9-num-exp-fail-med}{96.41}
\DefMacro{test-results-3-100-model2-lc9-num-exp-fail-std}{2.69}
\DefMacro{test-results-3-100-model2-lc9-num-pass-to-fail-avg}{17.33}
\DefMacro{test-results-3-100-model2-lc9-num-pass-to-fail-med}{4}
\DefMacro{test-results-3-100-model2-lc9-num-pass-to-fail-std}{12.425}
\DefMacro{test-results-3-100-model2-lc2-num-seed-fail-avg}{58.67}
\DefMacro{test-results-3-100-model2-lc2-num-seed-fail-med}{58.0}
\DefMacro{test-results-3-100-model2-lc2-num-seed-fail-std}{3.015}
\DefMacro{test-results-3-100-model2-lc2-num-exp-fail-avg}{60.14}
\DefMacro{test-results-3-100-model2-lc2-num-exp-fail-med}{62.11}
\DefMacro{test-results-3-100-model2-lc2-num-exp-fail-std}{2.64}
\DefMacro{test-results-3-100-model2-lc2-num-pass-to-fail-avg}{79.33}
\DefMacro{test-results-3-100-model2-lc2-num-pass-to-fail-med}{82}
\DefMacro{test-results-3-100-model2-lc2-num-pass-to-fail-std}{9.075}
\DefMacro{test-results-3-100-model2-lc0-num-seed-fail-avg}{100.0}
\DefMacro{test-results-3-100-model2-lc0-num-seed-fail-med}{100.0}
\DefMacro{test-results-3-100-model2-lc0-num-seed-fail-std}{0.0}
\DefMacro{test-results-3-100-model2-lc0-num-exp-fail-avg}{95.75}
\DefMacro{test-results-3-100-model2-lc0-num-exp-fail-med}{95.82}
\DefMacro{test-results-3-100-model2-lc0-num-exp-fail-std}{0.34}
\DefMacro{test-results-3-100-model2-lc0-num-pass-to-fail-avg}{0.0}
\DefMacro{test-results-3-100-model2-lc0-num-pass-to-fail-med}{0}
\DefMacro{test-results-3-100-model2-lc0-num-pass-to-fail-std}{0.0}
\DefMacro{test-results-3-100-model2-lc1-num-seed-fail-avg}{1.33}
\DefMacro{test-results-3-100-model2-lc1-num-seed-fail-med}{1.0}
\DefMacro{test-results-3-100-model2-lc1-num-seed-fail-std}{0.29}
\DefMacro{test-results-3-100-model2-lc1-num-exp-fail-avg}{2.61}
\DefMacro{test-results-3-100-model2-lc1-num-exp-fail-med}{1.96}
\DefMacro{test-results-3-100-model2-lc1-num-exp-fail-std}{0.99}
\DefMacro{test-results-3-100-model2-lc1-num-pass-to-fail-avg}{8.0}
\DefMacro{test-results-3-100-model2-lc1-num-pass-to-fail-med}{8}
\DefMacro{test-results-3-100-model2-lc1-num-pass-to-fail-std}{1.5}
\DefMacro{test-results-3-100-model2-lc8-num-seed-fail-avg}{5.0}
\DefMacro{test-results-3-100-model2-lc8-num-seed-fail-med}{5.0}
\DefMacro{test-results-3-100-model2-lc8-num-seed-fail-std}{0.5}
\DefMacro{test-results-3-100-model2-lc8-num-exp-fail-avg}{5.97}
\DefMacro{test-results-3-100-model2-lc8-num-exp-fail-med}{5.01}
\DefMacro{test-results-3-100-model2-lc8-num-exp-fail-std}{0.935}
\DefMacro{test-results-3-100-model2-lc8-num-pass-to-fail-avg}{38.67}
\DefMacro{test-results-3-100-model2-lc8-num-pass-to-fail-med}{32}
\DefMacro{test-results-3-100-model2-lc8-num-pass-to-fail-std}{12.34}

### 2022-08-29 paper/icse23/tables/test-results-3-100-table.tex
add icse

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumSeedFail} & \parbox{1.5cm}{\centering\tNumExpFail} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-3-100-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc0-num-exps-avg}\pm\UseMacro{test-results-3-100-lc0-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc0-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc0-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc0-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc0-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc0-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc0-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc0-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc0-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc0-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-3-100-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc1-num-exps-avg}\pm\UseMacro{test-results-3-100-lc1-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc1-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc1-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc1-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc1-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc1-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc1-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc1-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc1-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc1-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-3-100-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc2-num-exps-avg}\pm\UseMacro{test-results-3-100-lc2-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc2-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc2-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc2-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc2-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc2-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc2-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc2-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc2-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc2-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-3-100-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc3-num-exps-avg}\pm\UseMacro{test-results-3-100-lc3-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc3-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc3-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc3-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc3-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc3-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc3-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc3-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc3-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc3-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-3-100-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc4-num-exps-avg}\pm\UseMacro{test-results-3-100-lc4-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc4-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc4-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc4-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc4-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc4-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc4-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc4-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc4-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc4-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-3-100-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc5-num-exps-avg}\pm\UseMacro{test-results-3-100-lc5-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc5-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc5-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc5-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc5-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc5-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc5-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc5-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc5-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc5-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-3-100-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc6-num-exps-avg}\pm\UseMacro{test-results-3-100-lc6-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc6-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc6-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc6-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc6-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc6-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc6-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc6-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc6-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc6-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-3-100-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc7-num-exps-avg}\pm\UseMacro{test-results-3-100-lc7-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc7-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc7-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc7-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc7-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc7-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc7-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc7-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc7-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc7-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-3-100-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc8-num-exps-avg}\pm\UseMacro{test-results-3-100-lc8-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc8-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc8-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc8-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc8-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc8-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc8-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc8-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc8-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc8-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-3-100-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-100-lc9-num-exps-avg}\pm\UseMacro{test-results-3-100-lc9-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc9-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc9-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-100-model0-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model0-lc9-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc9-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc9-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-100-model1-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model1-lc9-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc9-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc9-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-100-model2-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-100-model2-lc9-num-pass-to-fail-std}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-08-29 paper/icse23/tables/test-results-3-50-table.tex
add icse

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumSeedFail} & \parbox{1.5cm}{\centering\tNumExpFail} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-3-50-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc0-num-exps-avg}\pm\UseMacro{test-results-3-50-lc0-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc0-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc0-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc0-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc0-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc0-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc0-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc0-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc0-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc0-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-3-50-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc1-num-exps-avg}\pm\UseMacro{test-results-3-50-lc1-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc1-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc1-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc1-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc1-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc1-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc1-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc1-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc1-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc1-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-3-50-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc2-num-exps-avg}\pm\UseMacro{test-results-3-50-lc2-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc2-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc2-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc2-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc2-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc2-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc2-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc2-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc2-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc2-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-3-50-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc3-num-exps-avg}\pm\UseMacro{test-results-3-50-lc3-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc3-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc3-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc3-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc3-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc3-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc3-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc3-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc3-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc3-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-3-50-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc4-num-exps-avg}\pm\UseMacro{test-results-3-50-lc4-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc4-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc4-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc4-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc4-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc4-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc4-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc4-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc4-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc4-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-3-50-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc5-num-exps-avg}\pm\UseMacro{test-results-3-50-lc5-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc5-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc5-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc5-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc5-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc5-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc5-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc5-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc5-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc5-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-3-50-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc6-num-exps-avg}\pm\UseMacro{test-results-3-50-lc6-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc6-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc6-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc6-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc6-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc6-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc6-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc6-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc6-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc6-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-3-50-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc7-num-exps-avg}\pm\UseMacro{test-results-3-50-lc7-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc7-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc7-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc7-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc7-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc7-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc7-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc7-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc7-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc7-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-3-50-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc8-num-exps-avg}\pm\UseMacro{test-results-3-50-lc8-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc8-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc8-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc8-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc8-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc8-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc8-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc8-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc8-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc8-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-3-50-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc9-num-exps-avg}\pm\UseMacro{test-results-3-50-lc9-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc9-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc9-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model0-lc9-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc9-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc9-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model1-lc9-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc9-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc9-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-50-model2-lc9-num-pass-to-fail-std}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-08-29 paper/icse23/threats.tex
add icse

\section{Threats to Validity}
\label{sec:threats}

There are two potential threats to validity.
First, the dataset
used in our study might not be representative of all
English grammatical structures and word sentiments. We
mitigate this threat by using widely used dataset in the NLP
domain~\cite{husnain2021swnvalidity}.
Second, using ranges of the sentiment scores in SST-2 to determine the sentiment labels of search dataset may introduce incorrect labels. We performed a manual study to confirm that this is rare. 
% Use of publicly available datasets poses an external validity threat
% with respect to the generalizability of our results. We implemented
% domain-specific knowledge on publicly available word sentiments
% dataset~\cite{baccianella2010sentiwordnet}. We also constructed
% reference CFG from publicly available corpus dataset
\cite{mitchell1993treebank, nltkTreebankCorporaWebPage}.

### 2022-08-29 paper/icse23/code/requirement_sa2.py

@@ -1,0 +1,11 @@
+SRL_PHASE_TEMPLATE = {
+    "prefix": [
+        "Some people think that",
+        "Many people agree with that",
+        "They think that",
+        "You agree with that"
+    ],
+    "sent1": [],
+    "middlefix": ["but I think that"],
+    "sent2": [],
+}

### 2022-08-29 paper/ase22/tables/lc-requirement-numbers.tex
change lc-req table

@@
 \DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{[`I wouldn't say,', `I do not think,', `I don't agree with,']+[neutral\_sent]+[`,']+[pos\_sent]\}}
-\DefMacro{lc_8_desc}{Author sentiment is more important than others}
+\DefMacro{lc_8_desc}{Author sentiment is more important than of others}
 \DefMacro{lc_8_search}{\textbf{Search}~pos\_sent=\{label:pos\}, neg\_sent=\{label: neg\}}
@@
 \DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent | neg\_sent]+[`? yes']\}}
-\DefMacro{lc_10_desc}{Parsing positive sentiment in (question, no) form}
-\DefMacro{lc_10_search}{\textbf{Search}~pos\_sent=\{label: pos\}}
-\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent]+[`? no']\}}
-\DefMacro{lc_11_desc}{Parsing negative sentiment in (question, no) form}
-\DefMacro{lc_11_search}{\textbf{Search}~neg\_sent=\{label: neg\}}
-\DefMacro{lc_11_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[neg\_sent]+[`? no']\}}
+\DefMacro{lc_10_desc}{Parsing sentiment in (question, no) form}
+\DefMacro{lc_10_search}{\textbf{Search}~pos\_sent=\{label:pos\}, neg\_sent=\{label:neg\}}
+\DefMacro{lc_10_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent \ neg\_sent]+[`? no']\}}

### 2022-08-30 paper/icse23/approach.tex

--- 2022-05-05 paper/ase22/approach.tex
@@
   \includegraphics[width=\linewidth]{figs/overview.pdf}
+  \vspace{-6mm}
   \caption{\OverviewFigCaption}
@@
 \emph{Specification- and Syntax-based Linguistic Capability Testing
-  (\tool{})}, that automatically generate test cases with oracles to
-test the robustness of sentiment analysis models. \tool{} addresses
-all three challenges discussed above.
+  (\tool{})}, that automatically generates test cases with oracles to assess the quality of sentiment analysis models. \tool{} addresses all three challenges discussed in Section~\ref{sec:intro}.
 
@@
   generation} phase performs rule-based searches from a real-world
-dataset and template-based transformation to obtain the initial seed
-\sents.  The search rules (e.g., search for \neu \sents that do not
-include any \pstv or \ngtv words) and transformation templates (e.g.,
-negating a sentence) are defined in the \emph{\lc specifications},
-which guarantee that each resulting seed conforms to a specific \lc
-({\bf C2}) and is labelled correctly ({\bf C3}).
+dataset and template-based transformation to obtain the
+initial seed \sents.  The search rules (e.g., search for \neu
+\sents that do not include any \pstv or \ngtv words) and
+transformation templates (e.g., negating a sentence) are defined in the \emph{\lc
+  specifications} (Table~\ref{tab:specification}), which result in seed sentences that are most likely to conform
+to a specific \lc ({\bf C2}) and is labelled
+correctly ({\bf C3}).
 
-The \emph{syntax-based \sent expansion} phase expands the seed \sents
-with additional syntactic elements (i.e., words) to cover many
-real-world syntactic structures ({\bf C1}). It first performs a syntax
-analysis to identify the \pos (PoS) tags that can be inserted to each
-seed, by comparing the PoS parse trees between the seed \sent and many
-other \sents from a large reference dataset. Each identified tag is
-inserted into the seed as a \emph{mask}. It then uses an NLP
-recommendation model (i.e., BERT \cite{}) to suggest possible
+The \emph{syntax-based \sent expansion} phase expands the seed
+\sents with additional syntactic elements (i.e., words) to cover many real-world
+syntactic structures ({\bf C1}). It first performs a syntax analysis
+to identify the \pos (PoS) tags that can be inserted to each
+seed, by comparing the PoS parse trees between the seed \sent and
+many other \sents from a large reference dataset. Each identified
+tag is inserted into the seed as a \emph{mask}. It then uses an NLP
+recommendation model (i.e., BERT \cite{devlin2019bert}) to suggest possible
 words. If a resulting \sent is validated to be consistent with the
@@
 (e.g., the expanded word should be \neu), {\bf C2} and {\bf C3} are
-still satisfied. Last, because some validated \sents may include
-unacceptable suggested words given the context, we use a heuristic
-(i.e., the confidence score from the NLP recommendation model) to
-select the more realistic context-aware expanded \sents into \tool{}'s
-test suite.
+still satisfied.
+% Last, because some validated \sents may include
+% unacceptable suggested words given the context, we use a heuristic (i.e., the
+% confidence score from the NLP recommendation model) to select the more
+% realistic context-aware expanded \sents into \tool{}'s test suite.
 
@@
 specification, and then transforming the matched \sents using
-templates to generate seed \sents that conform to individual \lcs. The
-reasons for this design choice are twofold.  First, while generally
-judging which \lc any \sent falls into and which label it should have
-is infeasible, there exist simple rules and templates to allow
-classifying the resulting \sents into individual \lcs and with the
-correct labels, with high confidence.  This enables us to test each
-\lc individually.  Second, searching from a real-world dataset ensures
-that the \sents used as test cases for testing \lcs are realistic and
-diverse. The diverse test cases are more likely to achieve a high
-coverage of the target model's functionality in each \lc, thus
-detecting more errors.
+templates to generate seed \sents that conform to individual
+\lcs. The reasons for this design choice are twofold.  First, while
+generally judging which \lc any \sent falls into and which label it
+should have is infeasible, there exist simple rules and templates to
+allow classifying the resulting \sents into individual \lcs and
+with the correct labels, with high confidence.  This enables us to
+test each \lc individually.  Second, searching from a real-world
+dataset ensures that the \sents used as test cases for testing \lcs
+are realistic and diverse. The diverse test cases are more likely to
+achieve a high coverage of the target model's functionality in each
+\lc, thus detecting more errors.
 %
-In this phase, \tool first search and selects \sents applicable to the
-\lc in a given real-world dataset with search rules. In case that the
-search rules only fulfill portion of the \lc specifications, the
-selected \sents are not yet appropriate to become seed, we transform
-the selected \sents into seed \sents using the heuristic templates.
+In this phase, \tool first searches and selects \sents applicable to
+the \lc in a given real-world dataset with search rules. In case that
+the search rules only fulfill portion of the \lc specifications, the
+selected \sents are not yet ready to be used as seeds, we
+transform the selected \sents into seed \sents using the
+heuristic templates.
 %
@@
 models are evaluated in the scope of short \sents with selective
-sentiment words. It does not require any transformation because the
-search rule alone is sufficient to conform to the \lcs. On the other
-hand, search rules of LC3 to LC11 are not enough to match their \lc
-specification, thus \tool uses heuristic templates to conform the
-searched \sents to the \lc. For example, in LC3's transformation
-template, the searched \sents become seeds by preturbing them with the
-defined templates.  In LC4's transformation template, the searched
-demonstrative sentences are negated.
+sentiment words. It does not require any
+transformation because the search rules alone are sufficient to find sentences that conform
+to the \lcs. On the other hand, search rules of LC3 to LC11 are not enough to match their \lc specification; thus, \tool additionally uses 
+templates to transform the searched \sents to match the corresponding \lc. For example, in LC3's transformation template, the searched \sents are appended as part of a sentence to generate a seed.
+In LC4's transformation template, the searched demonstrative sentences are negated.
 % \sw{@Jaeseong: revise the rest of 3.1 based on
@@
 cover. To address this limitation, the syntax-based \sent expansion
-phase extends the seed \sents to cover syntactic structures commonly
-used in real-life \sents. Our idea is to differentiate the parse trees
-between the seed \sents and the reference \sents from a large
-real-world dataset. The extra PoS tags in the reference parse trees
-are identified as potential syntactic elements for expansion and
-inserted into the seed \sents as masks. We then use masked language
-model to suggest the fill-ins. If the resulting \sents still conform
-to the \lc specification, they are added to \tool{}'s test suite.
+phase extends the seed \sents to cover syntactic structures
+commonly used in real-life \sents. Our idea is to differentiate the
+parse trees between the seed \sents and the reference \sents
+from a large real-world dataset. The extra PoS tags in the reference
+parse trees are identified as potential syntactic elements for
+expansion and inserted into the seed \sents as masks. We then use
+masked language model to suggest the fill-ins. If the resulting
+\sents still conform to the \lc specification,
+they are added to \tool{}'s test suite.
 
@@
 reference context-free grammar (CFG) from the Penn Treebank corpus
-dataset \cite{} as inputs.  The reference CFG is learned from a large
-dataset \cite{} that is representative of the distribution of
-real-world language usage.  The algorithm identifies the discrepancy
-between the seed syntax and the reference grammar to decide how a seed
-can be expanded.
+dataset~\cite{mitchell1993treebank} as inputs.  
+This reference CFG was learned from a large dataset~\cite{nltkTreebankCorporaWebPage} that is representative of the distribution of real-world language usage.  
+The algorithm identifies the discrepancy between the seed syntax 
+and the reference grammar to decide how a seed can be expanded.
 %This phase builds \pcfg from the reference corpus. \cfg
@@
 7, the algorithm iterates through all productions in the reference
-context-free grammar and match these that have the same non-terminal
+context-free grammar and matches these that have the same non-terminal
 at the left-hand-side as $s\_lhs$.  The right-hand-side of each
@@
 symbols in the $r\_rhs$ are inserted as masks in the parse tree of
-seed \sent, in their respective positions in the expanded production.
+the seed \sent, in their respective positions in the expanded production.
 The left to right traversal of the leaves of an expanded parse tree
-forms a masked \sent.  Lastly, due to the inefficient cost of
-accessing full list of the masked \sents, we randomly select $k$
-masked \sents for the next \sent expansion and validation phase when
-the masked \sents are more than maximum number of masked \sents. The
-random sampling is unbiased approach since it gives same chance to be
-chosen. Thus, the random sample becomes representative of the
-population of the masked \sents, and it efficiently shows the
-usefulness of the \tool.
+forms a masked \sent.  Due to a potential large number of masked \sents created by this algorithm, we randomly select $k$
+masked \sents for the next \sent expansion and validation phase (line 14).
+% The
+% random sampling is unbiased approach since it gives same chance to be
+% chosen. Thus, the random sample becomes representative of the
+% population of the masked \sents, and it efficiently shows the
+% usefulness of the \tool.
 
@@
   \includegraphics[scale=0.7]{figs/running_example.pdf}
+  \vspace{-5mm}
   \caption{\RunningExCaption}
@@
 \paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
-to generate a masked \sent. The \sent ``Or both." is a seed of \lc of
+to generate a masked \sent. The \sent ``Or both." is a seed of the \lc of
 \SareqExOne.  The tree on the left shows the parse tree of this seed;
@@
 In this phase, the words to fill in the masks in the masked \sents are
-suggested by the BERT pretrained model~\cite{devlin2019bert}.  The
-BERT is a transformer-based \nl model. It is pretrained on two tasks
-of masked token prediction and next sentence prediction. As a result
-of the training process, the BERT model suggests word for the mask
-token according to its surrounding context in \sent. For each masked
-token, multiple words are suggested ranked by their confidence scores.
+suggested by the BERT model~\cite{devlin2019bert}. 
+BERT is a transformer-based \nl model that is pre-trained on two tasks: masked token prediction and next sentence prediction. BERT model is capable of suggesting words for the masked
+token according to its surrounding context in a \sent. For each masked
+token, multiple words are suggested, ranked by their confidence scores.
 % \sw{Algorithm 1 does not require we only have one mask in the masked
@@
 %
-Because BERT model is not aware of the \lc specification and the
-grammar symbol in the expanded parse tree, an expanded \sent using the
-suggested words may no longer satisfy the \lc
-specification. Therefore, we perform validation on the suggested words
-and only accept them if the following three criteria are met.
+Because BERT model is not aware of the \lc
+specification and the grammar symbol in the expanded parse tree, an
+expanded \sent using the suggested words may no longer satisfy the
+\lc specification. Therefore, we perform validation
+on the suggested words and only accept them if the following three
+criteria are met.
 
@@
 Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
-noun); thus, the suggested word must also be a ``NNS". In this work,
-we use \spacy, a free open-source library for \nlp, for extracting PoS
-tags for each suggested word.
+noun); thus, the suggested word must also be a ``NNS". We use \spacy \cite{spacy}, a free open-source library for \nlp, to extract the PoS
+tag for each suggested word.
 
-Second, it is required that the sentiment of the expanded \sent
-becomes the same as the seed \sent. To ensure this, the suggested
-words must be \neu.
+Second, it is required that the
+sentiment of the expanded \sent is the same as the seed \sent. To
+ensure this, the suggested words must be \neu.
 
-Third, we additionally verify that the expanded \sents satisfied the
-same search rules for the seed \sent in LC1 and LC2. This criteria
-cannot be applied to other linguistic capabilities because they have
-additional transformation templates.
+Third, we additionally verify that the
+expanded \sents satisfy the same search rules for the seed
+\sent in LC1 and LC2. This criteria cannot be applied to other linguistic capabilities because they have additional transformation templates.
 
-In this work, out of the BERT suggested words, we randomly selects
-words that matches their PoS tag of the expanded symbol in the parse
-tree. The words that meets the second and third criteria are finally
-employed for the expanded \sents.
+% In this work, out of the BERT suggested words, we randomly selects
+% words that matches their PoS tag of the expanded symbol in the parse
+% tree. The words that meets the second and third criteria are finally
+% employed for the expanded \sents.
+
 % Our goal for generating the expanded \sents is to use them for
@@
 \paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
-by BERT. For this masked \sent, BERT suggested six words. Each word is
-associated with the confidence score provided by BERT, the PoS tag,
+by BERT. For this masked \sent, BERT suggested six words. Each word
+is associated with the confidence score provided by BERT, the PoS tag,
 and the sentiment. Among the six words, only ``ways'' and ``things''
 are validated by \tool{} because they have the Pos tag ``NNS'' and are
-\neu. In addition, it is found that both \sents meets the search rule
-of the associated \lc of \SareqExOne. In the end, two \sents of ``Or
-both ways'' and ``Or both things'' are generated.
+\neu. In addition, it is found that both \sents meets the search
+rule of the associated \lc of \SareqExOne. In the end, two \sents
+of ``Or both ways'' and ``Or both things'' are generated.
 

### 2022-08-30 paper/icse23/background.tex

\section{Background}
\label{sec:background}

%% \sw{We should motivate the testing of linguistic capabilities. Give
%%   background of the work that has been done in CheckList: what
%%   capabilities they support and their limitations. Maybe find a
%%   motivating example?}

In this section, we provide a brief background of \Cklst's approach of test case generation
 via an example.
%  Quality of software is verified by ensuring
% the proper working of all functionalities without knowing the internal
% workings of the software. Knowing performances of model on the
% multiple functionalities provides users with better understanding and
% debugging the software. The same principle applies to the NLP model.
% Traditional NLP model evaluation relying on a test set lacks the
% specification of model functionality. However, in NLP domain, there
% are many phenomena on linguistic input such as negation, and
% questionization. Given a NLP task, the phenomena determine
% task-relevant output. Traditional evaluation method neglects them;
% thus, it becomes less efficient to detect and analyze which aspect the
% model yields unexpected outcome.
\Cklst
introduces task-dependent \lcs for monitoring model performance on
each \lc. It assumes that the linguistic phenomena can be represented
in the behavior of the model under test, because each linguistic capability specifies the desired behavior between inputs and outputs. For each \lc, \Cklst creates
test case templates and generates sentences by filling in the values of
each placeholder.

We show an example of \Cklst templates in
Figure~\ref{code:TempEx}. These templates are used for
evaluating a \sa model on the linguistic capability of \SareqExThree.
For the templates defined
from lines~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}, they
have placeholders such as ${it}$, ${air\_noun}$, ${pos\_adj}$. Values
for the placeholders are defined at
line~\ref{code:tempex:airnoun:1},~\ref{code:tempex:posadj:1} and~\ref{code:tempex:itbe}, .
For each template, \Cklst fills in all the combinations of the
values of placeholders, and
the sentences such as ``The flight is good'', ``That
airline was happy'' are generated. These sentences are used for the evaluation
of the \lc.

Despite its simplicity of test case generation, \Cklst has
limitations. First, it relies on manual work for defining template
structure and its placeholder values making the test case
generation a costly process. Moreover, such
manual work generates the limited number of templates and produces high similarity between test cases, and induces bias in the test cases. These limitations motivated the design of our approach.

\begin{figure}[hbp!]
 \centering
 \lstinputlisting[language=python-pretty]{code/checklist_template.py}
 \vspace{-10pt}
 \caption{\CklstTemplateFigCaption}
 \vspace{-10pt}
\end{figure}

### 2022-08-30 paper/icse23/intro.tex

--- 2022-05-06 paper/ase22/intro.tex
@@
 for its practical use in the real world.  Therefore, quality assurance
-of NLP applications is an essential process in the software
-development processes.  Researchers aim to improve the current
-practices of testing NLP models from three perspectives: (i)
-\emph{Test input generation}, (ii) \emph{Automated test oracle}, and
-(iii) \emph{Meaningful quality metrics}.
+of NLP applications is essential in the software
+development process.  
+Researchers aim to improve the current practices of testing NLP models
+from three perspectives: (i) \emph{test input generation}, (ii)
+\emph{automated test oracle}, and (iii) \emph{meaningful quality
+  metrics}.
 
 \noindent \textbf{Test input generation.} Currently, most testing of
-an NLP model reuses existing large textual corpus as the testing
-dataset to evaluate the model. This practice will often overestimates
+an NLP model uses existing, large textual corpus as the testing
+dataset to evaluate the model. This practice often overestimates
 the model performances from the \ho
-set~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
+dataset~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
   marcoACL2020checklist}.  The overestimation comes from the
-discrepancy between the distribution of the used dataset and the
-actual data distribution in real world. Oftentimes, the \ho dataset is
-not representative and is likely to introduce specific biases, leading
-to the decreased robustness of NLP models. In this regard, prior works
-have proposed techniques for testing the robustness of NLP models by
-crafting adversarial examples and attacking a model with them
-intentionally \cite{ribeiro2018sear,belinkov2018breaknmt,
+discrepancy between the distribution of the used dataset and the actual data
+distribution in real world. Oftentimes, the \ho dataset is not
+representative and is likely to introduce specific biases, leading to the
+decreased robustness of NLP models. In this regard, prior works
+have proposed techniques for testing the robustness of NLP models by crafting
+adversarial examples and attacking a model with them intentionally (i.e., adversarial testing)
+\cite{ribeiro2018sear,belinkov2018breaknmt,
   rychalska2019wildnlp,iyyer2018adversarial}.
@@
 \noindent \textbf{Automated test oracle.} The current testing practice
-requires manual work for labelling the test oracles of the \ho
+requires manual efforts to label the test oracles of the \ho
 data. The manual work is costly in terms of time consumption and its
-impact on market price. Therefore, it necessitates automated test
-oracle generation for improving the testing process of NLP models.
+impact on the market price. Therefore, it necessitates automated test
+oracle generation for improving the testing process of NLP
+models. 
 % validity of the automation is ensured by the
 % correctness of test oracle.
-However, automatically generated test oracles may not always be
-feasible; predicting the correct test oracles remains one of main
-challenges. Along with this, software metamorphic testing approach has
-been introduced~\cite{segura2016metamorphictest} to alleviate the test
-oracle discrepancy between expected and observed test oracles.
+However, automatically generating test oracles may not always
+be feasible; predicting the correct test oracles remains one of main
+challenges. Along with this, motivated by software metamorphic testing 
+approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules. 
 % \TODO{Describe and Add citations to metamorphic testing techniques
@@
 % distribution between the dataset and real-world data.
-\noindent \textbf{Meaningful quality metrics.}  Traditionally, the
-quality of NLP models are represented by numbers in quality
-metrics. Especially, accuracy (i.e., the fraction of outputs that the
+\noindent \textbf{Meaningful quality metrics.}  
+Traditionally, the quality of NLP models are
+represented by numbers in quality metrics. Especially, accuracy (i.e., the fraction of outputs that the
 model correctly predicts) is the most widely used metric for assessing
-the quality of classification models.  Generally, higher accuracy
-number suggests better quality of a model.  However, all NLP models
-have their strength and weakness and forcing aggregation statistics
-into a single number makes the users difficult to assess the
-capabilities of NLP models.  Not to mention localizing and fixing the
-bugs found from the \ho set (i.e., testing dataset, as opposed to
-training dataset). Therefore, this forced aggregation method not only
-fails to validate the linguistic capability of the model, but it also
-makes the localization of the causes of the inaccuracy more
-costly~\cite{wu2019errudite}.
+the quality of classification models. 
+Generally, higher accuracy number suggests better quality of a model.
+However, all NLP models have their strengths and weaknesses, and 
+forcing aggregation statistics into a single number (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.  Not to
+mention localizing and fixing the bugs found from the \ho
+set (i.e., testing dataset, as opposed to training dataset). Therefore, this forced aggregation method not only fails to
+validate the linguistic capability of the model, but it also makes the localization of the
+causes of the inaccuracy more costly~\cite{wu2019errudite}.
 % Therefore behavioral testing
@@
 However, none of the above approaches satisfy all three requirements
-at the same time. First, adversarial testing approaches merely focus
-on evaluating model robustness. They measure how sensitive the models
-are to input perturbations while do not evaluate linguistic
-functionalities.  Second, the metamorphic testing approach is required
-to understand the characteristics of metamorphic relations between
-inputs and outputs. However, finding these remains one of the most
-challenging problem in metamorphic
-testing~\cite{segura2016metamorphictest}. Along with this, such
-relation in textual data in NLP domain has not been evaluated despite
-its importance.  Third, \Cklst relies on manually generated input
-templates, which need to be preset before test input
-generation. Consequently, \Cklst templates are distributed in a
-limited range of their structures. This restricts \Cklst's ability to
-comprehensively test the linguistic capabilities.
+at the same time. First, the adversarial testing approaches merely
+focus on evaluating model robustness. They measure how sensitive the models
+are to input perturbations while do not
+evaluate linguistic functionalities.
+Second, the metamorphic testing approach requires understanding the characteristics of metamorphic relations between inputs
+and outputs. However, finding these remains one of the most challenging
+problems~\cite{segura2016metamorphictest}. In addition, metamorphic
+relation in textual data in the NLP domain has not been explored despite
+its importance.
+Third, \Cklst relies on manually generated input templates,
+which need to be preset before test input generation. Consequently,
+\Cklst templates are distributed in a limited range of their
+structures. This restricts \Cklst's ability to comprehensively test
+the linguistic capabilities.
 
@@
 NLP model under test. Typically, it describes certain type of inputs
-and outputs observed in real world for the target NLP task ranging
-from simple to complicated behaviors, so the model developers can
-better understand the capabilities and potential issues of the NLP
+and outputs observed in real world for the target NLP task, ranging
+from simple to complicated behaviors. Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
 models. For example, a linguistic capability of ``Negated neutral
 should still be neutral'' measures how accurately the \sa model
-understands the negative neutral input as an neutral sentiment
-\cite{marcoACL2020checklist}.  Therefore, it requires the \sa model to
-output neutral sentiment on the negated neutral input.  Such
-methodology of evaluation on the specified functionalities avoids the
-overestimation of the model performance as it equivalently measures
+understands that the negated neutral input has neutral sentiment
+\cite{marcoACL2020checklist}, requiring the \sa model to
+output neutral sentiment on the negated neutral inputs.  Such evaluation
+methodology on the specified functionalities avoids the
+overestimation of the model performance as it measures
 the model performance on each functionality.
@@
 To satisfy all three requirements mentioned above, we present \tool,
-an automated NLP model evaluation method for comprehensive behavioral
+an automated evaluation method for comprehensive behavioral
 testing of NLP models on \sa task.  There are three main challenges
@@
 \item[{\bf C1}] The test suite should cover diverse syntactic structures;
-\item[{\bf C2}] Each test case should be categorized into a \lc;
+\item[{\bf C2}] Each test case should be automatically categorized into a \lc;
 \item[{\bf C3}] The label of each test case should be automatically
@@
 
-\noindent \textbf{C1.} The first challenge comes with the second and
-third challenges of maintaining the label and linguistic capability of
-the test sentence while making the syntactic structure of the sentence
-more diverse. In addition, text have a higher order of structures and
-structures are obscured by word usage~\cite{}. To address the
-challenge, \tool establishes specifications for evaluating a
-linguistic capability and searches suitable sentences that satisfy the
-specification from existing public dataset. In this process, \tool
+\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse.
+To address this challenge, \tool establishes specifications for evaluating
+a linguistic capability and searches suitable sentences that satisfy
+the specification from existing public dataset. In this process, \tool
 generates new inputs by mutating the searched sentences, used as seed
-inputs. \tool expands seed input grammar structures and determines its
+inputs. \tool expands the grammar structure of a seed input and determines its
 available \pos to maintain structural naturalness.
@@
 
-\noindent \textbf{C2.} Suitability of test sentences for evaluating
-NLP model on a \lc is obtained from its high relevancy to the
-\lc. Relevancy between a test sentence and its \lc is challenging to
-be maintained during the transformation and expansion of the test
-sentence.  This is because the \lc is defined on a specific mixture of
-syntaxe and semantics of the sentence, and there exists no automatic
-way to check the consistency between each sentence with the semantics
-specified in corresponding \lc due to the inherent ambiguity of
-natural language sentences. To address the difficulty, \tool
-implements search rules and the transformation templates of \lcs. In
-addition, anlyzing parse tree of seed sentence is used for its
-expansion identification.
+\noindent \textbf{C2.} Suitability of test sentences for evaluating NLP
+model on a \lc is determined by its relevancy to the
+\lc. Relevancy between a test sentence and its \lc is challenging to be maintained when transforming and expanding the test sentence.
+This is because the \lc is defined on a specific 
+mixture of syntax and semantics of the sentence, and there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc due to the inherent ambiguity of natural language sentences.
+To address this difficulty, \tool implements search rules
+and the transformation templates of \lcs. In addition, it analyzes the parse
+tree of the seed sentence to identify possible expansion.
 %% \tool adopts behavioral model testing method by
@@
 
-\noindent \textbf{C3.} Last challenge is on automated test oracle.
-For NLP tasks, test oracle is determined by understanding meaning from
-texts. This requires domain knowledge for different NLP tasks
+\noindent \textbf{C3.} Last challenge is on automated test oracle.  For NLP tasks, test oracle is
+determined by understanding the meaning of texts. This requires domain knowledge of different NLP tasks.
 % Therefore, generation of test case ought to ensure the
 %correctness of its oracle allocation.
-In this work, as a first step, we consider \sa as the NLP task for the
-models under test. \tool obtain the appropriateness of test oracle by
-implementing domain-specific knowledge on word sentiment dataset and
-word suggestion model pre-trained on large corpus for validation of
-generated sentence and its oracle.
+In this work, as a first step, we consider \sa as the NLP task for the models under test. \tool obtains the
+appropriate test oracle by implementing domain-specific
+knowledge on the word sentiment dataset and word suggestion model for validation of generated sentence and its oracle.
 
-We demonstrate its generality and utility as a NLP model evaluation
-tool by evaluating well-known \sa models: \Bert~\cite{devlin2019bert},
+We demonstrate the generality of \tool and its utility as a NLP model evaluation
+tool by evaluating three well-known \sa models: \Bert~\cite{devlin2019bert},
 \Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.
-We show that ...
+
+\vspace{2pt}
+\noindent
+We made the following contributions in this work:
+
+\begin{itemize}[topsep=3pt,itemsep=3pt,partopsep=0ex,parsep=0ex,leftmargin=*]
+\item We design and implement an automated testing tool, \tool, and compared it with \Cklst.
+We find that the test cases generated by \tool achieves higher coverage than \Cklst when used for testing sentiment analysis models.
+%
+\item We perform a manual study to
+measure the correctness of the sentiment labels and their \lcs produced by \tool. We find that \tool generates test cases that consistently label their sentiment correctly as human understanding.
+%
+\item We analyze the root causes of the misclassification in the sentiment analysis models, guided by \tool testing result.
+We find that seed and expanded test cases, produced by \tool, are usefulness of \tool for understanding bugs in the models.
+\end{itemize}
+
+% \sw{results are missing}
+
+% \sw{Do we want to explicitly list contributions?}
 

### 2022-08-30 paper/icse23/tables/test-results-3-200-table.tex

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumSeedFail} & \parbox{1.5cm}{\centering\tNumExpFail} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-3-200-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc0-num-exps-avg}\pm\UseMacro{test-results-3-200-lc0-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc0-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc0-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc0-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc0-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc0-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc0-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc0-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc0-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc0-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc0-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc0-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc0-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-3-200-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc1-num-exps-avg}\pm\UseMacro{test-results-3-200-lc1-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc1-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc1-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc1-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc1-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc1-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc1-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc1-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc1-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc1-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc1-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc1-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc1-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-3-200-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc2-num-exps-avg}\pm\UseMacro{test-results-3-200-lc2-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc2-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc2-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc2-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc2-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc2-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc2-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc2-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc2-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc2-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc2-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc2-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc2-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-3-200-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc3-num-exps-avg}\pm\UseMacro{test-results-3-200-lc3-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc3-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc3-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc3-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc3-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc3-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc3-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc3-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc3-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc3-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc3-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc3-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc3-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-3-200-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc4-num-exps-avg}\pm\UseMacro{test-results-3-200-lc4-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc4-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc4-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc4-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc4-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc4-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc4-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc4-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc4-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc4-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc4-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc4-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc4-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-3-200-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc5-num-exps-avg}\pm\UseMacro{test-results-3-200-lc5-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc5-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc5-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc5-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc5-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc5-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc5-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc5-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc5-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc5-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc5-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc5-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc5-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-3-200-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc6-num-exps-avg}\pm\UseMacro{test-results-3-200-lc6-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc6-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc6-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc6-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc6-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc6-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc6-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc6-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc6-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc6-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc6-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc6-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc6-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-3-200-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc7-num-exps-avg}\pm\UseMacro{test-results-3-200-lc7-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc7-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc7-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc7-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc7-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc7-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc7-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc7-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc7-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc7-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc7-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc7-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc7-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-3-200-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc8-num-exps-avg}\pm\UseMacro{test-results-3-200-lc8-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc8-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc8-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc8-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc8-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc8-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc8-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc8-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc8-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc8-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc8-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc8-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc8-num-pass-to-fail-std}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-3-200-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-200-lc9-num-exps-avg}\pm\UseMacro{test-results-3-200-lc9-num-exps-std}}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc9-num-seed-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc9-num-exp-fail-std}
 & BERT$\colon$\UseMacro{test-results-3-200-model0-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model0-lc9-num-pass-to-fail-std}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc9-num-seed-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc9-num-exp-fail-std}
 & RoBERTa$\colon$\UseMacro{test-results-3-200-model1-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model1-lc9-num-pass-to-fail-std}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc9-num-seed-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc9-num-seed-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc9-num-exp-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc9-num-exp-fail-std}
 & dstBERT$\colon$\UseMacro{test-results-3-200-model2-lc9-num-pass-to-fail-avg}\pm\UseMacro{test-results-3-200-model2-lc9-num-pass-to-fail-std}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-08-30 python/hs/requirement/Requirements.py
hs debug

@@ -240,7 +240,7 @@ class Requirements:
                             'length': None,
                             'include': {
                                 'POS': None,
-                                'word': ["It is in <hurtlex_pos:n>'s nature to be uncivilised"]
+                                'word': ["It is in <hurtlex_pos:n> 's nature to be uncivilised"]
                             },
                             'label': 'toxic'
                         }, {

### 2022-08-30 python/hs/testsuite/Search.py

@@ -133,6 +133,7 @@ class SearchOperator:
                 if tw.startswith('<') and tw.endswith('>'):
                     # search any words in the values in the target template
                     target_template = tw.strip('<>')
+                    
                     if target_template.endswith('_syn'):
                         _tw = target_template.split('_syn')[0]
                         _tw_syns = self.get_synonyms(nlp, _tw)

### 2022-08-30 python/hs/testsuite/Suggest.py

@@ -189,7 +189,7 @@ class Suggest:
         return False
     
     @classmethod
-    def eval_sug_words_by_req(cls, new_input, requirement, label):
+    def eval_sug_words_by_req(cls, new_input, nlp, requirement, label):
         if requirement['transform_req'] is not None:
             _requirement = {
                 'capability': requirement['capability'],
@@ -200,7 +200,12 @@ class Suggest:
             _requirement = requirement
         # end if
         search_obj = SearchOperator(_requirement)
-        search_res = search_obj.search([('1', new_input, label)])
+        # search_res = search_obj.search([('1', new_input, label)], nlp)
+        search_res = search_obj.search([{
+            'post_id': '1',
+            'tokens': Utils.tokenize(new_input),
+            'label': label
+        }], nlp)
         return any(search_res)
         # if len(search_res)>0:
         #     return True
@@ -492,14 +497,15 @@ class Suggest:
     @classmethod
     def eval_word_suggestions_over_seeds(cls,
                                          masked_inputs_w_word_sug,
+                                         nlp,
                                          req,
                                          num_target=Macros.num_suggestions_on_exp_grammer_elem,
                                          selection_method=None,
                                          no_mask_key='<no_mask>',
                                          logger=None):
         st = time.time()
-        nlp = spacy.load('en_core_web_md')
-        nlp.add_pipe("spacy_wordnet", after='tagger', config={'lang': nlp.lang})
+        # nlp = spacy.load('en_core_web_md')
+        # nlp.add_pipe("spacy_wordnet", after='tagger', config={'lang': nlp.lang})
         exp_results = dict()
         for masked_sent in masked_inputs_w_word_sug.keys():
             word_sug = masked_inputs_w_word_sug[masked_sent]['word_sug']
@@ -533,15 +539,14 @@ class Suggest:
                     for w_sug in word_suggest:
                         input_candid = cls.replace_mask_w_suggestion(masked_sent, w_sug)
                         # check sentence and expansion requirements
-                        if cls.eval_sug_words_by_req(input_candid, req, seed_label):
-                            if cls.eval_sug_words_by_exp_req(nlp, w_sug, req):
-                                results.append((masked_sent,
-                                                cfg_from,
-                                                cfg_to,
-                                                mask_pos,
-                                                w_sug,
-                                                input_candid))
-                            # end if
+                        # if cls.eval_sug_words_by_req(input_candid, nlp, req, seed_label):
[…]

### 2022-08-30 python/hs/testsuite/Template.py

@@ -117,8 +117,9 @@ class Template:
         args = list()
         pool = multiprocessing.Pool(processes=cls.NUM_PROCESSES)
         for index, (_id, seed, seed_label) in enumerate(seeds):
-            args.append((index, seed, seed_label, 0., pcfg_ref, logger))
-        # end for    
+            _seed = Utils.detokenize(seed) if type(seed)==list else seed
+            args.append((index, _seed, seed_label, 0., pcfg_ref, logger))
+        # end for
         results = pool.starmap_async(cls.generate_seed_cfg_parallel,
                                      args,
                                      chunksize=len(seeds)//cls.NUM_PROCESSES).get()
@@ -309,6 +310,7 @@ class Template:
         
         # validate word suggestion
         exp_results = Suggest.eval_word_suggestions_over_seeds(masked_inputs_w_word_sug,
+                                                               nlp,
                                                                req,
                                                                num_target=num_target,
                                                                selection_method=selection_method,

### 2022-08-31 paper/ase22/tables/lc-requirement-numbers.tex
fix table lc-req

@@
 \DefMacro{lc_1_desc}{Short sentences with neutral adjectives and nouns}
-\DefMacro{lc_1_search}{\textbf{Search}~seed=\{length: <10; include: neutral adjs \& neutral nouns;~exlcude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
+\DefMacro{lc_1_search}{\textbf{Search}~seed=\{length: $<$ 10; include: neutral adjs \& neutral nouns;~exlcude: pos adjs \& neg adjs \& pos nouns \& neg nouns; label: neutral\}}
 \DefMacro{lc_1_transform}{\textbf{Transform}~N/A}
 \DefMacro{lc_2_desc}{Short sentences with sentiment-laden adjectives}
-\DefMacro{lc_2_search}{\textbf{Search}~seed=\{length: <10; include: pos adjs;~exlcude: neg adjs \& neg verbs \& neg nouns; label: pos\} | \{length: <10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
+\DefMacro{lc_2_search}{\textbf{Search}~seed=\{length: $<$ 10; include: pos adjs;~exlcude: neg adjs \& neg verbs \& neg nouns; label: pos\} $|$ \{length: $<$ 10; include: neg adjs;exclude: pos adjs \& pos verbs \& pos nouns \& neg verbs \& neg nouns; label: neg\}}
 \DefMacro{lc_2_transform}{\textbf{Transform}~N/A}
 \DefMacro{lc_3_desc}{Sentiment change over time, present should prevail}
-\DefMacro{lc_3_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{[`Previously, I used to like it saying that',`Last time, I agreed with saying that',`I liked it much as to say that']+[pos\_sent | neg\_sent]+[`but', `although', `on the other hand']+[`now I don't like it.', `now I hate it.']\} | \{[`I used to disagree with saying that',`Last time, I didn't like it saying that',`I hated it much as to say that']+[neg\_sent, pos\_sent]+[`but', `although', `on the other hand']+[`now I like it.']\}}
+\DefMacro{lc_3_search}{\textbf{Search}~pos\_sent=\{label: pos, length: $<$ 20\}, neg\_sent=\{label: neg, length: $<$ 20\}}
+\DefMacro{lc_3_transform}{\textbf{Transform}~seed=\{[`Previously, I used to like it saying that',`Last time, I agreed with saying that',`I liked it much as to say that']+[pos\_sent $|$ neg\_sent]+[`but', `although', `on the other hand']+[`now I don't like it.', `now I hate it.']\} $|$ \{[`I used to disagree with saying that',`Last time, I didn't like it saying that',`I hated it much as to say that']+[neg\_sent, pos\_sent]+[`but', `although', `on the other hand']+[`now I like it.']\}}
 \DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
 \DefMacro{lc_4_search}{\textbf{Search}~demonstrative\_sent=\{start: [This, That, These, Those] + [is, are]; label: neg\}}
-\DefMacro{lc_4_transform}{\textbf{Transform}~seed=negation of demonstrative\_sent ([`is'] -> [`is not', `isn't'], [`are'] -> [`are not', `aren't'])}
+\DefMacro{lc_4_transform}{\textbf{Transform}~seed=negation of demonstrative\_sent ([`is'] $\to$ [`is not', `isn't'], [`are'] $\to$ [`are not', `aren't'])}
 \DefMacro{lc_5_desc}{Negated neutral should still be neutral}
@@
 \DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
-\DefMacro{lc_7_search}{\textbf{Search}~pos\_sent=\{length: <20; label: pos\}, neutral\_sent=\{length: <20; label: neutral\}}
+\DefMacro{lc_7_search}{\textbf{Search}~pos\_sent=\{length: $<$ 20; label: pos\}, neutral\_sent=\{length: $<$ 20; label: neutral\}}
 \DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{[`I wouldn't say,', `I do not think,', `I don't agree with,']+[neutral\_sent]+[`,']+[pos\_sent]\}}
@@
 \DefMacro{lc_8_search}{\textbf{Search}~pos\_sent=\{label:pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\} | \{[temp1]+[neg\_sent]+[temp2]+[pos\_sent]\} where temp1=\{[`Some people think that', `Many people agree with that', `They think that', `You agree with that'], temp2=[`but I think that']\}}
+\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\} $|$ \{[temp1]+[neg\_sent]+[temp2]+[pos\_sent]\} where temp1=\{[`Some people think that', `Many people agree with that', `They think that', `You agree with that'], temp2=[`but I think that']\}}
 \DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}
 \DefMacro{lc_9_search}{\textbf{Search}~pos\_sent=\{label: pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent | neg\_sent]+[`? yes']\}}
+\DefMacro{lc_9_transform}{\textbf{Transform}~seed=\{[`Do I think that', `Do I agree that']+[pos\_sent $|$ neg\_sent]+[`? yes']\}}
 \DefMacro{lc_10_desc}{Parsing sentiment in (question, no) form}

### 2022-08-31 python/sa/paper/Tables.py

@@ -28,7 +28,14 @@ class Tables:
     FMT_FLOAT = "{:,.2f}"
 
     LATEX_SYMBOL_MAP = {
-        '&': '\&', '{': '\{', '}': '\}', '_': '\_'
+        '&': '\&',
+        '{': '\{',
+        '}': '\}',
+        '_': '\_',
+        ' < ': ' $<$ ',
+        ' > ': ' $>$ ',
+        '|': '$|$',
+        '->': '$\\to$'
     }
     
     @classmethod

### 2022-08-31 python/sa/paper/Tables.py
change name of model

@@ -615,7 +615,7 @@ class Tables:
                 if m_i==1:
                     m_name = 'RoBERTa'
                 else:
-                    m_name = 'dstBERT'
+                    m_name = 'DistilBERT'
                 # output_file.append(f" & & {m_name}$\colon$" + latex.Macro(f"test-results-bl-model{m_i}-lc{lc_i}-num-fail").use())
                 output_file.append(f" & & & {m_name}$\colon$" + latex.Macro(f"test-results-{num_trials}-{num_seeds}-model{m_i}-lc{lc_i}-num-seed-fail-avg").use() + \
                                    "\pm" + latex.Macro(f"test-results-{num_trials}-{num_seeds}-model{m_i}-lc{lc_i}-num-seed-fail-std").use())

### 2022-09-02 paper/icse23/abstract.tex
icse23 submission latex

--- 2022-06-07 paper/ase22/abstract.tex
@@
 \begin{abstract}
-  \Nlp (NLP) technique has become one of the core techniques for
-  developing text  analytic applications.  These applications need to achieve high
-  reliability to be useful in practice.  The trustworthiness of the NLP applications is often obtained by measuring the accuracy of
-  the applications on holdout datasets. However, evaluating NLP on the accuracy of the holdout datasets is limited in validating its overall
-  quality because these datasets are often not
-  comprehensive. To address this limitation, evaluating an NLP model on
-  task-specific behaviors defined on linguistic
-  capabilities has been introduced. However, such evaluation relies on manually
-  created test cases, and  is still limited to measure the model
-  performance on limited datasets. In this work, we introduce \tool,
-  an NLP model testing infrastructure.  Given a linguistic capability that users want to evaluate for a NLP model, \tool finds suitable seed inputs
-  from existing datasets, generates sufficient number
-  of new test inputs by expanding the seed inputs based on their \cfg
-  (CFG).  We evaluate \tool by showing that it can generate test cases that are more diverse than an existing approach.
-  We also show that \tool facilitates
-  identification of critical failures and its origins in the NLP models
-  for the \sa task.
+  \Nlp has been widely used for developing a variety of text analytic applications with high reliability.
+For any NLP-based applications to be trustworthy, assessment through measuring the accuracy of the holdout datasets is needed.
+Recent research introduced methods that assess an NLP model on a set of linguistic capabilities.
+  However, we observe that state-of-the-art methods rely on manually created test cases, which may be limited in terms of scalability and diversity.
+%\Nlp (NLP) technique has become one of the core techniques fordeveloping text  analytic applications.  These applications need to achieve high reliability to be useful in practice.  
+%The trustworthiness of the NLP applications is often obtained by measuring the accuracy ofthe applications on holdout datasets.
+However, assessing an NLP application on the accuracy of the holdout datasets is limited in validating its overallquality because these datasets are often notcomprehensive.
+  %To address this limitation, methodologies to assess an NLP model on a set oflinguistic capabilities has recently been introduced.
+However, current state-of-the-art methodologies rely on manuallycreated test cases which limits the scale of the testing dataset.
+  In this work, we introduce \tool,
+  an automated linguistic capability-based testing technique.
+Given a set of linguistic capabilities that assess an NLP model, \tool first searches for suitable seed inputs from existing datasets, and then generates a sufficient number
+  of new test inputs by expanding the seed inputs based on their \cfg (CFG). 
+  \tool guarantees the correctness of the generated test input labels and that these test inputs belong to the correct linguistic capabilities. 
+  Evaluation results show that \tool can generate test cases that are 100\%  more diverse than state-of-the-art 
+   while ensuring the correctness of labels and linguistic capabilities of the test inputs. 
+%   \Cong{You mention comprehensive and scalability before, so better give improvement numbers in terms of these metrics.}
+  We also show that \tool facilitates the identification of critical failures and its origins in the NLP models.
 \end{abstract}

### 2022-09-02 paper/icse23/approach.tex
icse23 submission latex

@@
   \centering
-  \includegraphics[width=\linewidth]{figs/overview.pdf}
-  \vspace{-6mm}
+  \includegraphics[width=0.85\linewidth]{figs/overview.pdf}
+  \vspace{-2mm}
   \caption{\OverviewFigCaption}
@@
 \emph{Specification- and Syntax-based Linguistic Capability Testing
-  (\tool{})}, that automatically generates test cases with oracles to assess the quality of sentiment analysis models. \tool{} addresses all three challenges discussed in Section~\ref{sec:intro}.
+  (\tool{})}, which automatically generates test cases with oracles to assess the quality of NLP models.
+%   \tool{} addresses the challenges discussed in Section~\ref{sec:intro}. \sw{Revisit overview part of this section when intro is revised (see if these three challenges are still listed).}
 
@@
 %   design choices (e.g., why we do the differentiation).}
-Figure~\ref{fig:overview} shows the overview of \tool{}, which
+Figure~\ref{fig:overview} depicts an overview of \tool{}, which
 consists of two phases.  The \emph{specification-based seed
@@
 transformation templates (e.g., negating a sentence) are defined in the \emph{\lc
-  specifications} (Table~\ref{tab:specification}), which result in seed sentences that are most likely to conform
-to a specific \lc ({\bf C2}) and is labelled
-correctly ({\bf C3}).
+  specifications} (Table~\ref{tab:specification}). Using the specification will result in seed sentences that are most likely to conform
+to a specific \lc and is labelled
+correctly.
 
 The \emph{syntax-based \sent expansion} phase expands the seed
-\sents with additional syntactic elements (i.e., words) to cover many real-world
-syntactic structures ({\bf C1}). It first performs a syntax analysis
+\sents with additional syntactic elements (i.e., words) to cover many more real-world
+syntactic structures. It first performs a syntax analysis
 to identify the \pos (PoS) tags that can be inserted to each
@@
 recommendation model (i.e., BERT \cite{devlin2019bert}) to suggest possible
-words. If a resulting \sent is validated to be consistent with the
+words.
+Finally, the resulting \sent is validated to be consistent with the
 specification which additionally defines the rules for expansion
-(e.g., the expanded word should be \neu), {\bf C2} and {\bf C3} are
-still satisfied.
+(e.g., the expanded word should be \neu).
 % Last, because some validated \sents may include
@@
 \subsection{Specification-based Seed Generation}
-The seed generation phase of \tool starts by searching \sents in a
-real-world dataset that match the rules defined in the \lc
+The seed generation phase of \tool starts by searching \sents in a real-world dataset, which match the rules defined in the \lc
 specification, and then transforming the matched \sents using
 templates to generate seed \sents that conform to individual
-\lcs. The reasons for this design choice are twofold.  First, while
-generally judging which \lc any \sent falls into and which label it
-should have is infeasible, there exist simple rules and templates to
-allow classifying the resulting \sents into individual \lcs and
+\lcs. The reasons for this design choice are twofold.  First, while it is generally infeasible to judge which \lc any \sent falls into and which label it
+should have, there exist simple rules and templates that 
+allow for classifying the resulting \sents into individual \lcs and
 with the correct labels, with high confidence.  This enables us to
@@
 \lc, thus detecting more errors.
-%
-In this phase, \tool first searches and selects \sents applicable to
-the \lc in a given real-world dataset with search rules. In case that
-the search rules only fulfill portion of the \lc specifications, the
-selected \sents are not yet ready to be used as seeds, we
+
+Specifically, \tool first searches and selects \sents applicable to
+the \lc in a given real-world dataset with search rules. In case
+the search rules only fulfill part of the \lc specifications (i.e., LC3-LC10 in Table \ref{tab:specification}), we then
 transform the selected \sents into seed \sents using the
 heuristic templates.
-%
+
 Table~\ref{tab:specification} shows the search rules and the
-transformation templates of all 11 linguistic capabilities we
+transformation templates of all 10 linguistic capabilities we
 implemented in \tool. The first column shows the \lc type and its
@@
 transformation because the search rules alone are sufficient to find sentences that conform
-to the \lcs. On the other hand, search rules of LC3 to LC11 are not enough to match their \lc specification; thus, \tool additionally uses 
+to the \lcs. On the other hand, search rules of LC3 to LC10 are not enough to match their \lc specification; thus, \tool additionally uses 
 templates to transform the searched \sents to match the corresponding \lc. For example, in LC3's transformation template, the searched \sents are appended as part of a sentence to generate a seed.
@@
 
-For each production of in each seed's parse tree (lines 3 and 4), we
+For each production in each seed's parse tree (lines 3 and 4), we
 extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
@@
   \centering
-  \includegraphics[scale=0.7]{figs/running_example.pdf}
+  \includegraphics[scale=0.6]{figs/running_example.pdf}
   \vspace{-5mm}
@@
 
-\paragraph{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
+\paragraph*{Running example.} Figure~\ref{fig:ExpEx} shows an example using Algorithm \ref{alg:diff}
 to generate a masked \sent. The \sent ``Or both." is a seed of the \lc of
 \SareqExOne.  The tree on the left shows the parse tree of this seed;
-it consists of two productions: ``FRAG->[CC, NP, .]" and ``NP->[DT]".
+it consists of two productions: $``FRAG\rightarrow[CC, NP, .]"$ and $``NP\rightarrow[DT]"$.
 When matching the left-hand-side non-terminal of the second production
-(i.e., ``NP") in the reference CFG, we found that it includes a
-production ``NP->[DT, NNS]" which has an additional symbol ``NNS" on
+(i.e., $``NP"$) in the reference CFG, we found that it includes a
+production $``NP\rightarrow[DT, NNS]"$ which has an additional symbol ``NNS" on
 the right-hand-side.  The algorithm thus expands the parse tree with
@@
 token according to its surrounding context in a \sent. For each masked
-token, multiple words are suggested, ranked by their confidence scores.
+token, multiple words may be suggested, ranked by their confidence scores.
 % \sw{Algorithm 1 does not require we only have one mask in the masked
@@
 expanded symbol in the parse tree. For the example in
-Figure~\ref{fig:ExpEx}, the masked symbol is a ``NNS" (i.e., plural
-noun); thus, the suggested word must also be a ``NNS". We use \spacy \cite{spacy}, a free open-source library for \nlp, to extract the PoS
+Figure~\ref{fig:ExpEx}, the masked symbol is a $``NNS"$ (i.e., plural
+noun); thus, the suggested word must also be a $``NNS"$. We use \spacy \cite{spacy}, a free open-source library for \nlp, to extract the PoS
 tag for each suggested word.
-
-Second, it is required that the
-sentiment of the expanded \sent is the same as the seed \sent. To
-ensure this, the suggested words must be \neu.
-
+Second, the
+sentiment of the expanded \sent must be the same as the seed \sent. To
+ensure this, we require the suggested words be \neu. 
 Third, we additionally verify that the
 expanded \sents satisfy the same search rules for the seed
-\sent in LC1 and LC2. This criteria cannot be applied to other linguistic capabilities because they have additional transformation templates.
+\sents in LC1 and LC2. This criteria cannot be applied to other linguistic capabilities because they have additional transformation templates.
 
@@
 
-\paragraph{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
+\paragraph*{Running example.} The third step in Figure~\ref{fig:ExpEx} shows the words suggested
 by BERT. For this masked \sent, BERT suggested six words. Each word
@@
 are validated by \tool{} because they have the Pos tag ``NNS'' and are
-\neu. In addition, it is found that both \sents meets the search
-rule of the associated \lc of \SareqExOne. In the end, two \sents
-of ``Or both ways'' and ``Or both things'' are generated.
+\neu. In addition, both \sents still meet the search
+rule of the associated \lc of \SareqExOne. In the end,  the syntax-based sentence expansion results in two \sents, ``Or both ways.'' and ``Or both things.'', from the seed ``Or both.".
 

### 2022-09-02 paper/icse23/background.tex
icse23 submission latex

@@
 
-%% \sw{We should motivate the testing of linguistic capabilities. Give
-%%   background of the work that has been done in CheckList: what
-%%   capabilities they support and their limitations. Maybe find a
-%%   motivating example?}
-
-In this section, we provide a brief background of \Cklst's approach of test case generation
+In this section, we provide a brief background of \Cklst's \cite{marcoACL2020checklist} approach of test case generation
  via an example.
@@
 each \lc. It assumes that the linguistic phenomena can be represented
-in the behavior of the model under test, because each linguistic capability specifies the desired behavior between inputs and outputs. For each \lc, \Cklst creates
+in the behavior of the model under test, because each linguistic capability specifies the desired behavior between model inputs and outputs. For each \lc, \Cklst manually creates
 test case templates and generates sentences by filling in the values of
@@
 
-We show an example of \Cklst templates in
-Figure~\ref{code:TempEx}. These templates are used for
-evaluating a \sa model on the linguistic capability of \SareqExThree.
-For the templates defined
-from lines~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}, they
-have placeholders such as ${it}$, ${air\_noun}$, ${pos\_adj}$. Values
-for the placeholders are defined at
-line~\ref{code:tempex:airnoun:1},~\ref{code:tempex:posadj:1} and~\ref{code:tempex:itbe}, .
-For each template, \Cklst fills in all the combinations of the
-values of placeholders, and
-the sentences such as ``The flight is good'', ``That
-airline was happy'' are generated. These sentences are used for the evaluation
-of the \lc.
-
-Despite its simplicity of test case generation, \Cklst has
-limitations. First, it relies on manual work for defining template
-structure and its placeholder values making the test case
-generation a costly process. Moreover, such
-manual work generates the limited number of templates and produces high similarity between test cases, and induces bias in the test cases. These limitations motivated the design of our approach.
-
-\begin{figure}[hbp!]
+\begin{figure}[t]
  \centering
- \lstinputlisting[language=python-pretty]{code/checklist_template.py}
+ \lstinputlisting[language=python-pretty]{code/checklist_template2.py}
  \vspace{-10pt}
@@
 \end{figure}
+
+We show an example of \Cklst templates in
+Figure~\ref{code:TempEx}. These templates are used for
+evaluating the \sa model on the linguistic capability of \SareqExThree.
+For the templates defined
+at lines~\ref{code:tempex:template:1} to \ref{code:tempex:template:2}, they
+have placeholders such as ${it}$, ${air\_noun}$, ${pos\_adj}$. Values
+for the placeholders are defined at
+lines~\ref{code:tempex:airnoun:1} to~\ref{code:tempex:negadj:2}.
+For each template, \Cklst fills in all the combinations of the
+values of placeholders to generate sentences under this \lc.
+For example, sentences such as ``The flight is good'' and ``That
+airline was happy'' are generated using the template at line 10.
+
+Despite the simple approach used for test case generation, \Cklst has
+limitations. First, it relies on manual work for defining template
+structure and its placeholder values, making the test case
+generation a costly process. Moreover, such
+manual work generates a limited number of templates, produces similar test cases, and induces bias in the test cases. These limitations motivated the design of our approach.

### 2022-09-02 paper/icse23/related.tex
icse23 submission latex

@@
 %
-With the increasing use of NLP models, evaluation of NLP models is
-becoming a more important issue. Apart from the accuracy-based testing
+% With the increasing use of NLP models, evaluation of NLP models is
+% becoming a more important issue. 
+Apart from the accuracy-based testing
 scheme, recent works have considered model robustness as an
 aspect for evaluation. Belinkov and Bisk
-\textit{\etal}~\cite{belinkov2018breaknmt} aimed to fail neural machine
-translation model by intentionally introducing noise in the input
+\textit{\etal}~\cite{belinkov2018breaknmt} aimed to fail Neural Machine
+Translation (NMT) model by intentionally introducing noise in the input
 text. Pinjia
 \textit{\etal}~\cite{pinjia2020structinvtestingnmt,pinjia2020testnmtrt}
-measured the robustness by assuming syntactic and semantic relation
-between input and output of neural machine translation model.  Ribeiro
+measured the robustness of NMT model by assuming syntactic and semantic relation between input and output. Ribeiro
 \textit{\etal}~\cite{ribeiro2018sear} proposed an approach to
-generalize semantically equivalent adversarial rules. In addition,
-Rychalska \textit{\etal}~\cite{rychalska2019wildnlp} measured drops in
-BLEU scores by corruption operation, and compared model robustness
+generalize semantically equivalent adversarial rules. Rychalska \textit{\etal}~\cite{rychalska2019wildnlp} measured drops in
+BLEU by corruption operation, and compared model robustness
 based on the amount of the drops. Iyyer
@@
 \textit{\etal}~\cite{ribeiro2019consistencyeval} measured logical
-consistency of NLP model. These techniques evaluate the robustness of
-the NLP model. However, we focused on the evaluation of model capability
-over multiple perspectives and produce debugging information by comparing
-seed and expanded test cases.
+consistency of NLP model. However, in this work, we focused on the model evaluation over multiple perspectives and produced debugging information by comparing seed and expanded test cases.
+
+\MyPara{Text Generation}
+%
+Different data augmentation approaches have been proposed for text generation.
+One of methods in this category is easy data augmentation (EDA)~\cite{weizou2019eda}.
+It uses simple operations such as synonym replacement and random swap.
+Coulombe~\cite{coulombe2018textaugapi} implements rule-based transformations using regular expressions for text transformations such as insertion of spelling mistakes, data alterations, entity names, and abbreviations.
+Mixup interpolation, which was introduced in computer vision category, was implemented in text domain~\cite{hongyu2019dataaugmixup}.
+Learning-based language models has been used to generate text data for multiple tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}.
+While these approaches focus on obtaining synthetic training data, not testing NLP model over \lcs,
+% they are not able to be used for the capability testing of the NLP model, 
+our work generates text data for testing NLP model over \lcs.
 
@@
 Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} proposed
-multiple diagnostic datasets to evaluate NLP models. These datasets
-evaluate NLP model's ability to understand input sentence via natural
-language inference problems. More recently, \Cklst proposed an evaluation
+multiple diagnostic datasets to evaluate NLP models 
+% . These datasets
+% evaluate NLP model's ability to understand input sentence
+via natural language inference problems. More recently, \Cklst proposed an evaluation
 method of input-output behavior defined as \lcs. \Cklst generates
@@
 is useful for identifying the sources of model failure as shown in RQ4.
+
+% [1] Li Z, Ma X, Xu C, et al.
+Structural coverage criteria for neural networks could be misleading[C]//2019 IEEE/ACM 41st International Conference on Software Engineering: New Ideas and Emerging Results (ICSE-NIER).
+IEEE, 2019: 89-92.
+
+% [2] Harel-Canada F, Wang L, Gulzar M A, et al.
+Is neuron coverage a meaningful measure for testing deep neural networks?[C]//Proceedings of the 28th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.
+2020: 851-862.
+
+% [3] Yan S, Tao G, Liu X, et al.
+Correlations between deep neural network model coverage criteria and model quality[C]//Proceedings of the 28th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering.
+2020: 775-787.
+
+% [4] Chen J, Yan M, Wang Z, et al. Deep neural network test coverage: How far are we?[J]. arXiv preprint arXiv:2010.04946, 2020.
+% [5] Xie Q, Dai Z, Hovy E, et al. Unsupervised data augmentation for consistency training[J]. Advances in Neural Information Processing Systems, 2020, 33: 6256-6268.
+
+% [6] Coulombe C. Text data augmentation made simple by leveraging nlp cloud apis[J]. arXiv preprint arXiv:1812.04718, 2018.
+
+% [7] Wei J, Zou K. Eda: Easy data augmentation techniques for boosting performance on text classification tasks[J]. arXiv preprint arXiv:1901.11196, 2019.
+
+% [8] Guo H, Mao Y, Zhang R. Augmenting data with mixup for sentence classification: An empirical study[J]. arXiv preprint arXiv:1905.08941, 2019.
+
+% [9] Anaby-Tavor A, Carmeli B, Goldbraich E, et al. Do not have enough data? Deep learning to the rescue![C]//Proceedings of the AAAI Conference on Artificial Intelligence. 2020, 34(05): 7383-7390.

### 2022-09-02 paper/icse23/result.tex
add icse
icse23 submission latex

--- 2022-06-07 paper/ase22/result.tex
@@
 
-This section presents experiment results and answer the RQs by
-studying the results quantitatively and qualitatively.
+This section presents the experimental results and the answers to the RQs. More results are available at https://github.com/csresearcher27/s2lct$\_$project.
 
-\InputWithSpace{tables/test-results-table}
+% \InputWithSpace{tables/test-results-table}
+\InputWithSpace{tables/test-results-3-50-table}
+% \InputWithSpace{tables/test-results-3-100-table}
+% \InputWithSpace{tables/test-results-3-200-table}
 
-\subsection{RQ1: Test Suite Diversity}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.35\textwidth]{figs/pdr-selfbleu-agg-lineplot.eps}
+    \caption{\PdrSelfbleuFigCaption}
+\end{figure}
 
-Our experimental results show that \emph{\tool generated many test cases that the sentiment analysis models failed to predict the correct labels, and it produced significantly more diverse test cases than \Cklst did.}
+% \begin{figure}%
+%     \centering
+%     \includegraphics[width=0.35\textwidth]{figs/pdr-agg-lineplot.eps}
+%     \caption{\PdrFigCaption}
+% \end{figure}
 
-Table~\ref{table:TestResult} shows the testing results of three \sa models. First column lists 
-linguistic capabilities for the \sa task, and Columns 2-3 show 
-the numbers of seed and expanded test cases, respectively. 
-Columns 4-5 show the failure rate (i.e., percentage of test cases that a model predicts incorrect label) of each \sa models on the seed and expanded test cases respectively. 
-Column 6 shows the number of expanded test cases that failed,
-but their corresponding seed test cases passed.
+% \begin{figure}%
+%     \centering
+%     \subfloat[][\centering\SelfbleuFigCaption]{\includegraphics[width=0.35\textwidth]{figs/selfbleu-agg-sample-lineplot.eps}}%
+%     \qquad
+%     \subfloat[][\centering\PdrFigCaption]{\includegraphics[width=0.35\textwidth]{figs/pdr-agg-lineplot.eps}}
+%     \caption{\FailModelsFigCaption}
+% \end{figure}
 
-We observe that in all but one linguistic capabilities,
-\tool produces hundreds of test cases, expanding at least an order of magnitude more test cases than the seeds.
-LC3 is an outlier; the 50 randomly selected
-seeds in this linguistic capability did not produce any validated
-expansions.
-LC1 and LC5 have 19 and 26 seeds,
-respectively. This means that \tool's search rules and transformation templates of these two linguistic capabilities produced few seeds.
-Nevertheless, the syntax-base sentence expansion phase allows generation of 210 and 1009 test cases, respectively.
+\begin{figure}%
+    \centering
+    \includegraphics[width=0.35\textwidth]{figs/pdr-ours-50seeds-barplot.eps}
+    \caption{\PdrBarplotFigCaption}
+\end{figure}
 
-In terms of \sa model performance, all
-three models achieve low failure rates in LC9 and LC2 while the failure rates are high in all other linguistic capabilities (26\%-100\%).
-We also observe that there are significant number of expanded test cases that failed, but their corresponding seeds did not (last column in Table \ref{table:TestResult}).
+\begin{figure}%
+    \centering
+    \includegraphics[width=0.35\textwidth]{figs/numfail-pass2fail-agg-lineplot.eps}
+    \caption{\FailModelsFigCaption}
+\end{figure}
+
+% \begin{figure}%
+%     \centering
+%     \subfloat[][\centering\NumFailModelsSubFigCaption]{\includegraphics[width=0.35\textwidth]{figs/numfail-agg-lineplot.eps}}%
+%     \qquad
+%     \subfloat[][\centering\FailRateModelsSubFigCaption]{\includegraphics[width=0.35\textwidth]{figs/pass2fail-agg-lineplot.eps}}
+%     \caption{\FailModelsFigCaption}
+% \end{figure}
+
+\subsection{RQ1: Test Case Diversity}
+
+Our results show that \emph{\tool generated many test cases that the sentiment analysis models failed to predict the correct labels, and it produced significantly more diverse test cases than \Cklst did.}
+
+\paragraph*{\selfbleu} Left in Figure~\ref{fig:PdrSelfbleu} compares the \selfbleu scores between \tool seed sentences and \Cklst test cases.
+The x-axis shows sizes of random samples of \tool seeds and \Cklst test cases, and y-axis shows the \selfbleu scores.
+% Median value of \selcbleu scores are computed from randomly sampled seeds over 3 trials for each \lc,
+Median of the \selfbleu scores over all \lcs is shown in left in figure \ref{fig:PdrSelfbleu}.
+We observe that \selfbleu scores of \Cklst test cases is significantly higher than those of \tool seeds, for all numbers of seeds.
+This result indicates \Cklst test cases are less diverse than \tool seeds, which demonstrates the benefit of searching from a real-world search dataset over creating test cases from limited number of preset templates.
+% From the figure, we can observe that seed generation step in \tool generates more diverse text sentences than \Cklst.
+
+\paragraph*{\Pdr} Right in figure~\ref{fig:PdrSelfbleu} compares \pdr between the \tool seed sentences, \tool seed and expanded sentences, and the \Cklst test cases.
+The x-axis shows the sizes of random samples of \tool seed sentences, \tool seed and expanded sentences, and \Cklst test cases, and y-axis shows the \pdr scores.
+Median of the \pdr scores over all \lcs is shown in the right in the figure~\ref{fig:PdrSelfbleu}.
+The figure \ref{fig:PdrSelfbleu} shows that \tool seed and/or expanded sentences produce significantly higher \pdr scores than \Cklst test cases did.
+Also, more \tool seeds cover more production rules.
+
+Figure~\ref{fig:PdrBarplot} compares the \pdr between 50 \tool seeds and all \Cklst test cases for each \lc. The x-axis shows each one \lc, and the y-axis is the \pdr for these test cases.
+% \tool test cases are generated from randomly selected 50 seeds, and the median value over 3 trials for each \lc is reported.
+% It is observed that \tool covers significantly higher number of different syntactic production rules than \Cklst for all \lcs.
+We observed that even with only 50 seeds in each \lc, \tool seeds cover significantly higher number of production rules than all \Cklst test cases (ranging from 95 for LC1 to 367 for LC6 for \tool seeds and from 13 for LC1 to 44 for LC3 for \Cklst seeds) in each \lc.
+% (ranging from 4.92 times to 20.38 times higher scores for LC7 and LC6 respectively)
+
+Overall, the above results show that \tool test cases are significantly more diverse in terms of syntactic structure than \Cklst.
+
+\paragraph*{Model Test Results} Table~\ref{table:TestResult} shows the testing results of the three NLP models on \tool test cases using 50 seeds.
+First column lists linguistic capabilities for the \sa task, and Column 2 shows the numbers of seed test cases, and Column 3 shows the median numbers of expanded test cases over 3 trials.
+Columns 4 and 5 show the median numbers of failed test cases and the failure rates (i.e., percentage of test cases that a model predicts incorrect labels) of each NLP models on the seed and expanded test cases over the 3 trials, respectively.
+Column 6 shows the median number of expanded test cases that failed, but their corresponding seed test cases passed over the 3 trials(\Ptf).
+We observe that in all \lcs, \tool produces hundreds of test cases, expanding at least an order of magnitude more test cases than the seeds.
+LC1 and LC5 have 19 and 26 seeds, respectively.
+This is because \tool's search rules and transformation templates of these two linguistic capabilities produced few seeds.
+Nevertheless, the syntax-base sentence expansion phase generated of 224 and 1090 test cases, respectively.
+In terms of model performance, all three models achieve low failure rates in LC2 and LC9 while the failure rates are high in all other linguistic capabilities (13.52\%-99.95\%).
+We also observe that there are many expanded test cases that failed, but their corresponding seeds did not (last column).
 This shows that the syntax-based sentence expansion phase indeed introduces more diverse sentence structures in the test cases that cause the models to fail.
-% It finally
-% shows usefulness of \tool since the different test results between
-% seed and expanded cases provide accurate guidance for debugging model.
+
+In addition, Figure~\ref{fig:FailModels} shows the numbers of fail and pass-to-fail cases with different number of seeds used.
+We observed that more \tool seeds introduce more failed cases and more \Ptf cases, demonstrating the benefit of using more seeds when resource permits.
 
@@
 
-\subsection{RQ4: Use \tool for Understanding Errors}
+\section{Application of \tool}
+% \item \label{rq:four}: \textbf{Usefulness of Test Inputs.}
+
+In this section, we use one case study to show  \tool can be useful to help developers to find root causes of bugs in the \sa models.
 
@@
     \centering
-    \includegraphics[width=0.99\textwidth]{figs/explain.pdf}
+    \includegraphics[width=0.8\textwidth]{figs/explain.pdf}
     \vspace{-4mm}
@@
 
-Recall our RQ4 is to generate a template that will dominate the NLP model prediction to assist developers in understanding the false predictions.
-Figure \ref{fig:explain} shows the generated templates for two randomly selected seed inputs and corresponding generated test inputs.
-The first example is to test ``sentiments in (question, yes) form'' (LC9), and the second example is to test ``negative positive with neutral content in the middle''  (LC7).
-The first column contains the seed sentence, the second contains the generated sentence, and the third contains thCT  of each token's contribution score.
-The blue bar indicates thxe score for seed inputs, whereas the orange bar reflects the score f CTor created sentences.
+\MyPara{Experimental Process}
+we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
+Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input).
+Still, it is unclear why mutating one token will cause the model to produce misclassified results.
+We seek to help developers understand why such mutation will result in the misclassification. 
+Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences).
+Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.
+
+Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
+The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
+\begin{equation}
+    P(f(T(x)) = f(x)) \ge P_{thresh}
+    \label{eq:prob}
+\end{equation}
+To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}.
+We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
+We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
+Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$.
+Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).
+
+\MyPara{Results} We generate a template that dominates the NLP model prediction to assist developers in understanding the false predictions.
+Figure \ref{fig:explain} shows the generated templates for two randomly selected seeds and their corresponding expanded test inputs.
+The first example tests ``sentiments in (question, yes) form'' (LC9), and the second example tests ``negative positive with neutral content in the middle''  (LC7).
+The first column shows the seed sentence, the second shows the expanded sentence, and the third shows each token's contribution score.
+The blue bar indicates the score for seed inputs, whereas the orange bar reflects the score for the expanded sentences.
 We highlight the mutated token with yellow background and generated templates with red text.
@@
 The results show that after mutating the seed sentence with one token, the token set that dominates the NLP model prediction has changed.
-We can trace the root causes to the bias of training data on the \lc under test; as a result, for the \lc under test, the model has a bias towards positive/negative for certain token sequence patterns.
-For example, \lc 9 has a bias toward the token sequence pattern that includes "maybe ....
+We can trace the root causes to the bias of the training data on the \lc under test; as a result, for the \lc under test, the model has a bias towards positive/negative for certain token sequence patterns.
+For example, LC9 has a bias toward the token sequence pattern that includes "maybe ....
 but ...
@@
 yes".
-Thus, adding the token "even" to the seed sentence will match one of those biased sequence patterns.
-Sentences with s.8gmxuin the training dataset are dominantly positive, thus the models makes the wrong decision on the sentence with ``even'' as positive. 
-The visualization of each token's contribution score in the third column also confirms our observation.
+Thus, adding the token ``even" to the seed sentence will match one of those biased sequence patterns.
+Sentences with such pattern in the training dataset are dominantly positive; thus, the models make the wrong decision on the sentence with ``even'' as positive. 
+The visualization of each token's contribution score in the third column confirms our observation.
 Once ``even'' is added, scores of other tokens such as ``but'' and ``yes'' all change from negative to positive.
-To fix the issue for LC9, we ne ed to add more training negative samples with the 还 of ``maybe . .. but ... even ... yes''.
+To fix the issue for LC9, we need to add more negative training samples with the format of ``maybe . .. but ... even ... yes''.
 %he experimental results in Fig. \ref{fig:explain} illustrate that \tool can help developers to understand the buggy reason of the misclassification go no在，

### 2022-09-05 paper/ase22/tables/test-results-3-50-numbers.tex
final paper

@@
 \DefMacro{test-results-3-50-lc7-num-exps-std}{277.77}
-\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-avg}{24.0}
-\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-med}{24.0}
-\DefMacro{test-results-3-50-model0-lc7-num-seed-fail-std}{5.0}
-\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-avg}{24.58}
-\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-med}{21.87}
-\DefMacro{test-results-3-50-model0-lc7-num-exp-fail-std}{3.41}
+\DefMacro{test-results-3-50-model0-lc7-num-all-fail-avg}{375.0}
+\DefMacro{test-results-3-50-model0-lc7-num-all-fail-med}{331}
+\DefMacro{test-results-3-50-model0-lc7-num-all-fail-std}{38.54}
+\DefMacro{test-results-3-50-model0-lc7-num-all-failrate-avg}{24.57}
+\DefMacro{test-results-3-50-model0-lc7-num-all-failrate-med}{21.92}
+\DefMacro{test-results-3-50-model0-lc7-num-all-failrate-std}{3.46}
 \DefMacro{test-results-3-50-model0-lc7-num-pass-to-fail-avg}{46.0}
@@
 \DefMacro{test-results-3-50-lc3-num-exps-std}{98.56}
-\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-avg}{89.33}
-\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-med}{88.0}
-\DefMacro{test-results-3-50-model0-lc3-num-seed-fail-std}{1.155}
-\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-avg}{90.63}
-\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-med}{89.87}
-\DefMacro{test-results-3-50-model0-lc3-num-exp-fail-std}{0.705}
+\DefMacro{test-results-3-50-model0-lc3-num-all-fail-avg}{1969.67}
+\DefMacro{test-results-3-50-model0-lc3-num-all-fail-med}{1907}
+\DefMacro{test-results-3-50-model0-lc3-num-all-fail-std}{105.065}
+\DefMacro{test-results-3-50-model0-lc3-num-all-failrate-avg}{90.6}
+\DefMacro{test-results-3-50-model0-lc3-num-all-failrate-med}{89.83}
+\DefMacro{test-results-3-50-model0-lc3-num-all-failrate-std}{0.715}
 \DefMacro{test-results-3-50-model0-lc3-num-pass-to-fail-avg}{60.33}
@@
 \DefMacro{test-results-3-50-lc4-num-exps-std}{8.78}
-\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-avg}{92.31}
-\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-med}{92.31}
-\DefMacro{test-results-3-50-model0-lc4-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-avg}{93.04}
-\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-med}{93.02}
-\DefMacro{test-results-3-50-model0-lc4-num-exp-fail-std}{0.035}
+\DefMacro{test-results-3-50-model0-lc4-num-all-fail-avg}{1039.67}
+\DefMacro{test-results-3-50-model0-lc4-num-all-fail-med}{1039}
+\DefMacro{test-results-3-50-model0-lc4-num-all-fail-std}{8.005}
+\DefMacro{test-results-3-50-model0-lc4-num-all-failrate-avg}{93.02}
+\DefMacro{test-results-3-50-model0-lc4-num-all-failrate-med}{93.01}
+\DefMacro{test-results-3-50-model0-lc4-num-all-failrate-std}{0.035}
 \DefMacro{test-results-3-50-model0-lc4-num-pass-to-fail-avg}{62.67}
@@
 \DefMacro{test-results-3-50-lc6-num-exps-std}{56.69}
-\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-avg}{84.67}
-\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-med}{88.0}
-\DefMacro{test-results-3-50-model0-lc6-num-seed-fail-std}{3.785}
-\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-avg}{88.51}
-\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-med}{89.86}
-\DefMacro{test-results-3-50-model0-lc6-num-exp-fail-std}{4.55}
+\DefMacro{test-results-3-50-model0-lc6-num-all-fail-avg}{1026.33}
+\DefMacro{test-results-3-50-model0-lc6-num-all-fail-med}{934}
+\DefMacro{test-results-3-50-model0-lc6-num-all-fail-std}{81.265}
+\DefMacro{test-results-3-50-model0-lc6-num-all-failrate-avg}{88.35}
+\DefMacro{test-results-3-50-model0-lc6-num-all-failrate-med}{89.86}
+\DefMacro{test-results-3-50-model0-lc6-num-all-failrate-std}{4.5}
 \DefMacro{test-results-3-50-model0-lc6-num-pass-to-fail-avg}{8.0}
@@
 \DefMacro{test-results-3-50-lc5-num-exps-std}{128.42}
-\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-avg}{99.33}
-\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-med}{100.0}
-\DefMacro{test-results-3-50-model0-lc5-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-avg}{99.73}
-\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-med}{99.94}
-\DefMacro{test-results-3-50-model0-lc5-num-exp-fail-std}{0.205}
+\DefMacro{test-results-3-50-model0-lc5-num-all-fail-avg}{1523.0}
+\DefMacro{test-results-3-50-model0-lc5-num-all-fail-med}{1384}
+\DefMacro{test-results-3-50-model0-lc5-num-all-fail-std}{129.575}
+\DefMacro{test-results-3-50-model0-lc5-num-all-failrate-avg}{99.72}
+\DefMacro{test-results-3-50-model0-lc5-num-all-failrate-med}{99.95}
+\DefMacro{test-results-3-50-model0-lc5-num-all-failrate-std}{0.22}
 \DefMacro{test-results-3-50-model0-lc5-num-pass-to-fail-avg}{0.0}
@@
 \DefMacro{test-results-3-50-lc9-num-exps-std}{121.215}
-\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-avg}{76.67}
-\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-med}{80.0}
-\DefMacro{test-results-3-50-model0-lc9-num-seed-fail-std}{3.785}
-\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-avg}{75.51}
-\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-med}{79.39}
-\DefMacro{test-results-3-50-model0-lc9-num-exp-fail-std}{3.86}
+\DefMacro{test-results-3-50-model0-lc9-num-all-fail-avg}{1174.67}
+\DefMacro{test-results-3-50-model0-lc9-num-all-fail-med}{1181}
+\DefMacro{test-results-3-50-model0-lc9-num-all-fail-std}{135.78}
+\DefMacro{test-results-3-50-model0-lc9-num-all-failrate-avg}{75.54}
+\DefMacro{test-results-3-50-model0-lc9-num-all-failrate-med}{79.46}
+\DefMacro{test-results-3-50-model0-lc9-num-all-failrate-std}{3.855}
 \DefMacro{test-results-3-50-model0-lc9-num-pass-to-fail-avg}{38.33}
@@
 \DefMacro{test-results-3-50-lc2-num-exps-std}{34.065}
-\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-avg}{14.0}
-\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-med}{12.0}
-\DefMacro{test-results-3-50-model0-lc2-num-seed-fail-std}{3.605}
-\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-avg}{15.77}
-\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-med}{13.7}
-\DefMacro{test-results-3-50-model0-lc2-num-exp-fail-std}{5.195}
+\DefMacro{test-results-3-50-model0-lc2-num-all-fail-avg}{251.0}
+\DefMacro{test-results-3-50-model0-lc2-num-all-fail-med}{226}
+\DefMacro{test-results-3-50-model0-lc2-num-all-fail-std}{80.48}
+\DefMacro{test-results-3-50-model0-lc2-num-all-failrate-avg}{15.72}
+\DefMacro{test-results-3-50-model0-lc2-num-all-failrate-med}{13.52}
+\DefMacro{test-results-3-50-model0-lc2-num-all-failrate-std}{5.125}
 \DefMacro{test-results-3-50-model0-lc2-num-pass-to-fail-avg}{60.67}
@@
 \DefMacro{test-results-3-50-lc0-num-exps-std}{7.655}
-\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-avg}{78.95}
-\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-med}{78.95}
-\DefMacro{test-results-3-50-model0-lc0-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-avg}{87.8}
-\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-med}{88.0}
-\DefMacro{test-results-3-50-model0-lc0-num-exp-fail-std}{0.36}
+\DefMacro{test-results-3-50-model0-lc0-num-all-fail-avg}{219.0}
+\DefMacro{test-results-3-50-model0-lc0-num-all-fail-med}{213}
+\DefMacro{test-results-3-50-model0-lc0-num-all-fail-std}{7.0}
+\DefMacro{test-results-3-50-model0-lc0-num-all-failrate-avg}{87.13}
+\DefMacro{test-results-3-50-model0-lc0-num-all-failrate-med}{87.36}
+\DefMacro{test-results-3-50-model0-lc0-num-all-failrate-std}{0.34}
 \DefMacro{test-results-3-50-model0-lc0-num-pass-to-fail-avg}{17.33}
@@
 \DefMacro{test-results-3-50-lc1-num-exps-std}{42.625}
-\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-avg}{0.0}
-\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-med}{0.0}
-\DefMacro{test-results-3-50-model0-lc1-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-avg}{1.38}
-\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-med}{1.28}
-\DefMacro{test-results-3-50-model0-lc1-num-exp-fail-std}{0.25}
+\DefMacro{test-results-3-50-model0-lc1-num-all-fail-avg}{6.0}
+\DefMacro{test-results-3-50-model0-lc1-num-all-fail-med}{6}
+\DefMacro{test-results-3-50-model0-lc1-num-all-fail-std}{0.5}
+\DefMacro{test-results-3-50-model0-lc1-num-all-failrate-avg}{1.24}
+\DefMacro{test-results-3-50-model0-lc1-num-all-failrate-med}{1.16}
+\DefMacro{test-results-3-50-model0-lc1-num-all-failrate-std}{0.21}
 \DefMacro{test-results-3-50-model0-lc1-num-pass-to-fail-avg}{6.0}
@@
 \DefMacro{test-results-3-50-lc8-num-exps-std}{33.63}
-\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-avg}{4.67}
-\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-med}{4.0}
-\DefMacro{test-results-3-50-model0-lc8-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-avg}{5.87}
-\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-med}{6.67}
-\DefMacro{test-results-3-50-model0-lc8-num-exp-fail-std}{1.25}
+\DefMacro{test-results-3-50-model0-lc8-num-all-fail-avg}{79.33}
+\DefMacro{test-results-3-50-model0-lc8-num-all-fail-med}{91}
+\DefMacro{test-results-3-50-model0-lc8-num-all-fail-std}{15.12}
+\DefMacro{test-results-3-50-model0-lc8-num-all-failrate-avg}{5.82}
+\DefMacro{test-results-3-50-model0-lc8-num-all-failrate-med}{6.65}
+\DefMacro{test-results-3-50-model0-lc8-num-all-failrate-std}{1.21}
 \DefMacro{test-results-3-50-model0-lc8-num-pass-to-fail-avg}{27.33}
@@
 \DefMacro{test-results-3-50-model0-lc8-num-pass-to-fail-std}{8.605}
-\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-avg}{12.67}
-\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-med}{14.0}
-\DefMacro{test-results-3-50-model1-lc7-num-seed-fail-std}{2.08}
-\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-avg}{20.97}
-\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-med}{15.97}
-\DefMacro{test-results-3-50-model1-lc7-num-exp-fail-std}{5.215}
+\DefMacro{test-results-3-50-model1-lc7-num-all-fail-avg}{297.33}
+\DefMacro{test-results-3-50-model1-lc7-num-all-fail-med}{293}
+\DefMacro{test-results-3-50-model1-lc7-num-all-fail-std}{13.875}
+\DefMacro{test-results-3-50-model1-lc7-num-all-failrate-avg}{20.63}
+\DefMacro{test-results-3-50-model1-lc7-num-all-failrate-med}{15.92}
+\DefMacro{test-results-3-50-model1-lc7-num-all-failrate-std}{5.005}
 \DefMacro{test-results-3-50-model1-lc7-num-pass-to-fail-avg}{59.67}
@@
 \DefMacro{test-results-3-50-model1-lc7-num-pass-to-fail-std}{31.48}
-\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-avg}{86.0}
-\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-med}{84.0}
-\DefMacro{test-results-3-50-model1-lc3-num-seed-fail-std}{1.73}
-\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-avg}{88.14}
-\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-med}{87.15}
-\DefMacro{test-results-3-50-model1-lc3-num-exp-fail-std}{1.31}
+\DefMacro{test-results-3-50-model1-lc3-num-all-fail-avg}{1916.33}
+\DefMacro{test-results-3-50-model1-lc3-num-all-fail-med}{1828}
+\DefMacro{test-results-3-50-model1-lc3-num-all-fail-std}{114.34}
+\DefMacro{test-results-3-50-model1-lc3-num-all-failrate-avg}{88.09}
+\DefMacro{test-results-3-50-model1-lc3-num-all-failrate-med}{87.08}
+\DefMacro{test-results-3-50-model1-lc3-num-all-failrate-std}{1.32}
 \DefMacro{test-results-3-50-model1-lc3-num-pass-to-fail-avg}{53.67}
@@
 \DefMacro{test-results-3-50-model1-lc3-num-pass-to-fail-std}{3.685}
-\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-avg}{92.31}
-\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-med}{92.31}
-\DefMacro{test-results-3-50-model1-lc4-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-avg}{93.31}
-\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-med}{93.33}
-\DefMacro{test-results-3-50-model1-lc4-num-exp-fail-std}{0.14}
+\DefMacro{test-results-3-50-model1-lc4-num-all-fail-avg}{1042.67}
+\DefMacro{test-results-3-50-model1-lc4-num-all-fail-med}{1038}
+\DefMacro{test-results-3-50-model1-lc4-num-all-fail-std}{7.765}
+\DefMacro{test-results-3-50-model1-lc4-num-all-failrate-avg}{93.29}
+\DefMacro{test-results-3-50-model1-lc4-num-all-failrate-med}{93.31}
+\DefMacro{test-results-3-50-model1-lc4-num-all-failrate-std}{0.135}
 \DefMacro{test-results-3-50-model1-lc4-num-pass-to-fail-avg}{40.33}
@@
 \DefMacro{test-results-3-50-model1-lc4-num-pass-to-fail-std}{1.53}
-\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-avg}{74.67}
-\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-med}{74.0}
-\DefMacro{test-results-3-50-model1-lc6-num-seed-fail-std}{3.51}
-\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-avg}{73.04}
-\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-med}{70.1}
-\DefMacro{test-results-3-50-model1-lc6-num-exp-fail-std}{5.935}
+\DefMacro{test-results-3-50-model1-lc6-num-all-fail-avg}{839.33}
+\DefMacro{test-results-3-50-model1-lc6-num-all-fail-med}{831}
+\DefMacro{test-results-3-50-model1-lc6-num-all-fail-std}{23.53}
+\DefMacro{test-results-3-50-model1-lc6-num-all-failrate-avg}{73.09}
+\DefMacro{test-results-3-50-model1-lc6-num-all-failrate-med}{70.01}
+\DefMacro{test-results-3-50-model1-lc6-num-all-failrate-std}{5.795}
 \DefMacro{test-results-3-50-model1-lc6-num-pass-to-fail-avg}{30.33}
@@
 \DefMacro{test-results-3-50-model1-lc6-num-pass-to-fail-std}{14.375}
-\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-avg}{99.33}
-\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-med}{100.0}
-\DefMacro{test-results-3-50-model1-lc5-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-avg}{99.4}
-\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-med}{99.26}
-\DefMacro{test-results-3-50-model1-lc5-num-exp-fail-std}{0.2}
+\DefMacro{test-results-3-50-model1-lc5-num-all-fail-avg}{1517.33}
+\DefMacro{test-results-3-50-model1-lc5-num-all-fail-med}{1384}
+\DefMacro{test-results-3-50-model1-lc5-num-all-fail-std}{125.56}
+\DefMacro{test-results-3-50-model1-lc5-num-all-failrate-avg}{99.4}
+\DefMacro{test-results-3-50-model1-lc5-num-all-failrate-med}{99.21}
+\DefMacro{test-results-3-50-model1-lc5-num-all-failrate-std}{0.2}
 \DefMacro{test-results-3-50-model1-lc5-num-pass-to-fail-avg}{0.0}
@@
 \DefMacro{test-results-3-50-model1-lc5-num-pass-to-fail-std}{0.0}
-\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-avg}{78.0}
-\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-med}{78.0}
-\DefMacro{test-results-3-50-model1-lc9-num-seed-fail-std}{5.0}
-\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-avg}{78.77}
-\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-med}{82.92}
-\DefMacro{test-results-3-50-model1-lc9-num-exp-fail-std}{5.985}
+\DefMacro{test-results-3-50-model1-lc9-num-all-fail-avg}{1225.33}
+\DefMacro{test-results-3-50-model1-lc9-num-all-fail-med}{1117}
+\DefMacro{test-results-3-50-model1-lc9-num-all-fail-std}{166.975}
+\DefMacro{test-results-3-50-model1-lc9-num-all-failrate-avg}{78.74}
+\DefMacro{test-results-3-50-model1-lc9-num-all-failrate-med}{82.74}
+\DefMacro{test-results-3-50-model1-lc9-num-all-failrate-std}{5.94}
 \DefMacro{test-results-3-50-model1-lc9-num-pass-to-fail-avg}{20.0}
@@
 \DefMacro{test-results-3-50-model1-lc9-num-pass-to-fail-std}{10.21}
-\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-avg}{52.0}
-\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-med}{50.0}
-\DefMacro{test-results-3-50-model1-lc2-num-seed-fail-std}{1.73}
-\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-avg}{46.53}
-\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-med}{43.06}
-\DefMacro{test-results-3-50-model1-lc2-num-exp-fail-std}{4.615}
+\DefMacro{test-results-3-50-model1-lc2-num-all-fail-avg}{744.33}
+\DefMacro{test-results-3-50-model1-lc2-num-all-fail-med}{723}
+\DefMacro{test-results-3-50-model1-lc2-num-all-fail-std}{71.105}
+\DefMacro{test-results-3-50-model1-lc2-num-all-failrate-avg}{46.7}
+\DefMacro{test-results-3-50-model1-lc2-num-all-failrate-med}{43.27}
+\DefMacro{test-results-3-50-model1-lc2-num-all-failrate-std}{4.525}
 \DefMacro{test-results-3-50-model1-lc2-num-pass-to-fail-avg}{37.0}
@@
 \DefMacro{test-results-3-50-model1-lc2-num-pass-to-fail-std}{8.41}
-\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-avg}{89.47}
-\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-med}{89.47}
-\DefMacro{test-results-3-50-model1-lc0-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-avg}{78.7}
-\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-med}{78.12}
-\DefMacro{test-results-3-50-model1-lc0-num-exp-fail-std}{0.75}
+\DefMacro{test-results-3-50-model1-lc0-num-all-fail-avg}{200.0}
+\DefMacro{test-results-3-50-model1-lc0-num-all-fail-med}{192}
+\DefMacro{test-results-3-50-model1-lc0-num-all-fail-std}{7.81}
+\DefMacro{test-results-3-50-model1-lc0-num-all-failrate-avg}{79.52}
+\DefMacro{test-results-3-50-model1-lc0-num-all-failrate-med}{79.01}
+\DefMacro{test-results-3-50-model1-lc0-num-all-failrate-std}{0.67}
 \DefMacro{test-results-3-50-model1-lc0-num-pass-to-fail-avg}{9.33}
@@
 \DefMacro{test-results-3-50-model1-lc0-num-pass-to-fail-std}{0.29}
-\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-avg}{2.67}
-\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-med}{2.0}
-\DefMacro{test-results-3-50-model1-lc1-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-avg}{2.8}
-\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-med}{0.94}
-\DefMacro{test-results-3-50-model1-lc1-num-exp-fail-std}{1.66}
+\DefMacro{test-results-3-50-model1-lc1-num-all-fail-avg}{14.33}
+\DefMacro{test-results-3-50-model1-lc1-num-all-fail-med}{6}
+\DefMacro{test-results-3-50-model1-lc1-num-all-fail-std}{7.655}
+\DefMacro{test-results-3-50-model1-lc1-num-all-failrate-avg}{2.81}
+\DefMacro{test-results-3-50-model1-lc1-num-all-failrate-med}{1.21}
+\DefMacro{test-results-3-50-model1-lc1-num-all-failrate-std}{1.465}
 \DefMacro{test-results-3-50-model1-lc1-num-pass-to-fail-avg}{12.0}
@@
 \DefMacro{test-results-3-50-model1-lc1-num-pass-to-fail-std}{8.23}
-\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-avg}{5.33}
-\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-med}{6.0}
-\DefMacro{test-results-3-50-model1-lc8-num-seed-fail-std}{1.53}
-\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-avg}{5.85}
-\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-med}{6.14}
-\DefMacro{test-results-3-50-model1-lc8-num-exp-fail-std}{0.93}
+\DefMacro{test-results-3-50-model1-lc8-num-all-fail-avg}{81.0}
+\DefMacro{test-results-3-50-model1-lc8-num-all-fail-med}{81}
+\DefMacro{test-results-3-50-model1-lc8-num-all-fail-std}{14.5}
+\DefMacro{test-results-3-50-model1-lc8-num-all-failrate-avg}{5.84}
+\DefMacro{test-results-3-50-model1-lc8-num-all-failrate-med}{6.14}
+\DefMacro{test-results-3-50-model1-lc8-num-all-failrate-std}{0.95}
 \DefMacro{test-results-3-50-model1-lc8-num-pass-to-fail-avg}{25.67}
@@
 \DefMacro{test-results-3-50-model1-lc8-num-pass-to-fail-std}{5.53}
-\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-avg}{32.0}
-\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-med}{24.0}
-\DefMacro{test-results-3-50-model2-lc7-num-seed-fail-std}{10.585}
-\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-avg}{31.45}
-\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-med}{33.91}
-\DefMacro{test-results-3-50-model2-lc7-num-exp-fail-std}{5.245}
+\DefMacro{test-results-3-50-model2-lc7-num-all-fail-avg}{490.67}
+\DefMacro{test-results-3-50-model2-lc7-num-all-fail-med}{420}
+\DefMacro{test-results-3-50-model2-lc7-num-all-fail-std}{98.38}
+\DefMacro{test-results-3-50-model2-lc7-num-all-failrate-avg}{31.59}
+\DefMacro{test-results-3-50-model2-lc7-num-all-failrate-med}{33.68}
+\DefMacro{test-results-3-50-model2-lc7-num-all-failrate-std}{5.43}
 \DefMacro{test-results-3-50-model2-lc7-num-pass-to-fail-avg}{50.67}
@@
 \DefMacro{test-results-3-50-model2-lc7-num-pass-to-fail-std}{15.765}
-\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-avg}{83.33}
-\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-med}{84.0}
-\DefMacro{test-results-3-50-model2-lc3-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-avg}{85.71}
-\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-med}{86.11}
-\DefMacro{test-results-3-50-model2-lc3-num-exp-fail-std}{0.64}
+\DefMacro{test-results-3-50-model2-lc3-num-all-fail-avg}{1862.0}
+\DefMacro{test-results-3-50-model2-lc3-num-all-fail-med}{1827}
+\DefMacro{test-results-3-50-model2-lc3-num-all-fail-std}{96.94}
+\DefMacro{test-results-3-50-model2-lc3-num-all-failrate-avg}{85.66}
+\DefMacro{test-results-3-50-model2-lc3-num-all-failrate-med}{86.06}
+\DefMacro{test-results-3-50-model2-lc3-num-all-failrate-std}{0.64}
 \DefMacro{test-results-3-50-model2-lc3-num-pass-to-fail-avg}{33.67}
@@
 \DefMacro{test-results-3-50-model2-lc3-num-pass-to-fail-std}{2.255}
-\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-avg}{92.31}
-\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-med}{92.31}
-\DefMacro{test-results-3-50-model2-lc4-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-avg}{95.66}
-\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-med}{95.41}
-\DefMacro{test-results-3-50-model2-lc4-num-exp-fail-std}{0.25}
+\DefMacro{test-results-3-50-model2-lc4-num-all-fail-avg}{1068.33}
+\DefMacro{test-results-3-50-model2-lc4-num-all-fail-med}{1073}
+\DefMacro{test-results-3-50-model2-lc4-num-all-fail-std}{8.735}
+\DefMacro{test-results-3-50-model2-lc4-num-all-failrate-avg}{95.59}
+\DefMacro{test-results-3-50-model2-lc4-num-all-failrate-med}{95.33}
+\DefMacro{test-results-3-50-model2-lc4-num-all-failrate-std}{0.245}
 \DefMacro{test-results-3-50-model2-lc4-num-pass-to-fail-avg}{84.0}
@@
 \DefMacro{test-results-3-50-model2-lc4-num-pass-to-fail-std}{2.29}
-\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-avg}{87.33}
-\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-med}{88.0}
-\DefMacro{test-results-3-50-model2-lc6-num-seed-fail-std}{3.51}
-\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-avg}{91.1}
-\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-med}{92.9}
-\DefMacro{test-results-3-50-model2-lc6-num-exp-fail-std}{4.19}
+\DefMacro{test-results-3-50-model2-lc6-num-all-fail-avg}{1056.0}
+\DefMacro{test-results-3-50-model2-lc6-num-all-fail-med}{972}
+\DefMacro{test-results-3-50-model2-lc6-num-all-fail-std}{76.675}
+\DefMacro{test-results-3-50-model2-lc6-num-all-failrate-avg}{90.95}
+\DefMacro{test-results-3-50-model2-lc6-num-all-failrate-med}{92.95}
+\DefMacro{test-results-3-50-model2-lc6-num-all-failrate-std}{4.125}
 \DefMacro{test-results-3-50-model2-lc6-num-pass-to-fail-avg}{4.33}
@@
 \DefMacro{test-results-3-50-model2-lc6-num-pass-to-fail-std}{1.26}
-\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-avg}{98.67}
-\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-med}{98.0}
-\DefMacro{test-results-3-50-model2-lc5-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-avg}{98.44}
-\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-med}{99.11}
-\DefMacro{test-results-3-50-model2-lc5-num-exp-fail-std}{0.99}
+\DefMacro{test-results-3-50-model2-lc5-num-all-fail-avg}{1500.0}
+\DefMacro{test-results-3-50-model2-lc5-num-all-fail-med}{1382}
+\DefMacro{test-results-3-50-model2-lc5-num-all-fail-std}{110.52}
+\DefMacro{test-results-3-50-model2-lc5-num-all-failrate-avg}{98.45}
+\DefMacro{test-results-3-50-model2-lc5-num-all-failrate-med}{99.07}
+\DefMacro{test-results-3-50-model2-lc5-num-all-failrate-std}{0.97}
 \DefMacro{test-results-3-50-model2-lc5-num-pass-to-fail-avg}{1.33}
@@
 \DefMacro{test-results-3-50-model2-lc5-num-pass-to-fail-std}{1.155}
-\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-avg}{80.67}
-\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-med}{84.0}
-\DefMacro{test-results-3-50-model2-lc9-num-seed-fail-std}{9.61}
-\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-avg}{78.54}
-\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-med}{82.31}
-\DefMacro{test-results-3-50-model2-lc9-num-exp-fail-std}{11.03}
+\DefMacro{test-results-3-50-model2-lc9-num-all-fail-avg}{1235.67}
+\DefMacro{test-results-3-50-model2-lc9-num-all-fail-med}{1112}
+\DefMacro{test-results-3-50-model2-lc9-num-all-fail-std}{251.03}
+\DefMacro{test-results-3-50-model2-lc9-num-all-failrate-avg}{78.61}
+\DefMacro{test-results-3-50-model2-lc9-num-all-failrate-med}{82.37}
+\DefMacro{test-results-3-50-model2-lc9-num-all-failrate-std}{10.985}
 \DefMacro{test-results-3-50-model2-lc9-num-pass-to-fail-avg}{13.0}
@@
 \DefMacro{test-results-3-50-model2-lc9-num-pass-to-fail-std}{7.795}
-\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-avg}{54.67}
-\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-med}{58.0}
-\DefMacro{test-results-3-50-model2-lc2-num-seed-fail-std}{2.885}
-\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-avg}{55.97}
-\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-med}{60.67}
-\DefMacro{test-results-3-50-model2-lc2-num-exp-fail-std}{4.6}
+\DefMacro{test-results-3-50-model2-lc2-num-all-fail-avg}{895.0}
+\DefMacro{test-results-3-50-model2-lc2-num-all-fail-med}{953}
+\DefMacro{test-results-3-50-model2-lc2-num-all-fail-std}{86.715}
+\DefMacro{test-results-3-50-model2-lc2-num-all-failrate-avg}{55.93}
+\DefMacro{test-results-3-50-model2-lc2-num-all-failrate-med}{60.58}
+\DefMacro{test-results-3-50-model2-lc2-num-all-failrate-std}{4.545}
 \DefMacro{test-results-3-50-model2-lc2-num-pass-to-fail-avg}{49.33}
@@
 \DefMacro{test-results-3-50-model2-lc2-num-pass-to-fail-std}{11.015}
-\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-avg}{100.0}
-\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-med}{100.0}
-\DefMacro{test-results-3-50-model2-lc0-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-avg}{95.8}
-\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-med}{95.96}
-\DefMacro{test-results-3-50-model2-lc0-num-exp-fail-std}{0.545}
+\DefMacro{test-results-3-50-model2-lc0-num-all-fail-avg}{241.67}
+\DefMacro{test-results-3-50-model2-lc0-num-all-fail-med}{233}
+\DefMacro{test-results-3-50-model2-lc0-num-all-fail-std}{8.385}
+\DefMacro{test-results-3-50-model2-lc0-num-all-failrate-avg}{96.12}
+\DefMacro{test-results-3-50-model2-lc0-num-all-failrate-med}{96.28}
+\DefMacro{test-results-3-50-model2-lc0-num-all-failrate-std}{0.495}
 \DefMacro{test-results-3-50-model2-lc0-num-pass-to-fail-avg}{0.0}
@@
 \DefMacro{test-results-3-50-model2-lc0-num-pass-to-fail-std}{0.0}
-\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-avg}{0.0}
-\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-med}{0.0}
-\DefMacro{test-results-3-50-model2-lc1-num-seed-fail-std}{0.0}
-\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-avg}{0.92}
-\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-med}{0.94}
-\DefMacro{test-results-3-50-model2-lc1-num-exp-fail-std}{0.24}
+\DefMacro{test-results-3-50-model2-lc1-num-all-fail-avg}{4.0}
+\DefMacro{test-results-3-50-model2-lc1-num-all-fail-med}{5}
+\DefMacro{test-results-3-50-model2-lc1-num-all-fail-std}{0.865}
+\DefMacro{test-results-3-50-model2-lc1-num-all-failrate-avg}{0.82}
+\DefMacro{test-results-3-50-model2-lc1-num-all-failrate-med}{0.86}
+\DefMacro{test-results-3-50-model2-lc1-num-all-failrate-std}{0.205}
 \DefMacro{test-results-3-50-model2-lc1-num-pass-to-fail-avg}{4.0}
@@
 \DefMacro{test-results-3-50-model2-lc1-num-pass-to-fail-std}{0.865}
-\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-avg}{5.33}
-\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-med}{6.0}
-\DefMacro{test-results-3-50-model2-lc8-num-seed-fail-std}{0.575}
-\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-avg}{6.76}
-\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-med}{6.07}
-\DefMacro{test-results-3-50-model2-lc8-num-exp-fail-std}{1.515}
+\DefMacro{test-results-3-50-model2-lc8-num-all-fail-avg}{91.33}
+\DefMacro{test-results-3-50-model2-lc8-num-all-fail-med}{82}
+\DefMacro{test-results-3-50-model2-lc8-num-all-fail-std}{17.96}
+\DefMacro{test-results-3-50-model2-lc8-num-all-failrate-avg}{6.7}
+\DefMacro{test-results-3-50-model2-lc8-num-all-failrate-med}{5.99}
+\DefMacro{test-results-3-50-model2-lc8-num-all-failrate-std}{1.465}
 \DefMacro{test-results-3-50-model2-lc8-num-pass-to-fail-avg}{25.33}

### 2022-09-05 paper/ase22/tables/test-results-3-50-table.tex
final paper

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-3-50-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc0-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc0-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc0-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc0-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc0-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc0-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc0-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc0-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc0-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc0-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-3-50-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc1-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc1-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc1-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc1-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc1-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc1-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc1-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc1-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc1-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc1-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-3-50-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc2-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc2-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc2-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc2-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc2-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc2-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc2-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc2-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc2-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc2-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-3-50-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc3-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc3-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc3-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc3-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc3-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc3-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc3-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc3-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc3-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc3-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-3-50-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc4-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc4-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc4-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc4-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc4-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc4-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc4-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc4-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc4-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc4-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-3-50-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc5-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc5-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc5-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc5-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc5-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc5-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc5-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc5-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc5-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc5-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-3-50-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc6-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc6-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc6-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc6-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc6-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc6-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc6-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc6-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc6-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc6-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-3-50-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc7-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc7-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc7-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc7-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc7-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc7-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc7-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc7-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc7-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc7-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-3-50-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc8-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc8-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc8-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc8-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc8-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc8-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc8-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc8-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc8-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc8-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-3-50-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-3-50-lc9-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc9-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc9-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results-3-50-model0-lc9-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc9-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc9-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results-3-50-model1-lc9-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc9-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc9-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results-3-50-model2-lc9-num-pass-to-fail-med}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-09-05 python/sa/exp/Coverage.py

@@ -151,5 +151,4 @@ class Coverage:
         Utils.write_txt(res_sst_text, sst_save_file)
         Utils.write_txt(res_checklist_text, checklist_save_file)
         return
-
     

### 2022-09-05 python/sa/paper/.#Tables_prev.py

@@ -1,1 +1,0 @@
-jasonlee@thinkpad-x1.26656:1661960624

### 2022-09-05 python/sa/paper/Plots.py

@@ -52,7 +52,9 @@ class Plots:
         # end if
 
         for item in which:
-            if item == 'selfbleu':
+            if item == 'pdr-selfbleu-agg':
+                cls.pdr_selfbleu_agg_plot(Macros.result_dir, figs_dir)
+            elif item == 'selfbleu':
                 cls.selfbleu_ours_sample_plot(Macros.result_dir, figs_dir)
                 cls.selfbleu_bl_sample_plot(Macros.result_dir, figs_dir)
                 cls.selfbleu_agg_sample_plot(Macros.result_dir, figs_dir)
@@ -63,13 +65,15 @@ class Plots:
                 cls.pdr_seed_exp_plot(Macros.result_dir, figs_dir)
                 cls.pdr_agg_plot(Macros.result_dir, figs_dir)
             elif item == 'test-results':
-                cls.failrate_combined_over_seeds_plot(Macros.result_dir, figs_dir)
+                # cls.failrate_combined_over_seeds_plot(Macros.result_dir, figs_dir)
                 # cls.failrate_seed_over_seeds_plot(Macros.result_dir, figs_dir)
                 # cls.failrate_exp_over_seeds_plot(Macros.result_dir, figs_dir)
-                cls.pass2fail_over_seeds_plot(Macros.result_dir, figs_dir)
+                # cls.pass2fail_over_seeds_plot(Macros.result_dir, figs_dir)
+                # cls.numfail_over_seeds_plot(Macros.result_dir, figs_dir)
                 cls.pass2fail_agg_over_seeds_plot(Macros.result_dir, figs_dir)
-                cls.numfail_over_seeds_plot(Macros.result_dir, figs_dir)
                 cls.numfail_agg_over_seeds_plot(Macros.result_dir, figs_dir)
+            elif item == 'numfail-pass2fail-agg':
+                cls.numfail_pass2fail_agg_over_seeds_plot(Macros.result_dir, figs_dir)
             else:
                 raise(f"Unknown plot {item}")
             # end if
@@ -543,6 +547,7 @@ class Plots:
                     # 'med': result[lc_desc]['ours']['med_score'],
                     # 'std': result[lc_desc]['ours']['std_score']
                 })
+                print(l_i+1, bl_score, result[lc_desc]['ours']['med_score'], float(result[lc_desc]['ours']['med_score'])/bl_score)
                 for score in result[lc_desc]['ours']['coverage_scores']:
[…]

### 2022-09-05 python/sa/paper/Tables_prev.py

@@ -1,742 +1,0 @@
-
-# This script is for generating all tables used in paper
-
-from typing import *
-
-import collections
-from pathlib import Path
-
-# from seutil import LoggingUtils, IOUtils
-from seutil import latex
-
-from ..utils.Macros import Macros
-from ..utils.Utils import Utils
-from ..utils.Logger import Logger
-
-
-class Tables:
-
-    METRICS = ["selfbleu", "acc", "f1"]
-    METRICS_THEADS = {
-        "selfbleu": r"\tBleu",
-        "acc": r"\tAccuracy",
-        "f1": r"\tF1-score",
-    }
-
-    FMT_INT = "{:,d}"
-    FMT_PER = "{:.1%}"
-    FMT_FLOAT = "{:,.2f}"
-
-    LATEX_SYMBOL_MAP = {
-        '&': '\&',
-        '{': '\{',
-        '}': '\}',
-        '_': '\_',
-        ' < ': ' $<$ ',
-        ' > ': ' $>$ ',
-        '|': '$|$',
-        '->': '$\\to$'
-    }
-    
-    @classmethod
-    def make_tables(cls, **options):
-        paper_dir: Path = Macros.paper_dir
-        tables_dir: Path = paper_dir / "tables"
-        tables_dir.mkdir(parents=True, exist_ok=True)
-        which = options['which']
-        
-        if not isinstance(which, list):
-            which = [which]
-        # end if
-
-        for item in which: 
-            if item == "lc-req":
-                cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
-                cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
-            # elif item == "selfbleu": # deprecated
-            #     task = options.pop('task', 'sa')
-            #     search_dataset = options.pop('search_dataset_name', 'sst')
-            #     selection_method = options.pop('selection_method', 'random')
-            #     cls.make_numbers_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
-            #     cls.make_table_selfbleu(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
-            # elif item == "retrain-debug": # deprecated
-            #     task = options.pop('task', 'sa')
-            #     search_dataset = options.pop('search_dataset_name', 'sst')
-            #     selection_method = options.pop('selection_method', 'random')
-            #     epochs = options.pop('epochs', 5)
-            #     model_name = options.pop('model_name')
[…]

### 2022-10-26 python/hs/main.py
tables hs

@@ -14,7 +14,7 @@ from .utils.Utils import Utils
 parser = argparse.ArgumentParser(description='Process some integers.')
 parser.add_argument('--run', type=str, required=True,
                     choices=[
-                        'requirement', 'template', 'testsuite', 'testmodel', 'analyze'
+                        'requirement', 'template', 'testsuite', 'testmodel', 'analyze', 'tables'
                     ], help='task to be run')
 parser.add_argument('--nlp_task', type=str, default='hs',
                     choices=['hs'],
@@ -34,6 +34,10 @@ parser.add_argument('--model_name', type=str, default=None,
                     help='name of model to be evaluated or retrained')
 parser.add_argument('--test_baseline', action='store_true',
                     help='test models on running baseline (hatecheck) test cases')
+
+# arguments for tables and plots
+parser.add_argument('--which', type=str, default=None, nargs='+',
+                    help='tables/plots that you are interested in making')
 
 args = parser.parse_args()
 rand_seed_num = Macros.RAND_SEED[args.num_trials]
@@ -170,6 +174,22 @@ def run_analyze():
     # end if
     return
 
+# ==========
+# Tables & Plots
+
+def run_make_tables():
+    from .paper.Tables import Tables
+    options = {
+        'which': args.which,
+        'task': args.nlp_task,
+        'search_dataset_name': args.search_dataset,
+        'selection_method': args.syntax_selection,
+        'num_seeds': args.num_seeds,
+        'num_trials': args.num_trials,
+    }
+    Tables.make_tables(**options)
+    return
+
 
 func_map = {
     "hs": {
@@ -177,7 +197,8 @@ func_map = {
         'template': run_templates,
         'testsuite': run_testsuites,
         'testmodel': run_testmodel,
-        'analyze': run_analyze
+        'analyze': run_analyze,
+        'tables': run_make_tables
     }
 }
 

### 2022-10-26 python/hs/paper/Tables.py

@@ -97,12 +97,11 @@ class Tables:
 
         output_file = latex.File(tables_dir / f"test-results-{task}-all-numbers.tex")
         
-        lcs = Utils.read_txt(req_file)
         lc_ids = dict()
-        for l_i, l in enumerate(lcs):
-            desc = l.split('::')[0].strip()
+        for l_i, l in enumerate(Macros.OUR_LC_LIST):
+            desc = l.split('::')[1].strip()
             lc_ids[desc.lower()] = (desc,l_i)
-            desc = cls.replace_latex_symbol(desc)
+            # desc = cls.replace_latex_symbol(desc)
             lc_descs[l_i] = desc
         # end for
 
@@ -175,35 +174,16 @@ class Tables:
                     output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-seeds",
                                                          num_seeds_tot[m_name][lc_i][0]))
 
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-exps-avg",
-                                                         Utils.avg(num_exps_tot[m_name][lc_i], decimal=2)))
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-exps-med",
-                                                         Utils.median(num_exps_tot[m_name][lc_i], decimal=2)))
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-exps-std",
-                                                         str(float(Utils.stdev(num_exps_tot[m_name][lc_i], decimal=2))/2)))
+                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-exps",
+                                                         num_exps_tot[m_name][lc_i][0]))
                 # end if
 
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{lc_i}-num-all-fail-avg",
-                                                     Utils.avg(num_all_fail[m_name][lc_i], decimal=2)))
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{lc_i}-num-all-fail-med",
-                                                     Utils.median(num_all_fail[m_name][lc_i], decimal=2)))
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{lc_i}-num-all-fail-std",
[…]

### 2022-10-26 python/hs/utils/Macros.py

@@ -10,7 +10,7 @@ class Macros:
     this_dir: Path = Path(os.path.dirname(os.path.realpath(__file__))) # s2lct/python/utils
     root_dir: Path = this_dir.parent.parent.parent # s2lct/
     # storage_dir: Path = Path('/glusterfs/data/jxl115330/s2lct')
-    storage_dir: Path = Path('/nas1-nfs1/data/jxl115330/s2lct')
+    storage_dir: Path = root_dir # Path('/nas1-nfs1/data/jxl115330/s2lct')
     result_dir: Path = storage_dir / '_results' # /glusterfs/data/jxl115330/s2lct/_results
     # result_dir: Path = root_dir / "_results" # s2lct/_results
     

### 2022-10-26 python/hs/utils/Utils.py

@@ -180,17 +180,24 @@ class Utils:
             copy.deepcopy(d)
             for d in data_list
         ]
-    
+  
     @classmethod
-    def avg(cls, nums: list):
-        return "{:.3f}".format(sum(nums) / len(nums))
+    def avg(cls, nums: list, decimal=3):
+        return str(round(sum(nums) / len(nums), decimal))
 
     @classmethod
-    def median(cls, nums: list):
-        return "{:.3f}".format(statistics.median(nums))
+    def median(cls, nums: list, decimal=3):
+        return str(round(statistics.median(nums), decimal))
 
     @classmethod
-    def stdev(cls, nums: list):
-        return "{:.3f}".format(statistics.stdev(nums))
+    def stdev(cls, nums: list, decimal=3):
+        return str(round(statistics.stdev(nums), decimal))
 
-    
+    @classmethod
+    def lod_to_dol(cls, list_of_dict: List[dict]) -> Dict[Any, List]:
+        """
+        Converts a list of dict to a dict of list.
+        """
+        keys = set.union(*[set(d.keys()) for d in list_of_dict])
+        return {k: [d.get(k) for d in list_of_dict] for k in keys}
+

### 2022-10-26 python/hs/paper/Tables.py
debug

@@ -92,9 +92,6 @@ class Tables:
         num_all_fail_rate = dict()
         num_pass2fail = dict()
 
-        req_dir = result_dir / 'reqs'
-        req_file = req_dir / 'requirements_desc.txt'
-
         output_file = latex.File(tables_dir / f"test-results-{task}-all-numbers.tex")
         
         lc_ids = dict()
@@ -170,20 +167,24 @@ class Tables:
 
             for lc_i in num_seeds_tot[m_name].keys():
                 if m_i==0:
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}", lc_descs[lc_i]))
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-seeds",
+                    output_file.append_macro(latex.Macro(f"test-results-hs-lc{lc_i}", lc_descs[lc_i]))
+                    output_file.append_macro(latex.Macro(f"test-results-hs-lc{lc_i}-num-seeds",
                                                          num_seeds_tot[m_name][lc_i][0]))
 
-                    output_file.append_macro(latex.Macro(f"test-results-lc{lc_i}-num-exps",
+                    output_file.append_macro(latex.Macro(f"test-results-hs-lc{lc_i}-num-exps",
                                                          num_exps_tot[m_name][lc_i][0]))
                 # end if
 
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{lc_i}-num-all-fail",
-                                                     num_all_fail[m_name][lc_i]))
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{lc_i}-num-all-failrate",
-                                                     num_all_fail_rate[m_name][lc_i]))
-                output_file.append_macro(latex.Macro(f"test-results-model{m_i}-lc{lc_i}-num-pass-to-fail",
-                                                     num_pass2fail[m_name][lc_i]))
+                output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-all-fail",
+                                                     num_all_fail[m_name][lc_i][0]))
+                output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-seed-failrate",
+                                                     num_seed_fail_rate[m_name][lc_i][0]))
[…]

### 2022-10-26 python/hs/seed/Search.py

@@ -483,7 +483,7 @@ class Hatecheck:
         Macros.OUR_LC_LIST[12]: 'negate_pos_h',
         Macros.OUR_LC_LIST[13]: 'negate_neg_nh',
         Macros.OUR_LC_LIST[14]: 'phrase_question_h',
-        Macros.OUR_LC_LIST[15]: 'phrase_option_h',
+        Macros.OUR_LC_LIST[15]: 'phrase_opinion_h',
         Macros.OUR_LC_LIST[16]: 'ident_neutral_nh',
         Macros.OUR_LC_LIST[17]: 'ident_pos_nh',
         Macros.OUR_LC_LIST[18]: 'counter_quote_nh',

### 2022-10-26 python/hs/utils/Macros.py

@@ -16,7 +16,7 @@ class Macros:
     
     download_dir: Path = storage_dir / '_downloads' # /glusterfs/data/jxl115330/s2lct/_downloads
     log_dir: Path = storage_dir / '_logs' # /glusterfs/data/jxl115330/s2lct/_logs
-    paper_dir = root_dir / 'paper' / 'ase22'
+    paper_dir = root_dir / 'paper' / 'icse23'
     dataset_dir = download_dir / 'datasets'
 
     FMT_INT = "{:,d}"
@@ -25,7 +25,7 @@ class Macros:
     
     RAND_SEED = {1: 27, 2: 26, 3: 28} #26(trial2), 27(trial1), 28(trial3)
     MASK = "{mask}"
-
+    
     num_processes = 3
 
     ## hate speech setting

### 2022-10-26 python/hs/paper/Tables.py
formatting

@@ -176,15 +176,15 @@ class Tables:
                 # end if
 
                 output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-all-fail",
-                                                     num_all_fail[m_name][lc_i][0]))
+                                                     cls.FMT_INT.format(num_all_fail[m_name][lc_i][0])))
                 output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-seed-failrate",
-                                                     num_seed_fail_rate[m_name][lc_i][0]))
+                                                     cls.FMT_FLOAT.format(num_seed_fail_rate[m_name][lc_i][0])))
                 output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-exp-failrate",
-                                                     num_exp_fail_rate[m_name][lc_i][0]))
+                                                     cls.FMT_FLOAT.format(num_exp_fail_rate[m_name][lc_i][0])))
                 output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-all-failrate",
-                                                     num_all_fail_rate[m_name][lc_i][0]))
+                                                     cls.FMT_FLOAT.format(num_all_fail_rate[m_name][lc_i][0])))
                 output_file.append_macro(latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-pass-to-fail",
-                                                     num_pass2fail[m_name][lc_i][0]))
+                                                     cls.FMT_INT.format(num_pass2fail[m_name][lc_i][0])))
             # end for
         # end_for
         output_file.save()
@@ -345,12 +345,12 @@ class Tables:
                 if m_i==0:
                     output_file.append_macro(latex.Macro(f"test-results-hs-bl-lc{lc_i}", lc_descs[lc_i]))
                     output_file.append_macro(latex.Macro(f"test-results-hs-bl-lc{lc_i}-num-tcs",
-                                                         num_seeds_tot[m_name][lc_i][0]))
+                                                         cls.FMT_INT.format(num_seeds_tot[m_name][lc_i][0])))
                 # end if
                 output_file.append_macro(latex.Macro(f"test-results-hs-bl-model{m_i}-lc{lc_i}-num-fail",
-                                                     num_seed_fail[m_name][lc_i][0]))
+                                                     cls.FMT_INT.format(num_seed_fail[m_name][lc_i][0])))
[…]

### 2022-10-26 python/hs/paper/Tables.py
remove print in tables

@@ -340,7 +340,6 @@ class Tables:
             # num_exp_fail_rate[f"model{m_i}"] = dict()
             # num_pass2fail[f"model{m_i}"] = dict()
 
-            print(lc_descs)
             for lc_i in num_seeds_tot[m_name].keys():
                 if m_i==0:
                     output_file.append_macro(latex.Macro(f"test-results-hs-bl-lc{lc_i}", lc_descs[lc_i]))

### 2022-10-26 paper/icse23/tables/test-results-hs-all-numbers.tex
add hs table

%% Automatically generated by pyutil.latex

\DefMacro{test-results-hs-lc2}{Dehumanisation (explicit)}
\DefMacro{test-results-hs-lc2-num-seeds}{140}
\DefMacro{test-results-hs-lc2-num-exps}{3124}
\DefMacro{test-results-hs-model0-lc2-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc1}{Description using very negative attributes (explicit)}
\DefMacro{test-results-hs-lc1-num-seeds}{140}
\DefMacro{test-results-hs-lc1-num-exps}{2959}
\DefMacro{test-results-hs-model0-lc1-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc4}{Direct threat}
\DefMacro{test-results-hs-lc4-num-seeds}{133}
\DefMacro{test-results-hs-lc4-num-exps}{2689}
\DefMacro{test-results-hs-model0-lc4-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc0}{Expression of strong negative emotions (explicit)}
\DefMacro{test-results-hs-lc0-num-seeds}{140}
\DefMacro{test-results-hs-lc0-num-exps}{799}
\DefMacro{test-results-hs-model0-lc0-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc8}{Hate expressed using profanity}
\DefMacro{test-results-hs-lc8-num-seeds}{1842}
\DefMacro{test-results-hs-lc8-num-exps}{49743}
\DefMacro{test-results-hs-model0-lc8-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc6}{Hate expressed using slur}
\DefMacro{test-results-hs-lc6-num-seeds}{805}
\DefMacro{test-results-hs-lc6-num-exps}{17318}
\DefMacro{test-results-hs-model0-lc6-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc3}{Implicit derogation}
\DefMacro{test-results-hs-lc3-num-seeds}{140}
\DefMacro{test-results-hs-lc3-num-exps}{5664}
\DefMacro{test-results-hs-model0-lc3-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc9}{Non-Hateful use of profanity}
\DefMacro{test-results-hs-lc9-num-seeds}{701}
\DefMacro{test-results-hs-lc9-num-exps}{15761}
\DefMacro{test-results-hs-model0-lc9-num-all-fail}{16,462}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc7}{Non-hateful use of slur}
\DefMacro{test-results-hs-lc7-num-seeds}{395}
\DefMacro{test-results-hs-lc7-num-exps}{7881}
\DefMacro{test-results-hs-model0-lc7-num-all-fail}{8,276}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc5}{Threat as normative statement}
\DefMacro{test-results-hs-lc5-num-seeds}{140}
\DefMacro{test-results-hs-lc5-num-exps}{4163}
\DefMacro{test-results-hs-model0-lc5-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{3,210}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{98.34}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{98.35}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{11}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{3,011}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{97.86}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{97.13}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{97.16}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{30}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{2,750}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{97.32}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{97.45}
\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc0-num-all-fail}{845}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{95.71}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{88.99}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{89.99}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{19}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{49,739}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{96.15}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{96.42}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{188}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{17,212}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{96.40}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{94.91}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{94.97}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{81}
\DefMacro{test-results-hs-model1-lc3-num-all-fail}{5,526}
\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{95.18}
\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{95.21}
\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{56}
\DefMacro{test-results-hs-model1-lc9-num-all-fail}{541}
\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{3.28}
\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{3.29}
\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{3.29}
\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{51}
\DefMacro{test-results-hs-model1-lc7-num-all-fail}{318}
\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{2.03}
\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{3.93}
\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{3.84}
\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{20}
\DefMacro{test-results-hs-model1-lc5-num-all-fail}{4,198}
\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{97.57}
\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{97.56}
\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{12}
\DefMacro{test-results-hs-model2-lc2-num-all-fail}{3,220}
\DefMacro{test-results-hs-model2-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model2-lc2-num-exp-failrate}{98.66}
\DefMacro{test-results-hs-model2-lc2-num-all-failrate}{98.65}
\DefMacro{test-results-hs-model2-lc2-num-pass-to-fail}{18}
\DefMacro{test-results-hs-model2-lc1-num-all-fail}{3,067}
\DefMacro{test-results-hs-model2-lc1-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model2-lc1-num-exp-failrate}{98.99}
\DefMacro{test-results-hs-model2-lc1-num-all-failrate}{98.97}
\DefMacro{test-results-hs-model2-lc1-num-pass-to-fail}{23}
\DefMacro{test-results-hs-model2-lc4-num-all-fail}{2,770}
\DefMacro{test-results-hs-model2-lc4-num-seed-failrate}{97.74}
\DefMacro{test-results-hs-model2-lc4-num-exp-failrate}{98.18}
\DefMacro{test-results-hs-model2-lc4-num-all-failrate}{98.16}
\DefMacro{test-results-hs-model2-lc4-num-pass-to-fail}{9}
\DefMacro{test-results-hs-model2-lc0-num-all-fail}{920}
\DefMacro{test-results-hs-model2-lc0-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model2-lc0-num-exp-failrate}{98.12}
\DefMacro{test-results-hs-model2-lc0-num-all-failrate}{97.98}
\DefMacro{test-results-hs-model2-lc0-num-pass-to-fail}{22}
\DefMacro{test-results-hs-model2-lc8-num-all-fail}{50,158}
\DefMacro{test-results-hs-model2-lc8-num-seed-failrate}{97.34}
\DefMacro{test-results-hs-model2-lc8-num-exp-failrate}{97.23}
\DefMacro{test-results-hs-model2-lc8-num-all-failrate}{97.23}
\DefMacro{test-results-hs-model2-lc8-num-pass-to-fail}{164}
\DefMacro{test-results-hs-model2-lc6-num-all-fail}{17,597}
\DefMacro{test-results-hs-model2-lc6-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model2-lc6-num-exp-failrate}{97.10}
\DefMacro{test-results-hs-model2-lc6-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model2-lc6-num-pass-to-fail}{70}
\DefMacro{test-results-hs-model2-lc3-num-all-fail}{5,730}
\DefMacro{test-results-hs-model2-lc3-num-seed-failrate}{97.86}
\DefMacro{test-results-hs-model2-lc3-num-exp-failrate}{98.75}
\DefMacro{test-results-hs-model2-lc3-num-all-failrate}{98.73}
\DefMacro{test-results-hs-model2-lc3-num-pass-to-fail}{30}
\DefMacro{test-results-hs-model2-lc9-num-all-fail}{549}
\DefMacro{test-results-hs-model2-lc9-num-seed-failrate}{3.14}
\DefMacro{test-results-hs-model2-lc9-num-exp-failrate}{3.34}
\DefMacro{test-results-hs-model2-lc9-num-all-failrate}{3.33}
\DefMacro{test-results-hs-model2-lc9-num-pass-to-fail}{58}
\DefMacro{test-results-hs-model2-lc7-num-all-fail}{222}
\DefMacro{test-results-hs-model2-lc7-num-seed-failrate}{2.28}
\DefMacro{test-results-hs-model2-lc7-num-exp-failrate}{2.70}
\DefMacro{test-results-hs-model2-lc7-num-all-failrate}{2.68}
\DefMacro{test-results-hs-model2-lc7-num-pass-to-fail}{26}
\DefMacro{test-results-hs-model2-lc5-num-all-fail}{4,261}
\DefMacro{test-results-hs-model2-lc5-num-seed-failrate}{99.29}
\DefMacro{test-results-hs-model2-lc5-num-exp-failrate}{99.02}
\DefMacro{test-results-hs-model2-lc5-num-all-failrate}{99.02}
\DefMacro{test-results-hs-model2-lc5-num-pass-to-fail}{1}

### 2022-10-26 paper/icse23/tables/test-results-hs-bl-all-numbers.tex
add hs table

%% Automatically generated by pyutil.latex

\DefMacro{test-results-hs-bl-lc19}{Counter speech::Denouncements of hate that make direct reference to it}
\DefMacro{test-results-hs-bl-lc19-num-tcs}{141}
\DefMacro{test-results-hs-bl-model0-lc19-num-fail}{141}
\DefMacro{test-results-hs-bl-model0-lc19-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc18}{Counter speech::Denouncements of hate that quote it}
\DefMacro{test-results-hs-bl-lc18-num-tcs}{173}
\DefMacro{test-results-hs-bl-model0-lc18-num-fail}{173}
\DefMacro{test-results-hs-bl-model0-lc18-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc2}{Derogation::Dehumanisation (explicit)}
\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc1}{Derogation::Description using very negative attributes (explicit)}
\DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc0}{Derogation::Expression of strong negative emotions (explicit)}
\DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc3}{Derogation::Implicit derogation}
\DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc12}{Negation::Hate expressed using negated positive statement}
\DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc13}{Negation::Non-hate expressed using negated hateful statement}
\DefMacro{test-results-hs-bl-lc13-num-tcs}{133}
\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{133}
\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc16}{Non-hate grp. ident.::Neutral statements using protected group identifiers}
\DefMacro{test-results-hs-bl-lc16-num-tcs}{126}
\DefMacro{test-results-hs-bl-model0-lc16-num-fail}{126}
\DefMacro{test-results-hs-bl-model0-lc16-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc17}{Non-hate grp. ident.::Positive statements using protected group identifiers}
\DefMacro{test-results-hs-bl-lc17-num-tcs}{189}
\DefMacro{test-results-hs-bl-model0-lc17-num-fail}{189}
\DefMacro{test-results-hs-bl-model0-lc17-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc15}{Phrasing::Hate phrased as a opinion}
\DefMacro{test-results-hs-bl-lc15-num-tcs}{133}
\DefMacro{test-results-hs-bl-model0-lc15-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc15-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc14}{Phrasing::Hate phrased as a question}
\DefMacro{test-results-hs-bl-lc14-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc14-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc14-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc8}{Profanity usage::Hate expressed using profanity}
\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc9}{Profanity usage::Non-Hateful use of profanity}
\DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{100}
\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc10}{Pronoun reference::Hate expressed through reference in subsequent clauses}
\DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc11}{Pronoun reference::Hate expressed through reference in subsequent sentences}
\DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc6}{Slur usage::Hate expressed using slur}
\DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc7}{Slur usage::Non-hateful use of slur}
\DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{111}
\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-lc4}{Threatening language::Direct threat}
\DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-lc5}{Threatening language::Threat as normative statement}
\DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-model1-lc19-num-fail}{5}
\DefMacro{test-results-hs-bl-model1-lc19-num-failrate}{3.55}
\DefMacro{test-results-hs-bl-model1-lc18-num-fail}{4}
\DefMacro{test-results-hs-bl-model1-lc18-num-failrate}{2.31}
\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{138}
\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{98.57}
\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{136}
\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{97.14}
\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{134}
\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{95.71}
\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{135}
\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{96.43}
\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{136}
\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{97.14}
\DefMacro{test-results-hs-bl-model1-lc13-num-fail}{5}
\DefMacro{test-results-hs-bl-model1-lc13-num-failrate}{3.76}
\DefMacro{test-results-hs-bl-model1-lc16-num-fail}{3}
\DefMacro{test-results-hs-bl-model1-lc16-num-failrate}{2.38}
\DefMacro{test-results-hs-bl-model1-lc17-num-fail}{8}
\DefMacro{test-results-hs-bl-model1-lc17-num-failrate}{4.23}
\DefMacro{test-results-hs-bl-model1-lc15-num-fail}{128}
\DefMacro{test-results-hs-bl-model1-lc15-num-failrate}{96.24}
\DefMacro{test-results-hs-bl-model1-lc14-num-fail}{137}
\DefMacro{test-results-hs-bl-model1-lc14-num-failrate}{97.86}
\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{135}
\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{96.43}
\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{1}
\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{1.00}
\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{132}
\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{94.29}
\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{127}
\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{95.49}
\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{142}
\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{98.61}
\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{2}
\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{1.80}
\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{132}
\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{99.25}
\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{136}
\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{97.14}
\DefMacro{test-results-hs-bl-model2-lc19-num-fail}{1}
\DefMacro{test-results-hs-bl-model2-lc19-num-failrate}{0.71}
\DefMacro{test-results-hs-bl-model2-lc18-num-fail}{4}
\DefMacro{test-results-hs-bl-model2-lc18-num-failrate}{2.31}
\DefMacro{test-results-hs-bl-model2-lc2-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc2-num-failrate}{98.57}
\DefMacro{test-results-hs-bl-model2-lc1-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc1-num-failrate}{98.57}
\DefMacro{test-results-hs-bl-model2-lc0-num-fail}{136}
\DefMacro{test-results-hs-bl-model2-lc0-num-failrate}{97.14}
\DefMacro{test-results-hs-bl-model2-lc3-num-fail}{137}
\DefMacro{test-results-hs-bl-model2-lc3-num-failrate}{97.86}
\DefMacro{test-results-hs-bl-model2-lc12-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc12-num-failrate}{98.57}
\DefMacro{test-results-hs-bl-model2-lc13-num-fail}{2}
\DefMacro{test-results-hs-bl-model2-lc13-num-failrate}{1.50}
\DefMacro{test-results-hs-bl-model2-lc16-num-fail}{0}
\DefMacro{test-results-hs-bl-model2-lc16-num-failrate}{0.00}
\DefMacro{test-results-hs-bl-model2-lc17-num-fail}{3}
\DefMacro{test-results-hs-bl-model2-lc17-num-failrate}{1.59}
\DefMacro{test-results-hs-bl-model2-lc15-num-fail}{131}
\DefMacro{test-results-hs-bl-model2-lc15-num-failrate}{98.50}
\DefMacro{test-results-hs-bl-model2-lc14-num-fail}{139}
\DefMacro{test-results-hs-bl-model2-lc14-num-failrate}{99.29}
\DefMacro{test-results-hs-bl-model2-lc8-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc8-num-failrate}{98.57}
\DefMacro{test-results-hs-bl-model2-lc9-num-fail}{4}
\DefMacro{test-results-hs-bl-model2-lc9-num-failrate}{4.00}
\DefMacro{test-results-hs-bl-model2-lc10-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc10-num-failrate}{98.57}
\DefMacro{test-results-hs-bl-model2-lc11-num-fail}{133}
\DefMacro{test-results-hs-bl-model2-lc11-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-model2-lc6-num-fail}{144}
\DefMacro{test-results-hs-bl-model2-lc6-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-model2-lc7-num-fail}{1}
\DefMacro{test-results-hs-bl-model2-lc7-num-failrate}{0.90}
\DefMacro{test-results-hs-bl-model2-lc4-num-fail}{133}
\DefMacro{test-results-hs-bl-model2-lc4-num-failrate}{100.00}
\DefMacro{test-results-hs-bl-model2-lc5-num-fail}{139}
\DefMacro{test-results-hs-bl-model2-lc5-num-failrate}{99.29}

### 2022-10-26 paper/icse23/tables/test-results-hs-bl-table.tex
add hs table

%% Automatically generated by pyutil.latex

\begin{table*}[htbp]
\begin{small}
\begin{center}
\caption{\TestResultsHsBlTableCaption}
\resizebox{0.75\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-bl-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc0-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc0-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc0-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-bl-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc1-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc1-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc1-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-bl-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc2-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc2-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc2-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-bl-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc3-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc3-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc3-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-bl-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc4-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc4-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc4-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-bl-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc5-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc5-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc5-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-bl-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc6-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc6-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc6-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc6-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc6-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc6-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc6-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-bl-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc7-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc7-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc7-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc7-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc7-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc7-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc7-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-bl-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc8-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc8-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc8-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc8-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc8-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc8-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc8-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-bl-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc9-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc9-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc9-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc9-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc9-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc9-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc9-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-bl-lc10}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc10-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc10-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc10-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc10-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc10-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc10-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc10-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-bl-lc11}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc11-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc11-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc11-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc11-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc11-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc11-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc11-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-bl-lc12}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc12-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc12-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc12-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc12-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc12-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc12-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc12-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-bl-lc13}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc13-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc13-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc13-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc13-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc13-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc13-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc13-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-bl-lc14}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc14-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc14-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc14-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc14-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc14-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc14-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc14-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-bl-lc15}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc15-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc15-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc15-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc15-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc15-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc15-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc15-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-bl-lc16}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc16-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc16-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc16-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc16-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc16-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc16-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc16-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-bl-lc17}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc17-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc17-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc17-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc17-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc17-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc17-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc17-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-bl-lc18}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc18-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc18-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc18-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc18-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc18-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc18-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc18-num-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC20: \UseMacro{test-results-hs-bl-lc19}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc19-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc19-num-fail}
 & BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc19-num-failrate}\\
 & & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc19-num-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-bl-model1-lc19-num-failrate}\\
 & & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc19-num-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-bl-model2-lc19-num-failrate}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-10-26 paper/icse23/tables/test-results-hs-table.tex
add hs table

%% Automatically generated by pyutil.latex

\begin{table*}[htbp]
\begin{small}
\begin{center}
\caption{\TestResultsHsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc6-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc7-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc8-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-exps}}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-pass-to-fail}\\
 & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-fail}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-failrate}
 & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc9-num-pass-to-fail}\\
 & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-fail}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-failrate}
 & daBERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-pass-to-fail}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-10-26 paper/ase22/tables/test-results-all-table.tex
debug

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsAllTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results--1--1-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc0-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc0-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc0-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc0-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc0-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc0-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc0-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc0-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc0-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc0-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results--1--1-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc1-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc1-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc1-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc1-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc1-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc1-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc1-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc1-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc1-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc1-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results--1--1-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc2-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc2-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc2-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc2-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc2-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc2-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc2-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc2-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc2-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc2-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results--1--1-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc3-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc3-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc3-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc3-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc3-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc3-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc3-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc3-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc3-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc3-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results--1--1-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc4-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc4-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc4-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc4-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc4-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc4-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc4-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc4-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc4-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc4-num-pass-to-fail-med}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results--1--1-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results--1--1-lc5-num-exps-med}}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc5-num-all-fail-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc5-num-all-failrate-med}
 & BERT$\colon$\UseMacro{test-results--1--1-model0-lc5-num-pass-to-fail-med}\\
 & & & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc5-num-all-fail-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc5-num-all-failrate-med}
 & RoBERTa$\colon$\UseMacro{test-results--1--1-model1-lc5-num-pass-to-fail-med}\\
 & & & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc5-num-all-fail-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc5-num-all-failrate-med}
 & dstBERT$\colon$\UseMacro{test-results--1--1-model2-lc5-num-pass-to-fail-med}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-10-26 paper/icse23/tables/test-results-all-numbers.tex
debug

%% Automatically generated by pyutil.latex

\DefMacro{test-results-all-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-all-lc3-num-seeds}{62}
\DefMacro{test-results-all-lc3-num-exps}{503}
\DefMacro{test-results-all-model0-lc3-num-fail}{518}
\DefMacro{test-results-all-model0-lc3-num-failrate}{91.68}
\DefMacro{test-results-all-model0-lc3-num-pass-to-fail}{20}
\DefMacro{test-results-all-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-all-lc4-num-seeds}{24}
\DefMacro{test-results-all-lc4-num-exps}{194}
\DefMacro{test-results-all-model0-lc4-num-fail}{205}
\DefMacro{test-results-all-model0-lc4-num-failrate}{94.04}
\DefMacro{test-results-all-model0-lc4-num-pass-to-fail}{11}
\DefMacro{test-results-all-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-all-lc6-num-seeds}{24,328}
\DefMacro{test-results-all-lc6-num-exps}{190,723}
\DefMacro{test-results-all-model0-lc6-num-fail}{195,525}
\DefMacro{test-results-all-model0-lc6-num-failrate}{90.92}
\DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{2,014}
\DefMacro{test-results-all-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-all-lc5-num-seeds}{15,031}
\DefMacro{test-results-all-lc5-num-exps}{102,273}
\DefMacro{test-results-all-model0-lc5-num-fail}{116,894}
\DefMacro{test-results-all-model0-lc5-num-failrate}{99.65}
\DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{71}
\DefMacro{test-results-all-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-all-lc0-num-seeds}{15}
\DefMacro{test-results-all-lc0-num-exps}{51}
\DefMacro{test-results-all-model0-lc0-num-fail}{57}
\DefMacro{test-results-all-model0-lc0-num-failrate}{86.36}
\DefMacro{test-results-all-model0-lc0-num-pass-to-fail}{9}
\DefMacro{test-results-all-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-all-lc1-num-seeds}{83}
\DefMacro{test-results-all-lc1-num-exps}{258}
\DefMacro{test-results-all-model0-lc1-num-fail}{25}
\DefMacro{test-results-all-model0-lc1-num-failrate}{7.33}
\DefMacro{test-results-all-model0-lc1-num-pass-to-fail}{5}
\DefMacro{test-results-all-model1-lc3-num-fail}{493}
\DefMacro{test-results-all-model1-lc3-num-failrate}{87.26}
\DefMacro{test-results-all-model1-lc3-num-pass-to-fail}{9}
\DefMacro{test-results-all-model1-lc4-num-fail}{202}
\DefMacro{test-results-all-model1-lc4-num-failrate}{92.66}
\DefMacro{test-results-all-model1-lc4-num-pass-to-fail}{6}
\DefMacro{test-results-all-model1-lc6-num-fail}{157,635}
\DefMacro{test-results-all-model1-lc6-num-failrate}{73.30}
\DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,289}
\DefMacro{test-results-all-model1-lc5-num-fail}{116,514}
\DefMacro{test-results-all-model1-lc5-num-failrate}{99.33}
\DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{93}
\DefMacro{test-results-all-model1-lc0-num-fail}{51}
\DefMacro{test-results-all-model1-lc0-num-failrate}{77.27}
\DefMacro{test-results-all-model1-lc0-num-pass-to-fail}{2}
\DefMacro{test-results-all-model1-lc1-num-fail}{34}
\DefMacro{test-results-all-model1-lc1-num-failrate}{9.97}
\DefMacro{test-results-all-model1-lc1-num-pass-to-fail}{14}
\DefMacro{test-results-all-model2-lc3-num-fail}{489}
\DefMacro{test-results-all-model2-lc3-num-failrate}{86.55}
\DefMacro{test-results-all-model2-lc3-num-pass-to-fail}{6}
\DefMacro{test-results-all-model2-lc4-num-fail}{211}
\DefMacro{test-results-all-model2-lc4-num-failrate}{96.79}
\DefMacro{test-results-all-model2-lc4-num-pass-to-fail}{10}
\DefMacro{test-results-all-model2-lc6-num-fail}{180,865}
\DefMacro{test-results-all-model2-lc6-num-failrate}{84.10}
\DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,130}
\DefMacro{test-results-all-model2-lc5-num-fail}{115,407}
\DefMacro{test-results-all-model2-lc5-num-failrate}{98.38}
\DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{334}
\DefMacro{test-results-all-model2-lc0-num-fail}{64}
\DefMacro{test-results-all-model2-lc0-num-failrate}{96.97}
\DefMacro{test-results-all-model2-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-all-model2-lc1-num-fail}{17}
\DefMacro{test-results-all-model2-lc1-num-failrate}{4.99}
\DefMacro{test-results-all-model2-lc1-num-pass-to-fail}{10}

### 2022-10-26 paper/icse23/tables/test-results-all-table.tex
debug

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsAllTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-all-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc0-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc0-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc0-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc0-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc0-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc0-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc0-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc0-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc0-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc0-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-all-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc1-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc1-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc1-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc1-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc1-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc1-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc1-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc1-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc1-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc1-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-all-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc2-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc2-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc2-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc2-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc2-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc2-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc2-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc2-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc2-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc2-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-all-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc3-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc3-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc3-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc3-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc3-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc3-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc3-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc3-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc3-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc3-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-all-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc4-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc4-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc4-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc4-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc4-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc4-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc4-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc4-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc4-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc4-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-all-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc5-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc5-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc5-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc5-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc5-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc5-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc5-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc5-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc5-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc5-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-all-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc6-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc6-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc6-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc6-num-pass-to-fail}\\
 & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc6-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc6-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc6-num-pass-to-fail}\\
 & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc6-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc6-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc6-num-pass-to-fail}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-10-26 python/sa/main.py

@@ -60,7 +60,7 @@ parser.add_argument('--which', type=str, default=None, nargs='+',
                     help='tables/plots that you are interested in making')
 
 args = parser.parse_args()
-rand_seed_num = Macros.RAND_SEED[args.num_trials]
+rand_seed_num = Macros.RAND_SEED[args.num_trials] if args.num_trials>0 else Macros.RAND_SEED[1]
 random.seed(rand_seed_num)
 
 def run_requirements():

### 2022-10-26 python/sa/paper/Tables.py

@@ -81,6 +81,12 @@ class Tables:
                 num_trials = options.pop('num_trials', 3)
                 cls.make_numbers_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method, num_seeds, num_trials)
                 cls.make_table_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method, num_seeds, num_trials)
+            elif item == "test-results-all":
+                task = options.pop('task', 'sa')
+                search_dataset = options.pop('search_dataset_name', 'sst')
+                selection_method = options.pop('selection_method', 'random')
+                cls.make_numbers_test_results_all(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
+                cls.make_table_test_results_all(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
             else:
                 raise(f"Unknown table {item}")
             # end if
@@ -650,6 +656,177 @@ class Tables:
                 output_file.append(f" & & & {m_name}$\colon$" + latex.Macro(f"test-results-{num_trials}-{num_seeds}-model{m_i}-lc{lc_i}-num-all-fail-med").use())
                 output_file.append(f" & {m_name}$\colon$" + latex.Macro(f"test-results-{num_trials}-{num_seeds}-model{m_i}-lc{lc_i}-num-all-failrate-med").use())
                 output_file.append(f" & {m_name}$\colon$" + latex.Macro(f"test-results-{num_trials}-{num_seeds}-model{m_i}-lc{lc_i}-num-pass-to-fail-med").use() + r"\\")
+            # end for
+            output_file.append(r"\hline")
+        # end for
+        # Footer
+        output_file.append(r"\bottomrule")
+        output_file.append(r"\end{tabular}}")
+        output_file.append(r"\end{center}")
+        output_file.append(r"\end{small}")
+        output_file.append(r"\vspace{\TestResultsTableVSpace}")
+        output_file.append(r"\end{table*}")
+        output_file.save()
+        return
+    
+    @classmethod
+    def make_numbers_test_results_all(cls,
+                                      result_dir,
+                                      tables_dir,
+                                      task,
+                                      search_dataset,
+                                      selection_method):
[…]

### 2022-10-26 python/sa/utils/Macros.py

@@ -10,12 +10,12 @@ class Macros:
     this_dir: Path = Path(os.path.dirname(os.path.realpath(__file__)))
     root_dir: Path = this_dir.parent.parent.parent 
     python_dir: Path = this_dir.parent.parent
-    storage_dir: Path = Path("/glusterfs/data/jxl115330/s2lct")
+    storage_dir: Path = root_dir # Path("/glusterfs/data/jxl115330/s2lct")
     result_dir: Path = storage_dir / "_results"
     
     download_dir: Path = storage_dir / "_downloads"
     log_dir: Path = storage_dir / "_logs"
-    paper_dir = root_dir / "paper" / "ase22"
+    paper_dir = root_dir / "paper" / "icse23"
     dataset_dir = download_dir / "datasets"
 
     FMT_INT = "{:,d}"

### 2022-11-15 paper/icse23/RESPONSE.txt
response review 1

Thank you for the comments.

__REVIEW_1

>Differences with prior grammar-based work (e.g., MT-NLP, Astraea,
 Ogma etc)

Our method is a grammar-based behavioral testing method for over
linguistic capabilities(LCs) while the existing work (Ogma, Astraea and
MT-NLP) focus on testing fairness and erroneous inputs.  Second, our
method keeps label consistency while prior work doesn't garauntee the
label consistency as they only focus on input generation. Third, ours
generates input with new structure while others relies on the
original structure and replaces words based on their manually
generated grammar. Additionally, the existing work randomly selects
words, but our work selects grammatically and contextually natural
words suggested from CFG grammar and word suggestion model.

>Introducing the linguistic capability...the loop framework.

Our work uses the same linguistic capabilities introduced in
CEHCKLIST.

>Effort involved in specifying the rules?

LCs in CHECKLIST are ambiguously described in a sentence. Thus, we
manually extract elements of interests for each LCs in CHECKLIST. In
practice, we spent less than 10 min to generate each LC.

__REVIEW_2

### 2022-11-15 paper/icse23/RESPONSE.txt
review 2 questions
rebutal review 2

@@
 Our method is a grammar-based behavioral testing method for over
-linguistic capabilities(LCs) while the existing work (Ogma, Astraea and
-MT-NLP) focus on testing fairness and erroneous inputs.  Second, our
-method keeps label consistency while prior work doesn't garauntee the
-label consistency as they only focus on input generation. Third, ours
-generates input with new structure while others relies on the
+linguistic capabilities(LCs) while the existing work (Ogma, Astraea
+and MT-NLP) focus on testing fairness and erroneous inputs.  Second,
+our method keeps label consistency while prior work doesn't garauntee
+the label consistency as they only focus on input generation. Third,
+ours generates input with new structure while others relies on the
 original structure and replaces words based on their manually
@@
 
-Our work uses the same linguistic capabilities introduced in
-CEHCKLIST.
+Our work uses the same LCs provided in CEHCKLIST.
 
@@
 __REVIEW_2
+
+>Do not see a clear motivation of using linguistic capabilities.
+
+Our work uses the same LCs provided in CEHCKLIST. They describes
+specific metamorphic relations between linguistic patten in input and
+output. It enables behavior testing and finding erroneous patterns of
+models.
+
+>Generalizability of the proposed method seems limited.
+
+>Comparison of S^2LCT with NLP adversarial machine learning.
+
+S^2LCT evaluate model behavior under task-relevant LCs. It generates
+test cases suitable to evalaute model given LC rather error-causing
+test cases.
+
+>No discussion or results about repair strategy.
+
+Section VI
+
+__REVIEW_3

### 2022-11-16 paper/icse23/RESPONSE.txt
questions for review 3
response review3
revise response

--- 2022-11-15 paper/icse23/RESPONSE.txt
@@
 Our method is a grammar-based behavioral testing method for over
-linguistic capabilities(LCs) while the existing work (Ogma, Astraea and
-MT-NLP) focus on testing fairness and erroneous inputs.  Second, our
-method keeps label consistency while prior work doesn't garauntee the
-label consistency as they only focus on input generation. Third, ours
-generates input with new structure while others relies on the
-original structure and replaces words based on their manually
-generated grammar. Additionally, the existing work randomly selects
-words, but our work selects grammatically and contextually natural
-words suggested from CFG grammar and word suggestion model.
+linguistic capabilities(LCs). On the other hand, to best of my
+knowledge, the existing work (e.g. Ogma, Astraea and MT-NLP) focus on
+testing fairness or generating adversarial inputs.  Second, our method
+secure label consistency by only allowing neutral words from the set
+of contextually suggested words while prior work does not garauntee
+the label consistency as they only focus on input generation. For
+example, Ogma and Astraea replace a word with a different word that
+has same part-of-speech. the method is limited to secure the semantic
+of input sentence, and it does not gaurantee same label as a
+result. Third, ours generates new test cases with a variety of new
+input structures while others rely on the original structure, new
+input sentences are limited to the original structure based on their
+manually generated grammar. Additionally, our work selects
+grammatically and contextually natural words suggested from CFG
+grammar and word suggestion model. In contrast, the existing work
+randomly selects words.
+
+>How much effort involved in specifying the rules?
+
+LCs in CHECKLIST are described in a sentence, thus it is not clear to
+specify linguistic characteristics of interest and how the input and
+output should be formed because of semantic and structure diversity in
+natural language. Thus, we manually specify rule for seed generation
+for each LCs in CHECKLIST to achieve the semantic and structure
+diversity. In practice, we spent less than 10 min to generate each LC.
 
@@
 
-Our work uses the same linguistic capabilities introduced in
-CEHCKLIST.
-
->Effort involved in specifying the rules?
-
-LCs in CHECKLIST are ambiguously described in a sentence. Thus, we
-manually extract elements of interests for each LCs in CHECKLIST. In
-practice, we spent less than 10 min to generate each LC.
+Our work uses the same LCs provided in CHECKLIST. The LCs are
+pre-defined manually for each task of interest.
 
 __REVIEW_2
+
+>Do not see a clear motivation of using linguistic capabilities.
+
+Our work uses the same LCs provided in CEHCKLIST. They describe
+specific metamorphic relations between linguistic patten in input
+sentence and its output. Compared to the traditional train-valid-test
+split to test NLP models aggregately, Use of the LCs is able to assess
+NLP models over multiple linguistic characteristics in natural
+language relevant to task. Therefore, it enables model behavior
+testing finding erroneous patterns of models.
+
+>Comparison of S^2LCT with NLP adversarial machine learning [2-5].
+
+Extended from the previous response above, S^2LCT evaluates model
+behavior under task-relevant LCs. S^2LCT generates test cases suitable
+to given LC. Compared with out work, adversarial approaches focus on
+generating error-causing test cases. It is limited to assess NLP
+models over multiple linguistic characteristics.
+
+>Generalizability of the proposed method seems limited.
+
+S^2LCT is also implemented for hate speech detection task.  We will
+add results of the task in our final version [JL] or appendix?.
+
+>No discussion or results about repair strategy.
+
+In the section VI of our paper, we show the effectiveness of S^2LCT
+for finding root causes of bugs.
+
+__REVIEW_3
+
+>Limited Applicability & Generalizability
+
+See response to REVIEW_2
+
+>Fail Rate for CHECKLIST
+
+[JL] do we add the numbers here or say that we will add that in the
+appendix? or final version?
+
+>Production rule coverage.: We
+[JL] Do we answer the question?
+
+>label consistency results for CHECKLIST
+
+[JL] do we add the numbers here or say that we will add that in the appendix?

### 2022-11-17 paper/icse23/RESPONSE.txt
revise responce
revise response

--- 2022-11-15 paper/icse23/RESPONSE.txt
@@
+uniqueness of the test generation over lc
+difference metamorphic testing than our work
+
+ours: both label-consistency and LC-consistency
+manually discovered label consistency
+
+1. we generate new structure than other work
+
+our work more generally preserves semantic context(capability part)
+and grammatical correctness(syntactical part).
+
+==========
 Thank you for the comments.
+
+__REVIEW_1&2
+
+>Uniqueness of S^2LCT over prior work (MT-NLP, Astraea, Ogma and
+ adversarial methods for NLP models)
+
+S^2LCT is based on a grammar based test case generation method. The
+uniqueness of the S^2LCT stems from the following properties: First,
+S^2LCT generates new test cases with new and diverse input structures
+given the grammar obtained from commonly used large corpus.  Compared
+with the method, Astraea and Ogma generates input sentences by
+replacing words in an original sentences with other wrods with same
+tag of part-of-speech (POS) conforming to the grammar manually
+constructed. In addition, MT-NLP both replaces words and expands input
+structure, but the expansion only relies on a addition of adjective
+word before noun. In our paper, the structural diversity is shown by
+production rule coverage. Second, S^2LCT addresses consistency of
+label and linguistic capability (LC). The Ogma does not aim to
+preserve the semantic similarity, and it causes label inconsistency in
+input generation. In addition, Astraea and MT-NLP manually preserves
+label consistency by only relying on limited grammar attributes
+(e.g. replacement of noun words). Compared with it, S^2LCT preserves
+label and LC consistency by analyzing syntactic and semantic
+appropriateness of expanded words in the input sentence. Besides,
+S^2LCT generates test cases suitable to the LC and assess how the
+model behaves on a specific linguistic characteristics in input
+sentences. This method is different from the adversarial methods in a
+sense that the adversarial approaches rely on generating error-causing
+test cases, and they are limited to assess NLP models on multiple
+linguistic characteristics.
+
+>Motivation of using linguistic capabilities
+
+Traditional train-valid-test split tests NLP models aggregately and
+the test set reveals biases and fail to comprehensive testing the
+models. Therefore, prior work (e.g. CHECKLIST) introduced multiple
+task relevant LCs and relevant test cases. It enables assess NLP
+models over the multiple LCs. However, it requires manual effort to
+generate relevant test cases, and it results in obtaining limited
+semantic and syntactic attributes. In addition, It requires
+non-trivial manual efforts to define the metamorphic relations between
+inputs and outputs beacuse semantics of nature language can be greatly
+changed even by a slight perturbation to the sentences. In this work,
+we automates LC-relevant test cases generation using the same LCs
+provided in CEHCKLIST.
+
+__REVIEW_2&3
+
+>Limited Applicability & Generalizability
+
+S^2LCT is also implemented for hate speech detection task.
+# TODO: add HS results
+We will also add the results of the task in our final version.
 
@@
 
->Differences with prior grammar-based work (e.g., MT-NLP, Astraea,
- Ogma etc)
+>How much effort involved in specifying the rules?
 
-Our method is a grammar-based behavioral testing method for over
-linguistic capabilities(LCs) while the existing work (Ogma, Astraea and
-MT-NLP) focus on testing fairness and erroneous inputs.  Second, our
-method keeps label consistency while prior work doesn't garauntee the
-label consistency as they only focus on input generation. Third, ours
-generates input with new structure while others relies on the
-original structure and replaces words based on their manually
-generated grammar. Additionally, the existing work randomly selects
-words, but our work selects grammatically and contextually natural
-words suggested from CFG grammar and word suggestion model.
-
->Introducing the linguistic capability...the loop framework.
-
-Our work uses the same linguistic capabilities introduced in
-CEHCKLIST.
-
->Effort involved in specifying the rules?
-
-LCs in CHECKLIST are ambiguously described in a sentence. Thus, we
-manually extract elements of interests for each LCs in CHECKLIST. In
-practice, we spent less than 10 min to generate each LC.
+LCs in CHECKLIST are described in a sentence, thus it is not clear to
+specify linguistic characteristics of interest and how the input and
+output should be formed because of semantic and structure diversity in
+natural language. Thus, we manually specify rule for seed generation
+for each LCs in CHECKLIST to achieve the semantic and structure
+diversity. In practice, we spent less than 10 min to generate each LC.
 
 __REVIEW_2
+
+>No discussion or results about repair strategy.
+
+In the section VI of our paper, we show the effectiveness of S^2LCT
+for finding root causes of bugs.
+
+__REVIEW_3
+
+>Significant effort in defining search rules and transformation
+
+I agree that S^2LCT requires manual specification of search rules and
+transformation.
+
+>Fail Rate for CHECKLIST
+# TODO: add numbers here
+
+>Label Consistency
+
+During the manual study to measure label consistency, it is observered
+that the 83% of label consistency of the seed sentences comes from
+inconsistency between label and the raw sentences in the dataset, and
+it results in the 84% of label consistency of expanded
+sentences. Accordingly, we also empirically compare seed sentences and
+their expanded sentences from the pass-to-fail cases in the table II
+to check the label consistency of the expanded sentences. From the
+comparison, it is observed that no expanded words change the sentiment
+of the expanded sentences and the expanded words preserves the label
+consistency.
+# TODO: Check the label consistency on the example of pass-to-fail manually.

### 2022-11-17 paper/icse23/RESPONSE.txt
revise response

@@
 >Fail Rate for CHECKLIST
-# TODO: add numbers here
+
+LC1(Short sentences with neutral adjectives and nouns): BERT:77.51%, RoBERTa:81.06%, DistilBERT:96.79%
+LC2(Short sentences with sentiment-laden adjectives): BERT:0.3%, RoBERTa:1.61%, DistilBERT:1.44%
+LC3(Sentiment change over time, present should prevail): BERT:21%, RoBERTa:10.36% DistilBERT:31.65%
+LC4(Negated negative should be positive or neutral): BERT:11.77%, RoBERTa:3.21%, DistilBERT:10.82%
+LC5(Negated neutral should still be neutral): BERT:97.24%, RoBERTa:92.31%, DistilBERT:98.16%
+LC6(Negation of negative at the end, should be positive or neutral): BERT:88.09%, RoBERTa:20.95%, DistilBERT:100%
+LC7(Negated positive with neutral content in the middle): BERT:86%, RoBERTa:41.6%, DistilBERT:86.5%
+LC8(Author sentiment is more important than of others): BERT:43.87%, RoBERTa:31.57%, DistilBERT:41.45%
+LC9(Parsing sentiment in (question, yes) form): BERT:19.48%, RoBERTa:13.71%, DistilBERT:16.92%
+LC10(Parsing sentiment in (question, no) form): BERT:53.06%, RoBERTa:59.86%, DistilBERT:84.25%
 

### 2022-11-18 paper/icse23/tables/test-results-hs-all-numbers.tex
new table

@@
 \DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-lc10}{Hate expressed through reference in subsequent clauses}
+\DefMacro{test-results-hs-lc10-num-seeds}{11968}
+\DefMacro{test-results-hs-lc10-num-exps}{44890}
+\DefMacro{test-results-hs-model0-lc10-num-all-fail}{5,984}
+\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{50.00}
+\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{10.52}
+\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-lc11}{Hate expressed through reference in subsequent sentences}
+\DefMacro{test-results-hs-lc11-num-seeds}{11968}
+\DefMacro{test-results-hs-lc11-num-exps}{42840}
+\DefMacro{test-results-hs-model0-lc11-num-all-fail}{5,984}
+\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{50.00}
+\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{10.92}
+\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-lc12}{Hate expressed using negated positive statement}
+\DefMacro{test-results-hs-lc12-num-seeds}{23379}
+\DefMacro{test-results-hs-lc12-num-exps}{126742}
+\DefMacro{test-results-hs-model0-lc12-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{0}
 \DefMacro{test-results-hs-lc8}{Hate expressed using profanity}
@@
 \DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{19}
+\DefMacro{test-results-hs-model1-lc10-num-all-fail}{48,776}
+\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{49.97}
+\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{95.33}
+\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{85.79}
+\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{1,164}
+\DefMacro{test-results-hs-model1-lc11-num-all-fail}{46,721}
+\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{49.72}
+\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{95.17}
+\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{85.24}
+\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{1,070}
+\DefMacro{test-results-hs-model1-lc12-num-all-fail}{144,823}
+\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{96.71}
+\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{96.43}
+\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{96.47}
+\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{2,804}
 \DefMacro{test-results-hs-model1-lc8-num-all-fail}{49,739}
@@
 \DefMacro{test-results-hs-model2-lc0-num-pass-to-fail}{22}
+\DefMacro{test-results-hs-model2-lc10-num-all-fail}{48,642}
+\DefMacro{test-results-hs-model2-lc10-num-seed-failrate}{49.85}
+\DefMacro{test-results-hs-model2-lc10-num-exp-failrate}{95.07}
+\DefMacro{test-results-hs-model2-lc10-num-all-failrate}{85.55}
+\DefMacro{test-results-hs-model2-lc10-num-pass-to-fail}{1,169}
+\DefMacro{test-results-hs-model2-lc11-num-all-fail}{46,156}
+\DefMacro{test-results-hs-model2-lc11-num-seed-failrate}{49.41}
+\DefMacro{test-results-hs-model2-lc11-num-exp-failrate}{93.94}
+\DefMacro{test-results-hs-model2-lc11-num-all-failrate}{84.21}
+\DefMacro{test-results-hs-model2-lc11-num-pass-to-fail}{1,726}
+\DefMacro{test-results-hs-model2-lc12-num-all-fail}{145,761}
+\DefMacro{test-results-hs-model2-lc12-num-seed-failrate}{97.03}
+\DefMacro{test-results-hs-model2-lc12-num-exp-failrate}{97.11}
+\DefMacro{test-results-hs-model2-lc12-num-all-failrate}{97.10}
+\DefMacro{test-results-hs-model2-lc12-num-pass-to-fail}{2,290}
 \DefMacro{test-results-hs-model2-lc8-num-all-fail}{50,158}

### 2022-11-18 paper/icse23/tables/test-results-hs-table.tex
new table

@@
 \hline
+\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-fail}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-failrate}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-pass-to-fail}\\
+ & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-fail}
+ & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-failrate}
+ & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc10-num-pass-to-fail}\\
+ & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-fail}
+ & daBERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-failrate}
+ & daBERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-pass-to-fail}\\
+\hline
+\multirow{3}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-fail}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-failrate}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-pass-to-fail}\\
+ & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-fail}
+ & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-failrate}
+ & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc11-num-pass-to-fail}\\
+ & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-fail}
+ & daBERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-failrate}
+ & daBERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-pass-to-fail}\\
+\hline
+\multirow{3}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-fail}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-failrate}
+ & BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-pass-to-fail}\\
+ & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-fail}
+ & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-failrate}
+ & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc12-num-pass-to-fail}\\
+ & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-fail}
+ & daBERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-failrate}
+ & daBERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-pass-to-fail}\\
+\hline
 \bottomrule

### 2022-11-18 paper/icse23/RESPONSE.txt
table

@@
 
-S^2LCT is also implemented for hate speech detection task.
-# TODO: add HS results
-We will also add the results of the task in our final version.
+We show the applicability and generalizability of the S^2LCT by
+implementing it for other NLP task. In this work, we implement the
+S^2LCT for hate speech detection task. For its experiment, we use
+first 14 functionalities for the task introduced from the hatecheck
+(https://arxiv.org/abs/2012.15606), and we use all seeds for its
+expansion. Models under test for this experiment are
+Hate-speech-CNERG/bert-base-uncased-hatexplain-rationale-two,
+DaNLP/da-electra-hatespeech-detection and
+DaNLP/da-bert-hatespeech-detection. The experiment result over the
+functionalities are shown in the attachment. We will also add the
+results in our final version.
 
@@
 
+We will also add the results in our final version.
+
 >Label Consistency
@@
 consistency.
-# TODO: Check the label consistency on the example of pass-to-fail manually.

### 2022-11-18 paper/icse23/tables/test-results-bl-numbers.tex
table

%% Automatically generated by pyutil.latex

\DefMacro{test-results-bl-lc7}{Author sentiment is more important than of others}
\DefMacro{test-results-bl-lc7-num-seeds}{8,528}
\DefMacro{test-results-bl-model0-lc7-num-seed-fail}{3,741}
\DefMacro{test-results-bl-model0-lc7-num-seed-failrate}{43.87}
\DefMacro{test-results-bl-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-bl-lc3-num-seeds}{6,786}
\DefMacro{test-results-bl-model0-lc3-num-seed-fail}{799}
\DefMacro{test-results-bl-model0-lc3-num-seed-failrate}{11.77}
\DefMacro{test-results-bl-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-bl-lc4-num-seeds}{2,496}
\DefMacro{test-results-bl-model0-lc4-num-seed-fail}{2,427}
\DefMacro{test-results-bl-model0-lc4-num-seed-failrate}{97.24}
\DefMacro{test-results-bl-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-bl-lc6-num-seeds}{1,000}
\DefMacro{test-results-bl-model0-lc6-num-seed-fail}{860}
\DefMacro{test-results-bl-model0-lc6-num-seed-failrate}{86.00}
\DefMacro{test-results-bl-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-bl-lc5-num-seeds}{2,124}
\DefMacro{test-results-bl-model0-lc5-num-seed-fail}{1,871}
\DefMacro{test-results-bl-model0-lc5-num-seed-failrate}{88.09}
\DefMacro{test-results-bl-lc2}{Sentiment change over time, present should prevail}
\DefMacro{test-results-bl-lc2-num-seeds}{8,000}
\DefMacro{test-results-bl-model0-lc2-num-seed-fail}{1,680}
\DefMacro{test-results-bl-model0-lc2-num-seed-failrate}{21.00}
\DefMacro{test-results-bl-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-bl-lc0-num-seeds}{1,716}
\DefMacro{test-results-bl-model0-lc0-num-seed-fail}{1,330}
\DefMacro{test-results-bl-model0-lc0-num-seed-failrate}{77.51}
\DefMacro{test-results-bl-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-bl-lc1-num-seeds}{8,658}
\DefMacro{test-results-bl-model0-lc1-num-seed-fail}{26}
\DefMacro{test-results-bl-model0-lc1-num-seed-failrate}{0.30}
\DefMacro{test-results-bl-lc9}{Parsing sentiment in (question, no) form}
\DefMacro{test-results-bl-lc9-num-seeds}{7,644}
\DefMacro{test-results-bl-model0-lc9-num-seed-fail}{4,056}
\DefMacro{test-results-bl-model0-lc9-num-seed-failrate}{53.06}
\DefMacro{test-results-bl-lc8}{Parsing sentiment in (question, yes) form}
\DefMacro{test-results-bl-lc8-num-seeds}{9,204}
\DefMacro{test-results-bl-model0-lc8-num-seed-fail}{1,793}
\DefMacro{test-results-bl-model0-lc8-num-seed-failrate}{19.48}
\DefMacro{test-results-bl-model1-lc7-num-seed-fail}{2,692}
\DefMacro{test-results-bl-model1-lc7-num-seed-failrate}{31.57}
\DefMacro{test-results-bl-model1-lc3-num-seed-fail}{218}
\DefMacro{test-results-bl-model1-lc3-num-seed-failrate}{3.21}
\DefMacro{test-results-bl-model1-lc4-num-seed-fail}{2,304}
\DefMacro{test-results-bl-model1-lc4-num-seed-failrate}{92.31}
\DefMacro{test-results-bl-model1-lc6-num-seed-fail}{416}
\DefMacro{test-results-bl-model1-lc6-num-seed-failrate}{41.60}
\DefMacro{test-results-bl-model1-lc5-num-seed-fail}{445}
\DefMacro{test-results-bl-model1-lc5-num-seed-failrate}{20.95}
\DefMacro{test-results-bl-model1-lc2-num-seed-fail}{829}
\DefMacro{test-results-bl-model1-lc2-num-seed-failrate}{10.36}
\DefMacro{test-results-bl-model1-lc0-num-seed-fail}{1,391}
\DefMacro{test-results-bl-model1-lc0-num-seed-failrate}{81.06}
\DefMacro{test-results-bl-model1-lc1-num-seed-fail}{139}
\DefMacro{test-results-bl-model1-lc1-num-seed-failrate}{1.61}
\DefMacro{test-results-bl-model1-lc9-num-seed-fail}{4,576}
\DefMacro{test-results-bl-model1-lc9-num-seed-failrate}{59.86}
\DefMacro{test-results-bl-model1-lc8-num-seed-fail}{1,262}
\DefMacro{test-results-bl-model1-lc8-num-seed-failrate}{13.71}
\DefMacro{test-results-bl-model2-lc7-num-seed-fail}{3,535}
\DefMacro{test-results-bl-model2-lc7-num-seed-failrate}{41.45}
\DefMacro{test-results-bl-model2-lc3-num-seed-fail}{734}
\DefMacro{test-results-bl-model2-lc3-num-seed-failrate}{10.82}
\DefMacro{test-results-bl-model2-lc4-num-seed-fail}{2,450}
\DefMacro{test-results-bl-model2-lc4-num-seed-failrate}{98.16}
\DefMacro{test-results-bl-model2-lc6-num-seed-fail}{865}
\DefMacro{test-results-bl-model2-lc6-num-seed-failrate}{86.50}
\DefMacro{test-results-bl-model2-lc5-num-seed-fail}{2,124}
\DefMacro{test-results-bl-model2-lc5-num-seed-failrate}{100.00}
\DefMacro{test-results-bl-model2-lc2-num-seed-fail}{2,532}
\DefMacro{test-results-bl-model2-lc2-num-seed-failrate}{31.65}
\DefMacro{test-results-bl-model2-lc0-num-seed-fail}{1,661}
\DefMacro{test-results-bl-model2-lc0-num-seed-failrate}{96.79}
\DefMacro{test-results-bl-model2-lc1-num-seed-fail}{125}
\DefMacro{test-results-bl-model2-lc1-num-seed-failrate}{1.44}
\DefMacro{test-results-bl-model2-lc9-num-seed-fail}{6,440}
\DefMacro{test-results-bl-model2-lc9-num-seed-failrate}{84.25}
\DefMacro{test-results-bl-model2-lc8-num-seed-fail}{1,557}
\DefMacro{test-results-bl-model2-lc8-num-seed-failrate}{16.92}

### 2022-11-18 paper/icse23/tables/test-results-bl-table.tex
table

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsBlTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-bl-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc0-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc0-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc0-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-bl-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc1-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc1-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc1-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-bl-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc2-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc2-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc2-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-bl-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc3-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc3-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc3-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-bl-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc4-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc4-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc4-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-bl-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc5-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc5-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc5-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-bl-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc6-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc6-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc6-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-bl-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc7-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc7-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc7-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-bl-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc8-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc8-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc8-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-seed-failrate}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-bl-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc9-num-seeds}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-seed-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-seed-failrate}\\
 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc9-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc9-num-seed-failrate}\\
 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-seed-failrate}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2022-11-18 python/hs/paper/Tables.py

@@ -109,7 +109,7 @@ class Tables:
         # end if
         res_dir = result_dir / f"test_results_{task}_{search_dataset}_{selection_method}"
         result_file = res_dir / 'test_result_analysis.json'
-        result = Utils.read_json(result_file)            
+        result = Utils.read_json(result_file)
         for m_i, model_name in enumerate(result.keys()):
             if f"model{m_i}" not in num_seeds_tot.keys():
                 num_seeds_tot[f"model{m_i}"] = dict()
@@ -217,7 +217,7 @@ class Tables:
         output_file.append(r"\begin{small}")
         output_file.append(r"\begin{center}")
         output_file.append(r"\caption{\TestResultsHsTableCaption}")
-        output_file.append(r"\resizebox{0.9\textwidth}{!}{")
+        output_file.append(r"\resizebox{0.7\textwidth}{!}{")
         # output_file.append(r"\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}")
         output_file.append(r"\begin{tabular}{p{8cm}||cclll}")
         output_file.append(r"\toprule")

### 2022-11-18 python/sa/paper/Tables.py

@@ -87,6 +87,12 @@ class Tables:
                 selection_method = options.pop('selection_method', 'random')
                 cls.make_numbers_test_results_all(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
                 cls.make_table_test_results_all(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
+            elif item == "test-results-bl":
+                task = options.pop('task', 'sa')
+                search_dataset = options.pop('search_dataset_name', 'sst')
+                selection_method = options.pop('selection_method', 'random')
+                cls.make_numbers_test_results_baseline(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
+                cls.make_table_test_results_baseline(Macros.result_dir, tables_dir, task, search_dataset, selection_method)
             else:
                 raise(f"Unknown table {item}")
             # end if
@@ -827,6 +833,152 @@ class Tables:
                 output_file.append(f" & & & {m_name}$\colon$" + latex.Macro(f"test-results-all-model{m_i}-lc{lc_i}-num-fail").use())
                 output_file.append(f" & {m_name}$\colon$" + latex.Macro(f"test-results-all-model{m_i}-lc{lc_i}-num-failrate").use())
                 output_file.append(f" & {m_name}$\colon$" + latex.Macro(f"test-results-all-model{m_i}-lc{lc_i}-num-pass-to-fail").use() + r"\\")
+            # end for
+            output_file.append(r"\hline")
+        # end for
+        # Footer
+        output_file.append(r"\bottomrule")
+        output_file.append(r"\end{tabular}}")
+        output_file.append(r"\end{center}")
+        output_file.append(r"\end{small}")
+        output_file.append(r"\vspace{\TestResultsTableVSpace}")
+        output_file.append(r"\end{table*}")
+        output_file.save()
+        return
+
+
+    @classmethod
+    def make_numbers_test_results_baseline(cls,
+                                           result_dir,
+                                           tables_dir,
+                                           task,
+                                           search_dataset,
+                                           selection_method,
+                                           num_seeds=50,
+                                           num_trials=3):
+        lc_descs = dict()
+        num_seeds_tot = dict()
[…]

### 2022-11-18 paper/icse23/RESPONSE.txt
response

--- 2022-11-17 paper/icse23/RESPONSE.txt
@@
 
-S^2LCT is also implemented for hate speech detection task.
-# TODO: add HS results
-We will also add the results of the task in our final version.
+We show the applicability and generalizability of the S^2LCT by
+implementing it for other NLP task. In this work, we implement the
+S^2LCT for hate speech detection task. For its experiment, we use
+first 14 functionalities for the task introduced from the hatecheck
+(https://arxiv.org/abs/2012.15606), and we use all seeds for its
+expansion. Models under test for this experiment are
+Hate-speech-CNERG/bert-base-uncased-hatexplain-rationale-two,
+DaNLP/da-electra-hatespeech-detection and
+DaNLP/da-bert-hatespeech-detection. The experiment result over the
+functionalities are added in the attachment. We will also add the
+results in our final version.
 
@@
 >Fail Rate for CHECKLIST
-# TODO: add numbers here
+
+We add the fail rates for CHECKLIST in the attachment.
+We will also add the results in our final version.
 

### 2022-11-18 paper/icse23/RESPONSE.txt
typo

@@
 with the method, Astraea and Ogma generates input sentences by
-replacing words in an original sentences with other wrods with same
+replacing words in an original sentences with other words with same
 tag of part-of-speech (POS) conforming to the grammar manually
@@
 non-trivial manual efforts to define the metamorphic relations between
-inputs and outputs beacuse semantics of nature language can be greatly
+inputs and outputs because semantics of nature language can be greatly
 changed even by a slight perturbation to the sentences. In this work,
@@
 
-During the manual study to measure label consistency, it is observered
+During the manual study to measure label consistency, it is observed
 that the 83% of label consistency of the seed sentences comes from

### 2022-11-19 paper/icse23/RESPONSE.txt
new version of response

@@
+We thank the reviewer for their comments, which we will strive to
+address.
+
+**(Review A&B) How does S^2LCT differ from MT-NLP, Astraea, Ogma and adversarial generation techniques?**
+
+We would like to point out two fundamental differences. First, the
+linguistic capability(LC)-based testing requires S^2LCT generating
+test cases that belong to the specific LC and conform to the label
+defined by the LC. To the best of my knowledge, *no prior automated
+approach can generate test cases that satisfy this requirement*, while
+this is built into S^2LCT’s design, specifically using LC
+specification to generate seeds and validating the expanded
+sentences. Second, S^2LCT’s syntax-based sentence expansion improves
+the diversity of syntax (RQ1) by extending the sentence
+structures. Astraea and Ogma replace words in an original sentence
+with other words with the same tag of part-of-speech (POS), not
+changing the sentence structure. MT-NLP both replaces words and
+expands input structure, but its expansion only adds an adjective word
+before noun. Adversarial generation techniques replace words with
+another one to cause the model to make a mistake. S^2LCT’s expansion
+is more general by comparing the syntax in the reference corpus
+because more diverse syntax in the reference corpus provides more
+expansion rules.
+
+**(Review B&C) Limited applicability & generalizability.**
+
+S^2LCT takes the LC specifications and the labeled search database as
+inputs (Figure 2). Applying S^2LCT to other NLP tasks requires
+changing these inputs. Since the submission of the paper, we have
+applied S^2LCT to test hate speech detection models. Using the
+functionalities defined in [4], we show that S^2LCT also generates
+more diverse test cases to test three hate speech detection models
+than the manual approach in [4] did. We attached the results as
+following table and will add them to the paper.
+
+| Linguistic capability   | #Seeds   | #Exps | Failure rate[%] | #Pass-to-Fail |
+| :---                             | :---           | :---       | :---                   | :---                  |
+| LC1: Expression of strong negative emotions (explicit) | 140 | 799 | BERT: 0.00, daELECTRA: 89.99, daBERT: 97.98 | BERT: 0, daELECTRA: 19, daBERT: 22 |
+| LC2: Description using very negative attributes (explicit) | 140 | 2959 | BERT: 0.00, daELECTRA: 97.16, daBERT: 98.97 | BERT: 0, daELECTRA: 30, daBERT: 23 |
+| LC3: Dehumanization (explicit) | 140 | 3124 | BERT: 0.00, daELECTRA: 98.35, daBERT: 98.65 | BERT: 0, daELECTRA: 11, daBERT: 18 |
+| LC4: Implicit derogation | 140 | 5664 | BERT: 0.00, daELECTRA: 95.21, daBERT: 98.73 | BERT: 0, daELECTRA: 56, daBERT: 30 |
+
+| LC5: Direct threat | 133 | 2689 | BERT: 0.00, daELECTRA: 97.45, daBERT: 98.16 | BERT: 0, daELECTRA: 0, daBERT: 9 |
+| LC6: Threat as normative statement | 140 | 4163 | BERT: 0.00, daELECTRA: 97.56, daBERT: 99.02 | BERT: 0, daELECTRA: 12, daBERT: 1 |
+| LC7: Hate expressed using slur | 805 | 17318 | BERT: 0.00, daELECTRA: 94.97, daBERT: 97.10 | BERT: 0, daELECTRA: 81, daBERT: 70 |
+| LC8: Non-hateful use of slur | 395 | 7881 | BERT: 100.00, daELECTRA: 3.84, daBERT: 2.68 | BERT: 0, daELECTRA: 20, daBERT: 26 |
+| LC9: Hate expressed using profanity | 1842 | 49743 | BERT: 0.00, daELECTRA: 96.42, daBERT: 97.23 | BERT: 0, daELECTRA: 188, daBERT: 164 |
+| LC10: Non-Hateful use of profanity | 701 | 15761 | BERT: 100.00, daELECTRA: 3.29, daBERT: 3.33 | BERT: 0, daELECTRA: 51, daBERT: 58 |
+| LC11: Hate expressed through reference in subsequent clauses | 11968 | 44890 | BERT: 10.52, daELECTRA: 85.79, daBERT: 85.55 | BERT: 0, daELECTRA: 1164, daBERT: 1169 |
+| LC12: Hate expressed through reference in subsequent sentences | 11968 | 42840 | BERT: 10.92, daELECTRA: 85.24, daBERT: 84.21 | BERT: 0, daELECTRA: 1070, daBERT: 1726 |
+| LC13: Hate expressed using negated positive statement | 23379 | 126742 | BERT: 0.00, daELECTRA: 96.47, daBERT: 97.10 | BERT: 0, daELECTRA: 2804, daBERT: 2290 |
+
+**(Review A&C) How much effort is involved in specifying the rules?**
+
+LCs in CHECKLIST are described in a sentence, which is ambiguous. It
+is not possible to accurately tell if a sentence belongs to a
+CHECKLIST’s LC. We believe our rules for seed generation are more
+formal. We spent less than 10 minutes generating the specification for
+each LC. We will elaborate this effort in the paper.
+
+**(Review A) How sensible are the generated sentences by the approach?**
+
+S^2LCT seed sentences were generated by applying the search rules on
+the labeled search database which contains real-world sentences. The
+transformation templates, as shown in Table 1, allow generating
+sensible seed sentences as they are straightforward concatenation of
+sentence parts. Expanded sentences are also sensible because they are
+generated by using a semantic-aware word suggestion model. The word
+suggestion model suggests words to expand based on the surrounding
+context in the seed sentences.
+
+**(Review A) The subjects only include BERT or some of its variants.**
+
+S^2LCT is a model-agnostic approach, and it works on a variety of NLP
+models. We use BERT and some of its variants because these
+transformer-based models are one of the most advanced types of NLP
+models, which were also used in [3]. We would appreciate it if the
+reviewer can suggest other specific models to test.
+
+**(Review B) Motivation for using linguistic capabilities to generate testing samples.**
+
+LCs are linguistic patterns that appear frequently in the natural
+language for a NLP task. LCs, which define relations between the input
+and output, have shown to be useful to test “functionalities” of the
+NLP models [3]. Evaluation based on LCs allows us to assess to what
+extent NLP models understand the relations and measure the model
+performance per LC. S^2LCT generates test cases that can be mapped to
+the LCs, thereby S^2LCT enables automated, comprehensive functionality
+testing of the NLP model.
+
+**(Review B) Formal definition of linguistic capabilities.**
+
+As discussed above, we define LC specifications which are more formal
+than the past works did. The linguistic capabilities are task and
+language specific. We believe the linguistic capabilities should be
+defined together linguists and NLP model developers for each specific
+task.
+
+**(Review B) How does the proposed method help improve the model's performance after finding bugs?**
+
+In Section VI, we show that a specific pattern in an expanded sentence
+causes erroneous behavior in the model. More test cases using this
+pattern can be generated as additional training data to improve the
+model performance. Our approach enables the detection of such patterns
+by analyzing the changes of the model behavior on the seed and
+expanded sentences.
+
+**(Review C) Fail rate for CHECKLIST.**
+
+We have provided the failure rate in the following table. The order of
+the LCs are same as one in table 2 in the paper. We will also add them
+to the paper.
+
+| Linguistic capability   | #test cases   | Failure rate [%]                                                              |
+| :---                             | :---                 | :---                                                                                  |
+| LC1                           | 1716             | BERT: 77.51, RoBERTa: 81.06, dstBERT: 96.79           |
+| LC2                           | 8658             | BERT: 0.30, RoBERTa: 1.61, dstBERT: 1.44                 |
+| LC3                           | 8000             | BERT: 21.00, RoBERTa: 10.36, dstBERT:31.65            |
+| LC4                           | 6786             | BERT: 11.77, RoBERTa: 3.21, dstBERT: 10.82             |
+| LC5                           | 2496             | BERT: 97.24, RoBERTa: 92.31, dstBERT: 98.16           |
+| LC6                           | 2124             | BERT: 88.09, RoBERTa: 20.95, dstBERT: 100.00         |
+| LC7                           | 1000             | BERT: 86.00, RoBERTa: 41.60, dstBERT: 86.50           |
+| LC8                           | 8528             | BERT: 43.87, RoBERTa: 31.57, dstBERT: 41.45           |
+| LC9                           | 9204             | BERT: 19.48, RoBERTa: 13.71, dstBERT: 16.92           |
+| LC10                         | 7644             | BERT: 53.06, RoBERTa: 59.86, dstBERT: 84.25           |
+
+**(Review C) Label consistency.**
+
+The reviewer is right that the label inconsistency may affect the
+evaluation of the models. We would like to note that most
+inconsistency originated from the seed sentences (in Table III, for
+almost all expanded sentences with the inconsistent label, its seed
+has an inconsistent label). We manually checked all the pass-to-fail
+cases in Table II (last column) and confirmed they all have consistent
+labels.
+
+==========
+
 uniqueness of the test generation over lc

### 2022-11-20 paper/icse23/RESPONSE.txt
dr.yang's pass on response

@@
+We thank the reviewers for their comments.
+
+**(Review A&B) How does S^2LCT differ from MT-NLP, Astraea, Ogma and adversarial generation techniques?**
+
+We would like to point out two fundamental differences. First, the
+linguistic capability(LC)-based testing requires S^2LCT generating
+test cases that belong to a specific LC and conform to the label
+defined by the LC throughout the test generation process. To the best
+of our knowledge, *no prior automated approach can generate test cases
+that satisfy this requirement of LC-based testing*, while this is
+built into S^2LCT’s design, specifically using LC specification to
+generate seeds and validating the expanded sentences. Second, S^2LCT’s
+syntax-based sentence expansion improves the diversity of syntax (RQ1)
+by extending the sentence structures. Astraea and Ogma replace words
+in an original sentence with other words with the same tag of
+part-of-speech (POS), without changing the sentence structure. MT-NLP
+applies a simple expansion that only adds an adjective word before
+noun. S^2LCT’s expansion finds natural variance of sentence structures
+in the reference corpus which lead to diverse syntax in expansion
+rules.
+
+**(Review B&C) Limited applicability & generalizability.**
+
+S^2LCT takes the LC specifications and the labeled search database as
+inputs (Figure 2). Applying S^2LCT to other NLP tasks requires
+changing these inputs. Actually we have applied S^2LCT to test hate
+speech detection models (results were not reported in this submission
+due to space limit). Using the functionalities defined in [4], we show
+that S^2LCT also generates more diverse test cases to test three hate
+speech detection models than the manual approach in [4] did. We
+attached the results as the following table and will add them to the
+final version of the paper.
+
+| Linguistic capability   | #Seeds   | #Exps | Failure rate[%] | #Pass-to-Fail |
+| :---                             | :---           | :---       | :---                   | :---                  |
+| LC1: Expression of strong negative emotions (explicit) | 140 | 799 | BERT: 0.00, daELECTRA: 89.99, daBERT: 97.98 | BERT: 0, daELECTRA: 19, daBERT: 22 |
+| LC2: Description using very negative attributes (explicit) | 140 | 2959 | BERT: 0.00, daELECTRA: 97.16, daBERT: 98.97 | BERT: 0, daELECTRA: 30, daBERT: 23 |
+| LC3: Dehumanization (explicit) | 140 | 3124 | BERT: 0.00, daELECTRA: 98.35, daBERT: 98.65 | BERT: 0, daELECTRA: 11, daBERT: 18 |
+| LC4: Implicit derogation | 140 | 5664 | BERT: 0.00, daELECTRA: 95.21, daBERT: 98.73 | BERT: 0, daELECTRA: 56, daBERT: 30 |
+
+| LC5: Direct threat | 133 | 2689 | BERT: 0.00, daELECTRA: 97.45, daBERT: 98.16 | BERT: 0, daELECTRA: 0, daBERT: 9 |
+| LC6: Threat as normative statement | 140 | 4163 | BERT: 0.00, daELECTRA: 97.56, daBERT: 99.02 | BERT: 0, daELECTRA: 12, daBERT: 1 |
+| LC7: Hate expressed using slur | 805 | 17318 | BERT: 0.00, daELECTRA: 94.97, daBERT: 97.10 | BERT: 0, daELECTRA: 81, daBERT: 70 |
+| LC8: Non-hateful use of slur | 395 | 7881 | BERT: 100.00, daELECTRA: 3.84, daBERT: 2.68 | BERT: 0, daELECTRA: 20, daBERT: 26 |
+| LC9: Hate expressed using profanity | 1842 | 49743 | BERT: 0.00, daELECTRA: 96.42, daBERT: 97.23 | BERT: 0, daELECTRA: 188, daBERT: 164 |
+| LC10: Non-Hateful use of profanity | 701 | 15761 | BERT: 100.00, daELECTRA: 3.29, daBERT: 3.33 | BERT: 0, daELECTRA: 51, daBERT: 58 |
+| LC11: Hate expressed through reference in subsequent clauses | 11968 | 44890 | BERT: 10.52, daELECTRA: 85.79, daBERT: 85.55 | BERT: 0, daELECTRA: 1164, daBERT: 1169 |
+| LC12: Hate expressed through reference in subsequent sentences | 11968 | 42840 | BERT: 10.92, daELECTRA: 85.24, daBERT: 84.21 | BERT: 0, daELECTRA: 1070, daBERT: 1726 |
+| LC13: Hate expressed using negated positive statement | 23379 | 126742 | BERT: 0.00, daELECTRA: 96.47, daBERT: 97.10 | BERT: 0, daELECTRA: 2804, daBERT: 2290 |
+
+**(Review A&C) How much effort is involved in specifying the rules?**
+
+We spent less than 10 minutes generating the specification for each
+LC. Note that LCs in CHECKLIST are described in a non-formal natural
+language sentence, which is ambiguous. It is impossible to determine
+automatically whether a sentence belongs to a CHECKLIST’s
+LC. Comparatively, our rules for seed generation are formal and can be
+automatically checked against. We will elaborate the rule-specifying
+effort in the paper.
+
+**(Review A) How sensible are the generated sentences by the approach?**
+
+S^2LCT seed sentences were generated by applying the search rules on
+the labeled search database which contains real-world sentences. The
+transformation templates, as shown in Table 1, allow generating
+sensible seed sentences as they are straightforward concatenation of
+sentence parts. Expanded sentences are also sensible because they are
+generated by using a semantic-aware word suggestion model. The word
+suggestion model suggests words to expand based on the surrounding
+context in the seed sentences.
+
+**(Review A) The subjects only include BERT or some of its variants.**
+
+S^2LCT is a model-agnostic approach, and it works on a variety of NLP
+models. We use BERT and some of its variants because these
+transformer-based models are one of the most advanced types of NLP
+models, which were also used in [3]. We would appreciate it if the
+reviewer can suggest other specific models to test.
+
+**(Review B) Motivation for using linguistic capabilities to generate testing samples.**
+
+LCs are linguistic patterns that appear frequently in the natural
+language for a NLP task. LCs, which define relations between the input
+and output, have shown to be useful to test “functionalities” of the
+NLP models [3]. Evaluation based on LCs allows us to assess to what
+extent NLP models understand the relations and measure the model
+performance per LC. S^2LCT generates test cases that can be mapped to
+the LCs, thereby S^2LCT enables automated, comprehensive functionality
+testing of the NLP model.
+
+**(Review B) Formal definition of linguistic capabilities.**
+
+As discussed above, we define LC specifications which are more formal
+than the past works did. The linguistic capabilities are task and
+language specific. We believe the linguistic capabilities should be
+defined together linguists and NLP model developers for each specific
+task.
+
+**(Review B) How does the proposed method help improve the model's performance after finding bugs?**
+
+In Section VI, we show that a specific pattern in an expanded sentence
+causes erroneous behavior in the model. More test cases using this
+pattern can be generated as additional training data to improve the
+model performance. Our approach enables the detection of such patterns
+by analyzing the changes of the model behavior on the seed and
+expanded sentences.
+
+**(Review C) Fail rate for CHECKLIST.**
+
+We have provided the failure rate in the following table. The order of the LCs are same as one in table 2 in the paper. We will also add them to the paper.
+
+| Linguistic capability   | #test cases   | Failure rate [%]                                                              |
+| :---                             | :---                 | :---                                                                                  |
+| LC1                           | 1716             | BERT: 77.51, RoBERTa: 81.06, dstBERT: 96.79           |
+| LC2                           | 8658             | BERT: 0.30, RoBERTa: 1.61, dstBERT: 1.44                 |
+| LC3                           | 8000             | BERT: 21.00, RoBERTa: 10.36, dstBERT:31.65            |
+| LC4                           | 6786             | BERT: 11.77, RoBERTa: 3.21, dstBERT: 10.82             |
+| LC5                           | 2496             | BERT: 97.24, RoBERTa: 92.31, dstBERT: 98.16           |
+| LC6                           | 2124             | BERT: 88.09, RoBERTa: 20.95, dstBERT: 100.00         |
+| LC7                           | 1000             | BERT: 86.00, RoBERTa: 41.60, dstBERT: 86.50           |
+| LC8                           | 8528             | BERT: 43.87, RoBERTa: 31.57, dstBERT: 41.45           |
+| LC9                           | 9204             | BERT: 19.48, RoBERTa: 13.71, dstBERT: 16.92           |
+| LC10                         | 7644             | BERT: 53.06, RoBERTa: 59.86, dstBERT: 84.25           |
+
+**(Review C) Label consistency.**
+
+The reviewer is right that the label inconsistency may affect the
+evaluation of the models. We would like to note that most
+inconsistency originated from the seed sentences (in Table III, for
+almost all expanded sentences with the inconsistent label, its seed
+has an inconsistent label). We manually checked all the pass-to-fail
+cases in Table II (last column) and confirmed they all have consistent
+labels.
+
+==========
+
 We thank the reviewer for their comments, which we will strive to

### 2022-11-20 paper/icse23/RESPONSE.txt
pass on response

@@
 applies a simple expansion that only adds an adjective word before
-noun. S^2LCT’s expansion finds natural variance of sentence structures
-in the reference corpus which lead to diverse syntax in expansion
-rules.
+noun. Many adversarial generation techniques also rely on word
+substitution, but some of them insert a word [5]. However, it is
+limited to keep label consistency. S^2LCT’s expansion finds natural
+variance of sentence structures in the reference corpus which lead to
+diverse syntax in expansion rules. In addition, it accepts words that
+do not influence semantics in seed sentences and preserves label
+consistency in the generated test cases.
 
@@
 
-S^2LCT seed sentences were generated by applying the search rules on
-the labeled search database which contains real-world sentences. The
-transformation templates, as shown in Table 1, allow generating
-sensible seed sentences as they are straightforward concatenation of
-sentence parts. Expanded sentences are also sensible because they are
-generated by using a semantic-aware word suggestion model. The word
-suggestion model suggests words to expand based on the surrounding
-context in the seed sentences.
+S^2LCT ensures the sensibility of generated sentences from both syntax
+and semantic levels. From the syntax level, seed sentences were
+generated by applying the search rules on the labeled search database
+which contains real-world sentences. The transformation templates, as
+shown in Table 1, allow generating sensible seed sentences as they are
+straightforward concatenation of sentence parts. From the semantic
+level, expanded sentences are also sensible because they are generated
+by using a semantic-aware word suggestion model. The word suggestion
+model suggests words to expand based on the surrounding context in the
+seed sentences.
 
@@
 language specific. We believe the linguistic capabilities should be
-defined together linguists and NLP model developers for each specific
-task.
+defined together with linguists and NLP model developers for each
+specific task.
 
@@
 
-We have provided the failure rate in the following table. The order of the LCs are same as one in table 2 in the paper. We will also add them to the paper.
+We have provided the failure rate in the following table. The order of
+the LCs are the same as one in table 2 in the paper. We will also add
+them to the paper.
 
@@
 labels.
-
-==========
-
-We thank the reviewer for their comments, which we will strive to
-address.
-
-**(Review A&B) How does S^2LCT differ from MT-NLP, Astraea, Ogma and adversarial generation techniques?**
-
-We would like to point out two fundamental differences. First, the
-linguistic capability(LC)-based testing requires S^2LCT generating
-test cases that belong to the specific LC and conform to the label
-defined by the LC. To the best of my knowledge, *no prior automated
-approach can generate test cases that satisfy this requirement*, while
-this is built into S^2LCT’s design, specifically using LC
-specification to generate seeds and validating the expanded
-sentences. Second, S^2LCT’s syntax-based sentence expansion improves
-the diversity of syntax (RQ1) by extending the sentence
-structures. Astraea and Ogma replace words in an original sentence
-with other words with the same tag of part-of-speech (POS), not
-changing the sentence structure. MT-NLP both replaces words and
-expands input structure, but its expansion only adds an adjective word
-before noun. Adversarial generation techniques replace words with
-another one to cause the model to make a mistake. S^2LCT’s expansion
-is more general by comparing the syntax in the reference corpus
-because more diverse syntax in the reference corpus provides more
-expansion rules.
-
-**(Review B&C) Limited applicability & generalizability.**
-
-S^2LCT takes the LC specifications and the labeled search database as
-inputs (Figure 2). Applying S^2LCT to other NLP tasks requires
-changing these inputs. Since the submission of the paper, we have
-applied S^2LCT to test hate speech detection models. Using the
-functionalities defined in [4], we show that S^2LCT also generates
-more diverse test cases to test three hate speech detection models
-than the manual approach in [4] did. We attached the results as
-following table and will add them to the paper.
-
-| Linguistic capability   | #Seeds   | #Exps | Failure rate[%] | #Pass-to-Fail |
-| :---                             | :---           | :---       | :---                   | :---                  |
-| LC1: Expression of strong negative emotions (explicit) | 140 | 799 | BERT: 0.00, daELECTRA: 89.99, daBERT: 97.98 | BERT: 0, daELECTRA: 19, daBERT: 22 |
-| LC2: Description using very negative attributes (explicit) | 140 | 2959 | BERT: 0.00, daELECTRA: 97.16, daBERT: 98.97 | BERT: 0, daELECTRA: 30, daBERT: 23 |
-| LC3: Dehumanization (explicit) | 140 | 3124 | BERT: 0.00, daELECTRA: 98.35, daBERT: 98.65 | BERT: 0, daELECTRA: 11, daBERT: 18 |
-| LC4: Implicit derogation | 140 | 5664 | BERT: 0.00, daELECTRA: 95.21, daBERT: 98.73 | BERT: 0, daELECTRA: 56, daBERT: 30 |
-
-| LC5: Direct threat | 133 | 2689 | BERT: 0.00, daELECTRA: 97.45, daBERT: 98.16 | BERT: 0, daELECTRA: 0, daBERT: 9 |
-| LC6: Threat as normative statement | 140 | 4163 | BERT: 0.00, daELECTRA: 97.56, daBERT: 99.02 | BERT: 0, daELECTRA: 12, daBERT: 1 |
-| LC7: Hate expressed using slur | 805 | 17318 | BERT: 0.00, daELECTRA: 94.97, daBERT: 97.10 | BERT: 0, daELECTRA: 81, daBERT: 70 |
-| LC8: Non-hateful use of slur | 395 | 7881 | BERT: 100.00, daELECTRA: 3.84, daBERT: 2.68 | BERT: 0, daELECTRA: 20, daBERT: 26 |
-| LC9: Hate expressed using profanity | 1842 | 49743 | BERT: 0.00, daELECTRA: 96.42, daBERT: 97.23 | BERT: 0, daELECTRA: 188, daBERT: 164 |
-| LC10: Non-Hateful use of profanity | 701 | 15761 | BERT: 100.00, daELECTRA: 3.29, daBERT: 3.33 | BERT: 0, daELECTRA: 51, daBERT: 58 |
-| LC11: Hate expressed through reference in subsequent clauses | 11968 | 44890 | BERT: 10.52, daELECTRA: 85.79, daBERT: 85.55 | BERT: 0, daELECTRA: 1164, daBERT: 1169 |
-| LC12: Hate expressed through reference in subsequent sentences | 11968 | 42840 | BERT: 10.92, daELECTRA: 85.24, daBERT: 84.21 | BERT: 0, daELECTRA: 1070, daBERT: 1726 |
-| LC13: Hate expressed using negated positive statement | 23379 | 126742 | BERT: 0.00, daELECTRA: 96.47, daBERT: 97.10 | BERT: 0, daELECTRA: 2804, daBERT: 2290 |
-
-**(Review A&C) How much effort is involved in specifying the rules?**
-
-LCs in CHECKLIST are described in a sentence, which is ambiguous. It
-is not possible to accurately tell if a sentence belongs to a
-CHECKLIST’s LC. We believe our rules for seed generation are more
-formal. We spent less than 10 minutes generating the specification for
-each LC. We will elaborate this effort in the paper.
-
-**(Review A) How sensible are the generated sentences by the approach?**
-
-S^2LCT seed sentences were generated by applying the search rules on
-the labeled search database which contains real-world sentences. The
-transformation templates, as shown in Table 1, allow generating
-sensible seed sentences as they are straightforward concatenation of
-sentence parts. Expanded sentences are also sensible because they are
-generated by using a semantic-aware word suggestion model. The word
-suggestion model suggests words to expand based on the surrounding
-context in the seed sentences.
-
-**(Review A) The subjects only include BERT or some of its variants.**
-
-S^2LCT is a model-agnostic approach, and it works on a variety of NLP
-models. We use BERT and some of its variants because these
-transformer-based models are one of the most advanced types of NLP
-models, which were also used in [3]. We would appreciate it if the
-reviewer can suggest other specific models to test.
-
-**(Review B) Motivation for using linguistic capabilities to generate testing samples.**
-
-LCs are linguistic patterns that appear frequently in the natural
-language for a NLP task. LCs, which define relations between the input
-and output, have shown to be useful to test “functionalities” of the
-NLP models [3]. Evaluation based on LCs allows us to assess to what
-extent NLP models understand the relations and measure the model
-performance per LC. S^2LCT generates test cases that can be mapped to
-the LCs, thereby S^2LCT enables automated, comprehensive functionality
-testing of the NLP model.
-
-**(Review B) Formal definition of linguistic capabilities.**
-
-As discussed above, we define LC specifications which are more formal
-than the past works did. The linguistic capabilities are task and
-language specific. We believe the linguistic capabilities should be
-defined together linguists and NLP model developers for each specific
-task.
-
-**(Review B) How does the proposed method help improve the model's performance after finding bugs?**
-
-In Section VI, we show that a specific pattern in an expanded sentence
-causes erroneous behavior in the model. More test cases using this
-pattern can be generated as additional training data to improve the
-model performance. Our approach enables the detection of such patterns
-by analyzing the changes of the model behavior on the seed and
-expanded sentences.
-
-**(Review C) Fail rate for CHECKLIST.**
-
-We have provided the failure rate in the following table. The order of
-the LCs are same as one in table 2 in the paper. We will also add them
-to the paper.
-
-| Linguistic capability   | #test cases   | Failure rate [%]                                                              |
-| :---                             | :---                 | :---                                                                                  |
-| LC1                           | 1716             | BERT: 77.51, RoBERTa: 81.06, dstBERT: 96.79           |
-| LC2                           | 8658             | BERT: 0.30, RoBERTa: 1.61, dstBERT: 1.44                 |
-| LC3                           | 8000             | BERT: 21.00, RoBERTa: 10.36, dstBERT:31.65            |
-| LC4                           | 6786             | BERT: 11.77, RoBERTa: 3.21, dstBERT: 10.82             |
-| LC5                           | 2496             | BERT: 97.24, RoBERTa: 92.31, dstBERT: 98.16           |
-| LC6                           | 2124             | BERT: 88.09, RoBERTa: 20.95, dstBERT: 100.00         |
-| LC7                           | 1000             | BERT: 86.00, RoBERTa: 41.60, dstBERT: 86.50           |
-| LC8                           | 8528             | BERT: 43.87, RoBERTa: 31.57, dstBERT: 41.45           |
-| LC9                           | 9204             | BERT: 19.48, RoBERTa: 13.71, dstBERT: 16.92           |
-| LC10                         | 7644             | BERT: 53.06, RoBERTa: 59.86, dstBERT: 84.25           |
-
-**(Review C) Label consistency.**
-
-The reviewer is right that the label inconsistency may affect the
-evaluation of the models. We would like to note that most
-inconsistency originated from the seed sentences (in Table III, for
-almost all expanded sentences with the inconsistent label, its seed
-has an inconsistent label). We manually checked all the pass-to-fail
-cases in Table II (last column) and confirmed they all have consistent
-labels.
-
-==========
-
-uniqueness of the test generation over lc
-difference metamorphic testing than our work
-
-ours: both label-consistency and LC-consistency
-manually discovered label consistency
-
-1. we generate new structure than other work
-
-our work more generally preserves semantic context(capability part)
-and grammatical correctness(syntactical part).
-
-==========
-Thank you for the comments.
-
-__REVIEW_1&2
-
->Uniqueness of S^2LCT over prior work (MT-NLP, Astraea, Ogma and
- adversarial methods for NLP models)
-
-S^2LCT is based on a grammar based test case generation method. The
-uniqueness of the S^2LCT stems from the following properties: First,
-S^2LCT generates new test cases with new and diverse input structures
-given the grammar obtained from commonly used large corpus.  Compared
-with the method, Astraea and Ogma generates input sentences by
-replacing words in an original sentences with other words with same
-tag of part-of-speech (POS) conforming to the grammar manually
-constructed. In addition, MT-NLP both replaces words and expands input
-structure, but the expansion only relies on a addition of adjective
-word before noun. In our paper, the structural diversity is shown by
-production rule coverage. Second, S^2LCT addresses consistency of
-label and linguistic capability (LC). The Ogma does not aim to
-preserve the semantic similarity, and it causes label inconsistency in
-input generation. In addition, Astraea and MT-NLP manually preserves
-label consistency by only relying on limited grammar attributes
-(e.g. replacement of noun words). Compared with it, S^2LCT preserves
-label and LC consistency by analyzing syntactic and semantic
-appropriateness of expanded words in the input sentence. Besides,
-S^2LCT generates test cases suitable to the LC and assess how the
-model behaves on a specific linguistic characteristics in input
-sentences. This method is different from the adversarial methods in a
-sense that the adversarial approaches rely on generating error-causing
-test cases, and they are limited to assess NLP models on multiple
-linguistic characteristics.
-
->Motivation of using linguistic capabilities
-
-Traditional train-valid-test split tests NLP models aggregately and
-the test set reveals biases and fail to comprehensive testing the
-models. Therefore, prior work (e.g. CHECKLIST) introduced multiple
-task relevant LCs and relevant test cases. It enables assess NLP
-models over the multiple LCs. However, it requires manual effort to
-generate relevant test cases, and it results in obtaining limited
-semantic and syntactic attributes. In addition, It requires
-non-trivial manual efforts to define the metamorphic relations between
-inputs and outputs because semantics of nature language can be greatly
-changed even by a slight perturbation to the sentences. In this work,
-we automates LC-relevant test cases generation using the same LCs
-provided in CEHCKLIST.
-
-__REVIEW_2&3
-
->Limited Applicability & Generalizability
-
-We show the applicability and generalizability of the S^2LCT by
-implementing it for other NLP task. In this work, we implement the
-S^2LCT for hate speech detection task. For its experiment, we use
-first 14 functionalities for the task introduced from the hatecheck
-(https://arxiv.org/abs/2012.15606), and we use all seeds for its
-expansion. Models under test for this experiment are
-Hate-speech-CNERG/bert-base-uncased-hatexplain-rationale-two,
-DaNLP/da-electra-hatespeech-detection and
-DaNLP/da-bert-hatespeech-detection. The experiment result over the
-functionalities are added in the attachment. We will also add the
-results in our final version.
-
-__REVIEW_1
-
->How much effort involved in specifying the rules?
-
-LCs in CHECKLIST are described in a sentence, thus it is not clear to
-specify linguistic characteristics of interest and how the input and
-output should be formed because of semantic and structure diversity in
-natural language. Thus, we manually specify rule for seed generation
-for each LCs in CHECKLIST to achieve the semantic and structure
-diversity. In practice, we spent less than 10 min to generate each LC.
-
-__REVIEW_2
-
->No discussion or results about repair strategy.
-
-In the section VI of our paper, we show the effectiveness of S^2LCT
-for finding root causes of bugs.
-
-__REVIEW_3
-
->Significant effort in defining search rules and transformation
-
-I agree that S^2LCT requires manual specification of search rules and
-transformation.
-
->Fail Rate for CHECKLIST
-
-We add the fail rates for CHECKLIST in the attachment.
-We will also add the results in our final version.
-
->Label Consistency
-
-During the manual study to measure label consistency, it is observed
-that the 83% of label consistency of the seed sentences comes from
-inconsistency between label and the raw sentences in the dataset, and
-it results in the 84% of label consistency of expanded
-sentences. Accordingly, we also empirically compare seed sentences and
-their expanded sentences from the pass-to-fail cases in the table II
-to check the label consistency of the expanded sentences. From the
-comparison, it is observed that no expanded words change the sentiment
-of the expanded sentences and the expanded words preserves the label
-consistency.

### 2023-01-09 python/hs/main.py
debug

@@ -58,8 +58,8 @@ def run_templates():
     search_dataset_name = args.search_dataset
     selection_method = args.syntax_selection
     num_seeds = args.num_seeds
-    num_trials = '' if args.num_trials==1 else str(args.num_trials)
-    _num_trials = '' if num_trials==1 else str(num_trials)
+    num_trials = '' if args.num_trials<2 else str(args.num_trials)
+    _num_trials = '' if args.num_trials<2 else str(num_trials)
     gpu_ids = args.gpu_ids
     if gpu_ids is not None:
         assert len(gpu_ids)==Macros.num_processes
@@ -89,7 +89,7 @@ def run_testsuites():
     search_dataset_name = args.search_dataset
     selection_method = args.syntax_selection
     num_seeds = args.num_seeds
-    num_trials = '' if args.num_trials==1 else str(args.num_trials)
+    num_trials = '' if args.num_trials<2 else str(args.num_trials)
     if num_seeds<0:
         log_dir = Macros.log_dir / f"{nlp_task}_{search_dataset_name}_{selection_method}"
     else:
@@ -140,7 +140,7 @@ def run_analyze():
     selection_method = args.syntax_selection
     test_baseline = args.test_baseline
     num_seeds = args.num_seeds
-    num_trials = '' if args.num_trials==1 else str(args.num_trials)
+    num_trials = '' if args.num_trials<2 else str(args.num_trials)
     if test_baseline:
         if num_seeds<0:
             result_dir = Macros.result_dir / f"test_results{num_trials}_{nlp_task}_{search_dataset_name}_{selection_method}"

### 2023-01-09 paper/icse23/tables/test-results-all-table.tex
debug

@@
 \hline
+\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-all-lc7}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc7-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc7-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc7-num-fail}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc7-num-failrate}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc7-num-pass-to-fail}\\
+ & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc7-num-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc7-num-failrate}
+ & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc7-num-pass-to-fail}\\
+ & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc7-num-fail}
+ & dstBERT$\colon$\UseMacro{test-results-all-model2-lc7-num-failrate}
+ & dstBERT$\colon$\UseMacro{test-results-all-model2-lc7-num-pass-to-fail}\\
+\hline
+\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-all-lc8}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc8-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc8-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc8-num-fail}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc8-num-failrate}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc8-num-pass-to-fail}\\
+ & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc8-num-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc8-num-failrate}
+ & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc8-num-pass-to-fail}\\
+ & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc8-num-fail}
+ & dstBERT$\colon$\UseMacro{test-results-all-model2-lc8-num-failrate}
+ & dstBERT$\colon$\UseMacro{test-results-all-model2-lc8-num-pass-to-fail}\\
+\hline
+\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-all-lc9}}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc9-num-seeds}}
+ & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc9-num-exps}}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc9-num-fail}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc9-num-failrate}
+ & BERT$\colon$\UseMacro{test-results-all-model0-lc9-num-pass-to-fail}\\
+ & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc9-num-fail}
+ & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc9-num-failrate}
+ & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc9-num-pass-to-fail}\\
+ & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc9-num-fail}
+ & dstBERT$\colon$\UseMacro{test-results-all-model2-lc9-num-failrate}
+ & dstBERT$\colon$\UseMacro{test-results-all-model2-lc9-num-pass-to-fail}\\
+\hline
 \bottomrule

### 2023-01-09 paper/icse23/tables/test-results-hs-bl-all-numbers.tex
debug

@@
 \DefMacro{test-results-hs-bl-lc19-num-tcs}{141}
-\DefMacro{test-results-hs-bl-model0-lc19-num-fail}{141}
-\DefMacro{test-results-hs-bl-model0-lc19-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc19-num-fail}{20}
+\DefMacro{test-results-hs-bl-model0-lc19-num-failrate}{14.18}
 \DefMacro{test-results-hs-bl-lc18}{Counter speech::Denouncements of hate that quote it}
 \DefMacro{test-results-hs-bl-lc18-num-tcs}{173}
-\DefMacro{test-results-hs-bl-model0-lc18-num-fail}{173}
-\DefMacro{test-results-hs-bl-model0-lc18-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc18-num-fail}{18}
+\DefMacro{test-results-hs-bl-model0-lc18-num-failrate}{10.40}
 \DefMacro{test-results-hs-bl-lc2}{Derogation::Dehumanisation (explicit)}
 \DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{138}
+\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{98.57}
 \DefMacro{test-results-hs-bl-lc1}{Derogation::Description using very negative attributes (explicit)}
 \DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{138}
+\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{98.57}
 \DefMacro{test-results-hs-bl-lc0}{Derogation::Expression of strong negative emotions (explicit)}
 \DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{136}
+\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{97.14}
 \DefMacro{test-results-hs-bl-lc3}{Derogation::Implicit derogation}
 \DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{137}
+\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{97.86}
 \DefMacro{test-results-hs-bl-lc12}{Negation::Hate expressed using negated positive statement}
 \DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{138}
+\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{98.57}
 \DefMacro{test-results-hs-bl-lc13}{Negation::Non-hate expressed using negated hateful statement}
 \DefMacro{test-results-hs-bl-lc13-num-tcs}{133}
-\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{133}
-\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{9}
+\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{6.77}
 \DefMacro{test-results-hs-bl-lc16}{Non-hate grp. ident.::Neutral statements using protected group identifiers}
 \DefMacro{test-results-hs-bl-lc16-num-tcs}{126}
-\DefMacro{test-results-hs-bl-model0-lc16-num-fail}{126}
-\DefMacro{test-results-hs-bl-model0-lc16-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc16-num-fail}{8}
+\DefMacro{test-results-hs-bl-model0-lc16-num-failrate}{6.35}
 \DefMacro{test-results-hs-bl-lc17}{Non-hate grp. ident.::Positive statements using protected group identifiers}
 \DefMacro{test-results-hs-bl-lc17-num-tcs}{189}
-\DefMacro{test-results-hs-bl-model0-lc17-num-fail}{189}
-\DefMacro{test-results-hs-bl-model0-lc17-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc17-num-fail}{10}
+\DefMacro{test-results-hs-bl-model0-lc17-num-failrate}{5.29}
 \DefMacro{test-results-hs-bl-lc15}{Phrasing::Hate phrased as a opinion}
 \DefMacro{test-results-hs-bl-lc15-num-tcs}{133}
-\DefMacro{test-results-hs-bl-model0-lc15-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc15-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc15-num-fail}{131}
+\DefMacro{test-results-hs-bl-model0-lc15-num-failrate}{98.50}
 \DefMacro{test-results-hs-bl-lc14}{Phrasing::Hate phrased as a question}
 \DefMacro{test-results-hs-bl-lc14-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc14-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc14-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc14-num-fail}{139}
+\DefMacro{test-results-hs-bl-model0-lc14-num-failrate}{99.29}
 \DefMacro{test-results-hs-bl-lc8}{Profanity usage::Hate expressed using profanity}
 \DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{138}
+\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{98.57}
 \DefMacro{test-results-hs-bl-lc9}{Profanity usage::Non-Hateful use of profanity}
 \DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
-\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{100}
-\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{30}
+\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{30.00}
 \DefMacro{test-results-hs-bl-lc10}{Pronoun reference::Hate expressed through reference in subsequent clauses}
 \DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{138}
+\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{98.57}
 \DefMacro{test-results-hs-bl-lc11}{Pronoun reference::Hate expressed through reference in subsequent sentences}
 \DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
-\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{133}
+\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{100.00}
 \DefMacro{test-results-hs-bl-lc6}{Slur usage::Hate expressed using slur}
 \DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
-\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{144}
+\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{100.00}
 \DefMacro{test-results-hs-bl-lc7}{Slur usage::Non-hateful use of slur}
 \DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
-\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{111}
-\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{5}
+\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{4.50}
 \DefMacro{test-results-hs-bl-lc4}{Threatening language::Direct threat}
 \DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
-\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{133}
+\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{100.00}
 \DefMacro{test-results-hs-bl-lc5}{Threatening language::Threat as normative statement}
 \DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
-\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{0}
-\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{0.00}
-\DefMacro{test-results-hs-bl-model1-lc19-num-fail}{5}
-\DefMacro{test-results-hs-bl-model1-lc19-num-failrate}{3.55}
-\DefMacro{test-results-hs-bl-model1-lc18-num-fail}{4}
-\DefMacro{test-results-hs-bl-model1-lc18-num-failrate}{2.31}
-\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{138}
-\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{98.57}
-\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{136}
-\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{97.14}
-\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{134}
-\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{95.71}
-\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{135}
-\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{96.43}
-\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{136}
-\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{97.14}
-\DefMacro{test-results-hs-bl-model1-lc13-num-fail}{5}
-\DefMacro{test-results-hs-bl-model1-lc13-num-failrate}{3.76}
-\DefMacro{test-results-hs-bl-model1-lc16-num-fail}{3}
-\DefMacro{test-results-hs-bl-model1-lc16-num-failrate}{2.38}
-\DefMacro{test-results-hs-bl-model1-lc17-num-fail}{8}
-\DefMacro{test-results-hs-bl-model1-lc17-num-failrate}{4.23}
-\DefMacro{test-results-hs-bl-model1-lc15-num-fail}{128}
-\DefMacro{test-results-hs-bl-model1-lc15-num-failrate}{96.24}
-\DefMacro{test-results-hs-bl-model1-lc14-num-fail}{137}
-\DefMacro{test-results-hs-bl-model1-lc14-num-failrate}{97.86}
-\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{135}
-\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{96.43}
-\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{1}
-\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{1.00}
-\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{132}
-\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{94.29}
-\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{127}
-\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{95.49}
-\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{142}
-\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{98.61}
-\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{2}
-\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{1.80}
-\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{132}
-\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{99.25}
-\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{136}
-\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{97.14}
-\DefMacro{test-results-hs-bl-model2-lc19-num-fail}{1}
-\DefMacro{test-results-hs-bl-model2-lc19-num-failrate}{0.71}
-\DefMacro{test-results-hs-bl-model2-lc18-num-fail}{4}
-\DefMacro{test-results-hs-bl-model2-lc18-num-failrate}{2.31}
-\DefMacro{test-results-hs-bl-model2-lc2-num-fail}{138}
-\DefMacro{test-results-hs-bl-model2-lc2-num-failrate}{98.57}
-\DefMacro{test-results-hs-bl-model2-lc1-num-fail}{138}
-\DefMacro{test-results-hs-bl-model2-lc1-num-failrate}{98.57}
-\DefMacro{test-results-hs-bl-model2-lc0-num-fail}{136}
-\DefMacro{test-results-hs-bl-model2-lc0-num-failrate}{97.14}
-\DefMacro{test-results-hs-bl-model2-lc3-num-fail}{137}
-\DefMacro{test-results-hs-bl-model2-lc3-num-failrate}{97.86}
-\DefMacro{test-results-hs-bl-model2-lc12-num-fail}{138}
-\DefMacro{test-results-hs-bl-model2-lc12-num-failrate}{98.57}
-\DefMacro{test-results-hs-bl-model2-lc13-num-fail}{2}
-\DefMacro{test-results-hs-bl-model2-lc13-num-failrate}{1.50}
-\DefMacro{test-results-hs-bl-model2-lc16-num-fail}{0}
-\DefMacro{test-results-hs-bl-model2-lc16-num-failrate}{0.00}
-\DefMacro{test-results-hs-bl-model2-lc17-num-fail}{3}
-\DefMacro{test-results-hs-bl-model2-lc17-num-failrate}{1.59}
-\DefMacro{test-results-hs-bl-model2-lc15-num-fail}{131}
-\DefMacro{test-results-hs-bl-model2-lc15-num-failrate}{98.50}
-\DefMacro{test-results-hs-bl-model2-lc14-num-fail}{139}
-\DefMacro{test-results-hs-bl-model2-lc14-num-failrate}{99.29}
-\DefMacro{test-results-hs-bl-model2-lc8-num-fail}{138}
-\DefMacro{test-results-hs-bl-model2-lc8-num-failrate}{98.57}
-\DefMacro{test-results-hs-bl-model2-lc9-num-fail}{4}
-\DefMacro{test-results-hs-bl-model2-lc9-num-failrate}{4.00}
-\DefMacro{test-results-hs-bl-model2-lc10-num-fail}{138}
-\DefMacro{test-results-hs-bl-model2-lc10-num-failrate}{98.57}
-\DefMacro{test-results-hs-bl-model2-lc11-num-fail}{133}
-\DefMacro{test-results-hs-bl-model2-lc11-num-failrate}{100.00}
-\DefMacro{test-results-hs-bl-model2-lc6-num-fail}{144}
-\DefMacro{test-results-hs-bl-model2-lc6-num-failrate}{100.00}
-\DefMacro{test-results-hs-bl-model2-lc7-num-fail}{1}
-\DefMacro{test-results-hs-bl-model2-lc7-num-failrate}{0.90}
-\DefMacro{test-results-hs-bl-model2-lc4-num-fail}{133}
-\DefMacro{test-results-hs-bl-model2-lc4-num-failrate}{100.00}
-\DefMacro{test-results-hs-bl-model2-lc5-num-fail}{139}
-\DefMacro{test-results-hs-bl-model2-lc5-num-failrate}{99.29}
+\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{139}
+\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{99.29}
+\DefMacro{test-results-hs-bl-model1-lc19-num-fail}{141}
+\DefMacro{test-results-hs-bl-model1-lc19-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc18-num-fail}{173}
+\DefMacro{test-results-hs-bl-model1-lc18-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{1}
+\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{0.71}
+\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc13-num-fail}{133}
+\DefMacro{test-results-hs-bl-model1-lc13-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc16-num-fail}{126}
+\DefMacro{test-results-hs-bl-model1-lc16-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc17-num-fail}{189}
+\DefMacro{test-results-hs-bl-model1-lc17-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc15-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc15-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc14-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc14-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{100}
+\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{11}
+\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{7.64}
+\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{111}
+\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{100.00}
+\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{0.00}
+\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{0.00}

### 2023-01-09 paper/icse23/tables/test-results-hs-table.tex
debug

--- 2022-10-26 paper/icse23/tables/test-results-hs-table.tex
@@
 \caption{\TestResultsHsTableCaption}
-\resizebox{0.9\textwidth}{!}{
+\resizebox{0.7\textwidth}{!}{
 \begin{tabular}{p{8cm}||cclll}
@@
 \midrule
-\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc6-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc6-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc6-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc7-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc7-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc7-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc8-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc8-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc8-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-exps}}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-fail}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-failrate}
- & BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-pass-to-fail}\\
- & & & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-fail}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-failrate}
- & daELECTRA$\colon$\UseMacro{test-results-hs-model1-lc9-num-pass-to-fail}\\
- & & & daBERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-fail}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-failrate}
- & daBERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-pass-to-fail}\\
+\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc9-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc9-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc10-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc10-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc11-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc11-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc12-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc12-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc13}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc13-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc13-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc13-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc13-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc13-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc13-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc13-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc13-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-lc14}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-lc15}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-lc16}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-lc17}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-lc18}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-pass-to-fail}\\
+ & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-pass-to-fail}\\
 \hline

### 2023-01-09 python/hs/paper/Tables.py

@@ -111,7 +111,6 @@ class Tables:
         result_file = res_dir / 'test_result_analysis.json'
         result = Utils.read_json(result_file)
         for m_i, model_name in enumerate(result.keys()):
-            print(m_i, model_name)
             if f"model{m_i}" not in num_seeds_tot.keys():
                 num_seeds_tot[f"model{m_i}"] = dict()
                 num_exps_tot[f"model{m_i}"] = dict()

### 2023-01-10 paper/fse23/experiment.tex
fse23

--- 2022-06-07 paper/ase22/experiment.tex
@@
 %
-In this section, we present the setup of the experiments to evaluate
-the effectiveness of \tool{}. We address the following research
+In this section, we present the setup of our experiments to evaluate
+the effectiveness of \tool. We answer the following research
 questions (RQs):
@@
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:three}: Can \tool generate more diverse test cases
+\item \label{rq:three}: \textbf{Test Case Diversity.} Can \tool generate more diverse test cases
   than \Cklst?
-\item \label{rq:one}: Can \tool generate test sentences with correct sentiment labels?
-\item \label{rq:two}: Are \tool generated test sentences correctly categorized into a \lc?
-\item \label{rq:four}: Can \tool be useful to find root causes of bugs
-  in the \sa models?
+\item \label{rq:one}: \textbf{Test Oracle.}  Can \tool generate test sentences with correct sentiment labels?
+\item \label{rq:two}: \textbf{Capability Testing.} Are \tool generated test sentences correctly categorized into a \lc?
+% \item \label{rq:four}: \textbf{Usefulness of Test Inputs.} Can \tool be useful to find root causes of bugs
+%   in the \sa models?
 %% \item \label{rq:three}: How effective is our new test case generation
@@
 
-\paragraph{\textbf{NLP Models \& Dataset.}}
-We evaluate our approach on three learning-based \sa models
-implemented in Transformer library from the Hugging Face centralized
-Model Hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
+\paragraph*{\textbf{NLP Models \& Dataset}}
+We evaluate our approach on three learning-based \sa models released from the Hugging Face centralized
+model hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
 (\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
 language using a masked language modeling (MLM) objective, and
-fine-tuned on the \sa task. In this experiment, we use \Sstt \cite{socher2013sst} dataset for
+were fine-tuned on the \sa task. In this experiment, we used the \Sstt \cite{socher2013sst} dataset for
 searching the seeds in \tool. \Sstt is a
-corpus of movie review, and consists of 11,855 sentences
+corpus of movie review, consisting of 11,855 sentences
 with sentiment scores. We split the
-scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign 
+scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign them
 negative, neutral and positive labels, respectively. In addition,
-we use \Swn as the word sentiment dataset~\cite{baccianella2010sentiwordnet}. 
-\Swn is a publicly available English sentiment lexicons.  
+\Swn~\cite{baccianella2010sentiwordnet} is a publicly available dataset for English sentiment lexicons.  
 It provides lexical sentiment scores and the sentiment word labels 
-are categorized by implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
-%% \TODO{introduce details about each model}
+are categorized by implementing the rules.
+We used \Swn as both the generation and the expansion domain knowledge as shown in Figure \ref{fig:overview}.
 
-\paragraph{\textbf{Comparison Baseline.}}
-We compare \tool with
+\paragraph*{\textbf{Comparison Baseline}}
+We compared \tool with
 \Cklst,\footnote{https://github.com/marcotcr/checklist} a
-manual template-based approach to generate test cases. In this
-experiment, we used the \Cklst released \sa test cases which are
-generated from its publicly available jupyter notebook implementation.
-%% \TODO{introduce details about CHECKLIST}
+manual template and \lc based approach to generate test cases. In this evalaution, we used \Cklst's \sa test cases that are
+generated from its publicly available Jupyter Notebook implementation.
 
@@
 
-\paragraph{\textbf{RQ1.}}
-Recall that a key limitation of \Cklst is that its template-based
-approach relies on significant manual efforts and may not generate test cases that comprehensively cover the sentences
-in a linguistic capability. \tool, instead, automatically generates test cases based on a search
+\paragraph*{\textbf{RQ1}}
+Recall that \Cklst relies on significant manual efforts and may not generate comprehensive test cases in a linguistic capability. \tool, instead, automatically generates test cases based on a search
 dataset and the syntax in a large reference corpus. 
-We expect \tool can generate a more diverse test suite than \Cklst, and achieve
-more probable evaluation results.
+We expect \tool can generate a more diverse test suite than \Cklst.
 
-We first evaluate the three \sa
-models by testing them on the \tool generated test cases, reporting number of test cases and each model's failure rate in each linguistic capability.
+We first evaluate the three \sa models by testing them on the \tool  test cases, reporting number of test cases and each model's failure rate in each linguistic capability.
+Specifically, for each \lc, we randomly choose 50, 100 and 200 seeds , and expand test cases from these seeds.
+We selected subsets of seeds to be used for expansion because the syntax-based expansion phase may be expensive to run all the generated seeds.
+We tested the three models using both seed and expanded test cases.
+To account for the randomness in random seed selection, we repeated these experiments 3 times and report median number of test cases and each model's failure rate.
 
-Next,
-to measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
+We use two metrics to compare the diversity between the \tool generated seeds and the \Cklst test cases.
+
+\paragraph*{\selfbleu} We reuse the input diversity metric, 
+called \selfbleu, that Zhu \etal introduced~\cite{zhu2018texygen}. \bleu evaluates the token-level similarity.
+% Regarding that \selfbleu takes each sentence as hypothesis and rest in a collection of textual data as reference, we calculate \bleu scores for every pairs of hypothesis and each reference sentence.
+The \selfbleu is defined as the average \bleu scores over all reference sentences.
+% Since the \bleu score ranges from 0 as the least similar inputs to 1 as the most similar inputs,
+A higher \selfbleu score indicates less diversity in the test suite.
+In the experiment, we collected 50, 100 and 200 randomly selected \tool seeds and reported the median \selfbleu score over three trials for each group of seeds.
+% The median \selfbleu over 3 trials of the random collection of the 50, 100 and 200 seeds is defined as the final \selfbleu scores.
+For the comparison, \selfbleu scores of \Cklst test cases are calculated in the same manner.
+
+\paragraph*{Production rule coverage.} We propose a new metric to evaluate the syntactic diversity of the generated test suite.
+It is defined as the number of production rules used in a set of test sentences.
+In our experiments, we used the Berkeley Neural Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and collect all the production covered in a set of test sentences.
+We compared the \pdr between 50, 100 and 200 randomly selected \tool seeds and the \Cklst test cases.
+% collect the  of 50, 100 and 200 randomly selected \tool seeds and \Cklst test cases by the Berkeley Neural Parse~\cite{kitaev2018seedparser,kitaev2019seedparser}.
+Next, we traverse the parse trees and the \pdr score is calculated as the number of the production rules for the 50, 100 and 200 selected \tool seeds and \Cklst test cases.
+
+% ---
+
+In addition,
+we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
 where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
@@
 \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
-It is worth noting that a test sample with a statistical distribution similar to the training data would rarely be found in the corner case region.
-As a result, covering a larger corner case region means that the test suite is more likely to be buggy.
+It is worth noting that a test sample with a statistical distribution similar to the training data is rarely found in the corner case region.
+Thus, covering a larger corner case region indicates that the test suite is more likely to be buggy.
 
@@
 
-\noindent Equation \ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
-Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
+\noindent Equation \ref{eq:corner} defines the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
+Equation \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
 
@@
 
-\noindent The formal definition of our coverage metrics are shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
+\noindent The definition of our coverage metrics is shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produces outputs exceeding the upper or lower bounds, and SActCov measures the coverage of neurons that creates outputs exceeding the lower bound.
 Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.
@@
 
-\paragraph{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
+\paragraph*{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
 \tool generates test cases in two steps: specification-based seed
@@
 may generate seed/expanded sentences marked with incorrect sentiment
-labels or categorized into wrong linguistic capabilities. For example,
-the search rule and template defined in a linguistic capability may
-not always generate seed sentences in that capability or with the
-correct label.  To answer RQ2 and RQ3, we performed a manual study to
+labels or categorized into wrong linguistic capabilities.
+% For example,
+% the search rule and template defined in a linguistic capability may
+% not always generate seed sentences in that capability or with the
+% correct label. 
+To answer RQ2 and RQ3, we performed a manual study to
 measure the correctness of the sentiment labels and linguistic
@@
 
-In the manual study, we randomly sample 100 seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set).
+In the manual study, we randomly sample 100 \tool seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set).
 For each sampled seed sentence, we randomly obtain one of its expanded sentences.
 This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
-We recruited three participants of this study; all of them are graduate students with no knowledge about this work. 
+We recruited three participants for this study; all of them are graduate students with no knowledge about this work. 
 2 of them were assigned one set of sentences and the third was assigned the other set.
@@
 
-\begin{eqnarray}
-  sent\_consistency &= \frac{1}{\#Sample\cdot~}\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human}) \label{metric:srel} \\
-  LC\_relevancy_{AVG} &= \frac{1}{\#Sample\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
-\end{eqnarray}
+\begin{equation}
+\begin{aligned}
+  Label\_consistency = &\frac{1}{\#Sample}\\
+  &\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human})\label{metric:srel}\\
+\end{aligned}
+\end{equation}
+\begin{equation}
+\begin{aligned}
+  LC\_relevancy_{AVG} = &\frac{1}{\#Sample}\\
+  &\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
+\end{aligned}
+\end{equation}
 
@@
 normalized relevancy score between a sentence and its associated
-\lc. Higher average score means indicates the linguistic capability categorization by \tool is correct. We answer RQ2 and RQ3 using the metrics defined by
+\lc.
+The relevancy score is to evaluate the relevancy of the sentence to be used for testing model under test on the corresponding \lc.
+Higher average score means indicate the linguistic capability categorization by \tool is correct.
+We answer RQ2 and RQ3 using the metrics defined by
 Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
 respectively.
-
-\paragraph{\textbf{RQ4.}}
-
-To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
-Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input).
-Still, it is unclear why mutating one token will cause the model to produce misclassified results.
-We seek to help developers understand why such mutation will result in the misclassification. 
-Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences).
-Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.
-
-Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
-The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
-\begin{equation}
-    P(f(T(x)) = f(x)) \ge P_{thresh}
-    \label{eq:prob}
-\end{equation}
-To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}.
-We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
-We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
-Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$.
-Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).
 

### 2023-01-10 paper/fse23/intro.tex
fse23

--- 2022-08-30 paper/icse23/intro.tex
@@
 
-\Nlp (NLP) applications are growing exponentially.  As a result,
-trustworthiness in the quality of NLP applications has become critical
-for its practical use in the real world.  Therefore, quality assurance
-of NLP applications is essential in the software
-development process.  
-Researchers aim to improve the current practices of testing NLP models
-from three perspectives: (i) \emph{test input generation}, (ii)
-\emph{automated test oracle}, and (iii) \emph{meaningful quality
-  metrics}.
+\Nlp (NLP) applications are growing rapidly.  As a result,
+trustworthiness in how the quality of NLP applications is assessed becomes critical
+for its practical use in the real world.  
+Traditionally, the quality of NLP models is
+assessed using aggregated metrics. In particular, accuracy (i.e., the fraction of outputs that the
+model correctly predicts) is the most widely used metric for assessing
+the quality of classification models:
+higher accuracy suggests better quality of a model.
+However, all NLP models have their strengths and weaknesses; 
+using a single, aggregated metric (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.
+Such a metric fails to validate how well a model supports linguistic capabilities~\cite{geva2019we,gururangan2018annotation} (e.g., when the model always fails on certain type of inputs).
+% Not to
+% mention localizing and fixing the bugs found from the \ho
+% set (i.e., testing dataset, as opposed to training dataset). Therefore, this forced aggregation method not only fails to
+% validate the linguistic capability of the model, but it also makes the localization of the
+% causes of the inaccuracy more costly~\cite{wu2019errudite}.
 
-\noindent \textbf{Test input generation.} Currently, most testing of
-an NLP model uses existing, large textual corpus as the testing
-dataset to evaluate the model. This practice often overestimates
-the model performances from the \ho
-dataset~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
-  marcoACL2020checklist}.  The overestimation comes from the
-discrepancy between the distribution of the used dataset and the actual data
-distribution in real world. Oftentimes, the \ho dataset is not
-representative and is likely to introduce specific biases, leading to the
-decreased robustness of NLP models. In this regard, prior works
-have proposed techniques for testing the robustness of NLP models by crafting
-adversarial examples and attacking a model with them intentionally (i.e., adversarial testing)
-\cite{ribeiro2018sear,belinkov2018breaknmt,
-  rychalska2019wildnlp,iyyer2018adversarial}.
+To address this limitation, methodologies to assess an NLP model on a set of
+  linguistic capabilities have been introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. 
+A \lc
+explains a functionality of the input and output behavior for the
+NLP model under test. Typically, it describes certain type of inputs
+and outputs observed in real world for the target NLP task.
+% , ranging
+% from simple to complicated behaviors.
+Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
+models. 
+For example,  \Cklst~\cite{marcoACL2020checklist}, a behavioral testing framework for evaluating NLP models, defines a linguistic capability called ``Negated neutral should still be neutral'' to measure how accurately a \sa model understands that the negated neutral input has neutral sentiment
+\cite{marcoACL2020checklist}. 
+It requires the \sa model to
+output neutral sentiment on the negated neutral inputs. 
+Such evaluation methodology avoids the overestimation of the model performance as it measures the model performance on each functionality.
+% ,and the separate model performance
+% explain distribution of the performance over the linguistic capabilities
+In the end, testing through linguistic capabilities provides not only the overall model performance, but also the malfunction facets of the model.
 
-\noindent \textbf{Automated test oracle.} The current testing practice
-requires manual efforts to label the test oracles of the \ho
-data. The manual work is costly in terms of time consumption and its
-impact on the market price. Therefore, it necessitates automated test
-oracle generation for improving the testing process of NLP
-models. 
-% validity of the automation is ensured by the
-% correctness of test oracle.
-However, automatically generating test oracles may not always
-be feasible; predicting the correct test oracles remains one of main
-challenges. Along with this, motivated by software metamorphic testing 
-approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules. 
+ However, existing linguistic capability-based testing approaches rely on manually generated input templates, which need to be preset before generating tests. 
+ As a result, these templates are limited in their sentence
+structures. This restricts existing approaches' ability to comprehensively test linguistic capabilities.
+
+%  For example, \. \Cklst defines
+% task-relevant linguistic capabilities and generates test cases for
+% each \lc.
+
+% Therefore, quality assurance
+% of NLP applications is essential in the software
+% development process.  
+% Researchers aim to improve the current practices of testing NLP models
+% from three perspectives: (i) \emph{test input generation}, (ii)
+% \emph{automated test oracle}, and (iii) \emph{meaningful quality
+%   metrics}.
+
+% \noindent \textbf{Test input generation.} Currently, most testing of
+% an NLP model uses existing, large textual corpus as the testing
+% dataset to evaluate the model. This practice often overestimates
+% the model performances from the \ho
+% dataset~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
+%   marcoACL2020checklist}.  The overestimation comes from the
+% discrepancy between the distribution of the used dataset and the actual data
+% distribution in real world. Oftentimes, the \ho dataset is not
+% representative and is likely to introduce specific biases, leading to the
+% decreased robustness of NLP models. In this regard, prior works
+% have proposed techniques for testing the robustness of NLP models by crafting
+% adversarial examples and attacking a model with them intentionally (i.e., adversarial testing)
+% \cite{ribeiro2018sear,belinkov2018breaknmt,
+%   rychalska2019wildnlp,iyyer2018adversarial}.
+
+% \noindent \textbf{Automated test oracle.} The current testing practice
+% requires manual efforts to label the test oracles of the \ho
+% data. The manual work is costly in terms of time consumption and its
+% impact on the market price. Therefore, it necessitates automated test
+% oracle generation for improving the testing process of NLP
+% models. 
+% % validity of the automation is ensured by the
+% % correctness of test oracle.
+% However, automatically generating test oracles may not always
+% be feasible; predicting the correct test oracles remains one of main
+% challenges. Along with this, motivated by software metamorphic testing 
+% approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules. 
 % \TODO{Describe and Add citations to metamorphic testing techniques
@@
 % distribution between the dataset and real-world data.
-\noindent \textbf{Meaningful quality metrics.}  
-Traditionally, the quality of NLP models are
-represented by numbers in quality metrics. Especially, accuracy (i.e., the fraction of outputs that the
-model correctly predicts) is the most widely used metric for assessing
-the quality of classification models. 
-Generally, higher accuracy number suggests better quality of a model.
-However, all NLP models have their strengths and weaknesses, and 
-forcing aggregation statistics into a single number (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.  Not to
-mention localizing and fixing the bugs found from the \ho
-set (i.e., testing dataset, as opposed to training dataset). Therefore, this forced aggregation method not only fails to
-validate the linguistic capability of the model, but it also makes the localization of the
-causes of the inaccuracy more costly~\cite{wu2019errudite}.
+% \noindent \textbf{Meaningful quality metrics.}
+
 % Therefore behavioral testing
@@
 % find the bugs in the model.
-To address this limitation,
+
 % several approaches have been proposed to
@@
 % addition,
-Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
-evaluating NLP model on multiple linguistic
-capabilities~\cite{marcoACL2020checklist}. \Cklst defines
-task-relevant linguistic capabilities and generates test cases for
-each \lc.
 
-However, none of the above approaches satisfy all three requirements
-at the same time. First, the adversarial testing approaches merely
-focus on evaluating model robustness. They measure how sensitive the models
-are to input perturbations while do not
-evaluate linguistic functionalities.
-Second, the metamorphic testing approach requires understanding the characteristics of metamorphic relations between inputs
-and outputs. However, finding these remains one of the most challenging
-problems~\cite{segura2016metamorphictest}. In addition, metamorphic
-relation in textual data in the NLP domain has not been explored despite
-its importance.
-Third, \Cklst relies on manually generated input templates,
-which need to be preset before test input generation. Consequently,
-\Cklst templates are distributed in a limited range of their
-structures. This restricts \Cklst's ability to comprehensively test
-the linguistic capabilities.
+% However, none of the above approaches satisfy all three requirements
+% at the same time. First, the adversarial testing approaches merely
+% focus on evaluating model robustness. They measure how sensitive the models
+% are to input perturbations while do not
+% evaluate linguistic functionalities.
+% Second, the metamorphic testing approach requires understanding the characteristics of metamorphic relations between inputs
+% and outputs. However, finding these remains one of the most challenging
+% problems~\cite{segura2016metamorphictest}. In addition, metamorphic
+% relation in textual data in the NLP domain has not been explored despite
+% its importance.
+% Third,
 
-Despite \Cklst's limitations, assessing the quality of NLP models
-through the linguistic capabilities is a promising direction. Each \lc
-explains the functionality of the input and output behavior for the
-NLP model under test. Typically, it describes certain type of inputs
-and outputs observed in real world for the target NLP task, ranging
-from simple to complicated behaviors. Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
-models. For example, a linguistic capability of ``Negated neutral
-should still be neutral'' measures how accurately the \sa model
-understands that the negated neutral input has neutral sentiment
-\cite{marcoACL2020checklist}, requiring the \sa model to
-output neutral sentiment on the negated neutral inputs.  Such evaluation
-methodology on the specified functionalities avoids the
-overestimation of the model performance as it measures
-the model performance on each functionality.
-% ,and the separate model performance
-% explain distribution of the performance over the linguistic capabilities
-In the end, testing through linguistic capabilities provides not only
-the overall model performance, but also the malfunction facets of the
-model.
+% Despite \Cklst's limitations, assessing the quality of NLP models
+% through the linguistic capabilities is a promising direction.
 
-To satisfy all three requirements mentioned above, we present \tool,
-an automated evaluation method for comprehensive behavioral
-testing of NLP models on \sa task.  There are three main challenges
-that \tool overcomes to satisfy all three aforementioned requirements.
-\begin{description}
-\item[{\bf C1}] The test suite should cover diverse syntactic structures;
-\item[{\bf C2}] Each test case should be automatically categorized into a \lc;
-\item[{\bf C3}] The label of each test case should be automatically
+To address this issue, we present \tool,
+an automated linguistic capability-based testing framework for NLP models.  
+The goal of \tool is to generate a diverse linguistic capability-based test suite for a given model, both in terms of covering diverse linguistic structures and diverse model behaviors.
+To achieve the goal, \tool needs to address two challenges.
+\textit{(i) Capability-based Assessment.} Each test case should be automatically categorized into a \lc;
+and \textit{(ii) Automated Test Oracle.} The label of each test case should be automatically
   and accurately defined.
-\end{description}
+% \end{description}
 
-\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse.
-To address this challenge, \tool establishes specifications for evaluating
-a linguistic capability and searches suitable sentences that satisfy
-the specification from existing public dataset. In this process, \tool
-generates new inputs by mutating the searched sentences, used as seed
-inputs. \tool expands the grammar structure of a seed input and determines its
-available \pos to maintain structural naturalness.
+%\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse.
+To address this challenge, \tool establishes specifications for evaluating a linguistic capability and searches suitable sentences that satisfy the specification from existing public dataset.
+In this process, \tool generates new inputs by mutating the searched sentences, used as seed inputs.
+\tool expands the grammar structure of a seed input and determines its available \pos to maintain structural naturalness.
 
@@
 
-\noindent \textbf{C2.} Suitability of test sentences for evaluating NLP
-model on a \lc is determined by its relevancy to the
-\lc. Relevancy between a test sentence and its \lc is challenging to be maintained when transforming and expanding the test sentence.
+\noindent \textbf{Capability-based Assessment.} The suitability of test sentences for evaluating NLP
+models on a \lc is determined by its relevancy to this
+\lc. It is challenging to maintain relevancy between a test sentence and its \lc when transforming and expanding the test sentence.
 This is because the \lc is defined on a specific 
-mixture of syntax and semantics of the sentence, and there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc due to the inherent ambiguity of natural language sentences.
-To address this difficulty, \tool implements search rules
-and the transformation templates of \lcs. In addition, it analyzes the parse
+mixture of syntax and semantics of the sentence.
+Due to the inherent ambiguity of natural language sentences, there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc.
+To address this difficulty, \tool defines specifications (search rules
+and transformation templates) of \lcs, and analyzes the parse
 tree of the seed sentence to identify possible expansion.
@@
 
-\noindent \textbf{C3.} Last challenge is on automated test oracle.  For NLP tasks, test oracle is
-determined by understanding the meaning of texts. This requires domain knowledge of different NLP tasks.
+\noindent \textbf{Automated Test Oracle.}   For NLP model testing, test oracle is usually determined by understanding the semantics of texts and requires domain knowledge of different NLP tasks.
+Thus, the current testing practice requires manual efforts to create the test oracles of the \ho data.
+The manual work is costly in terms of time consumption.
+Therefore, it necessitates automated test oracle generation for improving the testing process of NLP models.
+% % validity of the automation is ensured by the
+% % correctness of test oracle.
+ However, automatically generating the  test oracles remains one of the main challenges in NLP software testing~\cite{huang2022aeon}. 
+ A few metamorphic testing approaches have been proposed in image recognition domain, but they require understanding the characteristics of metamorphic relations between inputs and outputs, which require domain expertise and non-trivial manual efforts ~\cite{segura2016metamorphictest}.
+In addition, it is even more challenging to design metamorphic relations in textual data because the semantics of nature language sentences can be greatly changed even by a slight perturbation to the sentences.
+ %Along with this, motivated by software metamorphic testing approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules.
+
 % Therefore, generation of test case ought to ensure the
 %correctness of its oracle allocation.
-In this work, as a first step, we consider \sa as the NLP task for the models under test. \tool obtains the
+In this work, as a first step, we consider \sa as the NLP task for the models under test. 
+\tool obtains the
 appropriate test oracle by implementing domain-specific
-knowledge on the word sentiment dataset and word suggestion model for validation of generated sentence and its oracle.
+knowledge on the word sentiment dataset and word suggestion model for validating the generated sentence and its oracle.
 
@@
 \item We design and implement an automated testing tool, \tool, and compared it with \Cklst.
-We find that the test cases generated by \tool achieves higher coverage than \Cklst when used for testing sentiment analysis models.
+We find that the test cases generated by \tool achieve 100\% higher coverage than \Cklst when used for testing sentiment analysis models.
 %
 \item We perform a manual study to
-measure the correctness of the sentiment labels and their \lcs produced by \tool. We find that \tool generates test cases that consistently label their sentiment correctly as human understanding.
+measure the correctness of the sentiment labels and their \lcs produced by \tool. We find that \tool generates test cases that consistently label their sentiment correctly as human.
 %
-\item We analyze the root causes of the misclassification in the sentiment analysis models, guided by \tool testing result.
-We find that seed and expanded test cases, produced by \tool, are usefulness of \tool for understanding bugs in the models.
+\item We analyze the root causes of misclassification in the sentiment analysis models, guided by \tool testing result.
+We find that seeds and expanded test cases produced by \tool are rather useful in helping developers understand bugs in the model.
 \end{itemize}

### 2023-01-10 paper/fse23/main.tex
fse23

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%% Use macros
\input{macros}

\begin{document}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\title{\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models}

%% \title{\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models}
\maketitle

%% Abstract
\input{abstract}

%% Contents
\input{intro}
\input{background}
\input{approach}
%\input{rq}
\input{experiment}
\input{result}
\input{threats}
\input{related}
\input{concl}
\clearpage

\bibliographystyle{IEEEtran}
\bibliography{bib}

%% Appendix
%\input{appendix}

%% Text of appendix \ldots

\end{document}

### 2023-01-10 paper/fse23/tables/lc-requirement-numbers.tex
fse23

--- 2022-08-31 paper/ase22/tables/lc-requirement-numbers.tex
@@
 \DefMacro{lc_7_search}{\textbf{Search}~pos\_sent=\{length: $<$ 20; label: pos\}, neutral\_sent=\{length: $<$ 20; label: neutral\}}
-\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{[`I wouldn't say,', `I do not think,', `I don't agree with,']+[neutral\_sent]+[`,']+[pos\_sent]\}}
+\DefMacro{lc_7_transform}{\textbf{Transform}~seed=\{[`I$\,$wouldn't$\,$say,', `I$\,$do$\,$not$\,$think,', `I$\,$don't$\,$agree$\,$with,']+[neutral\_sent]
++[`,']+[pos\_sent]\}}
 \DefMacro{lc_8_desc}{Author sentiment is more important than of others}
 \DefMacro{lc_8_search}{\textbf{Search}~pos\_sent=\{label:pos\}, neg\_sent=\{label: neg\}}
-\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\} $|$ \{[temp1]+[neg\_sent]+[temp2]+[pos\_sent]\} where temp1=\{[`Some people think that', `Many people agree with that', `They think that', `You agree with that'], temp2=[`but I think that']\}}
+\DefMacro{lc_8_transform}{\textbf{Transform}~seed=\{[temp1]+[pos\_sent]+[temp2]+[neg\_sent]\}$\;|\;$\{[temp1]+[neg\_sent]+[temp2]+ [pos\_sent]\} where temp1=\{[`Some people think that', `Many people agree with that', `They think that', `You agree with that'], temp2=[`but I think that']\}}
 \DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}

### 2023-01-10 paper/fse23/tables/test-results-all-numbers.tex
fse23

%% Automatically generated by pyutil.latex

\DefMacro{test-results-all-lc7}{Author sentiment is more important than of others}
\DefMacro{test-results-all-lc7-num-seeds}{68,284}
\DefMacro{test-results-all-lc7-num-exps}{492,817}
\DefMacro{test-results-all-model0-lc7-num-fail}{158,854}
\DefMacro{test-results-all-model0-lc7-num-failrate}{28.31}
\DefMacro{test-results-all-model0-lc7-num-pass-to-fail}{9,748}
\DefMacro{test-results-all-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-all-lc3-num-seeds}{67}
\DefMacro{test-results-all-lc3-num-exps}{503}
\DefMacro{test-results-all-model0-lc3-num-fail}{523}
\DefMacro{test-results-all-model0-lc3-num-failrate}{91.75}
\DefMacro{test-results-all-model0-lc3-num-pass-to-fail}{20}
\DefMacro{test-results-all-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-all-lc4-num-seeds}{26}
\DefMacro{test-results-all-lc4-num-exps}{194}
\DefMacro{test-results-all-model0-lc4-num-fail}{207}
\DefMacro{test-results-all-model0-lc4-num-failrate}{94.09}
\DefMacro{test-results-all-model0-lc4-num-pass-to-fail}{11}
\DefMacro{test-results-all-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-all-lc6-num-seeds}{24,328}
\DefMacro{test-results-all-lc6-num-exps}{190,723}
\DefMacro{test-results-all-model0-lc6-num-fail}{195,525}
\DefMacro{test-results-all-model0-lc6-num-failrate}{90.92}
\DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{2,014}
\DefMacro{test-results-all-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-all-lc5-num-seeds}{18,576}
\DefMacro{test-results-all-lc5-num-exps}{102,304}
\DefMacro{test-results-all-model0-lc5-num-fail}{120,451}
\DefMacro{test-results-all-model0-lc5-num-failrate}{99.65}
\DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{71}
\DefMacro{test-results-all-lc9}{Parsing sentiment in (question, no) form}
\DefMacro{test-results-all-lc9-num-seeds}{15,483}
\DefMacro{test-results-all-lc9-num-exps}{108,412}
\DefMacro{test-results-all-model0-lc9-num-fail}{93,329}
\DefMacro{test-results-all-model0-lc9-num-failrate}{75.33}
\DefMacro{test-results-all-model0-lc9-num-pass-to-fail}{1,891}
\DefMacro{test-results-all-lc2}{Sentiment change over time, present should prevail}
\DefMacro{test-results-all-lc2-num-seeds}{75,159}
\DefMacro{test-results-all-lc2-num-exps}{507,091}
\DefMacro{test-results-all-model0-lc2-num-fail}{134,641}
\DefMacro{test-results-all-model0-lc2-num-failrate}{23.12}
\DefMacro{test-results-all-model0-lc2-num-pass-to-fail}{18,510}
\DefMacro{test-results-all-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-all-lc0-num-seeds}{19}
\DefMacro{test-results-all-lc0-num-exps}{51}
\DefMacro{test-results-all-model0-lc0-num-fail}{60}
\DefMacro{test-results-all-model0-lc0-num-failrate}{85.71}
\DefMacro{test-results-all-model0-lc0-num-pass-to-fail}{9}
\DefMacro{test-results-all-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-all-lc1-num-seeds}{160}
\DefMacro{test-results-all-lc1-num-exps}{262}
\DefMacro{test-results-all-model0-lc1-num-fail}{25}
\DefMacro{test-results-all-model0-lc1-num-failrate}{5.92}
\DefMacro{test-results-all-model0-lc1-num-pass-to-fail}{5}
\DefMacro{test-results-all-lc8}{Parsing sentiment in (question, yes) form}
\DefMacro{test-results-all-lc8-num-seeds}{15,465}
\DefMacro{test-results-all-lc8-num-exps}{106,907}
\DefMacro{test-results-all-model0-lc8-num-fail}{7,361}
\DefMacro{test-results-all-model0-lc8-num-failrate}{6.02}
\DefMacro{test-results-all-model0-lc8-num-pass-to-fail}{1,646}
\DefMacro{test-results-all-model1-lc7-num-fail}{112,390}
\DefMacro{test-results-all-model1-lc7-num-failrate}{20.03}
\DefMacro{test-results-all-model1-lc7-num-pass-to-fail}{9,453}
\DefMacro{test-results-all-model1-lc3-num-fail}{498}
\DefMacro{test-results-all-model1-lc3-num-failrate}{87.37}
\DefMacro{test-results-all-model1-lc3-num-pass-to-fail}{9}
\DefMacro{test-results-all-model1-lc4-num-fail}{204}
\DefMacro{test-results-all-model1-lc4-num-failrate}{92.73}
\DefMacro{test-results-all-model1-lc4-num-pass-to-fail}{6}
\DefMacro{test-results-all-model1-lc6-num-fail}{157,635}
\DefMacro{test-results-all-model1-lc6-num-failrate}{73.30}
\DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,289}
\DefMacro{test-results-all-model1-lc5-num-fail}{120,054}
\DefMacro{test-results-all-model1-lc5-num-failrate}{99.32}
\DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{93}
\DefMacro{test-results-all-model1-lc9-num-fail}{105,319}
\DefMacro{test-results-all-model1-lc9-num-failrate}{85.01}
\DefMacro{test-results-all-model1-lc9-num-pass-to-fail}{1,764}
\DefMacro{test-results-all-model1-lc2-num-fail}{283,614}
\DefMacro{test-results-all-model1-lc2-num-failrate}{48.71}
\DefMacro{test-results-all-model1-lc2-num-pass-to-fail}{17,142}
\DefMacro{test-results-all-model1-lc0-num-fail}{55}
\DefMacro{test-results-all-model1-lc0-num-failrate}{78.57}
\DefMacro{test-results-all-model1-lc0-num-pass-to-fail}{2}
\DefMacro{test-results-all-model1-lc1-num-fail}{39}
\DefMacro{test-results-all-model1-lc1-num-failrate}{9.24}
\DefMacro{test-results-all-model1-lc1-num-pass-to-fail}{14}
\DefMacro{test-results-all-model1-lc8-num-fail}{6,510}
\DefMacro{test-results-all-model1-lc8-num-failrate}{5.32}
\DefMacro{test-results-all-model1-lc8-num-pass-to-fail}{1,519}
\DefMacro{test-results-all-model2-lc7-num-fail}{170,198}
\DefMacro{test-results-all-model2-lc7-num-failrate}{30.33}
\DefMacro{test-results-all-model2-lc7-num-pass-to-fail}{13,870}
\DefMacro{test-results-all-model2-lc3-num-fail}{494}
\DefMacro{test-results-all-model2-lc3-num-failrate}{86.67}
\DefMacro{test-results-all-model2-lc3-num-pass-to-fail}{6}
\DefMacro{test-results-all-model2-lc4-num-fail}{213}
\DefMacro{test-results-all-model2-lc4-num-failrate}{96.82}
\DefMacro{test-results-all-model2-lc4-num-pass-to-fail}{10}
\DefMacro{test-results-all-model2-lc6-num-fail}{180,865}
\DefMacro{test-results-all-model2-lc6-num-failrate}{84.10}
\DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,130}
\DefMacro{test-results-all-model2-lc5-num-fail}{118,910}
\DefMacro{test-results-all-model2-lc5-num-failrate}{98.37}
\DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{334}
\DefMacro{test-results-all-model2-lc9-num-fail}{117,664}
\DefMacro{test-results-all-model2-lc9-num-failrate}{94.97}
\DefMacro{test-results-all-model2-lc9-num-pass-to-fail}{594}
\DefMacro{test-results-all-model2-lc2-num-fail}{363,619}
\DefMacro{test-results-all-model2-lc2-num-failrate}{62.45}
\DefMacro{test-results-all-model2-lc2-num-pass-to-fail}{16,527}
\DefMacro{test-results-all-model2-lc0-num-fail}{68}
\DefMacro{test-results-all-model2-lc0-num-failrate}{97.14}
\DefMacro{test-results-all-model2-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-all-model2-lc1-num-fail}{18}
\DefMacro{test-results-all-model2-lc1-num-failrate}{4.27}
\DefMacro{test-results-all-model2-lc1-num-pass-to-fail}{10}
\DefMacro{test-results-all-model2-lc8-num-fail}{5,702}
\DefMacro{test-results-all-model2-lc8-num-failrate}{4.66}
\DefMacro{test-results-all-model2-lc8-num-pass-to-fail}{1,193}

### 2023-01-10 paper/fse23/tables/test-results-hs-all-numbers.tex
fse23

%% Automatically generated by pyutil.latex

\DefMacro{test-results-hs-lc2}{Dehumanisation (explicit)}
\DefMacro{test-results-hs-lc2-num-seeds}{140}
\DefMacro{test-results-hs-lc2-num-exps}{3,124}
\DefMacro{test-results-hs-model0-lc2-num-all-fail}{3,220}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{98.66}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{98.65}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{18}
\DefMacro{test-results-hs-lc18}{Denouncements of hate that quote it}
\DefMacro{test-results-hs-lc18-num-seeds}{45,616}
\DefMacro{test-results-hs-lc18-num-exps}{300,704}
\DefMacro{test-results-hs-model0-lc18-num-all-fail}{48,804}
\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{13.78}
\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{14.14}
\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{14.09}
\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{4,831}
\DefMacro{test-results-hs-lc1}{Description using very negative attributes (explicit)}
\DefMacro{test-results-hs-lc1-num-seeds}{140}
\DefMacro{test-results-hs-lc1-num-exps}{2,959}
\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,067}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{98.99}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{98.97}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{23}
\DefMacro{test-results-hs-lc4}{Direct threat}
\DefMacro{test-results-hs-lc4-num-seeds}{133}
\DefMacro{test-results-hs-lc4-num-exps}{2,689}
\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,770}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{97.74}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{98.18}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{98.16}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{9}
\DefMacro{test-results-hs-lc0}{Expression of strong negative emotions (explicit)}
\DefMacro{test-results-hs-lc0-num-seeds}{140}
\DefMacro{test-results-hs-lc0-num-exps}{799}
\DefMacro{test-results-hs-model0-lc0-num-all-fail}{920}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{98.12}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{97.98}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{22}
\DefMacro{test-results-hs-lc10}{Hate expressed through reference in subsequent clauses}
\DefMacro{test-results-hs-lc10-num-seeds}{11,968}
\DefMacro{test-results-hs-lc10-num-exps}{44,890}
\DefMacro{test-results-hs-model0-lc10-num-all-fail}{49,929}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{60.60}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{95.07}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{87.81}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,169}
\DefMacro{test-results-hs-lc11}{Hate expressed through reference in subsequent sentences}
\DefMacro{test-results-hs-lc11-num-seeds}{11,968}
\DefMacro{test-results-hs-lc11-num-exps}{42,840}
\DefMacro{test-results-hs-model0-lc11-num-all-fail}{47,294}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{58.92}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{93.94}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{86.29}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,726}
\DefMacro{test-results-hs-lc12}{Hate expressed using negated positive statement}
\DefMacro{test-results-hs-lc12-num-seeds}{23,379}
\DefMacro{test-results-hs-lc12-num-exps}{126,742}
\DefMacro{test-results-hs-model0-lc12-num-all-fail}{145,761}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{97.03}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{97.11}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{2,290}
\DefMacro{test-results-hs-lc8}{Hate expressed using profanity}
\DefMacro{test-results-hs-lc8-num-seeds}{1,842}
\DefMacro{test-results-hs-lc8-num-exps}{49,743}
\DefMacro{test-results-hs-model0-lc8-num-all-fail}{50,158}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{97.34}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{97.23}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{97.23}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{164}
\DefMacro{test-results-hs-lc6}{Hate expressed using slur}
\DefMacro{test-results-hs-lc6-num-seeds}{805}
\DefMacro{test-results-hs-lc6-num-exps}{17,318}
\DefMacro{test-results-hs-model0-lc6-num-all-fail}{17,597}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{70}
\DefMacro{test-results-hs-lc15}{Hate phrased as a opinion}
\DefMacro{test-results-hs-lc15-num-seeds}{22,808}
\DefMacro{test-results-hs-lc15-num-exps}{160,927}
\DefMacro{test-results-hs-model0-lc15-num-all-fail}{178,058}
\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{97.25}
\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{96.86}
\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{96.91}
\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,078}
\DefMacro{test-results-hs-lc14}{Hate phrased as a question}
\DefMacro{test-results-hs-lc14-num-seeds}{22,808}
\DefMacro{test-results-hs-lc14-num-exps}{185,267}
\DefMacro{test-results-hs-model0-lc14-num-all-fail}{202,023}
\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{97.37}
\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{97.06}
\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{97.09}
\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{2,956}
\DefMacro{test-results-hs-lc3}{Implicit derogation}
\DefMacro{test-results-hs-lc3-num-seeds}{140}
\DefMacro{test-results-hs-lc3-num-exps}{5,664}
\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,730}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{97.86}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{98.75}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{98.73}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{30}
\DefMacro{test-results-hs-lc16}{Neutral statements using protected group identifiers}
\DefMacro{test-results-hs-lc16-num-seeds}{5}
\DefMacro{test-results-hs-lc16-num-exps}{9}
\DefMacro{test-results-hs-model0-lc16-num-all-fail}{1}
\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{20.00}
\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{7.14}
\DefMacro{test-results-hs-model0-lc16-num-pass-to-fail}{0}
\DefMacro{test-results-hs-lc9}{Non-Hateful use of profanity}
\DefMacro{test-results-hs-lc9-num-seeds}{701}
\DefMacro{test-results-hs-lc9-num-exps}{15,761}
\DefMacro{test-results-hs-model0-lc9-num-all-fail}{11,939}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{71.04}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{72.59}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{72.52}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{75}
\DefMacro{test-results-hs-lc13}{Non-hate expressed using negated hateful statement}
\DefMacro{test-results-hs-lc13-num-seeds}{34,212}
\DefMacro{test-results-hs-lc13-num-exps}{243,739}
\DefMacro{test-results-hs-model0-lc13-num-all-fail}{77,191}
\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{26.90}
\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{27.89}
\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{27.77}
\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{5,222}
\DefMacro{test-results-hs-lc7}{Non-hateful use of slur}
\DefMacro{test-results-hs-lc7-num-seeds}{395}
\DefMacro{test-results-hs-lc7-num-exps}{7,881}
\DefMacro{test-results-hs-model0-lc7-num-all-fail}{2,739}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{30.89}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{33.21}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{33.10}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{44}
\DefMacro{test-results-hs-lc17}{Positive statements using protected group identifiers}
\DefMacro{test-results-hs-lc17-num-seeds}{41}
\DefMacro{test-results-hs-lc17-num-exps}{182}
\DefMacro{test-results-hs-model0-lc17-num-all-fail}{14}
\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{4.88}
\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{6.59}
\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{6.28}
\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{1}
\DefMacro{test-results-hs-lc5}{Threat as normative statement}
\DefMacro{test-results-hs-lc5-num-seeds}{140}
\DefMacro{test-results-hs-lc5-num-exps}{4,163}
\DefMacro{test-results-hs-model0-lc5-num-all-fail}{4,261}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{99.29}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{99.02}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{99.02}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{1}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{87}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{2.78}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{2.67}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{31}
\DefMacro{test-results-hs-model1-lc18-num-all-fail}{346,320}
\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc0-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc10-num-all-fail}{5,984}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{10.52}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{5,984}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{10.92}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc15-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc14-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc3-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc16-num-all-fail}{14}
\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc9-num-all-fail}{16,462}
\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc13-num-all-fail}{277,951}
\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc7-num-all-fail}{8,276}
\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc17-num-all-fail}{223}
\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc5-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{0}

### 2023-01-10 paper/fse23/tables/test-results-hs-bl-table.tex
fse23

%% Automatically generated by pyutil.latex

\begin{table*}[htbp]
\begin{small}
\begin{center}
\caption{\TestResultsHsBlTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate}\\
\midrule
\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-bl-lc0}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc0-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-bl-lc1}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc1-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-bl-lc2}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc2-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-bl-lc3}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc3-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-bl-lc4}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc4-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-bl-lc5}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc5-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-bl-lc6}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc6-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc6-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc6-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc6-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc6-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-bl-lc7}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc7-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc7-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc7-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc7-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc7-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-bl-lc8}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc8-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc8-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc8-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc8-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc8-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-bl-lc9}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc9-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc9-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc9-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc9-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc9-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-bl-lc10}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc10-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc10-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc10-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc10-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc10-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-bl-lc11}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc11-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc11-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc11-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc11-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc11-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-bl-lc12}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc12-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc12-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc12-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc12-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc12-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-bl-lc13}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc13-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc13-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc13-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc13-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc13-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-bl-lc14}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc14-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc14-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc14-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc14-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc14-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-bl-lc15}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc15-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc15-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc15-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc15-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc15-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-bl-lc16}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc16-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc16-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc16-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc16-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc16-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-bl-lc17}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc17-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc17-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc17-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc17-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc17-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-bl-lc18}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc18-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc18-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc18-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc18-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc18-num-failrate}\\
\hline
\multirow{2}{*}{\parbox{8cm}{LC20: \UseMacro{test-results-hs-bl-lc19}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc19-num-tcs}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc19-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-bl-model0-lc19-num-failrate}\\
 & & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc19-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-bl-model1-lc19-num-failrate}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2023-01-10 paper/fse23/code/checklist_template2.py

@@ -1,0 +1,17 @@
+air_noun = [(*@\label{code:tempex:airnoun:1}@*)
+    'flight', 'seat', 'pilot', 'staff', ... 
+](*@\label{code:tempex:airnoun:2}@*)
+pos_adj = [(*@\label{code:tempex:posadj:1}@*)
+    'good', 'great', 'excellent', 'amazing', ...
+](*@\label{code:tempex:posadj:2}@*)
+neg_adj = [(*@\label{code:tempex:negadj:1}@*)
+    'awful', 'bad', 'horrible', 'weird', ...
+](*@\label{code:tempex:negadj:2}@*)
+t = editor.template('{it} {air_noun} {be} {pos_adj}.', (*@\label{code:tempex:template:1}@*)
+                    it=['The', 'This', 'That'], be=['is', 'was'], labels=2, save=True)(*@\label{code:tempex:itbe}@*)
+t += editor.template('{it} {be} {a:pos_adj} {air_noun}.', 
+                     it=['It', 'This', 'That'], be=['is', 'was'], labels=2, save=True)
+t += ...
+t += editor.template('{it} {be} {a:neg_adj} {air_noun}.', 
+                     it=['It', 'This', 'That'], be=['is', 'was'], labels=0, save=True)(*@\label{code:tempex:template:2}@*)
+

### 2023-01-10 python/hs/utils/Macros.py

@@ -17,7 +17,7 @@ class Macros:
     
     download_dir: Path = storage_dir / '_downloads' # /glusterfs/data/jxl115330/s2lct/_downloads
     log_dir: Path = storage_dir / '_logs' # /glusterfs/data/jxl115330/s2lct/_logs
-    paper_dir = root_dir / 'paper' / 'icse23'
+    paper_dir = root_dir / 'paper' / 'fse23'
     dataset_dir = download_dir / 'datasets'
 
     FMT_INT = "{:,d}"

### 2023-01-10 python/sa/utils/Macros.py

@@ -17,7 +17,7 @@ class Macros:
     
     download_dir: Path = storage_dir / "_downloads"
     log_dir: Path = storage_dir / "_logs"
-    paper_dir = root_dir / "paper" / "icse23"
+    paper_dir = root_dir / "paper" / "fse23"
     dataset_dir = download_dir / "datasets"
 
     FMT_INT = "{:,d}"

### 2023-01-10 paper/fse23/intro.tex
rewrite intro

@@
 \Nlp (NLP) applications are growing rapidly.  As a result,
-trustworthiness in how the quality of NLP applications is assessed becomes critical
-for its practical use in the real world.  
-Traditionally, the quality of NLP models is
-assessed using aggregated metrics. In particular, accuracy (i.e., the fraction of outputs that the
-model correctly predicts) is the most widely used metric for assessing
-the quality of classification models:
-higher accuracy suggests better quality of a model.
-However, all NLP models have their strengths and weaknesses; 
-using a single, aggregated metric (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.
-Such a metric fails to validate how well a model supports linguistic capabilities~\cite{geva2019we,gururangan2018annotation} (e.g., when the model always fails on certain type of inputs).
+trustworthiness in how the quality of NLP applications is assessed
+becomes critical for its practical use in the real world.
+Traditionally, the quality of NLP models is assessed using aggregated
+metrics. In particular, accuracy (i.e., the fraction of outputs that
+the model correctly predicts) is the most widely used metric for
+assessing the quality of classification models: higher accuracy
+suggests better quality of a model.  However, all NLP models have
+their strengths and weaknesses; using a single, aggregated metric
+(i.e., accuracy) makes it difficult for the users to assess the
+capabilities of NLP models.  Such a metric fails to validate how well
+a model supports linguistic
+capabilities~\cite{geva2019we,gururangan2018annotation} (e.g., when
+the model always fails on certain type of inputs).
 % Not to
@@
 
-To address this limitation, methodologies to assess an NLP model on a set of
-  linguistic capabilities have been introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. 
-A \lc
-explains a functionality of the input and output behavior for the
-NLP model under test. Typically, it describes certain type of inputs
-and outputs observed in real world for the target NLP task.
+\jl{To address this limitation, increasing number of evaluation
+  methodologies has been conducted to measure and obtain the
+  trustworthiness of a NLP model. First, as the NLP model is still
+  fragile to adversarial attacks and decreases trustworthness of the
+  NLP model, adversarial examples of the model generated by
+  perturbations to the input are used to measure the robustness of the
+  model.~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack,udeshi2019ogma}. Also,
+  fairness, specific bias in the NLP model such as gender and races,
+  has been
+  evaluated~\cite{soremekun2020astraea,udeshi2018fairnesstest}. Additionally,
+  methodologies to assess an NLP model on a set of \lcs have been
+  introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. Compared
+  with the aforementioned testing aspects, a \lc explains a more
+  comprehensive functionalities of the input and output behavior for
+  the NLP model under test. Typically, it describes certain type of
+  inputs and outputs observed in real world for the target NLP task.
+}
 % , ranging
 % from simple to complicated behaviors.
-Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
-models. 
-For example,  \Cklst~\cite{marcoACL2020checklist}, a behavioral testing framework for evaluating NLP models, defines a linguistic capability called ``Negated neutral should still be neutral'' to measure how accurately a \sa model understands that the negated neutral input has neutral sentiment
-\cite{marcoACL2020checklist}. 
-It requires the \sa model to
-output neutral sentiment on the negated neutral inputs. 
-Such evaluation methodology avoids the overestimation of the model performance as it measures the model performance on each functionality.
+Testing the linguistic capabilities allows the model developers to
+better understand the capabilities and potential issues of the NLP
+models.  For example, \Cklst~\cite{marcoACL2020checklist}, a
+behavioral testing framework for evaluating NLP models, defines a
+linguistic capability called ``Negated neutral should still be
+neutral'' to measure how accurately a \sa model understands that the
+negated neutral input has neutral sentiment
+\cite{marcoACL2020checklist}.  It requires the \sa model to output
+neutral sentiment on the negated neutral inputs.  Such evaluation
+methodology avoids the overestimation of the model performance as it
+measures the model performance on each functionality.
 % ,and the separate model performance
 % explain distribution of the performance over the linguistic capabilities
-In the end, testing through linguistic capabilities provides not only the overall model performance, but also the malfunction facets of the model.
+In the end, testing through linguistic capabilities provides not only
+the overall model performance, but also the malfunction facets of the
+model.
 
- However, existing linguistic capability-based testing approaches rely on manually generated input templates, which need to be preset before generating tests. 
- As a result, these templates are limited in their sentence
-structures. This restricts existing approaches' ability to comprehensively test linguistic capabilities.
+ However, existing linguistic capability-based testing approaches rely
+ on manually generated input templates, which need to be preset before
+ generating tests.  As a result, these templates are limited in their
+ sentence structures. This restricts existing approaches' ability to
+ comprehensively test linguistic capabilities.
 

### 2023-01-10 paper/fse23/intro.tex
intro

@@
 
- However, existing linguistic capability-based testing approaches rely
- on manually generated input templates, which need to be preset before
- generating tests.  As a result, these templates are limited in their
- sentence structures. This restricts existing approaches' ability to
- comprehensively test linguistic capabilities.
+However, existing linguistic capability-based testing approaches
+generate inputs only relying on word substitution, and need to be
+preset before generating tests.  As a result, these templates are
+limited in their sentence structures. This restricts existing
+approaches' ability to comprehensively test linguistic capabilities.
 

### 2023-01-11 paper/ase22/tables/test-results-bl-hs-all-numbers.tex
related work

%% Automatically generated by pyutil.latex

\DefMacro{test-results-bl-lc19}{Counter speech::Denouncements of hate that make direct reference to it}
\DefMacro{test-results-bl-lc19-num-tcs}{141}
\DefMacro{test-results-bl-model0-lc19-num-fail}{[141]}
\DefMacro{test-results-bl-model0-lc19-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc18}{Counter speech::Denouncements of hate that quote it}
\DefMacro{test-results-bl-lc18-num-tcs}{173}
\DefMacro{test-results-bl-model0-lc18-num-fail}{[173]}
\DefMacro{test-results-bl-model0-lc18-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc2}{Derogation::Dehumanisation (explicit)}
\DefMacro{test-results-bl-lc2-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc2-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc2-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc1}{Derogation::Description using very negative attributes (explicit)}
\DefMacro{test-results-bl-lc1-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc1-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc1-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc0}{Derogation::Expression of strong negative emotions (explicit)}
\DefMacro{test-results-bl-lc0-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc0-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc0-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc3}{Derogation::Implicit derogation}
\DefMacro{test-results-bl-lc3-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc3-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc3-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc12}{Negation::Hate expressed using negated positive statement}
\DefMacro{test-results-bl-lc12-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc12-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc12-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc13}{Negation::Non-hate expressed using negated hateful statement}
\DefMacro{test-results-bl-lc13-num-tcs}{133}
\DefMacro{test-results-bl-model0-lc13-num-fail}{[133]}
\DefMacro{test-results-bl-model0-lc13-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc16}{Non-hate grp. ident.::Neutral statements using protected group identifiers}
\DefMacro{test-results-bl-lc16-num-tcs}{126}
\DefMacro{test-results-bl-model0-lc16-num-fail}{[126]}
\DefMacro{test-results-bl-model0-lc16-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc17}{Non-hate grp. ident.::Positive statements using protected group identifiers}
\DefMacro{test-results-bl-lc17-num-tcs}{189}
\DefMacro{test-results-bl-model0-lc17-num-fail}{[189]}
\DefMacro{test-results-bl-model0-lc17-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc14}{Phrasing::Hate phrased as a question}
\DefMacro{test-results-bl-lc14-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc14-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc14-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc8}{Profanity usage::Hate expressed using profanity}
\DefMacro{test-results-bl-lc8-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc8-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc8-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc9}{Profanity usage::Non-Hateful use of profanity}
\DefMacro{test-results-bl-lc9-num-tcs}{100}
\DefMacro{test-results-bl-model0-lc9-num-fail}{[100]}
\DefMacro{test-results-bl-model0-lc9-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc10}{Pronoun reference::Hate expressed through reference in subsequent clauses}
\DefMacro{test-results-bl-lc10-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc10-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc10-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc11}{Pronoun reference::Hate expressed through reference in subsequent sentences}
\DefMacro{test-results-bl-lc11-num-tcs}{133}
\DefMacro{test-results-bl-model0-lc11-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc11-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc6}{Slur usage::Hate expressed using slur}
\DefMacro{test-results-bl-lc6-num-tcs}{144}
\DefMacro{test-results-bl-model0-lc6-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc6-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc7}{Slur usage::Non-hateful use of slur}
\DefMacro{test-results-bl-lc7-num-tcs}{111}
\DefMacro{test-results-bl-model0-lc7-num-fail}{[111]}
\DefMacro{test-results-bl-model0-lc7-num-failrate}{[100.0]}
\DefMacro{test-results-bl-lc4}{Threatening language::Direct threat}
\DefMacro{test-results-bl-lc4-num-tcs}{133}
\DefMacro{test-results-bl-model0-lc4-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc4-num-failrate}{[0.0]}
\DefMacro{test-results-bl-lc5}{Threatening language::Threat as normative statement}
\DefMacro{test-results-bl-lc5-num-tcs}{140}
\DefMacro{test-results-bl-model0-lc5-num-fail}{[0]}
\DefMacro{test-results-bl-model0-lc5-num-failrate}{[0.0]}
\DefMacro{test-results-bl-model1-lc19-num-fail}{[5]}
\DefMacro{test-results-bl-model1-lc19-num-failrate}{[3.5460992907801416]}
\DefMacro{test-results-bl-model1-lc18-num-fail}{[4]}
\DefMacro{test-results-bl-model1-lc18-num-failrate}{[2.3121387283236996]}
\DefMacro{test-results-bl-model1-lc2-num-fail}{[138]}
\DefMacro{test-results-bl-model1-lc2-num-failrate}{[98.57142857142857]}
\DefMacro{test-results-bl-model1-lc1-num-fail}{[136]}
\DefMacro{test-results-bl-model1-lc1-num-failrate}{[97.14285714285714]}
\DefMacro{test-results-bl-model1-lc0-num-fail}{[134]}
\DefMacro{test-results-bl-model1-lc0-num-failrate}{[95.71428571428571]}
\DefMacro{test-results-bl-model1-lc3-num-fail}{[135]}
\DefMacro{test-results-bl-model1-lc3-num-failrate}{[96.42857142857143]}
\DefMacro{test-results-bl-model1-lc12-num-fail}{[136]}
\DefMacro{test-results-bl-model1-lc12-num-failrate}{[97.14285714285714]}
\DefMacro{test-results-bl-model1-lc13-num-fail}{[5]}
\DefMacro{test-results-bl-model1-lc13-num-failrate}{[3.7593984962406015]}
\DefMacro{test-results-bl-model1-lc16-num-fail}{[3]}
\DefMacro{test-results-bl-model1-lc16-num-failrate}{[2.380952380952381]}
\DefMacro{test-results-bl-model1-lc17-num-fail}{[8]}
\DefMacro{test-results-bl-model1-lc17-num-failrate}{[4.232804232804233]}
\DefMacro{test-results-bl-model1-lc14-num-fail}{[137]}
\DefMacro{test-results-bl-model1-lc14-num-failrate}{[97.85714285714286]}
\DefMacro{test-results-bl-model1-lc8-num-fail}{[135]}
\DefMacro{test-results-bl-model1-lc8-num-failrate}{[96.42857142857143]}
\DefMacro{test-results-bl-model1-lc9-num-fail}{[1]}
\DefMacro{test-results-bl-model1-lc9-num-failrate}{[1.0]}
\DefMacro{test-results-bl-model1-lc10-num-fail}{[132]}
\DefMacro{test-results-bl-model1-lc10-num-failrate}{[94.28571428571429]}
\DefMacro{test-results-bl-model1-lc11-num-fail}{[127]}
\DefMacro{test-results-bl-model1-lc11-num-failrate}{[95.48872180451127]}
\DefMacro{test-results-bl-model1-lc6-num-fail}{[142]}
\DefMacro{test-results-bl-model1-lc6-num-failrate}{[98.61111111111111]}
\DefMacro{test-results-bl-model1-lc7-num-fail}{[2]}
\DefMacro{test-results-bl-model1-lc7-num-failrate}{[1.8018018018018018]}
\DefMacro{test-results-bl-model1-lc4-num-fail}{[132]}
\DefMacro{test-results-bl-model1-lc4-num-failrate}{[99.24812030075188]}
\DefMacro{test-results-bl-model1-lc5-num-fail}{[136]}
\DefMacro{test-results-bl-model1-lc5-num-failrate}{[97.14285714285714]}
\DefMacro{test-results-bl-model2-lc19-num-fail}{[1]}
\DefMacro{test-results-bl-model2-lc19-num-failrate}{[0.7092198581560284]}
\DefMacro{test-results-bl-model2-lc18-num-fail}{[4]}
\DefMacro{test-results-bl-model2-lc18-num-failrate}{[2.3121387283236996]}
\DefMacro{test-results-bl-model2-lc2-num-fail}{[138]}
\DefMacro{test-results-bl-model2-lc2-num-failrate}{[98.57142857142857]}
\DefMacro{test-results-bl-model2-lc1-num-fail}{[138]}
\DefMacro{test-results-bl-model2-lc1-num-failrate}{[98.57142857142857]}
\DefMacro{test-results-bl-model2-lc0-num-fail}{[136]}
\DefMacro{test-results-bl-model2-lc0-num-failrate}{[97.14285714285714]}
\DefMacro{test-results-bl-model2-lc3-num-fail}{[137]}
\DefMacro{test-results-bl-model2-lc3-num-failrate}{[97.85714285714286]}
\DefMacro{test-results-bl-model2-lc12-num-fail}{[138]}
\DefMacro{test-results-bl-model2-lc12-num-failrate}{[98.57142857142857]}
\DefMacro{test-results-bl-model2-lc13-num-fail}{[2]}
\DefMacro{test-results-bl-model2-lc13-num-failrate}{[1.5037593984962405]}
\DefMacro{test-results-bl-model2-lc16-num-fail}{[0]}
\DefMacro{test-results-bl-model2-lc16-num-failrate}{[0.0]}
\DefMacro{test-results-bl-model2-lc17-num-fail}{[3]}
\DefMacro{test-results-bl-model2-lc17-num-failrate}{[1.5873015873015872]}
\DefMacro{test-results-bl-model2-lc14-num-fail}{[139]}
\DefMacro{test-results-bl-model2-lc14-num-failrate}{[99.28571428571429]}
\DefMacro{test-results-bl-model2-lc8-num-fail}{[138]}
\DefMacro{test-results-bl-model2-lc8-num-failrate}{[98.57142857142857]}
\DefMacro{test-results-bl-model2-lc9-num-fail}{[4]}
\DefMacro{test-results-bl-model2-lc9-num-failrate}{[4.0]}
\DefMacro{test-results-bl-model2-lc10-num-fail}{[138]}
\DefMacro{test-results-bl-model2-lc10-num-failrate}{[98.57142857142857]}
\DefMacro{test-results-bl-model2-lc11-num-fail}{[133]}
\DefMacro{test-results-bl-model2-lc11-num-failrate}{[100.0]}
\DefMacro{test-results-bl-model2-lc6-num-fail}{[144]}
\DefMacro{test-results-bl-model2-lc6-num-failrate}{[100.0]}
\DefMacro{test-results-bl-model2-lc7-num-fail}{[1]}
\DefMacro{test-results-bl-model2-lc7-num-failrate}{[0.9009009009009009]}
\DefMacro{test-results-bl-model2-lc4-num-fail}{[133]}
\DefMacro{test-results-bl-model2-lc4-num-failrate}{[100.0]}
\DefMacro{test-results-bl-model2-lc5-num-fail}{[139]}
\DefMacro{test-results-bl-model2-lc5-num-failrate}{[99.28571428571429]}

### 2023-01-11 paper/ase22/tables/test-results-bl-table.tex
related work

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-bl-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc0-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc0-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-bl-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc1-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc1-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-bl-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc2-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc2-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-bl-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc3-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc3-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-bl-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc4-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc4-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-bl-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc5-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc5-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-bl-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc6-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc6-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-bl-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc7-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc7-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-bl-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc8-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc8-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-bl-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc9-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc9-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-bl-lc10}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc10-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc10-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc10-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc10-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc10-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc10-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc10-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-bl-lc11}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc11-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc11-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc11-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc11-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc11-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc11-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc11-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-bl-lc12}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc12-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc12-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc12-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc12-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc12-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc12-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc12-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-bl-lc13}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc13-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc13-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc13-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc13-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc13-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc13-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc13-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-bl-lc14}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc14-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc14-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc14-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc14-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc14-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc14-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc14-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-bl-lc15}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc15-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc15-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc15-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc15-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc15-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc15-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc15-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-bl-lc16}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc16-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc16-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc16-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc16-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc16-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc16-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc16-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-bl-lc17}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc17-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc17-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc17-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc17-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc17-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc17-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc17-num-failrate}
\hline
\multirow{3}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-bl-lc18}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc18-num-tcs}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc18-num-fail}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc18-num-failrate}
 & & & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc18-num-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-bl-model1-lc18-num-failrate}
 & & & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc18-num-fail}
 & da-BERT$\colon$\UseMacro{test-results-bl-model2-lc18-num-failrate}
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsHsBlTableVSpace}
\end{table*}

### 2023-01-11 paper/ase22/tables/test-results-hs-all-numbers.tex
related work

%% Automatically generated by pyutil.latex

\DefMacro{test-results-lc2}{Dehumanisation (explicit)}
\DefMacro{test-results-lc2-num-seeds}{140}
\DefMacro{test-results-lc2-num-exps}{3124}
\DefMacro{test-results-model0-lc2-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc2-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc2-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc1}{Description using very negative attributes (explicit)}
\DefMacro{test-results-lc1-num-seeds}{140}
\DefMacro{test-results-lc1-num-exps}{2959}
\DefMacro{test-results-model0-lc1-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc1-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc1-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc4}{Direct threat}
\DefMacro{test-results-lc4-num-seeds}{133}
\DefMacro{test-results-lc4-num-exps}{2689}
\DefMacro{test-results-model0-lc4-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc4-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc4-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc0}{Expression of strong negative emotions (explicit)}
\DefMacro{test-results-lc0-num-seeds}{140}
\DefMacro{test-results-lc0-num-exps}{799}
\DefMacro{test-results-model0-lc0-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc0-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc0-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc8}{Hate expressed using profanity}
\DefMacro{test-results-lc8-num-seeds}{1842}
\DefMacro{test-results-lc8-num-exps}{49743}
\DefMacro{test-results-model0-lc8-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc8-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc8-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc6}{Hate expressed using slur}
\DefMacro{test-results-lc6-num-seeds}{805}
\DefMacro{test-results-lc6-num-exps}{17318}
\DefMacro{test-results-model0-lc6-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc6-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc6-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc3}{Implicit derogation}
\DefMacro{test-results-lc3-num-seeds}{140}
\DefMacro{test-results-lc3-num-exps}{5664}
\DefMacro{test-results-model0-lc3-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc3-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc3-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc9}{Non-Hateful use of profanity}
\DefMacro{test-results-lc9-num-seeds}{701}
\DefMacro{test-results-lc9-num-exps}{15761}
\DefMacro{test-results-model0-lc9-num-all-fail}{[16462]}
\DefMacro{test-results-model0-lc9-num-all-failrate}{[100.0]}
\DefMacro{test-results-model0-lc9-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc7}{Non-hateful use of slur}
\DefMacro{test-results-lc7-num-seeds}{395}
\DefMacro{test-results-lc7-num-exps}{7881}
\DefMacro{test-results-model0-lc7-num-all-fail}{[8276]}
\DefMacro{test-results-model0-lc7-num-all-failrate}{[100.0]}
\DefMacro{test-results-model0-lc7-num-pass-to-fail}{[0]}
\DefMacro{test-results-lc5}{Threat as normative statement}
\DefMacro{test-results-lc5-num-seeds}{140}
\DefMacro{test-results-lc5-num-exps}{4163}
\DefMacro{test-results-model0-lc5-num-all-fail}{[0]}
\DefMacro{test-results-model0-lc5-num-all-failrate}{[0.0]}
\DefMacro{test-results-model0-lc5-num-pass-to-fail}{[0]}
\DefMacro{test-results-model1-lc2-num-all-fail}{[3210]}
\DefMacro{test-results-model1-lc2-num-all-failrate}{[98.34558823529412]}
\DefMacro{test-results-model1-lc2-num-pass-to-fail}{[11]}
\DefMacro{test-results-model1-lc1-num-all-fail}{[3011]}
\DefMacro{test-results-model1-lc1-num-all-failrate}{[97.16037431429493]}
\DefMacro{test-results-model1-lc1-num-pass-to-fail}{[30]}
\DefMacro{test-results-model1-lc4-num-all-fail}{[2750]}
\DefMacro{test-results-model1-lc4-num-all-failrate}{[97.44861800141743]}
\DefMacro{test-results-model1-lc4-num-pass-to-fail}{[0]}
\DefMacro{test-results-model1-lc0-num-all-fail}{[845]}
\DefMacro{test-results-model1-lc0-num-all-failrate}{[89.98935037273695]}
\DefMacro{test-results-model1-lc0-num-pass-to-fail}{[19]}
\DefMacro{test-results-model1-lc8-num-all-fail}{[49739]}
\DefMacro{test-results-model1-lc8-num-all-failrate}{[96.42144034118445]}
\DefMacro{test-results-model1-lc8-num-pass-to-fail}{[188]}
\DefMacro{test-results-model1-lc6-num-all-fail}{[17212]}
\DefMacro{test-results-model1-lc6-num-all-failrate}{[94.97323842630911]}
\DefMacro{test-results-model1-lc6-num-pass-to-fail}{[81]}
\DefMacro{test-results-model1-lc3-num-all-fail}{[5526]}
\DefMacro{test-results-model1-lc3-num-all-failrate}{[95.21019986216402]}
\DefMacro{test-results-model1-lc3-num-pass-to-fail}{[56]}
\DefMacro{test-results-model1-lc9-num-all-fail}{[541]}
\DefMacro{test-results-model1-lc9-num-all-failrate}{[3.28635645729559]}
\DefMacro{test-results-model1-lc9-num-pass-to-fail}{[51]}
\DefMacro{test-results-model1-lc7-num-all-fail}{[318]}
\DefMacro{test-results-model1-lc7-num-all-failrate}{[3.8424359594006767]}
\DefMacro{test-results-model1-lc7-num-pass-to-fail}{[20]}
\DefMacro{test-results-model1-lc5-num-all-fail}{[4198]}
\DefMacro{test-results-model1-lc5-num-all-failrate}{[97.5598419707181]}
\DefMacro{test-results-model1-lc5-num-pass-to-fail}{[12]}
\DefMacro{test-results-model2-lc2-num-all-fail}{[3220]}
\DefMacro{test-results-model2-lc2-num-all-failrate}{[98.65196078431373]}
\DefMacro{test-results-model2-lc2-num-pass-to-fail}{[18]}
\DefMacro{test-results-model2-lc1-num-all-fail}{[3067]}
\DefMacro{test-results-model2-lc1-num-all-failrate}{[98.96740884156179]}
\DefMacro{test-results-model2-lc1-num-pass-to-fail}{[23]}
\DefMacro{test-results-model2-lc4-num-all-fail}{[2770]}
\DefMacro{test-results-model2-lc4-num-all-failrate}{[98.15733522324592]}
\DefMacro{test-results-model2-lc4-num-pass-to-fail}{[9]}
\DefMacro{test-results-model2-lc0-num-all-fail}{[920]}
\DefMacro{test-results-model2-lc0-num-all-failrate}{[97.9765708200213]}
\DefMacro{test-results-model2-lc0-num-pass-to-fail}{[22]}
\DefMacro{test-results-model2-lc8-num-all-fail}{[50158]}
\DefMacro{test-results-model2-lc8-num-all-failrate}{[97.23369196471843]}
\DefMacro{test-results-model2-lc8-num-pass-to-fail}{[164]}
\DefMacro{test-results-model2-lc6-num-all-fail}{[17597]}
\DefMacro{test-results-model2-lc6-num-all-failrate}{[97.09761077084367]}
\DefMacro{test-results-model2-lc6-num-pass-to-fail}{[70]}
\DefMacro{test-results-model2-lc3-num-all-fail}{[5730]}
\DefMacro{test-results-model2-lc3-num-all-failrate}{[98.7250172294969]}
\DefMacro{test-results-model2-lc3-num-pass-to-fail}{[30]}
\DefMacro{test-results-model2-lc9-num-all-fail}{[549]}
\DefMacro{test-results-model2-lc9-num-all-failrate}{[3.334953225610497]}
\DefMacro{test-results-model2-lc9-num-pass-to-fail}{[58]}
\DefMacro{test-results-model2-lc7-num-all-fail}{[222]}
\DefMacro{test-results-model2-lc7-num-all-failrate}{[2.682455292411793]}
\DefMacro{test-results-model2-lc7-num-pass-to-fail}{[26]}
\DefMacro{test-results-model2-lc5-num-all-fail}{[4261]}
\DefMacro{test-results-model2-lc5-num-all-failrate}{[99.02393678828724]}
\DefMacro{test-results-model2-lc5-num-pass-to-fail}{[1]}

### 2023-01-11 paper/ase22/tables/test-results-hs-table.tex
related work

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||cclll}
\toprule
\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc0-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc0-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc0-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc0-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc0-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc0-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc0-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc0-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc0-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc1-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc1-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc1-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc1-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc1-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc1-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc1-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc1-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc1-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc2-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc2-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc2-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc2-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc2-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc2-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc2-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc2-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc2-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc3-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc3-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc3-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc3-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc3-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc3-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc3-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc3-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc3-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc4-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc4-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc4-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc4-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc4-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc4-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc4-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc4-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc4-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc5-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc5-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc5-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc5-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc5-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc5-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc5-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc5-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc5-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc6-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc6-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc6-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc6-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc6-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc6-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc6-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc6-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc6-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc7-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc7-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc7-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc7-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc7-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc7-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc7-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc7-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc7-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc8-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc8-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc8-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc8-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc8-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc8-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc8-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc8-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc8-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-exps}}
 & BERT$\colon$\UseMacro{test-results-model0-lc9-num-all-fail}
 & BERT$\colon$\UseMacro{test-results-model0-lc9-num-all-failrate}
 & BERT$\colon$\UseMacro{test-results-model0-lc9-num-pass-to-fail}\\
 & & & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc9-num-all-fail}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc9-num-all-failrate}
 & da-ELECTRA$\colon$\UseMacro{test-results-model1-lc9-num-pass-to-fail}\\
 & & & da-BERT$\colon$\UseMacro{test-results-model2-lc9-num-all-fail}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc9-num-all-failrate}
 & da-BERT$\colon$\UseMacro{test-results-model2-lc9-num-pass-to-fail}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsHsTableVSpace}
\end{table*}

### 2023-01-11 paper/fse23/related.tex
related work

--- 2022-09-02 paper/icse23/related.tex
@@
 %
-Different data augmentation approaches have been proposed for text generation.
-One of methods in this category is easy data augmentation (EDA)~\cite{weizou2019eda}.
-It uses simple operations such as synonym replacement and random swap.
-Coulombe~\cite{coulombe2018textaugapi} implements rule-based transformations using regular expressions for text transformations such as insertion of spelling mistakes, data alterations, entity names, and abbreviations.
-Mixup interpolation, which was introduced in computer vision category, was implemented in text domain~\cite{hongyu2019dataaugmixup}.
-Learning-based language models has been used to generate text data for multiple tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}.
-While these approaches focus on obtaining synthetic training data, not testing NLP model over \lcs,
+Different data augmentation approaches have been proposed for text
+generation. One of methods in this category is easy data augmentation
+(EDA)~\cite{weizou2019eda}. It uses simple operations such as synonym
+replacement and random swap. Coulombe~\cite{coulombe2018textaugapi}
+implements rule-based transformations using regular expressions for
+text transformations such as insertion of spelling mistakes, data
+alterations, entity names, and abbreviations. Mixup interpolation,
+which was introduced in computer vision category, was implemented in
+text domain~\cite{hongyu2019dataaugmixup}. Learning-based language
+models has been used to generate text data for multiple
+tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}. While these
+approaches focus on obtaining synthetic training data, not testing NLP
+model over \lcs,
 % they are not able to be used for the capability testing of the NLP model, 
-our work generates text data for testing NLP model over \lcs.
+our work generates text data for testing NLP model over \lcs.  In
+addition, adversarial text generation methods has been used for
+attacking NLP
+model~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack}. Morris \textit{\etal}~\cite{morris2020textattack}
+transform input text by leveraging existing methods such as insertion,
+deletion and swap of word/character within the similarity-based
+constraints. Zang \textit{\etal}~\cite{zang2020sememepso} finds
+sememe-based synonyms and generates adversarial examples by the word
+substitution. Alzantot \textit{\etal}~\cite{alzantot2018genadvexp}
+substitutes word in an input text with its neighboring words in
+embedding space that fools an NLP
+model. Linyang \textit{\etal}~\cite{linyang2020bertattack} generates
+word substitutes with BERT predicted words for attacking an NLP
+model. Also, Grammar-based text generation has been also
+introduced~\cite{udeshi2019ogma,soremekun2020astraea,maIJCAI2020mtnlp}.
+Ogma~\cite{udeshi2019ogma} and Astraea~\cite{soremekun2020astraea}
+leverages predefined grammar, and search adversarial examples by
+replacing word in an input text with another one that conforms to same
+production rule in the grammar until the replacement leads to error in
+the model. Ma \textit{\etal}~\cite{maIJCAI2020mtnlp} applies a simple
+expansion that inserts an adjective word before noun besides to
+replacement of analogy word found in embedding space. Our work
+generates text data does not only rely on the word substitution, but
+also changes diverse structures from the input text. In addition, we
+generates text conforming to same context of input text and its
+corresponding \lc by investigating its semantic and syntax.
 

### 2023-01-13 paper/fse23/intro.tex
intro

--- 2023-01-10 paper/fse23/intro.tex
@@
 
-To address this limitation, methodologies to assess an NLP model on a set of
-  linguistic capabilities have been introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. 
-A \lc
-explains a functionality of the input and output behavior for the
-NLP model under test. Typically, it describes certain type of inputs
-and outputs observed in real world for the target NLP task.
+\jl{To address this limitation, increasing number of evaluation
+  methodologies has been conducted to measure and evaluate the a NLP
+  model in different aspects. First, the NLP model can be fragile to
+  adversarial attacks, and it decreases trustworthiness of the NLP
+  model. Thus, robustness on adversarial examples are evaluated by
+  generating the examples using perturbations to an input
+  text.~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack,udeshi2019ogma}. Second,
+  fairness, specific bias in an NLP model toward certain subpopulation
+  groups such as gender and races, has been
+  measured~\cite{soremekun2020astraea,udeshi2018fairnesstest}. Additionally,
+  methodologies to assess an NLP model on a set of \lcs have been
+  introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. Typically,
+  it describes certain type of inputs and outputs observed in real
+  world for the target NLP task. A \lc includes comprehensive
+  functionalities of the input and output behavior for an NLP model,
+  and various task-specific model behaviors are evaluated compared
+  with the aforementioned evaluation metrics. Therefore,}
 % , ranging
 % from simple to complicated behaviors.
-Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
-models. 
-For example,  \Cklst~\cite{marcoACL2020checklist}, a behavioral testing framework for evaluating NLP models, defines a linguistic capability called ``Negated neutral should still be neutral'' to measure how accurately a \sa model understands that the negated neutral input has neutral sentiment
-\cite{marcoACL2020checklist}. 
-It requires the \sa model to
-output neutral sentiment on the negated neutral inputs. 
-Such evaluation methodology avoids the overestimation of the model performance as it measures the model performance on each functionality.
+Testing the linguistic capabilities allows the model developers to
+better understand the capabilities and potential issues of the NLP
+models.  For example, \Cklst~\cite{marcoACL2020checklist}, a
+behavioral testing framework for evaluating NLP models, defines a
+linguistic capability called ``Negated neutral should still be
+neutral'' to measure how accurately a \sa model understands that the
+negated neutral input has neutral sentiment
+\cite{marcoACL2020checklist}.  It requires the \sa model to output
+neutral sentiment on the negated neutral inputs.  Such evaluation
+methodology avoids the overestimation of the model performance as it
+measures the model performance on each functionality.
 % ,and the separate model performance
 % explain distribution of the performance over the linguistic capabilities
-In the end, testing through linguistic capabilities provides not only the overall model performance, but also the malfunction facets of the model.
+In the end, testing through linguistic capabilities provides not only
+the overall model performance, but also the malfunction facets of the
+model.
 
- However, existing linguistic capability-based testing approaches rely on manually generated input templates, which need to be preset before generating tests. 
- As a result, these templates are limited in their sentence
-structures. This restricts existing approaches' ability to comprehensively test linguistic capabilities.
+However, existing linguistic capability-based testing approaches
+generate inputs only relying on word substitution, and need to be
+preset before generating tests.  As a result, these templates are
+limited in their sentence structures. This restricts existing
+approaches' ability to comprehensively test linguistic capabilities.
 
@@
 
-To address this issue, we present \tool,
-an automated linguistic capability-based testing framework for NLP models.  
-The goal of \tool is to generate a diverse linguistic capability-based test suite for a given model, both in terms of covering diverse linguistic structures and diverse model behaviors.
-To achieve the goal, \tool needs to address two challenges.
-\textit{(i) Capability-based Assessment.} Each test case should be automatically categorized into a \lc;
-and \textit{(ii) Automated Test Oracle.} The label of each test case should be automatically
-  and accurately defined.
-% \end{description}
+To address this issue, we present \tool, an automated linguistic
+capability-based testing framework for NLP models.  The goal of \tool
+is to generate a diverse linguistic capability-based test suite for a
+given model, both in terms of covering diverse linguistic structures
+and diverse model behaviors.  To achieve the goal, \tool needs to
+address two challenges.
 
-%\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse.
-To address this challenge, \tool establishes specifications for evaluating a linguistic capability and searches suitable sentences that satisfy the specification from existing public dataset.
-In this process, \tool generates new inputs by mutating the searched sentences, used as seed inputs.
-\tool expands the grammar structure of a seed input and determines its available \pos to maintain structural naturalness.
+\textit{(i) Capability-based text generation.}
+Each test case should be automatically categorized into a \lc; and
+\textit{(ii) Automated Test Oracle.} The label of each test case
+should be automatically and accurately defined.
 
-% After that, to hold contextual naturalness of the mutated
-% inputs, the fuzzer completes the expanded new structures via
-% data-driven context-aware word suggestion. Additionally,
-% sentiment-independent words in the inputs are replaced with rule-based
-% word suggestion. Further, we address the manual input generation
-% process by automating the process mentioned above.
+\noindent \textbf{Capability-based text generation.} The suitability
+of test sentences for evaluating NLP models on a \lc is determined by
+its relevancy to this \lc. It is challenging to maintain relevancy
+between a test sentence and its \lc when transforming and expanding
+the test sentence. This is because the \lc is defined on a specific
+mixture of syntax and semantics of the sentence. Due to the inherent
+ambiguity of natural language sentences, there exists no automatic way
+to check the consistency of each sentence with the semantics and
+structures specified in the corresponding \lc. \tool defines
+specifications (search rules and transformation templates) from \lcs,
+and generates seed test cases by searching and transforming test cases
+that conform to the specifications. In addition, \tool analyzes the
+parse tree of the seed sentence to identify possible expansion and
+validates coherence of \lc relevancy between the seed and its
+expansion.
 
-\noindent \textbf{Capability-based Assessment.} The suitability of test sentences for evaluating NLP
-models on a \lc is determined by its relevancy to this
-\lc. It is challenging to maintain relevancy between a test sentence and its \lc when transforming and expanding the test sentence.
-This is because the \lc is defined on a specific 
-mixture of syntax and semantics of the sentence.
-Due to the inherent ambiguity of natural language sentences, there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc.
-To address this difficulty, \tool defines specifications (search rules
-and transformation templates) of \lcs, and analyzes the parse
-tree of the seed sentence to identify possible expansion.
-%% \tool adopts behavioral model testing method by
-%% introducing multiple behaviors from \lcs on \sa tasks and generating
-%% inputs relevant to each \lc. Each test case provides not only
-%% correctness of model prediction on it, but \lc on the test case also
-%% gives information about classification on the model
-%% performance. Therefore assigning appropriate \lc for each test case
-%% alleviates overestimation of model testing results.
-
-\noindent \textbf{Automated Test Oracle.}   For NLP model testing, test oracle is usually determined by understanding the semantics of texts and requires domain knowledge of different NLP tasks.
-Thus, the current testing practice requires manual efforts to create the test oracles of the \ho data.
-The manual work is costly in terms of time consumption.
-Therefore, it necessitates automated test oracle generation for improving the testing process of NLP models.
-% % validity of the automation is ensured by the
-% % correctness of test oracle.
- However, automatically generating the  test oracles remains one of the main challenges in NLP software testing~\cite{huang2022aeon}. 
- A few metamorphic testing approaches have been proposed in image recognition domain, but they require understanding the characteristics of metamorphic relations between inputs and outputs, which require domain expertise and non-trivial manual efforts ~\cite{segura2016metamorphictest}.
-In addition, it is even more challenging to design metamorphic relations in textual data because the semantics of nature language sentences can be greatly changed even by a slight perturbation to the sentences.
- %Along with this, motivated by software metamorphic testing approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules.
+\noindent \textbf{Automated Test Oracle.}  For NLP model testing, test
+oracle is usually determined by understanding the semantics of texts
+and requires domain knowledge of different NLP tasks.  Thus, the
+current testing practice requires manual efforts to create the test
+oracles of the \ho data. The manual work is costly in terms of time
+consumption. Therefore, it necessitates automated test oracle
+generation for improving the testing process of NLP models.  However,
+automatically generating the test oracles remains one of the main
+challenges in NLP software testing~\cite{huang2022aeon}.  A few
+metamorphic testing approaches have been proposed in image recognition
+domain, but they require understanding the characteristics of
+metamorphic relations between inputs and outputs, which require domain
+expertise and non-trivial manual efforts
+~\cite{segura2016metamorphictest}. In addition, it is even more
+challenging to design metamorphic relations in textual data because
+the semantics of nature language sentences can be greatly changed even
+by a slight perturbation to the sentences.  Motivated by software
+metamorphic testing approach~\cite{segura2016metamorphictest}, we
+address the challenge by only accepting validated test oracles by the
+\lc specification and linguistic rules determined by input-output
+relations.
 
@@
 %correctness of its oracle allocation.
-In this work, as a first step, we consider \sa as the NLP task for the models under test. 
-\tool obtains the
-appropriate test oracle by implementing domain-specific
-knowledge on the word sentiment dataset and word suggestion model for validating the generated sentence and its oracle.
+In this work, as a first step, we consider \sa and \hsd as the NLP
+tasks for the models under test.  \tool obtains the appropriate test
+oracle by implementing domain-specific knowledge on the word sentiment
+dataset and word suggestion model for validating the generated
+sentence and its oracle.
 

### 2023-01-13 paper/fse23/related.tex
intro

@@
 our work generates text data for testing NLP model over \lcs.  In
-addition, adversarial text generation methods has been used for
-attacking NLP
-model~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack}. Morris \textit{\etal}~\cite{morris2020textattack}
-transform input text by leveraging existing methods such as insertion,
-deletion and swap of word/character within the similarity-based
+addition, text generation methods has been used for attacking NLP
+model~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack}.
+Morris \textit{\etal}~\cite{morris2020textattack} transform input text
+by leveraging existing methods such as insertion, deletion and swap of
+word/character within the similarity-based
 constraints. Zang \textit{\etal}~\cite{zang2020sememepso} finds
@@
 also changes diverse structures from the input text. In addition, we
-generates text conforming to same context of input text and its
-corresponding \lc by investigating its semantic and syntax.
+investigate input semantic and syntax to generate text conforming to
+the same context as input text and its corresponding \lc.
 

### 2023-01-13 python/hs/paper/Tables.py
add hsd rule table

@@ -49,8 +49,11 @@ class Tables:
             which = [which]
         # end if
 
-        for item in which: 
-            if item == "test-results":
+        for item in which:
+            if item == 'lc-req':
+                cls.make_numbers_lc_requirement(Macros.result_dir, tables_dir)
+                cls.make_table_lc_requirement(Macros.result_dir, tables_dir)
+            elif item == 'test-results':
                 task = options.pop('task', 'hs')
                 search_dataset = options.pop('search_dataset_name', 'hatexplain')
                 selection_method = options.pop('selection_method', 'random')
@@ -58,7 +61,7 @@ class Tables:
                 num_trials = options.pop('num_trials', -1)
                 cls.make_numbers_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method, num_seeds, num_trials)
                 cls.make_table_test_results(Macros.result_dir, tables_dir, task, search_dataset, selection_method, num_seeds, num_trials)
-            elif item == "test-results-baseline":
+            elif item == 'test-results-baseline':
                 task = options.pop('task', 'hs')
                 search_dataset = options.pop('search_dataset_name', 'hatexplain')
                 selection_method = options.pop('selection_method', 'random')
@@ -70,6 +73,78 @@ class Tables:
                 raise(f"Unknown table {item}")
             # end if
         # end for
+        return
+
+    @classmethod
+    def replace_latex_symbol(cls, string):
+        for symbol in cls.LATEX_SYMBOL_MAP.keys():
+            string = string.replace(symbol, cls.LATEX_SYMBOL_MAP[symbol])
+        # end for
+        return string
+
+    @classmethod
+    def make_numbers_lc_requirement(cls, results_dir: Path, tables_dir: Path):
+        req_dir = results_dir / 'reqs'
+        req_file = req_dir / 'requirements_desc_hs.txt'
+        output_file = latex.File(tables_dir / 'lc-hsd-requirement-numbers.tex')
+        for l_i, l in enumerate(Utils.read_txt(req_file)):
+            l_split = l.strip().split('::')
+            if len(l_split)>3:
+                desc, search, exclude, transform = l_split[0], l_split[1], l_split[2], l_split[3]
+                desc = cls.replace_latex_symbol(desc)
[…]

### 2023-01-13 paper/fse23/tables/lc-hsd-requirement-numbers.tex
debug table

%% Automatically generated by pyutil.latex

\DefMacro{hsd_lc_1_desc}{Expression of strong negative emotions (explicit)}
\DefMacro{hsd_lc_1_search}{\textbf{Search}~hatecheck}
\DefMacro{hsd_lc_1_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_2_desc}{Description using very negative attributes (explicit)}
\DefMacro{hsd_lc_2_search}{\textbf{Search}~hatecheck}
\DefMacro{hsd_lc_2_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_3_desc}{Dehumanisation (explicit)}
\DefMacro{hsd_lc_3_search}{\textbf{Search}~hatecheck}
\DefMacro{hsd_lc_3_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_4_desc}{Implicit derogation}
\DefMacro{hsd_lc_4_search}{\textbf{Search}~hatecheck}
\DefMacro{hsd_lc_4_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_5_desc}{Direct threat}
\DefMacro{hsd_lc_5_search}{\textbf{Search}~hatecheck}
\DefMacro{hsd_lc_5_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_6_desc}{Threat as normative statement}
\DefMacro{hsd_lc_6_search}{\textbf{Search}~hatecheck}
\DefMacro{hsd_lc_6_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_7_desc}{Hate expressed using slur}
\DefMacro{hsd_lc_7_search}{\textbf{Search}~seed=\{include: slur; label: toxic\}}
\DefMacro{hsd_lc_7_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_8_desc}{Non-hateful use of slur}
\DefMacro{hsd_lc_8_search}{\textbf{Search}~seed=\{include: slur; label: non-toxic\}}
\DefMacro{hsd_lc_8_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_9_desc}{Hate expressed using profanity}
\DefMacro{hsd_lc_9_search}{\textbf{Search}~seed=\{include: profanity; label: toxic\}}
\DefMacro{hsd_lc_9_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_10_desc}{Non-Hateful use of profanity}
\DefMacro{hsd_lc_10_search}{\textbf{Search}~seed=\{include: profanity; label: non-toxic\}}
\DefMacro{hsd_lc_10_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_11_desc}{Hate expressed through reference in subsequent clauses}
\DefMacro{hsd_lc_11_search}{\textbf{Search}~toxic\_sent=\{include: identity; label: toxic\}, non\_toxic\_sent=\{include: identity; label: non-toxic\}}
\DefMacro{hsd_lc_11_transform}{\textbf{Transform}~seed=\{['people say', 'I heard that']+[toxic\_sent]+['and']+['i hate them too', 'i also hate them']\} $|$ \{['people say', 'I heard that']+[toxic\_sent]+['but']+['i do not hate them', 'i like them']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['but']+['i hate them', 'i dislike them']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['and']+['i also do not hate them', 'i do not hate them too']\}}
\DefMacro{hsd_lc_12_desc}{Hate expressed through reference in subsequent sentences}
\DefMacro{hsd_lc_12_search}{\textbf{Search}~toxic\_sent=\{include: identity; label: toxic\}, non\_toxic\_sent=\{include: identity; label: non-toxic\}}
\DefMacro{hsd_lc_12_transform}{\textbf{Transform}~seed=\{['people say', 'I heard that']+[toxic\_sent]+['.']+['i hate them too', 'i also hate them']\} $|$ \{['people say', 'I heard that']+[toxic\_sent]+['.']+['however i do not hate them', 'regardless i like them']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['.']+['however i hate them', 'i dislike them though']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['.']+['i also do not hate them', 'i do not hate them too']\}}
\DefMacro{hsd_lc_13_desc}{Hate expressed using negated positive statement}
\DefMacro{hsd_lc_13_search}{\textbf{Search}~non\_toxic\_sent=\{label: non-toxic\}}
\DefMacro{hsd_lc_13_transform}{\textbf{Transform}~seed=\{['I do not think that', 'I do not agree with that', 'I do not believe that']+[non\_toxic\_sent]\}}
\DefMacro{hsd_lc_14_desc}{Non-hate expressed using negated hateful statement}
\DefMacro{hsd_lc_14_search}{\textbf{Search}~toxic\_sent=\{label: toxic\}}
\DefMacro{hsd_lc_14_transform}{\textbf{Transform}~seed=\{['I do not think that', 'I do not agree with that', 'I do not believe that']+[toxic\_sent]\}}
\DefMacro{hsd_lc_15_desc}{Hate phrased as a question}
\DefMacro{hsd_lc_15_search}{\textbf{Search}~toxic\_sent=\{label: toxic\}}
\DefMacro{hsd_lc_15_transform}{\textbf{Transform}~seed=\{['why do you agree with that', 'why do you like to say that']+[toxic\_sent]+['?']\}}
\DefMacro{hsd_lc_16_desc}{Hate phrased as a opinion}
\DefMacro{hsd_lc_16_search}{\textbf{Search}~toxic\_sent=\{label: toxic\}}
\DefMacro{hsd_lc_16_transform}{\textbf{Transform}~seed=\{['i think that', 'i believe that']+[toxic\_sent]\}}
\DefMacro{hsd_lc_17_desc}{Neutral statements using protected group identifiers}
\DefMacro{hsd_lc_17_search}{\textbf{Search}~seed=\{include: identity; exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns \& pos verbs \& neg verbs; label: non-toxic\}}
\DefMacro{hsd_lc_17_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_18_desc}{Positive statements using protected group identifiers}
\DefMacro{hsd_lc_18_search}{\textbf{Search}~seed=\{include: identity; exclude: neg adjs \& neg nouns \& neg verbs; label: non-toxic\}}
\DefMacro{hsd_lc_18_transform}{\textbf{Transform}~N/A}
\DefMacro{hsd_lc_19_desc}{Denouncements of hate that quote it}
\DefMacro{hsd_lc_19_search}{\textbf{Search}~toxic\_sent=\{label: toxic\}}
\DefMacro{hsd_lc_19_transform}{\textbf{Transform}~seed=\{['statements like']+[toxic\_sent]+['are hurtful', 'are harmful', 'are deleterious']\} $|$ \{['you should stop saying like']+[toxic\_sent]\}}

### 2023-01-13 python/hs/paper/Tables.py

@@ -101,9 +101,9 @@ class Tables:
                 search = r"\textbf{Search}~"+cls.replace_latex_symbol(search.split('<SEARCH>')[-1])
                 transform = r"\textbf{Transform}~"+cls.replace_latex_symbol(transform.split('<TRANSFORM>')[-1])
             # end if
-            output_file.append_macro(latex.Macro(f"lc_{l_i+1}_desc", desc))
-            output_file.append_macro(latex.Macro(f"lc_{l_i+1}_search", search))
-            output_file.append_macro(latex.Macro(f"lc_{l_i+1}_transform", transform))
+            output_file.append_macro(latex.Macro(f"hsd_lc_{l_i+1}_desc", desc))
+            output_file.append_macro(latex.Macro(f"hsd_lc_{l_i+1}_search", search))
+            output_file.append_macro(latex.Macro(f"hsd_lc_{l_i+1}_transform", transform))
         # end for
         output_file.save()
         return
@@ -117,7 +117,8 @@ class Tables:
         output_file.append(r"\begin{small}")
         output_file.append(r"\begin{center}")
         output_file.append(r"\caption{\HsdReqTableCaption}")
-        output_file.append(r"\begin{tabular}{p{5cm}||p{9cm}}")
+        output_file.append(r"\resizebox{0.8\textwidth}{!}{")
+        output_file.append(r"\begin{tabular}{p{5cm}||p{12.5cm}}")
         output_file.append(r"\toprule")
         
         # Content
@@ -130,16 +131,16 @@ class Tables:
             l_split = l.split('::')
             len_l = len(l_split) # 3 or 4
             output_file.append("\multirow{3}{*}{\parbox{5cm}{" + \
-                               f"LC{l_i+1}: " + latex.Macro(f"lc_{l_i+1}_desc").use() + "}}")
-            output_file.append(" & " + latex.Macro(f"lc_{l_i+1}_search").use() + r"\\")
-            output_file.append(" & " + latex.Macro(f"lc_{l_i+1}_transform").use() + r"\\")
+                               f"LC{l_i+1}: " + latex.Macro(f"hsd_lc_{l_i+1}_desc").use() + "}}")
+            output_file.append(" & " + latex.Macro(f"hsd_lc_{l_i+1}_search").use() + r"\\")
+            output_file.append(" & " + latex.Macro(f"hsd_lc_{l_i+1}_transform").use() + r"\\")
             output_file.append(r"\\")
             output_file.append(r"\hline")
[…]

### 2023-01-17 paper/fse23/tables/test-results-all-numbers.tex
modify table

@@
 \DefMacro{test-results-all-lc7-num-exps}{492,817}
+\DefMacro{test-results-bl-lc7-num-tcs}{8,528}
 \DefMacro{test-results-all-model0-lc7-num-fail}{158,854}
@@
 \DefMacro{test-results-all-model0-lc7-num-pass-to-fail}{9,748}
+\DefMacro{test-results-bl-model0-lc7-num-fail}{3,741}
+\DefMacro{test-results-bl-model0-lc7-num-failrate}{43.87}
 \DefMacro{test-results-all-lc3}{Negated negative should be positive or neutral}
@@
 \DefMacro{test-results-all-lc3-num-exps}{503}
+\DefMacro{test-results-bl-lc3-num-tcs}{6,786}
 \DefMacro{test-results-all-model0-lc3-num-fail}{523}
@@
 \DefMacro{test-results-all-model0-lc3-num-pass-to-fail}{20}
+\DefMacro{test-results-bl-model0-lc3-num-fail}{799}
+\DefMacro{test-results-bl-model0-lc3-num-failrate}{11.77}
 \DefMacro{test-results-all-lc4}{Negated neutral should still be neutral}
@@
 \DefMacro{test-results-all-lc4-num-exps}{194}
+\DefMacro{test-results-bl-lc4-num-tcs}{2,496}
 \DefMacro{test-results-all-model0-lc4-num-fail}{207}
@@
 \DefMacro{test-results-all-model0-lc4-num-pass-to-fail}{11}
+\DefMacro{test-results-bl-model0-lc4-num-fail}{2,427}
+\DefMacro{test-results-bl-model0-lc4-num-failrate}{97.24}
 \DefMacro{test-results-all-lc6}{Negated positive with neutral content in the middle}
@@
 \DefMacro{test-results-all-lc6-num-exps}{190,723}
+\DefMacro{test-results-bl-lc6-num-tcs}{1,000}
 \DefMacro{test-results-all-model0-lc6-num-fail}{195,525}
@@
 \DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{2,014}
+\DefMacro{test-results-bl-model0-lc6-num-fail}{860}
+\DefMacro{test-results-bl-model0-lc6-num-failrate}{86.00}
 \DefMacro{test-results-all-lc5}{Negation of negative at the end, should be positive or neutral}
@@
 \DefMacro{test-results-all-lc5-num-exps}{102,304}
+\DefMacro{test-results-bl-lc5-num-tcs}{2,124}
 \DefMacro{test-results-all-model0-lc5-num-fail}{120,451}
@@
 \DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{71}
+\DefMacro{test-results-bl-model0-lc5-num-fail}{1,871}
+\DefMacro{test-results-bl-model0-lc5-num-failrate}{88.09}
 \DefMacro{test-results-all-lc9}{Parsing sentiment in (question, no) form}
@@
 \DefMacro{test-results-all-lc9-num-exps}{108,412}
+\DefMacro{test-results-bl-lc9-num-tcs}{7,644}
 \DefMacro{test-results-all-model0-lc9-num-fail}{93,329}
@@
 \DefMacro{test-results-all-model0-lc9-num-pass-to-fail}{1,891}
+\DefMacro{test-results-bl-model0-lc9-num-fail}{4,056}
+\DefMacro{test-results-bl-model0-lc9-num-failrate}{53.06}
 \DefMacro{test-results-all-lc2}{Sentiment change over time, present should prevail}
@@
 \DefMacro{test-results-all-lc2-num-exps}{507,091}
+\DefMacro{test-results-bl-lc2-num-tcs}{8,000}
 \DefMacro{test-results-all-model0-lc2-num-fail}{134,641}
@@
 \DefMacro{test-results-all-model0-lc2-num-pass-to-fail}{18,510}
+\DefMacro{test-results-bl-model0-lc2-num-fail}{1,680}
+\DefMacro{test-results-bl-model0-lc2-num-failrate}{21.00}
 \DefMacro{test-results-all-lc0}{Short sentences with neutral adjectives and nouns}
@@
 \DefMacro{test-results-all-lc0-num-exps}{51}
+\DefMacro{test-results-bl-lc0-num-tcs}{1,716}
 \DefMacro{test-results-all-model0-lc0-num-fail}{60}
@@
 \DefMacro{test-results-all-model0-lc0-num-pass-to-fail}{9}
+\DefMacro{test-results-bl-model0-lc0-num-fail}{1,330}
+\DefMacro{test-results-bl-model0-lc0-num-failrate}{77.51}
 \DefMacro{test-results-all-lc1}{Short sentences with sentiment-laden adjectives}
@@
 \DefMacro{test-results-all-lc1-num-exps}{262}
+\DefMacro{test-results-bl-lc1-num-tcs}{8,658}
 \DefMacro{test-results-all-model0-lc1-num-fail}{25}
@@
 \DefMacro{test-results-all-model0-lc1-num-pass-to-fail}{5}
+\DefMacro{test-results-bl-model0-lc1-num-fail}{26}
+\DefMacro{test-results-bl-model0-lc1-num-failrate}{0.30}
 \DefMacro{test-results-all-lc8}{Parsing sentiment in (question, yes) form}
@@
 \DefMacro{test-results-all-lc8-num-exps}{106,907}
+\DefMacro{test-results-bl-lc8-num-tcs}{7,644}
 \DefMacro{test-results-all-model0-lc8-num-fail}{7,361}
@@
 \DefMacro{test-results-all-model0-lc8-num-pass-to-fail}{1,646}
+\DefMacro{test-results-bl-model0-lc8-num-fail}{253}
+\DefMacro{test-results-bl-model0-lc8-num-failrate}{3.31}
 \DefMacro{test-results-all-model1-lc7-num-fail}{112,390}
@@
 \DefMacro{test-results-all-model1-lc7-num-pass-to-fail}{9,453}
+\DefMacro{test-results-bl-model1-lc7-num-fail}{2,692}
+\DefMacro{test-results-bl-model1-lc7-num-failrate}{31.57}
 \DefMacro{test-results-all-model1-lc3-num-fail}{498}
@@
 \DefMacro{test-results-all-model1-lc3-num-pass-to-fail}{9}
+\DefMacro{test-results-bl-model1-lc3-num-fail}{218}
+\DefMacro{test-results-bl-model1-lc3-num-failrate}{3.21}
 \DefMacro{test-results-all-model1-lc4-num-fail}{204}
@@
 \DefMacro{test-results-all-model1-lc4-num-pass-to-fail}{6}
+\DefMacro{test-results-bl-model1-lc4-num-fail}{2,304}
+\DefMacro{test-results-bl-model1-lc4-num-failrate}{92.31}
 \DefMacro{test-results-all-model1-lc6-num-fail}{157,635}
@@
 \DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,289}
+\DefMacro{test-results-bl-model1-lc6-num-fail}{416}
+\DefMacro{test-results-bl-model1-lc6-num-failrate}{41.60}
 \DefMacro{test-results-all-model1-lc5-num-fail}{120,054}
@@
 \DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{93}
+\DefMacro{test-results-bl-model1-lc5-num-fail}{445}
+\DefMacro{test-results-bl-model1-lc5-num-failrate}{20.95}
 \DefMacro{test-results-all-model1-lc9-num-fail}{105,319}
@@
 \DefMacro{test-results-all-model1-lc9-num-pass-to-fail}{1,764}
+\DefMacro{test-results-bl-model1-lc9-num-fail}{4,576}
+\DefMacro{test-results-bl-model1-lc9-num-failrate}{59.86}
 \DefMacro{test-results-all-model1-lc2-num-fail}{283,614}
@@
 \DefMacro{test-results-all-model1-lc2-num-pass-to-fail}{17,142}
+\DefMacro{test-results-bl-model1-lc2-num-fail}{829}
+\DefMacro{test-results-bl-model1-lc2-num-failrate}{10.36}
 \DefMacro{test-results-all-model1-lc0-num-fail}{55}
@@
 \DefMacro{test-results-all-model1-lc0-num-pass-to-fail}{2}
+\DefMacro{test-results-bl-model1-lc0-num-fail}{1,391}
+\DefMacro{test-results-bl-model1-lc0-num-failrate}{81.06}
 \DefMacro{test-results-all-model1-lc1-num-fail}{39}
@@
 \DefMacro{test-results-all-model1-lc1-num-pass-to-fail}{14}
+\DefMacro{test-results-bl-model1-lc1-num-fail}{139}
+\DefMacro{test-results-bl-model1-lc1-num-failrate}{1.61}
 \DefMacro{test-results-all-model1-lc8-num-fail}{6,510}
@@
 \DefMacro{test-results-all-model1-lc8-num-pass-to-fail}{1,519}
+\DefMacro{test-results-bl-model1-lc8-num-fail}{32}
+\DefMacro{test-results-bl-model1-lc8-num-failrate}{0.42}
 \DefMacro{test-results-all-model2-lc7-num-fail}{170,198}
@@
 \DefMacro{test-results-all-model2-lc7-num-pass-to-fail}{13,870}
+\DefMacro{test-results-bl-model2-lc7-num-fail}{3,535}
+\DefMacro{test-results-bl-model2-lc7-num-failrate}{41.45}
 \DefMacro{test-results-all-model2-lc3-num-fail}{494}
@@
 \DefMacro{test-results-all-model2-lc3-num-pass-to-fail}{6}
+\DefMacro{test-results-bl-model2-lc3-num-fail}{734}
+\DefMacro{test-results-bl-model2-lc3-num-failrate}{10.82}
 \DefMacro{test-results-all-model2-lc4-num-fail}{213}
@@
 \DefMacro{test-results-all-model2-lc4-num-pass-to-fail}{10}
+\DefMacro{test-results-bl-model2-lc4-num-fail}{2,450}
+\DefMacro{test-results-bl-model2-lc4-num-failrate}{98.16}
 \DefMacro{test-results-all-model2-lc6-num-fail}{180,865}
@@
 \DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,130}
+\DefMacro{test-results-bl-model2-lc6-num-fail}{865}
+\DefMacro{test-results-bl-model2-lc6-num-failrate}{86.50}
 \DefMacro{test-results-all-model2-lc5-num-fail}{118,910}
@@
 \DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{334}
+\DefMacro{test-results-bl-model2-lc5-num-fail}{2,124}
+\DefMacro{test-results-bl-model2-lc5-num-failrate}{100.00}
 \DefMacro{test-results-all-model2-lc9-num-fail}{117,664}
@@
 \DefMacro{test-results-all-model2-lc9-num-pass-to-fail}{594}
+\DefMacro{test-results-bl-model2-lc9-num-fail}{6,440}
+\DefMacro{test-results-bl-model2-lc9-num-failrate}{84.25}
 \DefMacro{test-results-all-model2-lc2-num-fail}{363,619}
@@
 \DefMacro{test-results-all-model2-lc2-num-pass-to-fail}{16,527}
+\DefMacro{test-results-bl-model2-lc2-num-fail}{2,532}
+\DefMacro{test-results-bl-model2-lc2-num-failrate}{31.65}
 \DefMacro{test-results-all-model2-lc0-num-fail}{68}
@@
 \DefMacro{test-results-all-model2-lc0-num-pass-to-fail}{0}
+\DefMacro{test-results-bl-model2-lc0-num-fail}{1,661}
+\DefMacro{test-results-bl-model2-lc0-num-failrate}{96.79}
 \DefMacro{test-results-all-model2-lc1-num-fail}{18}
@@
 \DefMacro{test-results-all-model2-lc1-num-pass-to-fail}{10}
+\DefMacro{test-results-bl-model2-lc1-num-fail}{125}
+\DefMacro{test-results-bl-model2-lc1-num-failrate}{1.44}
 \DefMacro{test-results-all-model2-lc8-num-fail}{5,702}
@@
 \DefMacro{test-results-all-model2-lc8-num-pass-to-fail}{1,193}
+\DefMacro{test-results-bl-model2-lc8-num-fail}{52}
+\DefMacro{test-results-bl-model2-lc8-num-failrate}{0.68}

### 2023-01-17 paper/fse23/tables/test-results-all-table.tex
modify table

%% Automatically generated by pyutil.latex

\begin{table*}[t]
\begin{small}
\begin{center}
\caption{\TestResultsAllTableCaption}
\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8cm}||ccclll}
\toprule
\tLc & \parbox{1.5cm}{\tNumBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-all-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc0-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc0-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc0-num-fail}/\UseMacro{test-results-bl-model0-lc0-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc0-num-failrate}/\UseMacro{test-results-bl-model0-lc0-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc0-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc0-num-fail}/\UseMacro{test-results-bl-model1-lc0-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc0-num-failrate}/\UseMacro{test-results-bl-model1-lc0-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc0-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc0-num-fail}/\UseMacro{test-results-bl-model2-lc0-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc0-num-failrate}/\UseMacro{test-results-bl-model2-lc0-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc0-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-all-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc1-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc1-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc1-num-fail}/\UseMacro{test-results-bl-model0-lc1-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc1-num-failrate}/\UseMacro{test-results-bl-model0-lc1-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc1-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc1-num-fail}/\UseMacro{test-results-bl-model1-lc1-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc1-num-failrate}/\UseMacro{test-results-bl-model1-lc1-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc1-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc1-num-fail}/\UseMacro{test-results-bl-model2-lc1-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc1-num-failrate}/\UseMacro{test-results-bl-model2-lc1-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc1-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-all-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc2-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc2-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc2-num-fail}/\UseMacro{test-results-bl-model0-lc2-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc2-num-failrate}/\UseMacro{test-results-bl-model0-lc2-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc2-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc2-num-fail}/\UseMacro{test-results-bl-model1-lc2-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc2-num-failrate}/\UseMacro{test-results-bl-model1-lc2-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc2-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc2-num-fail}/\UseMacro{test-results-bl-model2-lc2-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc2-num-failrate}/\UseMacro{test-results-bl-model2-lc2-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc2-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-all-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc3-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc3-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc3-num-fail}/\UseMacro{test-results-bl-model0-lc3-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc3-num-failrate}/\UseMacro{test-results-bl-model0-lc3-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc3-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc3-num-fail}/\UseMacro{test-results-bl-model1-lc3-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc3-num-failrate}/\UseMacro{test-results-bl-model1-lc3-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc3-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc3-num-fail}/\UseMacro{test-results-bl-model2-lc3-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc3-num-failrate}/\UseMacro{test-results-bl-model2-lc3-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc3-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-all-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc4-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc4-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc4-num-fail}/\UseMacro{test-results-bl-model0-lc4-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc4-num-failrate}/\UseMacro{test-results-bl-model0-lc4-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc4-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc4-num-fail}/\UseMacro{test-results-bl-model1-lc4-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc4-num-failrate}/\UseMacro{test-results-bl-model1-lc4-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc4-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc4-num-fail}/\UseMacro{test-results-bl-model2-lc4-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc4-num-failrate}/\UseMacro{test-results-bl-model2-lc4-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc4-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-all-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc5-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc5-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc5-num-fail}/\UseMacro{test-results-bl-model0-lc5-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc5-num-failrate}/\UseMacro{test-results-bl-model0-lc5-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc5-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc5-num-fail}/\UseMacro{test-results-bl-model1-lc5-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc5-num-failrate}/\UseMacro{test-results-bl-model1-lc5-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc5-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc5-num-fail}/\UseMacro{test-results-bl-model2-lc5-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc5-num-failrate}/\UseMacro{test-results-bl-model2-lc5-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc5-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-all-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc6-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc6-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc6-num-fail}/\UseMacro{test-results-bl-model0-lc6-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc6-num-failrate}/\UseMacro{test-results-bl-model0-lc6-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc6-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc6-num-fail}/\UseMacro{test-results-bl-model1-lc6-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc6-num-failrate}/\UseMacro{test-results-bl-model1-lc6-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc6-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc6-num-fail}/\UseMacro{test-results-bl-model2-lc6-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc6-num-failrate}/\UseMacro{test-results-bl-model2-lc6-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc6-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-all-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc7-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc7-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc7-num-fail}/\UseMacro{test-results-bl-model0-lc7-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc7-num-failrate}/\UseMacro{test-results-bl-model0-lc7-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc7-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc7-num-fail}/\UseMacro{test-results-bl-model1-lc7-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc7-num-failrate}/\UseMacro{test-results-bl-model1-lc7-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc7-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc7-num-fail}/\UseMacro{test-results-bl-model2-lc7-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc7-num-failrate}/\UseMacro{test-results-bl-model2-lc7-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc7-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-all-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc8-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc8-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc8-num-fail}/\UseMacro{test-results-bl-model0-lc8-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc8-num-failrate}/\UseMacro{test-results-bl-model0-lc8-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc8-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc8-num-fail}/\UseMacro{test-results-bl-model1-lc8-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc8-num-failrate}/\UseMacro{test-results-bl-model1-lc8-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc8-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc8-num-fail}/\UseMacro{test-results-bl-model2-lc8-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc8-num-failrate}/\UseMacro{test-results-bl-model2-lc8-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc8-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-all-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-bl-lc9-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-all-lc9-num-exps}}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc9-num-fail}/\UseMacro{test-results-bl-model0-lc9-num-fail}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc9-num-failrate}/\UseMacro{test-results-bl-model0-lc9-num-failrate}
 & BERT$\colon$\UseMacro{test-results-all-model0-lc9-num-pass-to-fail}\\
 & & & & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc9-num-fail}/\UseMacro{test-results-bl-model1-lc9-num-fail}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc9-num-failrate}/\UseMacro{test-results-bl-model1-lc9-num-failrate}
 & RoBERTa$\colon$\UseMacro{test-results-all-model1-lc9-num-pass-to-fail}\\
 & & & & dstBERT$\colon$\UseMacro{test-results-all-model2-lc9-num-fail}/\UseMacro{test-results-bl-model2-lc9-num-fail}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc9-num-failrate}/\UseMacro{test-results-bl-model2-lc9-num-failrate}
 & dstBERT$\colon$\UseMacro{test-results-all-model2-lc9-num-pass-to-fail}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2023-01-17 paper/fse23/tables/test-results-hs-all-numbers.tex
modify table

@@
 \DefMacro{test-results-hs-lc2-num-exps}{3,124}
-\DefMacro{test-results-hs-model0-lc2-num-all-fail}{3,220}
-\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{98.57}
-\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{98.66}
-\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{98.65}
-\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{18}
-\DefMacro{test-results-hs-lc18}{Denouncements of hate that quote it}
-\DefMacro{test-results-hs-lc18-num-seeds}{45,616}
-\DefMacro{test-results-hs-lc18-num-exps}{300,704}
-\DefMacro{test-results-hs-model0-lc18-num-all-fail}{48,804}
-\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{13.78}
-\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{14.14}
-\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{14.09}
-\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{4,831}
+\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc2-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc1}{Description using very negative attributes (explicit)}
@@
 \DefMacro{test-results-hs-lc1-num-exps}{2,959}
-\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,067}
-\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{98.57}
-\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{98.99}
-\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{98.97}
-\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{23}
+\DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc1-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc4}{Direct threat}
@@
 \DefMacro{test-results-hs-lc4-num-exps}{2,689}
-\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,770}
-\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{97.74}
-\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{98.18}
-\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{98.16}
-\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{9}
+\DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc4-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc0}{Expression of strong negative emotions (explicit)}
@@
 \DefMacro{test-results-hs-lc0-num-exps}{799}
-\DefMacro{test-results-hs-model0-lc0-num-all-fail}{920}
-\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{97.14}
-\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{98.12}
-\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{97.98}
-\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{22}
+\DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc0-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc10}{Hate expressed through reference in subsequent clauses}
@@
 \DefMacro{test-results-hs-lc10-num-exps}{44,890}
-\DefMacro{test-results-hs-model0-lc10-num-all-fail}{49,929}
-\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{60.60}
-\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{95.07}
-\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{87.81}
-\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,169}
+\DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc10-num-all-fail}{5,984}
+\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{50.00}
+\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{10.52}
+\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc11}{Hate expressed through reference in subsequent sentences}
@@
 \DefMacro{test-results-hs-lc11-num-exps}{42,840}
-\DefMacro{test-results-hs-model0-lc11-num-all-fail}{47,294}
-\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{58.92}
-\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{93.94}
-\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{86.29}
-\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,726}
+\DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc11-num-all-fail}{5,984}
+\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{50.00}
+\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{10.92}
+\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc12}{Hate expressed using negated positive statement}
@@
 \DefMacro{test-results-hs-lc12-num-exps}{126,742}
-\DefMacro{test-results-hs-model0-lc12-num-all-fail}{145,761}
-\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{97.03}
-\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{97.11}
-\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{2,290}
+\DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc12-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc8}{Hate expressed using profanity}
@@
 \DefMacro{test-results-hs-lc8-num-exps}{49,743}
-\DefMacro{test-results-hs-model0-lc8-num-all-fail}{50,158}
-\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{97.34}
-\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{97.23}
-\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{97.23}
-\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{164}
+\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc8-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc6}{Hate expressed using slur}
@@
 \DefMacro{test-results-hs-lc6-num-exps}{17,318}
-\DefMacro{test-results-hs-model0-lc6-num-all-fail}{17,597}
-\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{97.14}
-\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{70}
-\DefMacro{test-results-hs-lc15}{Hate phrased as a opinion}
-\DefMacro{test-results-hs-lc15-num-seeds}{22,808}
-\DefMacro{test-results-hs-lc15-num-exps}{160,927}
-\DefMacro{test-results-hs-model0-lc15-num-all-fail}{178,058}
-\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{97.25}
-\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{96.86}
-\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{96.91}
-\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,078}
-\DefMacro{test-results-hs-lc14}{Hate phrased as a question}
-\DefMacro{test-results-hs-lc14-num-seeds}{22,808}
-\DefMacro{test-results-hs-lc14-num-exps}{185,267}
-\DefMacro{test-results-hs-model0-lc14-num-all-fail}{202,023}
-\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{97.37}
-\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{97.06}
-\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{97.09}
-\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{2,956}
+\DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
+\DefMacro{test-results-hs-model0-lc6-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc3}{Implicit derogation}
@@
 \DefMacro{test-results-hs-lc3-num-exps}{5,664}
-\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,730}
-\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{97.86}
-\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{98.75}
-\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{98.73}
-\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{30}
-\DefMacro{test-results-hs-lc16}{Neutral statements using protected group identifiers}
-\DefMacro{test-results-hs-lc16-num-seeds}{5}
-\DefMacro{test-results-hs-lc16-num-exps}{9}
-\DefMacro{test-results-hs-model0-lc16-num-all-fail}{1}
-\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{20.00}
-\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{7.14}
-\DefMacro{test-results-hs-model0-lc16-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc3-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{0.00}
 \DefMacro{test-results-hs-lc9}{Non-Hateful use of profanity}
@@
 \DefMacro{test-results-hs-lc9-num-exps}{15,761}
-\DefMacro{test-results-hs-model0-lc9-num-all-fail}{11,939}
-\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{71.04}
-\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{72.59}
-\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{72.52}
-\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{75}
-\DefMacro{test-results-hs-lc13}{Non-hate expressed using negated hateful statement}
-\DefMacro{test-results-hs-lc13-num-seeds}{34,212}
-\DefMacro{test-results-hs-lc13-num-exps}{243,739}
-\DefMacro{test-results-hs-model0-lc13-num-all-fail}{77,191}
-\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{26.90}
-\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{27.89}
-\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{27.77}
-\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{5,222}
+\DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
+\DefMacro{test-results-hs-model0-lc9-num-all-fail}{16,462}
+\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{100}
+\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{100.00}
 \DefMacro{test-results-hs-lc7}{Non-hateful use of slur}
@@
 \DefMacro{test-results-hs-lc7-num-exps}{7,881}
-\DefMacro{test-results-hs-model0-lc7-num-all-fail}{2,739}
-\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{30.89}
-\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{33.21}
-\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{33.10}
-\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{44}
-\DefMacro{test-results-hs-lc17}{Positive statements using protected group identifiers}
-\DefMacro{test-results-hs-lc17-num-seeds}{41}
-\DefMacro{test-results-hs-lc17-num-exps}{182}
-\DefMacro{test-results-hs-model0-lc17-num-all-fail}{14}
-\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{4.88}
-\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{6.59}
-\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{6.28}
-\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{1}
+\DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
+\DefMacro{test-results-hs-model0-lc7-num-all-fail}{8,276}
+\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{111}
+\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{100.00}
 \DefMacro{test-results-hs-lc5}{Threat as normative statement}
@@
 \DefMacro{test-results-hs-lc5-num-exps}{4,163}
-\DefMacro{test-results-hs-model0-lc5-num-all-fail}{4,261}
-\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{99.29}
-\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{99.02}
-\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{99.02}
-\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{1}
-\DefMacro{test-results-hs-model1-lc2-num-all-fail}{87}
-\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{2.78}
-\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{2.67}
-\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{31}
-\DefMacro{test-results-hs-model1-lc18-num-all-fail}{346,320}
-\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc1-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc4-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc5-num-all-fail}{0}
+\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{0.00}
+\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{0.00}
+\DefMacro{test-results-hs-model1-lc2-num-all-fail}{3,210}
+\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{98.57}
+\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{98.34}
+\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{98.35}
+\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{11}
+\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{138}
+\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{98.57}
+\DefMacro{test-results-hs-model1-lc1-num-all-fail}{3,011}
+\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{97.86}
+\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{97.13}
+\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{97.16}
+\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{30}
+\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{136}
+\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{97.14}
+\DefMacro{test-results-hs-model1-lc4-num-all-fail}{2,750}
+\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{100.00}
+\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{97.32}
+\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{97.45}
 \DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc0-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc10-num-all-fail}{5,984}
-\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.00}
-\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{10.52}
-\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc11-num-all-fail}{5,984}
-\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{50.00}
-\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{10.92}
-\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc12-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc8-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc6-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc15-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc14-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc3-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc16-num-all-fail}{14}
-\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc9-num-all-fail}{16,462}
-\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc13-num-all-fail}{277,951}
-\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc7-num-all-fail}{8,276}
-\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc17-num-all-fail}{223}
-\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc5-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{132}
+\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{99.25}
+\DefMacro{test-results-hs-model1-lc0-num-all-fail}{845}
+\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{95.71}
+\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{88.99}
+\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{89.99}
+\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{19}
+\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{134}
+\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{95.71}
+\DefMacro{test-results-hs-model1-lc10-num-all-fail}{48,776}
+\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{49.97}
+\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{95.33}
+\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{85.79}
+\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{1,164}
+\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{132}
+\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{94.29}
+\DefMacro{test-results-hs-model1-lc11-num-all-fail}{46,721}
+\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{49.72}
+\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{95.17}
+\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{85.24}
+\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{1,070}
+\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{127}
+\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{95.49}
+\DefMacro{test-results-hs-model1-lc12-num-all-fail}{144,823}
+\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{96.71}
+\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{96.43}
+\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{96.47}
+\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{2,804}
+\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{136}
+\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{97.14}
+\DefMacro{test-results-hs-model1-lc8-num-all-fail}{49,739}
+\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{96.15}
+\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{96.43}
+\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{96.42}
+\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{188}
+\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{135}
+\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{96.43}
+\DefMacro{test-results-hs-model1-lc6-num-all-fail}{17,212}
+\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{96.40}
+\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{94.91}
+\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{94.97}
+\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{81}
+\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{142}
+\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{98.61}
+\DefMacro{test-results-hs-model1-lc3-num-all-fail}{5,526}
+\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{96.43}
+\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{95.18}
+\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{95.21}
+\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{56}
+\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{135}
+\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{96.43}
+\DefMacro{test-results-hs-model1-lc9-num-all-fail}{541}
+\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{3.28}
+\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{3.29}
+\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{3.29}
+\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{51}
+\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{1}
+\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{1.00}
+\DefMacro{test-results-hs-model1-lc7-num-all-fail}{318}
+\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{2.03}
+\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{3.93}
+\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{3.84}
+\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{20}
+\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{2}
+\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{1.80}
+\DefMacro{test-results-hs-model1-lc5-num-all-fail}{4,198}
+\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{97.14}
+\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{97.57}
+\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{97.56}
+\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{12}
+\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{136}
+\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{97.14}
+\DefMacro{test-results-hs-model2-lc2-num-all-fail}{3,220}
+\DefMacro{test-results-hs-model2-lc2-num-seed-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc2-num-exp-failrate}{98.66}
+\DefMacro{test-results-hs-model2-lc2-num-all-failrate}{98.65}
+\DefMacro{test-results-hs-model2-lc2-num-pass-to-fail}{18}
+\DefMacro{test-results-hs-bl-model2-lc2-num-fail}{138}
+\DefMacro{test-results-hs-bl-model2-lc2-num-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc1-num-all-fail}{3,067}
+\DefMacro{test-results-hs-model2-lc1-num-seed-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc1-num-exp-failrate}{98.99}
+\DefMacro{test-results-hs-model2-lc1-num-all-failrate}{98.97}
+\DefMacro{test-results-hs-model2-lc1-num-pass-to-fail}{23}
+\DefMacro{test-results-hs-bl-model2-lc1-num-fail}{138}
+\DefMacro{test-results-hs-bl-model2-lc1-num-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc4-num-all-fail}{2,770}
+\DefMacro{test-results-hs-model2-lc4-num-seed-failrate}{97.74}
+\DefMacro{test-results-hs-model2-lc4-num-exp-failrate}{98.18}
+\DefMacro{test-results-hs-model2-lc4-num-all-failrate}{98.16}
+\DefMacro{test-results-hs-model2-lc4-num-pass-to-fail}{9}
+\DefMacro{test-results-hs-bl-model2-lc4-num-fail}{133}
+\DefMacro{test-results-hs-bl-model2-lc4-num-failrate}{100.00}
+\DefMacro{test-results-hs-model2-lc0-num-all-fail}{920}
+\DefMacro{test-results-hs-model2-lc0-num-seed-failrate}{97.14}
+\DefMacro{test-results-hs-model2-lc0-num-exp-failrate}{98.12}
+\DefMacro{test-results-hs-model2-lc0-num-all-failrate}{97.98}
+\DefMacro{test-results-hs-model2-lc0-num-pass-to-fail}{22}
+\DefMacro{test-results-hs-bl-model2-lc0-num-fail}{136}
+\DefMacro{test-results-hs-bl-model2-lc0-num-failrate}{97.14}
+\DefMacro{test-results-hs-model2-lc10-num-all-fail}{48,642}
+\DefMacro{test-results-hs-model2-lc10-num-seed-failrate}{49.85}
+\DefMacro{test-results-hs-model2-lc10-num-exp-failrate}{95.07}
+\DefMacro{test-results-hs-model2-lc10-num-all-failrate}{85.55}
+\DefMacro{test-results-hs-model2-lc10-num-pass-to-fail}{1,169}
+\DefMacro{test-results-hs-bl-model2-lc10-num-fail}{138}
+\DefMacro{test-results-hs-bl-model2-lc10-num-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc11-num-all-fail}{46,156}
+\DefMacro{test-results-hs-model2-lc11-num-seed-failrate}{49.41}
+\DefMacro{test-results-hs-model2-lc11-num-exp-failrate}{93.94}
+\DefMacro{test-results-hs-model2-lc11-num-all-failrate}{84.21}
+\DefMacro{test-results-hs-model2-lc11-num-pass-to-fail}{1,726}
+\DefMacro{test-results-hs-bl-model2-lc11-num-fail}{133}
+\DefMacro{test-results-hs-bl-model2-lc11-num-failrate}{100.00}
+\DefMacro{test-results-hs-model2-lc12-num-all-fail}{145,761}
+\DefMacro{test-results-hs-model2-lc12-num-seed-failrate}{97.03}
+\DefMacro{test-results-hs-model2-lc12-num-exp-failrate}{97.11}
+\DefMacro{test-results-hs-model2-lc12-num-all-failrate}{97.10}
+\DefMacro{test-results-hs-model2-lc12-num-pass-to-fail}{2,290}
+\DefMacro{test-results-hs-bl-model2-lc12-num-fail}{138}
+\DefMacro{test-results-hs-bl-model2-lc12-num-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc8-num-all-fail}{50,158}
+\DefMacro{test-results-hs-model2-lc8-num-seed-failrate}{97.34}
+\DefMacro{test-results-hs-model2-lc8-num-exp-failrate}{97.23}
+\DefMacro{test-results-hs-model2-lc8-num-all-failrate}{97.23}
+\DefMacro{test-results-hs-model2-lc8-num-pass-to-fail}{164}
+\DefMacro{test-results-hs-bl-model2-lc8-num-fail}{138}
+\DefMacro{test-results-hs-bl-model2-lc8-num-failrate}{98.57}
+\DefMacro{test-results-hs-model2-lc6-num-all-fail}{17,597}
+\DefMacro{test-results-hs-model2-lc6-num-seed-failrate}{97.14}
+\DefMacro{test-results-hs-model2-lc6-num-exp-failrate}{97.10}
+\DefMacro{test-results-hs-model2-lc6-num-all-failrate}{97.10}
+\DefMacro{test-results-hs-model2-lc6-num-pass-to-fail}{70}
+\DefMacro{test-results-hs-bl-model2-lc6-num-fail}{144}
+\DefMacro{test-results-hs-bl-model2-lc6-num-failrate}{100.00}
+\DefMacro{test-results-hs-model2-lc3-num-all-fail}{5,730}
+\DefMacro{test-results-hs-model2-lc3-num-seed-failrate}{97.86}
+\DefMacro{test-results-hs-model2-lc3-num-exp-failrate}{98.75}
+\DefMacro{test-results-hs-model2-lc3-num-all-failrate}{98.73}
+\DefMacro{test-results-hs-model2-lc3-num-pass-to-fail}{30}
+\DefMacro{test-results-hs-bl-model2-lc3-num-fail}{137}
+\DefMacro{test-results-hs-bl-model2-lc3-num-failrate}{97.86}
+\DefMacro{test-results-hs-model2-lc9-num-all-fail}{549}
+\DefMacro{test-results-hs-model2-lc9-num-seed-failrate}{3.14}
+\DefMacro{test-results-hs-model2-lc9-num-exp-failrate}{3.34}
+\DefMacro{test-results-hs-model2-lc9-num-all-failrate}{3.33}
+\DefMacro{test-results-hs-model2-lc9-num-pass-to-fail}{58}
+\DefMacro{test-results-hs-bl-model2-lc9-num-fail}{4}
+\DefMacro{test-results-hs-bl-model2-lc9-num-failrate}{4.00}
+\DefMacro{test-results-hs-model2-lc7-num-all-fail}{222}
+\DefMacro{test-results-hs-model2-lc7-num-seed-failrate}{2.28}
+\DefMacro{test-results-hs-model2-lc7-num-exp-failrate}{2.70}
+\DefMacro{test-results-hs-model2-lc7-num-all-failrate}{2.68}
+\DefMacro{test-results-hs-model2-lc7-num-pass-to-fail}{26}
+\DefMacro{test-results-hs-bl-model2-lc7-num-fail}{1}
+\DefMacro{test-results-hs-bl-model2-lc7-num-failrate}{0.90}
+\DefMacro{test-results-hs-model2-lc5-num-all-fail}{4,261}
+\DefMacro{test-results-hs-model2-lc5-num-seed-failrate}{99.29}
+\DefMacro{test-results-hs-model2-lc5-num-exp-failrate}{99.02}
+\DefMacro{test-results-hs-model2-lc5-num-all-failrate}{99.02}
+\DefMacro{test-results-hs-model2-lc5-num-pass-to-fail}{1}
+\DefMacro{test-results-hs-bl-model2-lc5-num-fail}{139}
+\DefMacro{test-results-hs-bl-model2-lc5-num-failrate}{99.29}

### 2023-01-17 paper/fse23/tables/test-results-hs-table.tex
modify table

%% Automatically generated by pyutil.latex

\begin{table*}[htbp]
\begin{small}
\begin{center}
\caption{\TestResultsHsTableCaption}
\resizebox{0.7\textwidth}{!}{
\begin{tabular}{p{8cm}||ccclll}
\toprule
\tLc & \parbox{1cm}{\tNumBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
\midrule
\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc0-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc0-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc0-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc1-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc1-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc1-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc2-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc2-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc2-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc3-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc3-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc3-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc4-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc4-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc4-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc5-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc5-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc5-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc6-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc6-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc6-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc6-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc6-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc6-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc6-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc7-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc7-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc7-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc7-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc7-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc7-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc7-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc8-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc8-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc8-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc8-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc8-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc8-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc8-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc9-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc9-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc9-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc9-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc9-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc9-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc9-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc10-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc10-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc10-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc10-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc10-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc10-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc10-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc11-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc11-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc11-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc11-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc11-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc11-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc11-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-pass-to-fail}\\
\hline
\multirow{3}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc12-num-tcs}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc12-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc12-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc12-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc12-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-pass-to-fail}\\
 & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc12-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc12-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-pass-to-fail}\\
\hline
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\TestResultsTableVSpace}
\end{table*}

### 2023-01-18 paper/fse23/tables/test-results-hs-all-numbers.tex
tabnle

--- 2023-01-10 paper/fse23/tables/test-results-hs-all-numbers.tex
@@
 \DefMacro{test-results-hs-lc2-num-exps}{3,124}
-\DefMacro{test-results-hs-model0-lc2-num-all-fail}{3,220}
-\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{98.57}
-\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{98.66}
-\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{98.65}
-\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{18}
+\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc2-num-all-fail}{2,646}
+\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{85.00}
+\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{80.89}
+\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{81.07}
+\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{15}
+\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{119}
+\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{85.00}
 \DefMacro{test-results-hs-lc18}{Denouncements of hate that quote it}
@@
 \DefMacro{test-results-hs-lc18-num-exps}{300,704}
-\DefMacro{test-results-hs-model0-lc18-num-all-fail}{48,804}
-\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{13.78}
-\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{14.14}
-\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{14.09}
-\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{4,831}
+\DefMacro{test-results-hs-bl-lc18-num-tcs}{173}
+\DefMacro{test-results-hs-model0-lc18-num-all-fail}{87,197}
+\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{23.04}
+\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{25.50}
+\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{25.18}
+\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{3,379}
+\DefMacro{test-results-hs-bl-model0-lc18-num-fail}{36}
+\DefMacro{test-results-hs-bl-model0-lc18-num-failrate}{20.81}
 \DefMacro{test-results-hs-lc1}{Description using very negative attributes (explicit)}
@@
 \DefMacro{test-results-hs-lc1-num-exps}{2,959}
-\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,067}
-\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{98.57}
-\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{98.99}
-\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{98.97}
-\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{23}
+\DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc1-num-all-fail}{2,731}
+\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{87.86}
+\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{88.14}
+\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{88.13}
+\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{31}
+\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{123}
+\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{87.86}
 \DefMacro{test-results-hs-lc4}{Direct threat}
@@
 \DefMacro{test-results-hs-lc4-num-exps}{2,689}
-\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,770}
-\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{97.74}
-\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{98.18}
-\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{98.16}
-\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{9}
+\DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,056}
+\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{69.17}
+\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{73.04}
+\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{72.86}
+\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{49}
+\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{90}
+\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{67.67}
 \DefMacro{test-results-hs-lc0}{Expression of strong negative emotions (explicit)}
@@
 \DefMacro{test-results-hs-lc0-num-exps}{799}
-\DefMacro{test-results-hs-model0-lc0-num-all-fail}{920}
-\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{97.14}
-\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{98.12}
-\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{97.98}
-\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{22}
+\DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc0-num-all-fail}{823}
+\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{87.86}
+\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{87.61}
+\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{87.65}
+\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{12}
+\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{123}
+\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{87.86}
 \DefMacro{test-results-hs-lc10}{Hate expressed through reference in subsequent clauses}
@@
 \DefMacro{test-results-hs-lc10-num-exps}{44,890}
-\DefMacro{test-results-hs-model0-lc10-num-all-fail}{49,929}
-\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{60.60}
-\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{95.07}
-\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{87.81}
-\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,169}
+\DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc10-num-all-fail}{33,230}
+\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{48.53}
+\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{61.09}
+\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{58.44}
+\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,434}
+\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{114}
+\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{81.43}
 \DefMacro{test-results-hs-lc11}{Hate expressed through reference in subsequent sentences}
@@
 \DefMacro{test-results-hs-lc11-num-exps}{42,840}
-\DefMacro{test-results-hs-model0-lc11-num-all-fail}{47,294}
-\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{58.92}
-\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{93.94}
-\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{86.29}
-\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,726}
+\DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc11-num-all-fail}{32,167}
+\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{50.70}
+\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{60.92}
+\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{58.69}
+\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,410}
+\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{104}
+\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{78.20}
 \DefMacro{test-results-hs-lc12}{Hate expressed using negated positive statement}
@@
 \DefMacro{test-results-hs-lc12-num-exps}{126,742}
-\DefMacro{test-results-hs-model0-lc12-num-all-fail}{145,761}
-\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{97.03}
-\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{97.11}
-\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{2,290}
+\DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc12-num-all-fail}{130,886}
+\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{86.56}
+\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{87.30}
+\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{87.19}
+\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{1,888}
+\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{123}
+\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{87.86}
 \DefMacro{test-results-hs-lc8}{Hate expressed using profanity}
@@
 \DefMacro{test-results-hs-lc8-num-exps}{49,743}
-\DefMacro{test-results-hs-model0-lc8-num-all-fail}{50,158}
-\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{97.34}
-\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{97.23}
-\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{97.23}
-\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{164}
+\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc8-num-all-fail}{38,673}
+\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{77.31}
+\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{74.88}
+\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{74.97}
+\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{177}
+\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{119}
+\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{85.00}
 \DefMacro{test-results-hs-lc6}{Hate expressed using slur}
@@
 \DefMacro{test-results-hs-lc6-num-exps}{17,318}
-\DefMacro{test-results-hs-model0-lc6-num-all-fail}{17,597}
-\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{97.14}
-\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{70}
+\DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
+\DefMacro{test-results-hs-model0-lc6-num-all-fail}{13,383}
+\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{75.16}
+\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{73.78}
+\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{73.85}
+\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{92}
+\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{129}
+\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{89.58}
 \DefMacro{test-results-hs-lc15}{Hate phrased as a opinion}
@@
 \DefMacro{test-results-hs-lc15-num-exps}{160,927}
-\DefMacro{test-results-hs-model0-lc15-num-all-fail}{178,058}
-\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{97.25}
-\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{96.86}
-\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{96.91}
-\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,078}
+\DefMacro{test-results-hs-bl-lc15-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc15-num-all-fail}{142,434}
+\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{79.31}
+\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{77.27}
+\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{77.52}
+\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,544}
+\DefMacro{test-results-hs-bl-model0-lc15-num-fail}{108}
+\DefMacro{test-results-hs-bl-model0-lc15-num-failrate}{81.20}
 \DefMacro{test-results-hs-lc14}{Hate phrased as a question}
@@
 \DefMacro{test-results-hs-lc14-num-exps}{185,267}
-\DefMacro{test-results-hs-model0-lc14-num-all-fail}{202,023}
-\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{97.37}
-\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{97.06}
-\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{97.09}
-\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{2,956}
+\DefMacro{test-results-hs-bl-lc14-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc14-num-all-fail}{163,340}
+\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{80.37}
+\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{78.27}
+\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{78.50}
+\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{3,435}
+\DefMacro{test-results-hs-bl-model0-lc14-num-fail}{117}
+\DefMacro{test-results-hs-bl-model0-lc14-num-failrate}{83.57}
 \DefMacro{test-results-hs-lc3}{Implicit derogation}
@@
 \DefMacro{test-results-hs-lc3-num-exps}{5,664}
-\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,730}
-\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{97.86}
-\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{98.75}
-\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{98.73}
-\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{30}
+\DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,029}
+\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{84.29}
+\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{86.71}
+\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{86.65}
+\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{77}
+\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{118}
+\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{84.29}
 \DefMacro{test-results-hs-lc16}{Neutral statements using protected group identifiers}
@@
 \DefMacro{test-results-hs-lc16-num-exps}{9}
-\DefMacro{test-results-hs-model0-lc16-num-all-fail}{1}
-\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{20.00}
-\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{7.14}
+\DefMacro{test-results-hs-bl-lc16-num-tcs}{126}
+\DefMacro{test-results-hs-model0-lc16-num-all-fail}{13}
+\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{80.00}
+\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{92.86}
 \DefMacro{test-results-hs-model0-lc16-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc16-num-fail}{12}
+\DefMacro{test-results-hs-bl-model0-lc16-num-failrate}{9.52}
 \DefMacro{test-results-hs-lc9}{Non-Hateful use of profanity}
@@
 \DefMacro{test-results-hs-lc9-num-exps}{15,761}
-\DefMacro{test-results-hs-model0-lc9-num-all-fail}{11,939}
-\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{71.04}
-\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{72.59}
-\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{72.52}
-\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{75}
+\DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
+\DefMacro{test-results-hs-model0-lc9-num-all-fail}{3,583}
+\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{17.69}
+\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{21.95}
+\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{21.77}
+\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{44}
+\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{6}
+\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{6.00}
 \DefMacro{test-results-hs-lc13}{Non-hate expressed using negated hateful statement}
@@
 \DefMacro{test-results-hs-lc13-num-exps}{243,739}
-\DefMacro{test-results-hs-model0-lc13-num-all-fail}{77,191}
-\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{26.90}
-\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{27.89}
-\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{27.77}
-\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{5,222}
+\DefMacro{test-results-hs-bl-lc13-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc13-num-all-fail}{86,576}
+\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{29.45}
+\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{31.39}
+\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{31.15}
+\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{3,134}
+\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{25}
+\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{18.80}
 \DefMacro{test-results-hs-lc7}{Non-hateful use of slur}
@@
 \DefMacro{test-results-hs-lc7-num-exps}{7,881}
-\DefMacro{test-results-hs-model0-lc7-num-all-fail}{2,739}
-\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{30.89}
-\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{33.21}
-\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{33.10}
-\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{44}
+\DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
+\DefMacro{test-results-hs-model0-lc7-num-all-fail}{5,600}
+\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{73.16}
+\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{67.39}
+\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{67.67}
+\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{11}
+\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{22}
+\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{19.82}
 \DefMacro{test-results-hs-lc17}{Positive statements using protected group identifiers}
@@
 \DefMacro{test-results-hs-lc17-num-exps}{182}
-\DefMacro{test-results-hs-model0-lc17-num-all-fail}{14}
-\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{4.88}
-\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{6.59}
-\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{6.28}
+\DefMacro{test-results-hs-bl-lc17-num-tcs}{189}
+\DefMacro{test-results-hs-model0-lc17-num-all-fail}{137}
+\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{65.85}
+\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{60.44}
+\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{61.43}
 \DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{1}
+\DefMacro{test-results-hs-bl-model0-lc17-num-fail}{32}
+\DefMacro{test-results-hs-bl-model0-lc17-num-failrate}{16.93}
 \DefMacro{test-results-hs-lc5}{Threat as normative statement}
@@
 \DefMacro{test-results-hs-lc5-num-exps}{4,163}
-\DefMacro{test-results-hs-model0-lc5-num-all-fail}{4,261}
-\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{99.29}
-\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{99.02}
-\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{99.02}
-\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{1}
-\DefMacro{test-results-hs-model1-lc2-num-all-fail}{87}
-\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{2.78}
-\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{2.67}
-\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{31}
-\DefMacro{test-results-hs-model1-lc18-num-all-fail}{346,320}
-\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc1-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc4-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc0-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc10-num-all-fail}{5,984}
-\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.00}
-\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{10.52}
-\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc11-num-all-fail}{5,984}
-\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{50.00}
-\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{10.92}
-\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc12-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc8-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc6-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc15-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc14-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc3-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc16-num-all-fail}{14}
-\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc9-num-all-fail}{16,462}
-\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc13-num-all-fail}{277,951}
-\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc7-num-all-fail}{8,276}
-\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc17-num-all-fail}{223}
-\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc5-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc5-num-all-fail}{3,207}
+\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{77.14}
+\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{74.44}
+\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{74.53}
+\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{31}
+\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{108}
+\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{77.14}
+\DefMacro{test-results-hs-model1-lc2-num-all-fail}{2,854}
+\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{88.57}
+\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{87.39}
+\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{87.44}
+\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{96}
+\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{124}
+\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{88.57}
+\DefMacro{test-results-hs-model1-lc18-num-all-fail}{200,285}
+\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{56.83}
+\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{57.98}
+\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{57.83}
+\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{5,259}
+\DefMacro{test-results-hs-bl-model1-lc18-num-fail}{8}
+\DefMacro{test-results-hs-bl-model1-lc18-num-failrate}{4.62}
+\DefMacro{test-results-hs-model1-lc1-num-all-fail}{2,465}
+\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{77.14}
+\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{79.66}
+\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{79.54}
+\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{140}
+\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{108}
+\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{77.14}
+\DefMacro{test-results-hs-model1-lc4-num-all-fail}{2,455}
+\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{93.23}
+\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{86.69}
+\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{87.00}
+\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{25}
+\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{121}
+\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{90.98}
+\DefMacro{test-results-hs-model1-lc0-num-all-fail}{829}
+\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{88.57}
+\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{88.24}
+\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{88.29}
+\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{38}
+\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{124}
+\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{88.57}
+\DefMacro{test-results-hs-model1-lc10-num-all-fail}{44,034}
+\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{67.54}
+\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{80.09}
+\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{77.45}
+\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{1,441}
+\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{122}
+\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{87.14}
+\DefMacro{test-results-hs-model1-lc11-num-all-fail}{43,256}
+\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{68.57}
+\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{81.81}
+\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{78.92}
+\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{1,348}
+\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{102}
+\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{76.69}
+\DefMacro{test-results-hs-model1-lc12-num-all-fail}{126,635}
+\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{82.76}
+\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{84.65}
+\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{84.36}
+\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{4,361}
+\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{124}
+\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{88.57}
+\DefMacro{test-results-hs-model1-lc8-num-all-fail}{46,325}
+\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{90.88}
+\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{89.76}
+\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{89.80}
+\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{145}
+\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{114}
+\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{81.43}
+\DefMacro{test-results-hs-model1-lc6-num-all-fail}{15,710}
+\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{89.07}
+\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{86.57}
+\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{86.69}
+\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{68}
+\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{135}
+\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{93.75}
+\DefMacro{test-results-hs-model1-lc15-num-all-fail}{158,127}
+\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{85.90}
+\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{86.09}
+\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{86.06}
+\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{4,584}
+\DefMacro{test-results-hs-bl-model1-lc15-num-fail}{121}
+\DefMacro{test-results-hs-bl-model1-lc15-num-failrate}{90.98}
+\DefMacro{test-results-hs-model1-lc14-num-all-fail}{182,688}
+\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{87.13}
+\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{87.88}
+\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{87.80}
+\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{5,531}
+\DefMacro{test-results-hs-bl-model1-lc14-num-fail}{131}
+\DefMacro{test-results-hs-bl-model1-lc14-num-failrate}{93.57}
+\DefMacro{test-results-hs-model1-lc3-num-all-fail}{5,481}
+\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{95.00}
+\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{94.42}
+\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{94.43}
+\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{19}
+\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{133}
+\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{95.00}
+\DefMacro{test-results-hs-model1-lc16-num-all-fail}{2}
+\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{20.00}
+\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{11.11}
+\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{14.29}
+\DefMacro{test-results-hs-model1-lc16-num-pass-to-fail}{1}
+\DefMacro{test-results-hs-bl-model1-lc16-num-fail}{1}
+\DefMacro{test-results-hs-bl-model1-lc16-num-failrate}{0.79}
+\DefMacro{test-results-hs-model1-lc9-num-all-fail}{7,267}
+\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{58.35}
+\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{43.51}
+\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{44.14}
+\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{60}
+\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{3}
+\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{3.00}
+\DefMacro{test-results-hs-model1-lc13-num-all-fail}{203,241}
+\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{74.12}
+\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{72.98}
+\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{73.12}
+\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{3,274}
+\DefMacro{test-results-hs-bl-model1-lc13-num-fail}{33}
+\DefMacro{test-results-hs-bl-model1-lc13-num-failrate}{24.81}
+\DefMacro{test-results-hs-model1-lc7-num-all-fail}{6,815}
+\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{89.62}
+\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{81.98}
+\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{82.35}
+\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{26}
+\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{76}
+\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{68.47}
+\DefMacro{test-results-hs-model1-lc17-num-all-fail}{63}
+\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{39.02}
+\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{25.82}
+\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{28.25}
+\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{5}
+\DefMacro{test-results-hs-bl-model1-lc17-num-fail}{26}
+\DefMacro{test-results-hs-bl-model1-lc17-num-failrate}{13.76}
+\DefMacro{test-results-hs-model1-lc5-num-all-fail}{3,591}
+\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{84.29}
+\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{83.43}
+\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{83.45}
+\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{50}
+\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{118}
+\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{84.29}

### 2023-01-18 paper/fse23/tables/test-results-hs-table.tex
tabnle

@@
 \toprule
-\tLc & \parbox{1cm}{\tNumBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\
+\tLc & \parbox{1cm}{\tNumHsBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.7cm}{\centering\tNumHsFail} & \parbox{1.7cm}{\centering\tHsFailRate} & \parbox{1.7cm}{\centering\tNumPasstoFail}\\
 \midrule
-\multirow{3}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc0-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc0-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc0-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc1-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc1-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc1-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc2-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc2-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc2-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc3-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc3-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc3-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc4-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc4-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc4-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc5-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc5-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc5-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc6-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc6-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc6-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc6-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc6-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc6-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc6-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc6-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc6-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc6-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc6-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc6-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc6-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc6-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc7-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc7-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc7-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc7-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc7-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc7-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc7-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc7-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc7-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc7-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc7-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc7-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc7-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc7-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc8-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc8-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc8-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc8-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc8-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc8-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc8-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc8-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc8-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc8-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc8-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc8-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc8-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc8-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc9-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc9-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc9-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc9-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc9-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc9-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc9-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc9-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc9-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc9-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc9-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc9-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc9-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc9-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc10-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc10-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc10-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc10-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc10-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc10-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc10-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc10-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc10-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc10-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc10-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc10-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc10-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc10-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc11-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc11-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc11-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc11-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc11-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc11-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc11-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc11-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc11-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc11-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc11-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc11-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc11-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc11-num-pass-to-fail}\\
 \hline
-\multirow{3}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-bl-lc12-num-tcs}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-seeds}}
- & \multirow{3}{*}{\centering\UseMacro{test-results-hs-lc12-num-exps}}
+\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc12-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc12-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc12-num-exps}}
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc12-num-fail}
@@
  & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc12-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc12-num-fail}
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc12-num-fail}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc12-num-failrate}
  & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc12-num-pass-to-fail}\\
- & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-fail}/\UseMacro{test-results-hs-bl-model2-lc12-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-all-failrate}/\UseMacro{test-results-hs-bl-model2-lc12-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model2-lc12-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc13}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc13-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc13-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc13-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc13-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc13-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc13-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc13-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc13-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc13-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc13-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc13-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc13-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc13-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-lc14}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc14-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc14-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc14-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc14-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc14-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-lc15}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc15-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc15-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc15-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc15-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc15-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-lc16}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc16-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc16-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc16-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc16-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc16-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-lc17}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc17-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc17-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc17-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc17-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc17-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-pass-to-fail}\\
+\hline
+\multirow{2}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-lc18}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc18-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc18-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc18-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc18-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc18-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-pass-to-fail}\\
 \hline

### 2023-01-18 python/hs/paper/Tables.py

@@ -328,7 +328,7 @@ class Tables:
         output_file.append(r"\toprule")
         
         # output_file.append(r"\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\")
-        output_file.append(r"\tLc & \parbox{1cm}{\tNumBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\")
+        output_file.append(r"\tLc & \parbox{1cm}{\tNumHsBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.7cm}{\centering\tNumHsFail} & \parbox{1.7cm}{\centering\tHsFailRate} & \parbox{1.7cm}{\centering\tNumPasstoFail}\\")
         output_file.append(r"\midrule")
         
         # Content
@@ -357,7 +357,7 @@ class Tables:
                 # # end if
                 m_name = 'CNERG-BERT'
                 # output_file.append(f" & & {m_name}$\colon$" + latex.Macro(f"test-results-hs-bl-model{m_i}-lc{lc_i}-num-fail").use())
-                output_file.append(f" & & & {m_name}$\colon$" + latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-all-fail").use() + '/' + \
+                output_file.append(f" & & & & {m_name}$\colon$" + latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-all-fail").use() + '/' + \
                                    latex.Macro(f"test-results-hs-bl-model{m_i}-lc{lc_i}-num-fail").use())
                 output_file.append(f" & {m_name}$\colon$" + latex.Macro(f"test-results-hs-model{m_i}-lc{lc_i}-num-all-failrate").use() + '/' + \
                                    latex.Macro(f"test-results-hs-bl-model{m_i}-lc{lc_i}-num-failrate").use())

### 2023-01-18 python/sa/paper/Tables.py

@@ -836,7 +836,7 @@ class Tables:
         output_file.append(r"\begin{tabular}{p{8cm}||ccclll}")
         output_file.append(r"\toprule")
         
-        output_file.append(r"\tLc & \parbox{1cm}{\tNumBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\")
+        output_file.append(r"\tLc & \parbox{1.5cm}{\tNumBlTcs} & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumFail} & \parbox{1.5cm}{\centering\tFailRate} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\")
         output_file.append(r"\midrule")
         
         # Content
@@ -864,7 +864,7 @@ class Tables:
                 else:
                     m_name = 'dstBERT'
                 # output_file.append(f" & & {m_name}$\colon$" + latex.Macro(f"test-results-bl-model{m_i}-lc{lc_i}-num-fail").use())
-                output_file.append(f" & & & {m_name}$\colon$" + latex.Macro(f"test-results-all-model{m_i}-lc{lc_i}-num-fail").use() + '/' + \
+                output_file.append(f" & & & & {m_name}$\colon$" + latex.Macro(f"test-results-all-model{m_i}-lc{lc_i}-num-fail").use() + '/' + \
                                    latex.Macro(f"test-results-bl-model{m_i}-lc{lc_i}-num-fail").use())
                 output_file.append(f" & {m_name}$\colon$" + latex.Macro(f"test-results-all-model{m_i}-lc{lc_i}-num-failrate").use() + '/' + \
                                    latex.Macro(f"test-results-bl-model{m_i}-lc{lc_i}-num-failrate").use())

### 2023-01-18 paper/fse23/experiment.tex
debug

@@
 language using a masked language modeling (MLM) objective, and
-were fine-tuned on the \sa task. In this experiment, we used the \Sstt \cite{socher2013sst} dataset for
-searching the seeds in \tool. \Sstt is a
+were fine-tuned on the \sa task. In this experiment, we used the \Sst \cite{socher2013sst} dataset for
+searching the seeds in \tool. \Sst is a
 corpus of movie review, consisting of 11,855 sentences

### 2023-01-18 paper/fse23/experiment.tex
debug

@@
 \begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:three}: \textbf{Test Case Diversity.} Can \tool generate more diverse test cases
-  than \Cklst?
+% \item \label{rq:three}: \textbf{Test Case Diversity.} Can \tool generate more diverse test cases
+%   than \Cklst?
+\item \label{rq:three}: \textbf{Test Efficiency.} Can \tool generated test cases evaluate an NLP model more efficiently?
 \item \label{rq:one}: \textbf{Test Oracle.}  Can \tool generate test sentences with correct sentiment labels?
@@
 \subsection{Experimental Subjects}
+\paragraph*{\textbf{NLP Models \& Dataset}}
+We evaluate our approach on three \sa models and two \hsd models. All
+are learning-based models released from the Hugging Face centralized
+model hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
+(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and
+\texttt{\Dbert} (\disbertsamodel~\cite{sanh2019distilbertad}) for \sa
+task, and \texttt{\hsdBert} (\berthsdmodel~\cite{aluru2020deep}) and
+\texttt{\hsdRoBerta} (\robertahsdmodel) for \hsd.
 
-\paragraph*{\textbf{NLP Models \& Dataset}}
-We evaluate our approach on three learning-based \sa models released from the Hugging Face centralized
-model hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
-(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
-language using a masked language modeling (MLM) objective, and
-were fine-tuned on the \sa task. In this experiment, we used the \Sst \cite{socher2013sst} dataset for
-searching the seeds in \tool. \Sst is a
-corpus of movie review, consisting of 11,855 sentences
-with sentiment scores. We split the
-scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign them
-negative, neutral and positive labels, respectively. In addition,
-\Swn~\cite{baccianella2010sentiwordnet} is a publicly available dataset for English sentiment lexicons.  
-It provides lexical sentiment scores and the sentiment word labels 
-are categorized by implementing the rules.
-We used \Swn as both the generation and the expansion domain knowledge as shown in Figure \ref{fig:overview}.
+These models were pre-trained on English language using a masked
+language modeling (MLM) objective, and were fine-tuned on the \sa and
+\hsd task. In this experiment, we used the \Sst~\cite{socher2013sst}
+and \Hatexp~\cite{mathew2021hatexplain} datasets, for \sa and \hsd
+respectively, for searching the seeds in \tool. \Sst is a corpus of
+movie review, consisting of 11,855 sentences with sentiment scores. We
+split the scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to
+    assign them negative, neutral and positive labels,
+    respectively. \Hatexp is a hate speech dataset collected from
+    Twitter and Gab. It consists of 20,148 sentences (9,055 from
+    Twitter and 11,093 from Gab). Each data has sentence, class of
+    hate speech, target community, and rationale for the labelling
+    decision.  In addition, \Swn~\cite{baccianella2010sentiwordnet} is
+    a publicly available dataset for English sentiment lexicons.  We
+    used \Swn as both the generation and the expansion domain
+    knowledge as shown in Figure \ref{fig:overview}.
 
@@
 We compared \tool with
-\Cklst,\footnote{https://github.com/marcotcr/checklist} a
-manual template and \lc based approach to generate test cases. In this evalaution, we used \Cklst's \sa test cases that are
-generated from its publicly available Jupyter Notebook implementation.
+\Cklst,\footnote{https://github.com/marcotcr/checklist} a manual
+template and \lc based approach to generate test cases. In this
+evalaution, we used \Cklst's \sa test cases that are generated from
+its publicly available Jupyter Notebook implementation. \jl{Do we need
+  to explain why we used checklist only as a baseline?}
 
@@
 \paragraph*{\textbf{RQ1}}
-Recall that \Cklst relies on significant manual efforts and may not generate comprehensive test cases in a linguistic capability. \tool, instead, automatically generates test cases based on a search
-dataset and the syntax in a large reference corpus. 
-We expect \tool can generate a more diverse test suite than \Cklst.
+Recall that \Cklst relies on significant manual efforts and may not
+generate comprehensive test cases in a linguistic capability. \tool,
+instead, automatically generates test cases based on a search dataset
+and the syntax in a large reference corpus.  We expect \tool can
+generate more efficient test suite than \Cklst for finding errors with
+regards to quantity and diversity of test suite.
 
-We first evaluate the three \sa models by testing them on the \tool  test cases, reporting number of test cases and each model's failure rate in each linguistic capability.
-Specifically, for each \lc, we randomly choose 50, 100 and 200 seeds , and expand test cases from these seeds.
-We selected subsets of seeds to be used for expansion because the syntax-based expansion phase may be expensive to run all the generated seeds.
-We tested the three models using both seed and expanded test cases.
-To account for the randomness in random seed selection, we repeated these experiments 3 times and report median number of test cases and each model's failure rate.
+We first evaluate the three \sa models and two \hsd models by testing
+them on the \tool test cases, reporting number of test cases and each
+model's failure rate in each linguistic capability. Specifically, for
+each \lc, we expand test cases from all generated seeds.
+% We selected subsets of seeds to be used for expansion because the
+% syntax-based expansion phase may be expensive to run all the
+% generated seeds.
+We test the five models using both seed and expanded test cases. 
+% To account for the randomness in random seed selection, we repeated
+% these experiments 3 times and report median number of test cases and
+% each model's failure rate.
 
-We use two metrics to compare the diversity between the \tool generated seeds and the \Cklst test cases.
+We use two metrics to compare the diversity between the \tool
+generated seeds and the \Cklst test cases.
 
 \paragraph*{\selfbleu} We reuse the input diversity metric, 
-called \selfbleu, that Zhu \etal introduced~\cite{zhu2018texygen}. \bleu evaluates the token-level similarity.
-% Regarding that \selfbleu takes each sentence as hypothesis and rest in a collection of textual data as reference, we calculate \bleu scores for every pairs of hypothesis and each reference sentence.
-The \selfbleu is defined as the average \bleu scores over all reference sentences.
-% Since the \bleu score ranges from 0 as the least similar inputs to 1 as the most similar inputs,
-A higher \selfbleu score indicates less diversity in the test suite.
-In the experiment, we collected 50, 100 and 200 randomly selected \tool seeds and reported the median \selfbleu score over three trials for each group of seeds.
-% The median \selfbleu over 3 trials of the random collection of the 50, 100 and 200 seeds is defined as the final \selfbleu scores.
-For the comparison, \selfbleu scores of \Cklst test cases are calculated in the same manner.
+called \selfbleu, that Zhu \etal
+introduced~\cite{zhu2018texygen}. \bleu evaluates the token-level
+similarity.
+% Regarding that \selfbleu takes each sentence as hypothesis and rest
+% in a collection of textual data as reference, we calculate \bleu
+% scores for every pairs of hypothesis and each reference sentence.
+The \selfbleu is defined as the average \bleu scores over all
+reference sentences.
+% Since the \bleu score ranges from 0 as the least similar inputs to 1
+% as the most similar inputs,
+A higher \selfbleu score indicates less diversity in the test
+suite. In the experiment, we collected 50, 100 and 200 randomly
+selected \tool seeds and reported the median \selfbleu score over
+three trials for each group of seeds.
+% The median \selfbleu over 3 trials of the random collection of the
+% 50, 100 and 200 seeds is defined as the final \selfbleu scores. For
+% the comparison, \selfbleu scores of \Cklst test cases are calculated
+% in the same manner.
 
 \paragraph*{Production rule coverage.} We propose a new metric to evaluate the syntactic diversity of the generated test suite.
-It is defined as the number of production rules used in a set of test sentences.
-In our experiments, we used the Berkeley Neural Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and collect all the production covered in a set of test sentences.
-We compared the \pdr between 50, 100 and 200 randomly selected \tool seeds and the \Cklst test cases.
-% collect the  of 50, 100 and 200 randomly selected \tool seeds and \Cklst test cases by the Berkeley Neural Parse~\cite{kitaev2018seedparser,kitaev2019seedparser}.
-Next, we traverse the parse trees and the \pdr score is calculated as the number of the production rules for the 50, 100 and 200 selected \tool seeds and \Cklst test cases.
+It is defined as the number of production rules used in a set of test
+sentences. In our experiments, we used the Berkeley Neural
+Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and
+collect all the production covered in a set of test sentences.  We
+compared the \pdr between 50, 100 and 200 randomly selected \tool
+seeds and the \Cklst test cases.
+% collect the of 50, 100 and 200 randomly selected \tool seeds and
+% \Cklst test cases by the Berkeley Neural
+% Parse~\cite{kitaev2018seedparser,kitaev2019seedparser}. Next, we
+% traverse the parse trees and the \pdr score is calculated as the
+% number of the production rules for the 50, 100 and 200 selected
+% \tool seeds and \Cklst test cases.
 
@@
 
-In addition,
-we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
-where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
-Because the matrix computation of intermediate states impacts NLP model decision-making, a test suite that covers a greater number of intermediate states can represent more NLP model decision-making, making it more diverse.
-Specifically, we used two coverage metrics by Ma et al.
-\cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
-It is worth noting that a test sample with a statistical distribution similar to the training data is rarely found in the corner case region.
-Thus, covering a larger corner case region indicates that the test suite is more likely to be buggy.
+In addition, we follow the approach presented by Ma et
+al. \cite{ma2018deepgauge}, where the authors measure the coverage of
+NLP model intermediate states as corner-case neurons.  Because the
+matrix computation of intermediate states impacts NLP model
+decision-making, a test suite that covers a greater number of
+intermediate states can represent more NLP model decision-making,
+making it more diverse.  Specifically, we used two coverage metrics by
+Ma et al. \cite{ma2018deepgauge}, \textit{boundary coverage}
+(BoundCov) and \textit{strong activation coverage} (SActCov), to
+evaluate the test suite diversity.  It is worth noting that a test
+sample with a statistical distribution similar to the training data is
+rarely found in the corner case region.  Thus, covering a larger
+corner case region indicates that the test suite is more likely to be
+buggy.
 
@@
 
-\noindent Equation \ref{eq:corner} defines the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
-Equation \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
+\noindent Equation \ref{eq:corner} defines the corner-case neuron of
+the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite,
+$N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the
+$n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$
+neurons' output bounds on the model training dataset.  Equation
+\ref{eq:corner} can be interpreted as the collection of neurons that
+emit outputs beyond the model's numerical boundary.
 
@@
 
-\noindent The definition of our coverage metrics is shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produces outputs exceeding the upper or lower bounds, and SActCov measures the coverage of neurons that creates outputs exceeding the lower bound.
-Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.
+\noindent The definition of our coverage metrics is shown in Equation
+\ref{eq:coverage}, where BoundCov measures the coverage of neurons
+that produces outputs exceeding the upper or lower bounds, and SActCov
+measures the coverage of neurons that creates outputs exceeding the
+lower bound.  Higher coverage indicates the test suite is better for
+triggering the corner-case neurons, thus better test suite diversity.
 
-% ($Cov(\mathcal{X})$ in \equref{eq:coverage}),
-% where $N$ is the total number blocks, $\mathbb I(\cdot)$ is the indicator function, and
-% $(B_i(x) > \tau_i))$ represents whether $i^{th}$ block is activated by input $x$~(the definition of $B_i$ and $\tau_i$ are the same with \equref{eq:new2} and \equref{eq:new3}).
-% Because AdNNs activate different blocks for decision making, then a higher block coverage indicates the test samples cover more decision behaviors.
+% ($Cov(\mathcal{X})$ in \equref{eq:coverage}), where $N$ is the total
+% number blocks, $\mathbb I(\cdot)$ is the indicator function, and
+% $(B_i(x) > \tau_i))$ represents whether $i^{th}$ block is activated
+% by input $x$~(the definition of $B_i$ and $\tau_i$ are the same with
+% \equref{eq:new2} and \equref{eq:new3}).  Because AdNNs activate
+% different blocks for decision making, then a higher block coverage
+% indicates the test samples cover more decision behaviors.
 
-To answer RQ1, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
-After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
+To answer RQ1, for each NLP model under test, we first feed its
+training dataset to compute each neuron's lower and upper
+bounds. After that, we select the same number of test cases from \tool
+and \Cklst as the test suite and compute the corresponding coverage
+metrics.
 
-% For each subject, we randomly select 100 seed samples from the test dataset as seed inputs. We then feed the same seed inputs into \tool and \texttt{ILFO} to generate test samples. 
-% Finally, we feed the generated test samples to AdNNs and measure block coverage.
-% We repeat this process 10 times and record the average coverage and the variance.
-% The results are shown in \tabref{tab:coverage} last two columns.
+% For each subject, we randomly select 100 seed samples from the test
+% dataset as seed inputs. We then feed the same seed inputs into \tool
+% and \texttt{ILFO} to generate test samples.  Finally, we feed the
+% generated test samples to AdNNs and measure block coverage.  We
+% repeat this process 10 times and record the average coverage and the
+% variance.  The results are shown in \tabref{tab:coverage} last two
+% columns.
 
@@
 
-\paragraph*{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
+\paragraph*{\textbf{RQ2 and RQ3}} \jl{need to do the manual study for the \hsd task also?} As described in Section \ref{sec:approach},
 \tool generates test cases in two steps: specification-based seed
@@
 % correct label. 
-To answer RQ2 and RQ3, we performed a manual study to
-measure the correctness of the sentiment labels and linguistic
-capabilities associated with the seed/expanded sentences, produced by
-\tool.
+To answer RQ2 and RQ3, we performed a manual study to measure the
+correctness of the sentiment labels and linguistic capabilities
+associated with the seed/expanded sentences, produced by \tool.
 
-In the manual study, we randomly sample 100 \tool seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set).
-For each sampled seed sentence, we randomly obtain one of its expanded sentences.
-This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
-We recruited three participants for this study; all of them are graduate students with no knowledge about this work. 
-2 of them were assigned one set of sentences and the third was assigned the other set.
-Each participant was asked to provide two scores for each sentence.
-\emph{(1) Relevancy score between sentence and its associated \lc}:
-this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete,
-ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment score of the sentence}: this score measures the sentiment level of the sentence . It
-is also discrete, ranging from 1 (``strongly
-negative'') to 5 (``strongly positive''). 
-We measure the following:
+In the manual study, we randomly sample 100 \tool seed sentences, each
+of which has at least one expanded sentence, and divide these seeds to
+two sets (i.e., 50 in each set). For each sampled seed sentence, we
+randomly obtain one of its expanded sentences.  This forms the two
+sets of sentences (200 sentences in total) we use for this study, each
+with 50 seeds and 50 corresponding expanded sentences.  We recruited
+three participants for this study; all of them are graduate students
+with no knowledge about this work.  2 of them were assigned one set of
+sentences and the third was assigned the other set.  Each participant
+was asked to provide two scores for each sentence.  \emph{(1)
+Relevancy score between sentence and its associated \lc}: this score
+measures the correctness of \tool linguistic capability
+categorization.  The scores are discrete, ranging from 1 (``strongly
+not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment
+score of the sentence}: this score measures the sentiment level of the
+sentence . It is also discrete, ranging from 1 (``strongly negative'')
+to 5 (``strongly positive'').  We measure the following:
 
@@
 
-Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants produce the same sentiment labels.
-High value of this metric indicates \tool generates test cases with correct labels.
-Equation~\ref{metric:lcrel} represents the average of the
-normalized relevancy score between a sentence and its associated
-\lc.
-The relevancy score is to evaluate the relevancy of the sentence to be used for testing model under test on the corresponding \lc.
-Higher average score means indicate the linguistic capability categorization by \tool is correct.
-We answer RQ2 and RQ3 using the metrics defined by
-Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
-respectively.
+Equation~\ref{metric:srel} represents the percentage of the test cases
+that \tool and the participants produce the same sentiment
+labels. High value of this metric indicates \tool generates test cases
+with correct labels. Equation~\ref{metric:lcrel} represents the
+average of the normalized relevancy score between a sentence and its
+associated \lc. The relevancy score is to evaluate the relevancy of
+the sentence to be used for testing model under test on the
+corresponding \lc. Higher average score means indicate the linguistic
+capability categorization by \tool is correct. We answer RQ2 and RQ3
+using the metrics defined by Equation~\ref{metric:srel} and
+Equation~\ref{metric:lcrel}, respectively.
 

### 2023-01-30 paper/fse23/tables/manual-study-numbers.tex
add table/plot

%% Automatically generated by pyutil.latex

\DefMacro{manual-study-sa-seed-num-sents}{78}
\DefMacro{manual-study-sa-seed-label-consistency}{0.85}
\DefMacro{manual-study-sa-seed-lc-relevancy}{0.89}
\DefMacro{manual-study-sa-exp-num-sents}{78}
\DefMacro{manual-study-sa-exp-label-consistency}{0.85}
\DefMacro{manual-study-sa-exp-lc-relevancy}{0.89}
\DefMacro{manual-study-hs-seed-num-sents}{100}
\DefMacro{manual-study-hs-seed-label-consistency}{0.79}
\DefMacro{manual-study-hs-seed-lc-relevancy}{0.88}
\DefMacro{manual-study-hs-exp-num-sents}{100}
\DefMacro{manual-study-hs-exp-label-consistency}{0.79}
\DefMacro{manual-study-hs-exp-lc-relevancy}{0.88}

### 2023-01-30 paper/fse23/tables/manual-study-table.tex
add table/plot

%% Automatically generated by pyutil.latex

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{\ManualStudyTableCaption}
\resizebox{0.47\textwidth}{!}{
\begin{tabular}{l|l|ccc}
\toprule
\tTask & \tSentType & \tNumTestCases & \tAvgLabelCons & \tAvgLCRel \\
\midrule
\multirow{2}{*}{SA} 
 & SEED & \UseMacro{manual-study-sa-seed-num-sents}
 & \UseMacro{manual-study-sa-seed-label-consistency}
 & \UseMacro{manual-study-sa-seed-lc-relevancy}\\
 & EXP & \UseMacro{manual-study-sa-exp-num-sents}
 & \UseMacro{manual-study-sa-exp-label-consistency}
 & \UseMacro{manual-study-sa-exp-lc-relevancy}\\
\hline
\multirow{2}{*}{HSD} 
 & SEED & \UseMacro{manual-study-hs-seed-num-sents}
 & \UseMacro{manual-study-hs-seed-label-consistency}
 & \UseMacro{manual-study-hs-seed-lc-relevancy}\\
 & EXP & \UseMacro{manual-study-hs-exp-num-sents}
 & \UseMacro{manual-study-hs-exp-label-consistency}
 & \UseMacro{manual-study-hs-exp-lc-relevancy}\\
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\ManualStudyTableVSpace}
\end{table}

### 2023-01-30 paper/fse23/tables/mtnlp-comp-numbers.tex
add table/plot

%% Automatically generated by pyutil.latex

\DefMacro{mtnlp-comp-sa-ours-selfbleu-num-mutate}{50}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-avg}{0.15}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-med}{0.15}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-std}{0.02}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-num-mutate}{32}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-avg}{0.93}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-med}{0.93}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-std}{0.0}
\DefMacro{mtnlp-comp-sa-ours-pdr-num-mutate}{50}
\DefMacro{mtnlp-comp-sa-ours-pdr-avg}{164.7}
\DefMacro{mtnlp-comp-sa-ours-pdr-med}{160.5}
\DefMacro{mtnlp-comp-sa-ours-pdr-std}{10.07}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-num-mutate}{32}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-avg}{129.0}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-med}{129.0}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-std}{0.0}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-num-mutate}{50}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-avg}{0.15}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-med}{0.15}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-std}{0.01}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-num-mutate}{40}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-avg}{0.93}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-med}{0.93}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-std}{0.0}
\DefMacro{mtnlp-comp-hs-ours-pdr-num-mutate}{50}
\DefMacro{mtnlp-comp-hs-ours-pdr-avg}{206.6}
\DefMacro{mtnlp-comp-hs-ours-pdr-med}{208.0}
\DefMacro{mtnlp-comp-hs-ours-pdr-std}{7.12}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-num-mutate}{40}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-avg}{131.0}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-med}{131.0}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-std}{0.0}

### 2023-01-30 paper/fse23/tables/mtnlp-comp-table.tex
add table/plot

%% Automatically generated by pyutil.latex

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{\MtnlpCompTableCaption}
\resizebox{0.47\textwidth}{!}{
\begin{tabular}{l|l|ccc}
\toprule
\tTask & \tApproach & \tNummut & \tSelfbleu & \tPdrcov \\
\midrule
\multirow{2}{*}{SA} 
 & S^{2}LCT & \UseMacro{mtnlp-comp-sa-ours-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-sa-ours-selfbleu-avg}\pm
\UseMacro{mtnlp-comp-sa-ours-selfbleu-std}
 & \UseMacro{mtnlp-comp-sa-ours-pdr-avg}\pm\UseMacro{mtnlp-comp-sa-ours-pdr-std}\\
 & MT-NLP & \UseMacro{mtnlp-comp-sa-mtnlp-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-sa-mtnlp-selfbleu-avg}\pm
\UseMacro{mtnlp-comp-sa-mtnlp-selfbleu-std}
 & \UseMacro{mtnlp-comp-sa-mtnlp-pdr-avg}\pm\UseMacro{mtnlp-comp-sa-mtnlp-pdr-std}\\
\hline
\multirow{2}{*}{HSD} 
 & S^{2}LCT & \UseMacro{mtnlp-comp-hs-ours-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-hs-ours-selfbleu-avg}\pm
\UseMacro{mtnlp-comp-hs-ours-selfbleu-std}
 & \UseMacro{mtnlp-comp-hs-ours-pdr-avg}\pm\UseMacro{mtnlp-comp-hs-ours-pdr-std}\\
 & MT-NLP & \UseMacro{mtnlp-comp-hs-mtnlp-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-hs-mtnlp-selfbleu-avg}\pm
\UseMacro{mtnlp-comp-hs-mtnlp-selfbleu-std}
 & \UseMacro{mtnlp-comp-hs-mtnlp-pdr-avg}\pm\UseMacro{mtnlp-comp-hs-mtnlp-pdr-std}\\
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\MtnlpCompTableVSpace}
\end{table*}

### 2023-03-16 paper/fse23/tables/adv-comp-numbers.tex
icse24

%% Automatically generated by pyutil.latex

\DefMacro{adv-comp-sa-model-under-test}{textattack/bert-base-uncased-SST-2}
\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
\DefMacro{adv-comp-sa-alzantot-num-samples}{20}
\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{0.373}
\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{0.373}
\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-med}{170}
\DefMacro{adv-comp-sa-alzantot-pdrcov-avg}{170.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
\DefMacro{adv-comp-sa-bert-attack-num-samples}{25}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-med}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-avg}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-med}{178}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-pso-num-adv}{25}
\DefMacro{adv-comp-sa-pso-num-samples}{25}
\DefMacro{adv-comp-sa-pso-selfbleu-med}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-avg}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-pso-pdrcov-med}{178}
\DefMacro{adv-comp-sa-pso-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-pso-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-ours-num-adv}{323}
\DefMacro{adv-comp-sa-ours-num-samples}{50}
\DefMacro{adv-comp-sa-ours-selfbleu-med}{0.437}
\DefMacro{adv-comp-sa-ours-selfbleu-avg}{0.435}
\DefMacro{adv-comp-sa-ours-selfbleu-std}{0.005}
\DefMacro{adv-comp-sa-ours-pdrcov-med}{264}
\DefMacro{adv-comp-sa-ours-pdrcov-avg}{262.0}
\DefMacro{adv-comp-sa-ours-pdrcov-std}{2.739}

### 2023-03-16 paper/fse23/tables/adv-comp-table.tex
icse24

%% Automatically generated by pyutil.latex

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{\AdvCompTableCaption}
\resizebox{0.47\textwidth}{!}{
\begin{tabular}{l|ccc}
\toprule
\tApproach & \tNummut & \tSelfbleu & \tPdrcov \\
\midrule
 \tool & \UseMacro{adv-comp-sa-ours-num-adv}
 & \UseMacro{adv-comp-sa-ours-selfbleu-avg}\pm\UseMacro{adv-comp-sa-ours-selfbleu-std}
 & \UseMacro{adv-comp-sa-ours-pdrcov-avg}\pm\UseMacro{adv-comp-sa-ours-pdrcov-std}\\
Alzantot & \UseMacro{adv-comp-sa-alzantot-num-adv}
 & \UseMacro{adv-comp-sa-alzantot-selfbleu-avg}\pm\UseMacro{adv-comp-sa-alzantot-selfbleu-std}
 & \UseMacro{adv-comp-sa-alzantot-pdrcov-avg}\pm\UseMacro{adv-comp-sa-alzantot-pdrcov-std}\\
BERT-Attack & \UseMacro{adv-comp-sa-bert-attack-num-adv}
 & \UseMacro{adv-comp-sa-bert-attack-selfbleu-avg}\pm\UseMacro{adv-comp-sa-bert-attack-selfbleu-std}
 & \UseMacro{adv-comp-sa-bert-attack-pdrcov-avg}\pm\UseMacro{adv-comp-sa-bert-attack-pdrcov-std}\\
PSO & \UseMacro{adv-comp-sa-pso-num-adv}
 & \UseMacro{adv-comp-sa-pso-selfbleu-avg}\pm\UseMacro{adv-comp-sa-pso-selfbleu-std}
 & \UseMacro{adv-comp-sa-pso-pdrcov-avg}\pm\UseMacro{adv-comp-sa-pso-pdrcov-std}\\
\bottomrule
\end{tabular}}
\end{center}
\end{small}
\vspace{\AdvCompTableVSpace}
\end{table*}

### 2023-03-16 paper/fse23/tables/manual-study-table.tex
icse24

@@
 \resizebox{0.47\textwidth}{!}{
-\begin{tabular}{l|l|ccc}
+\begin{tabular}{l|l|cccc}
 \toprule
-\tTask & \tSentType & \tNumTestCases & \tAvgLabelCons & \tAvgLCRel \\
+\tTask & \tSentType & \tNumTestCases & \tAvgLabelCons & \tAvgLCRel & \tAvgExpVal \\
 \midrule
@@
  & \UseMacro{manual-study-sa-seed-label-consistency}
- & \UseMacro{manual-study-sa-seed-lc-relevancy}\\
+ & \UseMacro{manual-study-sa-seed-lc-relevancy}
+ & \UseMacro{manual-study-sa-seed-validity}\\
  & EXP & \UseMacro{manual-study-sa-exp-num-sents}
  & \UseMacro{manual-study-sa-exp-label-consistency}
- & \UseMacro{manual-study-sa-exp-lc-relevancy}\\
+ & \UseMacro{manual-study-sa-exp-lc-relevancy}
+ & \UseMacro{manual-study-sa-exp-validity}\\
 \hline
@@
  & \UseMacro{manual-study-hs-seed-label-consistency}
- & \UseMacro{manual-study-hs-seed-lc-relevancy}\\
+ & \UseMacro{manual-study-hs-seed-lc-relevancy}
+ & \UseMacro{manual-study-hs-seed-validity}\\
  & EXP & \UseMacro{manual-study-hs-exp-num-sents}
  & \UseMacro{manual-study-hs-exp-label-consistency}
- & \UseMacro{manual-study-hs-exp-lc-relevancy}\\
+ & \UseMacro{manual-study-hs-exp-lc-relevancy}
+ & \UseMacro{manual-study-hs-exp-validity}\\
 \bottomrule

### 2023-03-16 paper/fse23/tables/mtnlp-comp-numbers.tex
icse24

@@
 
-\DefMacro{mtnlp-comp-sa-ours-selfbleu-num-mutate}{50}
-\DefMacro{mtnlp-comp-sa-ours-selfbleu-avg}{0.15}
-\DefMacro{mtnlp-comp-sa-ours-selfbleu-med}{0.15}
-\DefMacro{mtnlp-comp-sa-ours-selfbleu-std}{0.02}
-\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-num-mutate}{32}
-\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-avg}{0.93}
-\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-med}{0.93}
-\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-std}{0.0}
-\DefMacro{mtnlp-comp-sa-ours-pdr-num-mutate}{50}
-\DefMacro{mtnlp-comp-sa-ours-pdr-avg}{164.7}
-\DefMacro{mtnlp-comp-sa-ours-pdr-med}{160.5}
-\DefMacro{mtnlp-comp-sa-ours-pdr-std}{10.07}
-\DefMacro{mtnlp-comp-sa-mtnlp-pdr-num-mutate}{32}
-\DefMacro{mtnlp-comp-sa-mtnlp-pdr-avg}{129.0}
-\DefMacro{mtnlp-comp-sa-mtnlp-pdr-med}{129.0}
-\DefMacro{mtnlp-comp-sa-mtnlp-pdr-std}{0.0}
-\DefMacro{mtnlp-comp-hs-ours-selfbleu-num-mutate}{50}
-\DefMacro{mtnlp-comp-hs-ours-selfbleu-avg}{0.15}
-\DefMacro{mtnlp-comp-hs-ours-selfbleu-med}{0.15}
-\DefMacro{mtnlp-comp-hs-ours-selfbleu-std}{0.01}
-\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-num-mutate}{40}
-\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-avg}{0.93}
-\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-med}{0.93}
-\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-std}{0.0}
-\DefMacro{mtnlp-comp-hs-ours-pdr-num-mutate}{50}
-\DefMacro{mtnlp-comp-hs-ours-pdr-avg}{206.6}
-\DefMacro{mtnlp-comp-hs-ours-pdr-med}{208.0}
-\DefMacro{mtnlp-comp-hs-ours-pdr-std}{7.12}
-\DefMacro{mtnlp-comp-hs-mtnlp-pdr-num-mutate}{40}
-\DefMacro{mtnlp-comp-hs-mtnlp-pdr-avg}{131.0}
-\DefMacro{mtnlp-comp-hs-mtnlp-pdr-med}{131.0}
-\DefMacro{mtnlp-comp-hs-mtnlp-pdr-std}{0.0}
+\DefMacro{adv-comp-sa-model-under-test}{textattack/bert-base-uncased-SST-2}
+\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
+\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
+\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{0.373}
+\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{0.373}
+\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{0.0}
+\DefMacro{adv-comp-sa-alzantot-pdrcov-med}{170}
+\DefMacro{adv-comp-sa-alzantot-pdrcov-avg}{170.0}
+\DefMacro{adv-comp-sa-alzantot-pdrcov-std}{0.0}
+\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
+\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
+\DefMacro{adv-comp-sa-bert-attack-selfbleu-med}{0.438}
+\DefMacro{adv-comp-sa-bert-attack-selfbleu-avg}{0.438}
+\DefMacro{adv-comp-sa-bert-attack-selfbleu-std}{0.0}
+\DefMacro{adv-comp-sa-bert-attack-pdrcov-med}{178}
+\DefMacro{adv-comp-sa-bert-attack-pdrcov-avg}{178.0}
+\DefMacro{adv-comp-sa-bert-attack-pdrcov-std}{0.0}
+\DefMacro{adv-comp-sa-pso-num-adv}{25}
+\DefMacro{adv-comp-sa-pso-num-adv}{25}
+\DefMacro{adv-comp-sa-pso-selfbleu-med}{0.411}
+\DefMacro{adv-comp-sa-pso-selfbleu-avg}{0.411}
+\DefMacro{adv-comp-sa-pso-selfbleu-std}{0.0}
+\DefMacro{adv-comp-sa-pso-pdrcov-med}{178}
+\DefMacro{adv-comp-sa-pso-pdrcov-avg}{178.0}
+\DefMacro{adv-comp-sa-pso-pdrcov-std}{0.0}
+\DefMacro{adv-comp-sa-ours-num-adv}{323}
+\DefMacro{adv-comp-sa-ours_exp-num-adv}{50}
+\DefMacro{adv-comp-sa-ours-selfbleu-med}{0.437}
+\DefMacro{adv-comp-sa-ours-selfbleu-avg}{0.435}
+\DefMacro{adv-comp-sa-ours-selfbleu-std}{0.005}
+\DefMacro{adv-comp-sa-ours-pdrcov-med}{264}
+\DefMacro{adv-comp-sa-ours-pdrcov-avg}{262.0}
+\DefMacro{adv-comp-sa-ours-pdrcov-std}{2.739}

### 2023-03-16 paper/fse23/tables/test-results-hs-all-numbers.tex
icse24

--- 2023-01-10 paper/fse23/tables/test-results-hs-all-numbers.tex
@@
 \DefMacro{test-results-hs-lc2-num-seeds}{140}
-\DefMacro{test-results-hs-lc2-num-exps}{3,124}
-\DefMacro{test-results-hs-model0-lc2-num-all-fail}{3,220}
-\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{98.57}
-\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{98.66}
-\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{98.65}
-\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{18}
+\DefMacro{test-results-hs-lc2-num-exps}{1,791}
+\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc2-num-all-fail}{1,419}
+\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{72.14}
+\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{73.59}
+\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{73.49}
+\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{48}
+\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{101}
+\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{72.14}
+\DefMacro{test-results-hs-lc19}{Denouncements of hate that make direct reference to it}
+\DefMacro{test-results-hs-lc19-num-seeds}{34,212}
+\DefMacro{test-results-hs-lc19-num-exps}{209,389}
+\DefMacro{test-results-hs-bl-lc19-num-tcs}{141}
+\DefMacro{test-results-hs-model0-lc19-num-all-fail}{33,397}
+\DefMacro{test-results-hs-model0-lc19-num-seed-failrate}{13.06}
+\DefMacro{test-results-hs-model0-lc19-num-exp-failrate}{13.82}
+\DefMacro{test-results-hs-model0-lc19-num-all-failrate}{13.71}
+\DefMacro{test-results-hs-model0-lc19-num-pass-to-fail}{1,888}
+\DefMacro{test-results-hs-bl-model0-lc19-num-fail}{4}
+\DefMacro{test-results-hs-bl-model0-lc19-num-failrate}{2.84}
 \DefMacro{test-results-hs-lc18}{Denouncements of hate that quote it}
 \DefMacro{test-results-hs-lc18-num-seeds}{45,616}
-\DefMacro{test-results-hs-lc18-num-exps}{300,704}
-\DefMacro{test-results-hs-model0-lc18-num-all-fail}{48,804}
-\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{13.78}
-\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{14.14}
-\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{14.09}
-\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{4,831}
+\DefMacro{test-results-hs-lc18-num-exps}{258,317}
+\DefMacro{test-results-hs-bl-lc18-num-tcs}{173}
+\DefMacro{test-results-hs-model0-lc18-num-all-fail}{38,262}
+\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{11.96}
+\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{12.70}
+\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{12.59}
+\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{2,049}
+\DefMacro{test-results-hs-bl-model0-lc18-num-fail}{17}
+\DefMacro{test-results-hs-bl-model0-lc18-num-failrate}{9.83}
 \DefMacro{test-results-hs-lc1}{Description using very negative attributes (explicit)}
 \DefMacro{test-results-hs-lc1-num-seeds}{140}
-\DefMacro{test-results-hs-lc1-num-exps}{2,959}
-\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,067}
-\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{98.57}
-\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{98.99}
-\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{98.97}
-\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{23}
+\DefMacro{test-results-hs-lc1-num-exps}{2,433}
+\DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc1-num-all-fail}{1,935}
+\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{73.57}
+\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{75.30}
+\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{75.20}
+\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{86}
+\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{103}
+\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{73.57}
 \DefMacro{test-results-hs-lc4}{Direct threat}
 \DefMacro{test-results-hs-lc4-num-seeds}{133}
-\DefMacro{test-results-hs-lc4-num-exps}{2,689}
-\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,770}
-\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{97.74}
-\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{98.18}
-\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{98.16}
-\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{9}
+\DefMacro{test-results-hs-lc4-num-exps}{698}
+\DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc4-num-all-fail}{654}
+\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{78.95}
+\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{78.65}
+\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{78.70}
+\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{14}
+\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{104}
+\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{78.20}
 \DefMacro{test-results-hs-lc0}{Expression of strong negative emotions (explicit)}
@@
 \DefMacro{test-results-hs-lc0-num-exps}{799}
-\DefMacro{test-results-hs-model0-lc0-num-all-fail}{920}
-\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{97.14}
-\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{98.12}
-\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{97.98}
-\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{22}
+\DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc0-num-all-fail}{772}
+\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{77.14}
+\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{83.10}
+\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{82.22}
+\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{27}
+\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{108}
+\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{77.14}
 \DefMacro{test-results-hs-lc10}{Hate expressed through reference in subsequent clauses}
-\DefMacro{test-results-hs-lc10-num-seeds}{11,968}
-\DefMacro{test-results-hs-lc10-num-exps}{44,890}
-\DefMacro{test-results-hs-model0-lc10-num-all-fail}{49,929}
-\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{60.60}
-\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{95.07}
-\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{87.81}
-\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,169}
+\DefMacro{test-results-hs-lc10-num-seeds}{13,442}
+\DefMacro{test-results-hs-lc10-num-exps}{41,806}
+\DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc10-num-all-fail}{36,054}
+\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{42.47}
+\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{72.59}
+\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{65.26}
+\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{751}
+\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{108}
+\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{77.14}
 \DefMacro{test-results-hs-lc11}{Hate expressed through reference in subsequent sentences}
 \DefMacro{test-results-hs-lc11-num-seeds}{11,968}
-\DefMacro{test-results-hs-lc11-num-exps}{42,840}
-\DefMacro{test-results-hs-model0-lc11-num-all-fail}{47,294}
-\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{58.92}
-\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{93.94}
-\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{86.29}
-\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,726}
+\DefMacro{test-results-hs-lc11-num-exps}{40,942}
+\DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc11-num-all-fail}{34,859}
+\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{45.96}
+\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{71.71}
+\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{65.88}
+\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{764}
+\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{101}
+\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{75.94}
 \DefMacro{test-results-hs-lc12}{Hate expressed using negated positive statement}
 \DefMacro{test-results-hs-lc12-num-seeds}{23,379}
-\DefMacro{test-results-hs-lc12-num-exps}{126,742}
-\DefMacro{test-results-hs-model0-lc12-num-all-fail}{145,761}
-\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{97.03}
-\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{97.11}
-\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{2,290}
+\DefMacro{test-results-hs-lc12-num-exps}{105,280}
+\DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc12-num-all-fail}{114,827}
+\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{89.68}
+\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{89.15}
+\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{89.25}
+\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{954}
+\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{109}
+\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{77.86}
 \DefMacro{test-results-hs-lc8}{Hate expressed using profanity}
 \DefMacro{test-results-hs-lc8-num-seeds}{1,842}
-\DefMacro{test-results-hs-lc8-num-exps}{49,743}
-\DefMacro{test-results-hs-model0-lc8-num-all-fail}{50,158}
-\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{97.34}
-\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{97.23}
-\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{97.23}
-\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{164}
+\DefMacro{test-results-hs-lc8-num-exps}{10,755}
+\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc8-num-all-fail}{9,874}
+\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{78.66}
+\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{78.34}
+\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{78.38}
+\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{114}
+\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{98}
+\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{70.00}
 \DefMacro{test-results-hs-lc6}{Hate expressed using slur}
 \DefMacro{test-results-hs-lc6-num-seeds}{805}
-\DefMacro{test-results-hs-lc6-num-exps}{17,318}
-\DefMacro{test-results-hs-model0-lc6-num-all-fail}{17,597}
-\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{97.14}
-\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{97.10}
-\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{70}
+\DefMacro{test-results-hs-lc6-num-exps}{3,923}
+\DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
+\DefMacro{test-results-hs-model0-lc6-num-all-fail}{1,214}
+\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{23.60}
+\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{26.10}
+\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{25.68}
+\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{84}
+\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{108}
+\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{75.00}
 \DefMacro{test-results-hs-lc15}{Hate phrased as a opinion}
 \DefMacro{test-results-hs-lc15-num-seeds}{22,808}
-\DefMacro{test-results-hs-lc15-num-exps}{160,927}
-\DefMacro{test-results-hs-model0-lc15-num-all-fail}{178,058}
-\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{97.25}
-\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{96.86}
-\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{96.91}
-\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,078}
+\DefMacro{test-results-hs-lc15-num-exps}{141,890}
+\DefMacro{test-results-hs-bl-lc15-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc15-num-all-fail}{135,520}
+\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{82.88}
+\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{82.19}
+\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{82.28}
+\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{1,713}
+\DefMacro{test-results-hs-bl-model0-lc15-num-fail}{100}
+\DefMacro{test-results-hs-bl-model0-lc15-num-failrate}{75.19}
 \DefMacro{test-results-hs-lc14}{Hate phrased as a question}
 \DefMacro{test-results-hs-lc14-num-seeds}{22,808}
-\DefMacro{test-results-hs-lc14-num-exps}{185,267}
-\DefMacro{test-results-hs-model0-lc14-num-all-fail}{202,023}
-\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{97.37}
-\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{97.06}
-\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{97.09}
-\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{2,956}
+\DefMacro{test-results-hs-lc14-num-exps}{127,800}
+\DefMacro{test-results-hs-bl-lc14-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc14-num-all-fail}{127,991}
+\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{85.52}
+\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{84.89}
+\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{84.98}
+\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{1,357}
+\DefMacro{test-results-hs-bl-model0-lc14-num-fail}{107}
+\DefMacro{test-results-hs-bl-model0-lc14-num-failrate}{76.43}
 \DefMacro{test-results-hs-lc3}{Implicit derogation}
 \DefMacro{test-results-hs-lc3-num-seeds}{140}
-\DefMacro{test-results-hs-lc3-num-exps}{5,664}
-\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,730}
-\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{97.86}
-\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{98.75}
-\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{98.73}
-\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{30}
+\DefMacro{test-results-hs-lc3-num-exps}{2,674}
+\DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc3-num-all-fail}{2,385}
+\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{83.57}
+\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{84.82}
+\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{84.75}
+\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{44}
+\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{115}
+\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{82.14}
 \DefMacro{test-results-hs-lc16}{Neutral statements using protected group identifiers}
@@
 \DefMacro{test-results-hs-lc16-num-exps}{9}
-\DefMacro{test-results-hs-model0-lc16-num-all-fail}{1}
-\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{20.00}
-\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{7.14}
+\DefMacro{test-results-hs-bl-lc16-num-tcs}{126}
+\DefMacro{test-results-hs-model0-lc16-num-all-fail}{12}
+\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{60.00}
+\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{100.00}
+\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{85.71}
 \DefMacro{test-results-hs-model0-lc16-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model0-lc16-num-fail}{9}
+\DefMacro{test-results-hs-bl-model0-lc16-num-failrate}{7.14}
 \DefMacro{test-results-hs-lc9}{Non-Hateful use of profanity}
 \DefMacro{test-results-hs-lc9-num-seeds}{701}
-\DefMacro{test-results-hs-lc9-num-exps}{15,761}
-\DefMacro{test-results-hs-model0-lc9-num-all-fail}{11,939}
-\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{71.04}
-\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{72.59}
-\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{72.52}
-\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{75}
+\DefMacro{test-results-hs-lc9-num-exps}{3,360}
+\DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
+\DefMacro{test-results-hs-model0-lc9-num-all-fail}{548}
+\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{11.41}
+\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{13.93}
+\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{13.49}
+\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{20}
+\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{1}
+\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{1.00}
 \DefMacro{test-results-hs-lc13}{Non-hate expressed using negated hateful statement}
 \DefMacro{test-results-hs-lc13-num-seeds}{34,212}
-\DefMacro{test-results-hs-lc13-num-exps}{243,739}
-\DefMacro{test-results-hs-model0-lc13-num-all-fail}{77,191}
-\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{26.90}
-\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{27.89}
-\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{27.77}
-\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{5,222}
+\DefMacro{test-results-hs-lc13-num-exps}{209,980}
+\DefMacro{test-results-hs-bl-lc13-num-tcs}{133}
+\DefMacro{test-results-hs-model0-lc13-num-all-fail}{42,530}
+\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{16.82}
+\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{17.51}
+\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{17.42}
+\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{2,184}
+\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{13}
+\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{9.77}
 \DefMacro{test-results-hs-lc7}{Non-hateful use of slur}
 \DefMacro{test-results-hs-lc7-num-seeds}{395}
-\DefMacro{test-results-hs-lc7-num-exps}{7,881}
-\DefMacro{test-results-hs-model0-lc7-num-all-fail}{2,739}
-\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{30.89}
-\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{33.21}
-\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{33.10}
-\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{44}
+\DefMacro{test-results-hs-lc7-num-exps}{1,667}
+\DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
+\DefMacro{test-results-hs-model0-lc7-num-all-fail}{1,263}
+\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{63.29}
+\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{60.77}
+\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{61.25}
+\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{10}
+\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{18}
+\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{16.22}
 \DefMacro{test-results-hs-lc17}{Positive statements using protected group identifiers}
@@
 \DefMacro{test-results-hs-lc17-num-exps}{182}
-\DefMacro{test-results-hs-model0-lc17-num-all-fail}{14}
-\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{4.88}
-\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{6.59}
-\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{6.28}
-\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{1}
+\DefMacro{test-results-hs-bl-lc17-num-tcs}{189}
+\DefMacro{test-results-hs-model0-lc17-num-all-fail}{84}
+\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{46.34}
+\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{35.71}
+\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{37.67}
+\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{7}
+\DefMacro{test-results-hs-bl-model0-lc17-num-fail}{23}
+\DefMacro{test-results-hs-bl-model0-lc17-num-failrate}{12.17}
 \DefMacro{test-results-hs-lc5}{Threat as normative statement}
 \DefMacro{test-results-hs-lc5-num-seeds}{140}
-\DefMacro{test-results-hs-lc5-num-exps}{4,163}
-\DefMacro{test-results-hs-model0-lc5-num-all-fail}{4,261}
-\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{99.29}
-\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{99.02}
-\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{99.02}
-\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{1}
-\DefMacro{test-results-hs-model1-lc2-num-all-fail}{87}
-\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{2.78}
-\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{2.67}
-\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{31}
-\DefMacro{test-results-hs-model1-lc18-num-all-fail}{346,320}
-\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc1-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc4-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc0-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc10-num-all-fail}{5,984}
-\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.00}
-\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{10.52}
-\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc11-num-all-fail}{5,984}
-\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{50.00}
-\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{10.92}
-\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc12-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc8-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc6-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc15-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc14-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc3-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc16-num-all-fail}{14}
-\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{100.00}
+\DefMacro{test-results-hs-lc5-num-exps}{992}
+\DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
+\DefMacro{test-results-hs-model0-lc5-num-all-fail}{804}
+\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{70.71}
+\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{71.07}
+\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{71.02}
+\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{13}
+\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{99}
+\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{70.71}
+\DefMacro{test-results-hs-model1-lc2-num-all-fail}{897}
+\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{42.14}
+\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{46.79}
+\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{46.45}
+\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{157}
+\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{59}
+\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{42.14}
+\DefMacro{test-results-hs-model1-lc19-num-all-fail}{146,576}
+\DefMacro{test-results-hs-model1-lc19-num-seed-failrate}{60.74}
+\DefMacro{test-results-hs-model1-lc19-num-exp-failrate}{60.08}
+\DefMacro{test-results-hs-model1-lc19-num-all-failrate}{60.17}
+\DefMacro{test-results-hs-model1-lc19-num-pass-to-fail}{3,362}
+\DefMacro{test-results-hs-bl-model1-lc19-num-fail}{7}
+\DefMacro{test-results-hs-bl-model1-lc19-num-failrate}{4.96}
+\DefMacro{test-results-hs-model1-lc18-num-all-fail}{150,815}
+\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{48.34}
+\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{49.85}
+\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{49.62}
+\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{4,861}
+\DefMacro{test-results-hs-bl-model1-lc18-num-fail}{5}
+\DefMacro{test-results-hs-bl-model1-lc18-num-failrate}{2.89}
+\DefMacro{test-results-hs-model1-lc1-num-all-fail}{1,230}
+\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{46.43}
+\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{47.88}
+\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{47.80}
+\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{410}
+\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{67}
+\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{47.86}
+\DefMacro{test-results-hs-model1-lc4-num-all-fail}{681}
+\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{84.21}
+\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{81.52}
+\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{81.95}
+\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{26}
+\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{110}
+\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{82.71}
+\DefMacro{test-results-hs-model1-lc0-num-all-fail}{753}
+\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{77.86}
+\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{80.60}
+\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{80.19}
+\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{29}
+\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{109}
+\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{77.86}
+\DefMacro{test-results-hs-model1-lc10-num-all-fail}{28,848}
+\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.23}
+\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{52.85}
+\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{52.22}
+\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{762}
+\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{93}
+\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{66.43}
+\DefMacro{test-results-hs-model1-lc11-num-all-fail}{28,308}
+\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{49.72}
+\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{54.61}
+\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{53.50}
+\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{745}
+\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{69}
+\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{51.88}
+\DefMacro{test-results-hs-model1-lc12-num-all-fail}{90,337}
+\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{66.01}
+\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{71.15}
+\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{70.21}
+\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{1,913}
+\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{116}
+\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{82.86}
+\DefMacro{test-results-hs-model1-lc8-num-all-fail}{2,702}
+\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{18.46}
+\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{21.96}
+\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{21.45}
+\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{151}
+\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{93}
+\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{66.43}
+\DefMacro{test-results-hs-model1-lc6-num-all-fail}{395}
+\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{5.71}
+\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{8.90}
+\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{8.35}
+\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{90}
+\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{56}
+\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{38.89}
+\DefMacro{test-results-hs-model1-lc15-num-all-fail}{60,205}
+\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{35.09}
+\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{36.79}
+\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{36.55}
+\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{2,469}
+\DefMacro{test-results-hs-bl-model1-lc15-num-fail}{109}
+\DefMacro{test-results-hs-bl-model1-lc15-num-failrate}{81.95}
+\DefMacro{test-results-hs-model1-lc14-num-all-fail}{58,770}
+\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{37.10}
+\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{39.36}
+\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{39.02}
+\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{2,123}
+\DefMacro{test-results-hs-bl-model1-lc14-num-fail}{123}
+\DefMacro{test-results-hs-bl-model1-lc14-num-failrate}{87.86}
+\DefMacro{test-results-hs-model1-lc3-num-all-fail}{2,493}
+\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{85.00}
+\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{88.78}
+\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{88.59}
+\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{59}
+\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{119}
+\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{85.00}
+\DefMacro{test-results-hs-model1-lc16-num-all-fail}{1}
+\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{20.00}
+\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{0.00}
+\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{7.14}
 \DefMacro{test-results-hs-model1-lc16-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc9-num-all-fail}{16,462}
-\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc13-num-all-fail}{277,951}
-\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc7-num-all-fail}{8,276}
-\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc17-num-all-fail}{223}
-\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{100.00}
-\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{0}
-\DefMacro{test-results-hs-model1-lc5-num-all-fail}{0}
-\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{0.00}
-\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc16-num-fail}{0}
+\DefMacro{test-results-hs-bl-model1-lc16-num-failrate}{0.00}
+\DefMacro{test-results-hs-model1-lc9-num-all-fail}{1,627}
+\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{49.64}
+\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{38.07}
+\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{40.06}
+\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{74}
+\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{1}
+\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{1.00}
+\DefMacro{test-results-hs-model1-lc13-num-all-fail}{162,094}
+\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{67.53}
+\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{66.19}
+\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{66.38}
+\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{3,170}
+\DefMacro{test-results-hs-bl-model1-lc13-num-fail}{26}
+\DefMacro{test-results-hs-bl-model1-lc13-num-failrate}{19.55}
+\DefMacro{test-results-hs-model1-lc7-num-all-fail}{1,483}
+\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{78.73}
+\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{70.31}
+\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{71.92}
+\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{47}
+\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{68}
+\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{61.26}
+\DefMacro{test-results-hs-model1-lc17-num-all-fail}{46}
+\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{34.15}
+\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{17.58}
+\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{20.63}
+\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{1}
+\DefMacro{test-results-hs-bl-model1-lc17-num-fail}{16}
+\DefMacro{test-results-hs-bl-model1-lc17-num-failrate}{8.47}
+\DefMacro{test-results-hs-model1-lc5-num-all-fail}{786}
+\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{65.00}
+\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{70.06}
+\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{69.43}
+\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{33}
+\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{91}
+\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{65.00}

### 2023-03-16 paper/fse23/tables/test-results-hs-table.tex
icse24

@@
 \midrule
-\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc0-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc1-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc2-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc3-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc4-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc5-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}
+\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc6}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc6-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}
+\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc7}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc7-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}
+\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc8}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc8-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}
+\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc9}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc9-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}
+\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc10}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc10-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}
+\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc11}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc11-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}
+\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc12}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc12-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc13}}}
+\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc13}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc13-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-lc14}}}
+\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc14}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc14-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-lc15}}}
+\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc15}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc15-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-lc16}}}
+\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc16}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc16-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-lc17}}}
+\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc17}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc17-num-tcs}}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-lc18}}}
+\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc18}}}
  & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc18-num-tcs}}
@@
 \hline
+\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc19}}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc19-num-tcs}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc19-num-seeds}}
+ & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc19-num-exps}}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc19-num-fail}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc19-num-failrate}
+ & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-pass-to-fail}\\
+ & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc19-num-fail}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc19-num-failrate}
+ & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-pass-to-fail}\\
+\hline
 \bottomrule

### 2023-03-16 paper/icse24/CM/coverage.tex
icse24

--- 2022-06-07 paper/ase22/CM/coverage.tex
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/coverage.pdf}
-    \vspace{-4mm}
-    \caption{Coverage results of \tool and \Cklst test cases.}
+    \includegraphics[width=0.5\textwidth]{figs/nlp_coverage.pdf}
+    \vspace{-6mm}
+    \caption{Coverage results of \tool and \Cklst.}
     \label{fig:coverage}
@@
 
-Next, Figure \ref{fig:coverage} shows the coverage results of \tool and \Cklst test cases.
+\MyPara{Neuron Coverage} 
+Figure \ref{fig:coverage} shows the coverage results of \tool and \Cklst test cases.
 The red line represents \tool coverage and the black line represents \Cklst coverage.
-Each column in Figure \ref{fig:coverage} represents the results for one NLP model.
+Each column in Figure \ref{fig:coverage} represents the results for one \sa model.
 The first row is the \textit{BoundCov} results and the second row is the \textit{SActCov} results.
-
-We made three observations.
+We made three observations from the results.
 First, for \emph{all} experimental settings (i.e., NLP model and coverage metric), \tool achieves higher coverage than \Cklst.
@@
 This result confirms that \tool can generate more diverse test cases to complement the holdout dataset for testing NLP models.
-
 Second, as the number of test cases increases, the test suite can achieve better coverage.
@@
 However, generating a more extensive test suite is not easy, particularly  for \Cklst, which is a manually template-based approach.
-
 Third, for each NLP model, there is no fixed relationship between \textit{BoundCov} and \textit{SActCov}.

### 2023-03-16 paper/icse24/abstract.tex
icse24

\begin{abstract}

\Nlp (NLP) has gained widespread adoption in the development 
of diverse real-world applications. However, the black-box nature of the backend neural networks in NLP applications poses a challenge when evaluating their performance, let alone ensuring it. 
Recent research has proposed testing techniques to enhance the trustworthiness of NLP-based applications. 
However, existing works either generate invalid test cases (\ie those with incorrect grammar) or rely on manually designed test cases, which may limit their diversity.
To address this limitation, we propose \tool, an automated testing technique for validating NLP applications based on their \lcs. 
\tool first transforms test cases from existing real-world datasets into seed inputs  that belong to individual \lcs. \tool then generates a sufficient number of test cases by expanding syntax of the seed inputs based on their context-free grammar (CFG). 
In the syntax expansion process, \tool validates that the expanded test cases maintain the same semantic and capability as the seed inputs, thereby automatically  constructing a test oracle and \lc for the expanded test cases.
We evaluate \tool on two widely adopted NLP tasks, \sa and \hsd, to determine its  performance in terms of diversity, effectiveness, and consistency.
The results showed that \tool generates test cases that are at least 88\% more diverse than those produced by \sota techniques, as measured by \selfbleu and \pdr metrics. % two neuron coverage metrics.
Additionally, \tool was found to produce a larger number of NLP model failures.
% \sw{I'm not sure what 7 and 13 were referring to.}
% over 7 \lcs for \sa and 14 \lcs for \hsd.
% Our evaluation also revealed that \tool facilitates the identification of critical failures and the sources of these failures within NLP models. 
% \sw{Double check numbers and update evaluation results when finalized.}

\end{abstract}

### 2023-03-16 paper/icse24/abstract_old.tex
icse24

--- 2022-09-02 paper/icse23/abstract.tex
@@
 \begin{abstract}
-  \Nlp has been widely used for developing a variety of text analytic applications with high reliability.
-For any NLP-based applications to be trustworthy, assessment through measuring the accuracy of the holdout datasets is needed.
-Recent research introduced methods that assess an NLP model on a set of linguistic capabilities.
-  However, we observe that state-of-the-art methods rely on manually created test cases, which may be limited in terms of scalability and diversity.
+
+\Nlp has been widely used for developing a variety of text analytic applications. 
+For NLP-based applications to be trustworthy, %assessment through measuring the accuracy of the holdout datasets is needed. 
+recent research introduced methods that assess an NLP model on a set of linguistic capabilities.
+However, state-of-the-art methods rely on manually created test cases, which may be limited in terms of scalability and diversity.
 %\Nlp (NLP) technique has become one of the core techniques fordeveloping text  analytic applications.  These applications need to achieve high reliability to be useful in practice.  
@@
 However, current state-of-the-art methodologies rely on manuallycreated test cases which limits the scale of the testing dataset.
-  In this work, we introduce \tool,
-  an automated linguistic capability-based testing technique.
-Given a set of linguistic capabilities that assess an NLP model, \tool first searches for suitable seed inputs from existing datasets, and then generates a sufficient number
-  of new test inputs by expanding the seed inputs based on their \cfg (CFG). 
+In this work, we introduce \tool, an automated linguistic capability-based testing technique. 
+Given a set of linguistic capabilities that assess an NLP model, 
+\tool first searches for suitable seed inputs from existing datasets, 
+and then generates a sufficient number of new test inputs by expanding the seed inputs based on their \cfg (CFG).
 \tool guarantees the correctness of the generated test input labels and that these test inputs belong to the correct linguistic capabilities. 
-  Evaluation results show that \tool can generate test cases that are 100\%  more diverse than state-of-the-art 
-   while ensuring the correctness of labels and linguistic capabilities of the test inputs. 
+We evaluate \tool generated test cases on \lcs of \sa and \hsd tasks.
+Evaluation results show that \tool can generate test cases that are 100\% more diverse than \sota.
+In addition, while ensuring the correctness of labels and \lcs of the test inputs,
+\tool produces larger number of NLP model failures than \sota over 7 and 13 \lcs on all NLP models under test for \sa and \hsd tasks respectively. 
 %   \Cong{You mention comprehensive and scalability before, so better give improvement numbers in terms of these metrics.}

### 2023-03-16 paper/icse24/approach.tex
icse24

\section{Specification- and Syntax-based Linguistic Capability Testing}
\label{sec:approach}

\begin{figure}[thb]
  \centering
  \includegraphics[width=0.49\textwidth]{figs/overview.pdf}
  \vspace{-6mm}
  \caption{\OverviewFigCaption}
\end{figure}

  We design and implement a new NLP model testing framework, \tool, which automatically generates test cases with oracles for defined linguistic capabilities to assess the quality of NLP models.

Figure~\ref{fig:overview} depicts an overview of \tool, which
consists of two phases.  The \emph{specification-based seed generation} phase generates the initial set of seed test cases based on generation rules.
Generation rule is consisted of operations and \phs.
\tool provides two built-in operations \texttt{Combine} and \texttt{Replace} and two types of \phs, search-based and enumerative \phs (Section \ref{sec:seed-gen}). 
% The seed generation results in seed test cases that are most likely to conform to a specific \lc and be labelled correctly.
To increase the diversity of test cases generated by \tool, we utilize a \emph{syntax-based sentence expansion} phase (Section \ref{sec:sent-exp}). This phase begins by performing a syntax analysis to identify \pos (PoS) tags that can be added to the seed test cases, by comparing the PoS parse trees of the seed test cases with a large reference corpus of sentences. The identified tags are then inserted into the seed test cases as a \emph{mask}. A masked language model, such as BERT \cite{devlin2019bert}, is then used to suggest words that can fill in the mask. Finally, the resulting sentence is checked to ensure it is consistent with the seed's label and \lc. The generated test suite includes both the original seed test cases and the expanded test cases. This approach enables \tool to cover a wider range of syntactic structures, enhancing its effectiveness in evaluating NLP models.
\vspace{\AlgCompTableVSpace}

% specification which additionally defines the rules for expansion
% (e.g. the expanded word should be \neu).
% Last, because some validated \sents may include
% unacceptable suggested words given the context, we use a heuristic (i.e., the
% confidence score from the NLP recommendation model) to select the more
% realistic context-aware expanded \sents into \tool{}'s test suite.

% We now describe each phase of \tool in detail.

\subsection{Specification-based Seed Generation}
\label{sec:seed-gen}
%\sw{@Jaeseong: I made many changes to this subsection. You need to read through and make sure what I wrote is accurate. @Wei Yang: I think we have been using the terms "seed generation", "\ph", "predicate", and "function" in inconsistent and confusing ways. I think you should take a pass over this subsection to make the presentation accurate.}

%\sw{This may be the general structure we want to discuss our approach in this subsection? (1) We have two seed generation functions: combine and replace. (Describe their high-level functionality.) (2) (Now we describe combine in detail.) Combine has four kinds of parameters, prefix, postfix, infix, and search. (3) Search is a set of sentences from the real-world dataset resulted by applying the predicates: we define two kinds of predicates: implicit and explicit. (4) Prefix, postfix, and infix parameters are sets of user-defined clauses, defined by their relative positions to the search parameter. (5) (Now we describe the replace function). We  implemented negations as an instance of replace function.}

\tool generates the
initial set of seed test cases based on generation rules.
Each generation rule is consisted of operations and \phs.
\tool provides two built-in operations \texttt{combine} and \texttt{replace}.
The \texttt{combine} function takes \phs as parameters, perturbs them in the order as they appear, and returns a collection of seed \sents.
The order of the parameters defines the scope of the \lc.
Specifically,  \tool supports two types of \phs:  enumerative and search-based \phs.
\tool supports four types of \emph{enumerative} \phs, \emph{prefix}, \emph{sent}, \emph{infix} and 
\emph{postfix}.
A \emph{sent} \ph is a collection of the sentences returned by applying the search-based predicates on the real-world dataset (i.e., search-based \phs). 
\emph{prefix}, \emph{infix}, and \emph{postfix} \phs are sets of user-defined clauses, defined by their relative positions to the \emph{sent} \ph.

%\TODO{@Jaeseong, please add description about combine and replace operations}.

% The seed generation phase of \tool takes test cases as the \ph values and 
% performs seed generation on the \phs to match the specifications defined in the \lcs.
% The reasons for this design are twofold.
% First, it generally is infeasible to judge which \lc any \sent falls into and
% which label it should have. 
% Therefore, transforming test cases allows for classifying the resulting test cases
% into individual \lcs with high confidence. This enables us to test each \lc individually. 
% Second, seed generation of test cases from a real-world dataset ensures that our test cases are realistic and diverse. 
% These diverse test cases are more likely to achieve a high coverage of 
% the target model's functionality in each \lc, allowing more comprehensive
% and reliable model evaluation. 
%thus detecting more errors.

% The search-based \ph is a mathematical assertion that verifies 
% a test case in some specific domain of \lc.
In addition to enumerative \phs, \tool also supports search-based \phs. Search-based \phs allow users to define search predicates to construct constraints (in the form of combinational logic) for each linguistic capability.
Search-based \phs enable \tool to find candidate \sents in given 
real-world datasets matching (partial) 
description of each linguistic capability.
%  The search-based \ph is represented as a  of 
% \emph{search predicates}.
\tool supports two types of search predicates as boolean-valued functions, \emph{implicit} and 
\emph{explicit}, which evaluate and verify
that a test case meets the criteria on explicit and implicit linguistic attributes, respectively.
An explicit attribute is an attribute that can be verified directly in the search dataset, while an implicit attribute requires external domain knowledge.
\tool provides a built-in predicate for each type of the attributes (\texttt{hasattr} for explicit attribute and \texttt{contain} for implicit attribute).
% Explicit attribute is different from implicit attribute 
% in that the implicit attribute is not specified explicitly 
% and limited to be verified in test case itself.
%  Accordingly, \emph{hasattr} function
% searches explicit attributes in test case alone while \emph{contain} function explores 
% implicit attributes using external domain knowledge.
% Label attribute is an example of explicit attribute.
For example, for a sentiment analysis, a predicate for any test cases labeled with negative sentiment can be expressed as 
\texttt{hasattr}$(label, negative)$.
For finding test cases with  any neutral adjective words, the predicate can be expressed as $contain(pos, neutral\_adj)$.
The difference between the two cases is that the latter case requires the analysis of each word in the \sent
to identify its semantic and tag of PoS, which may  
not be obtained directly in the search dataset.
Thus, external linguistic  knowledge of tag of PoS and sentiment of word is needed.

\InputWithSpace{tables/lc-requirement-table}
% \InputWithSpace{tables/lc-hsd-requirement-table}

In later phase, after a whole test case is generated, we use combinational logic of 
user-defined predicates to evaluate if the test case is within the scope of a \lc. 
%\sw{I included this example because I think it better illustrates the search-based predicates.}
For example, the second row in Table~\ref{tab:specification} shows the search predicates of the \lc ``\emph{short sentences with sentiment-laden adjectives}". The search predicates define that the sentences with less than 10 tokens (explicit attribute) and have positive/negative labels (explicit attribute) containing positive/negative adjectives or nouns (implicit attributes) are within this linguistic capability.

% In case the search-based \ph only fulfills part of the \lc specifications, 
% we generate seed test cases using \emph{enumerative} \phs.
% The \emph{enumerative} \ph takes the searched \sents, combines them with user-defined
% clauses, and returns seed \sents. We define four types of \emph{enumerative} \phs, \emph{prefix}, \emph{sent}, \emph{infix} and 
% \emph{postfix}, and combine them using a function called \emph{combine} to generate seed test cases.

The third row in Table~\ref{tab:specification} shows an example of the  search-based and enumerative predicates of the \lc ``\emph{negation of negative at the end, should be positive or neutral}'' for \sa. The search-based predicate only finds negative test case using the \emph{hasattr}, expressed as $hasattr(label,negative)$.
In its enumerative predicates, \emph{sent} maps to the searched negative test cases, and \emph{prefix} and \emph{postfix} are user-defined clauses appearing before and after \emph{sent}, respectively.

In addition to the \texttt{combine} operation, \tool also supports \texttt{replace} operations that allow linguistic attributes of \phs be changed in specific ways. 
In this work, we employ negation for some \lcs that requires negation of \sents. Our complete set of seed generation rules is available on the project website.\footnote{\href{https://sites.google.com/view/s2lct/home}{https://sites.google.com/view/s2lct/home}} 
% \sw{This still reads vague. An example of negation could help.}

\paragraph*{Running example.} We use the running example shown in Figure~\ref{fig:ExpEx} to illustrate how \tool works. The first column illustrates the specification-based seed generation phase. Given the \lc ``short sentences with neutral adjectives and nouns'' for the sentiment analysis task, a sentence ``Or both.'' is selected as a seed for the \lc as it satisfies the search-based predicates which require the short sentence be labeled as neutral and has neutral adjective (\ie both). Other sentences in the first column are excluded because their labels are not neutral and/or they include adjectives/nouns that are not neutral, violating the search-based predicates of this linguistic capability.

% (i.e., LC3-LC10 in Table~\ref{tab:specification} and LC11-LC16 and LC19 in Table~\ref{tab:hsd-specification})

% Table~\ref{tab:specification} and~\ref{tab:hsd-specification} shows the search rules and the
% seed generation templates of all 10 linguistic capabilities we
% implemented in \tool for \sa and \hsd tasks respectively. The first column shows the \lc type and its
% description, and the second column shows the search rule and
% seed generation template used in each \lc.

% For LC1 and LC2 in the Table~\ref{tab:specification}, the NLP
% models are evaluated in the scope of short \sents with selective
% sentiment words. It does not require any
% seed generation because the search rules alone are sufficient to find sentences that conform
% to the \lcs. On the other hand, search rules of LC3 to LC10 are not enough to match their \lc specification; thus, \tool additionally uses 
% templates to transform the searched \sents to match the corresponding \lc. For example, in LC3's seed generation template, the searched \sents are appended as part of a sentence to generate a seed.
% In LC4's seed generation template, the searched demonstrative sentences are negated.
% LC1-LC6 in table~\ref{tab:hsd-specification} assess an NLP model on specific semantics expressed in an input sentence such as emotion and threat. Search and seed generation rules are constructed on semantic and structural requirements of test cases described in \lc. Along with it, they are limited to extract inclusive search and seed generation rules that conform to the \lc. In this work, association of search and seed generation rules with the natural language description in \lc is out of our scope, thus we use hatecheck test cases as seed for the \lc, called \textit{hatecheck} in the table.

% \sw{@Jaeseong: revise the rest of 3.1 based on
%   Table~\ref{tab:specification}. I commented out the old text but it
%   is still in the tex file.} \jl{I revised and added the explanation}

%The search phase in \Model searches inputs in dataset and selects
%subset of input \sents in the dataset that meets the \lc
%\req. The idea behind this phase is that input distribution of
%\lc is important to generate inputs relevant to \lc. \Lc explains
%expected behaviors of NLP model on specific types of input and
%output. The NLP model is evaluated on how much it performs on the
%input and output. Thus, \lc introduces the constraints of the input
%data. Input data from the constrained distribution are only qualified
%to be used for evaluating the NLP model on the \lc.  In addition,
%diversity in inputs is important to evaluate NLP models on the
%\lc. Inputs that differ are more likely to cover the NLP model
%behavior, and more coverage increases trustworthiness of the
%evaluation. To generate inputs from same distribution on \lc and high
%diversity of inputs, we estabilish \reqs of input and output
%for each \lc, and find inputs that fulfil the \reqs. Given a
%\lc, a \req consists of search \req, transform
%\req and expansion \req. The search \req
%describes features and functionalities that we seek to have in
%inputs. \Model check each input if it satisfy the \req.

%\begin{figure}[t]
%  \centering
%  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
%  \vspace{-10pt}
%  \caption{\SearchRequirementExampleFigCaption}
%  \vspace{-10pt}
%\end{figure}
%
%\begin{figure}[t]
%  \centering
%  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
%  \\
%  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python]{code/requirement_sa2.py}}
%  \\
%  \caption{\TransformRequirementExampleFigCaption}
%  \vspace{-10pt}
%\end{figure}
%
%Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
%this \lc, the input is required to be short and have only \neu \adjs,
%\neu \nns. In addition, the label needs to be \neu. Therefore, all
%short natural \sents with only \neu \adjs and \neu \nns are available
%to evaluate NLP models. In this work, the sentiment of the words for
%the search are classified based on the sentiment scores from
%\Swn~\cite{baccianella2010sentiwordnet}, a publicly available English
%sentiment lexicons.  It provides lexical sentiment scores and the
%sentiment word labels are categorized by implementing the rules
%in~\cite{mihaela2017sentiwordnetlabel}. Next, transform \req explains
%how the input and output needs to be tranfromed. Some \lc only accepts
%heavily limited input distribution, and it is unlikely to be included
%in searching dataset because of its high structural diversity, thus,
%finding such \sents is costly. Therefore, our approach is to find
%inputs by relaxing search requirement and transform the input to match
%the target requirement of the \lc. In this work, the inputs are
%transformed by word addition or perturbing the found inputs with \lc
%dependent templates. The figure~\ref{fig:TransformReqEx} shows the
%example of use of the template requirement. The \lc of \SareqExTwo in
%the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
%negated \pstv \sents and the \neu expression in the middle. Rather
%than searching \sents that match the input distribution of the \lc,
%the \Model search \pstv and \neu inputs and combine them into negated
%\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
%for the \lc. According to the \lc, The value of ``sent1'' and
%``sent2'' become each searched \neu and \pstv inputs respectively, and
%the template completion generates new inputs that matches the target
%\lc. In addition, the seed generation of inputs also produce high
%diversity in the inputs because of that from initially found
%inputs. In this paper, we will denote the searched inputs in this
%phase as seed inputs.

\subsection{Syntax-based \Sent Expansion}
\label{sec:sent-exp}

The seed test cases generated 
may still be limited in their syntactic structures because the search dataset may not cover all the syntax. To address this limitation, we design the syntax-based \sent expansion
phase to extend the seed \sents to cover diverse syntactic structures while still conform to its respective \lc specification.
Our insight is that sentences commonly used in real life cover diverse and realistic syntactic structures that can be used as the basis for the expansion. Thus, in this stage, we differentiate the
parse trees between the seed \sents and a set of reference \sents
obtained from a large real-world dataset. The extra tags of PoS in the reference
parse trees are identified as potential syntactic elements for
expansion and inserted into the seed \sents as masks. We then use
masked language model to suggest the fill-ins. If the resulting
\sents still conform to the \lc specification,
they are added to \tool's test suite.

\subsubsection{Syntax Expansion Identification}

Algorithm~\ref{alg:diff} shows how masks are identified for the seed
\sents.  It takes the parse trees of the seeds, generated by the
Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}, and a
reference context-free grammar (CFG) (i.e., the reference dataset in Figure \ref{fig:overview}) as inputs.
Overall, this algorithm identifies the discrepancy between the seed syntax 
and the reference grammar, which is representative of the distribution of real-world language usage, to decide how a seed and what syntax in the seed can be expanded, producing a set of masked sentences.

\input{code/prod_diff_pseudocode}

For each production in each seed's parse tree (lines 3 and 4), we
extract its non-terminal at the left-hand-side (line 5), $s\_lhs$, and
the grammar symbols at the right-hand-side (line 6), $s\_rhs$. In line
7, the algorithm iterates through all productions in the reference
CFG and matches these that have the same non-terminal
at the left-hand-side as $s\_lhs$.  The right-hand-side of each
matched production is called $r\_rhs$.  If $s\_rhs$ consists of a
subset of the grammar symbols in $r\_rhs$ (line 8), the additional
symbols in the $r\_rhs$ are inserted as masks in the parse tree of
the seed \sent, in their respective positions in the expanded production.
The left to right traversal of the leaves of an expanded parse tree
forms a masked \sent.
All the masked \sents of each seed are returned at line 14.
% The
% random sampling is unbiased approach since it gives same chance to be
% chosen. Thus, the random sample becomes representative of the
% population of the masked \sents, and it efficiently shows the
% usefulness of the \tool.

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.5]{figs/running_example.pdf}
  \vspace{-8mm}
  \caption{Running example of \tool.}
  \label{fig:ExpEx}
\end{figure*}

\paragraph*{Running example.} The second and third columns in Figure~\ref{fig:ExpEx} illustrate how Algorithm \ref{alg:diff} is used to generate a masked \sent. The second column shows the parse tree of the seed \sent ``Or both.", which consists of two productions: $``FRAG\rightarrow[CC, NP, .]"$ and $``NP\rightarrow[DT]"$.
When matching the left-hand-side non-terminal of the second production
(\ie, $``NP"$) in the reference CFG, we found that the reference CFG includes a
production $``NP\rightarrow[DT, NNS]"$ which has an additional symbol ``NNS" on
the right-hand-side. The algorithm thus expands the parse tree with
this symbol, shown in the third column.  The masked \sent ``Or both
\{\emph{MASK}\}." is the result of the left-to-right traversal of this leaves of the
expanded parse tree.

\subsubsection{\Sent Expansion and Validation}
\label{sec:approach:syntaxexpnvalidation}
To expand a masked sentence, the words to fill in the masks are
suggested by the BERT model~\cite{devlin2019bert}.
BERT is a transformer-based \nl model that is pre-trained on masked token prediction task. BERT model is capable of suggesting words for the masked
token according to its surrounding context in a \sent. For each masked
token, multiple words may be suggested, ranked by their confidence scores.
Because BERT model is not aware of the \lc
specification and the grammar symbol in the expanded parse tree, an
expanded \sent using all suggested words may no longer satisfy the
\lc specification or the expanded grammar symbol. Therefore, we perform \emph{validation}
on the suggested words and only accept them if the following three
criteria are met.

First, the tag of PoS of the suggested word must match the PoS tag of the
expanded symbol in the parse tree. For the example in
Figure~\ref{fig:ExpEx}, the masked symbol is a $``NNS"$ (\ie, plural
noun); thus, the suggested word must also be a $``NNS"$. In our implementation, we use the \spacy \cite{spacy} library to extract the tag of PoS for each suggested word.

Second, we require the suggested words be \neu. 
% The sentiment of the expanded \sent must be the same as the seed \sent. However
In general, changing even just one word 
may change the overall label and/or linguistic capability of a \sent, which violates the goal of \tool. To reduce this risk, we only accept neutral words from the suggested words, which requires us to use the expansion domain knowledge to verify the sentiment of each suggested word.

Third, we verify that the expanded \sents satisfy the same \lc specification as their seed
\sents. 
% \sw{Update the following based on what we update in Section 3.1. Currently, the description seems 
% inaccurate and unprincipled.} 
An expanded \sent may no longer be within the scope of its seed's linguistic capability. For example, the predicate shown in the second row of Table \ref{tab:specification}, \emph{\textbf{hasattr}(length,<10)}, may no longer hold after expanding a seed sentence with multiple words.
We only accept an expanded sentence if the search-based predicates are still satisfied and the expansion does not happen within an enuramerate \ph.

% Accordingly, we validate if the expanded \sents are still in the scope of their \lc. 
% Not only that, this criteria may not be applied to other \lcs because enumerative \phs can be used for seed test case generation. In this case, the user-defined enumerative \ph values (e.g. \emph{prefix}, \emph{infix} and \emph{postfix}), are to shift sentiment within the scope of their \lc. Expansion of the \ph values may change context the \ph and fail to conform to the \lc. Therefore, we exclude expansions of syntactic elements within the user-defined \ph values to 
% ensure the expanded \sents within the scope of their \lc.

% In this work, out of the BERT suggested words, we randomly selects
% words that matches their PoS tag of the expanded symbol in the parse
% tree. The words that meets the second and third criteria are finally
% employed for the expanded \sents.

% Our goal for generating the expanded \sents is to use them for
% evaluating the \sa models on the associated \lc in addition to the
% seed \sent. It is only achieved when the expanded \sents are also met
% with the same search rules for the \lc. For LC1 as an example, the
% expanded \sent must still conform to the specification of the seed's
% \lc specification. Therefore, the expanded \sents are required to be
% short and to only have \neu adjectives and \nns.
% \sw{Say why we use
%   the third criteria only for LC1 and LC2.}  \jl{I added the
%   explanation}

\paragraph*{Running example.} The fourth column in Figure~\ref{fig:ExpEx} shows the words suggested by BERT. For this masked \sent, BERT suggested six words. Each word is associated with the tag of PoS and the sentiment. Among the six words, only ``ways'' and ``things'' are validated by \tool because they have the tag of Pos ``NNS'' and are \neu. In addition, both \sents still meet the satisfy the search-based predicates of the \lc \SareqExOne. In the end,  the syntax-based sentence expansion results in two more test cases,  ``Or both ways.'' and ``Or both things.'', from the seed ``Or both.".

%The suggested word are
%validated by three criteria. First, The tag of POS must be matched with
%that suggested from the production differentiation phase. In the
%example in the Figure~\ref{fig:ExpEx}, the mask token comes from the
%structural component of NNS, plural noun. Therefore, the BERT
%suggested words must be also tagged with the NNS. Accordingly, every
%words of the NNS are only available. Second, \Model focuses on the \sa
%task, and it assume that the suggested words must not change sentiment
%of its input and must preserve its consistency of original sentiment
%label. Therefore, we only accept the \neu words for the
%expansion. Third, the expanded \sents with the BERT suggested words
%must be appropriate for evaluating NLP models on the target \lc, and the
%\sents must pass the \req of the \lc. In this work, the BERT
%suggestions are validated by the three criteria.

% \subsubsection{\Sent Selection}
% \sw{@Jaeseong: Add how we select expanded \sents and motivate why.}

% \paragraph{Running example.} \jl{I dont think we need this
%   subsection of \sent selection it is already explained at the
%   previous stage with running example.} \sw{This is to use the bert score to rank and select. Did we discuss this already?}

### 2023-03-16 paper/icse24/background.tex
icse24

\section{Background \& Motivation}
\label{sec:background}
\begin{figure}[t]
 \centering
 \lstinputlisting[language=python-pretty]{code/checklist_template2.py}
 \vspace{-10pt}
 \caption{\CklstTemplateFigCaption}
 \label{code:TempEx}
 \vspace{-10pt}
\end{figure}

% In this section, we introduce the concept of \lc-based testing for NLP 
% and a motivating example of our approach.
% We use \Cklst~\cite{marcoACL2020checklist}, a \sota capability testing 
% approach via the code snippet shown in Figure~\ref{code:TempEx}.

Linguistic capability-based testing introduces task-dependent \lcs for monitoring model performance on each \lc \cite{marcoACL2020checklist, searleman1977review}. 
% It assumes that the linguistic scenario can be represented in the behavior of the model under test, because each linguistic capability specifies the desired behavior between model inputs and outputs. \sw{Not exactly sure what the last sentence is trying to say.}
%  Quality of software is verified by ensuring
% the proper working of all functionalities without knowing the internal
% workings of the software. Knowing performances of model on the
% multiple functionalities provides users with better understanding and
% debugging the software. The same principle applies to the NLP model.
% Traditional NLP model evaluation relying on a test set lacks the
% specification of model functionality. However, in NLP domain, there
% are many phenomena on linguistic input such as negation, and
% questionization. Given a NLP task, the phenomena determine
% task-relevant output. Traditional evaluation method neglects them;
% thus, it becomes less efficient to detect and analyze which aspect the
% model yields unexpected outcome.
Test cases that conform to the \lc are generated, and accuracy of the model prediction on them is measured. 
We use \Cklst~\cite{marcoACL2020checklist}, a \sota \lc-based testing approach to illustrate the idea.
In Figure~\ref{code:TempEx}, templates defined
in lines~\ref{code:tempex:template:1} to \ref{code:tempex:template:2} are used for evaluating the \sa model on the linguistic capability \SareqExThree. These templates contain placeholders, ${pos\_adj}$, ${neg\_adj}$, and ${change}$. Values for the placeholders are a collection of words defined in lines~\ref{code:tempex:posadj:1} to~\ref{code:tempex:change}.
For each template, \Cklst fills in all the combinations of the
possible values of placeholders to generate sentences under this \lc.
For example, sentences such as ``I used to think this airline was bad, but now I think it is good.'' and ``In the past I thought this airline was weird, although now I think it is great.'' are generated. 
In this manner, all test cases generated from the template conform to the \lc
of interest, \ie, sentiment change over time for this example. These test cases can be used to assess how well a \sa model 
understands sentiment change over time.
Therefore, \lc testing is beneficial to evaluate not only how model accurately predicts, 
but also how model understands the metamorphic relation between input and output and if it behaves 
as the \lc specifies.
% Further, evaluation of model on multiple \lcs provides the deficient aspect
% of model behavior.

Despite the potential usefulness of \lc-based testing, all existing capability testing 
work~\cite{marcoACL2020checklist, rottger2020hatecheck} shares common limitations. First,
they require manual work for defining templates and its placeholder values for every \lcs, as illustrated in Figure \ref{code:TempEx}.
This manual work is costly, and it makes the test case generation rely on relatively simple template structure, thus limiting test coverage on each \lc. Moreover, performing word substitution for the template placeholders produces similar test cases with regard to input text and structure. The limited diversity in test cases results in bias in model evaluation on the \lc with the test cases.
% \sw{I don't understand what we mean by ``induces bias in the test cases consequently".} 
These limitations motivated the design of our approach.

### 2023-03-16 paper/icse24/exp_bake.tex
icse24

--- 2022-06-07 paper/ase22/experiment.tex
@@
-\section{Experimental Setup}
-\label{sec:experiment}
-%
-In this section, we present the setup of the experiments to evaluate
-the effectiveness of \tool{}. We address the following research
-questions (RQs):
+\paragraph*{\selfbleu and production rule coverage.} First, we reuse the input diversity metric, 
+called \selfbleu, that Zhu \etal introduced~\cite{zhu2018texygen}. \bleu~\cite{papineni2002bleu} evaluates token-level similarity.
+% Regarding that \selfbleu takes each \sent as hypothesis and rest in a collection of textual data as reference, we calculate \bleu scores for every pairs of hypothesis and each reference \sent.
+\selfbleu is defined as the average \bleu scores over all reference \sents, ranging between 0 and 1.
+% Since the \bleu score ranges from 0 as the least similar inputs to 1 as the most similar inputs,
+A higher \selfbleu score indicates lower diversity in the test suite.
+Second, we propose a new metric to 
+evaluate the syntactic diversity of the generated test suite.
+It is defined as the number of production rules covered in a set of 
+test \sents. In our experiments, we used the Berkeley Neural 
+Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and
+collect all the productions.
 
-\begin{enumerate}[label=\textbf{RQ\arabic*}]
-\item \label{rq:three}: Can \tool generate more diverse test cases
-  than \Cklst?
-\item \label{rq:one}: Can \tool generate test sentences with correct sentiment labels?
-\item \label{rq:two}: Are \tool generated test sentences correctly categorized into a \lc?
-\item \label{rq:four}: Can \tool be useful to find root causes of bugs
-  in the \sa models?
-%% \item \label{rq:three}: How effective is our new test case generation
-%%   using \cfg expansion? % ablation study
-\end{enumerate}
+In the evaluation, we collected 200, 400, 600, 800 and 1000 test cases for \sa and 10000, 50000, 100000, 150000 and 200000 test cases for \hsd, randomly selected \tool seed and expanded \sents.
+We then computed the median of \selfbleu and \pdr scores over all \lcs.
+We repeated this computation with different \tool seeds over 5 trials and reported the median.
+% \sw{I am lost with the rest of this paragraph. Explain to me; then we will fix.}
+We also evaluated \tool expansion phase by generating expanded \sents from \Cklst and 
+\hck as seeds. We collected up to 200 randomly selected test cases from \Cklst and 
+\hck and generate their expanded \sents. We computed the median of \selfbleu and \pdr 
+scores from the \sents over all \lcs. We repeated the computation with different \tool
+seeds over 3 trials and reported the median over the 3 trials.
+In addition, we compared \selfbleu and \pdr scores between \tool and text generation 
+\bls. First, we generate two groups of \sents from 100 randomly selected \tool seeds 
+for each \sa and \hsd using \tool expansion and syntax-based text generation \bl. 
+\selfbleu and \pdr scores of the two groups of \sents were then compared. Second. we 
+generate two groups of \sents from 50 randomly selected \tool seeds for \sa using 
+\tool expansion and adversarial text generation \bls. Likewise, we compared \selfbleu 
+and \pdr scores of the two groups of \sents.
 
-%To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
-%evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
-%finding bugs; (\romnum{3}) degree of execution of a \sa model on testcases;
-%and (\romnum{4}) ability to guide to find cause of bug in a \sa
-%model.
-
-\subsection{Experimental Subjects}
-
-\paragraph{\textbf{NLP Models \& Dataset.}}
-We evaluate our approach on three learning-based \sa models
-implemented in Transformer library from the Hugging Face centralized
-Model Hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
-(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
-language using a masked language modeling (MLM) objective, and
-fine-tuned on the \sa task. In this experiment, we use \Sstt \cite{socher2013sst} dataset for
-searching the seeds in \tool. \Sstt is a
-corpus of movie review, and consists of 11,855 sentences
-with sentiment scores. We split the
-scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign 
-negative, neutral and positive labels, respectively. In addition, 
-we use \Swn as the word sentiment dataset~\cite{baccianella2010sentiwordnet}. 
-\Swn is a publicly available English sentiment lexicons.  
-It provides lexical sentiment scores and the sentiment word labels 
-are categorized by implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
-%% \TODO{introduce details about each model}
-
-\paragraph{\textbf{Comparison Baseline.}}
-We compare \tool with
-\Cklst,\footnote{https://github.com/marcotcr/checklist} a
-manual template-based approach to generate test cases. In this
-experiment, we used the \Cklst released \sa test cases which are
-generated from its publicly available jupyter notebook implementation.
-%% \TODO{introduce details about CHECKLIST}
-
-\subsection{Experimental Process}
-
-\paragraph{\textbf{RQ1.}}
-Recall that a key limitation of \Cklst is that its template-based
-approach relies on significant manual efforts and may not generate test cases that comprehensively cover the sentences
-in a linguistic capability. \tool, instead, automatically generates test cases based on a search
-dataset and the syntax in a large reference corpus. 
-We expect \tool can generate a more diverse test suite than \Cklst, and achieve
-more probable evaluation results.
-
-We first evaluate the three \sa
-models by testing them on the \tool generated test cases, reporting number of test cases and each model's failure rate in each linguistic capability.
-
-Next,
-to measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
+\paragraph*{Model coverage.}
+We follow the approach presented by Ma et al. \cite{ma2018deepgauge},
 where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
@@
 \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
-It is worth noting that a test sample with a statistical distribution similar to the training data would rarely be found in the corner case region.
-As a result, covering a larger corner case region means that the test suite is more likely to be buggy.
 
+% It is worth noting that a test sample with a statistical distribution similar to the training data is rarely found in the corner case region.
+% Thus, covering a larger corner case region indicates that the test suite is more likely to be buggy.
 \begin{equation}
@@
 
-\noindent Equation \ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
-Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
+\noindent Equation \ref{eq:corner} defines the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' upper and lower output bounds on the model training dataset respectively.
+Equation \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.
 
+\begin{small}
 \begin{equation}
@@
 \end{equation}
-
-\noindent The formal definition of our coverage metrics are shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
+\end{small}
+\noindent The definition of our model coverage metrics is shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produces outputs exceeding the upper or lower bounds, and SActCov measures the coverage of neurons that creates outputs exceeding the lower bound.
 Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.
 
-% ($Cov(\mathcal{X})$ in \equref{eq:coverage}),
-% where $N$ is the total number blocks, $\mathbb I(\cdot)$ is the indicator function, and
-% $(B_i(x) > \tau_i))$ represents whether $i^{th}$ block is activated by input $x$~(the definition of $B_i$ and $\tau_i$ are the same with \equref{eq:new2} and \equref{eq:new3}).
-% Because AdNNs activate different blocks for decision making, then a higher block coverage indicates the test samples cover more decision behaviors.
-
-To answer RQ1, for each NLP model under test, we first feed its training dataset to compute each neuron's lower and upper bounds.
-After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding coverage metrics.
+To evaluate model coverage, we feed the training dataset of each NLP model under test to compute each neuron's lower and upper bounds.
+After that, we select the same number of test cases from \tool and \Cklst as the test suite and compute the corresponding model coverage metrics.
 
@@
 % Finally, we feed the generated test samples to AdNNs and measure block coverage.
-% We repeat this process 10 times and record the average coverage and the variance.
+% We repeat this process 10 times and record the a  verage coverage and the variance.
 % The results are shown in \tabref{tab:coverage} last two columns.
 
-%
-%The amount of \sa model
+%%The amount of \sa model
 %components \sw{?} executed during testing is a critical measurement for
@@
 %\bertsamodel and compare the coverage between \tool and \Cklst.
-
-\paragraph{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
-\tool generates test cases in two steps: specification-based seed
-generation and syntax-based sentence expansion. These automated steps
-may generate seed/expanded sentences marked with incorrect sentiment
-labels or categorized into wrong linguistic capabilities. For example,
-the search rule and template defined in a linguistic capability may
-not always generate seed sentences in that capability or with the
-correct label.  To answer RQ2 and RQ3, we performed a manual study to
-measure the correctness of the sentiment labels and linguistic
-capabilities associated with the seed/expanded sentences, produced by
-\tool.
-
-In the manual study, we randomly sample 100 seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set).
-For each sampled seed sentence, we randomly obtain one of its expanded sentences.
-This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
-We recruited three participants of this study; all of them are graduate students with no knowledge about this work. 
-2 of them were assigned one set of sentences and the third was assigned the other set.
-Each participant was asked to provide two scores for each sentence.
-\emph{(1) Relevancy score between sentence and its associated \lc}:
-this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete,
-ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment score of the sentence}: this score measures the sentiment level of the sentence . It
-is also discrete, ranging from 1 (``strongly
-negative'') to 5 (``strongly positive''). 
-We measure the following:
-
-\begin{eqnarray}
-  sent\_consistency &= \frac{1}{\#Sample\cdot~}\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human}) \label{metric:srel} \\
-  LC\_relevancy_{AVG} &= \frac{1}{\#Sample\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
-\end{eqnarray}
-
-Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants produce the same sentiment labels.
-High value of this metric indicates \tool generates test cases with correct labels.
-Equation~\ref{metric:lcrel} represents the average of the
-normalized relevancy score between a sentence and its associated
-\lc. Higher average score means indicates the linguistic capability categorization by \tool is correct. We answer RQ2 and RQ3 using the metrics defined by
-Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
-respectively.
-
-\paragraph{\textbf{RQ4.}}
-
-To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
-Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input).
-Still, it is unclear why mutating one token will cause the model to produce misclassified results.
-We seek to help developers understand why such mutation will result in the misclassification. 
-Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences).
-Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.
-
-Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
-The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
-\begin{equation}
-    P(f(T(x)) = f(x)) \ge P_{thresh}
-    \label{eq:prob}
-\end{equation}
-To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}.
-We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
-We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
-Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$.
-Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).
-
-% In particular, we apply the explainable ML techniques to visualize the contribution of each input token to the model predictions.
-%
-
-% \sw{@Simin: add the setup of the bug explanation case study here.}
-%In addition to the detection of bugs \sw{have we defined ``bug" in this context?} in the model,
-%explanation of the bugs is also important for debugging and
-%repairing the model. Therefore, we answer {\bf RQ3} by analyzing the \sa model based on \tool test cases to find the root causes of the bugs.
-%
-%Specifically, we adapt \Denas{} for this experiment. \sw{Say more what DENAS does.} Rules generated from
-%\Denas{} are interpretable functions mapping certain features of the
-%input to the expected output of a deep \nn system, and the generated
-%rules are considered as the behaviors of the deep \nn system. To
-%analyze the bug of a \sa model, we generates rules over the test
-%inputs using \Denas{} and identifies faulty rules for the failed test
-%inputs.
-%\sw{Previous sounds vague. Any specific adaptation of DENAS we did?}
-%We manually identify the root of the faulty rules and find the
-%root causes of bug in the end.
-
-% \noindent\textbf{Implementation Details.}
-
-% \sw{Missing: environment running these experiments.}
-
-%% \MyPara{Seed Input Selection}
-%% %
-%% For each linguistic capability, we first search all sentences that
-%% meet its requirement. Among found sentences, we randomly select 10
-%% sentences due to memory constraint.
-
-%% \MyPara{Word Sentiment}
-%% %
-%% we extract sentiments of words using the
-%% \Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
-%% available lexical resource of words on Wordnet with three numerical
-%% scores of objectivity, positivity and negativity. Sentiment word
-%% labels from the scores are classified from the algorithm from Mihaela
-%% \etal~\cite{mihaela2017sentiwordnetlabel}.
-
-%% \MyPara{\Cfg Expansion}
-%% %
-%% We build a reference \Cfg of natural language from the English Penn
-%% \Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
-%% The corpus is sampled from 2,499 stories from a tree year \Wsj
-%% collection The \Trb provides a parsed text corpus with annotation of
-%% syntactic and semantic structure. In this experiment We implement the
-%% \trb corpora available through \Nltk, which is a suite of libraries
-%% and programs for \Nlp for English. In addition, we parse the seed
-%% input using into its CFG using the Berkeley Neural
-%% Parser~\cite{kitaev2018constituency, kitaev2019multilingual}, a
-%% high-accuracy parser with models for 11 languages. The input is a raw
-%% text in natural language and the output is the string representation of
-%% parse tree. Next after comparing CFGs between reference and seed input,
-%% we randomly select 10 expansions for generating templates due to
-%% memory constraint.
-
-%% \MyPara{Synonyms}
-%% %
-%% \Model searches synonyms of each token from synonym sets extracted
-%% from \Wrdnt using \Spacy open-source library for NLP.
-
-%% \MyPara{Models}
-%% %
-%% We evaluate the following \sa models via \Model:
-%% \Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
-%% \Dbert~\cite{sanh2019distilbert}. These models are fine-tuned on \Sstt
-%% and their accuracies are \BertAcc, \RobertaAcc and \DbertAcc.
-
-%% \MyPara{Retraining}
-%% %
-%% We retrain \sa models. we split \Model generated test cases into
-%% train/validation/test sets with the ratio of 8:1:1. The number of
-%% epochs and batch size for retraining are 1 and 16 respectively.
-
-%\input{CM/coverage}
-
-%\input{CM/explain}

### 2023-03-16 paper/icse24/experiment.tex
icse24

\section{Experimental Setup}
\label{sec:experiment}

In this section, we present the setup of our experiments. We answer the following research questions (RQs):

\begin{enumerate}[label=\textbf{RQ\arabic*}]
    \item \label{rq:one} \textbf{Diversity.} Can \tool generate more diverse test cases than existing approaches?

    \item \label{rq:two} \textbf{Effectiveness.} Is \tool more effective than existing approaches at generating test cases that can trigger more errors in the model?

    \item \label{rq:three}  \textbf{Consistency.} Can \tool maintain consistency in terms of labels, linguistic capabilities, and semantics throughout the expansion process?
    % \TODO{CM: what is correct labels}

    % \item \label{rq:four}  \textbf{Capability Consistency.} Are test cases generated by \tool correctly categorized into a linguistic capability?

\end{enumerate}

%To answer the RQs, we need to show: (\romnum{1}) correctness of testcase to
%evaluate its target \lc.  (\romnum{2}) effect of testcase distribution on
%finding bugs; (\romnum{3}) degree of execution of a \sa model on testcases;
%and (\romnum{4}) ability to guide to find cause of bug in a \sa
%model.

\input{tables/model}

\subsection{Experimental Subjects}
\MyPara{NLP Models} We evaluate our approach on three \sa models and two \hsd models.  We obtain our evaluation models from the HuggingFace model hub \cite{huggingface}.
Table \ref{tab:model} presents the models and their corresponding API URLs. The ``API URL'' column displays the public URL of each model, while the ``$\#$ of downloads'' column indicates the number of downloads for each model in Jan. 2023. Based on the information provided in Table \ref{tab:model}, it is evident that all models utilized in our evaluation have been widely adopted in real-world settings, with a considerable number of downloads. 
For readers who seek more comprehensive information about each model, we recommend referring to the corresponding API URL of each model.

%\CM{do we need to create a table to show these models are public API and are widely used} \footnote{https://huggingface.co/models} \texttt{\Bert}
%(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel~\cite{sanh2019distilbertad}) for \sa, and \texttt{\hsdBert} (\berthsdmodel~\cite{aluru2020deep}) and \texttt{\hsdRoBerta} (\robertahsdmodel) for \hsd.
%These models were pre-trained on English language with a masked language modeling objective, and were fine-tuned on the \sa and \hsd tasks.

\MyPara{Datasets} In our evaluation of sentiment analysis models, we utilize \Sst~\cite{socher2013sst} as our initial labeled search dataset. Meanwhile, for assessing models designed for hate speech detection, we make use of \Hatexp~\cite{mathew2021hatexplain} as our initial dataset.
\Sst is a corpus of movie reviews that consists of 11,855 sentences, each of which has been labeled as either negative, neutral, or positive to indicate the expressed sentiment in the sentence.
% Following the original setting of \Sst~\cite{socher2013sst}, we divide the scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign them negative, neutral and positive labels, respectively.
\Hatexp is a dataset that has been collected from social media platforms Twitter and Gab. It consists of 20,148 sentences, with 9,055 of them being from Twitter and 11,093 from Gab. Each sentence in this dataset has been labeled as either "hate" or "non-hate" to indicate the presence or absence of hate speech in the sentence \cite{mathew2021hatexplain}.

% has been annotated by three different annotators.
% For each sentence, it has been labeled as ``hate'' label when majority label over the annotators is hate, and non-hate label otherwise.
% \sw{I don't understand what ``three labels of hate speech for three different annotators" mean. Explain to me and we will update.}

% as shown in Figure \ref{fig:overview}.

\MyPara{\Bls}
\label{sec:experiment_bl}
For RQ1, we first compare \tool against \Cklst~\cite{marcoACL2020checklist} and \hck~\cite{rottger2020hatecheck}. After that, we also compare \tool against \mtnlp, Alzantot-attack, BERT-Attack and SememePSO-attack~\cite{maIJCAI2020mtnlp,alzantot2018genadvexp,linyang2020bertattack,zang2020sememepso}.
For RQ2, we compare \tool against \Cklst and \hck again.

% \TODO{Notice that although there are several existing adversarial NLP techniques that can generate test inputs to test NLP models, 
% We compare \tool against 
% \Cklst and \hck are manual template- and \lc-based test case generation approaches for \sa and \hsd, respectively. 
% In this evaluation, we used \Cklst's \sa test cases that are generated from its original implementation \footnote{https://github.com/marcotcr/checklist} and \hsd test cases on the \hck's public 
% Github pages.\footnote{https://github.com/paul-rottger/hatecheck-data}
% by comparing them with \tool generated test cases and \tool expanded test cases from \Cklst and \hck as seeds.
% We also consider existing text generation methods to evaluate \tool's syntax-based expansion phase. First, we compared to \mtnlp, another syntax-based text generation tool. While there exist other syntax-based other syntax-based text generation methods \cite{udeshi2019ogma,soremekun2022astraea,asyrofi2021biasfinder}, their tools are not publicly available or we were not successfully build them. \sw{Is the last \sent (which I changed) correct? Need to be careful.} \mtnlp presents a NLP fuzz testing approach to evaluate NLP model 
% fairness by replacing a word with its analogy or inserting fairness-sensitive words.
% % \sw{Resume here.}
% Second, we compared to three adversarial example generation methods~\cite{alzantot2018genadvexp,linyang2020bertattack,zang2020sememepso}. \sw{Is it right that we are comparing to three? What is the name for each?} Alzantot~\etal attacks a NLP model with nearest neighbors of input word in embedding space~\cite{alzantot2018genadvexp}. Bert-Attack finds adversarial words in \sent using suggestions from a pretrained masked language model~\cite{linyang2020bertattack}. SememePSO-Attack substitutes word using \sw{What is ``particle swarm optimization" and what is ``search space"?} particle swarm optimization method in search space~\cite{zang2020sememepso}.
% }
% A search algorithm based on particle swarm
% optimization is proposed to search adversarial
% examples.

\begin{equation}
\label{eq:syntactic}
    Syntactic\;Diversity(\mathcal{X}) = || \{\mathcal{P}(x) \;\; | \;\; \forall x \in \mathcal{X} \}||
\end{equation}

\subsection{Evaluation Metrics}
\label{sec:metric}
To answer RQ1, we define three metrics to measure the diversity of the generated test suite. Our first metric is \textit{\selfbleu}, which was introduced by \cite{zhu2018texygen}. \selfbleu is defined as the average \bleu score~\cite{papineni2002bleu} over all reference sentences, ranging between 0 and 1. A higher \selfbleu score indicates lower diversity in the test suite, while a lower score indicates greater diversity.
However, since \selfbleu cannot represent the syntactic diversity of a test suite, we have proposed a new metric, \textit{syntactic diversity}, to evaluate the diversity of the test suite. The syntactic diversity of a test suite $\mathcal{X}$ is defined as the number of production rules covered in this test suite. The formal definition of syntactic diversity is shown in  \eqref{eq:syntactic}, where $\mathcal{P}$ is the Berkeley Neural Parsing function~\cite{kitaev2018seedparser,kitaev2019seedparser} that return the production rule of the given sentence.
Our final metric is \textit{neuron coverage}. 
We follow the approach presented by Ma et al. \cite{ma2018deepgauge}, where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
Because the matrix computation of intermediate states impacts NLP model decision-making, a test suite that covers a greater number of intermediate states can represent more NLP model decision-making, making it more diverse.
Specifically, we used two coverage metrics by Ma et al. \cite{ma2018deepgauge}, boundary coverage (BoundCov) and strong activation coverage (SActCov), to evaluate the test suite diversity.
% It is worth noting that a test sample with a statistical distribution similar to the training data is rarely found in the corner case region.
% Thus, covering a larger corner case region indicates that the test suite is more likely to be buggy.
\begin{equation}
\begin{split}
    \text{UpperCorner}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (high_n, +\infty)\}; \\
    \text{LowerCorner}(\mathcal{X}) = \{n \in N | \exists x \in \mathcal{X}: f_n(x) \in (-\infty, low_n)\}; \\
\end{split}
    \label{eq:corner}
\end{equation}

\noindent Equation \ref{eq:corner} defines the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' upper and lower output bounds on the model training dataset respectively.
Equation \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.

\begin{small}
\begin{equation}
\begin{split}
     & BoundCov(\mathcal{X}) = \frac{|UpperCorner(\mathcal{X})| + |LowerCorner(\mathcal{X})| }{2 \times |N|} \\ 
     &\quad  \qquad \qquad  SActCov(\mathcal{X}) = \frac{|UpperCorner(\mathcal{X})|} {|N|} \\ 
\end{split}
    \label{eq:coverage}
\end{equation}
\end{small}

\noindent The definition of our model coverage metrics is shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produces outputs exceeding the upper or lower bounds, and SActCov measures the coverage of neurons that creates outputs exceeding the lower bound.
Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better diversity.

For RQ2, our goal is to answer whether \tool is more effective than other methods for generating test cases that can trigger incorrect predictions. Thus, we measure three key metrics: (1) the number of test cases generated, (2) the number of failed test cases, and (3) the failure rates of the generated test cases. Additionally, we also report on the number of expanded test cases that failed but whose corresponding seed test cases passed (\Ptf) using \tool.

\begin{equation}
\label{eq:consistency}
\begin{split}
    &  LabelCons = \frac{1}{\#Sample}\cdot \sum_{i}\delta(label_{S^2LCT}=label_{human}) \\
    & LCRel_{AVG} = \frac{1}{\#Sample}\cdot\sum_{i} Norm(LCRel_i)   \\
    &  ExpValidity_{AVG} = \frac{1}{\#ExpSample}\cdot\sum_{i} Norm(ExpValidity_i)  
\end{split}
\end{equation}

% \begin{equation}
% \begin{small}
% \begin{aligned}
%   LabelCons = \frac{1}{\#Sample}\cdot \sum_{i}\delta(label_{S^2LCT}=label_{human})\label{eq:lcons}
% \end{aligned}
% \end{small}
% \end{equation}
% \begin{equation}
% \begin{small}
% \begin{aligned}
%   LCRel_{AVG} = \frac{1}{\#Sample}\cdot\sum_{i} Norm(LCRel_i) \label{eq:lcrel}
% \end{aligned}
% \end{small}
% \end{equation}
% \begin{equation}
% \begin{small}
% \begin{aligned}
%   ExpValidity_{AVG} = \frac{1}{\#ExpSample}\cdot\sum_{i} Norm(ExpValidity_i) \label{eq:expval}
% \end{aligned}
% \end{small}
% \end{equation}

% \begin{equation}
% \label{eq:consistency}
%     \begin{split}
%         & \qquad\quad \zeta_{label} = \frac{1}{||\mathcal{X}||} \sum_{x \in \mathcal{X}} \mathbb{I}(label(x) == \text{HLabel(x)}) \\
%         & \zeta_{linguistic} = \frac{1}{||\mathcal{X}||} \sum_{x \in \mathcal{X}} \mathbb{I}(linguistic(x) == \text{Hlinguistic(x)}) \\
%         & \zeta_{semantic} = \frac{1}{||\mathcal{X}||} \sum_{x \in \mathcal{X}} \mathbb{I}(\text{HSemantic}(x) == \text{HSemantic}(Seed(x)))  \\
%     \end{split}
% \end{equation}

To answer RQ3, we introduce three new metrics: the label consistent rate ($LabelCons$), the linguistic capability consistent rate ($LCRel_{AVG}$), and the semantic consistent rate ($ExpValidity_{AVG}$). The formal definitions of these metrics are listed in Equation \ref{eq:consistency}.
% In Equation \ref{eq:consistency}, HLabel$(\cdot)$, Hlinguistic$(\cdot)$, and HSemantic$(\cdot)$ represent the label, linguistic capability, and semantic assigned by humans to a given sentence, while $label(\cdot)$ and $linguistic(\cdot)$ are functions used to obtain the automatic constructed label, linguistic capability of a test input.

% \TODO{Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants 
% produce the same sentiment labels. High value of this metric indicates \tool generates test cases with
% correct labels. Equation~\ref{metric:lcrel} represents the average of the
% normalized relevancy score between a \sent and its associated
% \lc. The relevancy score is to evaluate the relevancy of the test case on the 
% corresponding \lc. Higher average score indicates the linguistic capability 
% categorization by \tool is correct. 
% Equation~\ref{metric:expval} represents expansion validity, the average of the normalized validity score between expanded \sent and its corresponding seed \sent.
% The higher score indicates higher semantic similarity between expanded \sent and its corresponding seed \sent enough to use semantic label of the seed \sent for the expanded \sent.
% We answer \ref{rq:three} and \ref{rq:four} using the metrics defined by
% Equations~\ref{metric:srel}, \ref{metric:lcrel} and~\ref{metric:expval}, respectively.}

% In our experiments, we used the Berkeley Neural Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and
% collect all the productions.

% First, we reuse the input diversity metric,
% called , that Zhu \etal introduced~\cite{zhu2018texygen}. \bleu~\cite{papineni2002bleu} evaluates token-level similarity.
% Regarding that \selfbleu takes each \sent as hypothesis and rest in a collection of textual data as reference, we calculate \bleu scores for every pairs of hypothesis and each reference \sent.
% Since the \bleu score ranges from 0 as the least similar inputs to 1 as the most similar inputs,
% A higher \selfbleu score indicates lower diversity in the test suite.
% Second, we propose a new metric to 
% evaluate the syntactic diversity of the generated test suite.
% It is defined as the number of production rules covered in a set of 
% test \sents. In our experiments, we used the Berkeley Neural 
% Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and
% collect all the productions.

% To answer RQ2,

\subsection{Experimental Process}

\MyPara{\ref{rq:one} Process} In the evaluation, we collected 200, 400, 600, 800 and 1000 test cases for \sa and 10000, 50000, 100000, 150000 and 200000 test cases for \hsd, randomly selected \tool seed and expanded \sents. We then computed the median of \selfbleu and \pdr scores over all \lcs. We repeated this computation with different \tool seeds over 5 trials and reported the median. 
% \sw{I am lost with the rest of this paragraph. Explain to me; then we will fix.}
We also evaluated \tool expansion phase by generating expanded \sents from \Cklst and 
\hck as seeds. We collected up to 200 randomly selected test cases from \Cklst and 
\hck and generate their expanded \sents. We computed the median of \selfbleu and \pdr 
scores from the \sents over all \lcs. We repeated the computation with different \tool
seeds over 3 trials and reported the median over the 3 trials.
In addition, we compared \selfbleu and \pdr scores between \tool and text generation 
\bls. First, we generate two groups of \sents from 100 randomly selected \tool seeds 
for each \sa and \hsd using \tool expansion and syntax-based text generation \bl. 
\selfbleu and \pdr scores of the two groups of \sents were then compared. Second. we 
generate two groups of \sents from 50 randomly selected \tool seeds for \sa using 
\tool expansion and adversarial text generation \bls. Likewise, we compared \selfbleu 
and \pdr scores of the two groups of \sents.

% \TODO{how about production rule coverage}

For the model coverage metric, we begin by feeding the training dataset of each NLP model under test into the system in order to compute the lower and upper bounds for each neuron. Then, we select an equal number of test cases from both \tool and \Cklst to construct the test suite and calculate the corresponding model coverage metrics.

% Recall that \Cklst relies on significant manual efforts and may not generate comprehensive test cases in a linguistic capability. \tool, instead, automatically generates test cases based on a search dataset and the syntax in a large reference corpus. We expect \tool can generate more qualitative test cases than \bls.

\MyPara{\ref{rq:two} Process}
% We expect that the iterative seed generation and syntactic expansion generate more qualitative and quantitative test suite for finding errors effectively.s
% To evaluate test effectiveness of \tool, we compared \tool and capability-based testing \bls 
% using (1) number of test cases, (2) number of failed test cases, and (3) failure rates of NLP models under test.
% In addition, we report the number of expanded test cases that failed, 
% but their corresponding seed test cases passed (\Ptf) from the \tool.
% \TODO{Recall that our syntax-based expansion validates label consistency; thus, the models are expected to classify the expanded sentences with the same labels as their seed sentences. 
% However, we observed that an expanded sentence might deceive the model into producing a different prediction from its seed. Identification of these cases may provide further insight into the root causes of the erroneous behaviors of the model in the \lc, which we demonstrate in an application of \tool (Section \ref{sec:application}). 
% }
We address RQ2 by evaluating 5 models in Table~\ref{tab:model} on test cases of \tool and \lc-based testing \bls for \sa and \hsd. For each \lc, we measure the number of test cases generated from the \bls, \tool seeds and their expansions. We calculate the number of failures and fail rate of the 5 models. In addition, we compare model performances on test cases between \tool seeds and their expansions, and measure the number of \Ptf cases.
% Accordingly, we compute the median of the number of \Ptf test cases over 
% all \lcs between 200, 400, 600 and 800 randomly selected \tool seeds 
% and the \Cklst test cases, and we compare the median of the median numbers 
% over 10 trials for each group of seeds.

\MyPara{\ref{rq:three} Process}
% As described in Section~\ref{sec:approach},
% \tool generates test cases in two steps: specification-based seed generation and syntax-based \sent expansion. These automated steps
% may generate seed/expanded \sents marked with incorrect sentiment
% labels or categorized into wrong linguistic capabilities.
% For example,
% the search rule and template defined in a linguistic capability may
% not always generate seed \sents in that capability or with the
% correct label. 
To address RQ3, we conduct a manual study to evaluate the three consistency metrics listed in Equation \eqref{eq:consistency} for the test suite generated by \tool. For each task, we randomly sampled 100 \tool seed \sents. We divide these seeds to two sets (i.e., 50 \sents in each set). For each sampled seed \sent, we randomly obtain one of its expanded \sents.
This forms the two sets of \sents, each with 50 seeds and 50 corresponding expanded \sents. We recruited two participants for each task; all of them are graduate students with no 
knowledge about this work. Each of them was assigned a different set of \sents, and asked to provide three scores for each \sent. \emph{(1) Relevancy score between \sent and its associated \lc}:
this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete, ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant'').
\emph{(2) Sentiment score of the \sent}: this score measures the sentiment level of the \sent . It is also discrete, ranging from 1 to 5 representing ``strongly negative'' to ``strongly positive'' for \sa and ``strongly normal'' to ``strongly hateful'' for \hsd, respectively.
\emph{(3) Validity score of expanded \sent}: this score measures the validity of the use of label of a seed \sent for its associated \tool expanded \sent. The scores are discrete ranging from 1 (``strongly not consistent'') to (``strongly consistent'').

% \sw{If possible, make each of the following equations show in one line.}\jl{made them in one line.}

\MyPara{Implementation Details} In our implementation, we obtained our reference CFG from the Penn Treebank corpus~\cite{mitchell1993treebank}. Additionally, we utilized \Swn~\cite{baccianella2010sentiwordnet}, which is a lexical sentiment resource, as the domain-specific knowledge for sentence expansion. All experiments were conducted on a Ubuntu 14.04 server with three Intel Xeon E5-2660 v3 CPUs @2.60GHz, eight Nvidia 1080Ti GPUs, and 500GB of RAM.

### 2023-03-16 paper/icse24/intro.tex
icse24

\section{Introduction}
\label{sec:intro}

% In the early stage of the software development process, automated
% software testing and debugging can identify and fix
% defects. Therefore, effective software testing assures software
% quality, and it meets needs of the end user. Nowdays, software at work
% has elements of \ml (ML). Especially,

\Nlp (NLP) applications are growing rapidly.  As a result, trustworthiness in 
how the quality of NLP applications is assessed becomes critical for its 
practical use in the real world. Traditionally, the quality of NLP models is 
assessed using aggregated metrics. In particular, accuracy (\ie, the fraction of 
outputs that the model correctly predicts) is the most widely used metric for 
assessing the quality of classification models:
higher accuracy suggests better quality of a model. However, all NLP models have 
their strengths and weaknesses; using a single, aggregated metric (i.e., 
accuracy) makes it difficult for the users to assess model behavior on fine-grained aspects of NLP models. To address this limitation of the 
traditional quality metric, an increasing number of evaluation methods has been 
introduced to evaluate an NLP model in different aspects such as robustness on 
adversarial examples~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack,udeshi2019ogma} and bias on demographic groups~\cite{soremekun2020astraea,udeshi2018fairnesstest,asyrofi2022biasfinder,maIJCAI2020mtnlp}. However, such metrics still assess specific facet of the NLP models, and they still fail to validate how well a model behaves in different linguistic scenarios~\cite{geva2019we,gururangan2018annotation}.

Recent research has proposed methods to assess an NLP model on a set of \lcs in 
different NLP applications~\cite{marcoACL2020checklist,rottger2020hatecheck}. 
A \lc is a specific linguistic scenario between input and output observed in the  domain 
of NLP application. Compared with the traditional evaluation metrics, 
\lc-based testing avoids the overestimation of the model performance by
measuring variances of model performance over the capabilities. Thus,
it is able to give detail assessment on strength and weakness of a given NLP model.
% \sw{The last sentence is a strong claim. Is there a citation for this claim? Maybe checklist?}
% For example, performance of \sa model on negation and questionization in texts can be different, and variance in the model performances enables identification of certain input type that causes the performance inconsistency in NLP models~\cite{marcoACL2020checklist}.
Nevertheless, existing \lc-based testing approaches are limited to facilitate automated and comprehensive testing.
%rely on unprincipled description of \lcs. In addition,
They rely on manually designed word substitution-based templates. The test cases are generated by  replacing words on the place holders in the templates \cite{marcoACL2020checklist, rottger2020hatecheck} 
% \CM{fix} \sw{cite checklist and hatecheck again here?}. 
Therefore, their test cases  do not cover diverse \sent structures, preventing comprehensive testing of NLP model on \lcs.

To address this issue, we present \tool,
an automated linguistic capability-based framework for testing NLP models. 
% Instead of relying on the word-level templates, we transform test case from the real-world dataset into seeds by perturbing it on search-based and enumerative \phs defined on \lc. Next, \tool finds potentially extensive syntactic elements from the seeds by comparing their production rules with the reference corpus. \tool obtains the appropriate the test sentence and test oracle by implementing domain-specific knowledge on the word sentiment and word suggestion model for validating the generated sentence and its oracle.
The goal of this work is to generate a diverse \lc-based test suite automatically.
% Key challenge to achieve the goal is \textit{Consistency}.
% As the semantics of nature language \sents can be greatly changed even by a slight perturbation to the \sents, it is challenging to maintain consistency of test case to the \lc and its label, enhancing diversity of the test case at the same time. To address this difficulty, \tool defines \emph{specifications} (search-based and enumerative seed generation \phs) from \lcs,
% and generates seed test cases by perturbing test cases into the \phs. In addition, \tool validates coherence of \lc specification and test oracles defined by input-output relations determined by the \lc specification.
To achieve the goal, \tool needs to address two requirements:
\textit{(i) Capability-based Generation.} Each test case should be automatically categorized into a \lc;
and \textit{(ii) Automated Test Oracle.} The label of each test case should be automatically
  and accurately defined.

\noindent \textbf{Capability-based text generation.} Whether a test sentence is suitable for evaluating a specific \lc is decided by its relevancy to this
\lc. It is challenging to maintain relevancy between a test sentence and its \lc when generating the test sentence.
This is because the \lc is defined on a specific 
mixture of syntax and semantics of the sentences. Due to the inherent ambiguity of natural language \sents, there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc. Existing metamorphic or adversarial testing~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack,udeshi2019ogma} considers only labels of generated test cases without linguistic capacity guarantee. To address this difficulty, \tool defines \emph{specifications} (search-based and enumerative seed generation \phs) from \lcs,
and generates seed test cases by perturbing test cases into the \phs. In addition, \tool analyzes the parse trees of the seed sentences to identify possible expansion and validates coherence of \lc relevancy between each seed and its expansion.

\noindent \textbf{Automated Test Oracle.}   For NLP model testing, test oracle is usually determined by understanding the semantics of texts, which requires domain knowledge for different NLP tasks \cite{barr2014oracle, nmt_se1, nmt_se2, nmt_se3}.
Thus, the current testing practice requires manual effort to create the test oracles of the \ho data, which is time-consuming. Therefore, it necessitates automated test oracle generation for improving the testing process of NLP models. 
However, automatically generating the  test oracles remains one of the main challenges in NLP testing~\cite{huang2022aeon, nmt_se1, nmt_se2, nmt_se3}. 
Several metamorphic testing approaches have been proposed in image recognition domain, but they require understanding the characteristics of metamorphic relations between inputs and outputs, which require domain expertise and non-trivial manual efforts ~\cite{tian2018deeptest, ma2018deepgauge, pei2017deepxplore, xie2019deephunter, zhang2018deeproad, chen2022deepperform}. 
% \CM{fix} \sw{The only citation for metamorphic testing? We say there are ``several metamorphic testing approaches"}. 
It is even more challenging to design metamorphic relations in textual data because the semantics of nature language \sents can be greatly changed even by a slight perturbation to the \sents. We address the challenge by only accepting validated test oracles defined by input-output relations determined by the \lc specification. 
% \jl{fix}\sw{The last sentence seems broken (I made a slight change). But I don't understand what the ``determined by input-output relations" part means.}

In this work, as a first step, we consider \sa and \hsd as the NLP applications for automated \lc-based testing.
We demonstrate the effectiveness of \tool by evaluating three \sa and two \hsd models.
% We reveal that addressing these requirements contributes to automated test case generation for \lc testing, measured in terms of label and capability consistency in \sents.

% Experiments show that \tool test cases are 
% % \sw{Not clear how we got the 100\% value. Generally, need to double check all the results here after evaluation is finalized.}\jl{comparing \selfbleu and \pdr scores of \tool and \Cklst and \hck shows the smallest ratio (\tool metric/baseline metric) is 0.88 from \selfbleu} 
% at least 88\% more diverse in \selfbleu and \pdr metrics, and \tool finds more failures than the \sota approaches in 21 out of 24 \lcs over the two NLP applications. 
% In addition, we perform a manual study and confirm that \tool test cases are accurately labelled  and categorized into \lcs. Besides, based on an existing explainable ML technique \cite{simin2020denas}, we perform a case study to show that \tool is useful to support understanding the erroneous model behavior.
% % : \Bert~\cite{devlin2019bert},
% % \Roberta~\cite{liu2019roberta} and \Dbert~\cite{sanh2019distilbert}.

\vspace{2pt}
\noindent
In summary, we made the following contributions in this work:

\begin{itemize}[topsep=3pt,itemsep=3pt,partopsep=0ex,parsep=0ex,leftmargin=*]
% \item We design and instantiate formal specifications of 10 and 20 \lcs on \sa and \hsd tasks respectively.
%
\item We design and implement an 
% \sw{do we want to say ``the first"?} 
automated linguistic capability-based testing approach, \tool, capable of producing diverse test cases while performing capability-based text generation using automated test oracle.
%
\item We evaluate text classification models on test cases generated by \tool on 10 and 14 \lcs for \sa and \hsd, respectively. Comparing with the \sota \lc-based testing baselines, we find that \tool produces at least 88\% more diverse test cases, measured in \selfbleu and \pdr, and a larger number of NLP model failures in 21 out of 24 \lcs over the two NLP applications.
We also analyze the root causes of the misclassifications, and find that seeds and expanded test cases produced by \tool are useful in helping developers understand bugs in the model. 
% \sw{Quite some redundancy in this paragraph with the paragraph before ``We made the following contributions ...". I did not address this because I think we need to know the final results before deciding what to write here and there.}
%
\item We perform a manual study and confirm that \tool test cases are accurately labelled  and categorized into \lcs. 
\end{itemize}

### 2023-03-16 paper/icse24/macros.tex
icse24

%%% macros.tex
%%% Import packages, define utility commands and define macros
%%% Version 1.2.0

%%%----------
%%% Imports

%%% Text Formatting
% \usepackage{cite}
% \usepackage{amssymb}
% \usepackage{amsfonts} 
% \usepackage{amsmath}
\usepackage[compact]{titlesec}
\usepackage[noend]{algorithmic}
\usepackage{textcomp}
\usepackage{microtype}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage[normalem]{ulem} % normalem do not replace \emph to underline
\usepackage{breakcites}
\usepackage{enumitem}
\usepackage{adjustbox}

%%% Reference, Citation and Link
\usepackage{hyperref}
%\usepackage{url}
\usepackage{breakurl}
%\usepackage{cite}

%%% Tables
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{ragged2e}

%%% Plots
\usepackage{caption}
%\usepackage{subcaption}
%\usepackage{subfloat}
%\usepackage{wrapfig}
\usepackage{subfig}

% Code
\usepackage{algorithm}
% \usepackage{algpseudocode} 
\usepackage{listings}

% Tikz Figs
\usepackage{tikz}
%\usepackage{pgf-umlsd} % for flow diagram
\usetikzlibrary{calc}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{positioning}
%\usetikzlibrary{shapes}

%%% Miscellaneous
%\usepackage{flushend} % balance the end of double column document
\usepackage{datetime} % for getting current date time

\input{defs-logic} % for logic symbols
\input{defs-code} % for code listings

%%%----------
%%% Utility Commands
\newcommand{\Cong}[1]{\textbf{\color{blue}Cong:{ #1} }}

\newcommand{\XSpace}[1]{}
\newcommand{\XComment}[1]{}
\newcommand{\Fix}[1]{\textcolor{red}{#1}}
%\newcommand{\CR}[2]{\textcolor{blue}{#1}\textcolor{brown}{\sout{#2}}}
\newcommand{\CR}[2]{#1}
\newcommand{\EditAdd}[1]{\textcolor{green}{[#1]}}
\newcommand{\EditRm}[1]{\textcolor{red}{[\sout{#1}]}}
\newcommand{\EditMod}[2]{\textcolor{red}{[\sout{#1}]}\textcolor{green}{[#2]}}
\newcommand{\DefMacro}[2]{\expandafter\newcommand\csname rmk-#1\endcsname{#2}}
\newcommand{\UseMacro}[1]{\csname rmk-#1\endcsname}
\newcommand{\AlgCompTableVSpace}{-5pt}
\newcommand{\CfgStmtTableCaptionVSpace}{-5pt}
\newcommand{\ResultTableCaptionVSpace}{-5pt}
\newcommand{\ReqTableVSpace}{-5pt}
\newcommand{\HsdReqTableVSpace}{-5pt}
\newcommand{\SelfBleuTableVSpace}{-5pt}
\newcommand{\RetrainDebugTableVSpace}{-5pt}
\newcommand{\TestResultsTableVSpace}{-5pt}
\newcommand{\ManualStudyTableVSpace}{-5pt}
\newcommand{\MtnlpCompTableVSpace}{-5pt}
\newcommand{\AdvCompTableVSpace}{-15pt}

\newcommand{\romnum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

\newcommand{\jl}[1]{\textcolor{teal}{JL: #1}}
\newcommand{\sw}[1]{\textcolor{purple}{Shiyi: #1}}
\newcommand{\wy}[1]{\textcolor{blue}{WY: #1}}
\newcommand{\CM}[1]{\textcolor{blue}{Simin: #1}}
\newcommand{\TODO}[1]{\textcolor{red}{TODO: #1}}

\newcommand{\MyPara}[1]{\vspace{0pt}\noindent\textbf{#1}.}
\newcommand{\MyParaOnly}[1]{\noindent\textbf{#1}}
\newcommand{\reducedstrut}{\vrule width 0pt height .9\ht\strutbox depth .9\dp\strutbox\relax}
\newcommand{\InputWithSpace}[1]{\bgroup\def\arraystretch{1.2}\input{#1}\egroup}
\newcommand{\Code}[1]{{\ifmmode{\mathtt{#1}}\else$\mathtt{#1}$\fi}}
\newcommand{\CodeIn}[1]{{\ifmmode{\mathtt{#1}}\else$\mathtt{#1}$\fi}}
\newcommand{\ColorBack}[1]{%
  \begingroup
  \setlength{\fboxsep}{0pt}%
  \colorbox{purple!20}{\reducedstrut#1\/}%
  \endgroup
}

% for table headers
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}
\def\clap#1{\hbox to 0pt{\hss#1\hss}}

%%% TEXT
\newcommand{\Title}{Programming Language Representation with Semantic-level Structure}

\newcommand{\TreeSitterURL}{https://github.com/tree-sitter/tree-sitter}
\newcommand{\Dxp}{DeepXplore}
\newcommand{\Denas}{DENAS}

\newcommand{\tool}{S$^2$LCT\xspace}

% Sorted alphabetically, ignoring case
\newcommand{\Model}{Auto-CHECKLIST\xspace}
\newcommand{\Lc}{Linguistic capability\xspace}
\newcommand{\lc}{linguistic capability\xspace}
\newcommand{\lcs}{linguistic capabilities\xspace}
\newcommand{\Cfg}{Context-free grammar\xspace}
\newcommand{\cfg}{context-free grammar\xspace}
\newcommand{\Pcfg}{Probabilistic context-free grammar\xspace}
\newcommand{\pcfg}{probabilistic context-free grammar\xspace}
\newcommand{\lm}{langugae model\xspace}
\newcommand{\lms}{langugae models\xspace}
\newcommand{\Lm}{Langugae Model\xspace}
\newcommand{\dl}{deep learning\xspace}
\newcommand{\Dl}{Deep Learning\xspace}
\newcommand{\Hsd}{Hate speech detection\xspace}
\newcommand{\hsd}{hate speech detection\xspace}
\newcommand{\ml}{machine learning\xspace}
\newcommand{\ML}{Machine Learning\xspace}
\newcommand{\nl}{natural language\xspace}
\newcommand{\Nl}{Natural language\xspace}
\newcommand{\nlp}{natural language processing\xspace}
\newcommand{\Nlp}{Natural language processing\xspace}
\newcommand{\Sa}{Sentiment analysis\xspace}
\newcommand{\sa}{sentiment analysis\xspace}
\newcommand{\se}{software engineering\xspace}
\newcommand{\Se}{Software Engineering\xspace}
\newcommand{\sota}{state-of-the-art\xspace}
\newcommand{\sent}{sentence\xspace}
\newcommand{\sents}{sentences\xspace}
\newcommand{\Sent}{Sentence\xspace}
%\newcommand{\Sw}{Software\xspace}
%\newcommand{\sw}{software\xspace}
\newcommand{\pos}{part-of-speech\xspace}
\newcommand{\ho}{holdout\xspace}
\newcommand{\ie}{i.e.\xspace}
\newcommand{\eg}{e.g.\xspace}
\newcommand{\etal}{et al.\xspace}

\newcommand{\Req}{Requirement\xspace}
\newcommand{\req}{requirement\xspace}
\newcommand{\Prodr}{Production rule\xspace}
\newcommand{\prodr}{production rule\xspace}
\newcommand{\prodrs}{production rules\xspace}
\newcommand{\lhs}{left-hand side\xspace}
\newcommand{\rhs}{right-hand side\xspace}
\newcommand{\mask}{\{MASK\}}
\newcommand{\SareqExOne}{``Short sentences with neutral adjectives and nouns''\xspace}
\newcommand{\SareqExTwo}{``Negated positive with neutral content in the middle''\xspace}
\newcommand{\reqs}{requirements\xspace}
\newcommand{\bl}{baseline\xspace}
\newcommand{\Bl}{Baseline\xspace}
\newcommand{\bls}{baselines\xspace}
\newcommand{\Bls}{Baselines\xspace}
\newcommand{\Pstv}{Positive\xspace}
\newcommand{\pstv}{positive\xspace}
\newcommand{\Neu}{Neutral\xspace}
\newcommand{\neu}{neutral\xspace}
\newcommand{\Ngtv}{Negative\xspace}
\newcommand{\ngtv}{negative\xspace}
\newcommand{\Noun}{Noun\xspace}
\newcommand{\noun}{noun\xspace}
\newcommand{\nns}{nouns\xspace}
\newcommand{\Vb}{Verb\xspace}
\newcommand{\vb}{verb\xspace}
\newcommand{\vbs}{verbs\xspace}
\newcommand{\Adj}{Adjective\xspace}
\newcommand{\adj}{adjective\xspace}
\newcommand{\adjs}{adjectives\xspace}
\newcommand{\bleu}{BLEU\xspace}
\newcommand{\ph}{non-terminal\xspace}
\newcommand{\phs}{non-terminals\xspace}
\newcommand{\Ph}{Non-terminal\xspace}
\newcommand{\Phs}{Non-terminals\xspace}
\newcommand{\selfbleu}{Self-BLEU\xspace}
\newcommand{\Pdr}{Production Rule Coverage\xspace}
\newcommand{\pdr}{production rule coverage\xspace}

\newcommand{\Nn}{neural network\xspace}
\newcommand{\nn}{neural network\xspace}
\newcommand{\Bert}{BERT-base\xspace}
\newcommand{\BertAcc}{92.43\%\xspace}
\newcommand{\Roberta}{RoBERTa-base\xspace}
\newcommand{\RobertaAcc}{94.04\%\xspace}
\newcommand{\Dbert}{DistilBERT-base\xspace}
\newcommand{\DbertAcc}{91.3\%\xspace}
\newcommand{\hsdBert}{dehate-BERT\xspace}
\newcommand{\hsdRoBerta}{tweeter-RoBERTa\xspace}
\newcommand{\Cklst}{CHECKLIST\xspace}
\newcommand{\hck}{Hatecheck\xspace}
\newcommand{\mtnlp}{MT-NLP\xspace}
\newcommand{\Trb}{Treebank\xspace}
\newcommand{\trb}{treebank\xspace}
\newcommand{\Wsj}{Wall Street Journal\xspace}
\newcommand{\Nltk}{NLTK\xspace}
\newcommand{\Spacy}{Spacy\xspace}
\newcommand{\Wrdnt}{WordNet\xspace}
\newcommand{\Swn}{SentiWordNet\xspace}
\newcommand{\Sst}{SST\xspace}
\newcommand{\Hatexp}{HateXplain\xspace}
\newcommand{\spacy}{SpaCy\xspace}
\newcommand{\bertsamodel}{textattack/bert-base-uncased-SST-2\xspace}
\newcommand{\robertasamodel}{textattack/bert-base-uncased-SST-2\xspace}
\newcommand{\disbertsamodel}{distilbert-base-uncased\xspace}
\newcommand{\berthsdmodel}{Hate-speech-CNERG/dehatebert-mono-english\xspace}
\newcommand{\robertahsdmodel}{cardiffnlp/twitter-roberta-base-hate\xspace}
\newcommand{\Ptf}{Pass-to-Fail\xspace}

%% Table
\newcommand{\tStatement}{\textbf{Statement Types}}
\newcommand{\tModel}{\textbf{Models}}
\newcommand{\tMetric}{\textbf{Metrics}}
\newcommand{\tLc}{\textbf{Linguistic capability}}
\newcommand{\tRules}{\textbf{Search rule and transformation template}}
\newcommand{\tOurNumData}{\textbf{\sharp~Data (\tool)}}
\newcommand{\tChecklistNumData}{\textbf{\sharp~Data (\Cklst)}}
\newcommand{\tOurSelfBleuScore}{\textbf{\selfbleu score (\tool)}}
\newcommand{\tChecklistSelfBleuScore}{\textbf{\selfbleu score (\Cklst)}}
\newcommand{\tApproach}{\textbf{Approach}}
\newcommand{\tRetrainlc}{\textbf{RetrainLC}}
\newcommand{\tEvallc}{\textbf{EvalLC}}
\newcommand{\tNumfailpass}{\textbf{\#Fail2Pass}}
\newcommand{\tNumfailbeforeretrain}{\textbf{\#Fail(BeforeRetrain)}}
\newcommand{\tNumpassbeforeretrain}{\textbf{\#Pass(BeforeRetrain)}}
\newcommand{\tNumfailafterretrain}{\textbf{\#Fail(AfterRetrain)}}
\newcommand{\tNumpassafterretrain}{\textbf{\#Pass(AfterRetrain)}}
\newcommand{\tTask}{\textbf{Task}}
\newcommand{\tSentType}{\textbf{Type}}
\newcommand{\tNumTestCases}{\textbf{\#TC}}
\newcommand{\tAvgLabelCons}{\textbf{LabelCons}}
\newcommand{\tAvgLCRel}{\textbf{LCRel}}
\newcommand{\tAvgExpVal}{\textbf{ExpValidity}}
\newcommand{\tNumBlSents}{\textbf{Cklst \#TCs}}
\newcommand{\tNumBlFail}{\textbf{Cklst \#Fails[\%]}}
\newcommand{\tNumBlTcs}{\textbf{Cklst \#TCs}}
\newcommand{\tNumSeeds}{\textbf{\tool\#Seeds}}
\newcommand{\tNumExps}{\textbf{\tool\#Exps}}
\newcommand{\tNumFail}{\textbf{\tool/Cklst \#Fail}}
\newcommand{\tFailRate}{\textbf{\tool/Cklst Fail rate[\%]}}
\newcommand{\tNumPasstoFail}{\textbf{\tool\#PassToFail}}
\newcommand{\tNumHsBlTcs}{\textbf{Htck \#TCs}}
\newcommand{\tNumHsFail}{\textbf{\tool/Htck \#Fail}}
\newcommand{\tHsFailRate}{\textbf{\tool/Htck Fail rate[\%]}}
\newcommand{\tNummut}{\textbf{\#Gen}}
\newcommand{\tSelfbleu}{\textbf{\selfbleu}}
\newcommand{\tPdrcov}{\textbf{PDRCov}}

%% Fig Caption
\newcommand{\OverviewFigCaption}{Overview of \tool.\label{fig:overview}\vspace{-5pt}}
\newcommand{\SearchRequirementExampleFigCaption}{Search requirement
on the linguistic capability of \SareqExOne.\label{fig:SearchReqEx}\vspace{-5pt}}
\newcommand{\TransformRequirementExampleSubFigCaption}{Transform requirement.\label{fig:TransformReqSubEx}\vspace{-5pt}}
\newcommand{\TransformTemplateExampleSubFigCaption}{Transform template.\label{fig:TransformTempSubEx}\vspace{-5pt}}
\newcommand{\TransformRequirementExampleFigCaption}{Transform
requirement (\ref{fig:TransformReqSubEx}) and its template
(\ref{fig:TransformTempSubEx}) on the linguistic capability of \SareqExTwo.\label{fig:TransformReqEx}\vspace{-5pt}}
\newcommand{\ProdDiffAlgCaption}{Pseudocode of Production differentiation\label{code:ProdDiffAlg}\vspace{-5pt}}
\newcommand{\RunningExCaption}{Example of sentence expansion.\label{fig:ExpEx}\vspace{-5pt}}
\newcommand{\CklstTemplateFigCaption}{
% Example of \Cklst templates on the \lc of \SareqExThree.
Example of CHECKLIST template\label{code:TempEx}\vspace{-5pt}}
\newcommand{\PdrSelfbleuFigCaption}{Results of \selfbleu(left) and \Pdr(right) of \tool and capability-based testing baselines for \sa (SA) and \hsd (HS). Use of only \tool seed \sents and all \tool \sents are denoted as SEED and SEED+EXP respectively.\label{fig:PdrSelfbleu}\vspace{-10pt}}
% \newcommand{\PdrBarplotFigCaption}{Results of \pdr between \tool (seed and expanded cases) and \Cklst test cases for \sa.\label{fig:PdrBarplot}\vspace{-5pt}}
\newcommand{\PdrSelfbleuBarplotFigCaption}{Results of \selfbleu(left) and \Pdr(right) between original \sents of capability-based testing baselines and \tool generated \sents from the original \sents.\label{fig:PdrSelfbleuBarplot}\vspace{-5pt}}
% \newcommand{\PdrBarplotHsFigCaption}{Results of \pdr between \tool (seed and expanded cases) and \Cklst test cases for \hsd.\label{fig:HsPdrBarplot}\vspace{-5pt}}
\newcommand{\PdrBarplotHsFigCaption}{Results of \pdr between \tool (\hck and its expanded cases) and \hck test cases for \hsd.\label{fig:HsPdrBarplot}\vspace{-5pt}}
\newcommand{\SelfbleuBarplotFigCaption}{Results of \selfbleu between \tool (\Cklst and its expanded cases) and \Cklst test cases for \sa.\label{fig:SbBarplot}\vspace{-5pt}}
\newcommand{\SelfbleuBarplotHsFigCaption}{Results of \selfbleu between \tool (\hck and its expanded cases) and \hck test cases for \hsd.\label{fig:HsSbBarplot}\vspace{-5pt}}
\newcommand{\PdrFigCaption}{Results of \pdr between \tool (seed and expanded cases) and \Cklst.\label{fig:Pdr}\vspace{-5pt}}

\newcommand{\NumFailModelsSubFigCaption}{Number of fail cases from \tool test cases over numbers of seeds.\label{fig:NumFail}\vspace{-5pt}}
\newcommand{\FailRateModelsSubFigCaption}{Number of Pass-to-Fail cases from \tool test cases over numbers of seeds.\label{fig:FailRate}\vspace{-5pt}}
\newcommand{\FailModelsFigCaption}{Number of failure (left) and \Ptf(right) results of NLP models on \tool and \Cklst test cases over numbers of seeds.\label{fig:FailModels}\vspace{-5pt}}

\newcommand{\SareqExThree}{``Sentiment change over time, present should prevail"}

%% Table Caption
\newcommand{\ReqTableCaption}{Search-based and enumerate predicates for two linguistic
capabilities of \sa task.\label{tab:specification}\vspace{\ReqTableVSpace}}
\newcommand{\HsdReqTableCaption}{Search rules and transformation
templates for linguistic
capabilities of \hsd task. The \textit{slur}, \textit{profanity} in LC7-LC10 are the collections of terms that express slur and profanity. The \textit{identity} in and LC11-LC12 and LC17-18 is a list of names that used to describe social groups. In this work, we use the terms obtained from \hck~\cite{rottger2020hatecheck}.  \label{tab:hsd-specification}\vspace{\HsdReqTableVSpace}}
\newcommand{\ResultTableCaption}{Results on \Nlp tasks
of \Ccd, \Ctr, \Cref respectively.\label{table:Result}\vspace{-5pt}}
\newcommand{\SelfBleuTableCaption}{\selfbleu scores over testcases
from \tool and \Cklst}
\newcommand{\RetrainDebugTableCaption}{Result of retraining on
each \lc and the evaluation of the retrained model.\label{table:RetrainDebug}}
\newcommand{\ManualStudyTableCaption}{
Consistency Results
% Manual
% study results of label consistency, \lc relevancy and expansion validity of \tool 
% test cases.
% compared to human annotations for \sa and \hsd. \Sa and \hsd are denoted as SA and HSD respectively.
\label{table:ManualStudy}}
\newcommand{\TestResultsTableCaption}{Results of \Bert, \Roberta and
\Dbert \sa models on \tool test cases using 50 seeds. \Bert, \Roberta and
\Dbert models are denoted as BERT, RoBERTa and dstBERT, respectively.\label{table:TestResult}}
\newcommand{\TestResultsAllTableCaption}{Results of \Bert, \Roberta and
\Dbert \sa models on \tool test cases using all seeds. \Bert, \Roberta and
\Dbert models are denoted as BERT, RoBERTa and dstBERT, respectively.\label{table:TestResultAll}}
\newcommand{\TestResultsHsTableCaption}{Results of \hsdBert and \hsdRoBerta \hsd models on \tool test cases using all seeds. \hsdBert and \hsdRoBerta are denoted as BERT, RoBERTa respectively.\label{table:TestResultHsd}}
\newcommand{\MtnlpCompTableCaption}{Results of \sent generation from 100 seeds using \mtnlp and \tool expansion phase.
%using  100 sample size over 5 trials. \Sa and \hsd are denoted as SA and HSD respectively. The number of generated sentences, \selfbleu and \pdr are denoted as \tNummut, \selfbleu and PDRCov respectively. 
\label{table:MtnlpComp}}

\newcommand{\AdvCompTableCaption}{Results of \sent generation from 50 seeds using \tool expansion and adversarial text generation \bls. 
% and  using 50 \sa seeds, statistics of \selfbleu and \pdr using 50 sample size over 5 trials. The number of generated sentences, \selfbleu and \pdr are denoted as \tNummut, \selfbleu and PDRCov respectively. 
\label{table:AdvComp}}

%%% NUMBRERS
\input{tables/lc-requirement-numbers}
\input{tables/lc-hsd-requirement-numbers}
%% \input{tables/selfbleu-numbers}
%% \input{tables/retrain-debug-numbers}
\input{tables/manual-study-numbers}
\input{tables/test-results-numbers}
\input{tables/test-results-3-50-numbers}
\input{tables/test-results-3-100-numbers}
\input{tables/test-results-3-200-numbers}
\input{tables/test-results-all-numbers}
\input{tables/test-results-hs-all-numbers}
\input{tables/mtnlp-comp-numbers}
\input{tables/adv-comp-numbers}

### 2023-03-16 paper/icse24/related.tex
icse24

\section{Related Work}

In addition to the capability-based testing works discussed in Section \ref{sec:background}, we review other related works in this section.

% In addition to the existing capability-based testing works that are discussed in Section \ref{sec:background}, our work is related to works that (1) present new metrics and methodologies for NLP testing, (2) automated text augmentation, and (3) explanation and debugging of NLP model results.

\MyPara{NLP Algorithms \& Applications} Deep neural networks (DNNs) have significantly improved various natural language processing (NLP) applications \cite{mikolov2013efficient, sutskever2014sequence, vaswani2017attention, devlin2018bert, radford2018improving, gehring2017convolutional, pennington2014glove, joulin2016bag, schuster1997bidirectional, chen2022nicgslowdown}, including reading comprehension, hate speech detection, and machine translation.
For instance, Word2vec \cite{mikolov2013efficient} distributes the semantic of words into numeric vectors, which are then utilized to train neural networks for classification tasks. 
Meanwhile, Seq2Seq \cite{sutskever2014sequence} presents an encoder-decoder neural network architecture that has been widely adopted for modeling the sequence generation task, particularly in machine translation applications.
In recent years, Google \cite{vaswani2017attention} has introduced the attention mechanism, which, when combined with Seq2Seq, can greatly enhance the accuracy of the generated texts.

\MyPara{Machine Learning Testing \& NLP Testing} Machine learning has shown great potential in various real-world applications. Nonetheless, despite the high accuracy rates of ML models, there have been instances where ML models can generate inferior results, leading to fatal accidents \cite{lambert2016understanding, levin2018tesla}. Therefore, researchers have developed a series of techniques \cite{pei2017deepxplore, tian2018deeptest, ma2018deepgauge, hendrycks2021natural, du2019deepstellar, gambi2019automatically, kim2019guiding, ma2018deepmutation, pham2019cradle, xie2019deephunter, chen2022nicgslowdown, zhang2020machine, chen2022deepperform, token_nlp2, character_nlp1, character_nlp2, character_nlp3, nmt_se4} to test ML-based applications. 
% For example, DeepXplore \cite{pei2017deepxplore} developed a differential testing framework to generate test inputs that can expose inconsistencies between multiple (ML) models, and they introduced neuron coverage as a metric to measure the diversity of the generated test suite.
% Along this direction, DeepRoad \cite{zhang2018deeproad} proposed a GAN-based method for automatically transforming the style of scenes for testing autonomous driving systems. 
%Meanwhile, DeepGauge \cite{ma2018deepgauge} proposed several neuron coverage metrics to test ML models at multiple levels of granularity.
In recent years, researchers have investigated the occurrence of bugs produced by neural networks in NLP applications \cite{nmt_se1, nmt_se2, nmt_se3, token_nlp3, token_nlp1, token_nlp2, character_nlp1, character_nlp2, character_nlp3, nmt_se4, li2018textbugger, morris2020textattack, chen2022nmtsloth, sentence_nlp1, maIJCAI2020mtnlp}, inspired by the work on adversarial examples in computer vision.
% TestBugger \cite{li2018textbugger} proposes a gradient-guided approach to generate test inputs for identifying bugs in NLP models used for classification tasks, while SIT \cite{pinjia2020structinvtestingnmt} proposes a method to detect errors in neural machine translation (NMT) systems by constructing the structure invariant as an oracle. 
% In contrast, NMTSloth \cite{chen2022nmtsloth} focuses on generating test inputs that can expose performance bugs in NMT systems.
Our approach differs from existing work in that we concentrate on  testing the linguistic capabilities of NLP applications in an automatic manner, a topic that has yet to be explored.

% \MyPara{Linguistic Capability Evaluation} 
% \sw{This paragraph (1) is incomplete (missing hatecheck), and (2) may not be necessary (the intro/motivation should have already covered these). So I suggest removing this paragraph but make sure these works (including hatecheck) have been well discussed in intro/motivation sections.} 
% Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} proposed
% multiple diagnostic datasets to evaluate NLP models 
% % . These datasets
% % evaluate NLP model's ability to understand input sentence
% via natural language inference problems. More recently, \Cklst proposed an evaluation
% method of input-output behavior defined as \lcs. \Cklst generates
% behavior-guided inputs for validating the
% behaviors.~\cite{marcoACL2020checklist}. Unlike prior work that relies on manual
% test case generation, we used structural information in text to
% generate test cases automatically.

### 2023-03-16 paper/icse24/related_old.tex
icse24

--- 2023-01-13 paper/fse23/related.tex
@@
 \section{Related Work}
+
+To the best of our knowledge, \tool is the first approach that automatically generates test cases for linguistic capability testing of NLP models.
+In addition to the existing capability-based testing works that are discussed in Section \ref{sec:background}, our work is related to works that (1) present new metrics and methodologies for NLP testing, (2) automated text augmentation, and (3) explanation and debugging of NLP model results.
 
@@
 scheme, recent works have considered model robustness as an
-aspect for evaluation. Belinkov and Bisk
+aspect for evaluation.
+An important line of work is to perform adversarial attacks.
+Belinkov and Bisk
 \textit{\etal}~\cite{belinkov2018breaknmt} aimed to fail Neural Machine
@@
 
-In addition to the
-robustness on adversarial set, various other aspects of the NLP model have been
-considered for the robustness evaluation. Prabhakaran
+In addition, Prabhakaran
 \textit{\etal}~\cite{prabhakaran2019fairness} developed an evaluation
@@
 \textit{\etal}~\cite{ribeiro2019consistencyeval} measured logical
-consistency of NLP model. However, in this work, we focused on the model evaluation over multiple perspectives and produced debugging information by comparing seed and expanded test cases.
+consistency of NLP model. In this work, we focused on the evaluation over 
+multiple linguistic capabilities; \tool also produced information useful for debugging by comparing the seed and expanded test cases.
 
 \MyPara{Text Generation}
-%
-Different data augmentation approaches have been proposed for text
-generation. One of methods in this category is easy data augmentation
-(EDA)~\cite{weizou2019eda}. It uses simple operations such as synonym
-replacement and random swap. Coulombe~\cite{coulombe2018textaugapi}
-implements rule-based transformations using regular expressions for
-text transformations such as insertion of spelling mistakes, data
-alterations, entity names, and abbreviations. Mixup interpolation,
-which was introduced in computer vision category, was implemented in
-text domain~\cite{hongyu2019dataaugmixup}. Learning-based language
-models has been used to generate text data for multiple
-tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}. While these
-approaches focus on obtaining synthetic training data, not testing NLP
-model over \lcs,
-% they are not able to be used for the capability testing of the NLP model, 
-our work generates text data for testing NLP model over \lcs.  In
-addition, text generation methods has been used for attacking NLP
-model~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack}.
-Morris \textit{\etal}~\cite{morris2020textattack} transform input text
-by leveraging existing methods such as insertion, deletion and swap of
-word/character within the similarity-based
+\sw{I don't understand what we mean by ``text generation" and how it differs from the works in the ``NLP testing" cateogry.}
+Different data augmentation \sw{what does data augmentation mean? Has this phrase been used in describing our approach?} approaches have been proposed for text generation. 
+One approach is called easy data augmentation (EDA)~\cite{weizou2019eda},
+which applies simple operations such as synonym replacement and random swap. 
+Coulombe~\cite{coulombe2018textaugapi} implements rule-based transformations using regular
+expressions for text transformations such as insertion of spelling mistakes, 
+data alterations, entity names, and abbreviations. Mixup interpolation, which was originally introduced 
+for computer vision, was implemented for text augmentation~\cite{hongyu2019dataaugmixup}. 
+Learning-based language models have also been used to generate text data for multiple tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}.
+While these approaches focus on obtaining synthetic testing data, our work generates text data for testing NLP model over \lcs.
+\sw{The related work overall is written vaguely.
+Each citation was described in one sentence which does not help understand the difference from our work.
+More importantly, the contrast we make in the last sentence is very vague and I am not sure if these are accurate.
+E.g., we used a few adversarial approaches and syntax-based approach as baselines in our evaluation, there is no discussion how they are similar and differ from our work; I am not even sure which citations are these works.}
+
+Text generation methods have been used for attacking NLP model. \sw{How does the line of work differ from the first paragraph in ``NLP Testing"?}
+%~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack}. 
+Morris \textit{\etal}~\cite{morris2020textattack} provide a framework for
+transforming input text by leveraging existing methods such as insertion,
+deletion and swap of word/character within the similarity-based
 constraints. Zang \textit{\etal}~\cite{zang2020sememepso} finds
@@
 substitutes word in an input text with its neighboring words in
-embedding space that fools an NLP
-model. Linyang \textit{\etal}~\cite{linyang2020bertattack} generates
-word substitutes with BERT predicted words for attacking an NLP
-model. Also, Grammar-based text generation has been also
-introduced~\cite{udeshi2019ogma,soremekun2020astraea,maIJCAI2020mtnlp}.
+embedding space that fools an NLP model. Linyang \textit{\etal}~\cite{linyang2020bertattack} 
+generates word substitutes with BERT predicted words for attacking an NLP model. 
+In addition, grammar-based text generation has been introduced~\cite{udeshi2019ogma,soremekun2020astraea,maIJCAI2020mtnlp}.
 Ogma~\cite{udeshi2019ogma} and Astraea~\cite{soremekun2020astraea}
@@
 expansion that inserts an adjective word before noun besides to
-replacement of analogy word found in embedding space. Our work
-generates text data does not only rely on the word substitution, but
-also changes diverse structures from the input text. In addition, we
-investigate input semantic and syntax to generate text conforming to
-the same context as input text and its corresponding \lc.
+replacement of analogy word found in embedding space. Our syntax-based sentence expansion does not only use word substitution, but
+rather focus on improve the diversity of the sentence structure by expanding the production rules.
+In addition, our linguistic capability specifications ensure high label and linguistic capability consistencies, as demonstrated in the evaluation.
 
 \MyPara{Linguistic Capability Evaluation}
-%
+\sw{This paragraph (1) is incomplete (missing hatecheck), and (2) may not be necessary (the intro/motivation should have already covered these).
+So I suggest removing this paragraph but make sure these works (including hatecheck) have been well discussed in intro/motivation sections.}
 Wang \textit{\etal}~\cite{wang2018glue, wang2019superglue} proposed
@@
 %
-Researchers have been explaining NLP model prediction and
-analyzing it for debugging the model. Ribeiro
-\textit{\etal}~\cite{ribeiroSG16lime} evaluated model prediction guided by human feedback providing relevance scores for words on the model prediction. 
-Interactive error analysis~\cite{wu2019errudite} also has been proposed to evaluate
+Researchers have also tried to explain and debug NLP model results. Ribeiro
+\sw{I don't understand the next sentence.} \textit{\etal}~\cite{ribeiroSG16lime} evaluated model prediction guided by human feedback, providing relevance scores for words on the model prediction. 
+\sw{What is interactive error analysis?} Interactive error analysis~\cite{wu2019errudite} has also been proposed to evaluate
 model robustness. Zylberajch~\cite{zylberajch2021hildif} used influence functions to generate model explanation, and it enables interactive debugging incorporating humans feedback
@@
 model by disabling irrelevant hidden features. In this work, \tool
-is useful for identifying the sources of model failure as shown in RQ4.
+is useful for identifying the sources of model failure as shown in Section \ref{sec:application}. \sw{How is our application relevant to these works though?}
 

### 2023-03-16 paper/icse24/result.tex
icse24

\section{Experimental Results}
\label{sec:result}

This section presents the experimental results and the answers to the RQs. 
More results are available at the \tool repository.\footnote{\href{https://github.com/csresearcher27/s2lct_project}{https://github.com/csresearcher27/s2lct$\_$project}} 
% \sw{@Jaeseong: footnote typically goes after punctuation, without space. I fix these; just wanted to let you know.}

\InputWithSpace{tables/test-results-all-table}
% \InputWithSpace{tables/test-results-table}
% \InputWithSpace{tables/test-results-3-50-table}
% \InputWithSpace{tables/test-results-3-100-table}
% \InputWithSpace{tables/test-results-3-200-table}
\InputWithSpace{tables/test-results-hs-table}

\begin{figure}
    \centering
    \includegraphics[width=0.35\textwidth]{figs/pdr-selfbleu-agg-lc-task-agg-lineplot.eps}
    \vspace{-3mm}
    \caption{\PdrSelfbleuFigCaption}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.3\textwidth]{figs/pdr-selfbleu-ablation-lc-task-agg-barplot.eps}
    \vspace{-3mm}
    \caption{\PdrSelfbleuBarplotFigCaption}
\end{figure}

\InputWithSpace{tables/mtnlp-comp-table}
\InputWithSpace{tables/adv-comp-table}

% \begin{figure}%
%     \centering
%     \includegraphics[width=0.35\textwidth]{figs/pdr-agg-lineplot.eps}
%     \caption{\PdrFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \subfloat[][\centering\SelfbleuFigCaption]{\includegraphics[width=0.35\textwidth]{figs/selfbleu-agg-sample-lineplot.eps}}%
%     \qquad
%     \subfloat[][\centering\PdrFigCaption]{\includegraphics[width=0.35\textwidth]{figs/pdr-agg-lineplot.eps}}
%     \caption{\FailModelsFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \includegraphics[width=0.4\textwidth]{figs/pdr-checklist-barplot.eps}
%     \caption{\PdrBarplotFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \includegraphics[width=0.45\textwidth]{figs/pdr-hatecheck-barplot.eps}
%     \caption{\PdrBarplotHsFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \includegraphics[width=0.4\textwidth]{figs/selfbleu-checklist-barplot.eps}
%     \caption{\SelfbleuBarplotFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \includegraphics[width=0.45\textwidth]{figs/selfbleu-hatecheck-barplot.eps}
%     \caption{\SelfbleuBarplotHsFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \includegraphics[width=0.35\textwidth]{figs/numfail-pass2fail-agg-lineplot.eps}
%     \caption{\FailModelsFigCaption}
% \end{figure}

% \begin{figure}%
%     \centering
%     \subfloat[][\centering\NumFailModelsSubFigCaption]{\includegraphics[width=0.35\textwidth]{figs/numfail-agg-lineplot.eps}}%
%     \qquad
%     \subfloat[][\centering\FailRateModelsSubFigCaption]{\includegraphics[width=0.35\textwidth]{figs/pass2fail-agg-lineplot.eps}}
%     \caption{\FailModelsFigCaption}
% \end{figure}

\subsection{\ref{rq:one}: Diversity}

% Our results show that \emph{\tool generated many test cases that the sentiment analysis models failed to predict the correct labels, and it produced significantly more diverse test cases than \Cklst did.}
Our results show that \emph{\tool produced test suites with significantly more diversity than \bls did.} 
% In this experiment, we show the test case diversity by comparing \selfbleu and \pdr metrics between \tool and capability-based testing \bls. In addition, we show increase in test case diversity by comparing \selfbleu and \pdr metrics between \tool using \Cklst and \hck as seeds and \Cklst and \hck themselves.

\MyPara{\selfbleu and \Pdr} 
Figure~\ref{fig:PdrSelfbleu} compares the \selfbleu and \pdr scores of the test suite generated by \tool in contrast to those of \Cklst and \hck.
The x-axis shows the sizes of the generated test suite, and the y-axis shows the metric scores.
% Median value of \selcbleu scores are computed from randomly sampled seeds over 3 trials for each \lc,
The figure displays the median \selfbleu and \pdr scores over all \lcs and 5 trials on the left and right, respectively. The results show that \tool's test suite is more diverse than the baselines', with significantly lower \pdr scores and significantly higher \selfbleu scores. This highlights the advantages of searching from a real-world dataset rather than relying on limited preset templates. Furthermore, using expanded sentences in \tool leads to lower \selfbleu and higher \pdr scores, demonstrating the syntax-based expansion of \tool improves sentence diversity.

Figure~\ref{fig:PdrSelfbleuBarplot} shows the \selfbleu and \pdr scores of test suites generated by baseline methods and their expanded versions using \tool. The x-axis shows the method name, and the y-axis shows the corresponding scores across all \lcs. The left sub-figure displays the \selfbleu scores, and the right sub-figure shows the \pdr scores. The results indicate that the expanded \Cklst and \hck achieve better \pdr scores than their original versions, demonstrating the effectiveness of \tool's syntax-based expansion module in increasing the diversity of the generated test suite. Additionally, the expanded \Cklst performs worse in terms of \selfbleu scores, while the expanded \hck has comparable scores to its original version.

Table~\ref{table:MtnlpComp} compares \tool's expanded \sents and \mtnlp for 100 randomly selected seeds. The first column lists the NLP task, and the second column displays the approaches for text generation. Columns 3-5 show the number of generated \sents, \selfbleu, and \pdr scores over 5 sampling trials. \tool generates more \sents than \mtnlp for all tasks and has higher \selfbleu and \pdr scores, demonstrating the effectiveness of \tool's syntax expansion in increasing test case diversity. \mtnlp sometimes fails to mutate seed \sents due to the unavailability of suitable human-related words for mutation.

Table~\ref{table:AdvComp} compares \tool-expanded \sents with adversarial text generation baselines from Section~\ref{sec:experiment_bl}. The first column shows the approach type and the second column shows the number of generated \sents using \tool and the baselines from 50 randomly selected seeds. The third and fourth columns show the \selfbleu and \pdr scores over 5 sampling trials. Results show that Alzantot~\etal~\cite{alzantot2018genadvexp} has the lowest \selfbleu scores, whereas \tool expansion achieves the highest scores in the number of generated \sents and \pdr, introducing various syntax components while maintaining text diversity.

% \paragraph*{\Pdr} Right in figure~\ref{fig:PdrSelfbleu} compares \pdr between the \tool seed sentences, \tool seed and expanded sentences, and the \Cklst test cases. The x-axis shows the sizes of random samples of \tool seed sentences, \tool seed and expanded sentences, and \Cklst test cases, and y-axis shows the \pdr scores. Median of the \pdr scores over all \lcs is shown in the right in the figure~\ref{fig:PdrSelfbleu}. The figure \ref{fig:PdrSelfbleu} shows that \tool seed and/or expanded sentences produce significantly higher \pdr scores than \Cklst test cases did. Also, more \tool seeds cover more production rules because of the increase in diversity obtained from more \tool seeds.

% Figure~\ref{fig:PdrBarplot, HsPdrBarplot} compares the \pdr between all \tool seeds and all \Cklst test cases for each \lc. The x-axis shows each one \lc, and the y-axis is the natural logarithmic scale of \pdr for these test cases.
% % \tool test cases are generated from randomly selected 50 seeds, and the median value over 3 trials for each \lc is reported.
% % It is observed that \tool covers significantly higher number of different syntactic production rules than \Cklst for all \lcs.
% We observed that \tool seeds cover significantly higher number of production rules in each \lc than all \Cklst test cases (ranging from 90 for LC1 to 8518 for LC8 for \tool seeds and from 13 for LC1 to 44 for LC3 for \Cklst seeds) in each \lc.
% % (ranging from 4.92 times to 20.38 times higher scores for LC7 and LC6 respectively)

% Overall, the above results show that \tool test cases are significantly more diverse with regards to semantic and syntactic structure than \Cklst.

\input{CM/coverage}

\subsection{\ref{rq:two}: Effectiveness}
Our results show that \emph{\tool generates diverse test cases that expose classification errors in NLP models, outperforming the baselines.}
%Specifically, we compared the testing results of \tool with \Cklst for \sa and \hck for \hsd.

\MyPara{The Number of Test Cases}
Table~\ref{table:TestResultAll} and~\ref{table:TestResultHsd} present the results of our effectiveness metrics defined in Section \ref{sec:metric}.  For all \lcs, \tool generates a significant number of test cases, ranging from 70 on LC1 to 533,575 on LC8.
For LC1, LC2, LC4, and LC5, \tool generates fewer test cases than \Cklst because of the small number of seeds. However, the syntax-based sentence expansion phase generated 51 to 503 test cases. In Table~\ref{table:TestResultHsd}, \tool generates more test cases than \hck for every \lcs except LC11, indicating that \tool is more beneficial in generating a sufficient number of test cases. The results show that \tool generates many test cases in the NLP models that fail to predict the correct labels, providing further qualitative test cases than baselines for finding errors.

\MyPara{Fail Rate and Failed Cases}
Figure~\ref{table:TestResultAll} demonstrates that at least one model introduces a higher number of failed test cases on \tool test cases than \Cklst in 7 \lcs, and at least one model achieves a higher failure rate on \tool than on \Cklst in all other \lcs (ranging from 4.27\% to 99.64\%) except for LC8 and LC9. Additionally, in table~\ref{table:TestResultHsd}, we observe that every \lcs for \hsd has a higher number of failed test cases on \tool test cases than \hck, with the failure rate being higher for at least one model in every \lcs except for LC1 and LC5 (ranging from 1.89\% to 88.89\%). Based on these findings, we can conclude that \tool is more effective in generating test cases to identify  errors.

% \paragraph*{Failed Cases}
% Left in figure~\ref{fig:FailModels} compares the numbers of failed cases between \tool and \Cklst. 
% The x-axis shows the sizes of random samples of \tool seed sentences and CHECKLIST test cases, and y-axis shows the number of failed cases. Median number of failed cases from \sa models over \lcs is shown in left in figure~\ref{fig:FailModels}. We observed that \tool seeds introduce more failed cases than \Cklst test cases, and it shows the higher effectiveness of \tool test cases. In addition, it shows that more \tool seeds presents more failed cases, demonstrating the benefit of using more seeds when resource permits.

\MyPara{\Ptf Cases} We observed that many test cases failed in the expanded set but not in their corresponding seeds (as shown in the last column of Table~\ref{table:TestResultAll} and~\ref{table:TestResultHsd}). This type of error case ranges from 0 to 12,729 for \sa and from 0 to 4,365 for \hsd. These results demonstrate that the syntax-based sentence expansion phase effectively introduces more diverse sentence structures, which can potentially expose errors in NLP models that may not be evident in the original seed test cases.

\InputWithSpace{tables/manual-study-table}

\subsection{\ref{rq:three}:  Consistency}

Table~\ref{table:ManualStudy} shows the results of our consistency study. The first column lists the NLP tasks, and the second column distinguishes between seed and expanded sentences. The third column indicates the number of test cases used. Columns 4-6 present the scores of label consistency, LC relevancy, and expansion validity sentences, respectively. Our analysis shows that \emph{\tool generates test cases with high label consistency}, with scores of 0.83 for both seed and expanded test cases for \sa and 0.80 and 0.79 for seed and expanded cases, respectively, for \hsd, indicating that the test oracles constructed by \tool align with human sentiment labeling most of the time.
Moreover, the results show high expansion validity scores of 1.0 for \sa and 0.97 for \hsd, indicating that the tool effectively preserves the semantic meaning of seed sentences during the expansion process. The \lc relevancy score is presented in column 5 of Table \ref{table:ManualStudy}. The result shows that \emph{\tool generates test cases that are correctly categorized to the corresponding \lcs most of the time}. The \lc relevancy scores for the seed and expanded sentences are 0.92 and 0.84 for \sa and \hsd, respectively, achieving high agreement with human assessment. The fact that the expanded sentences generated by \tool have the same level of \lc relevancy as the seed sentences demonstrates that the syntax-based sentence expansion retains the \lcs.

\section{Application of \tool}
\label{sec:application}
% \item \label{rq:four}: \textbf{Usefulness of Test Inputs.}

In this section, we showcase how \tool can be used in conjunction with explainable ML techniques to assist developers in identifying the root causes of bugs in \sa models.

\begin{figure*}
    \centering
    \includegraphics[width=0.7\textwidth]{figs/explain.pdf}
    \vspace{-4mm}
    \caption{Visualization of the buggy reason of two \tool generated test cases.}
    \label{fig:explain}
\end{figure*}

\MyPara{Experimental Process}
we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input). Still, it is unclear why mutating one token will cause the model to produce misclassified results.
We seek to help developers understand why such mutation will result in the misclassification. 
Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences). Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.

Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
\begin{equation}
    P(f(T(x)) = f(x)) \ge P_{thresh}
    \label{eq:prob}
\end{equation}
To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}. We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$. Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).

\MyPara{Results} We generate a template that dominates the NLP model prediction to assist developers in understanding the false predictions. Figure \ref{fig:explain} shows the generated templates for two randomly selected seeds and their corresponding expanded test inputs.
The first example tests ``sentiments in (question, yes) form'' (LC9), and the second example tests ``negative positive with neutral content in the middle''  (LC7).
The first column shows the seed sentence, the second shows the expanded sentence, and the third shows each token's contribution score. The blue bar indicates the score for seed inputs, whereas the orange bar reflects the score for the expanded sentences.
We highlight the mutated token with yellow background and generated templates with red text.

The results show that after mutating the seed sentence with one token, the token set that dominates the NLP model prediction has changed.
We can trace the root causes to the bias of the training data on the \lc under test; as a result, for the \lc under test, the model has a bias towards positive/negative for certain token sequence patterns. For example, LC9 has a bias toward the token sequence pattern that includes "maybe .... but ... even... yes". Thus, adding the token ``even" to the seed sentence will match one of those biased sequence patterns.
Sentences with such pattern in the training dataset are dominantly positive; thus, the models make the wrong decision on the sentence with ``even'' as positive. 
The visualization of each token's contribution score in the third column confirms our observation. Once ``even'' is added, scores of other tokens such as ``but'' and ``yes'' all change from negative to positive.
To fix the issue for LC9, we need to add more negative training samples with the format of ``maybe . .. but ... even ... yes''.
%he experimental results in Fig. \ref{fig:explain} illustrate that \tool can help developers to understand the buggy reason of the misclassification go no在，

### 2023-03-16 paper/icse24/tables/adv-comp-numbers.tex
icse24

--- 2023-03-16 paper/fse23/tables/adv-comp-numbers.tex
@@
 \DefMacro{adv-comp-sa-alzantot-num-samples}{20}
-\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{0.373}
-\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{0.373}
-\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{0.0}
+\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{\textbf{0.373}}
+\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{\textbf{0.373}}
+\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{\textbf{0.0}}
 \DefMacro{adv-comp-sa-alzantot-pdrcov-med}{170}
@@
 \DefMacro{adv-comp-sa-pso-pdrcov-std}{0.0}
-\DefMacro{adv-comp-sa-ours-num-adv}{323}
+\DefMacro{adv-comp-sa-ours-num-adv}{\textbf{323}}
 \DefMacro{adv-comp-sa-ours-num-samples}{50}
@@
 \DefMacro{adv-comp-sa-ours-selfbleu-std}{0.005}
-\DefMacro{adv-comp-sa-ours-pdrcov-med}{264}
-\DefMacro{adv-comp-sa-ours-pdrcov-avg}{262.0}
-\DefMacro{adv-comp-sa-ours-pdrcov-std}{2.739}
+\DefMacro{adv-comp-sa-ours-pdrcov-med}{\textbf{264}}
+\DefMacro{adv-comp-sa-ours-pdrcov-avg}{\textbf{262.0}}
+\DefMacro{adv-comp-sa-ours-pdrcov-std}{\textbf{2.739}}

### 2023-03-16 paper/icse24/tables/adv-comp-table.tex
icse24

%% Automatically generated by pyutil.latex

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{Comparison results against adversarial attacks}
\label{table:AdvComp}
\vspace{-3mm}
\resizebox{0.35\textwidth}{!}{
\begin{tabular}{l|ccc}
\toprule
\tApproach & \tNummut & \tSelfbleu & \tPdrcov \\
\midrule
 \tool & \UseMacro{adv-comp-sa-ours-num-adv}
 & \UseMacro{adv-comp-sa-ours-selfbleu-avg}$\pm$\UseMacro{adv-comp-sa-ours-selfbleu-std}
 & \UseMacro{adv-comp-sa-ours-pdrcov-avg}$\pm$\UseMacro{adv-comp-sa-ours-pdrcov-std}\\
Alzantot & \UseMacro{adv-comp-sa-alzantot-num-adv}
 & \UseMacro{adv-comp-sa-alzantot-selfbleu-avg}$\pm$\UseMacro{adv-comp-sa-alzantot-selfbleu-std}
 & \UseMacro{adv-comp-sa-alzantot-pdrcov-avg}$\pm$\UseMacro{adv-comp-sa-alzantot-pdrcov-std}\\
BERT-Attack & \UseMacro{adv-comp-sa-bert-attack-num-adv}
 & \UseMacro{adv-comp-sa-bert-attack-selfbleu-avg}$\pm$\UseMacro{adv-comp-sa-bert-attack-selfbleu-std}
 & \UseMacro{adv-comp-sa-bert-attack-pdrcov-avg}$\pm$\UseMacro{adv-comp-sa-bert-attack-pdrcov-std}\\
PSO & \UseMacro{adv-comp-sa-pso-num-adv}
 & \UseMacro{adv-comp-sa-pso-selfbleu-avg}$\pm$\UseMacro{adv-comp-sa-pso-selfbleu-std}
 & \UseMacro{adv-comp-sa-pso-pdrcov-avg}$\pm$\UseMacro{adv-comp-sa-pso-pdrcov-std}\\
\bottomrule
\end{tabular}
}
\end{center}
\end{small}
\vspace{\AdvCompTableVSpace}
\end{table}

### 2023-03-16 paper/icse24/tables/lc-hsd-requirement-numbers.tex
icse24

--- 2023-01-13 paper/fse23/tables/lc-hsd-requirement-numbers.tex
@@
 \DefMacro{hsd_lc_1_desc}{Expression of strong negative emotions (explicit)}
-\DefMacro{hsd_lc_1_search}{\textbf{Search}~hatecheck}
+\DefMacro{hsd_lc_1_search}{\textbf{Search}~\textit{hatecheck}}
 \DefMacro{hsd_lc_1_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_2_desc}{Description using very negative attributes (explicit)}
-\DefMacro{hsd_lc_2_search}{\textbf{Search}~hatecheck}
+\DefMacro{hsd_lc_2_search}{\textbf{Search}~\textit{hatecheck}}
 \DefMacro{hsd_lc_2_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_3_desc}{Dehumanisation (explicit)}
-\DefMacro{hsd_lc_3_search}{\textbf{Search}~hatecheck}
+\DefMacro{hsd_lc_3_search}{\textbf{Search}~\textit{hatecheck}}
 \DefMacro{hsd_lc_3_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_4_desc}{Implicit derogation}
-\DefMacro{hsd_lc_4_search}{\textbf{Search}~hatecheck}
+\DefMacro{hsd_lc_4_search}{\textbf{Search}~\textit{hatecheck}}
 \DefMacro{hsd_lc_4_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_5_desc}{Direct threat}
-\DefMacro{hsd_lc_5_search}{\textbf{Search}~hatecheck}
+\DefMacro{hsd_lc_5_search}{\textbf{Search}~\textit{hatecheck}}
 \DefMacro{hsd_lc_5_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_6_desc}{Threat as normative statement}
-\DefMacro{hsd_lc_6_search}{\textbf{Search}~hatecheck}
+\DefMacro{hsd_lc_6_search}{\textbf{Search}~\textit{hatecheck}}
 \DefMacro{hsd_lc_6_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_7_desc}{Hate expressed using slur}
-\DefMacro{hsd_lc_7_search}{\textbf{Search}~seed=\{include: slur; label: toxic\}}
+\DefMacro{hsd_lc_7_search}{\textbf{Search}~seed=\{include: \textit{slur}; label: toxic\}}
 \DefMacro{hsd_lc_7_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_8_desc}{Non-hateful use of slur}
-\DefMacro{hsd_lc_8_search}{\textbf{Search}~seed=\{include: slur; label: non-toxic\}}
+\DefMacro{hsd_lc_8_search}{\textbf{Search}~seed=\{include: \textit{slur}; label: non-toxic\}}
 \DefMacro{hsd_lc_8_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_9_desc}{Hate expressed using profanity}
-\DefMacro{hsd_lc_9_search}{\textbf{Search}~seed=\{include: profanity; label: toxic\}}
+\DefMacro{hsd_lc_9_search}{\textbf{Search}~seed=\{include: \textit{profanity}; label: toxic\}}
 \DefMacro{hsd_lc_9_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_10_desc}{Non-Hateful use of profanity}
-\DefMacro{hsd_lc_10_search}{\textbf{Search}~seed=\{include: profanity; label: non-toxic\}}
+\DefMacro{hsd_lc_10_search}{\textbf{Search}~seed=\{include: \textit{profanity}; label: non-toxic\}}
 \DefMacro{hsd_lc_10_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_11_desc}{Hate expressed through reference in subsequent clauses}
-\DefMacro{hsd_lc_11_search}{\textbf{Search}~toxic\_sent=\{include: identity; label: toxic\}, non\_toxic\_sent=\{include: identity; label: non-toxic\}}
+\DefMacro{hsd_lc_11_search}{\textbf{Search}~toxic\_sent=\{include: \textit{identity}; label: toxic\}, non\_toxic\_sent=\{include: \textit{identity}; label: non-toxic\}}
 \DefMacro{hsd_lc_11_transform}{\textbf{Transform}~seed=\{['people say', 'I heard that']+[toxic\_sent]+['and']+['i hate them too', 'i also hate them']\} $|$ \{['people say', 'I heard that']+[toxic\_sent]+['but']+['i do not hate them', 'i like them']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['but']+['i hate them', 'i dislike them']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['and']+['i also do not hate them', 'i do not hate them too']\}}
 \DefMacro{hsd_lc_12_desc}{Hate expressed through reference in subsequent sentences}
-\DefMacro{hsd_lc_12_search}{\textbf{Search}~toxic\_sent=\{include: identity; label: toxic\}, non\_toxic\_sent=\{include: identity; label: non-toxic\}}
+\DefMacro{hsd_lc_12_search}{\textbf{Search}~toxic\_sent=\{include: \textit{identity}; label: toxic\}, non\_toxic\_sent=\{include: \textit{identity}; label: non-toxic\}}
 \DefMacro{hsd_lc_12_transform}{\textbf{Transform}~seed=\{['people say', 'I heard that']+[toxic\_sent]+['.']+['i hate them too', 'i also hate them']\} $|$ \{['people say', 'I heard that']+[toxic\_sent]+['.']+['however i do not hate them', 'regardless i like them']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['.']+['however i hate them', 'i dislike them though']\} $|$ \{['people say', 'I heard that']+[non\_toxic\_sent]+['.']+['i also do not hate them', 'i do not hate them too']\}}
@@
 \DefMacro{hsd_lc_17_desc}{Neutral statements using protected group identifiers}
-\DefMacro{hsd_lc_17_search}{\textbf{Search}~seed=\{include: identity; exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns \& pos verbs \& neg verbs; label: non-toxic\}}
+\DefMacro{hsd_lc_17_search}{\textbf{Search}~seed=\{include: \textit{identity}; exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns \& pos verbs \& neg verbs; label: non-toxic\}}
 \DefMacro{hsd_lc_17_transform}{\textbf{Transform}~N/A}
 \DefMacro{hsd_lc_18_desc}{Positive statements using protected group identifiers}
-\DefMacro{hsd_lc_18_search}{\textbf{Search}~seed=\{include: identity; exclude: neg adjs \& neg nouns \& neg verbs; label: non-toxic\}}
+\DefMacro{hsd_lc_18_search}{\textbf{Search}~seed=\{include: \textit{identity}; exclude: neg adjs \& neg nouns \& neg verbs; label: non-toxic\}}
 \DefMacro{hsd_lc_18_transform}{\textbf{Transform}~N/A}

### 2023-03-16 paper/icse24/tables/lc-requirement-numbers.tex
icse24

%% Automatically generated by pyutil.latex

\DefMacro{lc_1_desc}{Short sentences with neutral adjectives and nouns}
\DefMacro{lc_1_search}{\textbf{Search-based:}~\textbf{hasattr}(length,<10)\land
\textbf{hasattr}(label,neutral)\land(\textbf{contain}(tag\_of\_pos,neutral\_adj)\lor
\textbf{contain}(tag\_of\_pos,neutral\_noun))\land~\neg(\textbf{contain}(tag\_of\_pos,positive\_adj)\lor
\textbf{contain}(tag\_of\_pos,positive\_noun)\lor~\textbf{contain}(tag\_of\_pos,negative\_adj)\lor
\textbf{contain}(tag\_of\_pos,negative\_noun))}
\DefMacro{lc_1_transform}{\textbf{Enumerative:}~N/A}
\DefMacro{lc_2_desc}{Short sentences with sentiment-laden adjectives}
\DefMacro{lc_2_search}{\textbf{Search-based:}~\textbf{hasattr}(length,$<$10)$\land$((\textbf{contain}
(pos,positive$\_$adj)$\lor$\textbf{contain}(pos,positive$\_$noun)$\land$\textbf{hasattr}(label,positive))$\lor$(\textbf{contain}(pos,negative$\_$adj)$\lor$\textbf{contain}(pos,negative$\_$noun)$\land$\textbf{hasattr}(label,negative)))}
\DefMacro{lc_2_transform}{\textbf{Enumerative:}~N/A}
\DefMacro{lc_3_desc}{Sentiment change over time, present should prevail}
\DefMacro{lc_3_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,positive), neg\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,negative)}
\DefMacro{lc_3_transform}{
\textbf{Enumerative:}~E1=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(Previously, I used to like it saying that|Last time, I agreed with saying that|I liked it much as to say that), sent=pos\_sent, infix=(but|although|on the other hand), postfix=(now I don't like it.|now I hate it.)

E2=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(I used to disagree with saying that|Last time, I didn't like it saying that|I hated it much as to say that), sent=neg\_sent, infix=(but|although|on the other hand), postfix=(now I like it.)}
\DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
\DefMacro{lc_4_search}{\textbf{Search-based:}~\textbf{hasattr}(word,`(This|That|These|Those)~(is|are)')\land\textbf{hasattr}(label,negative)}
\DefMacro{lc_4_transform}{\textbf{Transform:}~\textbf{replace}(is->is not,isn't'|are->are not,aren't)}
\DefMacro{lc_5_desc}{Negated neutral should still be neutral}
\DefMacro{lc_5_search}{\textbf{Search-based:}~\textbf{hasattr}(word,`(This|That|These|Those)~(is|are)')\land\textbf{hasattr}(label,neutral)}
\DefMacro{lc_5_transform}{\textbf{Transform:}~\textbf{replace}(is->is not,isn't'|are->are not,aren't)}
\DefMacro{lc_6_desc}{Negation of negative at the end, should be positive or neutral}
\DefMacro{lc_6_search}{\textbf{Search-based:}~$neg\_sent\rightarrow\textbf{hasattr}(label,negative)$}
\DefMacro{lc_6_transform}{\textbf{Enumerative:}~\textbf{combine}(prefix,sent,postfix) where prefix=(I agreed that$|$I thought that), sent=neg$\_$sent, postfix=(but it wasn't|but I didn't)}
\DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
\DefMacro{lc_7_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,positive),
neutral\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,neutral)}
\DefMacro{lc_7_transform}{
\textbf{Enumerative:}~\textbf{combine}(prefix,sent,infix,postfix) where prefix=(I$\,$wouldn't$\,$say,|I$\,$do$\,$not$\,$think,|I$\,$don't$\,$agree$\,$with,), sent=neutral\_sent, infix=`,', postfix=pos\_sent}
\DefMacro{lc_8_desc}{Author sentiment is more important than of others}
\DefMacro{lc_8_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(label,positive), neg\_sent\rightarrow\textbf{hasattr}(label,negative)}
\DefMacro{lc_8_transform}{\textbf{Enumerative:}~T1=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(Some people think that|Many people agree with that|They think that|You agree with that), sent=pos\_sent, infix=(but I think that), postfix=neg\_sent,

T2=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(Some people think that|Many people agree with that|They think that|You agree with that), sent=neg\_sent, infix=(but I think that), postfix=pos\_sent}
\DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}
\DefMacro{lc_9_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(label,positive), neg\_sent\rightarrow~\textbf{hasattr}(label,negative)}
\DefMacro{lc_9_transform}{\textbf{Enumerative:}~\textbf{combine}(prefix,sent,postfix) where prefix=(Do I think that|Do I agree that), sent=(pos\_sent|neg\_sent), postfix=`? yes'}
\DefMacro{lc_10_desc}{Parsing sentiment in (question, no) form}
\DefMacro{lc_10_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(label,positive), neg\_sent\rightarrow~\textbf{hasattr}(label,negative)}
\DefMacro{lc_10_transform}{\textbf{Enumerative:}~\textbf{combine}(prefix,sent,postfix) where prefix=(Do I think that|Do I agree that), sent=(pos\_sent|neg\_sent), postfix=`? no'}

### 2023-03-16 paper/icse24/tables/manual-study-numbers.tex
icse24

%% Automatically generated by pyutil.latex

\DefMacro{manual-study-sa-seed-num-sents}{100}
\DefMacro{manual-study-sa-seed-label-consistency}{0.83}
\DefMacro{manual-study-sa-seed-lc-relevancy}{0.92}
\DefMacro{manual-study-sa-seed-validity}{-}
\DefMacro{manual-study-sa-exp-num-sents}{100}
\DefMacro{manual-study-sa-exp-label-consistency}{0.83}
\DefMacro{manual-study-sa-exp-lc-relevancy}{0.92}
\DefMacro{manual-study-sa-exp-validity}{1.00}
\DefMacro{manual-study-hs-seed-num-sents}{100}
\DefMacro{manual-study-hs-seed-label-consistency}{0.80}
\DefMacro{manual-study-hs-seed-lc-relevancy}{0.84}
\DefMacro{manual-study-hs-seed-validity}{-}
\DefMacro{manual-study-hs-exp-num-sents}{100}
\DefMacro{manual-study-hs-exp-label-consistency}{0.79}
\DefMacro{manual-study-hs-exp-lc-relevancy}{0.84}
\DefMacro{manual-study-hs-exp-validity}{0.97}

### 2023-03-16 paper/icse24/tables/model.tex
icse24

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{The NLP model used in our evaluation}
  \vspace{-3mm}
  \resizebox{0.45\textwidth}{!}{
    \begin{tabular}{l|l|l|r}
    \toprule
    \textbf{Tasks} & \textbf{Model Name} & \textbf{API URL} & \multicolumn{1}{l}{\textbf{\#Downloads}} \\
    \midrule
    Semantic Analysis & BERT-base &
    \href{https://huggingface.co/textattack/bert-base-uncased-SST-2}{bert-base-uncased-SST-2} & 109,143 \\
    Semantic Analysis & RoBERTa-base &
    \href{https://huggingface.co/textattack/roberta-base-SST-2}{roberta-base-SST-2} & 6,099 \\
    Semantic Analysis & DistilBERT-base &
    \href{https://huggingface.co/textattack/distilbert-base-uncased-SST-2}{distilbert-base-uncased-SST-2} & 31 \\
    Hate Speech Detection & dehate-BERT & \href{https://huggingface.co/Hate-speech-CNERG/dehatebert-mono-english}{dehatebert-mono-english}  & 1,366 \\
    Hate Speech Detection & twitter-RoBERTa &
    \href{https://huggingface.co/cardiffnlp/twitter-roberta-base-hate}{twitter-roberta-base-hate} & 40,097 \\
    \bottomrule
    \end{tabular}%
    }
  \label{tab:model}%
\end{table}%

### 2023-03-16 paper/icse24/tables/mtnlp-comp-numbers.tex
icse24

%% Automatically generated by pyutil.latex

\DefMacro{mtnlp-comp-sa-ours-selfbleu-num-mutate}{\textbf{606}}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-avg}{\textbf{0.75}}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-med}{\textbf{0.76}}
\DefMacro{mtnlp-comp-sa-ours-selfbleu-std}{\textbf{0.01}}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-num-mutate}{23}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-avg}{0.91}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-med}{0.91}
\DefMacro{mtnlp-comp-sa-mtnlp-selfbleu-std}{0.0}
\DefMacro{mtnlp-comp-sa-ours-pdr-num-mutate}{\textbf{606}}
\DefMacro{mtnlp-comp-sa-ours-pdr-avg}{\textbf{338.8}}
\DefMacro{mtnlp-comp-sa-ours-pdr-med}{\textbf{338}}
\DefMacro{mtnlp-comp-sa-ours-pdr-std}{\textbf{12.03}}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-num-mutate}{23}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-avg}{96.0}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-med}{96}
\DefMacro{mtnlp-comp-sa-mtnlp-pdr-std}{0.0}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-num-mutate}{\textbf{800}}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-avg}{\textbf{0.69}}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-med}{\textbf{0.68}}
\DefMacro{mtnlp-comp-hs-ours-selfbleu-std}{\textbf{0.02}}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-num-mutate}{211}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-avg}{0.79}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-med}{0.78}
\DefMacro{mtnlp-comp-hs-mtnlp-selfbleu-std}{0.02}
\DefMacro{mtnlp-comp-hs-ours-pdr-num-mutate}{\textbf{800}}
\DefMacro{mtnlp-comp-hs-ours-pdr-avg}{\textbf{400.4}}
\DefMacro{mtnlp-comp-hs-ours-pdr-med}{\textbf{392}}
\DefMacro{mtnlp-comp-hs-ours-pdr-std}{\textbf{17.21}}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-num-mutate}{211}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-avg}{344.0}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-med}{348}
\DefMacro{mtnlp-comp-hs-mtnlp-pdr-std}{15.86}

### 2023-03-16 paper/icse24/tables/mtnlp-comp-table.tex
icse24

%% Automatically generated by pyutil.latex

\begin{table}[htbp]
\begin{small}
\begin{center}
\caption{Comparison results against MT-NLP}
\label{table:MtnlpComp}
\vspace{-3mm}
\resizebox{0.35\textwidth}{!}{
\begin{tabular}{l|l|ccc}
\toprule
\tTask & \tApproach & \tNummut & \tSelfbleu & \tPdrcov \\
\midrule
\multirow{2}{*}{SA} 
 & $S^{2}LCT$ & \UseMacro{mtnlp-comp-sa-ours-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-sa-ours-selfbleu-avg}$\pm$
\UseMacro{mtnlp-comp-sa-ours-selfbleu-std}
 & \UseMacro{mtnlp-comp-sa-ours-pdr-avg}$\pm$\UseMacro{mtnlp-comp-sa-ours-pdr-std}\\
 & MT-NLP & \UseMacro{mtnlp-comp-sa-mtnlp-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-sa-mtnlp-selfbleu-avg}$\pm$
\UseMacro{mtnlp-comp-sa-mtnlp-selfbleu-std}
 & \UseMacro{mtnlp-comp-sa-mtnlp-pdr-avg}$\pm$\UseMacro{mtnlp-comp-sa-mtnlp-pdr-std}\\
\hline
\multirow{2}{*}{HSD} 
 & $S^{2}LCT$ & \UseMacro{mtnlp-comp-hs-ours-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-hs-ours-selfbleu-avg}$\pm$
\UseMacro{mtnlp-comp-hs-ours-selfbleu-std}
 & \UseMacro{mtnlp-comp-hs-ours-pdr-avg}$\pm$\UseMacro{mtnlp-comp-hs-ours-pdr-std}\\
 & MT-NLP & \UseMacro{mtnlp-comp-hs-mtnlp-pdr-num-mutate}
 & \UseMacro{mtnlp-comp-hs-mtnlp-selfbleu-avg}$\pm$
\UseMacro{mtnlp-comp-hs-mtnlp-selfbleu-std}
 & \UseMacro{mtnlp-comp-hs-mtnlp-pdr-avg}$\pm$\UseMacro{mtnlp-comp-hs-mtnlp-pdr-std}\\
\bottomrule
\end{tabular}
}
\end{center}
\end{small}
\vspace{\MtnlpCompTableVSpace}
\end{table}

### 2023-03-16 paper/icse24/tables/test-results-all-numbers.tex
icse24

--- 2023-01-17 paper/fse23/tables/test-results-all-numbers.tex
@@
 \DefMacro{test-results-all-lc7-num-seeds}{68,284}
-\DefMacro{test-results-all-lc7-num-exps}{492,817}
+\DefMacro{test-results-all-lc7-num-exps}{465,291}
 \DefMacro{test-results-bl-lc7-num-tcs}{8,528}
-\DefMacro{test-results-all-model0-lc7-num-fail}{158,854}
-\DefMacro{test-results-all-model0-lc7-num-failrate}{28.31}
-\DefMacro{test-results-all-model0-lc7-num-pass-to-fail}{9,748}
+\DefMacro{test-results-all-model0-lc7-num-fail}{152,009}
+\DefMacro{test-results-all-model0-lc7-num-failrate}{28.49}
+\DefMacro{test-results-all-model0-lc7-num-pass-to-fail}{8,878}
 \DefMacro{test-results-bl-model0-lc7-num-fail}{3,741}
@@
 \DefMacro{test-results-all-lc6-num-seeds}{24,328}
-\DefMacro{test-results-all-lc6-num-exps}{190,723}
+\DefMacro{test-results-all-lc6-num-exps}{184,328}
 \DefMacro{test-results-bl-lc6-num-tcs}{1,000}
-\DefMacro{test-results-all-model0-lc6-num-fail}{195,525}
-\DefMacro{test-results-all-model0-lc6-num-failrate}{90.92}
-\DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{2,014}
+\DefMacro{test-results-all-model0-lc6-num-fail}{189,935}
+\DefMacro{test-results-all-model0-lc6-num-failrate}{91.03}
+\DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{1,972}
 \DefMacro{test-results-bl-model0-lc6-num-fail}{860}
@@
 \DefMacro{test-results-all-lc5-num-seeds}{18,576}
-\DefMacro{test-results-all-lc5-num-exps}{102,304}
+\DefMacro{test-results-all-lc5-num-exps}{97,897}
 \DefMacro{test-results-bl-lc5-num-tcs}{2,124}
-\DefMacro{test-results-all-model0-lc5-num-fail}{120,451}
-\DefMacro{test-results-all-model0-lc5-num-failrate}{99.65}
-\DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{71}
+\DefMacro{test-results-all-model0-lc5-num-fail}{116,049}
+\DefMacro{test-results-all-model0-lc5-num-failrate}{99.64}
+\DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{67}
 \DefMacro{test-results-bl-model0-lc5-num-fail}{1,871}
@@
 \DefMacro{test-results-all-lc9-num-seeds}{15,483}
-\DefMacro{test-results-all-lc9-num-exps}{108,412}
+\DefMacro{test-results-all-lc9-num-exps}{102,214}
 \DefMacro{test-results-bl-lc9-num-tcs}{7,644}
-\DefMacro{test-results-all-model0-lc9-num-fail}{93,329}
-\DefMacro{test-results-all-model0-lc9-num-failrate}{75.33}
-\DefMacro{test-results-all-model0-lc9-num-pass-to-fail}{1,891}
+\DefMacro{test-results-all-model0-lc9-num-fail}{89,155}
+\DefMacro{test-results-all-model0-lc9-num-failrate}{75.75}
+\DefMacro{test-results-all-model0-lc9-num-pass-to-fail}{1,722}
 \DefMacro{test-results-bl-model0-lc9-num-fail}{4,056}
@@
 \DefMacro{test-results-all-lc2-num-seeds}{75,159}
-\DefMacro{test-results-all-lc2-num-exps}{507,091}
+\DefMacro{test-results-all-lc2-num-exps}{343,214}
 \DefMacro{test-results-bl-lc2-num-tcs}{8,000}
-\DefMacro{test-results-all-model0-lc2-num-fail}{134,641}
-\DefMacro{test-results-all-model0-lc2-num-failrate}{23.12}
-\DefMacro{test-results-all-model0-lc2-num-pass-to-fail}{18,510}
+\DefMacro{test-results-all-model0-lc2-num-fail}{99,312}
+\DefMacro{test-results-all-model0-lc2-num-failrate}{23.74}
+\DefMacro{test-results-all-model0-lc2-num-pass-to-fail}{10,357}
 \DefMacro{test-results-bl-model0-lc2-num-fail}{1,680}
@@
 \DefMacro{test-results-all-lc8-num-seeds}{15,465}
-\DefMacro{test-results-all-lc8-num-exps}{106,907}
+\DefMacro{test-results-all-lc8-num-exps}{102,203}
 \DefMacro{test-results-bl-lc8-num-tcs}{7,644}
-\DefMacro{test-results-all-model0-lc8-num-fail}{7,361}
-\DefMacro{test-results-all-model0-lc8-num-failrate}{6.02}
-\DefMacro{test-results-all-model0-lc8-num-pass-to-fail}{1,646}
+\DefMacro{test-results-all-model0-lc8-num-fail}{7,097}
+\DefMacro{test-results-all-model0-lc8-num-failrate}{6.03}
+\DefMacro{test-results-all-model0-lc8-num-pass-to-fail}{1,590}
 \DefMacro{test-results-bl-model0-lc8-num-fail}{253}
 \DefMacro{test-results-bl-model0-lc8-num-failrate}{3.31}
-\DefMacro{test-results-all-model1-lc7-num-fail}{112,390}
-\DefMacro{test-results-all-model1-lc7-num-failrate}{20.03}
-\DefMacro{test-results-all-model1-lc7-num-pass-to-fail}{9,453}
-\DefMacro{test-results-bl-model1-lc7-num-fail}{2,692}
-\DefMacro{test-results-bl-model1-lc7-num-failrate}{31.57}
+\DefMacro{test-results-all-model1-lc7-num-fail}{105,152}
+\DefMacro{test-results-all-model1-lc7-num-failrate}{19.71}
+\DefMacro{test-results-all-model1-lc7-num-pass-to-fail}{8,487}
+\DefMacro{test-results-bl-model1-lc7-num-fail}{2,693}
+\DefMacro{test-results-bl-model1-lc7-num-failrate}{31.58}
 \DefMacro{test-results-all-model1-lc3-num-fail}{498}
@@
 \DefMacro{test-results-bl-model1-lc4-num-failrate}{92.31}
-\DefMacro{test-results-all-model1-lc6-num-fail}{157,635}
-\DefMacro{test-results-all-model1-lc6-num-failrate}{73.30}
-\DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,289}
+\DefMacro{test-results-all-model1-lc6-num-fail}{153,686}
+\DefMacro{test-results-all-model1-lc6-num-failrate}{73.66}
+\DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,007}
 \DefMacro{test-results-bl-model1-lc6-num-fail}{416}
 \DefMacro{test-results-bl-model1-lc6-num-failrate}{41.60}
-\DefMacro{test-results-all-model1-lc5-num-fail}{120,054}
+\DefMacro{test-results-all-model1-lc5-num-fail}{115,676}
 \DefMacro{test-results-all-model1-lc5-num-failrate}{99.32}
-\DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{93}
+\DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{90}
 \DefMacro{test-results-bl-model1-lc5-num-fail}{445}
 \DefMacro{test-results-bl-model1-lc5-num-failrate}{20.95}
-\DefMacro{test-results-all-model1-lc9-num-fail}{105,319}
-\DefMacro{test-results-all-model1-lc9-num-failrate}{85.01}
-\DefMacro{test-results-all-model1-lc9-num-pass-to-fail}{1,764}
+\DefMacro{test-results-all-model1-lc9-num-fail}{100,351}
+\DefMacro{test-results-all-model1-lc9-num-failrate}{85.26}
+\DefMacro{test-results-all-model1-lc9-num-pass-to-fail}{1,452}
 \DefMacro{test-results-bl-model1-lc9-num-fail}{4,576}
 \DefMacro{test-results-bl-model1-lc9-num-failrate}{59.86}
-\DefMacro{test-results-all-model1-lc2-num-fail}{283,614}
-\DefMacro{test-results-all-model1-lc2-num-failrate}{48.71}
-\DefMacro{test-results-all-model1-lc2-num-pass-to-fail}{17,142}
+\DefMacro{test-results-all-model1-lc2-num-fail}{208,313}
+\DefMacro{test-results-all-model1-lc2-num-failrate}{49.79}
+\DefMacro{test-results-all-model1-lc2-num-pass-to-fail}{11,472}
 \DefMacro{test-results-bl-model1-lc2-num-fail}{829}
@@
 \DefMacro{test-results-bl-model1-lc1-num-failrate}{1.61}
-\DefMacro{test-results-all-model1-lc8-num-fail}{6,510}
-\DefMacro{test-results-all-model1-lc8-num-failrate}{5.32}
-\DefMacro{test-results-all-model1-lc8-num-pass-to-fail}{1,519}
+\DefMacro{test-results-all-model1-lc8-num-fail}{6,226}
+\DefMacro{test-results-all-model1-lc8-num-failrate}{5.29}
+\DefMacro{test-results-all-model1-lc8-num-pass-to-fail}{1,489}
 \DefMacro{test-results-bl-model1-lc8-num-fail}{32}
 \DefMacro{test-results-bl-model1-lc8-num-failrate}{0.42}
-\DefMacro{test-results-all-model2-lc7-num-fail}{170,198}
-\DefMacro{test-results-all-model2-lc7-num-failrate}{30.33}
-\DefMacro{test-results-all-model2-lc7-num-pass-to-fail}{13,870}
+\DefMacro{test-results-all-model2-lc7-num-fail}{162,426}
+\DefMacro{test-results-all-model2-lc7-num-failrate}{30.44}
+\DefMacro{test-results-all-model2-lc7-num-pass-to-fail}{12,729}
 \DefMacro{test-results-bl-model2-lc7-num-fail}{3,535}
@@
 \DefMacro{test-results-bl-model2-lc4-num-failrate}{98.16}
-\DefMacro{test-results-all-model2-lc6-num-fail}{180,865}
-\DefMacro{test-results-all-model2-lc6-num-failrate}{84.10}
-\DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,130}
+\DefMacro{test-results-all-model2-lc6-num-fail}{175,323}
+\DefMacro{test-results-all-model2-lc6-num-failrate}{84.02}
+\DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,003}
 \DefMacro{test-results-bl-model2-lc6-num-fail}{865}
 \DefMacro{test-results-bl-model2-lc6-num-failrate}{86.50}
-\DefMacro{test-results-all-model2-lc5-num-fail}{118,910}
-\DefMacro{test-results-all-model2-lc5-num-failrate}{98.37}
-\DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{334}
+\DefMacro{test-results-all-model2-lc5-num-fail}{114,556}
+\DefMacro{test-results-all-model2-lc5-num-failrate}{98.35}
+\DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{325}
 \DefMacro{test-results-bl-model2-lc5-num-fail}{2,124}
 \DefMacro{test-results-bl-model2-lc5-num-failrate}{100.00}
-\DefMacro{test-results-all-model2-lc9-num-fail}{117,664}
-\DefMacro{test-results-all-model2-lc9-num-failrate}{94.97}
-\DefMacro{test-results-all-model2-lc9-num-pass-to-fail}{594}
+\DefMacro{test-results-all-model2-lc9-num-fail}{111,874}
+\DefMacro{test-results-all-model2-lc9-num-failrate}{95.05}
+\DefMacro{test-results-all-model2-lc9-num-pass-to-fail}{575}
 \DefMacro{test-results-bl-model2-lc9-num-fail}{6,440}
 \DefMacro{test-results-bl-model2-lc9-num-failrate}{84.25}
-\DefMacro{test-results-all-model2-lc2-num-fail}{363,619}
-\DefMacro{test-results-all-model2-lc2-num-failrate}{62.45}
-\DefMacro{test-results-all-model2-lc2-num-pass-to-fail}{16,527}
+\DefMacro{test-results-all-model2-lc2-num-fail}{262,994}
+\DefMacro{test-results-all-model2-lc2-num-failrate}{62.86}
+\DefMacro{test-results-all-model2-lc2-num-pass-to-fail}{9,808}
 \DefMacro{test-results-bl-model2-lc2-num-fail}{2,532}
@@
 \DefMacro{test-results-bl-model2-lc1-num-failrate}{1.44}
-\DefMacro{test-results-all-model2-lc8-num-fail}{5,702}
-\DefMacro{test-results-all-model2-lc8-num-failrate}{4.66}
-\DefMacro{test-results-all-model2-lc8-num-pass-to-fail}{1,193}
+\DefMacro{test-results-all-model2-lc8-num-fail}{5,470}
+\DefMacro{test-results-all-model2-lc8-num-failrate}{4.65}
+\DefMacro{test-results-all-model2-lc8-num-pass-to-fail}{1,151}
 \DefMacro{test-results-bl-model2-lc8-num-fail}{52}

### 2023-03-16 paper/icse24/tables/test-results-hs-all-numbers.tex
icse24

%% Automatically generated by pyutil.latex

\DefMacro{test-results-hs-lc13}{Denouncements of hate that make direct reference to it}
\DefMacro{test-results-hs-lc13-num-seeds}{17,796}
\DefMacro{test-results-hs-lc13-num-exps}{127,067}
\DefMacro{test-results-hs-bl-lc13-num-tcs}{141}
\DefMacro{test-results-hs-model0-lc13-num-all-fail}{17,060}
\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{10.60}
\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{11.94}
\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{11.78}
\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{1,070}
\DefMacro{test-results-hs-bl-model0-lc13-num-fail}{4}
\DefMacro{test-results-hs-bl-model0-lc13-num-failrate}{2.84}
\DefMacro{test-results-hs-lc12}{Denouncements of hate that quote it}
\DefMacro{test-results-hs-lc12-num-seeds}{23,728}
\DefMacro{test-results-hs-lc12-num-exps}{167,404}
\DefMacro{test-results-hs-bl-lc12-num-tcs}{173}
\DefMacro{test-results-hs-model0-lc12-num-all-fail}{20,511}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{9.47}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{10.91}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{10.73}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{1,229}
\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{17}
\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{9.83}
\DefMacro{test-results-hs-lc4}{Hate expressed through reference in subsequent clauses}
\DefMacro{test-results-hs-lc4-num-seeds}{11,968}
\DefMacro{test-results-hs-lc4-num-exps}{43,641}
\DefMacro{test-results-hs-bl-lc4-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc4-num-all-fail}{37,022}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{45.10}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{72.47}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{66.58}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{793}
\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{108}
\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{77.14}
\DefMacro{test-results-hs-lc5}{Hate expressed through reference in subsequent sentences}
\DefMacro{test-results-hs-lc5-num-seeds}{11,968}
\DefMacro{test-results-hs-lc5-num-exps}{42,416}
\DefMacro{test-results-hs-bl-lc5-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc5-num-all-fail}{35,958}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{45.19}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{72.02}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{66.12}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{783}
\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{101}
\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{75.94}
\DefMacro{test-results-hs-lc6}{Hate expressed using negated positive statement}
\DefMacro{test-results-hs-lc6-num-seeds}{39,783}
\DefMacro{test-results-hs-lc6-num-exps}{220,483}
\DefMacro{test-results-hs-bl-lc6-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc6-num-all-fail}{222,574}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{85.77}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{85.47}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{85.52}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{2,457}
\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{109}
\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{77.86}
\DefMacro{test-results-hs-lc2}{Hate expressed using profanity}
\DefMacro{test-results-hs-lc2-num-seeds}{1,064}
\DefMacro{test-results-hs-lc2-num-exps}{6,394}
\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc2-num-all-fail}{5,869}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{80.55}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{78.39}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{78.69}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{51}
\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{98}
\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{70.00}
\DefMacro{test-results-hs-lc0}{Hate expressed using slur}
\DefMacro{test-results-hs-lc0-num-seeds}{203}
\DefMacro{test-results-hs-lc0-num-exps}{1,171}
\DefMacro{test-results-hs-bl-lc0-num-tcs}{144}
\DefMacro{test-results-hs-model0-lc0-num-all-fail}{435}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{26.60}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{32.54}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{31.66}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{16}
\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{108}
\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{75.00}
\DefMacro{test-results-hs-lc9}{Hate phrased as a opinion}
\DefMacro{test-results-hs-lc9-num-seeds}{11,864}
\DefMacro{test-results-hs-lc9-num-exps}{87,996}
\DefMacro{test-results-hs-bl-lc9-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc9-num-all-fail}{84,221}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{85.45}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{84.19}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{84.34}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{999}
\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{100}
\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{75.19}
\DefMacro{test-results-hs-lc8}{Hate phrased as a question}
\DefMacro{test-results-hs-lc8-num-seeds}{11,864}
\DefMacro{test-results-hs-lc8-num-exps}{101,569}
\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc8-num-all-fail}{98,879}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{88.01}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{87.07}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{87.17}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{961}
\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{107}
\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{76.43}
\DefMacro{test-results-hs-lc10}{Neutral statements using protected group identifiers}
\DefMacro{test-results-hs-lc10-num-seeds}{6}
\DefMacro{test-results-hs-lc10-num-exps}{12}
\DefMacro{test-results-hs-bl-lc10-num-tcs}{126}
\DefMacro{test-results-hs-model0-lc10-num-all-fail}{16}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{66.67}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{88.89}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{9}
\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{7.14}
\DefMacro{test-results-hs-lc3}{Non-Hateful use of profanity}
\DefMacro{test-results-hs-lc3-num-seeds}{1,478}
\DefMacro{test-results-hs-lc3-num-exps}{7,709}
\DefMacro{test-results-hs-bl-lc3-num-tcs}{100}
\DefMacro{test-results-hs-model0-lc3-num-all-fail}{1,683}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{18.00}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{18.38}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{18.32}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{49}
\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{1}
\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{1.00}
\DefMacro{test-results-hs-lc7}{Non-hate expressed using negated hateful statement}
\DefMacro{test-results-hs-lc7-num-seeds}{17,796}
\DefMacro{test-results-hs-lc7-num-exps}{133,756}
\DefMacro{test-results-hs-bl-lc7-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc7-num-all-fail}{23,027}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{14.06}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{15.35}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{15.19}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{1,265}
\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{13}
\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{9.77}
\DefMacro{test-results-hs-lc1}{Non-hateful use of slur}
\DefMacro{test-results-hs-lc1-num-seeds}{997}
\DefMacro{test-results-hs-lc1-num-exps}{4,422}
\DefMacro{test-results-hs-bl-lc1-num-tcs}{111}
\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,835}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{71.82}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{70.53}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{70.77}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{29}
\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{18}
\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{16.22}
\DefMacro{test-results-hs-lc11}{Positive statements using protected group identifiers}
\DefMacro{test-results-hs-lc11-num-seeds}{57}
\DefMacro{test-results-hs-lc11-num-exps}{246}
\DefMacro{test-results-hs-bl-lc11-num-tcs}{189}
\DefMacro{test-results-hs-model0-lc11-num-all-fail}{151}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{52.63}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{49.19}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{49.83}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{7}
\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{23}
\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{12.17}
\DefMacro{test-results-hs-model1-lc13-num-all-fail}{100,848}
\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{69.93}
\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{69.57}
\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{69.62}
\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{1,594}
\DefMacro{test-results-hs-bl-model1-lc13-num-fail}{7}
\DefMacro{test-results-hs-bl-model1-lc13-num-failrate}{4.96}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{117,788}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{61.67}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{61.62}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{61.63}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{2,440}
\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{5}
\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{2.89}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{30,276}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{51.40}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{55.28}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{54.44}
\DefMacro{test-results-hs-model1-lc4-num-pass-to-fail}{855}
\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{93}
\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{66.43}
\DefMacro{test-results-hs-model1-lc5-num-all-fail}{31,195}
\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{52.92}
\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{58.61}
\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{57.36}
\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{721}
\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{69}
\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{51.88}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{152,929}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{55.55}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{59.34}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{58.76}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{4,365}
\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{116}
\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{82.86}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{1,115}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{14.00}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{15.11}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{14.95}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{69}
\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{93}
\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{66.43}
\DefMacro{test-results-hs-model1-lc0-num-all-fail}{26}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{1.48}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{1.96}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{1.89}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{12}
\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{56}
\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{38.89}
\DefMacro{test-results-hs-model1-lc9-num-all-fail}{27,637}
\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{27.08}
\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{27.76}
\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{27.68}
\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{1,348}
\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{109}
\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{81.95}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{33,589}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{28.51}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{29.74}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{29.61}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{1,305}
\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{123}
\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{87.86}
\DefMacro{test-results-hs-model1-lc10-num-all-fail}{1}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{16.67}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{5.56}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{0}
\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-all-fail}{5,160}
\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{63.19}
\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{54.82}
\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{56.17}
\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{120}
\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{1}
\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{1.00}
\DefMacro{test-results-hs-model1-lc7-num-all-fail}{113,265}
\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{75.11}
\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{74.69}
\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{74.74}
\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{1,626}
\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{26}
\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{19.55}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{4,484}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{87.26}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{81.73}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{82.75}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{70}
\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{68}
\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{61.26}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{73}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{38.60}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{20.73}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{24.09}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{1}
\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{16}
\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{8.47}

### 2023-03-16 paper/icse24/tables/test-results-hs-table.tex
icse24

--- 2023-01-18 paper/fse23/tables/test-results-hs-table.tex
@@
 \caption{\TestResultsHsTableCaption}
-\resizebox{0.7\textwidth}{!}{
+\resizebox{0.8\textwidth}{!}{
 \begin{tabular}{p{8cm}||ccclll}
@@
 \hline
-\multirow{2}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-lc14}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc14-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc14-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc14-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc14-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc14-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-lc15}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc15-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc15-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc15-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc15-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc15-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-lc16}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc16-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc16-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc16-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc16-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc16-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-lc17}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc17-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc17-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc17-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc17-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc17-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-pass-to-fail}\\
-\hline
-\multirow{2}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-lc18}}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc18-num-tcs}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-seeds}}
- & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-exps}}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc18-num-fail}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc18-num-failrate}
- & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-pass-to-fail}\\
- & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc18-num-fail}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc18-num-failrate}
- & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-pass-to-fail}\\
-\hline
 \bottomrule

### 2023-03-16 paper/icse24/threats.tex
icse24

--- 2022-08-29 paper/icse23/threats.tex
@@
 domain~\cite{husnain2021swnvalidity}.
-Second, using ranges of the sentiment scores in SST-2 to determine the sentiment labels of search dataset may introduce incorrect labels. We performed a manual study to confirm that this is rare. 
+Second, using ranges of the sentiment scores in \Sst and majority voting 
+method in \Hatexp to determine the sentiment labels of search dataset may 
+introduce incorrect labels. We performed a manual study to confirm that 
+this is rare. 
 % Use of publicly available datasets poses an external validity threat
@@
 % reference CFG from publicly available corpus dataset
-\cite{mitchell1993treebank, nltkTreebankCorporaWebPage}.
+% \cite{mitchell1993treebank, nltkTreebankCorporaWebPage}.

### 2023-06-08 paper/icse24/tables/lc-requirement-numbers.tex

@@
 \DefMacro{lc_1_desc}{Short sentences with neutral adjectives and nouns}
-\DefMacro{lc_1_search}{\textbf{Search-based:}~\textbf{hasattr}(length,<10)\land
-\textbf{hasattr}(label,neutral)\land(\textbf{contain}(tag\_of\_pos,neutral\_adj)\lor
-\textbf{contain}(tag\_of\_pos,neutral\_noun))\land~\neg(\textbf{contain}(tag\_of\_pos,positive\_adj)\lor
-\textbf{contain}(tag\_of\_pos,positive\_noun)\lor~\textbf{contain}(tag\_of\_pos,negative\_adj)\lor
+\DefMacro{lc_1_predicates}{$Seed\leftarrow$\textbf{hasattr}(length,<10)$\land$
+\textbf{hasattr}(label,neutral)$\land$(\textbf{contain}(tag\_of\_pos,neutral\_adj)$\lor$
+\textbf{contain}(tag\_of\_pos,neutral\_noun))$\land$~\neg(\textbf{contain}(tag\_of\_pos,positive\_adj)$\lor$
+\textbf{contain}(tag\_of\_pos,positive\_noun)$\lor$~\textbf{contain}(tag\_of\_pos,negative\_adj)$\lor$
 \textbf{contain}(tag\_of\_pos,negative\_noun))}
-\DefMacro{lc_1_transform}{\textbf{Enumerative:}~N/A}
 \DefMacro{lc_2_desc}{Short sentences with sentiment-laden adjectives}
-\DefMacro{lc_2_search}{\textbf{Search-based:}~\textbf{hasattr}(length,$<$10)$\land$((\textbf{contain}
-(pos,positive$\_$adj)$\lor$\textbf{contain}(pos,positive$\_$noun)$\land$\textbf{hasattr}(label,positive))$\lor$(\textbf{contain}(pos,negative$\_$adj)$\lor$\textbf{contain}(pos,negative$\_$noun)$\land$\textbf{hasattr}(label,negative)))}
-\DefMacro{lc_2_transform}{\textbf{Enumerative:}~N/A}
+\DefMacro{lc_2_predicates}{$Seed\leftarrow$\textbf{hasattr}(length,$<$10)$\land$((\textbf{contain}
+(tag\_of\_pos,positive$\_$adj)$\lor$\textbf{contain}
+(tag\_of\_pos,positive$\_$noun)
+$\land$\textbf{hasattr}(label,positive))$\lor$(\textbf{contain}
+(tag\_of\_pos,negative$\_$adj)$\lor$\textbf{contain}(tag\_of\_pos,negative$\_$noun)$\land$\textbf{hasattr}(label,negative)))}
 \DefMacro{lc_3_desc}{Sentiment change over time, present should prevail}
-\DefMacro{lc_3_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,positive), neg\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,negative)}
-\DefMacro{lc_3_transform}{
-\textbf{Enumerative:}~E1=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(Previously, I used to like it saying that|Last time, I agreed with saying that|I liked it much as to say that), sent=pos\_sent, infix=(but|although|on the other hand), postfix=(now I don't like it.|now I hate it.)
-
-E2=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(I used to disagree with saying that|Last time, I didn't like it saying that|I hated it much as to say that), sent=neg\_sent, infix=(but|although|on the other hand), postfix=(now I like it.)}
+\DefMacro{lc_3_predicates1}{$Seed\leftarrow$\textbf{combine}(prefix1,$S_{pos}$,infix,postfix1)$+$\textbf{combine}(prefix2,$S_{neg}$,infix,postfix2)}
+\DefMacro{lc_3_predicates2}{prefix1$:=$``Previously, I used to like it saying that''|``Last time, I agreed with saying that''|``I liked it much as to say that''}
+\DefMacro{lc_3_predicates3}{$S_{pos}\leftarrow$\textbf{hasattr}(length,<20)$\land$\textbf{hasattr}(label,positive)}
+\DefMacro{lc_3_predicates4}{infix$:=$``but''|``although''|``on the other hand''}
+\DefMacro{lc_3_predicates5}{postfix1$:=$``now I don't like it.''|``now I hate it.''}
+\DefMacro{lc_3_predicates6}{prefix2$:=$``I used to disagree with saying that''|``Last time, I didn't like it saying that''|``I hated it much as to say that''}
+\DefMacro{lc_3_predicates7}{$S_{neg}\leftarrow$\textbf{hasattr}(length,<20)$\land$\textbf{hasattr}(label,negative)}
+\DefMacro{lc_3_predicates8}{postfix2$:=$``now I like it.''}
 \DefMacro{lc_4_desc}{Negated negative should be positive or neutral}
-\DefMacro{lc_4_search}{\textbf{Search-based:}~\textbf{hasattr}(word,`(This|That|These|Those)~(is|are)')\land\textbf{hasattr}(label,negative)}
-\DefMacro{lc_4_transform}{\textbf{Transform:}~\textbf{replace}(is->is not,isn't'|are->are not,aren't)}
+\DefMacro{lc_4_predicates1}{$Seed\leftarrow$\textbf{replace}($S$, ``is'', [``is not'',``isn't''])$+$\textbf{replace}($S$, ``are'', [``are not'',``aren't''])}
+\DefMacro{lc_4_predicates2}{$S\leftarrow$\textbf{hasattr}(clause,`(This|That|These|Those)~(is|are)')$\land$\textbf{hasattr}(label,negative)}
 \DefMacro{lc_5_desc}{Negated neutral should still be neutral}
-\DefMacro{lc_5_search}{\textbf{Search-based:}~\textbf{hasattr}(word,`(This|That|These|Those)~(is|are)')\land\textbf{hasattr}(label,neutral)}
-\DefMacro{lc_5_transform}{\textbf{Transform:}~\textbf{replace}(is->is not,isn't'|are->are not,aren't)}
+\DefMacro{lc_5_predicates1}{$Seed\leftarrow$\textbf{replace}($S$, ``is'', [``is not'',``isn't''])$+$\textbf{replace}($S$, ``are'', [``are not'',``aren't''])}
+\DefMacro{lc_5_predicates2}{$S\leftarrow$\textbf{hasattr}(clause,`(This|That|These|Those)~(is|are)')$\land$\textbf{hasattr}(label,neutral)}
 \DefMacro{lc_6_desc}{Negation of negative at the end, should be positive or neutral}
-\DefMacro{lc_6_search}{\textbf{Search-based:}~$neg\_sent\rightarrow\textbf{hasattr}(label,negative)$}
-\DefMacro{lc_6_transform}{\textbf{Enumerative:}~\textbf{combine}(prefix,sent,postfix) where prefix=(I agreed that$|$I thought that), sent=neg$\_$sent, postfix=(but it wasn't|but I didn't)}
+\DefMacro{lc_6_predicates1}{$Seed\leftarrow$\textbf{combine}(prefix,$S_{neg}$,postfix)}
+\DefMacro{lc_6_predicates2}{prefix$:=$``I agreed that''|``I thought that''}
+\DefMacro{lc_6_predicates3}{$S_{neg}\leftarrow$\textbf{hasattr}(label,negative)}
+\DefMacro{lc_6_predicates4}{postfix$:=$``but it wasn't''|``but I didn't''}
 \DefMacro{lc_7_desc}{Negated positive with neutral content in the middle}
-\DefMacro{lc_7_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,positive),
-neutral\_sent\rightarrow\textbf{hasattr}(length,<20)\land\textbf{hasattr}(label,neutral)}
-\DefMacro{lc_7_transform}{
-\textbf{Enumerative:}~\textbf{combine}(prefix,sent,infix,postfix) where prefix=(I$\,$wouldn't$\,$say,|I$\,$do$\,$not$\,$think,|I$\,$don't$\,$agree$\,$with,), sent=neutral\_sent, infix=`,', postfix=pos\_sent}
+\DefMacro{lc_7_predicates1}{$Seed\leftarrow$\textbf{combine}(prefix,$S_{neutral}$,infix,$S_{pos}$)}
+\DefMacro{lc_7_predicates2}{prefix$:=$``I wouldn't say,''|``I do not think,''|``I don't agree with''}
+\DefMacro{lc_7_predicates3}{$S_{neutral}\leftarrow$\textbf{hasattr}(length,<20)$\land$\textbf{hasattr}(label,neutral)}
+\DefMacro{lc_7_predicates4}{infix$:=$`,'}
+\DefMacro{lc_7_predicates5}{$S_{pos}\leftarrow$\textbf{hasattr}(length,<20)$\land$\textbf{hasattr}(label,positive)}
 \DefMacro{lc_8_desc}{Author sentiment is more important than of others}
-\DefMacro{lc_8_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(label,positive), neg\_sent\rightarrow\textbf{hasattr}(label,negative)}
-\DefMacro{lc_8_transform}{\textbf{Enumerative:}~T1=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(Some people think that|Many people agree with that|They think that|You agree with that), sent=pos\_sent, infix=(but I think that), postfix=neg\_sent,
-
-T2=\textbf{combine}(prefix,sent,infix,postfix) where prefix=(Some people think that|Many people agree with that|They think that|You agree with that), sent=neg\_sent, infix=(but I think that), postfix=pos\_sent}
+\DefMacro{lc_8_predicates1}{$Seed\leftarrow$\textbf{combine}(prefix1,infix,$S_{neg}$)$+$\textbf{combine}(prefix2,infix,$S_{pos}$)}
+\DefMacro{lc_8_predicates2}{prefix1$:=$``Some people think that''|``Many people agree with that''|``They think that''|``You agree with that''}
+\DefMacro{lc_8_predicates3}{infix$:=$``but I think that''}
+\DefMacro{lc_8_predicates4}{$S_{neg}\leftarrow$\textbf{hasattr}(label,negative)}
+\DefMacro{lc_8_predicates5}{prefix2$:=$``Some people think that''|``Many people agree with that''|``They think that''|``You agree with that''}
+\DefMacro{lc_8_predicates6}{$S_{pos}\leftarrow$\textbf{hasattr}(label,positive)}
 \DefMacro{lc_9_desc}{Parsing sentiment in (question, yes) form}
-\DefMacro{lc_9_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(label,positive), neg\_sent\rightarrow~\textbf{hasattr}(label,negative)}
-\DefMacro{lc_9_transform}{\textbf{Enumerative:}~\textbf{combine}(prefix,sent,postfix) where prefix=(Do I think that|Do I agree that), sent=(pos\_sent|neg\_sent), postfix=`? yes'}
+\DefMacro{lc_9_predicates1}{$Seed\leftarrow$\textbf{combine}(prefix,$S_{pos}$,postfix)$+$\textbf{combine}(prefix,$S_{neg}$,postfix)}
+\DefMacro{lc_9_predicates2}{prefix$:=$``Do I think that''|``Do I agree that''}
+\DefMacro{lc_9_predicates3}{$S_{pos}\leftarrow$\textbf{hasattr}(label,positive)}
+\DefMacro{lc_9_predicates4}{postfix$:=$`? yes'}
+\DefMacro{lc_9_predicates5}{$S_{neg}\leftarrow$~\textbf{hasattr}(label,negative)}
 \DefMacro{lc_10_desc}{Parsing sentiment in (question, no) form}
-\DefMacro{lc_10_search}{\textbf{Search-based:}~pos\_sent\rightarrow\textbf{hasattr}(label,positive), neg\_sent\rightarrow~\textbf{hasattr}(label,negative)}
-\DefMacro{lc_10_transform}{\textbf{Enumerative:}~\textbf{combine}(prefix,sent,postfix) where prefix=(Do I think that|Do I agree that), sent=(pos\_sent|neg\_sent), postfix=`? no'}
+\DefMacro{lc_10_predicates1}{$Seed\leftarrow$\textbf{combine}(prefix,$S_{pos}$,postfix)$+$\textbf{combine}(prefix,$S_{neg}$,postfix)}
+\DefMacro{lc_10_predicates2}{prefix$:=$``Do I think that''|``Do I agree that''}
+\DefMacro{lc_10_predicates3}{$S_{pos}\leftarrow$\textbf{hasattr}(label,positive)}
+\DefMacro{lc_10_predicates4}{postfix$:=$`? no'}
+\DefMacro{lc_10_predicates5}{$S_{neg}\leftarrow$~\textbf{hasattr}(label,negative)}
